### 2011-12-22 tr-semanticsearchsurvey-data/mr.tex

\section{Matching \& Ranking in Semantic Data Retrieval}

\subsection{Query-Independent Ranking}
- Existing approaches based on PageRank

\subsection{Term-based Matching \& Ranking}
- Does not consider structure information \\
- Most existing engines use simple TF/IDF term weighting, do not take structure information into account

\subsection{Term-based Matching \& Structured-based Ranking}
- Take structure of data \& results into account for ranking\\
-	BM25F\\
- Language model for structured results

\subsection{Term- and Structure-based Matching \& Ranking} 
-	Matching: take structure of data account for computing structured results

### 2011-12-22 tr-semanticsearchsurvey-data/overview.tex

\section{Taxonomy of Semantic Search Approaches}
In this section, we identify the main dimensions in which existing solutions vary and then, provide a taxonomy of semantic search approaches.

Search is about retrieving information that are relevant with respect to a given information need. Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs. Generally, they can be defined in terms of the following main dimensions, i.e.

\begin{itemize}
\item the \emph{type of information needs} targeted by the system,  
\item the representation of the information need called the \textit{query}, 
\item the representation of the underlying \textit{information} called \emph{data}, 
\item the \emph{semantic models} used to interpret query and data and 
\item the techniques for \emph{matching} the query against the data and for \emph{ranking} the results.  
\end{itemize}

A general overview of the types of information needs, queries, data, semantic models and matching and ranking techniques supported by existing semantic search approaches is illustrated in Fig.~\ref{}. We will now discuss these approaches along these different dimensions.

\subsection{Information Needs}
Document search, entity search, factual search, relational search

\subsection{Queries}
Search is about end-user oriented interfaces: NL, keywords, facets

\subsection{Data}
Objects (documents, media and multimedia objects) with embedded semantic data, semantic datasets

\subsection{Semantic Models}
Linguistic models, conceptual models

\subsection{Matching \& Ranking Techniques}
Term-based, structure-based, semantic-based

%Generally, queries might be simple keywords, natural language or structured. Various kind of formal query languages have been proposed to formulate highly expressive (both in terms of structure and semantics) queries. Resources returned to the users range from text, audio and video up to multimedia documents. These documents embody different types of data, i.e. unstructured, semi-structured (in the form of RDF) that is not associated with a schema and fully structured data with a schema. Often, structured data available in Semantic Web languages such as RDF and OWL is also referred to as ``semantic data''.  Different matching framework are employed by these systems. IR systems primarily rely on features at the level of terms (language, words) whereas DB and KB systems exploit also the structure as well as the semantics for matching. On the other hand, while these DB and KB systems are concerned with producing precise matches (binary matching), IR systems rely on statistical methods that are inherently imprecise such that results are also associated with the degree of matching, i.e. IR systems perform imprecise matching and ranking. 
%
%Apart from these main aspects, semantic search systems can also be distinguished in terms of the notion of semantics that is employed for search.  
%
%\subsection{Semantic Models}
%Generally, semantics is concerned with the meaning of things. Meaning is established through a semantic model, which commonly captures interrelationships between elements and their interpretations. Various semantic models have been proposed and
%used in different research communities. The IR community typically relies on \textit{linguistic
%models} such as taxonomies and thesauri that capture relations between syntactical elements, i.e. words. In
%the database community, \textit{conceptual models} such as Entity Relationship (ER)
%diagrams are used to capture relations between entities
%\cite{DBLP:journals/tods/Chen76}. Thus, while linguistic models are concerned with meanings at the level of words, conceptual models more specifically deal with meanings at the level of real-world entities denoted by words. That is, conceptual models deal with interpretation of words in terms of real world entities the words refer to. Besides ER diagrams, conceptual models include less formal models such as semantic networks [cite] and very formal models such as logic-based theories, where interpretations are precise and computable \cite{DBLP:books/sp/StaabS04}.
% 
%In the Semantic Web community, \textit{ontologies} have received widespread acceptance. The notion of
%ontologies employed by this community is very general. Ontologies
%constitute rather a family of models, which might differ in the
%degree of expressiveness and formality, ranging from simple
%taxonomies and shallow conceptual model represented in RDF(S)
%to expressive formal models represented in Description Logics \cite{DBLP:books/sp/StaabS04}. Thus, ontologies include both linguistic and conceptual models. In practice, ontologies do not come only with the conceptual part but might also contain instances. In this sense, they are similar to databases (and knowledge bases) where the conceptual part corresponds to what is refer to as the schema (terminological knowledge) and instances correspond to the actual data of the database (assertional knowledge of the knowledge base).  
%
%\subsection{Semantic Search}
%As a general notion, a system essentially performs semantic search when a semantic model is employed. As illustrated in Fig. \ref{fig:semsearch}, a semantic model might be used to make sense of the data, to interpret the query and ultimately, to support matching that goes beyond the traditional term-based matching.  
%
%\begin{figure}
%	\centering
%		\includegraphics[width=0.5\textwidth]{figs/semsearch.pdf}
%	\label{fig:semsearch}
%	\caption{Semantic Search}
%\end{figure}
%
%\subsubsection{The DB\&KB Perspective}
%In retrieving data, semantics has always play an essential role in database systems. The foundation of database technologies manifested in theoretical models such as the relational model that provides formal semantics to both resources and queries, i.e. the model behind relational data and relational query (an important part of SQL) is in fact a fragment of first-order logic [cite]. This semantics is taken into account by database query engines to compute answers that precisely match the semantics of queries. More precisely, these engines perform binary matching that incorporates not only terms (i.e. constants) but also structure and semantics into account. Using this mechanism, information needs of different complexity have been served. In different commercial systems, we find the application of DB technologies in the form of simple product search (e.g. in commercial shopping sites like Ebay and Amazon) up to complex relational queries that are used to populate complex dynamic Web pages. 
%
%While the relational model is the one most widely used in practice, there exists also domain specific solutions that are built upon more expressive models. In the realm of deductive databases for instance, semantics represented in languages such Datalog or F-Logic is used to perform reasoning, with the goal of understanding and delivering not only explicitly asserted information, but also inferred one. Further down this steam, semantic models that are even more expressive are used by knowledge-based expert systems for answering complex questions. [TODO: applications of expert systems]
%
%
%\subsubsection{The IR Perspective}
%In the IR community, the representation of the information needs as well as resources is achieved primarily using lightweight models that operates at the level of words. In particular, the predominant paradigm is based on keyword queries and bag-of-words representation of resources. This works and most importantly, scales well for topical search, i.e. to retrieve documents based on topics expressed in terms of keywords, but is not sufficient to address the kind of complex information needs that can be served by DB and KB systems. 
%
%The need for going beyond the matching purely based on words and statistical dependencies that exist between them has been clearly expressed by leading researchers in the field. In the early years of IR research, Riksbergen clearly argue for the use of semantics. In order to return precise results to the user, it is essential to compute whether the resources semantically entail what the user ask for [cite]. Quoting a paper from W.B. Croft et al. published more than twenty years ago [cite]: ``The statistical approach has many advantages and can achieve a reasonable level of effectiveness with techniques that are very efficient. However, it appears that to achieve significant improvements in retrieval effectiveness compared to current techniques, systems must be designed to acquire and use explicit domain knowledge''. This explicit domain knowledge are captured using semantic models of varying degrees. Semantic networks have been used augment the models based on terms. This provide a richer representation which is exploited for assisted query formulation, query expansion, as well as for relevance propagation in ranking [cite].  Also, linguistic models particularly Wordnet and the Roget’s thesaurus have been widely used. 
%
%Recently, the IR community continues to embrace the vast body of explicit knowledge that increasingly, is made publicly available. There are approaches which not only use semantic models to enrich terms, but in fact, employ both the conceptual and the data part. In particular, there are systems that use ontologies including the semantic data contained in them [cite].   TODO: Applications: enterprise solutions such as IBM Avatar, Medline, Web solutions such as Hakia, Powerset. 
%
%
%\subsubsection{The SW Perspective}
%Semantic search from the this point of view is more similar to the DB and KB perspective in the sense that the main goal is to obtain precise answers for complex questions. However, while DB and KB systems are adopted to solve specific problems of a particular domain, semantics is taken by this community to the wider context of the Web. Semantic models used here are ontologies available in the W3C languages for resource description, namely RDF and OWL. 
%, while SPARQL is the primary mean to express information needs.
%On the Semantic Web, there is more data that is more hetetorogenous, i.e. data coming from different sources that differs in syntax, formats and quality. Thus, unlike traditional DB and KB systems, SW search engine are built with particular emphasis on the ability to scale in terms of both volume and the number of sources, to be domain independent and to perform ranking. 
%
%To achieve this, they are built upon concepts and technologies from database and expert systems. General concepts for data management (e.g. indexing and data partitioning []) as well as specific concepts for managing graph structured data and graph databases (e.g. structure indexes from XML databases []) have been adopted to deal with ontologies and semantic data available in RDF and OWL. For dealing with more expressive semantic models, techniques commonly applied in deductive databases (e.g. magic set optimizations [cite]) have been adopted to improve the efficiency and scalability of reasoning. However, to deal with scale and to perform ranking, techniques that are more commonly used by the IR technology has also been adopted. For instance, the inverted index has been used to scale to a large amount of data and to support term-based matching. Statistical dependencies of words such TF-IDF as well as authority-based metrics such as PageRank that is popular in IR web search engines, have been used for ranking. 
%
%TODO: Applications
%
%
%
%To summarize, semantics has proven to be useful for search in many aspects. There are commercial exploitations, which used semantics in different ways. Thus, the notion of semantic search is thus very broad. Semantic search covers the wide range of systems employing and exploiting semantic models of varying expressiveness. In the following sections, we will focus on semantic search systems driven by the IR and the SW communities which recently, have attracted much research and commercial interests.

### 2011-12-22 tr-semanticsearchsurvey-data/sdt.tex

\section{Semantic Data Retrieval}
\subsection{Applications} 
\subsection{Semantic Data Retrieval Process} 
- Crawling, integration, indexing, matching \& ranking, result presentation \\

\subsection{Taxonomy of Semantic Data Retrieval Approaches}
- overview of existing approaches categorized along the dimensions: need, data, queries, targeted task in the process \\
- following survey focus on keyword queries  \\

\subsection{Semantic Data Crawling} 
\subsection{Semantic Data Integration}
\subsection{Semantic Data Storage and Indexing}
\subsection{Semantic Search Result Presentation}

### 2011-12-22 trunk/tr-semanticsearchsurvey-data/intro.tex

\section{Introduction}
% unsolved information needs%
Advancements in search technologies enable users to deal and to exploit the ever increasing amount of information that we can find in different scenarios -- from the personal desktop to enterprises' databases up to the large-scale Web. As opposed to the structured querying capabilities commonly provided by commercial databases that are only accessible by experts, \emph{search} is rather understood as a \emph{end-user oriented paradigm} that is based on \emph{intuitive interfaces} and access mechanisms. Solutions that are widely used especially on the Web are based on \emph{keyword search}, and in smaller-scale scenarios, also support natural language (NL) inputs. While they are easy to use, the inputs provided by the users through these interfaces are \emph{ambiguous} such that the underlying information need (query intent) is not directly accessible to the system. Further, there are search scenarios where not only the query, but also the data representation does not precisely capture the semantics and structure of the underlying information. Accordingly, the core problems to be addressed in search are to \emph{understand the query intent and the data}, to \emph{match query against data}, and to \emph{rank results}.

\subsection{Many Unsolved Long-tail Queries}
Modern search engines can effectively interpret the topics and based on that, disambiguates the need intended in the provided query inputs. Combining with additional (query-independent) factors such as PageRank, they are able to address a large fraction fraction of common information needs. In particular, queries that request for pages about a particular topic (\emph{topical query}) or representing popular entry points to commonly used information that can be reached via further browsing activities (\emph{navigational queries}), can be successfully processed. However, dealing with the large number of distinct queries in the ``long tail'' of Web query logs \cite{} remains challenging. Two particular categories of problematic cases are ambiguous and complex queries:

\begin{itemize}
	\item \emph{Ambiguous queries}: these queries contain ambiguous terms, resulting in many possible interpretations (several query intents). For instance, the following query ask for entities (entity query): 
	\dtr{change running example} “Paris Hilton” “strong adventures people from Germany”

	\item \emph{Complex queries}: this class of queries capture complex information needs which may involve several entities and relationships between them. As an example, we have a query that mentions several entity and ask for relationships between them (relational queries):  
	\dtr{change running example} “32 year old computer scientist living in Karlsruhe” “digital camera under 300 dollars produced by canon in 1992”
\end{itemize}

Clearly, these two categories represent orthogonal aspects, namely the \emph{ambiguity of query terms} and the \emph{complexity of the intended information need}. Many queries in the long tail are both ambiguous and complex. They require deep understanding of the need and the information behind the query and data, respectively.

\subsection{Large Amount of Semantic Data}
Targeting these problematic cases, semantic search solutions aim at exploiting the large and increasing amount of semantic resources that have been made available in different settings. These resources include taxonomies, thesauri and formal ontologies that can be used for the interpretation of query terms and data representation. More generally, also structured data exposed as graph-structured RDF data belong to this type of semantic resources (henceforth called \emph{semantic data}) that are used for semantic search. They come as standalone RDF datasets or are embedded in Web pages in the form of RDFa. These data have been increasing rapidly. As a result of community projects such as Linking Open Data~\footnote{}, a large amount of structured datasets formerly kept protected in databases are now exposed as publicly Web-accessible RDF data. Besides large companies such as BestBuy and Facebook, also national governments such as the US and UK have followed this direction of publishing and linking semantic data on the Web. As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups~\cite{}.

The main idea behind semantic search solutions is to use these semantic resources to improve the search performance. Taxonomies, thesauri, and ontologies capture semantics that can be used to understand the query and data and to resolve ambiguities. Instead of returning textual data in documents, precise facts capturing entity related information and their relationships can be directly retrieved from semantic data to provide \emph{direct answers} to complex queries.

\subsection{Plethora of Semantic Search Solutions}
Capitalizing on the opportunities that arise from this increasing wealth of semantic resources on the Web, commercial search engines have made different kinds of semantic search features available to end users. The first well-known example towards this direction is Powerset, which makes use of semantic data extracted from Wikipedia to answer complex questions. Semantic data embedded in Web pages are now actively used by Google to provide rich result snippets\footnote{}.

Likewise, research interest in semantic search is stirring up. A large body of work has been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web. Correspondingly, semantic search has been viewed from different angles, resulting in a plethora of solutions. While underlying all these efforts lie one central idea, namely to use semantic resource for more effective search, existing approaches greatly vary in the information needs, the query and the data that are supported. Hence, different concepts and techniques have been studied in these settings. Most notably, there are principle differences between semantic search approaches, which use semantic resource to improve document retrieval, and the ones that compute direct results, i.e. \emph{semantic data retrieval}.

\subsection{Contributions}
Concepts for semantic search have been around for several several years and its mainstream adoption into commercial solutions is increasingly visible.

\begin{itemize}
	\item In this work, we present a systematic survey to provide a \emph{taxonomy of various semantic search approaches}, to reflect on the achievements that have been made over these years, and finally, to discuss the remaining challenges and directions for future research. To the best of our knowledge, the only work... 
	\item Besides this general overview, we discuss the \emph{state-of-the-art in semantic data retrieval}, a direction of semantic search that aims at direct results as answers. For this, different data management and processing tasks are needed, from the crawling and integration of data up to the computation and presentation of results. 
	\item We present specific solutions that have been proposed for these individual tasks. Particular emphasis is put on the most commonly used interface, namely \emph{keyword search}, and the concepts and techniques for dealing with the core search tasks of \emph{matching and ranking}.

\end{itemize}

\subsection{Outline}

### 2012-01-18 tr-semanticsearchsurvey-data/intro.tex

--- 2011-12-22 trunk/tr-semanticsearchsurvey-data/intro.tex
@@
 	\item \emph{Ambiguous queries}: these queries contain ambiguous terms, resulting in many possible interpretations (several query intents).
-For instance, the following query ask for entities (entity query):
-	\dtr{change running example} “Paris Hilton” “strong adventures people from Germany”
+For instance, the query ``young scholars from Germany'' is difficult to processed because without any additional context, it is not clear who is ``young'', and different types of people may be considered as ``scholars''.
 
 	\item \emph{Complex queries}: this class of queries capture complex information needs which may involve several entities and relationships between them.
-As an example, we have a query that mentions several entity and ask for relationships between them (relational queries):
-	\dtr{change running example} “32 year old computer scientist living in Karlsruhe” “digital camera under 300 dollars produced by canon in 1992”
+As an example, we have a query that mentions a person and a location, and asks for a relationship between that person and another location (relational queries):  ``birthplace of 32 year old computer scientist, who lives in Karlsruhe, a city in Germany''.
 \end{itemize}
@@
 These data have been increasing rapidly.
-As a result of community projects such as Linking Open Data~\footnote{}, a large amount of structured datasets formerly kept protected in databases are now exposed as publicly Web-accessible RDF data.
+As a result of community projects such as Linking Open Data\footnote{}, a large amount of structured datasets formerly kept protected in databases are now exposed as publicly Web-accessible RDF data.
 Besides large companies such as BestBuy and Facebook, also national governments such as the US and UK have followed this direction of publishing and linking semantic data on the Web.
-As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups~\cite{}.
+As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups such as RDFa~\cite{}.
 

### 2012-01-18 tr-semanticsearchsurvey-data/overview.tex

@@
 \section{Taxonomy of Semantic Search Approaches}
+Semantic search is a concept widely used by different communities to refer to retrieval approaches that aim to \emph{exploit the semantics behind data and query to improve the search experience}.
+Semantics here is to be understood in general terms, which may be captured as conceptual knowledge through \emph{semantic models} such as taxonomies, ontologies and data schemas, or as \emph{semantic data} representing concrete information about individual entities.
+While they all share this core idea, the retrieval context as well as the semantic resources used to represent or understand the meaning behind the query intent and data vary.
+
+\emph{Document Retrieval:} The IR community targets the document retrieval context where results are to be retrieved from a collection of documents.
+The traditional type of semantic models used here comprises of taxonomies, thesauri and dictionaries that are mainly employed to understand the \emph{terms} in the textual \emph{content} of queries and data (i.e.
+documents).
+Recently, semantic data such as RDF resource descriptions have also been employed to understand query and documents in terms of real-world \emph{entities} and their \emph{relationships}.
+
+\emph{Data Retrieval:} Querying entities and their relationships is a core problem in database research.
+As opposed to the hidden semantics of textual content in documents, information about entities and their relationships are explicitly available in this setting -- either directly as semantic data in RDF or as structured data that can be converted to RDF.
+Thus, understanding the semantics of the underlying data is not the problem here.
+However, as opposed to classic data retrieval that is based on structured query languages, data \emph{search} is regarded as an end-user oriented paradigm that is characterized by the use of (1) intuitive query interfaces and (2) ranking.
+Just like in the document context, the goal here is to enable easy access to the most relevant results.
+Especially in the Semantic Web community, solutions targeting this problem are also referred to as semantic search because they use semantic data to interpret the query intent and to rank results.
+
 In this section, we identify the main dimensions in which existing solutions vary and then, provide a taxonomy of semantic search approaches.
-
-Search is about retrieving information that are relevant with respect to a given information need.
-Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs.
-Generally, they can be defined in terms of the following main dimensions, i.e.
+We focus on approaches studied by researchers in the Semantic Web community that explicitly target semantic search.
+Selectively, we also point out works from the IR and database communities that deal with the same problem.
+%Search is about retrieving information that are relevant with respect to a given information need. 
+%Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs.
+They can be characterized in terms of the following main dimensions, i.e.
 
@@
 \item the \emph{type of information needs} targeted by the system,  
-\item the representation of the information need called the \textit{query}, 
+\item the representation of the information need called \textit{query}, 
 \item the representation of the underlying \textit{information} called \emph{data}, 
-\item the \emph{semantic models} used to interpret query and data and 
-\item the techniques for \emph{matching} the query against the data and for \emph{ranking} the results.  
+\item the \emph{semantic models} used to understand query and data, 
+\item the framework for \emph{matching} queries against data, which due to ambiguities, also involves \emph{interpreting} the content and the user intent and \emph{ranking} of results.  
 \end{itemize}
@@
 \subsection{Information Needs}
-Document search, entity search, factual search, relational search
+The main motivation for semantic search is to go beyond the relatively frequent but simple queries currently supported by existing search solutions to solve the long-tail queries representing rather complex information needs.
+But also for simple queries, semantic data have proven to be valuable.
+Instead of showing documents, semantic data are used by commercial Web search engines to create rich snippets for Web pages, or to deliver direct answers.
+
+\begin{itemize}
+	\item \emph{Entity search}: most queries on the Web asked for Web pages representing entities such as organization or people.
+They are used to obtain entry points, while additional navigation and browsing is still required to satisfy the actual information need.
+Thus, these queries are also referred to as navigational queries.
+Semantic data embedded in Web pages have been exploited by Google to present rich entity snippets\footnote{Google Rich Snippets} to this kind of queries.
+Instead of searching over a collection of documents, semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results.
+An example query for this is the one asking for ``young scholars in Germany'' already mentioned before.
+Results for queries of this type comprise one or several entities.
+
+	\item \emph{Factual search}: While results to the previous type of queries presented to the users are either some entity descriptions or Web pages about entities, the information needs behind this type of search require specific information from these descriptions and pages, respectively.
+Many searches on the Web for instance, aim at finding the ratings of restaurants, or the phone number of a particular person.
+To continue with our example, users may directly ask for ``the birth place of young scholars in Germany''.
+Direct answers to this type of queries are supported by Powerset\footnote{}, WolframAlpha\footnote{\url{http://www.wolframalpha.com/}}, or research prototypes such as Hermes and PowerAqua.
+	\item \emph{Relational search}: The information need here goes beyond single entities and their factual information.
+Answers to queries of this type comprise several entities and relationships between them.
+Hence, processing these queries requires some understanding of relations between entities.
+For instance, the example presented in the introduction about 32 year old computer scientists requires knowledge about their \verb+lives in+ and \verb+birth place+ relations to some locations.
+Relations may be explicitly specified as part of the keyword or NL query, and entities satisfying these relation constraints can be computed using SemSearchPro or Aqualog\dtr{}.
+Other systems such as NAGA also support searches where relations to be considered are not explicitly mentioned in the query, or unknown.
+They address information needs that involve finding ``how some entities are related to some other entities''.
+The interesting part of the results here are thus not the entities, but the relationships between them -- also referred in literatures as Semantic Associations (direct connection) or Property Sequence (path) \cite{DBLP:conf/www/AnyanwuS03}.
+
+\end{itemize}
 
 \subsection{Queries}
-Search is about end-user oriented interfaces: NL, keywords, facets
+Typically, answering complex questions requires the expertise of technical users who know the underlying data and schema and use them to formulate questions as structured queries.
+However, search is commonly seen as an end-user oriented paradigm, which instead of using structured query languages, involves intuitive and easy-to use access interfaces.
+The there main interfaces studied for semantic search are based on keywords, NL, and facets.
+
+\begin{itemize}
+	\item \emph{Keyword search}: Expressing the information needs as keywords is a paradigm that is not only popular for Web search but also widely adopted by the new breed of semantic search solutions.
+Most engines focusing on entity search such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} feature a keyword search interface.
+Keywords can also be used to formulate more complex relational searches.
+Addressing this scenario, engines such as Hermes and SemSearchPro retrieve entities matching keywords, and search for relations between them in the data.
+	\item \emph{NL search}: This is the other paradigm for users to express their needs using their own words.
+Traditionally, it has been used to formulate complex questions against expert systems built for specific domains.
+Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge~\footnote{\url{http://www.trueknowledge.com/}}.
+	\item \emph{Faceted / Iterative search:} Instead of formulating the entire query at once, \emph{faceted search} supports an iterative process of querying, browsing and query refinement.
+Upon the initial search performed by the user (e.g.
+using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/semweb/FerreH11,DBLP:conf/esws/HeimEZ10} presents results as well as facets representing attributes and relations relevant for entities in the result list.
+These facets can then be used to browse the results and to refine or expand the initial query.
+While most faceted search solutions focus on browsing and refining results of entity queries, faceted search in principle can also be used to capture complex needs.
+For instance, gFacet\cite{DBLP:conf/esws/HeimEZ10} supports relational search through the construction of complex facet graphs representing different types of entities and relations between them.
+While faceted search is a popular paradigm, there are other similar interfaces that support an \emph{iterative search} process.
+Instead of showing facets as users type, also \emph{completions} of the user keywords as well as completions in the form of results matching the (possible interpretations of the) the keywords provided so far (also called result completion~\cite{DBLP:conf/esws/TranMH10}) have been presented.
+For instance, ESTER~\cite{DBLP:conf/sigir/BastCSW07} shows entity search results matching the keywords as well as their facets while TASTIER~\cite{DBLP:conf/sigmod/LiJLF09}, provides type-ahead search by finding complex (joins of) database tuples as the user types in query keywords.
+With these systems, users can iteratively construct the query by selecting the presented completions and facets.
+VisiNav~\cite{DBLP:journals/ws/Harth10} goes beyond this, allowing iterative query construction also via drag and drop.
+
+	 \end{itemize}
 
 \subsection{Data}
-Objects (documents, media and multimedia objects) with embedded semantic data, semantic datasets
+Data used in semantic search solutions can be broadly categorized into two types, namely \emph{semantic data} and \emph{raw data}.
+The latter basically comprises all representations of media objects such as audio, video and text.
+In the semantic search context, it is not only the raw data itself but the semantic information embedded in or extracted from them (and made available as semantic data) that is crucial.
+These data are referred to as \emph{semantic metadata}.
+
+\begin{itemize}
+	\item \emph{Structured/semantic data}:  The most common type of semantic data used in semantic search systems is RDF.
+Basically, RDF can be seen as a graph-structured model, representing entities and relations between them as a set of triples.
+This general model can be used to capture structured data of different types.
+In fact, most of the data made publicly available on the Web and incorporated into semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09}, Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} and Hermes~\cite{DBLP:journals/ws/TranWH09} originate from relational or XML databases.
+Represented as RDF, this structured data captures knowledge in terms of entities and their relations.
+Hence, especially after its conversion to RDF, structured data is often synonymously referred to as semantic data.
+In fact, the reason why RDF data is actually called semantic data (instead of structured data) is because RDF is built upon a formal model of semantics, which can be exploited by a reasoning engine to infer new knowledge (i.e.
+the knowledge that is entailed by the semantics).
+There are also other types of semantic data that are represented using more expressive knowledge representation languages such as OWL.
+For instance, Serene makes use of facts that are captured as Abox assertions of an OWL ontology~\cite{DBLP:journals/ws/FazzingaGGL11}.
+
+	\item \emph{Raw data and semantic metadata}: While engines relying on semantic data only return direct answers (data retrieval), systems supporting the retrieval of documents or media objects in general, employ semantic metadata in addition to raw data.
+Basically, semantic metadata is semantic data that captures information about the objects to be retrieved.
+Because it is clear from the context, these terms are often used synonymously in this survey.
+Metadata includes basic information about the objects such as \verb+author+ and \verb+year+.
+One main challenge in semantic search is to interpret the semantics behind the content captured as raw data and to represent it as semantic metadata.
+However, semantic metadata representing the content may also be manually produced and embedded into the objects.
+Recently, several industry projects such as Google Rich Snippets and Yahoo!
+SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages.
+\end{itemize}
 
 \subsection{Semantic Models}
-Linguistic models, conceptual models
+As discussed, central to semantic search system is the used of semantics.
+A main source of semantics is the semantic data itself.
+Additionally, semantics can be captured by models of the following types:
 
-\subsection{Matching \& Ranking Techniques}
-Term-based, structure-based, semantic-based
+\begin{itemize}
+	\item \emph{Conceptual models}: While semantic data capture concrete entities, these are abstract model of knowledge, basically representing classes of entities and relations between them.
+Different models, which vary in the degree of formality and expressiveness have been used by different communities for semantic search.
+The model used in ORAKEL for NL question answering for instance is an \emph{ontology} (the TBox of an ontology to be more precise) consist of classes (also called concepts) that are ordered in a subsumption hierarchy and are connected through relations.
+Range and domain information are captured as restrictions on the relations.
+As shown for Serene~\cite{DBLP:journals/ws/FazzingaGGL11}, more complex expressions can be added to capture the semantics of concepts to reflect either general knowledge (such as the knowledge encoded in Wikipedia)
+or specific knowledge of a domain.
+Because the ontology models used in these systems are represented using the logic-based formalisms F-Logic or OWL (description logic), they can be seen as \emph{logical theories} with formal well-defined semantics.
+Also, \emph{conceptual graphs} (CGs) have been employed for representing ontology models, and used for the tasks of NL questions interpretation and answering~\cite{DBLP:conf/aswc/CaoCT08} as well as for interpreting and representing documents~\cite{DBLP:conf/iccs/ComparotHH07}.
+CGs combine the intuitiveness of graph-based languages and the formal foundation of logics, enabling the modeling of knowledge in terms of concepts and their relations and its mapping to different formal languages.
+Corese~\cite{DBLP:conf/ecai/CorbyDF04} uses CGs as an internal model (to take advantage of previous work on CGs in the KR community), which however, is translated to RDFS to conform with this more commonly used standard language for representing RDF schemas.
+Closer to the end of linguistic models discussed next are conceptual models that consist of concepts only.
+For instance, C-Search encodes knowledge as concepts expressed in propositional description logic (DL).
+This DL does not feature the representation of relations (also called roles) but the specification of complex concepts as a conjunction or disjunction of atomic concepts.
 
-%Generally, queries might be simple keywords, natural language or structured.
-Various kind of formal query languages have been proposed to formulate highly expressive (both in terms of structure and semantics) queries.
-Resources returned to the users range from text, audio and video up to multimedia documents.
-These documents embody different types of data, i.e.
-unstructured, semi-structured (in the form of RDF) that is not associated with a schema and fully structured data with a schema.
-Often, structured data available in Semantic Web languages such as RDF and OWL is also referred to as ``semantic data''.
-Different matching framework are employed by these systems.
-IR systems primarily rely on features at the level of terms (language, words) whereas DB and KB systems exploit also the structure as well as the semantics for matching.
-On the other hand, while these DB and KB systems are concerned with producing precise matches (binary matching), IR systems rely on statistical methods that are inherently imprecise such that results are also associated with the degree of matching, i.e.
-IR systems perform imprecise matching and ranking.
-%
-%Apart from these main aspects, semantic search systems can also be distinguished in terms of the notion of semantics that is employed for search.  
-%
-%\subsection{Semantic Models}
-%Generally, semantics is concerned with the meaning of things.
-Meaning is established through a semantic model, which commonly captures interrelationships between elements and their interpretations.
-Various semantic models have been proposed and
-%used in different research communities. The IR community typically relies on \textit{linguistic
-%models} such as taxonomies and thesauri that capture relations between syntactical elements, i.e. words. In
-%the database community, \textit{conceptual models} such as Entity Relationship (ER)
-%diagrams are used to capture relations between entities
-%\cite{DBLP:journals/tods/Chen76}.
-Thus, while linguistic models are concerned with meanings at the level of words, conceptual models more specifically deal with meanings at the level of real-world entities denoted by words.
-That is, conceptual models deal with interpretation of words in terms of real world entities the words refer to.
-Besides ER diagrams, conceptual models include less formal models such as semantic networks [cite] and very formal models such as logic-based theories, where interpretations are precise and computable \cite{DBLP:books/sp/StaabS04}.
-% 
-%In the Semantic Web community, \textit{ontologies} have received widespread acceptance. The notion of
-%ontologies employed by this community is very general. Ontologies
-%constitute rather a family of models, which might differ in the
-%degree of expressiveness and formality, ranging from simple
-%taxonomies and shallow conceptual model represented in RDF(S)
-%to expressive formal models represented in Description Logics \cite{DBLP:books/sp/StaabS04}.
-Thus, ontologies include both linguistic and conceptual models.
-In practice, ontologies do not come only with the conceptual part but might also contain instances.
-In this sense, they are similar to databases (and knowledge bases) where the conceptual part corresponds to what is refer to as the schema (terminological knowledge) and instances correspond to the actual data of the database (assertional knowledge of the knowledge base).
-%
-%\subsection{Semantic Search}
-%As a general notion, a system essentially performs semantic search when a semantic model is employed.
-As illustrated in Fig.
-\ref{fig:semsearch}, a semantic model might be used to make sense of the data, to interpret the query and ultimately, to support matching that goes beyond the traditional term-based matching.
-%
-%\begin{figure}
-%	\centering
-%		\includegraphics[width=0.5\textwidth]{figs/semsearch.pdf}
-%	\label{fig:semsearch}
-%	\caption{Semantic Search}
-%\end{figure}
-%
-%\subsubsection{The DB\&KB Perspective}
-%In retrieving data, semantics has always play an essential role in database systems.
-The foundation of database technologies manifested in theoretical models such as the relational model that provides formal semantics to both resources and queries, i.e.
-the model behind relational data and relational query (an important part of SQL) is in fact a fragment of first-order logic [cite].
-This semantics is taken into account by database query engines to compute answers that precisely match the semantics of queries.
-More precisely, these engines perform binary matching that incorporates not only terms (i.e.
-constants) but also structure and semantics into account.
-Using this mechanism, information needs of different complexity have been served.
-In different commercial systems, we find the application of DB technologies in the form of simple product search (e.g.
-in commercial shopping sites like Ebay and Amazon) up to complex relational queries that are used to populate complex dynamic Web pages.
-%
-%While the relational model is the one most widely used in practice, there exists also domain specific solutions that are built upon more expressive models.
-In the realm of deductive databases for instance, semantics represented in languages such Datalog or F-Logic is used to perform reasoning, with the goal of understanding and delivering not only explicitly asserted information, but also inferred one.
-Further down this steam, semantic models that are even more expressive are used by knowledge-based expert systems for answering complex questions.
-[TODO: applications of expert systems]
-%
-%
-%\subsubsection{The IR Perspective}
-%In the IR community, the representation of the information needs as well as resources is achieved primarily using lightweight models that operates at the level of words.
-In particular, the predominant paradigm is based on keyword queries and bag-of-words representation of resources.
-This works and most importantly, scales well for topical search, i.e.
-to retrieve documents based on topics expressed in terms of keywords, but is not sufficient to address the kind of complex information needs that can be served by DB and KB systems.
-%
-%The need for going beyond the matching purely based on words and statistical dependencies that exist between them has been clearly expressed by leading researchers in the field.
-In the early years of IR research, Riksbergen clearly argue for the use of semantics.
-In order to return precise results to the user, it is essential to compute whether the resources semantically entail what the user ask for [cite].
-Quoting a paper from W.B.
-Croft et al.
-published more than twenty years ago [cite]: ``The statistical approach has many advantages and can achieve a reasonable level of effectiveness with techniques that are very efficient.
-However, it appears that to achieve significant improvements in retrieval effectiveness compared to current techniques, systems must be designed to acquire and use explicit domain knowledge''.
-This explicit domain knowledge are captured using semantic models of varying degrees.
-Semantic networks have been used augment the models based on terms.
-This provide a richer representation which is exploited for assisted query formulation, query expansion, as well as for relevance propagation in ranking [cite].
-Also, linguistic models particularly Wordnet and the Roget’s thesaurus have been widely used.
-%
-%Recently, the IR community continues to embrace the vast body of explicit knowledge that increasingly, is made publicly available.
-There are approaches which not only use semantic models to enrich terms, but in fact, employ both the conceptual and the data part.
-In particular, there are systems that use ontologies including the semantic data contained in them [cite].
-TODO: Applications: enterprise solutions such as IBM Avatar, Medline, Web solutions such as Hakia, Powerset.
-%
-%
-%\subsubsection{The SW Perspective}
-%Semantic search from the this point of view is more similar to the DB and KB perspective in the sense that the main goal is to obtain precise answers for complex questions.
-However, while DB and KB systems are adopted to solve specific problems of a particular domain, semantics is taken by this community to the wider context of the Web.
-Semantic models used here are ontologies available in the W3C languages for resource description, namely RDF and OWL.
-%, while SPARQL is the primary mean to express information needs.
-%On the Semantic Web, there is more data that is more hetetorogenous, i.e.
-data coming from different sources that differs in syntax, formats and quality.
-Thus, unlike traditional DB and KB systems, SW search engine are built with particular emphasis on the ability to scale in terms of both volume and the number of sources, to be domain independent and to perform ranking.
-%
-%To achieve this, they are built upon concepts and technologies from database and expert systems.
-General concepts for data management (e.g.
-indexing and data partitioning []) as well as specific concepts for managing graph structured data and graph databases (e.g.
-structure indexes from XML databases []) have been adopted to deal with ontologies and semantic data available in RDF and OWL.
-For dealing with more expressive semantic models, techniques commonly applied in deductive databases (e.g.
-magic set optimizations [cite]) have been adopted to improve the efficiency and scalability of reasoning.
-However, to deal with scale and to perform ranking, techniques that are more commonly used by the IR technology has also been adopted.
-For instance, the inverted index has been used to scale to a large amount of data and to support term-based matching.
-Statistical dependencies of words such TF-IDF as well as authority-based metrics such as PageRank that is popular in IR web search engines, have been used for ranking.
-%
-%TODO: Applications
-%
-%
-%
-%To summarize, semantics has proven to be useful for search in many aspects.
-There are commercial exploitations, which used semantics in different ways.
-Thus, the notion of semantic search is thus very broad.
-Semantic search covers the wide range of systems employing and exploiting semantic models of varying expressiveness.
-In the following sections, we will focus on semantic search systems driven by the IR and the SW communities which recently, have attracted much research and commercial interests.
+	\item \emph{Lexical models}: The use of concepts has already been investigated in the early years of IR research.
+However, the models employed there capture words and their relationships, instead of knowledge about real-world entities and their relations.
+A thesaurus (often, \emph{lexicon} is also used as synonym) is a lexical resource extensively used in IR, which basically, groups words together according to their semantic similarity.
+In practice, lexical databases also considered as a thesaurus such as WordNet, or thesauri used in classic IR systems~\cite{DBLP:conf/sigir/Giger88}, not only capture these ``senses'', but also relationships between them such as synonym, broader, narrower and related.
+
+	~\cite{DBLP:conf/sigir/Voorhees93}
+	lexicons specifying the mappings between linguistic argument structures,
+such as verbs or nouns with their arguments, and concepts and relations in the semantic model
+\end{itemize}
+
+\subsection{Matching Framework}
+
+	\subsubsection{Content Interpretation} 
+	One crucial task in supporting semantic search over documents is to obtain a richer understanding and representation of the document collection.
+Instead of a the typical bag-of-words model used in classic IR, the goal is to capture the content of the documents as entities, concepts and relations, i.e.
+as semantic data or elements of a semantic model.
+For this, different tools for Natural Language Processing (NLP) have been employed.
+For instance, documents have been analyzed to extract concepts for the task of modeling documents as conceptual graphs~\cite{DBLP:conf/iccs/ComparotHH07}.
+For C-Search, which represent documents as DL concepts corresponding to WordNet senses, the authors identify words in documents matching senses, and uses POS tagging information and lexical database to perform word sense disambiguation.
+While words are mapped to atomic concepts, phrases are represented as complex concepts using DL formulas.
+
+	concepts~\cite{DBLP:conf/sigir/Voorhees93}, named entities, relation \cite{DBLP:conf/cikm/Chu-CarrollP07}
+
+	Given the documents have been annotated with entities and their relations (also referred to as ABox assertions), and given there is an underlying ontology with well-defined formal semantics, 
+	Our approach to Semantic Web search is done relative to a fixed
+underlying ontology, which defines an alphabet of elementary
+ontological ingredients, as well as terminological relationships between
+these ingredients. The ontology may either describe fully
+general knowledge (such as the knowledge encoded in Wikipedia)
+for general ontology-based search on the Web, or it may describe
+some specific knowledge (such as biomedical knowledge) for vertical
+ontology-based search on the Web. The
+
+	\subsubsection{Query Interpretation} 
+	Essentially, interpreting queries is similar to the task of understanding text in documents. The difference is that instead besides NL text, also keywords may be provided as inputs.
+
+	\emph{NL Query Interpretation:} Names entities, their types and relations between them are identified from NL questions~\cite{DBLP:conf/aswc/CaoCT08} and used to construct a semantic representation of the information need, i.e.
+a \emph{structure/semantic query}.
+Analogous to structured/semantic data, there is no clear distinction between a structured query and a semantic query (and thus, the corresponding terms are also used as synonyms).
+Basically, they capture the information need in terms of entities, their relations and variables that represent existential quantifiers or the pieces of information to be retrieved.
+While the common language used to query RDF is SPARQL, other (logic-based) formalisms have been used.
+Besides conceptual graphs~\cite{DBLP:conf/aswc/CaoCT08}, recognized entities, types and relations are also represented as logical formulas~\cite{DBLP:journals/dke/CimianoHHMS08}, XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} or SPARQL queries~\cite{DBLP:conf/esws/DamljanovicAC10}.
+For processing NL questions, the same NLP tools used for content interpretation have been applied.
+For instance, the Stanford Parser and GATE are used by FREyA~\cite{DBLP:conf/esws/DamljanovicAC10} to obtain the syntactic parse tree and to identify concepts in NL questions, respectively.
+Besides the semantic data or additional semantic models such as a domain ontology, lexicons specifying the mappings between syntactic elements,
+such as verbs or nouns with their arguments identified by the parser, and concepts and relations in the semantic models, have been used for NL question answering~\cite{DBLP:journals/dke/CimianoHHMS08}.
+This is to deal with the fact that these semantic elements have many lexical variants.
+These mappings are specified by lexicon engineers.
+Such a lexicon is especially needed for porting the NL interface from one domain to one other.
+Aiming at reducing this upfront customization effort and domain independence, there are also systems that in the case of lexical ambiguities, ask users to provide mappings, and use them to train models (e.g.
+via reinforcement learning~\cite{DBLP:conf/esws/DamljanovicAC10}) that automatically compute mappings.
+While it has been reported~\cite{DBLP:journals/ws/LopezUMP07} that domain customization usually improves recall, many NL-based semantic search systems exploit general domain-independent lexical resources (e.g.
+WordNet is used by AquaLog~\cite{DBLP:journals/ws/LopezUMP07}) but do not require domain-specific lexicons.
+
+	 keyword~\cite{DBLP:conf/sigmod/LiJLF09,DBLP:conf/sigir/BastCSW07,DBLP:conf/sigmod/PoundIW10}, NL, facets~\cite{DBLP:conf/sigir/BastCSW07}, query expansion~\cite{DBLP:series/sci/NgoC10}, query relaxation~\cite{DBLP:conf/esws/ElbassuoniRW11} graph exploration, PRF, speading activation~\cite{DBLP:conf/aaai/JiangT06,DBLP:conf/esws/SchumacherSS08,DBLP:conf/www/RochaSA04}
+
+	\subsubsection{Term- / Content-based Matching} standard IR methods
+	\subsubsection{Structure- / Semantic-based Matching} 
+	This matching is possible when the query and content are interpreted or directly available as a structured query and semantic data, respectively.
+That is, both the query and data are represented in terms of some entities and their relations.
+
+	\emph{Database-style Structure Matching:} Most frequent is the combination SPARQL queries and RDF data.
+The three common types of information needs discussed previously can be captured through the basic graph pattern (BGP) feature of SPARQL.
+Then, matching boils down to the task of \emph{graph pattern matching} where constants in the BGP representing entities, relation and attribute values are matched against RDF data (conceived as a data graph) to find matching subgraphs that contain bindings to variables in the BGP.
+Processing these BGPs involves standard \emph{database query evaluation} techniques, i.e.
+precompile the query to capture an optimal evaluation plan, then retrieve data (from optimized indexes) for each triple pattern and join intermediate results according to the plan.
+This task is supported by off-the-shelf triple stores.
+
+	\emph{Reasoning:} The formal well-defined semantics of some semantics models such as ontologies represented in OWL, have also be exploited for matching.
+More precisely, they are used for \emph{reasoning} to consider not only the available data but also new facts that can be automatically inferred from the formal semantics.
+For instance, the semantic models used in Serene~\cite{DBLP:journals/ws/FazzingaGGL11} is an ontology TBox represented as DL formulas, and semantic data are captured as ABox assertions of the same ontology.
+Serene uses an inference engine to derive new knowledge during an offline ontology compilation step.
+This computation is performed offline to improve the efficiency of online matching.
+Clearly, new knowledge relevant for the query can also be derived online.
+In ORAKEL for instance, the inference of new facts is performed as part of the computation of query matches.
+Notably, the first system created in the early years of Semantic Web research, which makes use of logical reasoning for computing semantic matches is SHOE~\cite{DBLP:conf/dagstuhl/HeflinHL03}.
+
+	\emph{Graph Exploration:}  Another combination that involves a special type of structure/semantic matching is the evaluation of keyword queries.
+As discussed before, the structure and semantics in the data can be used to interpret the keyword query and to convert it to a structured query.
+Instead of query interpretation, there are also systems~\cite{DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}, which use the same \emph{graph exploration} mechanism to directly evaluate the keyword query.
+They skip the computation of queries and directly explore for results in the data (subgraphs) that match the keywords.
+As opposed to standard IR-style keyword search on documents, the results here are semantic data graphs.
+That is, the keywords in the query do not refer to single documents but possibly, several entities that are connected through paths in the semantic data graph.
+Hence, simply joining results (documents), which match the query keywords is not sufficient.
+Entities matching keyword(s) in the query have to be retrieved, and subgraphs containing paths, which connect these keyword matching entities have to be explored in the data.
+
+Interestingly, graph exploration is also employed for the relational search scenario, where the relations (paths) between entities are unknown.
+For instance, the mechanism used by for graph exploration by Hermes~\cite{DBLP:journals/ws/TranWH09,DBLP:conf/icde/TranWRC09}, a keyword search system, is similar to the one proposed for answering P-Queries~\cite{DBLP:conf/www/AnyanwuS03}, a special type of queries that ask for unknown semantic associations between entities.
+
+	\subsubsection{Proximity-based Ranking} content and structure proximity
+	\subsubsection{Centrality-based Ranking} PageRank, authority
+	\subsubsection{Relevance-based Ranking} term-based, structure-aware
+
+- general \cite{DBLP:conf/www/GuhaMM03,DBLP:conf/www/AnyanwuMS05,DBLP:conf/cikm/DingFJPCPRDS04,DBLP:journals/ws/TranWH09,DBLP:journals/ws/TranHL11,DBLP:journals/ws/WangTLF11,DBLP:journals/ws/HalpinL11,DBLP:journals/ws/FazzingaGGL11,DBLP:journals/ws/FernandezCLVCM11}\\
+
+- concept search \cite{DBLP:conf/trec/JelierSEWMSMK03,DBLP:conf/ecir/SuomelaK05,DBLP:conf/trec/TrieschniggKS06,DBLP:conf/esws/GiunchigliaKZ09,DBLP:journals/ipm/MeijTRK10}\\
+
+- document retrieval based on ontologies, annotations 
+\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/sigmod/KandoganKRVZ06,DBLP:conf/aaai/JiangT06,DBLP:conf/cikm/Chu-CarrollP07,DBLP:journals/tkde/CastellsFV07}\\
+
+- keyword search on structured data \cite{DBLP:conf/sigir/BastCSW07,DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/WangLPFZTYP09}\\
+
+- ranking \cite{DBLP:conf/www/NieZWM05,DBLP:journals/internet/Aleman-MezaHARS05,DBLP:conf/vldb/BalminHP04,DBLP:conf/sigmod/LiuYMC06,DBLP:conf/webdb/StoyanovichBBW07,DBLP:conf/www/AnyanwuMS05,DBLP:conf/www/QinLZWXL08,DBLP:conf/semweb/BlancoMV11,DBLP:conf/semweb/DingPFJPK05,DBLP:conf/semweb/HarthKD09,DBLP:conf/esws/DelbruTCTD10,DBLP:conf/semweb/FranzSSS09,DBLP:journals/debu/ElbassuoniRSW10,DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}\\
+
+- faceted search \cite{DBLP:journals/ws/HoganHUKPD11,DBLP:conf/dexa/WagnerLT11,DBLP:conf/esws/HeimEZ10,DBLP:conf/semweb/FerreH11}\\
+
+- NL
+\cite{DBLP:conf/esws/WangXZY07,DBLP:journals/ws/LopezUMP07,DBLP:conf/esws/TablanDB08,DBLP:journals/dke/CimianoHHMS08,DBLP:conf/icde/KasneciSIRW08,DBLP:conf/aswc/CaoCT08,DBLP:conf/esws/DamljanovicAC10}
+
+\subsection{Document Retrieval vs. Data Retrieval}

### 2012-02-21 trunk/tr-semanticsearchsurvey-data/overview.tex

\section{Semantic Search}
\begin{figure}[tbh]
	\centering
		\includegraphics[width=0.35\textwidth]{figs/semsearch.pdf}
	\label{fig:semsearch}
	\caption{Semantic Search.}
\end{figure}

Basically, \emph{search} can be characterized by three components, namely the \emph{data}, the \emph{query} and the \emph{matching framework} for computing results from the data for a given query. This is illustrated in the left portion of Fig.~\ref{fig:semsearch}. One main characteristic of concepts behind search is its emphasize on \emph{end users}. That is, search typically involves intuitive interfaces targeting users, who may do not possess knowledge about the domain, the data, and the underlying query language. The query inputs that can be obtained from these interfaces are often ambiguous. That is, they allow for many possible interpretations, which in turn, result in many possible results. Because end users are often only interested in the few best results, \emph{ranking} is considered as an essential component in search. That is, the matching framework not only specifies what constitutes matches but also their degree of matching.

\emph{Semantic search} is a concept widely used by different communities to refer to search approaches that broadly speaking, aim to \emph{use semantics to improve the search experience}. Considering the core search tasks, semantics has been used to obtain a better understanding of the data and query and to improve matching and ranking based on that (see Fig.~\ref{fig:semsearch}). There are exist different notions of semantics. One the one hand, there are proposals for using the semantics of words captured as latent concepts (e.g. to use Latent Semantic Indexing for IR \cite{DBLP:conf/sigir/Hofmann99}) or latent topics (e.g. to use Latent Dirichlet Allocation~\cite{DBLP:conf/sigir/WeiC06}). While these models only implicitly capture the semantics in terms of some latent, unknown dimensions, there are also explicit models of semantics. For instance, Explicit Semantic Analysis uses Wikipedia articles, categories, and relations between articles to capture semantics. Other explicit models of semantics (henceforth called \emph{semantic models}) include thesauri, the terminological part (TBox) of ontologies and data schemas. While these models capture semantics at the conceptual level, there are also \emph{semantic data} capturing the semantics of individual entities. To accommodate the plethora of approaches that exist, we propose the following definition of semantic search.

\begin{definition}[Semantic Search] Semantic search is a search paradigm that make uses of \emph{explicit semantics} to solve any of the \emph{core search tasks}, i.e. interpreting query and (or) data, matching and ranking. 
\end{definition}

While all existing semantic search systems use some kinds of explicit semantics, the retrieval context and the specific semantic models and data used to deal with the meaning behind the query intent and data vary.

\emph{Document Retrieval:} The IR community targets the document retrieval context where results are to be retrieved from a collection of documents. The traditional type of semantic models used here are thesauri that are employed to \emph{interpret} the terms in the textual representation of queries and data (i.e. documents). Recently, semantic data such as RDF resource descriptions have also been employed to interpret query and documents in terms of real-world entities and their relations.

\emph{Data Retrieval:} Querying entities and their relationships is a core problem in database research. As opposed to the hidden semantics of textual content in documents, information about entities and their relationships are explicitly available in this setting -- either directly as semantic data in RDF or as structured data that can be converted to RDF. Thus, understanding the semantics of the underlying data is not the problem here. However, as opposed to classic data retrieval that is based on structured query languages, intuitive query interfaces are needed in the search context. This lead to the classic search problems of interpreting the query intent and ranking the many possible results. 
%Just like in the document context, the goal here is to enable easy access to the most relevant results. Especially in the Semantic Web community, solutions targeting this problem are also referred to as semantic search because they use semantic data to interpret the query intent and to rank results.

%In this section, we establish the main dimensions in which existing solutions vary and then discussed them in more detail in the subsequent sections. 
% and then, provide a taxonomy of semantic search approaches. We focus on approaches studied by researchers in the Semantic Web community that explicitly target semantic search. Selectively, we also point out works from the IR and database communities that deal with the same problem. 
%Search is about retrieving information that are relevant with respect to a given information need. 
%Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs. 
We characterize the many different solutions along the following dimensions:

\begin{itemize}
\item the type of targeted \emph{information needs},  
\item the representation of the information need called \textit{query}, 
\item the representation of the underlying resources called \emph{data}, 
\item the \emph{semantic models} used to understand query and data, 
\item the framework for \emph{matching} queries against data, which also involves \emph{interpreting} the content and the user intent as well as \emph{ranking} the results.  
\end{itemize}

A general overview of the main types of information needs (results), queries, data, semantic models as well as interpretation, matching and ranking techniques supported by existing semantic search solutions is illustrated in Fig.~\ref{fig:semsearch_detailed}. We will now discuss existing solutions along these dimensions.

\begin{figure*}[tbh]
	\centering
		\includegraphics[width=0.85\textwidth]{figs/semsearch_detailed.pdf}
	\label{fig:semsearch_detailed}
	\caption{Overview of Semantic Search Approaches.}
\end{figure*}

\section{Information Needs}
The main motivation for semantic search is to go beyond the relatively frequent but simple queries currently supported by existing search solutions to solve the long-tail queries representing rather complex information needs. But also for simple queries, semantic data have proven to be valuable. Instead of showing documents, semantic data are used by commercial Web search engines to create rich snippets for Web pages, or to deliver direct answers.

\subsection{Entity Search} most queries on the Web asked for Web pages representing entities such as organization or people. They are used to obtain entry points, while additional navigation and browsing is still required to satisfy the actual information need. Thus, these queries are also referred to as navigational queries. Semantic data embedded in Web pages have been exploited by Google to present rich entity snippets\footnote{Google Rich Snippets} to this kind of queries. Instead of searching over a collection of documents, semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results. Examples for this include the one asking for ``young scholars in Germany'' already mentioned before, or the query ``Researcher Thanh Tran'' depicted in the top left portion of Fig.~\ref{fig:matching}. Results for queries of this type comprise one or several entities.

\subsection{Factual Search} While results to the previous type of queries presented to the users are either some entity descriptions or Web pages about entities, the information needs behind this type of search require specific information from these descriptions and pages, respectively. Many searches on the Web for instance, aim at finding the ratings of restaurants, or the phone number of a particular person. To continue with our example, users may directly ask for ``the birth place of young scholars in Germany''. Direct answers to this type of queries are supported by WolframAlpha\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge~\footnote{\url{http://www.trueknowledge.com/}}, or the various research prototypes such as Hermes~\cite{DBLP:journals/ws/TranWH09} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}. Since factual search is mostly about facts that correspond to attribute values of entities, it is often regarded as a particular type of entity search. We also do not further distinguish this from the general entity search task.

\subsection{Relational Search} The information need here goes beyond single entities and their factual information. Answers to queries of this type comprise several entities and relationships between them. Hence, processing these queries requires some understanding of relations between entities. For instance, the example presented in the introduction about 32 year old computer scientists requires knowledge about their \verb+lives in+ and \verb+birth place+ relations to some locations. Relations may be explicitly specified as part of the keyword or NL query, and entities satisfying these relation constraints can be computed using SemSearchPro~\cite{DBLP:journals/ws/TranHL11} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}. Other systems such as NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} also support searches where relations to be considered are not explicitly mentioned in the query, or unknown. They address information needs that involve finding ``how some entities are related to some other entities''. The interesting part of the results here are thus not the entities, but the relationships between them -- also referred in literatures as semantic associations (direct connection) or property sequence (path)~\cite{DBLP:conf/www/AnyanwuS03}. An example for this query, asking for paths between ``Peter Mika'' and ``Thanh Tran'' is depicted in top right portion of Fig.~\ref{fig:matching}.

\section{Queries}
Typically, answering complex questions requires the expertise of technical users who know the underlying data and schema and use them to formulate questions as structured queries. However, search is commonly seen as an end-user oriented paradigm, which instead of using structured query languages, involves intuitive and easy-to use access interfaces. The there main interfaces studied for semantic search are based on keywords, NL, and facets. Often, a combination of these paradigms, e.g. keywords and facets, is used to support an iterative search process where instead of constructing the query at once, the user modifies the query and results respectively, through a series of operations.

\subsection{Keyword Search} Expressing the information needs as keywords is a paradigm that is not only popular for Web search but also widely adopted by the new breed of semantic search solutions. Most engines focusing on entity search such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} feature a keyword search interface. Keywords can also be used to formulate more complex relational searches. Addressing this scenario, engines such as Hermes~\cite{DBLP:journals/ws/TranWH09}, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}, AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} and TASTIER~\cite{DBLP:conf/sigmod/LiJLF0} retrieve entities matching keywords, and search for relations between them in the data.

\subsection{NL Search} This is the other paradigm for users to express their needs using their own words. Traditionally, it has been used to formulate complex questions against expert systems built for specific domains. Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha and True Knowledge.

\subsection{Faceted Search} Instead of formulating the entire query at once, \emph{faceted search} supports an iterative process of querying, browsing and query refinement. Upon the initial search performed by the user (e.g. using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/semweb/FerreH11,DBLP:conf/esws/HeimEZ10} presents results as well as facets representing attributes and relations relevant for entities in the result list. These facets can then be used to browse the results and to refine or expand the initial query. While most faceted search solutions focus on browsing and refining results of entity queries, faceted search in principle can also be used to capture complex needs. For instance, gFacet\cite{DBLP:conf/esws/HeimEZ10} supports relational search through the construction of complex facet graphs representing different types of entities and relations between them.

\subsection{Iterative Search}
While faceted search is a popular paradigm, there are other similar interfaces that support an \emph{iterative search} process. Instead of showing facets as users type, also \emph{completions} of the user keywords as well as completions in the form of results matching the (possible interpretations of the) the keywords provided so far (also called result completion~\cite{DBLP:conf/esws/TranMH10}) have been presented. For instance, ESTER~\cite{DBLP:conf/sigir/BastCSW07} shows entity search results matching the keywords as well as their facets while TASTIER~\cite{DBLP:conf/sigmod/LiJLF09}, provides type-ahead search by finding complex (joins of) database tuples as the user types in query keywords. With these systems, users can iteratively construct the query by selecting the presented completions and facets. VisiNav~\cite{DBLP:journals/ws/Harth10} goes beyond this, allowing iterative query construction also via drag and drop.

\section{Data}
Data used in semantic search solutions can be broadly categorized into two types, namely \emph{semantic data} and \emph{raw data}. The latter basically comprises all representations of media objects such as audio, video and text. 
There are solutions~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09}, which specifically target the data extracted from Semantic Web sources. That is, they directly operate on semantic data. In fact, structured data used in most data retrieval systems can be converted to a form that corresponds to the general notion of semantic data~\cite{DBLP:conf/sigmod/LiJLF09}. On the other hand, semantics may not be directly captured by semantic data but extracted from raw data. This is especially the case for document retrieval systems, where one of the essential task in semantic search is to obtain a semantic data representation of the documents (called \emph{semantic metadata}).

\subsection{Structured / Semantic Data}  The most common type of semantic data used in semantic search systems is RDF. Basically, RDF can be seen as a graph-structured model, representing entities, their attributes, and relations between them as a set of triples. A visual representation of such a \emph{semantic data graph} capturing information about two \verb+researcher+s with the \verb+name+s \verb+Thanh Tran+ and \verb+Peter Mika+ is depicted in the bottom portion of Fig.~\ref{fig:matching}

This general graph-structured model can be used to capture structured data of different types. In fact, most of the data made publicly available on the Web and incorporated into semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09}, Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} and Hermes~\cite{DBLP:journals/ws/TranWH09} originate from relational or XML databases. XML elements can be represented as nodes, and their structure information can be captured as edges. Likewise, information contained in tuples of a relation database can be mapped to nodes, while foreign key relationships can be modeled as edges. In fact, the conversion of XML and relational data to a RDF semantic data graph can be accomplished by using mapping rules, and there exist many standards and tools for accomplishing that (see \url{http://www.w3.org/2001/sw/rdb2rdf/}).  Represented as RDF, these and possibly other types of structured data also capture knowledge in terms of entities and their relations. Hence, especially after its conversion to RDF, structured data is often synonymously referred to as semantic data. In line with this general notion, semantic data used in semantic search systems can be defined as follows:

\begin{definition}[Semantic Data] 
Semantic data can be conceived as a graph, where nodes represent \emph{entities} and their \emph{attribute values}, and edges stand for \emph{attributes} of entities or \emph{relations} between entities. 
\end{definition}

Besides the various RDF datasets that exist on the Web, such as the hundreds of heterogeneous sources that have been made available as Linked Data~\footnote{\url{http://linkeddata.org/}}, Wikipedia can be as an extreme example that lies at one end of the spectrum of semantic data. While it is actually a collection of documents (i.e. contains mainly textual data), it fits the presented notion of semantic data because every Wikipedia page corresponds to an entity, and there are links between Wikipedia pages that can be seen as relations. In fact, exploiting this and other specific features of Wikipedia articles such as Infoboxes, a RDF dataset called DBpedia~\cite{DBLP:journals/ws/BizerLKABCH09} has been automatically derived from this collection. Wikipedia as a source of semantics is particularly popular for search systems that focus on expert search or entity search in general. It is used either to directly answer entity search queries, or as background knowledge~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/cikm/BronBR10}.

On the other end of the spectrum, there are more formal views on what constitute semantic data. In particular, many researchers may argue that the reason why RDF, and other data models that are built upon a formal model of semantics, are actually called semantic data (instead of structured data) is because they can be exploited by a reasoning engine to infer new knowledge (i.e. the knowledge that is entailed by the semantics). While the formal model of semantics specified for RDF is relatively simple (consists of a few inference rules), semantic data used in existing search systems have also been represented using more expressive knowledge representation languages such as OWL and F-logic. For instance, Serene~\cite{DBLP:journals/ws/FazzingaGGL11} makes use of facts that are captured as Abox assertions of an OWL ontology, while ORAKEL~\cite{DBLP:journals/dke/CimianoHHMS08} search over an F-logic knowledge base. However, while the use of formal semantics and reasoning has been investigated, they play only a limited role in existing systems. The 
majority of approaches does not rely on reasoning. It seems that the research focus still lies in correctly understanding the ambiguous queries and data (namely, to interpret queries and data as elements of the semantic data model as defined above), while reasoning over semantic data is beneficial but not essential yet.

Accordingly, a general notion of semantic data is employed in this work to consider all those systems, which consider the semantics of entities and relations but may not have a formal model of semantics available, or does not exploit it for search.

\begin{figure}[thb]
	\centering
		\includegraphics[width=0.5\textwidth]{figs/matching.pdf}
	\label{fig:matching}
	\caption{Examples for semantic data, queries and matching techniques.}
\end{figure}

\subsection{Raw Data and Semantic Metadata} There are engines directly operating on semantic data to provide direct answers (data retrieval systems). These are mainly systems, which provide search interfaces over structured databases that have been converted to semantic data graphs~\cite{DBLP:conf/sigmod/LiJLF09,DBLP:conf/sigmod/LiOFWZ08}, or RDF data and ontologies crawled from the Semantic web~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TranWH09,DBLP:journals/ws/HoganHUKPD11}. Besides them, there are also semantic search systems supporting the retrieval of documents or media objects in general. They employ semantic metadata, often in combination with the raw data representation of these objects. Basically, semantic metadata is semantic data that captures information about the objects to be retrieved. Because it is clear from the context, these terms are often used synonymously (in this work). Metadata includes basic information about the objects such as \verb+author+ and \verb+year+. One main challenge in semantic search is to interpret the semantics behind the content captured as raw data and to represent it as semantic metadata. For instance, the content of a document may be recognized as referring to a \verb+meeting+ with the two \verb+researcher+s \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participant+s. Semantic metadata representing the content may also be manually produced and embedded into the objects. Recently, several industry projects such as Google Rich Snippets and Yahoo! SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages. Note that while we discussed how to conceive Wikipedia as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).

While the amount of available metadata is increasing, it is still too sparse to cover all information needs. Thus, metadata is mostly used as additional information that can help to improve standard search over raw data~\cite{DBLP:journals/tkde/CastellsFV07,DBLP:journals/ws/FernandezCLVCM11}. Search over raw data can also be seen as a fall-back solution for cases where metadata cannot completely satisfy the information need. There exists also proposals for ontology-based IR, which completely rely on metadata~\cite{tran2007expressive}. In this case the retrieval of documents is formulated as a data retrieval task, where data about the documents (metadata) is returned as a direct answer.

\section{Semantics \& Semantic Models}
\begin{figure}[thb]
	\centering
		\includegraphics[width=0.5\textwidth]{figs/semantic_layer.pdf}
	\label{fig:semantic_layer}
	\caption{Words, concepts and entities.}
\end{figure}

As discussed, central to semantic search system is the use of semantics. A main source of semantics is the semantic data itself. This semantics of entities is illustrated in the top right corner of Fig.~\ref{fig:semantic_layer}. Additionally, this figure also shows additional sources of semantics as well as their use in the semantic search context, namely to understand words in terms of concepts and entities. Broadly, \emph{lexical models}, which capture semantics at the level of words in terms of \emph{concepts}, can be distinguished from \emph{knowledge models}, which capture real-world knowledge in terms of \emph{entities}, \emph{classes}, \emph{relations}, and \emph{attributes}.

\subsection{Knowledge Models} While semantic data capture concrete entities (instances), these are abstract models of knowledge, basically representing classes of entities, attributes associated with these classes, and relations between classes. This is visualized in the top left portion of Fig.~\ref{fig:semantic_layer}.

Different models, which vary in the degree of formality and expressiveness have been used by different communities for semantic search. The model used in ORAKEL for NL question answering for instance is captured by the TBox portion of an ontology and consists of classes (also called concepts) that are ordered in a subsumption hierarchy and are connected through relations. Range and domain information are captured as restrictions on the relations. As shown for Serene~\cite{DBLP:journals/ws/FazzingaGGL11}, more complex expressions can be added to capture the semantics of concepts to reflect either general knowledge (such as the knowledge encoded in Wikipedia)
or specific knowledge of a domain. Because the ontology models used in these systems are represented using the logic-based formalisms F-Logic or OWL (description logic), they can be seen as \emph{logical theories} with well-defined formal semantics.

Also, \emph{conceptual graphs} (CGs) have been employed for representing ontology models, and used for the tasks of NL questions interpretation and answering~\cite{DBLP:conf/aswc/CaoCT08} as well as for interpreting and representing documents~\cite{DBLP:conf/iccs/ComparotHH07}. CGs combine the intuitiveness of graph-based languages and the formal foundation of logics, enabling the modeling of knowledge in terms of concepts and their relations and its mapping to different formal languages. Corese~\cite{DBLP:conf/ecai/CorbyDF04} uses CGs as an internal model (to take advantage of previous work on CGs in the KR community), which however, is translated to RDFS to conform with this more commonly used standard language for representing RDF schemas.

Closer to the end of linguistic models discussed next are knowledge models that consist of concepts only. For instance, C-Search encodes knowledge as concepts expressed in propositional description logic (DL). This DL does not feature the representation of relations (also called roles) but the specification of complex concepts as a conjunction or disjunction of atomic concepts.

\subsection{Lexical Models} The use of concepts has already been investigated in the early years of IR research~\cite{DBLP:conf/sigir/Giger88}. Different to knowledge models, which capture semantics in terms of real-world entities and their relations, the models employed there are lexical in that they capture semantics at the level of words. While concepts in knowledge models stand for classes of real-world entities, concepts in lexical models correspond to \emph{senses of words}. The latter are more general such that they may refer to entities, classes, relations, attributes, or other senses of words. While these different ``types'' of senses are not explicitly distinguished, concepts are organized along lexical relationships in a lexical model.

\emph{Thesaurus} (often, \emph{lexicon} is also used as synonym) is a popular lexical model that has been extensively used for document retrieval in IR, which basically, groups words together according to their semantic similarity. Each group represents a different word sense. In practice, lexical databases also considered as thesauri such as WordNet, or thesauri used in classic IR systems~\cite{DBLP:conf/sigir/Giger88}, not only capture senses (concepts) and their lexical variants, but also relationships between them such as synonym, broader, narrower and related. This is illustrated in the bottom part of Fig.~\ref{fig:semantic_layer}.

\subsection{Semantics} 
Based on the above discussion, we derive a general notion of semantics that is used to characterize the different types of semantic search systems.

\begin{definition}[Semantics] 
The semantics of queries and data are captured by semantic search systems in different ways. Semantics can be represented (1) as word senses that are organized through lexical relations between words (\emph{lexical model}), (2) as specific knowledge about concrete entities, i.e. specific attribute values and individual relations between entities (\emph{semantic data}) or (3) as general knowledge about classes of entities, their attributes, and relations between classes (\emph{knowledge model}). 
\end{definition}

A prominent example that can be used to illustrate these many aspects of semantics is Wikipedia. As discussed, it has been used as semantic data to answer entity search queries, and converted to a semantic dataset called DBpedia. The Wikipedia categories of pages have been treated as classes and used to construct hierarchies of classes in an ontology called YAGO~\cite{DBLP:conf/www/SuchanekKW07}. Wikipedia is also used as a source for Explicit Semantic Analysis (ESA), where every Wikipedia page is regarded as a concept. Because ESA does not distinguish entities and classes, the concepts here can be seen as word senses. Thus, Wikipedia pages and links constitute a lexical model in this context.

\subsection{Focus: Semantics of Entities \& Relations}

The discussion of semantics so far focuses on entities and simply (binary) relations between them. Yet, the kind of semantics that can be expressed is only limited by the knowledge representation (KR) languages. There exist very powerful KR formalisms and many of them have been incorporated to perform document retrieval (already in the early years of IR~\cite{DBLP:conf/sigir/Rijsbergen89}) and to represent complex queries and knowledge used in NL question answering~\cite{DBLP:journals/tkde/VassiliadisTK94}(in the early years of expert systems). For instance, the employed formalisms have been used to represent temporal or fuzzy aspects of world knowledge. However, there are practical reasons why the focus of current research (and this paper) is set on simple descriptions of entities. On the hand, most queries on the Web seem to ask about entities and their relations. That is, most common queries as well as a large part of queries in the long tail (of Web query logs) are about entities and their relations (i.e., they are of the types entity, factual or relational queries). More importantly, the bottleneck is actually the availability of data. It became evident that manually capturing the content of documents as complex logical formulas does not scale. Extracting entities and relations from documents at high quality still remain hard problems, representing the limits of what can be done automatically by data extraction technologies. Also, most of the data residing in databases nowadays are mainly about entities and their relations. \dtr{maybe also discuss the difference to XML retrieval, which merely use structure information for ``focused'' retrieval: retrieve components of the structured XML documents that match the query}

\section{Interpretation}

\subsection{Content Interpretation}

One crucial task in supporting semantic search over documents is to obtain a richer understanding and representation of the document collection. Instead of a the typical bag-of-words model used in classic IR, the goal is to capture the content of the documents as entities, concepts and relations, i.e. as semantic data or elements of a semantic model. For this, different tools for Natural Language Processing (NLP) have been employed.

\emph{Detecting Concepts:} Documents have been analyzed to extract concepts for the task of modeling documents as conceptual graphs~\cite{DBLP:conf/iccs/ComparotHH07}. For C-Search~\cite{DBLP:conf/esws/GiunchigliaKZ09}, which represent documents as DL concepts corresponding to WordNet senses, the authors identify words in documents matching senses, and uses POS tagging information and lexical database to perform word sense disambiguation. While words are mapped to atomic concepts, phrases are represented as complex concepts using DL formulas~\cite{DBLP:conf/esws/GiunchigliaKZ09}. Especially in the biomedical domain, the use of thesauri concepts for interpreting and representing documents is very common~\cite{DBLP:conf/trec/TrieschniggKS06,DBLP:conf/trec/ZhouYTS06}. For instance, the Unified Medical Language System and a gene-thesaurus have been used to identify multi-word terms and to map synonymous words to one concept~\cite{DBLP:conf/trec/TrieschniggKS06}. The concepts were identified simply by by comparing document words to thesaurus terms.

\emph{Detecting Entities \& Relations}: For extracting entities and relations, the large body of research work on named entity recognition and data extraction has been leveraged by existing semantic search solutions. One of the platform, which is most frequently used by semantic search systems for extracting semantic data and
automatically annotating document collections at a large scale is KIM~\cite{KIM DBLP:journals/ws/KiryakovPTMO04}. IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} makes use of UIMA, a framework of annotators that can be configured in a pipeline to analyze and extract data from text. There is a another work from IBM, which focuses on extracting named entities and relations from text and using them for more precise search~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}. Also for this task, lexical resources, particularly Gazetteers, is frequently used. For disambiguating named entities mentions in text, it has been shown that semantic data about entities and their relations provides valuable information~\cite{DBLP:conf/esws/KlebA10}. The technique behind this is based on graph traversal, which starts from nodes matching the entity mentions. Controlled through spreading activation, path from these nodes are traversed to explore the semantic context of these nodes (i.e. entities). These contextual interpretations are then used for disambiguation. A special case of understand

\subsection{Query Interpretation} 
	Essentially, interpreting queries is similar to the task of understanding text in documents. The difference is that instead besides NL text, also keywords may be provided as inputs.

\emph{Translating NL Queries:} Names entities, their types and relations between them are identified from NL questions~\cite{DBLP:conf/aswc/CaoCT08} and used to construct a semantic representation of the information need, i.e. a \emph{structure/semantic query}. Analogous to structured/semantic data, there is no clear distinction between a structured query and a semantic query (and thus, the corresponding terms are also used as synonyms). Basically, they capture the information need in terms of entities, their relations and variables that represent existential quantifiers or the pieces of information to be retrieved. While the common language used to query RDF is SPARQL, other (logic-based) formalisms have been used. Besides conceptual graphs~\cite{DBLP:conf/aswc/CaoCT08}, recognized entities, types and relations are also represented as logical formulas~\cite{DBLP:journals/dke/CimianoHHMS08}, XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} or SPARQL queries~\cite{DBLP:conf/esws/DamljanovicAC10}. For processing NL questions, the same NLP tools used for content interpretation have been applied. For instance, the Stanford Parser~\footnote{\url{http://nlp.stanford.edu/software/lex-parser.shtml}} and GATE~\footnote{\url{http://gate.ac.uk/}} are used by FREyA~\cite{DBLP:conf/esws/DamljanovicAC10} to obtain the syntactic parse tree and to identify concepts in NL questions, respectively. Besides the semantic data or additional semantic models such as a domain ontology, lexicons specifying the mappings between syntactic elements,
such as verbs or nouns with their arguments identified by the parser, and concepts and relations in the semantic models, have been used for NL question answering~\cite{DBLP:journals/dke/CimianoHHMS08}. This is to deal with the fact that these semantic elements have many lexical variants. These mappings are specified by lexicon engineers. Such a lexicon is especially needed for porting the NL interface from one domain to one other. Aiming at reducing this upfront customization effort and domain independence, there are also systems that in the case of lexical ambiguities, ask users to provide mappings, and use them to train models (e.g. via reinforcement learning~\cite{DBLP:conf/esws/DamljanovicAC10}) that automatically compute mappings. While it has been reported~\cite{DBLP:journals/ws/LopezUMP07} that domain customization usually improves recall, many NL-based semantic search systems exploit general domain-independent lexical resources (e.g. WordNet is used by AquaLog~\cite{DBLP:journals/ws/LopezUMP07}) but do not require domain-specific lexicons.

	\emph{Detecting Concepts in Keyword Queries:} One of the main challenge in dealing with keywords in queries or NL words in general is their semantic ambiguity. The same meaning can be expressed in different ways. In particular, there are lexical variants that refer to the same concept, relation or entity (synonymy). One and the same word however, can also have different meanings (polysemy). These are only two prominent problems, and there exist many other subtle ambiguities (e.g. terms overlap or are related in meaning). The use of thesaurus (also called lexicon) to deal with semantic ambiguities of words has long history and has been investigated as the problem of concept-based IR~\cite{DBLP:conf/sigir/Giger88}. Concept-based IR is especially needed in the biomedical domain due to the frequent presence of acronyms, homonyms and synonyms. For detecting the underlying concepts, many lexical resources that are abundantly available for this domain, such as the Online Dictionary of Abbreviations from MEDLINE, the MESH thesaurus and the Gene Ontology have been used~\cite{DBLP:conf/sigir/ZhongH06,DBLP:conf/trec/JelierSEWMSMK03}. The detected concepts are used to expand the query~\cite{DBLP:conf/sigir/QiuF93,DBLP:conf/trec/JelierSEWMSMK03}. Concept-based query expansion \cite{DBLP:conf/sigir/QiuF93} for instance, detect the concept behind the query, and perform selection and weighting of additional search terms directly based on this concept (instead of the query terms). This and other works in this era, were based on the use of thesauri that capture concepts and relationships. WordNet for instance, was use to represent concepts by WordNet synonym sets, and for expanding query terms by following WordNet links \cite{DBLP:conf/sigir/Voorhees93}. WordNet links (is-a in particular) was also used to disambiguate query terms and to choose their senses \cite{DBLP:conf/sigir/Voorhees94}. Recently, a technique based on the idea of relevance model has been proposed to recognize the concepts underlying the query, referred to as conceptual query modeling~\cite{DBLP:journals/ipm/MeijTRK10}. Instead of detecting the concepts based on a thesauri, this approach retrieves the top pseudo-relevance feedback documents through an initial query run. Concept annotations associated with these documents are then used to construct the conceptual representation of the relevance model (the query). While OntoSearch~\cite{DBLP:conf/aaai/JiangT06} does not explicitly the query and the underlying relevance, it follows a similar idea. Concepts captured by ontologies (seen as network of concepts) are used here.  First, OntoSearch obtains a set of documents for the given query, then uses the concepts associated with these documents as the seeds to the semantic network. Through spreading activation, concepts that are semantically related to this initial concept set are inferred, and used to re-rank the documents.

\emph{Translating Keyword Queries:} Instead of concept-based query expansion or aiming at a conceptual representation, there are also proposals for mapping keyword queries to fully structured queries. Entities and relations in the semantic data that are mentioned in the queries are identified and represented as XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}. AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} is another system, which supports this kind of keyword query interpretation. It maintains a translation index, which can be conceived as a lexicon that returns all meanings for an individual keyword. Specifically, it returns schema concepts as well as schema paths matching the keywords. These keyword matches are then combined to enumerate all possible interpretations of the query. For RDF data, a top-k graph traversal algorithm has been proposed to efficiently compute all possible interpretations~\cite{DBLP:conf/icde/TranWRC09}. Here, keywords are interpreted as entities, classes or relations (called keyword matching elements), which are captured by the semantic data or the underlying semantic model. All possible paths between these keyword matching elements are computed online by traversing a combination of the semantic data graph and the schema graph (the semantic model), and combined to obtain interpretations which cover all the query keywords. This keyword query interpretation is implemented by Hermes~\cite{DBLP:journals/ws/TranWH09}, and later, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}. TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} also applies this graph traversal mechanism to interpret keywords not as possible queries (i.e. as information needs) but as answers. As the user types, TASTIER completes the query with answers that possibly match the intended information need.

These mentioned approaches deal with the interpretation of ambiguous queries that are expressed as NL or keywords. The end result is a more precise understanding of the need, represented as structured queries. This is also the aim of other related work that falls into the general category of query construction. For instance, faceted search~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/esws/HeimEZ10,DBLP:conf/semweb/FerreH11} or the other kind of iterative query interfaces based on visual manipulation (drag and drop)~\cite{DBLP:journals/ws/Harth10} as mentioned before, also belong to this general category. In these interfaces, every user operation is directly mapped to a query construct. For instance, adding and removing facets result in the addition (query expansion) and removal (query refinement) of query predicates, respectively. Clearly, the difference to work on query interpretation is the lack of ambiguity, i.e. the semantics of every user input is clear.

\section{Matching}
The differences between term matching, structure matching and graph traversal are illustrated in Fig.~\ref{fig:matching}.

\subsection{Term Matching} 
%\subsubsection{Term- / Content-based Matching}
This matching is needed when the representation of query and data is based on terms (i.e. is a bag of words). This is the case with all the existing concept-based document retrieval solutions~\cite{DBLP:conf/sigir/Giger88,DBLP:conf/sigir/ZhongH06,DBLP:conf/trec/JelierSEWMSMK03,DBLP:conf/sigir/QiuF93,DBLP:conf/sigir/QiuF93,DBLP:conf/sigir/Voorhees93,DBLP:conf/sigir/Voorhees94,DBLP:journals/ipm/MeijTRK10}, which identify the concepts behind the query and content but however, only use them for query or document expansion (i.e. expand the term-based query / content representation with additional terms corresponding to the identified concepts). Likewise, there are approaches, which interpret the query as entities and relations and to use this understanding to expand the queries with corresponding terms~\cite{DBLP:series/sci/NgoC10}. Many semantic data retrieval systems such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} also employ bag-of-words representations -- both of the query and the semantic data. In these cases, the structure and semantics are not taken into account during the matching (but possibly, might have been used in other steps such as query interpretation). The matching boils down to the standard IR retrieval problem. Namely, given a set of keywords, documents matching individual keywords are retrieved. Typically, they are then joined to obtain those, which match all query keywords (AND-semantics). 
%This matching goes beyond the term-level to consider the content, which may contain several mentions of the query terms, as well as mentions of terms that do not appear in the query. At this content level, results may differ in the degree of matching, an aspect that is dealt with during the ranking.

\subsection{Structure / Semantic Matching} 
	This matching is possible when the query and content are interpreted or are directly available as a structured query and semantic data, respectively. That is, the semantics of both the query and data is represented in terms of some entities and their relations.

	\emph{Matching Complete Structure Patterns (Structure Matching):} Most frequent is the combination SPARQL queries and RDF data. In particular, the three common types of information needs discussed previously can be captured through the basic graph pattern (BGP) feature of SPARQL. Just like semantic data, a BGP forms a graph where nodes and edges are either constants or variables. They form complete patterns in the sense that through explicitly captured join variables, the query engines know how to combine intermediate results obtained for subparts of the queries (for triple patterns in the BGP) to compute end results. Matching BGPs against semantic data boils down to the task of \emph{graph pattern matching} where constants in the BGP representing entities, relations, attributes and attribute values are matched against the RDF data graph to find matching subgraphs that contain bindings to variables in the BGP. Processing these BGPs involves standard \emph{database query evaluation} techniques, i.e. precompile the query to capture an optimal evaluation plan, then \emph{retrieve} data (from optimized indexes) for each triple pattern and \emph{join} intermediate results according to the plan. This matching is supported by off-the-shelf triple stores. For instance, it is used by SemSearchPro~\cite{DBLP:journals/ws/TranHL11} for computing results for SPARQL queries, after they have been derived from keywords through query interpretation.

	\emph{Matching Incomplete Structure Patterns (Graph Traversal):}  While join-based evaluation is possible for structured pattern that are complete, traversing the data graph is needed when query patterns entail missing connections. That is, the query engines cannot directly combine partial results based on join variables but needs to explore for different paths between them. One combination that involves this type of matching is the evaluation of keyword queries over semantic data. As discussed before, the structure and semantics in the data can be used to interpret the keyword query and to convert it to a structured query. Instead of query interpretation, there are also systems~\cite{DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}, which use the same \emph{graph traversal} mechanism to directly evaluate the keyword query. They skip the computation of queries and directly explore for results in the data (subgraphs) that match the keywords. As opposed to standard IR-style keyword search on documents, the results here are semantic data graphs. That is, the keywords in the query do not refer to single documents but possibly, several entities that are connected through paths in the semantic data graph. Hence, simply joining results (documents), which match the query keywords is not sufficient. Entities matching keyword(s) in the query have to be retrieved, and subgraphs containing paths, which connect these keyword matching entities have to be explored in the data through traversing graph nodes and edges. A different semantics has been used~\cite{DBLP:conf/www/RochaSA04}, where results do not have to cover those nodes matching the query keywords. Those parts of the data, which are interesting and thus, shall be explored and returned as results, are controlled through manually defined traversal constraints that are realized via spreading activation.

Interestingly, graph traversal is also employed for the relational search scenario, where the relations (paths) between entities are unknown. For instance, the mechanism used by for graph exploration by Hermes~\cite{DBLP:journals/ws/TranWH09,DBLP:conf/icde/TranWRC09}, a keyword search system, is similar to the one proposed for answering P-Queries~\cite{DBLP:conf/www/AnyanwuS03}, a special type of queries that ask for unknown semantic associations between entities.

Another application of graph traversal has been proposed for the combined scenario of document and data retrieval. The goal is to find entities in the knowledge base, which are related to the documents to be retrieved, or vice versa, to retrieve documents related to some given entities. The starting points here are thus documents or entities, and traversal from these points are controlled through spreading activation~\cite{DBLP:conf/esws/SchumacherSS08}.

	\emph{Reasoning:} The formal well-defined semantics of some semantics models such as ontologies represented in OWL, have also be exploited for matching. More precisely, they are used for \emph{reasoning} to consider not only the available data but also new facts that can be automatically inferred from the formal semantics. For instance, the semantic models used in Serene~\cite{DBLP:journals/ws/FazzingaGGL11} is an ontology TBox represented as DL formulas, and semantic data are captured as ABox assertions of the same ontology. Serene uses an inference engine to derive new knowledge during an offline ontology compilation step. This computation is performed offline to improve the efficiency of online matching. Clearly, new knowledge relevant for the query can also be derived online. In ORAKEL for instance, the inference of new facts is performed as part of the computation of query matches. Notably, the first system created in the early years of Semantic Web research, which makes use of logical reasoning for computing semantic matches is SHOE~\cite{DBLP:conf/dagstuhl/HeflinHL03}.

\subsection{Matching: Combination of Techniques}

\section{Ranking}
Ranking approaches leverage different factors, which in general, can be \emph{query-independent} or \emph{query-dependent}. The latter considers the \emph{relevance} of the result with respect to the query. The former includes different aspects, such as \emph{rarity} (measured in terms of occurrence~\cite{DBLP:journals/internet/Aleman-MezaHARS05}), \emph{popularity} (based on occurrences~\cite{DBLP:conf/icde/TranWRC09}, or centrality~\cite{DBLP:journals/internet/Aleman-MezaHARS05}), \emph{predictability} (based on information content~\cite{DBLP:conf/www/AnyanwuMS05}), \emph{trust} (e.g. trust assigned to sources~\cite{DBLP:journals/internet/Aleman-MezaHARS05}) or \emph{confidence} (e.g. confidence scores of data extraction outputs~\cite{DBLP:conf/www/NieZWM05,DBLP:conf/vldb/ChengYC07}). They could be seen as heuristics, which can complement the ranking based on query-relevance. Among those heuristics, there are two prominent ones that are widely used in existing approaches, namely \emph{centrality-} and \emph{proximity-based ranking}.

\subsection{Centrality-based Ranking} The algorithms commonly used for computing centrality in the context of ranking is PageRank and HITS. Basically, the idea behind it is to perform link analysis on the graph formed by the hyperlink structure of documents to identify nodes that are important (or popular or authoritative). In the semantic search context, much effort has been invested in extending the original PageRank and HITS proposals towards dealing with semantic data graphs, where instead of documents and hyperlinks, there are entities that are connected through different types of semantic links. One of the first proposal for using PageRank for dealing with semantic data is OntoRank~\cite{DBLP:conf/semweb/DingPFJPK05}. However, ranking here is only dealt with at the level of sources, namely ontolgies (instead of the entities contained in them). PageRank could be directly applied because ontologies are treated as Web pages, and there are no different types of links. ObjectRank~\cite{DBLP:conf/vldb/BalminHP04} build upon PageRank, but recognizes the variety of semantic links. Instead of using the same authority flow for all edges, it employs an authority transfer schema graph, which captures the strengths of authority for different types of edges. While all these weights has to be manually specified by domain experts in ObjectRank, PopRank~\cite{DBLP:conf/www/NieZWM05} incorporates a simulated annealing algorithm to learn these weights, based on a partial weighting provided by experts. A different direction for obtaining the weights of semantic relations is taken by TripleRank, which models data by means of a 3-dimensional tensor. Applying the PARAFAC decomposition (a multi-modal counterpart to HITS) then results in authority and hub scores for both the entities and links. EntityAuthority~\cite{DBLP:conf/webdb/StoyanovichBBW07} operates not only on the semantic data graph but on a combined graph that contains both entities and documents as nodes. Also, a two-layer approach has been pursuit, where PageRank is computed both for the sources and the entities contained in them~\cite{DBLP:conf/esws/DelbruTCTD10,DBLP:conf/semweb/HarthKD09}.

\subsection{Proximity-based Ranking} Another popular heuristic that has been successfully used in IR is the proximity between terms~\cite{DBLP:conf/sigir/ButtcherCL06a,DBLP:conf/sigir/TaoZ07}. According to this, a result is ranked high when it contains query terms that appear closer to each other in its textual content. 
Note that while it is not independent of the query, this heuristic does not directly capture the query-relevance. This notion of proximity has also been used for XML data retrieval: XRank proposes to rank results based on the smallest text window, which contains all matches to query keywords~\cite{DBLP:conf/sigmod/GuoSBS03}. The notion of proximity has also been adopted to the case of semantic data, where instead of textual proximity (distance between terms), the distance between semantic entities is taken into account. For document retrieval, several proximity measures have been proposed to measure the distance between named entities extracted from text~\cite{DBLP:conf/iiwas/LeCHC11}. In keyword search over semantic data, results are subgraphs containing nodes matching the query keywords. One of the factor often used for ranking these results is based on the (pair-wise) distances between keyword matching nodes (the length of the paths connecting them)~\cite{DBLP:conf/cikm/LadwigT11,DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiJLF09}. Similar to text proximity, the intuition here is that more compact results more likely correspond to the intended need.

\subsection{Query-Relevance Based Ranking} Given the ambiguous query, different results can be found that vary in the degree relevance. This classic problem is extensively studied in IR. In the semantic search setting, existing IR concepts have been used and extended to deal with semantic data and to leverage the availability of semantics.

Many semantic search systems, which provide keyword search over semantic data, apply standard IR ranking. For instance, Falcons~\cite{DBLP:journals/ijswis/ChengQ09} uses a standard IR tool (Lucene~\footnote{\url{http://lucene.apache.org/java/docs/index.html}}) to index entities as documents, and uses the built-in ranking mechanism for entity ranking.

For ranking more complex (relational search) results, there are keyword search systems, which use the Vector Space Model and adopted the \emph{TFIDF-based} term weighting. The result in this setting is a graph, which contain a set of keyword matching nodes. A popular ranking is based on sum of the individual TF-IDF score computed for every keyword match via pivoted normalization weighting. Specific normalization methods have proposed to recognize that the textual length of the matching elements is often very short (document length normalization), different attributes can be associated with different vocabularies (IDF normalization) and a result is actually an “aggregation of documents” and thus requires additional normalization beyond the document level. Also TF-IDF has been adopted for the case of document retrieval using semantic data. Here the TF-IDF weighting has to be modified to consider not only the frequency of terms but also the frequency of named entities~\cite{DBLP:series/sci/NgoC10} and annotations~\cite{DBLP:journals/tkde/CastellsFV07}.

Taking the specific semantics of entity results into account, an extension of the \emph{BM25F} has been proposed~\cite{DBLP:conf/semweb/BlancoMV11}. The idea is to use different fields for indexing different properties of RDF entities. Different weights are assigned to these fields to recognize that some properties are more important than others in ranking entities.

Also, the more recent \emph{language modeling} (LM) paradigm has been adapted to this case of complex results. Language models for documents and queries are employed to represent them as multinomial distributions over words of the vocabulary. The KL-divergence, basically measuring the distance between the query and document distribution, can then be used for ranking. For ranking structured objects, three different models were studies~\cite{DBLP:conf/www/NieMSWM07}: The simple unstructured model treats all object attributes and values as vocabulary terms. The structured variant employs language models for specific components of the structured results. The record-level representation models an object through several language models, each capturing a record of that object. The attribute-level representation further segments a record into multiple fields and assigns different weights to individual fields (similar to the idea behind BM25F). Moreover, specific term distributions for fields have been proposed. Using edge-specific relevance models~\cite{DBLP:conf/cikm/BicerTN11}, the probability of observing a word in a structured result may vary, depending on the attribute (the edge) to be considered. This edge-specific model is employed not only to exploit the structure and semantics in the data but also to capture the semantics behind the keyword query. For this, an initial run over the semantic data is performed to obtain pseudo-relevance feedback (PRF) results for the keyword query. Instead of using the short and ambiguous keyword query, an edge-specific model constructed from these PRF results is used to capture the information need (the relevance).

As opposed to the approaches mentioned before, which model queries and documents based on words, there are also language models defined as probability distributions over RDF triples~\cite{DBLP:journals/debu/ElbassuoniRSW10}. The probability of a given triple should capture its ``informativeness'', which is measured based on witness counts. The authors implement this by issuing keyword queries for each triple using Web search engines, and used the reported result sizes as witness count estimates. Following the same direction, NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} not only uses informativeness but also a measure of confidence to estimate parameters of the language models.

\subsection{Ranking: Combination of Factors}
Clearly, the ranking implemented by a system is often a combination of factors. For instance, for searching entities detected from documents, EntityRank~\cite{DBLP:conf/vldb/ChengYC07} rank entities based on the popularity of documents they have been extracted from (computed via PageRank), the confidence of the extraction outputs, contextual constraints as well as the proximity among entities and query words. For retrieving more complex objects (comprises multiple records) extracted from web documents, experiments with Libra (a scientific Web search engine) have shown that ranking can be improved when taking extraction confidences both at the record- and attribute-level into account~\cite{DBLP:conf/www/NieMSWM07}. Structured results (a subgraph) obtained from keyword search over structured data is mostly ranked based on the PageRank of its constituent nodes, aggregation of query-relevance scores obtained for individual nodes (records) matching query keywords, and the proximity defined through the length of paths between nodes~\cite{DBLP:conf/icde/TranWRC09}.

\dtr{todo:learning to rank  \cite{DBLP:conf/cikm/CoffmanW11}}

\section{Main Approaches and Their Performances}	
Semantic search has been investigated from different communities in different context. In the IR community, semantic search has mainly been viewed from the perspective of \emph{document retrieval}. Here, classic \emph{conceptual} approaches based on the use of lexical models can be distinguished from more recent approaches that employ of \emph{annotations in the form of semantic data}. Another line of research is \emph{entity search}, which has been studied in the context of entities extracted from Web pages, Wikipedia pages corresponding to entities, and entities captured by databases and Semantic Web datasets. Another popular topic is \emph{keyword search over databases and Semantic Web data}, which is mainly about relational information. Last but not least, the \emph{processing of NL questions} entail specific challenges and opportunities, which has attracted attention from a specific community of researchers. We will now discuss the role of semantics in solving these different search tasks and its impact on performance.

\subsection{Conceptual Document Retrieval} This is the classic type of semantic search systems, which has been studied already in the early years of IR research. Researchers have recognized for a richer representation of the information needs and data that goes beyond the bag-of-words model. It became evident that constructing a full-fledge logic-based representation~\cite{DBLP:conf/sigir/Rijsbergen89} for queries and especially for documents is not practical. Thus, lightweight \emph{lexical models} have been employed to interpret the semantics of query and documents as concepts, and used within standard bag-of-words IR paradigm (e.g. vector space model and language model). Then, retrieval may be done based on concepts alone, or in the form of query and document expansion. In the latter case, bag-of-words model constitutes the basis while the conceptual understanding helps to refine or add more relevant words. However, there are \emph{no clear evidences suggesting conceptual IR can outperform standard IR techniques}. It has been shown that automatic query expansion in the large diverse TREC collection using WordNet degrades performance. Even when selected by hand, it helps only when the query is an incomplete description of the need~\cite{DBLP:conf/sigir/Voorhees94}. More recently, it has been shown for the medical domain (TREC Genomics) that retrieval based on concepts alone could not outperform the standard baseline based on words~\cite{DBLP:conf/trec/TrieschniggKS06,DBLP:conf/trec/ZhouYTS06}. Current work in this direction, which combines concepts and bag-of-words in the form of query expansion, outperforms a state of the art baseline in one collection, and shows similar performances in other collections~\cite{DBLP:journals/ipm/MeijTRK10}. However, the experiments have been performed on 
collections where documents have been manually annotated with concepts (domain-specific CLEF and TREC Genomics collections).

\subsection{Annotation-based Document Retrieval} This encompasses the newer type of approaches, which exploit advancements in data extraction technologies to obtain a richer representation of queries and documents, namely as entities and relations represented as annotations (query and document annotations, respectively). To date, there exist only anecdotal evidences for the merits of this type of systems. Possibly, the most conclusive result in this direction is based on experiments using the TREC Question Answering track: For a subset of manually chosen questions, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}. The results there can also be interpreted as follows: The employed data extraction programs were optimized for a few specific types of relations and entities (e.g. \verb+Person+). High precision is possible for questions that can be covered by these types of annotations. However, high recall is difficult because it requires the data extraction program to recognize arbitrary types of entities and relations. While there are promising ideas towards this kind of open data extraction, this problem remains an open challenge. Along this line, there is a study showing that the quality of data extractions significantly impacts search performance~\cite{DBLP:conf/cikm/Chu-CarrollP07}.

\subsection{Entity Search} While the two mentioned types focus on documents, this category includes search over (1) documents (for processing factoid and list questions of the TREC QA track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or for expert search questions of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}), over Wikipedia data, which as discussed, can be seen as a kind of semantic data, or (2) documents associated with metadata, (for answering entity related questions of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), or over pure (3) semantic data (for answering entity queries of the SemSearch Entity track~\cite{DBLP:conf/semweb/BlancoMV11}). Some type(1) systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}. As discussed, it has been shown that precision can be improved when high quality extraction outputs are available~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}. The use of semantics in type(2) systems is limited to viewing Wikipedia pages as entities~\cite{DBLP:conf/cikm/KapteinSVK10}, exploiting categories associated with them~\cite{DBLP:journals/tois/BalogBR11} and links between them~\cite{DBLP:conf/ecir/PehcevskiVT08}. It has been shown that Wikipedia articles can be effectively used as a pivot for entity search on the Web: it contain entities for a large amount of queries as well as cues (e.g. external links) that can be used to effectively find entities' official homepages on the Web~\cite{DBLP:conf/cikm/KapteinSVK10}. As a source of semantics, experiments have shown that category information helps to interpret the query and entity documents and to outperform standard text-based retrieval~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:journals/tois/BalogBR11}. While many type(3) systems~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/HoganHUKPD11,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09} have been built to search for entities over data crawled from the Semantic Web, solutions for ranking and the evaluation of their results have attracted interest only recently. The best performed method~\cite{DBLP:conf/semweb/BlancoMV11} is based on BM25F, which ranks entities as documents that are segmented into different fields corresponding to entity attributes.

\subsection{Relational Keyword Search}
This category comprises all approaches, which process keyword queries over semantic data~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}. While the results here include entities, the focus is to find possibly complex subgraphs encompassing several entities and relations between them (i.e. to support relational search). There exist a variety of indexing strategies and traversal algorithms that help to perform this task more efficiently. However, recent work~\cite{DBLP:conf/cikm/CoffmanW10} has shown that the proposed ranking strategies~\ref{DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiuYMC06} based on the adoption of proximity, TFIDF and PageRank do not perform well when considering a broad range of queries. This work aims at a standardized framework and benchmark for evaluating the effectiveness of relational keyword search approaches~\cite{DBLP:conf/cikm/CoffmanW10}. Based on this benchmark, it has been shown that best performance can be achieved through the use of edge-specific language models that are constructed for results and queries (based on PRF results)~\cite{DBLP:conf/cikm/BicerTN11}. \dtr{compare to recent learning to rank approach \cite{DBLP:conf/cikm/CoffmanW11}}.

\subsection{NL Question Answering} \dtr{are there benchmarks for NL QA over data?}

% Table generated by Excel2LaTeX from sheet 'Tabelle1'
\begin{table*}[htbp]
  \centering
  \caption{Add caption}
    \begin{tabular}{r|r|r|r|r|r|r|r|r|r}
    \hline
          &       & C-Search & IBM   & Falcons & Yahoo! & AquaLog & Hermes & Naga  & TASTIER \bigstrut\\
    \hline
    \multicolumn{1}{l|}{\multirow{3}[6]{*}{Need}} & \multicolumn{1}{l|}{Entity} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Fact} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Relation} &       &       &       &       &       &       &       &  \bigstrut\\
    \hline
    \multicolumn{1}{l|}{\multirow{4}[8]{*}{Query}} & \multicolumn{1}{l|}{Keyword} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{NL} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Facet} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Iterative} &       &       &       &       &       &       &       &  \bigstrut\\
    \hline
    \multicolumn{1}{l|}{\multirow{3}[6]{*}{Data}} & \multicolumn{1}{l|}{Raw Data} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Semantic Data} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Semantic Metadata} &       &       &       &       &       &       &       &  \bigstrut\\
    \hline
    \multicolumn{1}{l|}{\multirow{2}[4]{*}{Semantic Model}} & \multicolumn{1}{l|}{Lexical} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Knowledge} &       &       &       &       &       &       &       &  \bigstrut\\
    \hline
    \multicolumn{1}{l|}{\multirow{3}[6]{*}{Interpretation}} & \multicolumn{1}{l|}{Concept} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Entity} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Relation} &       &       &       &       &       &       &       &  \bigstrut\\
    \hline
    \multicolumn{1}{l|}{\multirow{4}[8]{*}{Matching}} & \multicolumn{1}{l|}{Term } &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Structured Pattern } &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Reasoning} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Traversal} &       &       &       &       &       &       &       &  \bigstrut\\
    \hline
    \multicolumn{1}{l|}{\multirow{3}[6]{*}{Ranking}} & \multicolumn{1}{l|}{Centrality} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Proximity} &       &       &       &       &       &       &       &  \bigstrut\\
\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Query Relevance} &       &       &       &       &       &       &       &  \bigstrut\\
    \hline
    \end{tabular}%
  \label{tab:addlabel}%
\end{table*}%

### 2012-02-21 tr-semanticsearchsurvey-data/intro.tex

@@
 Hence, different concepts and techniques have been studied in these settings.
-Most notably, there are principle differences between semantic search approaches, which use semantic resource to improve document retrieval, and the ones that compute direct results, i.e.
-\emph{semantic data retrieval}.
+Most notably, there are principle differences between semantic search approaches, which use semantic resource to improve \emph{document retrieval}, and the ones that compute direct results, i.e.
+semantic \emph{data retrieval}.
 
@@
 To the best of our knowledge, the only work...
-	\item Besides this general overview, we discuss the \emph{state-of-the-art in semantic data retrieval}, a direction of semantic search that aims at direct results as answers.
+%	\item Besides this general overview, we discuss the \emph{state-of-the-art in semantic data retrieval}, a direction of semantic search that aims at direct results as answers.
 For this, different data management and processing tasks are needed, from the crawling and integration of data up to the computation and presentation of results.
-	\item We present specific solutions that have been proposed for these individual tasks.
+%	\item We present specific solutions that have been proposed for these individual tasks.
 Particular emphasis is put on the most commonly used interface, namely \emph{keyword search}, and the concepts and techniques for dealing with the core search tasks of \emph{matching and ranking}.

### 2012-04-05 trunk/tr-semanticsearchsurvey-data/intro.tex

@@
 % unsolved information needs%
-Advancements in search technologies enable users to deal and to exploit the ever increasing amount of information that we can find in different scenarios -- from the personal desktop to enterprises' databases up to the large-scale Web.
-As opposed to the structured querying capabilities commonly provided by commercial databases that are only accessible by experts, \emph{search} is rather understood as a \emph{end-user oriented paradigm} that is based on \emph{intuitive interfaces} and access mechanisms.
-Solutions that are widely used especially on the Web are based on \emph{keyword search}, and in smaller-scale scenarios, also support natural language (NL) inputs.
+Advancements in search technologies enable users to deal with and to exploit the ever increasing amount of information that we can find in different settings -- from the personal desktop to enterprises' databases up to the large-scale Web.
+As opposed to the structured querying capabilities commonly provided by commercial databases that are only accessible by experts, \emph{search} is rather understood as an end-user oriented paradigm that is based on intuitive interfaces and access mechanisms.
+Solutions that are widely used especially on the Web are based on keyword search, and in smaller-scale scenarios, also support natural language (NL) inputs.
 While they are easy to use, the inputs provided by the users through these interfaces are \emph{ambiguous} such that the underlying information need (query intent) is not directly accessible to the system.
 Further, there are search scenarios where not only the query, but also the data representation does not precisely capture the semantics and structure of the underlying information.
-Accordingly, the core problems to be addressed in search are to \emph{understand the query intent and the data}, to \emph{match query against data}, and to \emph{rank results}.
+Accordingly, the core problems to be addressed in search are (1) to \emph{understand the query intent and the data}, (2) to \emph{match query against data}, and (3) to \emph{rank results}.
 
 \subsection{Many Unsolved Long-tail Queries}
-Modern search engines can effectively interpret the topics and based on that, disambiguates the need intended in the provided query inputs.
-Combining with additional (query-independent) factors such as PageRank, they are able to address a large fraction fraction of common information needs.
-In particular, queries that request for pages about a particular topic (\emph{topical query}) or representing popular entry points to commonly used information that can be reached via further browsing activities (\emph{navigational queries}), can be successfully processed.
-However, dealing with the large number of distinct queries in the ``long tail'' of Web query logs \cite{} remains challenging.
+Modern search engines can effectively interpret the topics (semantic themes) and based on that, disambiguates the need intended in the provided query inputs.
+Combined with additional (query-independent) factors such as PageRank, they are able to address a large fraction of common information needs.
+In particular, queries that request for pages
+%about a particular topic (\emph{topical query}) or 
+representing popular entry points to commonly used information that can be reached via further browsing activities (\emph{navigational queries}), can be successfully processed.
+These queries work particularly well when the entry points represent named entities (and these named entities are mentioned in the query).
+For instance, when searching for a concrete product, current search engines are not only able to correctly return matching pages, but also meaningful summaries containing core information about that product.
+Such a query is rather \emph{unambiguous}, i.e.
+captures a unique meaning.
+However, dealing with the large number of queries in the ``long tail'' of Web query logs \cite{} remains challenging.
 Two particular categories of problematic cases are ambiguous and complex queries:
 
-\begin{itemize}
-	\item \emph{Ambiguous queries}: these queries contain ambiguous terms, resulting in many possible interpretations (several query intents).
-For instance, the following query ask for entities (entity query):
-	\dtr{change running example} “Paris Hilton” “strong adventures people from Germany”
+%\begin{itemize}
+%	\item 
+	\textbf{Ambiguous Queries:} These queries contain ambiguous terms, resulting in many possible interpretations (several query meanings).
+For instance, the query ``young scholars from Germany'' is difficult to process because without any additional context, it is not clear who is ``young'', and different types of people may be considered as ``scholars''.
+Especially difficult are queries, which search for secondary meanings, e.g.
+``George Bush'', not the president but the beer brewer.
 
-	\item \emph{Complex queries}: this class of queries capture complex information needs which may involve several entities and relationships between them.
-As an example, we have a query that mentions several entity and ask for relationships between them (relational queries):
-	\dtr{change running example} “32 year old computer scientist living in Karlsruhe” “digital camera under 300 dollars produced by canon in 1992”
-\end{itemize}
+%	\item 
+	\textbf{Complex Queries:} this class of queries captures complex information needs, which may involve several entities and relationships between them.
+As an example, we have a query that mentions a person and a location, and asks for a relationship between that person and another location (relational queries):  ``birthplace of 32 year old computer scientist, who lives in Karlsruhe, a city in Germany''.
+%\end{itemize}
 
-Clearly, these two categories represent orthogonal aspects, namely the \emph{ambiguity of query terms} and the \emph{complexity of the intended information need}.
+Clearly, these two categories represent orthogonal aspects, namely the ambiguity of query terms and the complexity of the intended information need.
 Many queries in the long tail are both ambiguous and complex.
-They require deep understanding of the need and the information behind the query and data, respectively.
+They require \emph{deep understanding} of the need and the information behind the query and data, respectively.
 
 \subsection{Large Amount of Semantic Data}
-Targeting these problematic cases, semantic search solutions aim at exploiting the large and increasing amount of semantic resources that have been made available in different settings.
-These resources include taxonomies, thesauri and formal ontologies that can be used for the interpretation of query terms and data representation.
-More generally, also structured data exposed as graph-structured RDF data belong to this type of semantic resources (henceforth called \emph{semantic data}) that are used for semantic search.
-They come as standalone RDF datasets or are embedded in Web pages in the form of RDFa.
+Targeting these problematic cases, there is a category of search solutions -- often referred to as semantic search solutions -- that aim at exploiting the large and increasing amount of semantic resources that have been made available in different settings.
+Prominently, Google refers to this as the next generation of search in a recent issue of the Wall Street Journal.
+
+Semantic resources are used by these solutions for the interpretation of queries and data. They include taxonomies, thesauri and formal ontologies. 
+More generally, also structured data exposed as graph-structured RDF\footnote{RDF stands for Resource Description Framework, a W3C Semantic Web standard for data representation and exchange on the Web: \url{http://www.w3.org/RDF/}} data are regarded as semantic resources (often called \emph{semantic data}).
+They come as standalone RDF datasets or are embedded in Web pages in the form of RDFa (a W3C standard\footnote{http://www.w3.org/TR/xhtml-rdfa-primer/} for embedding RDF data in Web pages).
 These data have been increasing rapidly.
-As a result of community projects such as Linking Open Data~\footnote{}, a large amount of structured datasets formerly kept protected in databases are now exposed as publicly Web-accessible RDF data.
+As a result of community projects such as Linking Open Data\footnote{\url{http://www.w3.org/wiki/SweoIG/TaskForces/CommunityProjects/LinkingOpenData}}, a large amount of structured datasets formerly kept protected in databases are now exposed as publicly Web-accessible RDF data (e.g.
+Linked Data\footnote{\url{http://linkeddata.org/}}).
 Besides large companies such as BestBuy and Facebook, also national governments such as the US and UK have followed this direction of publishing and linking semantic data on the Web.
-As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups~\cite{}.
+As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups such as RDFa~\cite{}.
 
 The main idea behind semantic search solutions is to use these semantic resources to improve the search performance.
-Taxonomies, thesauri, and ontologies capture semantics that can be used to understand the query and data and to resolve ambiguities.
-Instead of returning textual data in documents, precise facts capturing entity related information and their relationships can be directly retrieved from semantic data to provide \emph{direct answers} to complex queries.
+Taxonomies, thesauri, and ontologies capture semantics that can be used to understand the query and data and to \emph{resolve ambiguities}.
+Instead of returning textual data (Web pages, documents), precise facts capturing entity related information and their relationships can be directly retrieved from semantic data to provide \emph{direct answers to complex queries}.
 
 \subsection{Plethora of Semantic Search Solutions}
-Capitalizing on the opportunities that arise from this increasing wealth of semantic resources on the Web, commercial search engines have made different kinds of semantic search features available to end users.
-The first well-known example towards this direction is Powerset, which makes use of semantic data extracted from Wikipedia to answer complex questions.
-Semantic data embedded in Web pages are now actively used by Google to provide rich result snippets\footnote{}.
+Capitalizing on the opportunities that arise from this large and increasing amount of semantic resources on the Web, commercial search engines have made different kinds of semantic search features available to end users.
+The first well-known example towards this direction is Powerset\footnote{\url{http://en.wikipedia.org/wiki/Powerset_(company)}}, which makes use of semantic data extracted from Wikipedia to answer complex questions.
+Semantic data embedded in Web pages are now actively used by Google to provide rich result snippets\footnote{\url{http://www.google.com/webmasters/tools/richsnippets}}.
 
 Likewise, research interest in semantic search is stirring up.
-A large body of work has been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web.
+A wide range of semantic search approaches have been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web.
 Correspondingly, semantic search has been viewed from different angles, resulting in a plethora of solutions.
-While underlying all these efforts lie one central idea, namely to use semantic resource for more effective search, existing approaches greatly vary in the information needs, the query and the data that are supported.
-Hence, different concepts and techniques have been studied in these settings.
-Most notably, there are principle differences between semantic search approaches, which use semantic resource to improve document retrieval, and the ones that compute direct results, i.e.
-\emph{semantic data retrieval}.
+
+Underlying all these efforts lie one central idea, namely to use semantic resources for more effective search.
+However, existing approaches greatly vary in the \emph{data}, (2) the \emph{semantic resources}, the \emph{information needs} and (4) the \emph{querying paradigms} that are supported.
+Most notably, there are principle differences between semantic search approaches, which use semantic resources to improve document retrieval, and the ones that compute direct results, i.e.
+semantic data retrieval.
+That is, whereas the one category of approaches focuses on textual data, the other category targets the case of structured and semantic data.
+The specific types of semantic resources used by these approaches vary and may include thesauri, full-fledge ontologies or large amounts of semantic data.
+With respect to information needs, solutions focusing on the retrieval of single entities (and documents) can be distinguished from relational ones, where relationships between entities have to be considered.
+Substantial differences also exist between systems, which either use NL, keywords or facet-based operations as the primary means for querying.
+Further, research work found in literatures often studies one of the specific (5) \emph{subproblems in search}: Namely, different concepts and techniques have been proposed for (5a) the interpretation of query inputs and data, (5b) matching the query intent against data and (5c) ranking results.
 
 \subsection{Contributions}
-Concepts for semantic search have been around for several several years and its mainstream adoption into commercial solutions is increasingly visible.
+Different solutions for semantic search have been around for a long time.
+In this work, we present a systematic survey to provide a taxonomy of various semantic search approaches, to reflect on the achievements that have been made over these years, and finally, to discuss the challenges ahead and directions for future research.
 
-\begin{itemize}
-	\item In this work, we present a systematic survey to provide a \emph{taxonomy of various semantic search approaches}, to reflect on the achievements that have been made over these years, and finally, to discuss the remaining challenges and directions for future research.
-To the best of our knowledge, the only work...
-	\item Besides this general overview, we discuss the \emph{state-of-the-art in semantic data retrieval}, a direction of semantic search that aims at direct results as answers.
+% and their mainstream adoption into commercial solutions is increasingly visible. 
+There exist a few usability studies, which compare several semantic search solutions~\cite{DBLP:conf/semweb/KaufmannB07,DBLP:conf/esws/TranMH10}.
+However, this line of work focuses on the differences in querying paradigms.
+Towards a classification of semantic search approaches, Mangold discusses existing solutions along the dimensions of architecture, coupling, transparency, user context, ontology structure and ontology technology~\cite{DBLP:journals/ijmso/Mangold07}.
+The last two criteria basically capture the differences in semantic resources among existing systems, which are also discussed in our study.
+In addition to query paradigms and semantic resources, our study includes the aspects of data, information needs, and provides a fine-grained taxonomy that distinguishes approaches by the subproblems in search they addressing.
+Further, whereas the previous survey~\cite{DBLP:journals/ijmso/Mangold07} focuses on document retrieval, our study aims at a unified view of document and data retrieval.
+In particular, we cover a large body of recent work that is not part of that previous survey.
+
+%	\item Besides this general overview, we discuss the \emph{state-of-the-art in semantic data retrieval}, a direction of semantic search that aims at direct results as answers.
 For this, different data management and processing tasks are needed, from the crawling and integration of data up to the computation and presentation of results.
-	\item We present specific solutions that have been proposed for these individual tasks.
+%	\item We present specific solutions that have been proposed for these individual tasks.
 Particular emphasis is put on the most commonly used interface, namely \emph{keyword search}, and the concepts and techniques for dealing with the core search tasks of \emph{matching and ranking}.
 
-\end{itemize}
-
 \subsection{Outline}
+The paper is organized as follows: An overview of semantic search and the concepts it entails is presented in Section~\ref{sec:ss}.
+Then, the paper is organized mainly along the aspects based on which we distinguish different semantic search approaches.
+Different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and ~\ref{sec:semantics}.
+Then approaches are discussed along the subproblems of content interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}.
+After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches}.
+Main challenges derived from that and implications for future work are presented in Section~\ref{sec:challenges}, before we finally conclude in Section~\ref{sec:conclusion}.

### 2012-04-05 trunk/tr-semanticsearchsurvey-data/overview.tex

@@
-\section{Semantic Search}
-\begin{figure}[tbh]
+\section{Semantic Search}\label{sec:ss}
+
+\begin{figure}
 	\centering
 		\includegraphics[width=0.35\textwidth]{figs/semsearch.pdf}
+	\caption{Semantic Search.}
 	\label{fig:semsearch}
-	\caption{Semantic Search.}
 \end{figure}
 
-Basically, \emph{search} can be characterized by three components, namely the \emph{data}, the \emph{query} and the \emph{matching framework} for computing results from the data for a given query.
+Basically, \emph{search} can be characterized by three components, namely the \emph{data}, the \emph{query} and the \emph{matching} framework for computing results from the data for a given query.
 This is illustrated in the left portion of Fig.~\ref{fig:semsearch}.
-One main characteristic of concepts behind search is its emphasize on \emph{end users}.
-That is, search typically involves intuitive interfaces targeting users, who may do not possess knowledge about the domain, the data, and the underlying query language.
+One main characteristic of search concepts is its emphasize on end users.
+That is, search typically involves intuitive interfaces targeting users, who may do not possess knowledge about the domain, the data and structured query languages.
 The query inputs that can be obtained from these interfaces are often ambiguous.
-That is, they allow for many possible interpretations, which in turn, result in many possible results.
-Because end users are often only interested in the few best results, \emph{ranking} is considered as an essential component in search.
-That is, the matching framework not only specifies what constitutes matches but also their degree of matching.
+That is, they allow for many possible \emph{interpretation}s, which in turn, yield many possible results that vary in relevance w.r.t.~ the intended query intent.
+% Because end users are often only interested in the few best results, 
+\emph{Ranking} is an essential component in search that aims to address this, i.e.
+to distinguish results in terms of relevance.
+Basically, matching can be conceived as the task of identifying matches whereas ranking is more specifically about the degree of matching.
 
-\emph{Semantic search} is a concept widely used by different communities to refer to search approaches that broadly speaking, aim to \emph{use semantics to improve the search experience}.
-Considering the core search tasks, semantics has been used to obtain a better understanding of the data and query and to improve matching and ranking based on that (see Fig.~\ref{fig:semsearch}).
+\emph{Semantic search} is a concept widely used by different communities to refer to search approaches that broadly speaking, use semantics to improve the search experience.
+Considering the core search tasks, semantics has been used to obtain a better understanding of the data and query as well as to improve matching and ranking based on that (see Fig.~\ref{fig:semsearch}).
 There are exist different notions of semantics.
 One the one hand, there are proposals for using the semantics of words captured as latent concepts (e.g.
-to use Latent Semantic Indexing for IR \cite{DBLP:conf/sigir/Hofmann99}) or latent topics (e.g.
-to use Latent Dirichlet Allocation~\cite{DBLP:conf/sigir/WeiC06}).
+inferred through Latent Semantic Indexing~\cite{DBLP:conf/sigir/Hofmann99}) or latent topics (e.g.
+inferred through Latent Dirichlet Allocation~\cite{DBLP:conf/sigir/WeiC06}).
 While these models only implicitly capture the semantics in terms of some latent, unknown dimensions, there are also explicit models of semantics.
-For instance, Explicit Semantic Analysis uses Wikipedia articles, categories, and relations between articles to capture semantics.
+For instance, Explicit Semantic Analysis uses Wikipedia articles, categories, and relations between articles to capture semantics in terms concepts, which are then used for concept-based IR~\cite{DBLP:journals/tois/EgoziMG11}.
 Other explicit models of semantics (henceforth called \emph{semantic models}) include thesauri, the terminological part (TBox) of ontologies and data schemas.
 While these models capture semantics at the conceptual level, there are also \emph{semantic data} capturing the semantics of individual entities.
-To accommodate the plethora of approaches that exist, we propose the following definition of semantic search.
+To accommodate the wide range of semantic search approaches that exist, we formulate the following general notion of semantic search:
 
-\begin{definition}[Semantic Search] Semantic search is a search paradigm that make uses of \emph{explicit semantics} to solve any of the \emph{core search tasks}, i.e.
-interpreting query and (or) data, matching and ranking.
+\begin{definition} \emph{Semantic search} is a search paradigm that makes use of explicit semantics to solve core search tasks, i.e.
+to use semantics for interpreting query and data, matching query against data and ranking results.
 \end{definition}
 
-While all existing semantic search systems use some kinds of explicit semantics, the retrieval context and the specific semantic models and data used to deal with the meaning behind the query intent and data vary.
+While all semantic search approaches involve some kinds of explicit semantics, the retrieval contexts and the specific semantic models used to deal with the meaning behind the query intent and data vary.
+In particular, we identified the following aspects, based on which we will characterize and distinguish existing solutions:
 
-\emph{Document Retrieval:} The IR community targets the document retrieval context where results are to be retrieved from a collection of documents.
-The traditional type of semantic models used here are thesauri that are employed to \emph{interpret} the terms in the textual representation of queries and data (i.e.
-documents).
+\begin{itemize}
+\item the type of targeted \emph{information needs},  
+\item the representation of information resources (\emph{data}), 
+\item the representation of the information need (\textit{query}) or respectively, the underlying method for querying the data (querying paradigms), 
+\item the \emph{semantic models} used to understand and to represent the meaning behind query and data, 
+\item the framework for \emph{matching} queries against data, which also involves \emph{interpreting} the data and query intent as well as \emph{ranking} the results.  
+\end{itemize}
+
+For instance, we can look at the differences in the data to arrive at the distinction between document retrieval and data retrieval, two major research directions in search that mark the borders of large communities.
+
+\textbf{Document Retrieval:} The IR community targets the document retrieval context where results are retrieved from a collection of documents (primarily textual data).
+Semantic search of this type is different from standard document retrieval approaches in the use of semantics.
+The traditional type of semantic models used here are thesauri that are employed to interpret the terms in the textual representation of queries and data.
 Recently, semantic data such as RDF resource descriptions have also been employed to interpret query and documents in terms of real-world entities and their relations.
 
-\emph{Data Retrieval:} Querying entities and their relationships is a core problem in database research.
-As opposed to the hidden semantics of textual content in documents, information about entities and their relationships are explicitly available in this setting -- either directly as semantic data in RDF or as structured data that can be converted to RDF.
+\textbf{Data Retrieval:} Querying entities and their relations is a core problem in database research.
+As opposed to the hidden semantics of textual content in documents, information about entities and their relations are explicitly available in this setting -- either directly as semantic data in RDF or as some kinds of structured data that can be converted to RDF.
 Thus, understanding the semantics of the underlying data is not the problem here.
-However, as opposed to classic data retrieval that is based on structured query languages, intuitive query interfaces are needed in the search context.
-This lead to the classic search problems of interpreting the query intent and ranking the many possible results.
+However, as opposed to standard data retrieval that is based on structured query languages, intuitive query interfaces are needed in the search context.
+This leads to the issue of ambiguity.
+Hence, semantic search approaches of this type have to deal with the resulting problems of interpreting the query intent and ranking the many possible results.
 %Just like in the document context, the goal here is to enable easy access to the most relevant results.
@@
 %Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs.
-We characterize the many different solutions along the following dimensions:
 
-\begin{itemize}
-\item the type of targeted \emph{information needs},  
-\item the representation of the information need called \textit{query}, 
-\item the representation of the underlying resources called \emph{data}, 
-\item the \emph{semantic models} used to understand query and data, 
-\item the framework for \emph{matching} queries against data, which also involves \emph{interpreting} the content and the user intent as well as \emph{ranking} the results.  
-\end{itemize}
+More fine-grained than this general breakdown into document and data retrieval, Fig.~\ref{fig:semsearch_detailed} illustrates the specific differences in queries, data, semantics, results (corresponding to information needs) and solutions for the subproblems that distinguish existing semantic search approaches.
+We can see that central to semantic search is the use of semantics (depicted as gray boxes in Fig.~\ref{fig:semsearch_detailed}).
+In particular, semantic resources represented by lexical models, knowledge models as well as semantic data and metadata are used for the subproblems of understanding raw data (e.g.
+text) and queries.
+The resulting semantics of data and queries are then employed for solving the subproblems of matching and ranking.
 
-A general overview of the main types of information needs (results), queries, data, semantic models as well as interpretation, matching and ranking techniques supported by existing semantic search solutions is illustrated in Fig.~\ref{fig:semsearch_detailed}.
-We will now discuss existing solutions along these dimensions.
+%We will now discuss them along these aspects.
 
@@
 	\centering
-		\includegraphics[width=0.85\textwidth]{figs/semsearch_detailed.pdf}
+		\includegraphics[width=0.75\textwidth]{figs/semsearch_detailed}
+	\caption{Overview of Semantic Search Approaches.}
 	\label{fig:semsearch_detailed}
-	\caption{Overview of Semantic Search Approaches.}
 \end{figure*}
 
-\section{Information Needs}
-The main motivation for semantic search is to go beyond the relatively frequent but simple queries currently supported by existing search solutions to solve the long-tail queries representing rather complex information needs.
+\section{Information Needs}\label{sec:needs}
+
+The main motivation for semantic search is to go beyond the relatively frequent but simple queries currently supported by existing Web search solutions to solve the long-tail queries representing rather complex information needs.
 But also for simple queries, semantic data have proven to be valuable.
-Instead of showing documents, semantic data are used by commercial Web search engines to create rich snippets for Web pages, or to deliver direct answers.
+Instead of showing documents, semantic data are used by commercial Web search engines to create rich snippets for Web pages, or to deliver direct answers, e.g a specific address for a query mentioning ``location'' and a named entity such as ``Yahoo!
+Research Lab Barcelona''.
+We will now discuss several common types of queries and the information needs behind them, from the more simple entity queries to complex relational and analytical queries.
 
-\subsection{Entity Search} most queries on the Web asked for Web pages representing entities such as organization or people.
-They are used to obtain entry points, while additional navigation and browsing is still required to satisfy the actual information need.
-Thus, these queries are also referred to as navigational queries.
-Semantic data embedded in Web pages have been exploited by Google to present rich entity snippets\footnote{Google Rich Snippets} to this kind of queries.
+\subsection{Entity Search} Most queries on the Web ask for pages representing entities such as companies or people.
+They are used to obtain entry points, while additional navigation and browsing are still required to satisfy the actual information need.
+Thus, in the IR context, these queries are also referred to as navigational queries.
+Recently, semantic data embedded in Web pages have been exploited to address this type of queries.
+This was pioneered by Yahoo!
+in their SearchMonkey program, and later adopted by Google to present rich entity snippets\footnote{Google Rich Snippets} as answers to this kind of queries.
+As an example, Fig.~\ref{fig:semantic_layer} illustrates the entity search functionalities provided by Yahoo!.
+Not only there are Web pages but also entity descriptions appear as results.
+These descriptions are directly retrieved from semantic data (in this case, a dataset about music artists and their albums).
 Instead of searching over a collection of documents, semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results.
-Examples for this include the one asking for ``young scholars in Germany'' already mentioned before, or the query ``Researcher Thanh Tran'' depicted in the top left portion of Fig.~\ref{fig:matching}.
+Examples for this type of queries include the one asking for ``young scholars in Germany'' already mentioned before, or the query ``Researcher Thanh Tran'' depicted in the top left portion of Fig.~\ref{fig:matching}.
 Results for queries of this type comprise one or several entities.
 
-\subsection{Factual Search} While results to the previous type of queries presented to the users are either some entity descriptions or Web pages about entities, the information needs behind this type of search require specific information from these descriptions and pages, respectively.
+\subsection{Factual Search} While results to the previous type of queries presented to the users are either some entity descriptions or Web pages about entities, the information needs behind this type of search requests require specific information from these descriptions and pages, respectively.
 Many searches on the Web for instance, aim at finding the ratings of restaurants, or the phone number of a particular person.
 To continue with our example, users may directly ask for ``the birth place of young scholars in Germany''.
-Direct answers to this type of queries are supported by WolframAlpha\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge~\footnote{\url{http://www.trueknowledge.com/}}, or the various research prototypes such as Hermes~\cite{DBLP:journals/ws/TranWH09} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}.
+Direct answers to this type of queries are supported by WolframAlpha\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge\footnote{\url{http://www.trueknowledge.com/}}, or the various research prototypes such as Hermes~\cite{DBLP:journals/ws/TranWH09} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}.
 Since factual search is mostly about facts that correspond to attribute values of entities, it is often regarded as a particular type of entity search.
-We also do not further distinguish this from the general entity search task.
+In this survey, we do not further distinguish this from the general entity search task.
 
@@
 Relations may be explicitly specified as part of the keyword or NL query, and entities satisfying these relation constraints can be computed using SemSearchPro~\cite{DBLP:journals/ws/TranHL11} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}.
-Other systems such as NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} also support searches where relations to be considered are not explicitly mentioned in the query, or unknown.
-They address information needs that involve finding ``how some entities are related to some other entities''.
-The interesting part of the results here are thus not the entities, but the relationships between them -- also referred in literatures as semantic associations (direct connection) or property sequence (path)~\cite{DBLP:conf/www/AnyanwuS03}.
-An example for this query, asking for paths between ``Peter Mika'' and ``Thanh Tran'' is depicted in top right portion of Fig.~\ref{fig:matching}.
 
-\section{Queries}
-Typically, answering complex questions requires the expertise of technical users who know the underlying data and schema and use them to formulate questions as structured queries.
+Other systems such as NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} also support searches where relations to be considered are not explicitly mentioned in the query, or simply \emph{unknown}.
+They address information needs that involve finding how some entities are related to some other entities.
+The interesting part of the results here are thus not the entities, but the relationships between them -- also referred in literatures as semantic associations (direct connection) or property sequences (indirect connections, i.e.
+path)~\cite{DBLP:conf/www/AnyanwuS03}.
+An example for this type of query asking for paths between ``Peter Mika'' and ``Thanh Tran'' is depicted in the top right portion of Fig.~\ref{fig:matching}.
+
+Even though Yahoo!
+entity search as shown in Fig.~\ref{fig:screenshot_yahoo} does not directly search for relations, it can be seen on the left portion that relations between entities captured in semantic data constitute valuable information for suggesting related entities.
+Searching for known relations or unknown relations is supported by the Information Workbench\footnote{\url{http://iwb.fluidops.com}}, a commercial adoption of SemSearchPro.
+On the bottom part of Fig.~\cite{fig:screenshot_iwb}, we can see results returned to a query that specifically asks for entities connected through the \verb+producer+ relation.
+When relations are not explicitly given in the query but only entities and (or) concepts, this system is also able to explore paths between them.
+However, this system does not directly return relationships and paths in the data as results, but structured queries representing interpretations of the entered keywords -- a querying paradigm we will discuss in the next section.
+
+\subsection{Analytical Search}
+Beyond the common searches for entities and relations, which form the focus of this survey, there are also information needs, which can only be addressed when some additional analyses are performed on top of the data.
+Generally speaking, any kind of additional computation may be applied to the data and results for the purpose of analytical search.
+Analytics often found in semantic search engines are supported through simple sorting and averaging, more sophisticated statistical and mathematical models, or some form of Machine Learning based inductive reasoning or logic-based deductive reasoning.
+For instance, WolframAlpha is advertised as a computation engine because it applies different kinds of mathematical models to compute answers to queries, whereas True Knowledge uses an inference engine to perform temporal and geospatial reasoning.
+
+\begin{figure}
+	\centering
+		\includegraphics[width=0.5\textwidth]{figs/screenshot_yahoo}
+	\caption{Entity search with Yahoo!.}
+	\label{fig:screenshot_yahoo}
+\end{figure}
+
+\section{Querying Paradigms}\label{sec:querying}
+Typically, addressing complex needs requires the expertise of technical users who know the underlying data and schema and use them to formulate questions as structured queries.
 However, search is commonly seen as an end-user oriented paradigm, which instead of using structured query languages, involves intuitive and easy-to use access interfaces.
-The there main interfaces studied for semantic search are based on keywords, NL, and facets.
+The three main interfaces studied for semantic search are based on keywords, NL, and facets.
 Often, a combination of these paradigms, e.g.
@@
 Keywords can also be used to formulate more complex relational searches.
-Addressing this scenario, engines such as Hermes~\cite{DBLP:journals/ws/TranWH09}, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}, AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} and TASTIER~\cite{DBLP:conf/sigmod/LiJLF0} retrieve entities matching keywords, and search for relations between them in the data.
+Addressing this scenario, engines such as Hermes~\cite{DBLP:journals/ws/TranWH09}, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}, TASTIER~\cite{DBLP:conf/sigmod/LiJLF0} and IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} retrieve entities matching keywords, and search for relations between them in the data.
 
 \subsection{NL Search} This is the other paradigm for users to express their needs using their own words.
-Traditionally, it has been used to formulate complex questions against expert systems built for specific domains.
-Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha and True Knowledge.
+Traditionally, it has been used to pose complex questions against expert systems built for specific domains.
+Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha, True Knowledge and Apple's Siri\footnote{\url{http://en.wikipedia.org/wiki/Siri_(software)}}.
 
 \subsection{Faceted Search} Instead of formulating the entire query at once, \emph{faceted search} supports an iterative process of querying, browsing and query refinement.
+This belongs to the broader category of approaches called \emph{exploratory search}, which assumes that users do not precisely know how or what to search and thus, combines querying and browsing strategies to enable learning and investigation.
 Upon the initial search performed by the user (e.g.
-using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/semweb/FerreH11,DBLP:conf/esws/HeimEZ10} presents results as well as facets representing attributes and relations relevant for entities in the result list.
-These facets can then be used to browse the results and to refine or expand the initial query.
-While most faceted search solutions focus on browsing and refining results of entity queries, faceted search in principle can also be used to capture complex needs.
-For instance, gFacet\cite{DBLP:conf/esws/HeimEZ10} supports relational search through the construction of complex facet graphs representing different types of entities and relations between them.
+using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/semweb/FerreH11,DBLP:conf/esws/HeimEZ10} present results as well as facets representing attributes and relations that are applicable for refining (or simply, are related to) the current results.
+These facets can then be used to browse, to refine or to expand the results (i.e.
+to modify the query, respectively).
+Microsoft's EntityCube\footnote{\url{http://entitycube.research.microsoft.com/}} for instance, returns entities upon users' keyword search requests along with relations and attributes of these entity results as facets.
+Parallax\footnote{\url{http://www.freebase.com/labs/parallax/}} is another commercial faceted search solution (from Freebase, now Google) that enables a combination of search, intelligent result visualization and facet-based browsing.
 
-\subsection{Iterative Search}
-While faceted search is a popular paradigm, there are other similar interfaces that support an \emph{iterative search} process.
-Instead of showing facets as users type, also \emph{completions} of the user keywords as well as completions in the form of results matching the (possible interpretations of the) the keywords provided so far (also called result completion~\cite{DBLP:conf/esws/TranMH10}) have been presented.
-For instance, ESTER~\cite{DBLP:conf/sigir/BastCSW07} shows entity search results matching the keywords as well as their facets while TASTIER~\cite{DBLP:conf/sigmod/LiJLF09}, provides type-ahead search by finding complex (joins of) database tuples as the user types in query keywords.
+While most faceted search solutions focus on browsing and refining results of entity queries, faceted search in principle can also be used to address complex needs.
+For instance, gFacet~\cite{DBLP:conf/esws/HeimEZ10} supports relational search through the construction of complex facet graphs representing different types of entities and relations between them.
+Fig.~\ref{fig:screenshot_iwb} shows the faceted search feature from the Information Workbench.
+Every column in the result table captures one particular type of entities and this system shows facets for every type that appears in the results (e.g.
+Fig.~\ref{fig:screenshot_iwb} shows facets for column 1).
+Hence, entries in every column (representing a partial result and a query part, respectively) can be refined or expanded.
+For instance, the column of singles shown in Fig.~\ref{fig:screenshot_iwb} can be further refined to contain only those connected with \verb+Freddie Mercury+ through the \verb+writer+ relation.
+
+\subsection{Iterative / Exploratory Search} 
+While faceted search is the most popular paradigm in the industry, there are other exploratory search interfaces that support an \emph{iterative search} process.
+Instead of showing facets as users type, also \emph{completions} of the single user keywords (term completions) or of the entire query representing the full query intent (query completions) have been proposed.
+One example system supporting this is the Information Workbench shown in Fig.~\ref{fig:screenshot_iwb}, which presents terms matching the current tokens entered by the users, as well as full interpretations of the entire query.
+For ``queen single'', the interpretations shown indicate that the query intent may be something matching the word ``queen'' that is of the type \verb+single+, or something that is of the type \verb+single+, which is produced (or written) by something else matching the word ``queen''.
+Google, Freebase\footnote{\url{http://www.freebase.com/docs/suggest}} and True Knowledge also present possible interpretations of the query as the user type or after issuing a query.
+
+Instead query-based completions, also results matching the (possible interpretations of the) keywords provided so far have been presented (called result completions~\cite{DBLP:conf/esws/TranMH10}).
+For instance, ESTER~\cite{DBLP:conf/sigir/BastCSW07} shows entity search results matching the keywords as well as their facets (see CompleteSearch~\footnote{\url{http://www.dblp.org/search/index.php}}, which is an adoption of ESTER) whereas TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} provides type-ahead search by finding complex (joins of) database tuples as the user types query keywords.
 With these systems, users can iteratively construct the query by selecting the presented completions and facets.
-VisiNav~\cite{DBLP:journals/ws/Harth10} goes beyond this, allowing iterative query construction also via drag and drop.
+VisiNav~\cite{DBLP:journals/ws/Harth10} goes beyond this selection-based interaction, allowing iterative query construction also via drag and drop.
 
-\section{Data}
-Data used in semantic search solutions can be broadly categorized into two types, namely \emph{semantic data} and \emph{raw data}.
-The latter basically comprises all representations of media objects such as audio, video and text.
-There are solutions~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09}, which specifically target the data extracted from Semantic Web sources.
-That is, they directly operate on semantic data.
-In fact, structured data used in most data retrieval systems can be converted to a form that corresponds to the general notion of semantic data~\cite{DBLP:conf/sigmod/LiJLF09}.
-On the other hand, semantics may not be directly captured by semantic data but extracted from raw data.
-This is especially the case for document retrieval systems, where one of the essential task in semantic search is to obtain a semantic data representation of the documents (called \emph{semantic metadata}).
+\begin{figure}
+	\centering
+		\includegraphics[width=0.5\textwidth]{figs/screenshot_iwb}
+	\caption{Querying with the Information Workbench.}
+	\label{fig:screenshot_iwb}
+\end{figure}
 
-\subsection{Structured / Semantic Data}  The most common type of semantic data used in semantic search systems is RDF.
-Basically, RDF can be seen as a graph-structured model, representing entities, their attributes, and relations between them as a set of triples.
-A visual representation of such a \emph{semantic data graph} capturing information about two \verb+researcher+s with the \verb+name+s \verb+Thanh Tran+ and \verb+Peter Mika+ is depicted in the bottom portion of Fig.~\ref{fig:matching}
+\section{Data}\label{sec:data}
+The information resources made available for search as well as any kind of additional background information used to improve the search experience, are kept and managed by the system as data.
+In semantic search solutions, data can be broadly categorized into two types, namely \emph{semantic data} and \emph{raw data}.
+
+Basically, semantic data describe real-world objects in terms of entities and their relations.
+Primarily, semantic data have been used to refer to RDF datasets, or instance data contained in ontologies represented in Semantic Web languages such as OWL (the Web Ontology Language, a logic-based W3C standard\footnote{http://www.w3.org/TR/owl-features/} for representing the semantics of vocabulary / schema elements) and RIF (the Rule Interchange Format, a W3C standard for representing and exchanging rules).
+However, different kinds of structured data actually correspond to this rather general notion of semantic data.
+In fact, large amounts of structured data formerly kept in hidden
+%XML or relational 
+Web databases 
+have been converted to and published on the Web as RDF data.
+Several semantic search systems have been built that specifically target the retrieval of semantic data.
+Instead of searching directly over semantic data, classic retrieval systems search over a raw data representation of information objects such as audios, videos, images and texts.
+For instance, document retrieval systems search for textual documents that are represented as bags of words.
+As opposed to semantic data, raw data do not explicitly capture the semantics of information resources in terms of entities and their relations.
+Thus, for supporting document (or image, video or audio) retrieval as semantic search, one core subtask is the recognition of named entity in the raw text.
+Named entity recognition and other data interpretation tasks such as relation extraction are performed to obtain a semantic data representation of raw data (also called \emph{semantic metadata}).
+
+\subsection{Semantic Data}  The most common type of semantic data used in semantic search systems is RDF.
+Basically, RDF is a graph-structured model, representing entities, their attributes, and relations between them as a set of triples.
+A visual illustration of such a \emph{semantic data graph} capturing information about two \verb+researcher+s, whose \verb+names+ are \verb+Thanh Tran+ and \verb+Peter Mika+, is depicted in the bottom portion of Fig.~\ref{fig:matching}
 
@@
 Likewise, information contained in tuples of a relation database can be mapped to nodes, while foreign key relationships can be modeled as edges.
-In fact, the conversion of XML and relational data to a RDF semantic data graph can be accomplished by using mapping rules, and there exist many standards and tools for accomplishing that (see \url{http://www.w3.org/2001/sw/rdb2rdf/}).
-Represented as RDF, these and possibly other types of structured data also capture knowledge in terms of entities and their relations.
-Hence, especially after its conversion to RDF, structured data is often synonymously referred to as semantic data.
-In line with this general notion, semantic data used in semantic search systems can be defined as follows:
+In fact, the conversion of XML and relational data to a RDF semantic data graph can be accomplished by using mapping rules, and there exist many standards and tools for accomplishing that (e.g.
+see W3C RDB2RDF\footnote{\url{http://www.w3.org/2001/sw/rdb2rdf/}}).
+Represented as RDF, these and possibly other types of structured data also capture information about real-world objects in terms of entities and their relations.
+Hence, especially after their conversion to RDF, structured data are often synonymously referred to as semantic data.
+To capture this general notion of semantic data used in semantic search systems, we introduce the following definition:
 
-\begin{definition}[Semantic Data] 
-Semantic data can be conceived as a graph, where nodes represent \emph{entities} and their \emph{attribute values}, and edges stand for \emph{attributes} of entities or \emph{relations} between entities.
+\begin{definition}
+\emph{Semantic data} can be conceived as a graph, where nodes represent \emph{entities} and their \emph{attribute values}, and edges stand for \emph{attributes} of entities or \emph{relations} between entities.
 \end{definition}
 
-Besides the various RDF datasets that exist on the Web, such as the hundreds of heterogeneous sources that have been made available as Linked Data~\footnote{\url{http://linkeddata.org/}}, Wikipedia can be as an extreme example that lies at one end of the spectrum of semantic data.
+In particular, this notion accommodates three main types of semantic data currently used in semantic search systems, namely (1) text-rich entity descriptions contained in structured document collections, (2) structured entity descriptions in RDF and (3) formal logic-based entity descriptions specified using expressive knowledge representation languages such as OWL.
+
+\textbf{Text-Rich Entity Descriptions:} This category of semantic data contains entities that are largely described through text, i.e.
+entity attribute values are composed of lengthy textual descriptions.
+Wikipedia is the most popular example that lies at this end of the spectrum of semantic data.
 While it is actually a collection of documents (i.e.
@@
 Wikipedia as a source of semantics is particularly popular for search systems that focus on expert search or entity search in general.
-It is used either to directly answer entity search queries, or as background knowledge~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/cikm/BronBR10}.
+It is used either to directly answer entity search queries or as background knowledge~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/cikm/BronBR10}.
 
-On the other end of the spectrum, there are more formal views on what constitute semantic data.
+\textbf{Structured Entity Descriptions:} This type of semantic data is ubiquitous on the Web, capturing information about real-world objects as RDF resource descriptions (or structured entity descriptions that can be directly converted to RDF).
+Through industry efforts such as Yahoo's SearchMonkey, Google's Rich Snippets and Facebook Like\footnote{\url{http://developers.facebook.com/docs/reference/plugins/like/}}, a large amount of RDF descriptions of resources such as restaurants and movies have been embedded into existing Web pages as RDFa.
+Besides, hundreds of large-scale RDF datasets have been made available on the Web.
+Started with the Linking Open Data, more and more data are made freely available on the Web and linked with other public datasets.
+Not only Web content providers but many companies, public institutions and national governments (US, UK etc.) are now actively publishing and linking RDF data on the Web (called Linked Data).
+Availably datasets can be subdivided into broad/domain-independent ones such as as DBpedia and Freebase\footnote{\url{http://www.freebase.com/}} or deep/domain-specific ones.
+Large domains covered by Linked Data today include government, health care, entertainment and geography.
+
+\textbf{Formal Entity Descriptions:} On the other end of the spectrum, there are more formal views on what constitutes semantic data.
 In particular, many researchers may argue that the reason why RDF, and other data models that are built upon a formal model of semantics, are actually called semantic data (instead of structured data) is because they can be exploited by a reasoning engine to infer new knowledge (i.e.
 the knowledge that is entailed by the semantics).
-While the formal model of semantics specified for RDF is relatively simple (consists of a few inference rules), semantic data used in existing search systems have also been represented using more expressive knowledge representation languages such as OWL and F-logic.
-For instance, Serene~\cite{DBLP:journals/ws/FazzingaGGL11} makes use of facts that are captured as Abox assertions of an OWL ontology, while ORAKEL~\cite{DBLP:journals/dke/CimianoHHMS08} search over an F-logic knowledge base.
-However, while the use of formal semantics and reasoning has been investigated, they play only a limited role in existing systems.
+While the formal model of semantics specified for RDF is relatively simple (consists only of a few inference rules), semantic data in some existing search systems are represented using more expressive knowledge representation languages such as OWL and F-logic~\cite{DBLP:conf/sigmod/KiferL89} (basically, a combination of logic and object-oriented frame-based languages).
+For instance, Serene~\cite{DBLP:journals/ws/FazzingaGGL11} makes use of facts that are captured as Abox assertions (i.e.
+instance data, as opposed to Tbox, the schema part) of an OWL ontology.
+ORAKEL~\cite{DBLP:journals/dke/CimianoHHMS08} searches over an F-logic knowledge base.
+However, while the use of formal semantics and reasoning has been investigated for some scenarios, it plays only a limited role in existing systems.
 The
 majority of approaches does not rely on reasoning.
-It seems that the research focus still lies in correctly understanding the ambiguous queries and data (namely, to interpret queries and data as elements of the semantic data model as defined above), while reasoning over semantic data is beneficial but not essential yet.
+It seems that the research focus still lies in correctly understanding the ambiguous queries and data (namely, to interpret queries and data as elements of the semantic data model as defined above), while reasoning over semantic data may be beneficial but not essential yet.
 
-Accordingly, a general notion of semantic data is employed in this work to consider all those systems, which consider the semantics of entities and relations but may not have a formal model of semantics available, or does not exploit it for search.
+To sum up, a general notion of semantic data is employed in this work to consider all those systems, which capture the semantics of information resources and real-world objects as entities and relations.
+Often, these entities and relations are specified on the account of a formal data model with well-defined semantics (e.g.
+RDF, OWL, F-Logic).
+However, such a formal model is not strictly required (e.g.
+in the case of text-rich entity descriptions) and in particular, may not be exploited for reasoning.
 
@@
 		\includegraphics[width=0.5\textwidth]{figs/matching.pdf}
+	\caption{Examples for semantic data, queries and matching techniques.}
 	\label{fig:matching}
-	\caption{Examples for semantic data, queries and matching techniques.}
 \end{figure}
 
-\subsection{Raw Data and Semantic Metadata} There are engines directly operating on semantic data to provide direct answers (data retrieval systems).
-These are mainly systems, which provide search interfaces over structured databases that have been converted to semantic data graphs~\cite{DBLP:conf/sigmod/LiJLF09,DBLP:conf/sigmod/LiOFWZ08}, or RDF data and ontologies crawled from the Semantic web~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TranWH09,DBLP:journals/ws/HoganHUKPD11}.
-Besides them, there are also semantic search systems supporting the retrieval of documents or media objects in general.
+There are engines operating directly on semantic data to provide direct answers (data retrieval systems).
+These are mainly systems, which provide search interfaces over RDF data and ontologies crawled from the Semantic web~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TranWH09,DBLP:journals/ws/HoganHUKPD11}, or structured databases that have been converted to semantic data graphs~\cite{DBLP:conf/sigmod/LiJLF09,DBLP:conf/sigmod/LiOFWZ08}.
+Besides them, there are also semantic search systems supporting the retrieval of documents or information objects in general.
 They employ semantic metadata, often in combination with the raw data representation of these objects.
+
+\subsection{Semantic Metadata}
 Basically, semantic metadata is semantic data that captures information about the objects to be retrieved.
-Because it is clear from the context, these terms are often used synonymously (in this work).
-Metadata includes basic information about the objects such as \verb+author+ and \verb+year+.
-One main challenge in semantic search is to interpret the semantics behind the content captured as raw data and to represent it as semantic metadata.
-For instance, the content of a document may be recognized as referring to a \verb+meeting+ with the two \verb+researcher+s \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participant+s.
+Because it is clear from the context, these two terms are often used synonymously (in this work).
+Metadata include basic information about the objects such as \verb+author+ and the \verb+year+ it was published.
+Moreover, it may capture the semantics of the information contained in these objects.
+For instance, if a particular Web page is about a restaurant, its metadata may contain a structured description of that restaurant (as RDFa) corresponding to the text contained in the page.
+In fact, one main challenge in semantic search is to interpret the semantics behind the content of information objects and to represent it as semantic metadata.
+Not only entities may be recognized but for instance, the content of a document may be interpreted as referring to a \verb+meeting+ with the two \verb+researchers+ \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participants+.
 Semantic metadata representing the content may also be manually produced and embedded into the objects.
@@
 SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages.
-Note that while we discussed how to conceive Wikipedia as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).
+Complementary to this,  schema.org\footnote{\url{http://schema.org/}} is an initiative promoted by major Web search companies (Google, Microsoft, Yahoo!) aiming at the provision of a common vocabulary that can be used by site owners to capture their data.
+In this regard, we note that while Wikipedia can be conceived as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).
 
@@
 Search over raw data can also be seen as a fall-back solution for cases where metadata cannot completely satisfy the information need.
-There exists also proposals for ontology-based IR, which completely rely on metadata~\cite{tran2007expressive}.
-In this case the retrieval of documents is formulated as a data retrieval task, where data about the documents (metadata) is returned as a direct answer.
+There exist also 	proposals for ontology-based IR, which completely rely on metadata~\cite{tran2007expressive}.
+In this case, the retrieval of documents is formulated as a data retrieval task, where data about the documents (metadata) are returned as direct answers.
 
-\section{Semantics \& Semantic Models}
+\section{Semantics: Semantic Data and Semantic Models}\label{sec:semantics}
 \begin{figure}[thb]
@@
 		\includegraphics[width=0.5\textwidth]{figs/semantic_layer.pdf}
+	\caption{Words, concepts and entities.}
 	\label{fig:semantic_layer}
-	\caption{Words, concepts and entities.}
 \end{figure}
@@
 As discussed, central to semantic search system is the use of semantics.
-A main source of semantics is the semantic data itself.
-This semantics of entities is illustrated in the top right corner of Fig.~\ref{fig:semantic_layer}.
-Additionally, this figure also shows additional sources of semantics as well as their use in the semantic search context, namely to understand words in terms of concepts and entities.
-Broadly, \emph{lexical models}, which capture semantics at the level of words in terms of \emph{concepts}, can be distinguished from \emph{knowledge models}, which capture real-world knowledge in terms of \emph{entities}, \emph{classes}, \emph{relations}, and \emph{attributes}.
+The color highlighting (gray) in Fig.~\ref{fig:semsearch_detailed} indicates that a main source of semantics is the \emph{semantic data} itself.
+That is, semantic data can be used directly to answer queries (i.e.
+by matching queries against semantic data), or as a semantic resource to interpret raw data and queries (as we shall see in more detail in subsequent sections).
+More specifically, Fig.~\ref{fig:semantic_layer} shows that in the textual raw data context, these semantics can be used to interpret words in terms of entities and relations.
+It also shows the other sources of semantics called semantic models.
+Broadly, \emph{lexical models}, which capture semantics at the level of words in terms of concepts, can be distinguished from \emph{knowledge models}, which capture real-world knowledge in terms of entity classes, relations, and attributes.
+
+We have discussed semantic data as one source of semantics in the previous section.
+In this section, we provide an overview of the semantic models used by current systems, and subsequently, present a notion of semantics that combines the instance-level semantics captured by the data and the schema-level (conceptual) semantics captured by the semantic models.
 
@@
 Different models, which vary in the degree of formality and expressiveness have been used by different communities for semantic search.
-The model used in ORAKEL for NL question answering for instance is captured by the TBox portion of an ontology and consists of classes (also called concepts) that are ordered in a subsumption hierarchy and are connected through relations.
+For instance, the model used by ORAKEL for NL question answering is captured by the Tbox portion of an ontology and consists of classes (also called concepts) that are ordered in a subsumption hierarchy and are connected through relations.
 Range and domain information are captured as restrictions on the relations.
-As shown for Serene~\cite{DBLP:journals/ws/FazzingaGGL11}, more complex expressions can be added to capture the semantics of concepts to reflect either general knowledge (such as the knowledge encoded in Wikipedia)
+As shown for Serene~\cite{DBLP:journals/ws/FazzingaGGL11}, expressions more complex than these restrictions can be added to capture the semantics of concepts to reflect either general knowledge (such as the knowledge encoded in Wikipedia)
 or specific knowledge of a domain.
-Because the ontology models used in these systems are represented using the logic-based formalisms F-Logic or OWL (description logic), they can be seen as \emph{logical theories} with well-defined formal semantics.
+Because the ontology models used in these systems are represented using the logic-based formalisms F-logic or OWL (description logic, DL), they can be seen as \emph{logical theories} with well-defined formal semantics.
 
@@
 CGs combine the intuitiveness of graph-based languages and the formal foundation of logics, enabling the modeling of knowledge in terms of concepts and their relations and its mapping to different formal languages.
-Corese~\cite{DBLP:conf/ecai/CorbyDF04} uses CGs as an internal model (to take advantage of previous work on CGs in the KR community), which however, is translated to RDFS to conform with this more commonly used standard language for representing RDF schemas.
+Corese~\cite{DBLP:conf/ecai/CorbyDF04} uses CGs as an internal model (to take advantage of previous work on CGs in the KR community), which however, are then translated to RDFS to conform with this more commonly used standard language for representing RDF schemas.
 
 Closer to the end of linguistic models discussed next are knowledge models that consist of concepts only.
-For instance, C-Search encodes knowledge as concepts expressed in propositional description logic (DL).
-This DL does not feature the representation of relations (also called roles) but the specification of complex concepts as a conjunction or disjunction of atomic concepts.
+For instance, C-Search~\cite{DBLP:conf/esws/GiunchigliaKZ09} encodes knowledge as concepts expressed in propositional DL.
+This DL enables the representation of complex concepts as a conjunction or disjunction of atomic concepts.
+However, it does not support relations.
+% (also called roles) but the specification
 
 \subsection{Lexical Models} The use of concepts has already been investigated in the early years of IR research~\cite{DBLP:conf/sigir/Giger88}.
-Different to knowledge models, which capture semantics in terms of real-world entities and their relations, the models employed there are lexical in that they capture semantics at the level of words.
+Different to knowledge models, which capture semantics in terms of real-world entities and their relations, the models employed there are lexical in the sense that they capture semantics at the level of words.
 While concepts in knowledge models stand for classes of real-world entities, concepts in lexical models correspond to \emph{senses of words}.
-The latter are more general such that they may refer to entities, classes, relations, attributes, or other senses of words.
-While these different ``types'' of senses are not explicitly distinguished, concepts are organized along lexical relationships in a lexical model.
+Lexical concepts are more general such that they may refer to entities, classes, relations, attributes, or other senses of words.
+While these different ``types'' of senses are not explicitly distinguished like in a knowledge model, concepts can be organized along lexical relationships in a lexical model.
 
-\emph{Thesaurus} (often, \emph{lexicon} is also used as synonym) is a popular lexical model that has been extensively used for document retrieval in IR, which basically, groups words together according to their semantic similarity.
+\emph{Thesaurus} 
+%(often, \emph{lexicon} is also used as synonym) 
+is a popular lexical model that has been extensively used for document retrieval in IR, which basically, groups words together according to their semantic similarity.
 Each group represents a different word sense.
@@
 \subsection{Semantics} 
-Based on the above discussion, we derive a general notion of semantics that is used to characterize the different types of semantic search systems.
+Based on the above discussion, we introduce a general notion of semantics that can be used to characterize the different types of semantic search systems.
 
-\begin{definition}[Semantics] 
-The semantics of queries and data are captured by semantic search systems in different ways.
+\begin{definition} The \emph{semantics} of queries and data are captured by semantic search systems in different ways.
 Semantics can be represented (1) as word senses that are organized through lexical relations between words (\emph{lexical model}), (2) as specific knowledge about concrete entities, i.e.
-specific attribute values and individual relations between entities (\emph{semantic data}) or (3) as general knowledge about classes of entities, their attributes, and relations between classes (\emph{knowledge model}).
+specific attribute values and relations between entities (\emph{semantic data}) or (3) as general knowledge about classes of entities, class attributes, and relations between classes (\emph{knowledge model}).
 \end{definition}
@@
 A prominent example that can be used to illustrate these many aspects of semantics is Wikipedia.
-As discussed, it has been used as semantic data to answer entity search queries, and converted to a semantic dataset called DBpedia.
+As discussed, it has been used as semantic data to answer entity search queries, and converted to a semantic dataset called DBpedia~\cite{DBLP:journals/ws/BizerLKABCH09}.
 The Wikipedia categories of pages have been treated as classes and used to construct hierarchies of classes in an ontology called YAGO~\cite{DBLP:conf/www/SuchanekKW07}.
-Wikipedia is also used as a source for Explicit Semantic Analysis (ESA), where every Wikipedia page is regarded as a concept.
-Because ESA does not distinguish entities and classes, the concepts here can be seen as word senses.
+Wikipedia is also used as a source for Explicit Semantic Analysis (ESA)~\cite{DBLP:journals/tois/EgoziMG11}, where every Wikipedia page is regarded as a concept.
+Because ESA does not distinguish entities from classes, the concepts here can be seen as capturing word senses.
 Thus, Wikipedia pages and links constitute a lexical model in this context.
@@
 
-The discussion of semantics so far focuses on entities and simply (binary) relations between them.
+The discussion of semantics so far focuses on entities and simple (binary) relations between them.
 Yet, the kind of semantics that can be expressed is only limited by the knowledge representation (KR) languages.
-There exist very powerful KR formalisms and many of them have been incorporated to perform document retrieval (already in the early years of IR~\cite{DBLP:conf/sigir/Rijsbergen89}) and to represent complex queries and knowledge used in NL question answering~\cite{DBLP:journals/tkde/VassiliadisTK94}(in the early years of expert systems).
+There exist very powerful KR formalisms and many of them have been incorporated to perform document retrieval (already in the early years of IR~\cite{DBLP:conf/sigir/Rijsbergen89}) and to represent complex queries and knowledge used in NL question answering~\cite{DBLP:journals/tkde/VassiliadisTK94} (in the early years of expert systems).
 For instance, the employed formalisms have been used to represent temporal or fuzzy aspects of world knowledge.
-However, there are practical reasons why the focus of current research (and this paper) is set on simple descriptions of entities.
-On the hand, most queries on the Web seem to ask about entities and their relations.
-That is, most common queries as well as a large part of queries in the long tail (of Web query logs) are about entities and their relations (i.e., they are of the types entity, factual or relational queries).
+However, there are practical reasons why the focus of current research (and this paper) is set on simple descriptions of entities (via attribute and binary relations).
+On the one hand,
+%most queries on the Web ask about entities and their relations. That is, 
+most common queries as well as a large part of queries in the long tail of Web query logs 
+%can be addressed using semantics about 
+are about entities and relations (i.e.
+they are of the types entity, factual or relational queries).
 More importantly, the bottleneck is actually the availability of data.
@@
 Also, most of the data residing in databases nowadays are mainly about entities and their relations.
-\dtr{maybe also discuss the difference to XML retrieval, which merely use structure information for ``focused'' retrieval: retrieve components of the structured XML documents that match the query}
 
-\section{Interpretation}
+%\dtr{maybe also discuss the difference to XML retrieval, which merely use structure information for ``focused'' retrieval: retrieve components of the structured XML documents that match the query: The focus on the semantics of entities and relations also marks the boundary between semantic search and XML document retrieval.
+}
 
-\subsection{Content Interpretation}
+%\section{Interpretation}
+\begin{figure*}[htb]
+	\centering
+  \subfloat[Detecting concepts.]{\label{fig:detecting_concepts}\includegraphics[width=0.34\textwidth]{figs/conceptextraction}}
+  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc. (or a blank line to force the subfig onto a new line)
+  \subfloat[Detecting entities and relations.]{\label{fig:detecting_data}\includegraphics[width=0.6\textwidth]{figs/dataextraction}}
+  \caption{Detecting concepts, entities and relations.}
+  \label{fig:extraction}
+\end{figure*}
+
+\section{Content Interpretation}\label{sec:content}
 
@@
 as semantic data or elements of a semantic model.
-For this, different tools for Natural Language Processing (NLP) have been employed.
+In fact, there is a dedicated area of research focusing on this problem of knowledge extraction from text.
+Problems that have been studied include named entity recognition, semantic role labeling and relation extraction.
+For an overview of solutions proposed in this area, we refer the interested readers to surveys specifically focused on this problem~\cite{DBLP:journals/tkde/ChangKGS06}.
+Here, we discuss the kind of knowledge extraction that has been performed for the purpose of semantic search.
 
-\emph{Detecting Concepts:} Documents have been analyzed to extract concepts for the task of modeling documents as conceptual graphs~\cite{DBLP:conf/iccs/ComparotHH07}.
-For C-Search~\cite{DBLP:conf/esws/GiunchigliaKZ09}, which represent documents as DL concepts corresponding to WordNet senses, the authors identify words in documents matching senses, and uses POS tagging information and lexical database to perform word sense disambiguation.
+\subsection{Detecting Concepts in Text} This problem and the tasks carried out to solve it are illustrated in Fig.~\ref{fig:detecting_concepts}.
+Concepts are especially needed for supporting what is known as concept-based IR.
+
+Documents have been analyzed to extract concepts for the task of modeling documents as conceptual graphs~\cite{DBLP:conf/iccs/ComparotHH07}.
+For C-Search~\cite{DBLP:conf/esws/GiunchigliaKZ09}, which represent documents as DL concepts corresponding to WordNet senses, the authors identify words in documents matching Wordnet senses (i.e.
+direct matching), and uses part-of-speech (POS) tagging information and Wordnet, as lexical database of senses and word-level relationships, to perform word sense disambiguation.
 While words are mapped to atomic concepts, phrases are represented as complex concepts using DL formulas~\cite{DBLP:conf/esws/GiunchigliaKZ09}.
@@
 For instance, the Unified Medical Language System and a gene-thesaurus have been used to identify multi-word terms and to map synonymous words to one concept~\cite{DBLP:conf/trec/TrieschniggKS06}.
-The concepts were identified simply by by comparing document words to thesaurus terms.
+The concepts were identified simply by matching document words to thesaurus terms.
 
-\emph{Detecting Entities \& Relations}: For extracting entities and relations, the large body of research work on named entity recognition and data extraction has been leveraged by existing semantic search solutions.
-One of the platform, which is most frequently used by semantic search systems for extracting semantic data and
+\subsection{Detecting Entities \& Relations in Text} For extracting entities and relations, the large body of research work on named entity recognition and relation extraction has been leveraged by existing semantic search solutions.
+One of the platforms, which is frequently used by semantic search systems for extracting semantic data and
 automatically annotating document collections at a large scale is KIM~\cite{KIM DBLP:journals/ws/KiryakovPTMO04}.
 IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} makes use of UIMA, a framework of annotators that can be configured in a pipeline to analyze and extract data from text.
-There is a another work from IBM, which focuses on extracting named entities and relations from text and using them for more precise search~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}.
-Also for this task, lexical resources, particularly Gazetteers, is frequently used.
+There is a another work from IBM, which focuses on extracting named entities and relations from text and using them for more precise search (employing XML fragments as queries~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}).
+
+An overview of tasks involved in detecting entities and relations are shown in Fig.~\ref{fig:detecting_data}.
+As for most text interpretation tasks, a syntactic analysis of the text is needed.
+In this case, the typical analysis includes tokenization, POS tagging, chunking sentences into noun phrases, and some data extraction systems even derive entire parse trees from the text.
+Besides the syntactic information derived from text analysis, different semantic resources are used.
+In particular, Gazetteers are frequently used, which can be seen as a lexical model.
+The simplest way for detecting entities is simply to match words (tokens) against Gazetteer's entries representing entities of different classes.
 For disambiguating named entities mentions in text, it has been shown that semantic data about entities and their relations provides valuable information~\cite{DBLP:conf/esws/KlebA10}.
 The technique behind this is based on graph traversal, which starts from nodes matching the entity mentions.
-Controlled through spreading activation, path from these nodes are traversed to explore the semantic context of these nodes (i.e.
+Controlled through spreading activation, paths from these nodes are then traversed to explore the semantic context of these nodes (i.e.
 entities).
 These contextual interpretations are then used for disambiguation.
-A special case of understand
+This resembles the general technique called collective matching, which applied to this case, assumes entity mentions (words) to form a context.
+We have a higher a confidence that a word matches an entity $e$, when other words in this context, match entities related to $e$, i.e.
+the context formed by $e$ and its related entities corresponds to the word context.
 
-\subsection{Query Interpretation} 
-	Essentially, interpreting queries is similar to the task of understanding text in documents. The difference is that instead besides NL text, also keywords may be provided as inputs.
+Beyond direct matching and disambiguation, state-of-the-art techniques employ complex matching rules (or matching patterns in general), especially for the more complex task of relation extraction.
+Given a pattern like \verb+Mr.
+?
+works for ?+, matching texts can be identified and relevant entities and relations can be extracted.
+Matching patterns are specified manually or learned automatically through machine learning techniques for pattern induction.
+Current state-of-the-art data extraction programs in fact, not only use simple word patterns, but complex combination of features derived from the words (e.g.
+orthographic features such as whether the word contain digits or hyphens, word types such as lowercased and capitalized and syntactic features such as POS information), from the context (i.e.
+words in a text window along with their tags, labels etc.) as well as from background knowledge (e.g.
+from Gazetteers).
+These features along with labeled training examples are then used to train a classifier (one for every entity / relation type) or a probabilistic sequence model such as the Conditional Random Field~\cite{DBLP:conf/icml/ZhuNWZM05}.
+Besides these learning methods proposed for targeted information extraction, which assume a fixed set of predefined types of entities / relations to be extracted, there are also proposals for open information extraction~\cite{DBLP:conf/ijcai/EtzioniFCSM11}.
+So far, semantic search systems focus on the use of targeted information extraction tools (e.g.
+IBM's UIMA, SOFIE~\cite{DBLP:conf/www/SuchanekSW09}).
+While they provide lower coverage, the quality of extracted outputs is higher compared to open extraction tools, an aspect shown to be very influential in improving the precision of semantic search results~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}.
+Promising is the combined usage of targeted and open information extraction, a direction currently pursuit by Microsoft's EntityCube.
 
-\emph{Translating NL Queries:} Names entities, their types and relations between them are identified from NL questions~\cite{DBLP:conf/aswc/CaoCT08} and used to construct a semantic representation of the information need, i.e.
-a \emph{structure/semantic query}.
-Analogous to structured/semantic data, there is no clear distinction between a structured query and a semantic query (and thus, the corresponding terms are also used as synonyms).
-Basically, they capture the information need in terms of entities, their relations and variables that represent existential quantifiers or the pieces of information to be retrieved.
-While the common language used to query RDF is SPARQL, other (logic-based) formalisms have been used.
-Besides conceptual graphs~\cite{DBLP:conf/aswc/CaoCT08}, recognized entities, types and relations are also represented as logical formulas~\cite{DBLP:journals/dke/CimianoHHMS08}, XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} or SPARQL queries~\cite{DBLP:conf/esws/DamljanovicAC10}.
-For processing NL questions, the same NLP tools used for content interpretation have been applied.
-For instance, the Stanford Parser~\footnote{\url{http://nlp.stanford.edu/software/lex-parser.shtml}} and GATE~\footnote{\url{http://gate.ac.uk/}} are used by FREyA~\cite{DBLP:conf/esws/DamljanovicAC10} to obtain the syntactic parse tree and to identify concepts in NL questions, respectively.
-Besides the semantic data or additional semantic models such as a domain ontology, lexicons specifying the mappings between syntactic elements,
-such as verbs or nouns with their arguments identified by the parser, and concepts and relations in the semantic models, have been used for NL question answering~\cite{DBLP:journals/dke/CimianoHHMS08}.
-This is to deal with the fact that these semantic elements have many lexical variants.
-These mappings are specified by lexicon engineers.
-Such a lexicon is especially needed for porting the NL interface from one domain to one other.
-Aiming at reducing this upfront customization effort and domain independence, there are also systems that in the case of lexical ambiguities, ask users to provide mappings, and use them to train models (e.g.
-via reinforcement learning~\cite{DBLP:conf/esws/DamljanovicAC10}) that automatically compute mappings.
-While it has been reported~\cite{DBLP:journals/ws/LopezUMP07} that domain customization usually improves recall, many NL-based semantic search systems exploit general domain-independent lexical resources (e.g.
-WordNet is used by AquaLog~\cite{DBLP:journals/ws/LopezUMP07}) but do not require domain-specific lexicons.
+Many patterns and particularly rules used for extraction explicitly capture when candidates can be considered as matches, i.e.
+when they are considered as belonging to some types of entities or relations.
+These patterns can be seen as sources of semantics that feed as inputs to the extraction systems.
+Besides these matching-specific knowledge, also general as well as domain-specific knowledge stored in ontologies have been used as semantic constraints to filter matches, i.e.
+those that lead to semantic inconsistencies.
+For instance, SOFIE~\cite{DBLP:conf/www/SuchanekSW09} prunes extraction outputs that do not satisfy the semantic constraints captured by YAGO.
+As an example, having the pattern \verb+ ?x is mayor of ?y+ and the knowledge that \verb+ x, mayorOf, y+ requires \verb+ x, type, Person+ and \verb+ y, type, City+, we can filter out those extracted \verb+is mayor of+ relations that do not involve a person or a city.
 
-	\emph{Detecting Concepts in Keyword Queries:} One of the main challenge in dealing with keywords in queries or NL words in general is their semantic ambiguity.
+\section{Query Interpretation}\label{sec:query} 
+	Essentially, interpreting queries is similar to the task of understanding text in documents.
+However, these problems are studied from different viewpoints by overlapping but not same communities of researchers.
+Thus, the emphases are put on different subproblems.
+Further, besides NL text, also keywords may be provided as inputs to query interpretation.
+Keywords are different from NL text in the amount of syntactic features that can be obtained.
+
+\subsection{Detecting Concepts in Keyword Queries} One of the main challenge in dealing with keywords in queries (and words in NL text) is their semantic ambiguity.
 The same meaning can be expressed in different ways.
@@
 terms overlap or are related in meaning).
-The use of thesaurus (also called lexicon) to deal with semantic ambiguities of words has long history and has been investigated as the problem of concept-based IR~\cite{DBLP:conf/sigir/Giger88}.
+
+Compared to detecting concepts in text as illustrated in Fig.~\ref{fig:detecting_concepts}, solutions to the problem of detecting concepts in queries are different in the usage of features: Keywords are also matched and disambiguated against a thesaurus.
+However, there is no syntactic information such as POS tags that can be exploited.
+
+The use of thesauri to deal with semantic ambiguities of words has long history and has been investigated as the problem of concept-based IR~\cite{DBLP:conf/sigir/Giger88}.
 Concept-based IR is especially needed in the biomedical domain due to the frequent presence of acronyms, homonyms and synonyms.
@@
 The detected concepts are used to expand the query~\cite{DBLP:conf/sigir/QiuF93,DBLP:conf/trec/JelierSEWMSMK03}.
-Concept-based query expansion \cite{DBLP:conf/sigir/QiuF93} for instance, detect the concept behind the query, and perform selection and weighting of additional search terms directly based on this concept (instead of the query terms).
-This and other works in this era, were based on the use of thesauri that capture concepts and relationships.
+Concept-based query expansion \cite{DBLP:conf/sigir/QiuF93} for instance, detects the concept behind the query, and performs selection and weighting of additional search terms directly based on this concept (instead of the query terms).
+This and other works in this area, were based on the use of thesauri that capture concepts and relationships.
 WordNet for instance, was use to represent concepts by WordNet synonym sets, and for expanding query terms by following WordNet links \cite{DBLP:conf/sigir/Voorhees93}.
-WordNet links (is-a in particular) was also used to disambiguate query terms and to choose their senses \cite{DBLP:conf/sigir/Voorhees94}.
+WordNet links (is-a in particular) were also used to disambiguate query terms and to choose their senses \cite{DBLP:conf/sigir/Voorhees94}.
+
 Recently, a technique based on the idea of relevance model has been proposed to recognize the concepts underlying the query, referred to as conceptual query modeling~\cite{DBLP:journals/ipm/MeijTRK10}.
-Instead of detecting the concepts based on a thesauri, this approach retrieves the top pseudo-relevance feedback documents through an initial query run.
+Instead of detecting the concepts based on a thesaurus, this approach retrieves the top pseudo-relevance feedback documents through an initial query run.
 Concept annotations associated with these documents are then used to construct the conceptual representation of the relevance model (the query).
-While OntoSearch~\cite{DBLP:conf/aaai/JiangT06} does not explicitly the query and the underlying relevance, it follows a similar idea.
-Concepts captured by ontologies (seen as network of concepts) are used here.
-First, OntoSearch obtains a set of documents for the given query, then uses the concepts associated with these documents as the seeds to the semantic network.
-Through spreading activation, concepts that are semantically related to this initial concept set are inferred, and used to re-rank the documents.
+While OntoSearch~\cite{DBLP:conf/aaai/JiangT06} does not explicitly target the approximation of a relevance model, it follows a similar idea.
+Concepts captured by ontologies (seen as a semantic network of concepts) are used here.
+First, OntoSearch obtains a set of documents for the given query, and then uses the concepts associated with these documents as seeds to the semantic network.
+Through spreading activation, concepts that are semantically related to this seeds are inferred, and used to re-rank the documents.
 
-\emph{Translating Keyword Queries:} Instead of concept-based query expansion or aiming at a conceptual representation, there are also proposals for mapping keyword queries to fully structured queries.
-Entities and relations in the semantic data that are mentioned in the queries are identified and represented as XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
-AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} is another system, which supports this kind of keyword query interpretation.
+\subsection{Translating Keyword Queries} 
+%Instead of detecting concepts only, 
+%concept-based query expansion or aiming at a conceptual representation, 
+There are also proposals for mapping keyword queries to fully structured queries.
+In this case, not only concepts but also the entities and relations to which the query keywords may refer to, have to be recognized.
+The resulting semantics of query keywords, i.e.
+schema (concept and relation names) and data elements (entities) provides the basis for identifying the query intents, i.e.
+the keyword query interpretations.
+The assumption behind many approaches for query interpretation is that the intended query corresponds to a particular substructure in the semantic data or schema graph.
+However, relations may be not explicitly specified in the query, or are not sufficient to connect the detected entities and concepts.
+In this case, algorithms for graph traversal are used to find connecting paths.
+Query interpretations are then obtained by merging these paths, which are finally ranked and mapped to structured queries (i.e.
+concept, relation and entity names are mapped to query predicates and constants).
+While the common language used to query semantic data in RDF is SPARQL\footnote{\url{http://www.w3.org/TR/rdf-sparql-query/}} (basically, a language for expressing graph patterns), other (logic-based) formalisms have been used, i.e.
+recognized entities, classes and relations can be mapped to SPARQL queries~\cite{DBLP:conf/esws/DamljanovicAC10},
+conceptual graphs~\cite{DBLP:conf/aswc/CaoCT08}, logical formulas~\cite{DBLP:journals/dke/CimianoHHMS08} or XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
+An overview of this task is illustrated in Fig.~\ref{fig:inter_keywords}
+
+%For instance, entities and relations in the semantic data that are mentioned in the queries are identified and represented as XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}. 
+AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} is an example of systems supporting this kind of keyword query interpretation.
 It maintains a translation index, which can be conceived as a lexicon that returns all meanings for an individual keyword.
@@
 For RDF data, a top-k graph traversal algorithm has been proposed to efficiently compute all possible interpretations~\cite{DBLP:conf/icde/TranWRC09}.
-Here, keywords are interpreted as entities, classes or relations (called keyword matching elements), which are captured by the semantic data or the underlying semantic model.
-All possible paths between these keyword matching elements are computed online by traversing a combination of the semantic data graph and the schema graph (the semantic model), and combined to obtain interpretations which cover all the query keywords.
+Here, keywords are interpreted as entities, classes or relations (called keyword matching elements), which are contained in the semantic data or semantic model.
+All possible paths between these keyword matching elements are computed online by traversing a query search space that is formed by combining the semantic data graph and the schema graph, and then merged to obtain interpretations, which cover all the query keywords.
 This keyword query interpretation is implemented by Hermes~\cite{DBLP:journals/ws/TranWH09}, and later, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}.
-TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} also applies this graph traversal mechanism to interpret keywords not as possible queries (i.e.
-as information needs) but as answers.
+TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} also applies a graph traversal algorithm.
+However, it does not compute possible queries (i.e.
+interpretations) but directly output answers.
 As the user types, TASTIER completes the query with answers that possibly match the intended information need.
 
-These mentioned approaches deal with the interpretation of ambiguous queries that are expressed as NL or keywords.
-The end result is a more precise understanding of the need, represented as structured queries.
-This is also the aim of other related work that falls into the general category of query construction.
-For instance, faceted search~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/esws/HeimEZ10,DBLP:conf/semweb/FerreH11} or the other kind of iterative query interfaces based on visual manipulation (drag and drop)~\cite{DBLP:journals/ws/Harth10} as mentioned before, also belong to this general category.
-In these interfaces, every user operation is directly mapped to a query construct.
+\begin{figure*}[htb]
+	\centering
+  \subfloat[Translating keyword queries.]{\label{fig:inter_keywords}\includegraphics[width=0.34\textwidth]{figs/keywordinterpretation}}
+  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc. (or a blank line to force the subfig onto a new line)
+  \subfloat[Translating NL queries.]{\label{fig:inter_NL}\includegraphics[width=0.6\textwidth]{figs/nlinterpretation}}
+ \caption{Translating keywords and NL queries.}
+ \label{fig:translation}
+\end{figure*}
+
+\subsection{Translating NL Queries} There are two main categories of approaches for dealing with this problem.
+One the one hand, it can be tackled in a way similar to the translation of keyword queries.
+This solution (depicted in the bottom left portion of Fig.~\ref{fig:inter_NL}) involves the detection of concepts, entities, and relations~\cite{DBLP:conf/aswc/CaoCT08}, and their mapping to elements of structured queries.
+The problem of ambiguity is solved here by using robust techniques for the matching of words in the NL query against elements in the semantic data and semantic models, and for the ranking and disambiguation of resulting matches.
+In fact, this kind of approaches is particularly popular among domain-independent NL query translation systems.
+AquaLog~\cite{DBLP:journals/ws/LopezUMP07}) for instance, maps words in NL queries to elements in the semantic data, and disambiguates results using domain-independent lexical resources (e.g.
+WordNet).
+
+As depicted in Fig.~\ref{fig:inter_NL}, the other category of approaches involves the use of lexicons, often in combination with a syntactic analysis tools. 
+%Because NL questions also provide syntactic features, 
+In fact, the same text analysis tools used for content interpretation can be applied here.
+For instance, the Stanford Parser~\footnote{\url{http://nlp.stanford.edu/software/lex-parser.shtml}} and GATE~\footnote{\url{http://gate.ac.uk/}} are used by FREyA~\cite{DBLP:conf/esws/DamljanovicAC10} to identify concepts in NL questions and to derive the syntactic parse tree, respectively.
+The use of domain-specific lexicons provide is a common way to deal with ambiguities, especially for traditional NL translation systems that are focused on a particular domain.
+Basically, a lexicon captures the mappings from syntactic elements to semantic elements.
+For instance, ORAKEL uses a lexicon, which specifies the mappings between nouns (verbs) with their arguments identified through the syntactic analysis and concepts (relations) in the semantic models~\cite{DBLP:journals/dke/CimianoHHMS08}.
+These mappings are specified by lexicon engineers.
+A different lexicon is needed when porting the NL interface from one domain to one other.
+Aiming at reducing this upfront customization effort and domain independence, there are also systems that in the case of lexical ambiguities, ask users to provide mappings, and use them to train models (e.g.
+via reinforcement learning~\cite{DBLP:conf/esws/DamljanovicAC10}) that automatically compute mappings.
+
+%Instead of performing the syntactic parsing separately from the mapping of syntactic elements to semantic elements, these two steps have been also  in one pass, called semantic parsing.
+
+%While it has been reported~\cite{DBLP:journals/ws/LopezUMP07} that domain customization usually improves recall, many NL-based semantic search systems exploit general domain-independent lexical resources (e.g.
+WordNet is used by AquaLog~\cite{DBLP:journals/ws/LopezUMP07}) but do not require domain-specific lexicons.
+
+\subsection{Iterative Query Construction}
+
+The discussed query interpretation approaches 
+%deal with the interpretation of ambiguous queries that are expressed as NL or keywords. The 
+aim at a more precise understanding of the information need, represented as a structured query.
+This is also the objective of other related approaches that fall into the general category of query construction.
+For instance, faceted search~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/esws/HeimEZ10,DBLP:conf/semweb/FerreH11} as well as the other kind of iterative query interfaces based on visual manipulation (drag and drop)~\cite{DBLP:journals/ws/Harth10} as presented before, also belong to this general category.
+In these systems, user operations are directly mapped to changes in the query.
 For instance, adding and removing facets result in the addition (query expansion) and removal (query refinement) of query predicates, respectively.
-Clearly, the difference to work on query interpretation is the lack of ambiguity, i.e.
+Clearly, the difference to work on keyword and NL query interpretation is the lack of ambiguity, i.e.
 the semantics of every user input is clear.
 
-\section{Matching}
+\section{Matching}\label{sec:matching}
+% Table generated by Excel2LaTeX from sheet 'Tabelle1'
+\begin{table}[htbp]
+  \centering
+  \caption{Overview of matching approaches.}
+    \begin{tabular}{|c|c|c|}
+    \hline
+    \textbf{Term} & \textbf{Structure} & \textbf{Semantic} \bigstrut\\
+    \hline
+    \hline
+    Syntactic-based & Join  & Forward chaining \bigstrut\\
+    \hline
+    Lexicon-based & Graph traversal & Backward chaining \bigstrut\\
+    \hline
+    \end{tabular}%
+  \label{tab:addlabel}%
+\end{table}%
+
+\dtr{some systems may do interpretation, some not....}
 The differences between term matching, structure matching and graph traversal are illustrated in Fig.~\ref{fig:matching}.
@@
 
-\subsection{Structure / Semantic Matching} 
+\subsection{Matching Complete Structure Patterns (Structure Matching)} 
 	This matching is possible when the query and content are interpreted or are directly available as a structured query and semantic data, respectively.
 That is, the semantics of both the query and data is represented in terms of some entities and their relations.
-
-	\emph{Matching Complete Structure Patterns (Structure Matching):} Most frequent is the combination SPARQL queries and RDF data.
+Most frequent is the combination SPARQL queries and RDF data.
 In particular, the three common types of information needs discussed previously can be captured through the basic graph pattern (BGP) feature of SPARQL.
@@
 
-	\emph{Matching Incomplete Structure Patterns (Graph Traversal):}  While join-based evaluation is possible for structured pattern that are complete, traversing the data graph is needed when query patterns entail missing connections.
+	\subsection{Matching Incomplete Structure Patterns (Graph Traversal)}  While join-based evaluation is possible for structured pattern that are complete, traversing the data graph is needed when query patterns entail missing connections.
 That is, the query engines cannot directly combine partial results based on join variables but needs to explore for different paths between them.
@@
 Entities matching keyword(s) in the query have to be retrieved, and subgraphs containing paths, which connect these keyword matching entities have to be explored in the data through traversing graph nodes and edges.
+
 	A different semantics has been used~\cite{DBLP:conf/www/RochaSA04}, where results do not have to cover those nodes matching the query keywords.
@@
 
-	\emph{Reasoning:} The formal well-defined semantics of some semantics models such as ontologies represented in OWL, have also be exploited for matching.
+	\subsection{Reasoning} The formal well-defined semantics of some semantics models such as ontologies represented in OWL, have also be exploited for matching.
 More precisely, they are used for \emph{reasoning} to consider not only the available data but also new facts that can be automatically inferred from the formal semantics.
@@
 
-\section{Ranking}
+\section{Ranking}\label{sec:ranking}
 Ranking approaches leverage different factors, which in general, can be \emph{query-independent} or \emph{query-dependent}.
@@
 Among those heuristics, there are two prominent ones that are widely used in existing approaches, namely \emph{centrality-} and \emph{proximity-based ranking}.
+
+% Table generated by Excel2LaTeX from sheet 'Tabelle2'
+\begin{table}[htbp]
+  \centering
+  \caption{Overview of centrality-based ranking.}
+    \begin{tabular}{|p{3.5cm}|p{3.5cm}|}
+    \hline
+    Hyperlinks & Relations  \bigstrut\\
+    \hline
+    \hline
+    Adoption of PageRank to (1) ontologies as documents, (2) two-layered graph with sources (documents) representing one layer & Authority transfer weights (1) specified by experts, (2) learned through simulated annealing or PARAFAC decomposition \bigstrut\\
+    \hline
+    \end{tabular}%
+  \label{tab:addlabel}%
+\end{table}%
 
@@
 Similar to text proximity, the intuition here is that more compact results more likely correspond to the intended need.
+
+% Table generated by Excel2LaTeX from sheet 'Tabelle3'
+\begin{table}[htbp]
+  \centering
+  \caption{Overview of query-relevance based ranking.}
+    \begin{tabular}{|p{3.2cm}|p{3.8cm}|}
+    \hline
+    Content & Structure  \bigstrut\\
+    \hline
+    \hline
+    Treat entities as documents and adopt (1) Vector Space Model (2) unstructured LM & (1) BM25F, (2) structured LM, (3) edge-specific relevance model, (4) triple-based LM \bigstrut\\
+    \hline
+    \end{tabular}%
+  \label{tab:addlabel}%
+\end{table}%
 
@@
 
-\section{Main Approaches and Their Performances}	
+\section{Main Approaches and Their Performances}\label{sec:approaches}	
 Semantic search has been investigated from different communities in different context.

### 2012-04-08 trunk/tr-semanticsearchsurvey-data/intro.tex
Changes to intro

@@
 
+Modern search engines are efficient in retrieving documents (web pages in the case of web search) from large collections based on matching the text of the user's query with the textual content of the document or words in linking to the current document (\emph{anchortext}).
+These textual features are often combined with additional features that measure the popularity of results based on usage data (\emph{click-behaviour} or using metrics computed on the web graph such as \emph{PageRank} and its derivates.
+In combination, these relatively simple, but scalable matching techniques are are able to address a large fraction of common information needs.
+They work particularly well when the user is able to explicitly name the target of the query, this reference is unambiguous and refers to a popular item widely referred to with that name.
+An example is a product search, where the user enters the name of the product and that product is widely known by that name, e.g \emph{canon ixus 115}, a digital camera.
+
 \subsection{Many Unsolved Long-tail Queries}
-Modern search engines can effectively interpret the topics (semantic themes) and based on that, disambiguates the need intended in the provided query inputs.
-Combined with additional (query-independent) factors such as PageRank, they are able to address a large fraction of common information needs.
-In particular, queries that request for pages
-%about a particular topic (\emph{topical query}) or 
-representing popular entry points to commonly used information that can be reached via further browsing activities (\emph{navigational queries}), can be successfully processed.
-These queries work particularly well when the entry points represent named entities (and these named entities are mentioned in the query).
-For instance, when searching for a concrete product, current search engines are not only able to correctly return matching pages, but also meaningful summaries containing core information about that product.
-Such a query is rather \emph{unambiguous}, i.e.
-captures a unique meaning.
-However, dealing with the large number of queries in the ``long tail'' of Web query logs \cite{} remains challenging.
-Two particular categories of problematic cases are ambiguous and complex queries:
+
+While search engines have been effective in addressing common needs, most queries are still in the ``long tail'' of Web query logs.
+Baeza-Yates et al.
+report that even in a full year of query logs 88\% of the unique queries are singleton queries, i.e.
+appeared only once in the year.
+A lot of this variety comes from syntactic variations of the same popular need and can be addressed with spell-corrections and query suggestion techniques.
+However, the remaining queries tend to be less common because they refer to less popular needs that need disambiguation or require more complex explanation.
 
@@
 %	\item 
-	\textbf{Ambiguous Queries:} These queries contain ambiguous terms, resulting in many possible interpretations (several query meanings).
-For instance, the query ``young scholars from Germany'' is difficult to process because without any additional context, it is not clear who is ``young'', and different types of people may be considered as ``scholars''.
-Especially difficult are queries, which search for secondary meanings, e.g.
-``George Bush'', not the president but the beer brewer.
+	\textbf{Ambiguous Queries:} 
+	Ambiguous queries arise naturally when the user may not be able to name precisely the item that is sought.
+Coming back to the example of product search, a user who is in the early stages of selection may not know exactly which product to look for.
+In this case, the user may name one or two characteristics of the product, such as \emph{cheap digital camera}.
+The concept of digital camera covers a broad range of actual entities, and there might be some discussion as to which of these can be considered cheap.There are also systemic factors that lead to an increase in ambiguity.
+Despite the expectation that longer queries should leave to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ an AND semantics between words, and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult.
+Thus users have learned to avoid long queries, leading to shorter but more ambiguous queries.
+Lastly, users will try to find what they are looking for with the least possible words, adding additional terms after realizing that their original query was ambiguous.
+For example, when searching for people the user may type in a name, only to realize that there are multiple persons with the same name.
+Often, this is aggravated by the bias toward a single popular answer.
+For example, when searching for 'George Bush', the top results are crowded by references to the same person, even though this is a common name.
+\footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}.
 
 %	\item 
-	\textbf{Complex Queries:} this class of queries captures complex information needs, which may involve several entities and relationships between them.
-As an example, we have a query that mentions a person and a location, and asks for a relationship between that person and another location (relational queries):  ``birthplace of 32 year old computer scientist, who lives in Karlsruhe, a city in Germany''.
+	\textbf{Complex Queries:} We include in this class all queries that go beyond a reference to a single named entity, and involve several entities and relationships between them.
+These queries arise again when the user does not know the answer to a question and therefore has to describe the item sought and it's relationships to other items that he or she can name.
+For example, searching for this paper by the name of the second author is relatively straightforward.
+However, assuming the user does not know (or do not remember) the name, he or she might look for a "semantic search survey paper written by a researcher at yahoo".
+Complex queries are particularly hard to address in the traditional information retrieval paradigm when they require information extraction and aggregation, i.e.
+when not all the entities and relationships are mentioned in a single document.
+Queries for events naturally involve multiple entities, typically the participant in the event and a reference to another item, e.g.
+\emph{barrack obama birth certificate}.
 %\end{itemize}

### 2012-04-09 tr-semanticsearchsurvey-data/intro.tex

@@
 % unsolved information needs%
-Advancements in search technologies enable users to deal and to exploit the ever increasing amount of information that we can find in different scenarios -- from the personal desktop to enterprises' databases up to the large-scale Web.
-As opposed to the structured querying capabilities commonly provided by commercial databases that are only accessible by experts, \emph{search} is rather understood as a \emph{end-user oriented paradigm} that is based on \emph{intuitive interfaces} and access mechanisms.
-Solutions that are widely used especially on the Web are based on \emph{keyword search}, and in smaller-scale scenarios, also support natural language (NL) inputs.
+Advancements in search technologies enable users to deal with and to exploit the ever increasing amount of information that we can find in different settings -- from the personal desktop to enterprises' databases up to the large-scale Web.
+As opposed to the structured querying capabilities commonly provided by commercial databases that are only accessible by experts, \emph{search} is rather understood as an end-user oriented paradigm that is based on intuitive interfaces and access mechanisms.
+Solutions that are widely used especially on the Web are based on keyword search, and in smaller-scale scenarios, also support natural language (NL) inputs.
 While they are easy to use, the inputs provided by the users through these interfaces are \emph{ambiguous} such that the underlying information need (query intent) is not directly accessible to the system.
 Further, there are search scenarios where not only the query, but also the data representation does not precisely capture the semantics and structure of the underlying information.
-Accordingly, the core problems to be addressed in search are to \emph{understand the query intent and the data}, to \emph{match query against data}, and to \emph{rank results}.
+Accordingly, the core problems to be addressed in search are (1) to \emph{understand the query intent and the data}, (2) to \emph{match query against data}, and (3) to \emph{rank results}.
+
+Modern search engines are efficient in retrieving documents (web pages in the case of web search) from large collections based on matching the text of the user's query with the textual content of the document or words in linking to the current document (\emph{anchortext}).
+These textual features are often combined with additional features that measure the popularity of results based on usage data (\emph{click-behaviour} or using metrics computed on the web graph such as \emph{PageRank} and its derivates.
+In combination, these relatively simple, but scalable matching techniques are are able to address a large fraction of common information needs.
+They work particularly well when the user is able to explicitly name the target of the query, this reference is unambiguous and refers to a popular item widely referred to with that name.
+An example is a product search, where the user enters the name of the product and that product is widely known by that name, e.g \emph{canon ixus 115}, a digital camera.
 
 \subsection{Many Unsolved Long-tail Queries}
-Modern search engines can effectively interpret the topics and based on that, disambiguates the need intended in the provided query inputs.
-Combining with additional (query-independent) factors such as PageRank, they are able to address a large fraction fraction of common information needs.
-In particular, queries that request for pages about a particular topic (\emph{topical query}) or representing popular entry points to commonly used information that can be reached via further browsing activities (\emph{navigational queries}), can be successfully processed.
-However, dealing with the large number of distinct queries in the ``long tail'' of Web query logs \cite{} remains challenging.
-Two particular categories of problematic cases are ambiguous and complex queries:
 
-\begin{itemize}
-	\item \emph{Ambiguous queries}: these queries contain ambiguous terms, resulting in many possible interpretations (several query intents).
-For instance, the query ``young scholars from Germany'' is difficult to processed because without any additional context, it is not clear who is ``young'', and different types of people may be considered as ``scholars''.
+While search engines have been effective in addressing common needs, most queries are still in the ``long tail'' of Web query logs.
+Baeza-Yates et al.
+report that even in a full year of query logs 88\% of the unique queries are singleton queries, i.e.
+appeared only once in the year.
+A lot of this variety comes from syntactic variations of the same popular need and can be addressed with spell-corrections and query suggestion techniques.
+However, the remaining queries tend to be less common because they refer to less popular needs that need disambiguation or require more complex explanation.
 
-	\item \emph{Complex queries}: this class of queries capture complex information needs which may involve several entities and relationships between them.
-As an example, we have a query that mentions a person and a location, and asks for a relationship between that person and another location (relational queries):  ``birthplace of 32 year old computer scientist, who lives in Karlsruhe, a city in Germany''.
-\end{itemize}
+%\begin{itemize}
+%	\item 
+	\textbf{Ambiguous Queries:} 
+	Ambiguous queries arise naturally when the user may not be able to name precisely the item that is sought.
+Coming back to the example of product search, a user who is in the early stages of selection may not know exactly which product to look for.
+In this case, the user may name one or two characteristics of the product, such as \emph{cheap digital camera}.
+The concept of digital camera covers a broad range of actual entities, and there might be some discussion as to which of these can be considered cheap.There are also systemic factors that lead to an increase in ambiguity.
+Despite the expectation that longer queries should leave to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ an AND semantics between words, and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult.
+Thus users have learned to avoid long queries, leading to shorter but more ambiguous queries.
+Lastly, users will try to find what they are looking for with the least possible words, adding additional terms after realizing that their original query was ambiguous.
+For example, when searching for people the user may type in a name, only to realize that there are multiple persons with the same name.
+Often, this is aggravated by the bias toward a single popular answer.
+For example, when searching for 'George Bush', the top results are crowded by references to the same person, even though this is a common name.
+\footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}.
 
-Clearly, these two categories represent orthogonal aspects, namely the \emph{ambiguity of query terms} and the \emph{complexity of the intended information need}.
+%	\item 
+	\textbf{Complex Queries:} We include in this class all queries that go beyond a reference to a single named entity, and involve several entities and relationships between them.
+These queries arise again when the user does not know the answer to a question and therefore has to describe the item sought and it's relationships to other items that he or she can name.
+For example, searching for this paper by the name of the second author is relatively straightforward.
+However, assuming the user does not know (or do not remember) the name, he or she might look for a "semantic search survey paper written by a researcher at yahoo".
+Complex queries are particularly hard to address in the traditional information retrieval paradigm when they require information extraction and aggregation, i.e.
+when not all the entities and relationships are mentioned in a single document.
+Queries for events naturally involve multiple entities, typically the participant in the event and a reference to another item, e.g.
+\emph{barrack obama birth certificate}.
+%\end{itemize}
+
+Clearly, these two categories represent orthogonal aspects, namely the ambiguity of query terms and the complexity of the intended information need.
 Many queries in the long tail are both ambiguous and complex.
-They require deep understanding of the need and the information behind the query and data, respectively.
+They require \emph{deep understanding} of the need and the information behind the query and data, respectively.
 
 \subsection{Large Amount of Semantic Data}
-Targeting these problematic cases, semantic search solutions aim at exploiting the large and increasing amount of semantic resources that have been made available in different settings.
-These resources include taxonomies, thesauri and formal ontologies that can be used for the interpretation of query terms and data representation.
-More generally, also structured data exposed as graph-structured RDF data belong to this type of semantic resources (henceforth called \emph{semantic data}) that are used for semantic search.
-They come as standalone RDF datasets or are embedded in Web pages in the form of RDFa.
+Targeting these problematic cases, there is a category of search solutions -- often referred to as semantic search solutions -- that aim at exploiting the large and increasing amount of semantic resources that have been made available in different settings.
+Prominently, Google refers to this as the next generation of search in a recent issue of the Wall Street Journal.
+
+Semantic resources are used by these solutions for the interpretation of queries and data. They include taxonomies, thesauri and formal ontologies. 
+More generally, also structured data exposed as graph-structured RDF\footnote{RDF stands for Resource Description Framework, a W3C Semantic Web standard for data representation and exchange on the Web: \url{http://www.w3.org/RDF/}} data are regarded as semantic resources (often called \emph{semantic data}).
+They come as standalone RDF datasets or are embedded in Web pages in the form of RDFa (a W3C standard\footnote{http://www.w3.org/TR/xhtml-rdfa-primer/} for embedding RDF data in Web pages).
 These data have been increasing rapidly.
-As a result of community projects such as Linking Open Data\footnote{}, a large amount of structured datasets formerly kept protected in databases are now exposed as publicly Web-accessible RDF data.
+As a result of community projects such as Linking Open Data\footnote{\url{http://www.w3.org/wiki/SweoIG/TaskForces/CommunityProjects/LinkingOpenData}}, a large amount of structured datasets formerly kept protected in databases are now exposed as publicly Web-accessible RDF data (e.g.
+Linked Data\footnote{\url{http://linkeddata.org/}}).
 Besides large companies such as BestBuy and Facebook, also national governments such as the US and UK have followed this direction of publishing and linking semantic data on the Web.
@@
 The main idea behind semantic search solutions is to use these semantic resources to improve the search performance.
-Taxonomies, thesauri, and ontologies capture semantics that can be used to understand the query and data and to resolve ambiguities.
-Instead of returning textual data in documents, precise facts capturing entity related information and their relationships can be directly retrieved from semantic data to provide \emph{direct answers} to complex queries.
+Taxonomies, thesauri, and ontologies capture semantics that can be used to understand the query and data and to \emph{resolve ambiguities}.
+Instead of returning textual data (Web pages, documents), precise facts capturing entity related information and their relationships can be directly retrieved from semantic data to provide \emph{direct answers to complex queries}.
 
 \subsection{Plethora of Semantic Search Solutions}
-Capitalizing on the opportunities that arise from this increasing wealth of semantic resources on the Web, commercial search engines have made different kinds of semantic search features available to end users.
-The first well-known example towards this direction is Powerset, which makes use of semantic data extracted from Wikipedia to answer complex questions.
-Semantic data embedded in Web pages are now actively used by Google to provide rich result snippets\footnote{}.
+Capitalizing on the opportunities that arise from this large and increasing amount of semantic resources on the Web, commercial search engines have made different kinds of semantic search features available to end users.
+The first well-known example towards this direction is Powerset\footnote{\url{http://en.wikipedia.org/wiki/Powerset_(company)}}, which makes use of semantic data extracted from Wikipedia to answer complex questions.
+Semantic data embedded in Web pages are now actively used by Google to provide rich result snippets\footnote{\url{http://www.google.com/webmasters/tools/richsnippets}}.
 
 Likewise, research interest in semantic search is stirring up.
-A large body of work has been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web.
+A wide range of semantic search approaches have been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web.
 Correspondingly, semantic search has been viewed from different angles, resulting in a plethora of solutions.
-While underlying all these efforts lie one central idea, namely to use semantic resource for more effective search, existing approaches greatly vary in the information needs, the query and the data that are supported.
-Hence, different concepts and techniques have been studied in these settings.
-Most notably, there are principle differences between semantic search approaches, which use semantic resource to improve \emph{document retrieval}, and the ones that compute direct results, i.e.
-semantic \emph{data retrieval}.
+
+Underlying all these efforts lie one central idea, namely to use semantic resources for more effective search.
+However, existing approaches greatly vary in the \emph{data}, (2) the \emph{semantic resources}, the \emph{information needs} and (4) the \emph{querying paradigms} that are supported.
+Most notably, there are principle differences between semantic search approaches, which use semantic resources to improve document retrieval, and the ones that compute direct results, i.e.
+semantic data retrieval.
+That is, whereas the one category of approaches focuses on textual data, the other category targets the case of structured and semantic data.
+The specific types of semantic resources used by these approaches vary and may include thesauri, full-fledge ontologies or large amounts of semantic data.
+With respect to information needs, solutions focusing on the retrieval of single entities (and documents) can be distinguished from relational ones, where relationships between entities have to be considered.
+Substantial differences also exist between systems, which either use NL, keywords or facet-based operations as the primary means for querying.
+Further, research work found in literatures often studies one of the specific (5) \emph{subproblems in search}: Namely, different concepts and techniques have been proposed for (5a) the interpretation of query inputs and data, (5b) matching the query intent against data and (5c) ranking results.
 
 \subsection{Contributions}
-Concepts for semantic search have been around for several several years and its mainstream adoption into commercial solutions is increasingly visible.
+Different solutions for semantic search have been around for a long time.
+In this work, we present a systematic survey to provide a taxonomy of various semantic search approaches, to reflect on the achievements that have been made over these years, and finally, to discuss the challenges ahead and directions for future research.
 
-\begin{itemize}
-	\item In this work, we present a systematic survey to provide a \emph{taxonomy of various semantic search approaches}, to reflect on the achievements that have been made over these years, and finally, to discuss the remaining challenges and directions for future research.
-To the best of our knowledge, the only work...
+% and their mainstream adoption into commercial solutions is increasingly visible. 
+There exist a few usability studies, which compare several semantic search solutions~\cite{DBLP:conf/semweb/KaufmannB07,DBLP:conf/esws/TranMH10}.
+However, this line of work focuses on the differences in querying paradigms.
+Towards a classification of semantic search approaches, Mangold discusses existing solutions along the dimensions of architecture, coupling, transparency, user context, ontology structure and ontology technology~\cite{DBLP:journals/ijmso/Mangold07}.
+The last two criteria basically capture the differences in semantic resources among existing systems, which are also discussed in our study.
+In addition to query paradigms and semantic resources, our study includes the aspects of data, information needs, and provides a fine-grained taxonomy that distinguishes approaches by the subproblems in search they addressing.
+Further, whereas the previous survey~\cite{DBLP:journals/ijmso/Mangold07} focuses on document retrieval, our study aims at a unified view of document and data retrieval.
+In particular, we cover a large body of recent work that is not part of that previous survey.
+
 %	\item Besides this general overview, we discuss the \emph{state-of-the-art in semantic data retrieval}, a direction of semantic search that aims at direct results as answers.
@@
 
-\end{itemize}
-
 \subsection{Outline}
+The paper is organized as follows: An overview of semantic search and the concepts it entails is presented in Section~\ref{sec:ss}.
+Then, the paper is organized mainly along the aspects based on which we distinguish different semantic search approaches.
+Different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and ~\ref{sec:semantics}.
+Then approaches are discussed along the subproblems of data interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}.
+After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches}.
+Main challenges derived from that and implications for future work are presented in Section~\ref{sec:challenges}, before we finally conclude in Section~\ref{sec:conclusion}.

### 2012-04-09 tr-semanticsearchsurvey-data/overview.tex

--- 2011-12-22 tr-semanticsearchsurvey-data/overview.tex
@@
-\section{Taxonomy of Semantic Search Approaches}
-In this section, we identify the main dimensions in which existing solutions vary and then, provide a taxonomy of semantic search approaches.
+\section{Semantic Search}\label{sec:ss}
 
-Search is about retrieving information that are relevant with respect to a given information need.
-Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs.
-Generally, they can be defined in terms of the following main dimensions, i.e.
+\begin{figure}
+	\centering
+		\includegraphics[width=0.35\textwidth]{figs/semsearch.pdf}
+	\caption{Semantic Search.}
+	\label{fig:semsearch}
+\end{figure}
+
+Basically, \emph{search} can be characterized by three components, namely the \emph{data}, the \emph{query} and the \emph{matching} framework for computing results from the data for a given query.
+This is illustrated in the left portion of Fig.~\ref{fig:semsearch}.
+One main characteristic of search concepts is its emphasize on end users.
+That is, search typically involves intuitive interfaces targeting users, who may do not possess knowledge about the domain, the data and structured query languages.
+The query inputs that can be obtained from these interfaces are often ambiguous.
+That is, they allow for many possible \emph{interpretation}s, which in turn, yield many possible results that vary in relevance w.r.t.~ the intended query intent.
+% Because end users are often only interested in the few best results, 
+\emph{Ranking} is an essential component in search that aims to address this, i.e.
+to distinguish results in terms of relevance.
+Basically, matching can be conceived as the task of identifying matches whereas ranking is more specifically about the degree of matching.
+
+\emph{Semantic search} is a concept widely used by different communities to refer to search approaches that broadly speaking, use semantics to improve the search experience.
+Considering the core search tasks, semantics has been used to obtain a better understanding of the data and query as well as to improve matching and ranking based on that (see Fig.~\ref{fig:semsearch}).
+There are exist different notions of semantics.
+One the one hand, there are proposals for using the semantics of words captured as latent concepts (e.g.
+inferred through Latent Semantic Indexing~\cite{DBLP:conf/sigir/Hofmann99}) or latent topics (e.g.
+inferred through Latent Dirichlet Allocation~\cite{DBLP:conf/sigir/WeiC06}).
+While these models only implicitly capture the semantics in terms of some latent, unknown dimensions, there are also explicit models of semantics.
+For instance, Explicit Semantic Analysis uses Wikipedia articles, categories, and relations between articles to capture semantics in terms concepts, which are then used for concept-based IR~\cite{DBLP:journals/tois/EgoziMG11}.
+Other explicit models of semantics (henceforth called \emph{semantic models}) include thesauri, the terminological part (TBox) of ontologies and data schemas.
+While these models capture semantics at the conceptual level, there are also \emph{semantic data} capturing the semantics of individual entities.
+To accommodate the wide range of semantic search approaches that exist, we formulate the following general notion of semantic search:
+
+\begin{definition} \emph{Semantic search} is a search paradigm that makes use of explicit semantics to solve core search tasks, i.e.
+to use semantics for interpreting query and data, matching query against data and ranking results.
+\end{definition}
+
+While all semantic search approaches involve some kinds of explicit semantics, the retrieval contexts and the specific semantic models used to deal with the meaning behind the query intent and data vary.
+In particular, we identified the following aspects, based on which we will characterize and distinguish existing solutions:
 
 \begin{itemize}
-\item the \emph{type of information needs} targeted by the system,  
-\item the representation of the information need called the \textit{query}, 
-\item the representation of the underlying \textit{information} called \emph{data}, 
-\item the \emph{semantic models} used to interpret query and data and 
-\item the techniques for \emph{matching} the query against the data and for \emph{ranking} the results.  
+\item the type of targeted \emph{information needs},  
+\item the representation of information resources (\emph{data}), 
+\item the representation of the information need (\textit{query}) or respectively, the underlying method for querying the data (querying paradigms), 
+\item the \emph{semantic models} used to understand and to represent the meaning behind query and data, 
+\item the framework for \emph{matching} queries against data, which also involves \emph{interpreting} the data and query intent as well as \emph{ranking} the results.  
 \end{itemize}
 
-A general overview of the types of information needs, queries, data, semantic models and matching and ranking techniques supported by existing semantic search approaches is illustrated in Fig.~\ref{}.
-We will now discuss these approaches along these different dimensions.
+For instance, we can look at the differences in the data to arrive at the distinction between document retrieval and data retrieval, two major research directions in search that mark the borders of large communities.
 
-\subsection{Information Needs}
-Document search, entity search, factual search, relational search
+\textbf{Document Retrieval:} The IR community targets the document retrieval context where results are retrieved from a collection of documents (primarily textual data).
+Semantic search of this type is different from standard document retrieval approaches in the use of semantics.
+The traditional type of semantic models used here are thesauri that are employed to interpret the terms in the textual representation of queries and data.
+Recently, semantic data such as RDF resource descriptions have also been employed to interpret query and documents in terms of real-world entities and their relations.
 
-\subsection{Queries}
-Search is about end-user oriented interfaces: NL, keywords, facets
+\textbf{Data Retrieval:} Querying entities and their relations is a core problem in database research.
+As opposed to the hidden semantics of textual content in documents, information about entities and their relations are explicitly available in this setting -- either directly as semantic data in RDF or as some kinds of structured data that can be converted to RDF.
+Thus, understanding the semantics of the underlying data is not the problem here.
+However, as opposed to standard data retrieval that is based on structured query languages, intuitive query interfaces are needed in the search context.
+This leads to the issue of ambiguity.
+Hence, semantic search approaches of this type have to deal with the resulting problems of interpreting the query intent and ranking the many possible results.
+%Just like in the document context, the goal here is to enable easy access to the most relevant results.
+Especially in the Semantic Web community, solutions targeting this problem are also referred to as semantic search because they use semantic data to interpret the query intent and to rank results.
 
-\subsection{Data}
-Objects (documents, media and multimedia objects) with embedded semantic data, semantic datasets
+%In this section, we establish the main dimensions in which existing solutions vary and then discussed them in more detail in the subsequent sections. 
+% and then, provide a taxonomy of semantic search approaches.
+We focus on approaches studied by researchers in the Semantic Web community that explicitly target semantic search.
+Selectively, we also point out works from the IR and database communities that deal with the same problem.
+%Search is about retrieving information that are relevant with respect to a given information need. 
+%Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs.
 
-\subsection{Semantic Models}
-Linguistic models, conceptual models
+More fine-grained than this general breakdown into document and data retrieval, Fig.~\ref{fig:semsearch_detailed} illustrates the specific differences in queries, data, semantics, results (corresponding to information needs) and solutions for the subproblems that distinguish existing semantic search approaches.
+We can see that central to semantic search is the use of semantics (depicted as gray boxes in Fig.~\ref{fig:semsearch_detailed}).
+In particular, semantic resources represented by lexical models, knowledge models as well as semantic data and metadata are used for the subproblems of understanding raw data (e.g.
+text) and queries.
+The resulting semantics of data and queries are then employed for solving the subproblems of matching and ranking.
 
-\subsection{Matching \& Ranking Techniques}
-Term-based, structure-based, semantic-based
+%We will now discuss them along these aspects.
 
-%Generally, queries might be simple keywords, natural language or structured.
-Various kind of formal query languages have been proposed to formulate highly expressive (both in terms of structure and semantics) queries.
-Resources returned to the users range from text, audio and video up to multimedia documents.
-These documents embody different types of data, i.e.
-unstructured, semi-structured (in the form of RDF) that is not associated with a schema and fully structured data with a schema.
-Often, structured data available in Semantic Web languages such as RDF and OWL is also referred to as ``semantic data''.
-Different matching framework are employed by these systems.
-IR systems primarily rely on features at the level of terms (language, words) whereas DB and KB systems exploit also the structure as well as the semantics for matching.
-On the other hand, while these DB and KB systems are concerned with producing precise matches (binary matching), IR systems rely on statistical methods that are inherently imprecise such that results are also associated with the degree of matching, i.e.
-IR systems perform imprecise matching and ranking.
+\begin{figure*}[tbh]
+	\centering
+		\includegraphics[width=0.75\textwidth]{figs/semsearch_detailed}
+	\caption{Overview of Semantic Search Approaches.}
+	\label{fig:semsearch_detailed}
+\end{figure*}
+
+\section{Information Needs}\label{sec:needs}
+
+The main motivation for semantic search is to go beyond the relatively frequent but simple queries currently supported by existing Web search solutions to solve the long-tail queries representing rather complex information needs.
+But also for simple queries, semantic data have proven to be valuable.
+Instead of showing documents, semantic data are used by commercial Web search engines to create rich snippets for Web pages, or to deliver direct answers, e.g a specific address for a query mentioning ``location'' and a named entity such as ``Yahoo!
+Research Lab Barcelona''.
+We will now discuss several common types of queries and the information needs behind them, from the more simple entity queries to complex relational and analytical queries.
+
+\subsection{Entity Search} Most queries on the Web ask for pages representing entities such as companies or people.
+They are used to obtain entry points, while additional navigation and browsing are still required to satisfy the actual information need.
+Thus, in the IR context, these queries are also referred to as navigational queries.
+Recently, semantic data embedded in Web pages have been exploited to address this type of queries.
+This was pioneered by Yahoo!
+in their SearchMonkey program, and later adopted by Google to present rich entity snippets\footnote{Google Rich Snippets} as answers to this kind of queries.
+As an example, Fig.~\ref{fig:semantic_layer} illustrates the entity search functionalities provided by Yahoo!.
+Not only there are Web pages but also entity descriptions appear as results.
+These descriptions are directly retrieved from semantic data (in this case, a dataset about music artists and their albums).
+Instead of searching over a collection of documents, semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results.
+Examples for this type of queries include the one asking for ``young scholars in Germany'' already mentioned before, or the query ``Researcher Thanh Tran'' depicted in the top left portion of Fig.~\ref{fig:matching}.
+Results for queries of this type comprise one or several entities.
+
+\subsection{Factual Search} While results to the previous type of queries presented to the users are either some entity descriptions or Web pages about entities, the information needs behind this type of search requests require specific information from these descriptions and pages, respectively.
+Many searches on the Web for instance, aim at finding the ratings of restaurants, or the phone number of a particular person.
+To continue with our example, users may directly ask for ``the birth place of young scholars in Germany''.
+Direct answers to this type of queries are supported by WolframAlpha\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge\footnote{\url{http://www.trueknowledge.com/}}, or the various research prototypes such as Hermes~\cite{DBLP:journals/ws/TranWH09} (later incorporated into a larger system called SemSearchPro~\cite{DBLP:journals/ws/TranHL11}) or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}.
+Since factual search is mostly about facts that correspond to attribute values of entities, it is often regarded as a particular type of entity search.
+In this survey, we do not further distinguish this from the general entity search task.
+
+\subsection{Relational Search} The information need here goes beyond single entities and their factual information.
+Answers to queries of this type comprise several entities and relationships between them.
+Hence, processing these queries requires some understanding of relations between entities.
+For instance, the example presented in the introduction about 32 year old computer scientists requires knowledge about their \verb+lives in+ and \verb+birth place+ relations to some locations.
+Relations may be explicitly specified as part of the keyword or NL query, and entities satisfying these relation constraints can be computed using SemSearchPro~\cite{DBLP:journals/ws/TranHL11} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}.
+
+Other systems such as NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} also support searches where relations to be considered are not explicitly mentioned in the query, or simply \emph{unknown}.
+They address information needs that involve finding how some entities are related to some other entities.
+The interesting part of the results here are thus not the entities, but the relationships between them -- also referred in literatures as semantic associations (direct connection) or property sequences (indirect connections, i.e.
+path)~\cite{DBLP:conf/www/AnyanwuS03}.
+An example for this type of query asking for paths between ``Peter Mika'' and ``Thanh Tran'' is depicted in the top right portion of Fig.~\ref{fig:matching}.
+
+Even though Yahoo!
+entity search as shown in Fig.~\ref{fig:screenshot_yahoo} does not directly search for relations, it can be seen on the left portion that relations between entities captured in semantic data constitute valuable information for suggesting related entities.
+Searching for known relations or unknown relations is supported by the Information Workbench\footnote{\url{http://iwb.fluidops.com}}, a commercial adoption of SemSearchPro.
+On the bottom part of Fig.~\cite{fig:screenshot_iwb}, we can see results returned to a query that specifically asks for entities connected through the \verb+producer+ relation.
+When relations are not explicitly given in the query but only entities and (or) concepts, this system is also able to explore paths between them.
+However, this system does not directly return relationships and paths in the data as results, but structured queries representing interpretations of the entered keywords -- a querying paradigm we will discuss in the next section.
+
+\subsection{Analytical Search}
+Beyond the common searches for entities and relations, which form the focus of this survey, there are also information needs, which can only be addressed when some additional analyses are performed on top of the data.
+Generally speaking, any kind of additional computation may be applied to the data and results for the purpose of analytical search.
+Analytics often found in semantic search engines are supported through simple sorting and averaging, more sophisticated statistical and mathematical models, or some form of Machine Learning based inductive reasoning or logic-based deductive reasoning.
+For instance, WolframAlpha is advertised as a computation engine because it applies different kinds of mathematical models to compute answers to queries, whereas True Knowledge uses an inference engine to perform temporal and geospatial reasoning.
+
+\begin{figure}
+	\centering
+		\includegraphics[width=0.5\textwidth]{figs/screenshot_yahoo}
+	\caption{Entity search with Yahoo!.}
+	\label{fig:screenshot_yahoo}
+\end{figure}
+
+\section{Querying Paradigms}\label{sec:querying}
+Typically, addressing complex needs requires the expertise of technical users who know the underlying data and schema and use them to formulate questions as structured queries.
+However, search is commonly seen as an end-user oriented paradigm, which instead of using structured query languages, involves intuitive and easy-to use access interfaces.
+The three main interfaces studied for semantic search are based on keywords, NL, and facets.
+Often, a combination of these paradigms, e.g.
+keywords and facets, is used to support an iterative search process where instead of constructing the query at once, the user modifies the query and results respectively, through a series of operations.
+
+\subsection{Keyword Search} Expressing the information needs as keywords is a paradigm that is not only popular for Web search but also widely adopted by the new breed of semantic search solutions.
+Most engines focusing on entity search such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} feature a keyword search interface.
+Keywords can also be used to formulate more complex relational searches.
+Addressing this scenario, engines such as SemSearchPro~\cite{DBLP:journals/ws/TranHL11}, TASTIER~\cite{DBLP:conf/sigmod/LiJLF0} and IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} retrieve entities matching keywords, and search for relations between them in the data.
+
+\subsection{NL Search} This is the other paradigm for users to express their needs using their own words.
+Traditionally, it has been used to pose complex questions against expert systems built for specific domains.
+Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha, True Knowledge and Apple's Siri\footnote{\url{http://en.wikipedia.org/wiki/Siri_(software)}}.
+
+\subsection{Faceted Search} Instead of formulating the entire query at once, faceted search supports an iterative process of querying, browsing and query refinement.
+This belongs to the broader category of approaches called \emph{exploratory search}, which assumes that users do not precisely know how or what to search and thus, combines querying and browsing strategies to enable learning and investigation.
+Upon the initial search performed by the user (e.g.
+using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/semweb/FerreH11,DBLP:conf/esws/HeimEZ10} present results as well as facets representing attributes and relations that are applicable for refining (or simply, are related to) the current results.
+These facets can then be used to browse, to refine or to expand the results (i.e.
+to modify the query, respectively).
+Microsoft's EntityCube\footnote{\url{http://entitycube.research.microsoft.com/}} for instance, returns entities upon users' keyword search requests along with relations and attributes of these entity results as facets.
+Parallax\footnote{\url{http://www.freebase.com/labs/parallax/}} is another commercial faceted search solution (from Freebase, now Google) that enables a combination of search, intelligent result visualization and facet-based browsing.
+
+While most faceted search solutions focus on browsing and refining results of entity queries, faceted search in principle can also be used to address complex needs.
+For instance, gFacet~\cite{DBLP:conf/esws/HeimEZ10} supports relational search through the construction of complex facet graphs representing different types of entities and relations between them.
+Fig.~\ref{fig:screenshot_iwb} shows the faceted search feature from the Information Workbench.
+Every column in the result table captures one particular type of entities and this system shows facets for every type that appears in the results (e.g.
+Fig.~\ref{fig:screenshot_iwb} shows facets for column 1).
+Hence, entries in every column (representing a partial result and a query part, respectively) can be refined or expanded.
+For instance, the column of singles shown in Fig.~\ref{fig:screenshot_iwb} can be further refined to contain only those connected with \verb+Freddie Mercury+ through the \verb+writer+ relation.
+
+\subsection{Iterative / Exploratory Search} 
+While faceted search is the most popular paradigm in the industry, there are other exploratory search interfaces that support an iterative search process.
+Instead of showing facets as users type, also \emph{completions} of the single user keywords (term completions) or of the entire query representing the full query intent (query completions) have been proposed.
+One example system supporting this is the Information Workbench shown in Fig.~\ref{fig:screenshot_iwb}, which presents terms matching the current tokens entered by the users, as well as full interpretations of the entire query.
+For ``queen single'', the interpretations shown indicate that the query intent may be something matching the word ``queen'' that is of the type \verb+single+, or something that is of the type \verb+single+, which is produced (or written) by something else matching the word ``queen''.
+Google, Freebase\footnote{\url{http://www.freebase.com/docs/suggest}} and True Knowledge also present possible interpretations of the query as the user type or after issuing a query.
+
+Instead query-based completions, also results matching the (possible interpretations of the) keywords provided so far have been presented (called result completions~\cite{DBLP:conf/esws/TranMH10}).
+For instance, ESTER~\cite{DBLP:conf/sigir/BastCSW07} shows entity search results matching the keywords as well as their facets (see CompleteSearch~\footnote{\url{http://www.dblp.org/search/index.php}}, which is an adoption of ESTER) whereas TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} provides type-ahead search by finding complex (joins of) database tuples as the user types query keywords.
+With these systems, users can iteratively construct the query by selecting the presented completions and facets.
+VisiNav~\cite{DBLP:journals/ws/Harth10} goes beyond this selection-based interaction, allowing iterative query construction also via drag and drop.
+
+\begin{figure}
+	\centering
+		\includegraphics[width=0.5\textwidth]{figs/screenshot_iwb}
+	\caption{Querying with the Information Workbench.}
+	\label{fig:screenshot_iwb}
+\end{figure}
+
+\section{Data}\label{sec:data}
+The information resources made available for search as well as any kind of additional background information used to improve the search experience, are kept and managed by the system as data.
+In semantic search solutions, data can be broadly categorized into two types, namely \emph{semantic data} and \emph{raw data}.
+
+Basically, semantic data describe real-world objects in terms of entities and their relations.
+Primarily, semantic data have been used to refer to RDF datasets, or instance data contained in ontologies represented in Semantic Web languages such as OWL (the Web Ontology Language, a logic-based W3C standard\footnote{http://www.w3.org/TR/owl-features/} for representing the semantics of vocabulary / schema elements) and RIF (the Rule Interchange Format, a W3C standard for representing and exchanging rules).
+However, different kinds of structured data actually correspond to this rather general notion of semantic data.
+In fact, large amounts of structured data formerly kept in hidden
+%XML or relational 
+Web databases 
+have been converted to and published on the Web as RDF data.
+Several semantic search systems have been built that specifically target the retrieval of semantic data.
+Instead of searching directly over semantic data, classic retrieval systems search over a raw data representation of information objects such as audios, videos, images and texts.
+For instance, document retrieval systems search for textual documents that are represented as bags of words.
+As opposed to semantic data, raw data do not explicitly capture the semantics of information resources in terms of entities and their relations.
+Thus, for supporting document (or image, video or audio) retrieval as semantic search, one core subtask is the recognition of named entity in the raw text.
+Named entity recognition and other data interpretation tasks such as relation extraction are performed to obtain a semantic data representation of raw data (also called \emph{semantic metadata}).
+
+\subsection{Semantic Data}  The most common type of semantic data used in semantic search systems is RDF.
+Basically, RDF is a graph-structured model, representing entities, their attributes, and relations between them as a set of triples.
+A visual illustration of such a \emph{semantic data graph} capturing information about two \verb+researcher+s, whose \verb+names+ are \verb+Thanh Tran+ and \verb+Peter Mika+, is depicted in the bottom portion of Fig.~\ref{fig:matching}
+
+This general graph-structured model can be used to capture structured data of different types.
+In fact, most of the data made publicly available on the Web and incorporated into semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09}, Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} and SemSearchPro~\cite{DBLP:journals/ws/TranHL11} originate from relational or XML databases.
+XML elements can be represented as nodes, and their structure information can be captured as edges.
+Likewise, information contained in tuples of a relation database can be mapped to nodes, while foreign key relationships can be modeled as edges.
+In fact, the conversion of XML and relational data to a RDF semantic data graph can be accomplished by using mapping rules, and there exist many standards and tools for accomplishing that (e.g.
+see W3C RDB2RDF\footnote{\url{http://www.w3.org/2001/sw/rdb2rdf/}}).
+Represented as RDF, these and possibly other types of structured data also capture information about real-world objects in terms of entities and their relations.
+Hence, especially after their conversion to RDF, structured data are often synonymously referred to as semantic data.
+To capture this general notion of semantic data used in semantic search systems, we introduce the following definition:
+
+\begin{definition}
+\emph{Semantic data} can be conceived as a graph, where nodes represent \emph{entities} and their \emph{attribute values}, and edges stand for \emph{attributes} of entities or \emph{relations} between entities.
+\end{definition}
+
+In particular, this notion accommodates three main types of semantic data currently used in semantic search systems, namely (1) text-rich entity descriptions contained in structured document collections, (2) structured entity descriptions in RDF and (3) formal logic-based entity descriptions specified using expressive knowledge representation languages such as OWL.
+
+\textbf{Text-Rich Entity Descriptions:} This category of semantic data contains entities that are largely described through text, i.e.
+entity attribute values are composed of lengthy textual descriptions.
+Wikipedia is the most popular example that lies at this end of the spectrum of semantic data.
+While it is actually a collection of documents (i.e.
+contains mainly textual data), it fits the presented notion of semantic data because every Wikipedia page corresponds to an entity, and there are links between Wikipedia pages that can be seen as relations.
+In fact, exploiting this and other specific features of Wikipedia articles such as Infoboxes, a RDF dataset called DBpedia~\cite{DBLP:journals/ws/BizerLKABCH09} has been automatically derived from this collection.
+Wikipedia as a source of semantics is particularly popular for search systems that focus on expert search or entity search in general.
+It is used either to directly answer entity search queries or as background knowledge~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/cikm/BronBR10}.
+
+\textbf{Structured Entity Descriptions:} This type of semantic data is ubiquitous on the Web, capturing information about real-world objects as RDF resource descriptions (or structured entity descriptions that can be directly converted to RDF).
+Through industry efforts such as Yahoo's SearchMonkey, Google's Rich Snippets and Facebook Like\footnote{\url{http://developers.facebook.com/docs/reference/plugins/like/}}, a large amount of RDF descriptions of resources such as restaurants and movies have been embedded into existing Web pages as RDFa.
+Besides, hundreds of large-scale RDF datasets have been made available on the Web.
+Started with the Linking Open Data, more and more data are made freely available on the Web and linked with other public datasets.
+Not only Web content providers but many companies, public institutions and national governments (US, UK etc.) are now actively publishing and linking RDF data on the Web (called Linked Data).
+Availably datasets can be subdivided into broad/domain-independent ones such as as DBpedia and Freebase\footnote{\url{http://www.freebase.com/}} or deep/domain-specific ones.
+Large domains covered by Linked Data today include government, health care, entertainment and geography.
+
+\textbf{Formal Entity Descriptions:} On the other end of the spectrum, there are more formal views on what constitutes semantic data.
+In particular, many researchers may argue that the reason why RDF, and other data models that are built upon a formal model of semantics, are actually called semantic data (instead of structured data) is because they can be exploited by a reasoning engine to infer new knowledge (i.e.
+the knowledge that is entailed by the semantics).
+While the formal model of semantics specified for RDF is relatively simple (consists only of a few inference rules), semantic data in some existing search systems are represented using more expressive knowledge representation languages such as OWL and F-logic~\cite{DBLP:conf/sigmod/KiferL89} (basically, a combination of logic and object-oriented frame-based languages).
+For instance, Serene~\cite{DBLP:journals/ws/FazzingaGGL11} makes use of facts that are captured as Abox assertions (i.e.
+instance data, as opposed to Tbox, the schema part) of an OWL ontology.
+ORAKEL~\cite{DBLP:journals/dke/CimianoHHMS08} searches over an F-logic knowledge base.
+However, while the use of formal semantics and reasoning has been investigated for some scenarios, it plays only a limited role in existing systems.
+The
+majority of approaches does not rely on reasoning.
+It seems that the research focus still lies in correctly understanding the ambiguous queries and data (namely, to interpret queries and data as elements of the semantic data model as defined above), while reasoning over semantic data may be beneficial but not essential yet.
+
+To sum up, a general notion of semantic data is employed in this work to consider all those systems, which capture the semantics of information resources and real-world objects as entities and relations.
+Often, these entities and relations are specified on the account of a formal data model with well-defined semantics (e.g.
+RDF, OWL, F-Logic).
+However, such a formal model is not strictly required (e.g.
+in the case of text-rich entity descriptions) and in particular, may not be exploited for reasoning.
+
+\begin{figure}[thb]
+	\centering
+		\includegraphics[width=0.5\textwidth]{figs/matching}
+	\caption{Examples for semantic data, queries and matching techniques.}
+	\label{fig:matching}
+\end{figure}
+
+There are engines operating directly on semantic data to provide direct answers (data retrieval systems).
+These are mainly systems, which provide search interfaces over RDF data and ontologies crawled from the Semantic web~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TranWH09,DBLP:journals/ws/HoganHUKPD11}, or structured databases that have been converted to semantic data graphs~\cite{DBLP:conf/sigmod/LiJLF09,DBLP:conf/sigmod/LiOFWZ08}.
+Besides them, there are also semantic search systems supporting the retrieval of documents or information objects in general.
+They employ semantic metadata, often in combination with the raw data representation of these objects.
+
+\subsection{Semantic Metadata}
+Basically, semantic metadata is semantic data that captures information about the objects to be retrieved.
+Because it is clear from the context, these two terms are often used synonymously (in this work).
+Metadata include basic information about the objects such as \verb+author+ and the \verb+year+ it was published.
+Moreover, it may capture the semantics of the information contained in these objects.
+For instance, if a particular Web page is about a restaurant, its metadata may contain a structured description of that restaurant (as RDFa) corresponding to the text contained in the page.
+In fact, one main challenge in semantic search is to interpret the semantics behind the content of information objects and to represent it as semantic metadata.
+Not only entities may be recognized but for instance, the content of a document may be interpreted as referring to a \verb+meeting+ with the two \verb+researchers+ \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participants+.
+Semantic metadata representing the content may also be manually produced and embedded into the objects.
+Recently, several industry projects such as Google Rich Snippets and Yahoo!
+SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages.
+Complementary to this,  schema.org\footnote{\url{http://schema.org/}} is an initiative promoted by major Web search companies (Google, Microsoft, Yahoo!) aiming at the provision of a common vocabulary that can be used by site owners to capture their data.
+In this regard, we note that while Wikipedia can be conceived as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).
+
+While the amount of available metadata is increasing, it is still too sparse to cover all information needs.
+Thus, metadata is mostly used as additional information that can help to improve standard search over raw data~\cite{DBLP:journals/tkde/CastellsFV07,DBLP:journals/ws/FernandezCLVCM11}.
+Search over raw data can also be seen as a fall-back solution for cases where metadata cannot completely satisfy the information need.
+There exist also 	proposals for ontology-based IR, which completely rely on metadata~\cite{tran2007expressive}.
+In this case, the retrieval of documents is formulated as a data retrieval task, where data about the documents (metadata) are returned as direct answers.
+
+\section{Semantics: Semantic Data and Semantic Models}\label{sec:semantics}
+\begin{figure}[thb]
+	\centering
+		\includegraphics[width=0.5\textwidth]{figs/semantic_layer.pdf}
+	\caption{Words, concepts and entities.}
+	\label{fig:semantic_layer}
+\end{figure}
+
+As discussed, central to semantic search system is the use of semantics.
+The color highlighting (gray) in Fig.~\ref{fig:semsearch_detailed} indicates that a main source of semantics is the \emph{semantic data} itself.
+That is, semantic data can be used directly to answer queries (i.e.
+by matching queries against semantic data), or as a semantic resource to interpret raw data and queries (as we shall see in more detail in subsequent sections).
+More specifically, Fig.~\ref{fig:semantic_layer} shows that in the textual raw data context, these semantics can be used to interpret words in terms of entities and relations.
+It also shows the other sources of semantics called semantic models.
+Broadly, \emph{lexical models}, which capture semantics at the level of words in terms of concepts, can be distinguished from \emph{knowledge models}, which capture real-world knowledge in terms of entity classes, relations, and attributes.
+
+We have discussed semantic data as one source of semantics in the previous section.
+In this section, we provide an overview of the semantic models used by current systems, and subsequently, present a notion of semantics that combines the instance-level semantics captured by the data and the schema-level (conceptual) semantics captured by the semantic models.
+
+\subsection{Knowledge Models} While semantic data capture concrete entities (instances), these are abstract models of knowledge, basically representing classes of entities, attributes associated with these classes, and relations between classes.
+This is visualized in the top left portion of Fig.~\ref{fig:semantic_layer}.
+
+Different models, which vary in the degree of formality and expressiveness have been used by different communities for semantic search.
+For instance, the model used by ORAKEL for NL question answering is captured by the Tbox portion of an ontology and consists of classes (also called concepts) that are ordered in a subsumption hierarchy and are connected through relations.
+Range and domain information are captured as restrictions on the relations.
+As shown for Serene~\cite{DBLP:journals/ws/FazzingaGGL11}, expressions more complex than these restrictions can be added to capture the semantics of concepts to reflect either general knowledge (such as the knowledge encoded in Wikipedia)
+or specific knowledge of a domain.
+Because the ontology models used in these systems are represented using the logic-based formalisms F-logic or OWL (description logic, DL), they can be seen as \emph{logical theories} with well-defined formal semantics.
+
+Also, \emph{conceptual graphs} (CGs) have been employed for representing ontology models, and used for the tasks of NL questions interpretation and answering~\cite{DBLP:conf/aswc/CaoCT08} as well as for interpreting and representing documents~\cite{DBLP:conf/iccs/ComparotHH07}.
+CGs combine the intuitiveness of graph-based languages and the formal foundation of logics, enabling the modeling of knowledge in terms of concepts and their relations and its mapping to different formal languages.
+Corese~\cite{DBLP:conf/ecai/CorbyDF04} uses CGs as an internal model (to take advantage of previous work on CGs in the KR community), which however, are then translated to RDFS to conform with this more commonly used standard language for representing RDF schemas.
+
+Closer to the end of linguistic models discussed next are knowledge models that consist of concepts only.
+For instance, C-Search~\cite{DBLP:conf/esws/GiunchigliaKZ09} encodes knowledge as concepts expressed in propositional DL.
+This DL enables the representation of complex concepts as a conjunction or disjunction of atomic concepts.
+However, it does not support relations.
+% (also called roles) but the specification
+
+\subsection{Lexical Models} The use of concepts has already been investigated in the early years of IR research~\cite{DBLP:conf/sigir/Giger88}.
+Different to knowledge models, which capture semantics in terms of real-world entities and their relations, the models employed there are lexical in the sense that they capture semantics at the level of words.
+While concepts in knowledge models stand for classes of real-world entities, concepts in lexical models correspond to \emph{senses of words}.
+Lexical concepts are more general such that they may refer to entities, classes, relations, attributes, or other senses of words.
+While these different ``types'' of senses are not explicitly distinguished like in a knowledge model, concepts can be organized along lexical relationships in a lexical model.
+
+\emph{Thesaurus} 
+%(often, \emph{lexicon} is also used as synonym) 
+is a popular lexical model that has been extensively used for document retrieval in IR, which basically, groups words together according to their semantic similarity.
+Each group represents a different word sense.
+In practice, lexical databases also considered as thesauri such as WordNet, or thesauri used in classic IR systems~\cite{DBLP:conf/sigir/Giger88}, not only capture senses (concepts) and their lexical variants, but also relationships between them such as synonym, broader, narrower and related.
+This is illustrated in the bottom part of Fig.~\ref{fig:semantic_layer}.
+
+\subsection{Semantics} 
+Based on the above discussion, we introduce a general notion of semantics that can be used to characterize the different types of semantic search systems.
+
+\begin{definition} The \emph{semantics} of queries and data are captured by semantic search systems in different ways.
+Semantics can be represented (1) as word senses that are organized through lexical relations between words (\emph{lexical model}), (2) as specific knowledge about concrete entities, i.e.
+specific attribute values and relations between entities (\emph{semantic data}) or (3) as general knowledge about classes of entities, class attributes, and relations between classes (\emph{knowledge model}).
+\end{definition}
+
+A prominent example that can be used to illustrate these many aspects of semantics is Wikipedia.
+As discussed, it has been used as semantic data to answer entity search queries, and converted to a semantic dataset called DBpedia~\cite{DBLP:journals/ws/BizerLKABCH09}.
+The Wikipedia categories of pages have been treated as classes and used to construct hierarchies of classes in an ontology called YAGO~\cite{DBLP:conf/www/SuchanekKW07}.
+Wikipedia is also used as a source for Explicit Semantic Analysis (ESA)~\cite{DBLP:journals/tois/EgoziMG11}, where every Wikipedia page is regarded as a concept.
+Because ESA does not distinguish entities from classes, the concepts here can be seen as capturing word senses.
+Thus, Wikipedia pages and links constitute a lexical model in this context.
+
+\subsection{Focus: Semantics of Entities \& Relations}
+
+The discussion of semantics so far focuses on entities and simple (binary) relations between them.
+Yet, the kind of semantics that can be expressed is only limited by the knowledge representation (KR) languages.
+There exist very powerful KR formalisms and many of them have been incorporated to perform document retrieval (already in the early years of IR~\cite{DBLP:conf/sigir/Rijsbergen89}) and to represent complex queries and knowledge used in NL question answering~\cite{DBLP:journals/tkde/VassiliadisTK94} (in the early years of expert systems).
+For instance, the employed formalisms have been used to represent temporal or fuzzy aspects of world knowledge.
+However, most semantic search systems, whether document or data retrieval systems, rely primarily on the semantics of entities and relations.
+
+There are practical reasons why the focus of current research (and this paper) is set on simple descriptions of entities (via attribute and binary relations). On the one hand, 
+%most queries on the Web ask about entities and their relations. That is, 
+most common queries as well as a large part of queries in the long tail of Web query logs 
+%can be addressed using semantics about 
+are about entities and relations (i.e.
+they are of the types entity, factual or relational queries).
+More importantly, the bottleneck is actually the availability of data.
+It became evident that manually capturing the content of documents as complex logical formulas does not scale.
+Extracting entities and relations from documents at high quality still remain hard problems, representing the limits of what can be done automatically by information extraction technologies.
+Also, most of the data residing in databases or published on the Web (as RDF) today, are mainly about entities and their relations.
+
+%\dtr{maybe also discuss the difference to XML retrieval, which merely use structure information for ``focused'' retrieval: retrieve components of the structured XML documents that match the query: The focus on the semantics of entities and relations also marks the boundary between semantic search and XML document retrieval.
+}
+
+%\section{Interpretation}
+\begin{figure*}[htb]
+	\centering
+  \subfloat[Detecting concepts.]{\label{fig:detecting_concepts}\includegraphics[width=0.34\textwidth]{figs/conceptextraction}}
+  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc. (or a blank line to force the subfig onto a new line)
+  \subfloat[Detecting entities and relations.]{\label{fig:detecting_data}\includegraphics[width=0.6\textwidth]{figs/dataextraction}}
+  \caption{Detecting concepts, entities and relations.}
+  \label{fig:extraction}
+\end{figure*}
+
+\section{Document Interpretation}\label{sec:content}
+
+One crucial task in supporting semantic search over documents is to obtain a richer understanding and representation of the document collection.
+Instead of a the typical bag-of-words model used in classic IR, the goal is to capture the content of the documents as entities, concepts and relations, i.e.
+as semantic data or elements of a semantic model.
+In fact, there is a dedicated area of research focusing on this problem of information extraction from text.
+Problems that have been studied include named entity recognition, semantic role labeling and relation extraction.
+For an overview of solutions proposed in this area, we refer the interested readers to surveys specifically focused on this problem~\cite{DBLP:journals/tkde/ChangKGS06}.
+Here, we discuss the kind of information extraction that has been performed for the purpose of semantic search.
+
+\subsection{Detecting Concepts in Text} This problem and the tasks carried out to solve it are illustrated in Fig.~\ref{fig:detecting_concepts}.
+Concepts are especially needed for supporting what is known as concept-based IR.
+
+Documents have been analyzed to extract concepts for the task of modeling documents as conceptual graphs~\cite{DBLP:conf/iccs/ComparotHH07}.
+For C-Search~\cite{DBLP:conf/esws/GiunchigliaKZ09}, which represent documents as DL concepts corresponding to WordNet senses, the authors identify words in documents matching Wordnet senses (i.e.
+direct matching), and uses part-of-speech (POS) tagging information and Wordnet, as lexical database of senses and word-level relationships, to perform word sense disambiguation.
+While words are mapped to atomic concepts, phrases are represented as complex concepts using DL formulas~\cite{DBLP:conf/esws/GiunchigliaKZ09}.
+Especially in the biomedical domain, the use of thesauri concepts for interpreting and representing documents is very common~\cite{DBLP:conf/trec/TrieschniggKS06,DBLP:conf/trec/ZhouYTS06}.
+For instance, the Unified Medical Language System and a gene-thesaurus have been used to identify multi-word terms and to map synonymous words to one concept~\cite{DBLP:conf/trec/TrieschniggKS06}.
+The concepts were identified simply by matching document words to thesaurus terms.
+
+\subsection{Detecting Entities \& Relations in Text} For extracting entities and relations, the large body of research work on named entity recognition and relation extraction has been leveraged by existing semantic search solutions.
+One of the platforms, which is frequently used by semantic search systems for extracting semantic data and
+automatically annotating document collections at a large scale is KIM~\cite{KIM DBLP:journals/ws/KiryakovPTMO04}.
+IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} makes use of UIMA\footnote{\url{http://uima.apache.org/}}, a framework of annotators that can be configured in a pipeline to analyze and extract data from text.
+There is a another work from IBM, which focuses on extracting named entities and relations from text and using them for more precise search (employing XML fragments as queries~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}).
+
+An overview of tasks involved in detecting entities and relations are shown in Fig.~\ref{fig:detecting_data}.
+As for most text interpretation tasks, a syntactic analysis of the text is needed.
+In this case, the typical analysis includes tokenization, POS tagging, chunking sentences into noun phrases, and some information extraction systems even derive entire parse trees from the text.
+Besides the syntactic information derived from text analysis, different semantic resources are used.
+In particular, Gazetteers are frequently used, which can be seen as a lexical model.
+The simplest way for detecting entities is simply to match words (tokens) against Gazetteer's entries representing entities of different classes.
+For disambiguating named entities mentions in text, it has been shown that semantic data about entities and their relations provides valuable information~\cite{DBLP:conf/esws/KlebA10}.
+The technique behind this is based on graph traversal, which starts from nodes matching the entity mentions.
+Controlled through spreading activation, paths from these nodes are then traversed to explore the semantic context of these nodes (i.e.
+entities).
+These contextual interpretations are then used for disambiguation.
+This resembles the general technique called collective matching, which applied to this case, assumes entity mentions (words) to form a context.
+We have a higher a confidence that a word matches an entity $e$, when other words in this context, match entities related to $e$, i.e.
+the context formed by $e$ and its related entities corresponds to the word context.
+
+Beyond direct matching and disambiguation, state-of-the-art techniques employ complex matching rules (or matching patterns in general), especially for the more complex task of relation extraction.
+Given a pattern like \verb+Mr.
+?
+works for ?+, matching texts can be identified and relevant entities and relations can be extracted.
+Matching patterns are specified manually or learned automatically through machine learning techniques for pattern induction.
+Current state-of-the-art information extraction programs in fact, not only use simple word patterns, but complex combination of features derived from the words (e.g.
+orthographic features such as whether the word contain digits or hyphens, word types such as lowercased and capitalized and syntactic features such as POS information), from the context (i.e.
+words in a text window along with their tags, labels etc.) as well as from background knowledge (e.g.
+from Gazetteers).
+These features along with labeled training examples are then used to train a classifier (one for every entity / relation type) or a probabilistic sequence model such as the Conditional Random Field~\cite{DBLP:conf/icml/ZhuNWZM05}.
+Besides these learning methods proposed for targeted information extraction, which assume a fixed set of predefined types of entities / relations to be extracted, there are also proposals for open information extraction~\cite{DBLP:conf/ijcai/EtzioniFCSM11}.
+So far, semantic search systems focus on the use of targeted information extraction tools (e.g.
+IBM's UIMA, SOFIE~\cite{DBLP:conf/www/SuchanekSW09}).
+While they provide lower coverage, the quality of extracted outputs is higher compared to open information extraction tools, an aspect shown to be very influential in improving the precision of semantic search results~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}.
+Promising is the combined usage of targeted and open information extraction, a direction currently pursuit by Microsoft's EntityCube.
+
+Many patterns and particularly rules used for information extraction explicitly capture when candidates can be considered as matches, i.e.
+when they are considered as belonging to some types of entities or relations.
+These patterns can be seen as sources of semantics that feed as inputs to the information extraction systems.
+Besides these matching-specific knowledge, also general as well as domain-specific knowledge stored in ontologies have been used as semantic constraints to filter matches, i.e.
+those that lead to semantic inconsistencies.
+For instance, SOFIE~\cite{DBLP:conf/www/SuchanekSW09} prunes extraction outputs that do not satisfy the semantic constraints captured by YAGO.
+As an example, having the pattern \verb+ ?x is mayor of ?y+ and the knowledge that \verb+ x, mayorOf, y+ requires \verb+ x, type, Person+ and \verb+ y, type, City+, we can filter out those extracted \verb+is mayor of+ relations that do not involve a person or a city.
+
+\section{Query Interpretation}\label{sec:query} 
+	Essentially, interpreting queries is similar to the task of understanding text in documents.
+However, these problems are studied from different viewpoints by overlapping but not same communities of researchers.
+Thus, the emphases are put on different subproblems.
+Further, besides NL text, also keywords may be provided as inputs to query interpretation.
+Keywords are different from NL text in the amount of syntactic features that can be obtained.
+
+\subsection{Detecting Concepts in Keyword Queries} One of the main challenge in dealing with keywords in queries (and words in NL text) is their semantic ambiguity.
+The same meaning can be expressed in different ways.
+In particular, there are lexical variants that refer to the same concept, relation or entity (synonymy).
+One and the same word however, can also have different meanings (polysemy).
+These are only two prominent problems, and there exist many other subtle ambiguities (e.g.
+terms overlap or are related in meaning).
+
+Compared to detecting concepts in text as illustrated in Fig.~\ref{fig:detecting_concepts}, solutions to the problem of detecting concepts in queries are different in the usage of features: Keywords are also matched and disambiguated against a thesaurus.
+However, there is no syntactic information such as POS tags that can be exploited.
+
+The use of thesauri to deal with semantic ambiguities of words has long history and has been investigated as the problem of concept-based IR~\cite{DBLP:conf/sigir/Giger88}.
+Concept-based IR is especially needed in the biomedical domain due to the frequent presence of acronyms, homonyms and synonyms.
+For detecting the underlying concepts, many lexical resources that are abundantly available for this domain, such as the Online Dictionary of Abbreviations from MEDLINE, the MESH thesaurus and the Gene Ontology have been used~\cite{DBLP:conf/sigir/ZhongH06,DBLP:conf/trec/JelierSEWMSMK03}.
+The detected concepts are used to expand the query~\cite{DBLP:conf/sigir/QiuF93,DBLP:conf/trec/JelierSEWMSMK03}.
+Concept-based query expansion \cite{DBLP:conf/sigir/QiuF93} for instance, detects the concept behind the query, and performs selection and weighting of additional search terms directly based on this concept (instead of the query terms).
+This and other works in this area, were based on the use of thesauri that capture concepts and relationships.
+WordNet for instance, was use to represent concepts by WordNet synonym sets, and for expanding query terms by following WordNet links \cite{DBLP:conf/sigir/Voorhees93}.
+WordNet links (is-a in particular) were also used to disambiguate query terms and to choose their senses \cite{DBLP:conf/sigir/Voorhees94}.
+
+Recently, a technique based on the idea of relevance model has been proposed to recognize the concepts underlying the query, referred to as conceptual query modeling~\cite{DBLP:journals/ipm/MeijTRK10}.
+Instead of detecting the concepts based on a thesaurus, this approach retrieves the top pseudo-relevance feedback documents through an initial query run.
+Concept annotations associated with these documents are then used to construct the conceptual representation of the relevance model (the query).
+While OntoSearch~\cite{DBLP:conf/aaai/JiangT06} does not explicitly target the approximation of a relevance model, it follows a similar idea.
+Concepts captured by ontologies (seen as a semantic network of concepts) are used here.
+First, OntoSearch obtains a set of documents for the given query, and then uses the concepts associated with these documents as seeds to the semantic network.
+Through spreading activation, concepts that are semantically related to this seeds are inferred, and used to re-rank the documents.
+
+\subsection{Translating Keyword Queries} 
+%Instead of detecting concepts only, 
+%concept-based query expansion or aiming at a conceptual representation, 
+There are also proposals for mapping keyword queries to fully structured queries.
+In this case, not only concepts but also the entities and relations to which the query keywords may refer to, have to be recognized.
+The resulting semantics of query keywords, i.e.
+schema (concept and relation names) and data elements (entities) provides the basis for identifying the query intents, i.e.
+the keyword query interpretations.
+The assumption behind many approaches for query interpretation is that the intended query corresponds to a particular substructure in the semantic data or schema graph.
+However, relations may be not explicitly specified in the query, or are not sufficient to connect the detected entities and concepts.
+In this case, algorithms for graph traversal are used to find connecting paths.
+Query interpretations are then obtained by merging these paths, which are finally ranked and mapped to structured queries (i.e.
+concept, relation and entity names are mapped to query predicates and constants).
+While the common language used to query semantic data in RDF is SPARQL\footnote{\url{http://www.w3.org/TR/rdf-sparql-query/}} (basically, a language for expressing graph patterns), other (logic-based) formalisms have been used, i.e.
+recognized entities, classes and relations can be mapped to SPARQL queries~\cite{DBLP:conf/esws/DamljanovicAC10},
+conceptual graphs~\cite{DBLP:conf/aswc/CaoCT08}, logical formulas~\cite{DBLP:journals/dke/CimianoHHMS08} or XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
+An overview of this task is illustrated in Fig.~\ref{fig:inter_keywords}
+
+%For instance, entities and relations in the semantic data that are mentioned in the queries are identified and represented as XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}. 
+AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} is an example of systems supporting this kind of keyword query interpretation.
+It maintains a translation index, which can be conceived as a lexicon that returns all meanings for an individual keyword.
+Specifically, it returns schema concepts as well as schema paths matching the keywords.
+These keyword matches are then combined to enumerate all possible interpretations of the query.
+For RDF data, a top-k graph traversal algorithm has been proposed to efficiently compute all possible interpretations~\cite{DBLP:conf/icde/TranWRC09}.
+Here, keywords are interpreted as entities, classes or relations (called keyword matching elements), which are contained in the semantic data or semantic model.
+All possible paths between these keyword matching elements are computed online by traversing a query search space that is formed by combining the semantic data graph and the schema graph, and then merged to obtain interpretations, which cover all the query keywords.
+This keyword query interpretation is implemented by Hermes~\cite{DBLP:journals/ws/TranWH09}, and later, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}.
+TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} also applies a graph traversal algorithm.
+However, it does not compute possible queries (i.e.
+interpretations) but directly output answers.
+As the user types, TASTIER completes the query with answers that possibly match the intended information need.
+
+\begin{figure*}[htb]
+	\centering
+  \subfloat[Translating keyword queries.]{\label{fig:inter_keywords}\includegraphics[width=0.34\textwidth]{figs/keywordinterpretation}}
+  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc. (or a blank line to force the subfig onto a new line)
+  \subfloat[Translating NL queries.]{\label{fig:inter_NL}\includegraphics[width=0.6\textwidth]{figs/nlinterpretation}}
+ \caption{Translating keywords and NL queries.}
+ \label{fig:translation}
+\end{figure*}
+
+\subsection{Translating NL Queries} There are two main categories of approaches for dealing with this problem.
+One the one hand, it can be tackled in a way similar to the translation of keyword queries.
+This solution (depicted in the bottom left portion of Fig.~\ref{fig:inter_NL}) involves the detection of concepts, entities, and relations~\cite{DBLP:conf/aswc/CaoCT08}, and their mapping to elements of structured queries.
+The problem of ambiguity is solved here by using robust techniques for the matching of words in the NL query against elements in the semantic data and semantic models, and for the ranking and disambiguation of resulting matches.
+In fact, this kind of approaches is particularly popular among domain-independent NL query translation systems.
+AquaLog~\cite{DBLP:journals/ws/LopezUMP07}) for instance, maps words in NL queries to elements in the semantic data, and disambiguates results using domain-independent lexical resources (e.g.
+WordNet).
+
+As depicted in Fig.~\ref{fig:inter_NL}, the other category of approaches involves the use of lexicons, often in combination with a syntactic analysis tools. 
+%Because NL questions also provide syntactic features, 
+In fact, the same text analysis tools used for document interpretation can be applied here.
+For instance, the Stanford Parser~\footnote{\url{http://nlp.stanford.edu/software/lex-parser.shtml}} and GATE~\footnote{\url{http://gate.ac.uk/}} are used by FREyA~\cite{DBLP:conf/esws/DamljanovicAC10} to identify concepts in NL questions and to derive the syntactic parse tree, respectively.
+The use of domain-specific lexicons provide is a common way to deal with ambiguities, especially for traditional NL translation systems that are focused on a particular domain.
+Basically, a lexicon captures the mappings from syntactic elements to semantic elements.
+For instance, ORAKEL uses a lexicon, which specifies the mappings between nouns (verbs) with their arguments identified through the syntactic analysis and concepts (relations) in the semantic models~\cite{DBLP:journals/dke/CimianoHHMS08}.
+These mappings are specified by lexicon engineers.
+A different lexicon is needed when porting the NL interface from one domain to one other.
+Aiming at reducing this upfront customization effort and domain independence, there are also systems that in the case of lexical ambiguities, ask users to provide mappings, and use them to train models (e.g.
+via reinforcement learning~\cite{DBLP:conf/esws/DamljanovicAC10}) that automatically compute mappings.
+
+%Instead of performing the syntactic parsing separately from the mapping of syntactic elements to semantic elements, these two steps have been also  in one pass, called semantic parsing.
+
+%While it has been reported~\cite{DBLP:journals/ws/LopezUMP07} that domain customization usually improves recall, many NL-based semantic search systems exploit general domain-independent lexical resources (e.g.
+WordNet is used by AquaLog~\cite{DBLP:journals/ws/LopezUMP07}) but do not require domain-specific lexicons.
+
+\subsection{Iterative Query Construction}
+
+The discussed query interpretation approaches 
+%deal with the interpretation of ambiguous queries that are expressed as NL or keywords. The 
+aim at a more precise understanding of the information need, represented as a structured query.
+This is also the objective of other related approaches that fall into the general category of query construction.
+For instance, faceted search~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/esws/HeimEZ10,DBLP:conf/semweb/FerreH11} as well as the other kind of iterative query interfaces based on visual manipulation (drag and drop)~\cite{DBLP:journals/ws/Harth10} as presented before, also belong to this general category.
+In these systems, user operations are directly mapped to changes in the query.
+For instance, adding and removing facets result in the addition (query expansion) and removal (query refinement) of query predicates, respectively.
+Clearly, the difference to work on keyword and NL query interpretation is the lack of ambiguity, i.e.
+the semantics of every user input is clear.
+
+\section{Matching}\label{sec:matching}
+% Table generated by Excel2LaTeX from sheet 'Tabelle1'
+\begin{table}[htbp]
+  \centering
+  \caption{Overview of matching approaches.}
+    \begin{tabular}{|p{2.2cm}|p{2.7cm}|p{2.5cm}|}
+    \hline
+    \textbf{Term} & \textbf{Structure} & \textbf{Semantic} \bigstrut\\
+    \hline
+    \hline
+    Syntactic similarity & Graph pattern matching  & Logic-based inferencing \bigstrut\\
+    \hline
+    Semantic similarity & Graph traversal, spreading activation & Mathematical/statistical models\bigstrut\\
+    \hline
+    \end{tabular}%
+  \label{tab:matching}%
+\end{table}%
+
+Which kind of matchings is needed depends on the query given as input. This could be either directly the query input provided the user, or input preprocessed via query interpretation. 
+The differences in inputs between term matching, structure matching and graph traversal are illustrated in Fig.~\ref{fig:matching}.
+We can see that term matching and graph traversal are particularly needed when the query is keyword-based.
+Whereas document retrieval or entity retrieval in general, can be solved through term matching, relational search requires graph traversal for finding connections between keywords.
+Likewise, graph traversal is also useful for finding connection between elements, which have been recognized in the keywords through the preprocessing step of keyword interpretation.
+Structure matching is only possible when the keyword has been fully translated to a structured query.
+An overview of matching techniques is presented in Table~\ref{tab:matching}.
+
+\subsection{Term Matching} 
+%\subsubsection{Term- / Content-based Matching}
+This matching is needed when the representation of query or data is based on terms (i.e.
+is a bag of words).
+This is the case with all the existing concept-based document retrieval solutions~\cite{DBLP:conf/sigir/Giger88,DBLP:conf/sigir/ZhongH06,DBLP:conf/trec/JelierSEWMSMK03,DBLP:conf/sigir/QiuF93,DBLP:conf/sigir/QiuF93,DBLP:conf/sigir/Voorhees93,DBLP:conf/sigir/Voorhees94,DBLP:journals/ipm/MeijTRK10}, which identify the concepts behind the query and document but however, only use them for query or document expansion (i.e.
+expand the term-based query / document representation with additional terms corresponding to the identified concepts).
+Likewise, there are approaches, which interpret the query as entities and relations and use this understanding to expand the query with corresponding terms~\cite{DBLP:series/sci/NgoC10}.
+That is, instead of concept-based, entity- and relation-based query expansions are applied.
+In all cases, the resulting query is still a bag of words.
+
+Many semantic data retrieval systems such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} also employ bag-of-words representations -- at the query and sometime, also at the level of semantic data.
+For instance, Sindice\footnote{\url{http://sindice.com/}}, the inverted index implementation behind Sig.ma, supports keyword queries on entity descriptions that essentially, are indexed as bag-of-words just like unstructured documents.
+In this case, the semantics available in the data are not taken into account during the matching (but may have been used in other steps such as query interpretation, e.g.
+for concept-based query expansion as discussed).
+
+Matching here boils down to the standard IR retrieval problem.
+Namely, given a set of keywords, bag-of-words models of the data matching individual keywords are retrieved.
+Besides document retrieval style ranking of results, most IR engines employed by semantic search systems for this task (e.g.
+Falcons and SemSearchPro use Apache Lucene\footnote{\url{http://lucene.apache.org/core/}}) supports fuzzy term matching such that syntactically similar terms can also be recognized as matches.
+Besides, systems such as SemSearchPro uses a lexical model such as WordNet in additional, to find also lexical variants that match in terms of meaning.
+This technique is similar to the use of lexical resources for concept detection during document and query interpretation.
+After matches are identified for every query term, they are joined (or combined via union) to obtain those, which match all (some) query keywords (AND- vs.
+OR-semantics).
+%This matching goes beyond the term-level to consider the content, which may contain several mentions of the query terms, as well as mentions of terms that do not appear in the query.
+At this content level, results may differ in the degree of matching, an aspect that is dealt with during the ranking.
+
+\subsection{Matching Complete Structure Patterns (Structure Matching)} 
+	This matching is possible when the query and document are interpreted or are directly available as a structured query and semantic data, respectively.
+That is, the semantics of both the query and data is represented in terms of some entities and their relations.
+Most frequent is the combination SPARQL queries and RDF data.
+In particular, the three common types of information needs discussed previously can be captured through the basic graph pattern (BGP) feature of SPARQL.
+
+	Just like semantic data, a BGP forms a graph where nodes and edges are either constants or variables (e.g.
+the structured query shown in Fig.~\ref{fig:matching}).
+Through explicitly specified join variables, edges of the BGP become connected.
+However, edges in the BGP are not required to be connected such that basically, a BGP can be seen as a set of connected components.
+Results obtained for every connected component are finally combined via union.
+Through join variables, the query engine knows how to combine intermediate results obtained for edges in every connected component, i.e.
+for combining results obtained for triple patterns in the BGP.
+
+	In fact, matching BGPs against semantic data boils down to the task of \emph{graph pattern matching} where constants in the BGP are matched against elements in the RDF data graph to find matching subgraphs that contain bindings to variables in the BGP.
+For processing these BGPs, the underlying engine leverages standard database query evaluation techniques, i.e.
+it precompiles the query to capture an optimal evaluation plan, then retrieves data (from optimized, compressed indexes) for each triple pattern and joins intermediate results according to the plan.
+This processing is supported by off-the-shelf triple stores such as Virtuoso\dtr{footnote} and Sesame\dtr{footnote}.
+For instance, a customized triple store is used by SemSearchPro~\cite{DBLP:journals/ws/TranHL11} for computing results for SPARQL queries, after they have been derived from keywords through query interpretation.
+
+	\subsection{Matching Incomplete Structure Patterns (Graph Traversal)} The graph pattern matching technique discussed previously assumes that the structured query pattern is complete, i.e.
+it simply combines results via union when there are no join variables.
+As opposed to that, the lack of join variables may indicate missing connections.
+That is, the structured query pattern might be incomplete such that some connections between query elements are not explicitly given.
+This is the case with relational search, when the relations are unknown and have to be searched for.
+In fact, keyword queries are mostly incomplete in that sense.
+Even when the users know the connecting relations, they may fail to capture them as keywords or simply omit them in the query.
+
+	Instead of applying the union when there are no join variables, graph traversal aims to combine partial results by exploring for different paths between them that form \emph{connecting subgraphs}.
+It uses the structure and semantics captured in the data to find hidden connections.
+This kind of matching has been used in different scenarios.
+As discussed, it has been applied to explore paths between keywords to translate a given keyword query to a structured query.
+Instead of query interpretation, there are also systems~\cite{DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}, which use the same graph traversal mechanism to directly evaluate the keyword query.
+They skip the computation of structured queries and directly explore for results in the data (subgraphs) that match the keywords.
+As opposed to standard IR-style keyword search on documents (i.e.
+document/entity search), the results here are semantic data graphs (i.e.
+relational search results).
+The keywords in the query do not refer to single documents but possibly, several entities that are connected through paths in the semantic data graph.
+Hence, simply joining results (documents), which match the query keywords is not sufficient.
+Entities matching keywords in the query have to be retrieved, and subgraphs containing paths, which connect these keyword matching entities have to be explored in the data through traversing graph nodes and edges.
+
+	The common semantics employed by graph traversal approaches for interpreting or directly evaluating keyword queries mentioned above, is based on \emph{minimality}.
+They search for minimal subgraphs that for each keyword, contains at least one matching node.
+A different semantics has been used for a hybrid search approach that operates on documents and semantic data~\cite{DBLP:conf/www/RochaSA04}.
+%	results do not have to cover those nodes matching the query keywords. 
+Instead of minimality, those parts of the data, which are interesting and thus, shall be explored and returned as results, are controlled through manually defined traversal constraints that are realized via \emph{spreading activation}, a kind of graph traversal that is performed according to activation levels of nodes.
+In a similar hybrid search setting,
+%Another application of graph traversal has been proposed for the combined scenario of document and data retrieval. The goal is 
+spreading activation has been used to find entities in semantic data, which are related to the documents to be retrieved, or vice versa, to retrieve documents related to some given entities.
+The starting points here are thus documents or entities, and traversal from these points are controlled through spreading activation~\cite{DBLP:conf/esws/SchumacherSS08}.
+
+We note that graph traversal has also been applied in the structured query setting to deal with cases, where relations (paths) are unknown.
+For instance, the graph traversal algorithm used by SemSearchPro~\cite{DBLP:journals/ws/TranHL11,DBLP:conf/icde/TranWRC09}, a keyword search system, is similar to the one proposed for answering P-Queries~\cite{DBLP:conf/www/AnyanwuS03}, a special type of structured queries that ask for unknown semantic associations between entities.
+
+	\subsection{Inferencing} Strictly speaking, this is not a matching task but a processing step performed either subsequent to or during the process of matching.
+Common to semantic search systems are the use of \emph{logic-based reasoning} and mathematical/statistical models of \emph{computation}.
+
+	Simple computation such as sorting and averaging are commonly applied to search results.
+Complex models for advanced analytics however, are only available in expert systems and data warehouses.
+With Wolfram Alpha, the use of of computational models based on statistical and mathematical formulas to derive further insights from the results has crossed the boundaries of specific domains to reach the mass of Web users.
+In fact, simple analytical processing has been available in popular Web search engines such as Google for a while.
+For instance, users can pose queries to convert from one currency to another.
+
+	The other type of inferencing based on the formal semantics of logic-based models such as OWL, has been more popular in semantic search research. 
+%	The formal well-defined semantics of some semantics models such as ontologies represented in OWL, have also be exploited for matching. More precisely, 
+It is used 
+%for \emph{reasoning} 
+to consider not only the available data but also facts that can be automatically inferred from the formal semantics.
+For instance, the semantic models used in Serene~\cite{DBLP:journals/ws/FazzingaGGL11} is an ontology Tbox represented as DL formulas, and semantic data are captured as Abox assertions of the same ontology.
+Serene uses an inference engine to derive new knowledge during an offline ontology compilation step.
+This computation is performed offline to improve the efficiency of online processing.
+%, but in principle, could also be done online during the matching. 
+New knowledge relevant for the query can also be derived online. 
+In ORAKEL for instance, the inference of new facts is performed as part of the computation of query matches.
+Notably, the first system created in the early years of Semantic Web research, which makes use of logical reasoning for computing semantic matches, is SHOE~\cite{DBLP:conf/dagstuhl/HeflinHL03}.
+
+%\subsection{Matching: Combination of Techniques}
+
+\section{Ranking}\label{sec:ranking}
+Ranking approaches leverage different factors, which in general, can be \emph{query-independent} or \emph{query-dependent}.
+The latter type considers the \emph{relevance} of the result with respect to the query.
+The former type includes different aspects, such as \emph{rarity} (measured in terms of occurrence~\cite{DBLP:journals/internet/Aleman-MezaHARS05}), \emph{popularity} (based on occurrences~\cite{DBLP:conf/icde/TranWRC09}, or centrality~\cite{DBLP:journals/internet/Aleman-MezaHARS05}), \emph{predictability} (based on information content~\cite{DBLP:conf/www/AnyanwuMS05}), \emph{trust} (e.g.
+trust values manually assigned to sources~\cite{DBLP:journals/internet/Aleman-MezaHARS05}) or \emph{confidence} (e.g.
+confidence scores of information extraction outputs~\cite{DBLP:conf/www/NieZWM05,DBLP:conf/vldb/ChengYC07}).
+They could be seen as heuristics, which can complement the ranking based on query-relevance.
+There are two prominent heuristics that are extensively studied and widely used in existing approaches, namely for \emph{centrality}- and \emph{proximity}-based ranking.
+
+% Table generated by Excel2LaTeX from sheet 'Tabelle2'
+\begin{table}[htbp]
+  \centering
+  \caption{Overview of centrality-based ranking.}
+    \begin{tabular}{|p{3.7cm}|p{3.4cm}|}
+    \hline
+    \textbf{Hyperlinks} & \textbf{Relations}  \bigstrut\\
+    \hline
+    \hline
+    Adoption of PageRank to (1) ontologies as Web pages, (2) two-layered graph with data sources (Web pages) representing one layer and source data the other & Authority transfer weights (1) specified by experts, (2) learned through simulated annealing or PARAFAC decomposition \bigstrut\\
+    \hline
+    \end{tabular}%
+  \label{tab:centrality}%
+\end{table}%
+
+\subsection{Centrality-based Ranking} An overview of centrality-based techniques is presented in Table~\ref{tab:centrality}.
+The algorithms commonly used for computing centrality in the context of ranking is PageRank and HITS.
+Basically, the underlying idea is to perform link analysis on the graph formed by the hyperlink structure of documents to identify nodes that are important (or popular or authoritative).
+
+In the semantic search context, much effort has been invested in extending the original PageRank and HITS proposals towards dealing with semantic data graphs, where instead of documents and hyperlinks, there are entities that are connected through different types of semantic links (i.e.
+relations).
+One of the first proposal for using PageRank for dealing with semantic data is OntoRank~\cite{DBLP:conf/semweb/DingPFJPK05}.
+However, ranking here is only dealt with at the level of sources, namely to rank ontologies instead of the entities contained in them.
+PageRank could be directly applied because ontologies are treated as Web pages, and there are no different types of links but only \verb+import+\footnote{An ontology imports another one to make uses of its content.} relations.
+Similar to this idea, semantic data sources have been considered as Web pages~\cite{DBLP:conf/esws/DelbruTCTD10,DBLP:conf/semweb/HarthKD09}.
+However, a two-layer approach has been pursuit here, where the PageRank scores computed for the datasets propagate to the entities contained in them~\cite{DBLP:conf/semweb/HarthKD09}.
+
+ObjectRank~\cite{DBLP:conf/vldb/BalminHP04} also builds upon PageRank, but recognizes the variety of semantic links.
+Instead of using the same authority flow for all edges, it employs an authority transfer schema graph, which captures the strengths of authority for different types of links.
+While all these weights have to be manually specified by domain experts in ObjectRank, PopRank~\cite{DBLP:conf/www/NieZWM05} incorporates a simulated annealing algorithm to learn the weights, based on a partial weighting provided by experts.
+A different direction for obtaining the weights of different types of links is taken by TripleRank, which models semantic data by means of a 3-dimensional tensor.
+Applying the PARAFAC decomposition (a multi-modal counterpart to HITS) to the tensor results in authority and hub scores for both the entities and links.
+
+Also worth mentioning, we have EntityAuthority~\cite{DBLP:conf/webdb/StoyanovichBBW07}, which operates not only on the semantic data graph but on a combined graph that contains both entities and documents as nodes.
+
+\subsection{Proximity-based Ranking} Another popular heuristic that has been successfully used in IR is the proximity between terms~\cite{DBLP:conf/sigir/ButtcherCL06a,DBLP:conf/sigir/TaoZ07}.
+According to this, a result is ranked high when it contains query terms that appear closer to each other in its textual content.
+This notion of proximity has also been used for XML data retrieval: XRank proposes to rank results based on the smallest text window, which contains all matches to query keywords~\cite{DBLP:conf/sigmod/GuoSBS03}.
+The notion of proximity has also been adopted to the case of semantic data, where instead of textual proximity (distance between terms), the distance between semantic entities is taken into account.
+For document retrieval, several proximity measures have been proposed to measure the distance between named entities extracted from text~\cite{DBLP:conf/iiwas/LeCHC11}.
+In keyword search over semantic data, results are subgraphs containing nodes matching the query keywords.
+One of the factor often used for ranking these results is based on the (pair-wise) distances between keyword matching nodes (the length of the paths connecting them)~\cite{DBLP:conf/cikm/LadwigT11,DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiJLF09}.
+Similar to text proximity, the intuition here is that more compact results more likely correspond to the intended need.
+Note that while it is not independent of the query, this heuristic does not directly capture the query-relevance.
+
+% Table generated by Excel2LaTeX from sheet 'Tabelle3'
+\begin{table}[htbp]
+  \centering
+  \caption{Overview of query-relevance based ranking.}
+    \begin{tabular}{|p{3.2cm}|p{3.8cm}|}
+    \hline
+    \textbf{Content} & \textbf{Structure} / \textbf{Semantics}  \bigstrut\\
+    \hline
+    \hline
+    Treat entities as documents and adopt (1) vector space model (2) unstructured LM & (1) BM25F, (2) structured LM for results, (3) for both query and results, (4) triple-based LM \bigstrut\\
+    \hline
+    \end{tabular}%
+  \label{tab:queryrelevance}%
+\end{table}%
+
+\subsection{Query-Relevance Based Ranking} An overview of centrality-based techniques is presented in Table~\ref{tab:queryrelevance}.
+Given the ambiguous query, and given we know the query intent, results can be distinguished in the degree of relevance w.r.t.~intent.
+Finding the query intent (i.e.
+the query-relevance) and ranking results based on relevance represent a classic problem in IR.
+In the semantic search setting, existing IR concepts proposed for that have been used and extended to deal with semantic data and to leverage the availability of semantics.
+
+Many semantic search systems, which provide keyword search over semantic data, apply standard IR ranking.
+For instance, Falcons~\cite{DBLP:journals/ijswis/ChengQ09} uses a standard IR tool (Lucene) to index entities as documents, and uses the built-in ranking mechanism (TFIDF-based) for entity ranking.
+
+For ranking more complex (relational search) results, there are keyword search systems, which adopt the vector space model and \emph{TFIDF-based} term weighting.
+The result in this setting is actually a graph, which is simply conceived a set of keyword matching nodes.
+A popular ranking scheme is based on the sum of the individual TF-IDF score computed via pivoted normalization weighting for every keyword matching node~\cite{DBLP:conf/icde/TranWRC09}.
+Specific normalization methods have proposed to recognize that the textual length of the matching nodes (i.e.
+entity descriptions instead of textual documents) is often very short (e.g.
+document length normalization), different attributes actually represent different vocabularies (e.g.
+IDF normalization) and a result is actually an ``aggregation of documents'' and thus, requires additional normalization beyond the document level~\cite{DBLP:conf/sigmod/LiuYMC06}.
+Also, TFIDF has been adopted for the case of document retrieval using semantic data.
+Here, the TFIDF weighting has to be modified to consider not only the frequency of terms but also the frequency of named entities~\cite{DBLP:series/sci/NgoC10} and annotations~\cite{DBLP:journals/tkde/CastellsFV07}.
+
+Taking the specific semantics of entity results into account, an extension of the \emph{BM25F} has been proposed~\cite{DBLP:conf/semweb/BlancoMV11}.
+The idea here is to use different fields for indexing different attributes of entities.
+Different weights are assigned to these fields to recognize that some attributes are more important than others in ranking entities.
+
+Also, the \emph{language modeling} (LM) approach has been adapted to the case of ranking complex results.
+Language models for documents and queries are employed to represent them as multinomial distributions over words of a vocabulary.
+The KL-divergence, basically measuring the distance between the query and document distributions, can then be used for ranking.
+For ranking structured objects, three different models were studies~\cite{DBLP:conf/www/NieMSWM07}: The simple unstructured model treats all object attributes and values as vocabulary terms.
+The structured variant employs language models for specific components of the structured results.
+The record-level representation models an object through several language models, each capturing a record of that object (an object here is the output of merging several records).
+The attribute-level representation further segments a record into multiple fields and assigns different weights to individual fields (similar to the idea behind BM25F).
+%Similarly, a hierarchical view has been taken for the language modeling and ranking of entity search results: An entity can be decomposed into property groups consisting of individual properties.
+Each property is a distribution over terms.
+Moreover, specific term distributions for fields have been used for modeling results as well as queries.
+The query is modeled based on pseudo-relevance feedback results obtained from an initial query run, called the edge-specific relevance model~\cite{DBLP:conf/cikm/BicerTN11}.
+Similarly, the probability of observing a word in a structured result may vary, depending on the attribute (the edge) to be considered.
+This is captured by the edge-specific result model.
 %
-%Apart from these main aspects, semantic search systems can also be distinguished in terms of the notion of semantics that is employed for search.  
-%
-%\subsection{Semantic Models}
-%Generally, semantics is concerned with the meaning of things.
-Meaning is established through a semantic model, which commonly captures interrelationships between elements and their interpretations.
-Various semantic models have been proposed and
-%used in different research communities. The IR community typically relies on \textit{linguistic
-%models} such as taxonomies and thesauri that capture relations between syntactical elements, i.e. words. In
-%the database community, \textit{conceptual models} such as Entity Relationship (ER)
-%diagrams are used to capture relations between entities
-%\cite{DBLP:journals/tods/Chen76}.
-Thus, while linguistic models are concerned with meanings at the level of words, conceptual models more specifically deal with meanings at the level of real-world entities denoted by words.
-That is, conceptual models deal with interpretation of words in terms of real world entities the words refer to.
-Besides ER diagrams, conceptual models include less formal models such as semantic networks [cite] and very formal models such as logic-based theories, where interpretations are precise and computable \cite{DBLP:books/sp/StaabS04}.
-% 
-%In the Semantic Web community, \textit{ontologies} have received widespread acceptance. The notion of
-%ontologies employed by this community is very general. Ontologies
-%constitute rather a family of models, which might differ in the
-%degree of expressiveness and formality, ranging from simple
-%taxonomies and shallow conceptual model represented in RDF(S)
-%to expressive formal models represented in Description Logics \cite{DBLP:books/sp/StaabS04}.
-Thus, ontologies include both linguistic and conceptual models.
-In practice, ontologies do not come only with the conceptual part but might also contain instances.
-In this sense, they are similar to databases (and knowledge bases) where the conceptual part corresponds to what is refer to as the schema (terminological knowledge) and instances correspond to the actual data of the database (assertional knowledge of the knowledge base).
-%
-%\subsection{Semantic Search}
-%As a general notion, a system essentially performs semantic search when a semantic model is employed.
-As illustrated in Fig.
-\ref{fig:semsearch}, a semantic model might be used to make sense of the data, to interpret the query and ultimately, to support matching that goes beyond the traditional term-based matching.
-%
-%\begin{figure}
-%	\centering
-%		\includegraphics[width=0.5\textwidth]{figs/semsearch.pdf}
-%	\label{fig:semsearch}
-%	\caption{Semantic Search}
-%\end{figure}
-%
-%\subsubsection{The DB\&KB Perspective}
-%In retrieving data, semantics has always play an essential role in database systems.
-The foundation of database technologies manifested in theoretical models such as the relational model that provides formal semantics to both resources and queries, i.e.
-the model behind relational data and relational query (an important part of SQL) is in fact a fragment of first-order logic [cite].
-This semantics is taken into account by database query engines to compute answers that precisely match the semantics of queries.
-More precisely, these engines perform binary matching that incorporates not only terms (i.e.
-constants) but also structure and semantics into account.
-Using this mechanism, information needs of different complexity have been served.
-In different commercial systems, we find the application of DB technologies in the form of simple product search (e.g.
-in commercial shopping sites like Ebay and Amazon) up to complex relational queries that are used to populate complex dynamic Web pages.
-%
-%While the relational model is the one most widely used in practice, there exists also domain specific solutions that are built upon more expressive models.
-In the realm of deductive databases for instance, semantics represented in languages such Datalog or F-Logic is used to perform reasoning, with the goal of understanding and delivering not only explicitly asserted information, but also inferred one.
-Further down this steam, semantic models that are even more expressive are used by knowledge-based expert systems for answering complex questions.
-[TODO: applications of expert systems]
-%
-%
-%\subsubsection{The IR Perspective}
-%In the IR community, the representation of the information needs as well as resources is achieved primarily using lightweight models that operates at the level of words.
-In particular, the predominant paradigm is based on keyword queries and bag-of-words representation of resources.
-This works and most importantly, scales well for topical search, i.e.
-to retrieve documents based on topics expressed in terms of keywords, but is not sufficient to address the kind of complex information needs that can be served by DB and KB systems.
-%
-%The need for going beyond the matching purely based on words and statistical dependencies that exist between them has been clearly expressed by leading researchers in the field.
-In the early years of IR research, Riksbergen clearly argue for the use of semantics.
-In order to return precise results to the user, it is essential to compute whether the resources semantically entail what the user ask for [cite].
-Quoting a paper from W.B.
-Croft et al.
-published more than twenty years ago [cite]: ``The statistical approach has many advantages and can achieve a reasonable level of effectiveness with techniques that are very efficient.
-However, it appears that to achieve significant improvements in retrieval effectiveness compared to current techniques, systems must be designed to acquire and use explicit domain knowledge''.
-This explicit domain knowledge are captured using semantic models of varying degrees.
-Semantic networks have been used augment the models based on terms.
-This provide a richer representation which is exploited for assisted query formulation, query expansion, as well as for relevance propagation in ranking [cite].
-Also, linguistic models particularly Wordnet and the Roget’s thesaurus have been widely used.
-%
-%Recently, the IR community continues to embrace the vast body of explicit knowledge that increasingly, is made publicly available.
-There are approaches which not only use semantic models to enrich terms, but in fact, employ both the conceptual and the data part.
-In particular, there are systems that use ontologies including the semantic data contained in them [cite].
-TODO: Applications: enterprise solutions such as IBM Avatar, Medline, Web solutions such as Hakia, Powerset.
-%
-%
-%\subsubsection{The SW Perspective}
-%Semantic search from the this point of view is more similar to the DB and KB perspective in the sense that the main goal is to obtain precise answers for complex questions.
-However, while DB and KB systems are adopted to solve specific problems of a particular domain, semantics is taken by this community to the wider context of the Web.
-Semantic models used here are ontologies available in the W3C languages for resource description, namely RDF and OWL.
-%, while SPARQL is the primary mean to express information needs.
-%On the Semantic Web, there is more data that is more hetetorogenous, i.e.
-data coming from different sources that differs in syntax, formats and quality.
-Thus, unlike traditional DB and KB systems, SW search engine are built with particular emphasis on the ability to scale in terms of both volume and the number of sources, to be domain independent and to perform ranking.
-%
-%To achieve this, they are built upon concepts and technologies from database and expert systems.
-General concepts for data management (e.g.
-indexing and data partitioning []) as well as specific concepts for managing graph structured data and graph databases (e.g.
-structure indexes from XML databases []) have been adopted to deal with ontologies and semantic data available in RDF and OWL.
-For dealing with more expressive semantic models, techniques commonly applied in deductive databases (e.g.
-magic set optimizations [cite]) have been adopted to improve the efficiency and scalability of reasoning.
-However, to deal with scale and to perform ranking, techniques that are more commonly used by the IR technology has also been adopted.
-For instance, the inverted index has been used to scale to a large amount of data and to support term-based matching.
-Statistical dependencies of words such TF-IDF as well as authority-based metrics such as PageRank that is popular in IR web search engines, have been used for ranking.
-%
-%TODO: Applications
-%
-%
-%
-%To summarize, semantics has proven to be useful for search in many aspects.
-There are commercial exploitations, which used semantics in different ways.
-Thus, the notion of semantic search is thus very broad.
-Semantic search covers the wide range of systems employing and exploiting semantic models of varying expressiveness.
-In the following sections, we will focus on semantic search systems driven by the IR and the SW communities which recently, have attracted much research and commercial interests.
+%s are employed not only to exploit the structure and semantics in the data but also to capture the semantics behind the keyword query.
+For this, an initial run over the semantic data is performed to obtain pseudo-relevance feedback (PRF) results for the keyword query.
+%This approach is proposed to deal short and ambiguous keyword query, an edge-specific model constructed from these PRF results is used to capture the information need (the relevance).
+
+As opposed to the approaches mentioned before, which model queries and documents based on words, there are also language models defined as probability distributions over RDF triples~\cite{DBLP:journals/debu/ElbassuoniRSW10}.
+The probability of a given triple should capture its ``informativeness'', which is measured based on a notion called witness counts.
+The authors implement this by issuing keyword queries derived for each triple against Web search engines, and using the reported result sizes as witness count estimates.
+Following the same direction, NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} not only uses informativeness but also a measure of confidence to estimate parameters of the language models.
+
+\subsection{Ranking: Combination of Factors}
+The ranking implemented by a system is often a combination of factors.
+For instance, for searching entities detected from documents, EntityRank~\cite{DBLP:conf/vldb/ChengYC07} rank entities based on the popularity of documents they have been extracted from (computed via PageRank), the confidence of the extraction outputs, contextual constraints as well as the proximity among entities and words.
+For retrieving more complex objects (comprising multiple records) extracted from Web documents, experiments with Libra\footnote{\url{http://libra.msra.cn}} (a search engine for scientific literature) have shown that ranking can be improved when taking extraction confidences both at the record- and attribute-level into account~\cite{DBLP:conf/www/NieMSWM07}.
+Structured results (subgraphs) obtained from keyword search over semantic data are mostly ranked based on the PageRank of its constituent nodes, an aggregation of query-relevance scores obtained for individual nodes (records, entities) matching query keywords, and the proximity captured through the length of paths between nodes~\cite{DBLP:conf/icde/TranWRC09}.
+
+A robust and generic mechanism for combining these factors is \emph{learning to rank}.
+Given labeled examples, i.e.
+relevance judgments capturing which results are relevant, a learning to rank algorithm such as RankSVM can be used to learn the weights that control the influence of individual factors.
+For instance, RankSVM has been used to learn the optimal combination of query-independent factors in the entity search setting~\cite{DBLP:conf/eswc/Tran12}.
+In this study, the goal is to find out the factors, which determine the ranking of entities, given they do not distinguish in terms of query-relevance, i.e.
+they all are relevant.
+Besides centrality-based measures such as PageRank (and other ones derived from connectivity information in the RDF graph), also features external to the data such as Google n-gram statistics were considered.
+For relational keyword search over semantic data, TFIDF-based ranking scores obtained for individual nodes in the result graph as well as structure proximity scores derived from the result graph have been studied for learning to rank~\cite{DBLP:conf/cikm/CoffmanW11}.
+
+\section{Main Types of Approaches and Their Performances}\label{sec:approaches}	
+Semantic search has been investigated from different communities in different contexts.
+In the IR community, semantic search has mainly been viewed from the perspective of document retrieval.
+Here, classic \emph{concept}-based approaches based on the use of lexical models can be distinguished from more recent approaches that leverage document \emph{annotations} in the form of semantic data.
+Another line of research is \emph{entity} search, which has been studied in the context of entities extracted from Web pages, Wikipedia pages corresponding to entities, as well as entities captured by databases and semantic data sources.
+Another popular topic is keyword search over databases and semantic data, which is mainly about \emph{relational} information.
+Last but not least, the processing of NL queries over these semantic data entails specific challenges and opportunities, which has attracted interests from a specific community of researchers.
+We will now discuss these main types of approaches, several example systems, the ways they use semantics, as well as their reported performances.
+The classification of selected approaches into types is presented in Table~\ref{}.
+Further, Table~\ref{tab:examples} provides an overview of selected systems and their classification along the main aspects of semantic search discussed in this survey.
+
+% Table generated by Excel2LaTeX from sheet 'Tabelle5'
+\begin{table*}[htbp]
+  \centering
+  \caption{Classification of approaches into types.}
+    \begin{tabular}{|p{2cm}|p{1.5cm}|p{2cm}|p{1.5cm}|p{1.5cm}|p{2cm}|p{2cm}|p{1.5cm}|}
+    \hline
+    \multicolumn{1}{|c|}{\multirow{2}[4]{*}{Concept-based}} & \multicolumn{2}{c|}{Annotation-based} & \multicolumn{3}{c|}{Entity Search} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel.
+Keyword}} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel.
+NL}} \bigstrut\\
+\cline{2-6}    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{NL} & \multicolumn{1}{c|}{Keyword } & \multicolumn{1}{c|}{Document} & \multicolumn{1}{c|}{Wikipedia} & \multicolumn{1}{c|}{Semantic Data} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} \bigstrut\\
+    \hline
+    \hline
+    \cite{DBLP:conf/sigir/Giger88, DBLP:conf/esws/GiunchigliaKZ09, DBLP:conf/sigir/QiuF93, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/ZhouYTS06,  DBLP:journals/ws/JonquetLFCNMS11, DBLP:conf/trec/JelierSEWMSMK03, DBLP:conf/sigir/Voorhees93, DBLP:conf/sigir/Voorhees94, DBLP:journals/ipm/MeijTRK10} & \cite{DBLP:conf/sigir/Chu-CarrollPCFD06, DBLP:journals/tkde/CastellsFV07, DBLP:journals/ws/FernandezCLVCM11, tran2007expressive, DBLP:conf/cikm/Chu-CarrollP07} &  	  \cite{DBLP:journals/tkde/CastellsFV07, DBLP:conf/sigmod/KandoganKRVZ06, tran2007expressive, DBLP:conf/aaai/JiangT06, DBLP:series/sci/NgoC10, DBLP:conf/www/RochaSA04, DBLP:conf/esws/SchumacherSS08, DBLP:conf/www/GuhaMM03} & \cite{DBLP:journals/ipm/BalogAR09, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/sigir/Chu-CarrollPCFD06} & \cite{DBLP:journals/tois/BalogBR11, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/cikm/BronBR10, DBLP:conf/ecir/PehcevskiVT08} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/sigir/BastCSW07, DBLP:conf/semweb/BlancoMV11, DBLP:journals/ijswis/ChengQ09, DBLP:journals/ws/TummarelloCCDDD10, DBLP:conf/eswc/Tran12,DBLP:conf/www/NieMSWM07, DBLP:conf/www/NieZWM05} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/cikm/BicerTN11, DBLP:conf/cikm/CoffmanW11, DBLP:journals/debu/ElbassuoniRSW10, DBLP:journals/ws/TranWH09, DBLP:journals/ws/TranHL11, DBLP:conf/icde/KasneciSIRW08, DBLP:conf/sigmod/LiJLF09, DBLP:conf/cikm/LadwigT11} & \cite{DBLP:conf/aswc/CaoCT08, DBLP:journals/dke/CimianoHHMS08, DBLP:conf/esws/WangXZY07, DBLP:conf/esws/DamljanovicAC10, DBLP:journals/ws/LopezUMP07} \bigstrut\\
+    \hline
+    \end{tabular}%
+  \label{tab:approaches}%
+\end{table*}%
+
+\subsection{Concept-based Document Retrieval} This is the classic type of semantic search systems, which has been studied already in the early years of IR research.
+Researchers have recognized for a richer representation of the information needs and data that goes beyond the bag-of-words model.
+It became evident that constructing a full-fledge logic-based representation~\cite{DBLP:conf/sigir/Rijsbergen89} for queries and especially for documents is not practical.
+Thus, lightweight \emph{lexical models} have been employed to interpret the semantics of query and documents as concepts, and used within the standard bag-of-words IR paradigm (e.g.
+vector space model and language model).
+In fact, retrieval may be done based on concepts alone, i.e.
+using bag-of-concepts, or in the form of query and document expansion.
+In the latter case, bag-of-words model constitutes the basis while the conceptual understanding helps to refine or add more relevant words.
+
+There are \emph{no clear evidences} suggesting conceptual IR can outperform standard IR techniques.
+It has been shown that automatic query expansion in the large and diverse TREC collection using WordNet degrades performance.
+Even when concepts are selected by hand, it helps only when the query is an incomplete description of the need~\cite{DBLP:conf/sigir/Voorhees94}.
+More recently, it has been shown for the medical domain (TREC Genomics) that retrieval based on concepts alone could not outperform the standard baseline based on words~\cite{DBLP:conf/trec/TrieschniggKS06,DBLP:conf/trec/ZhouYTS06}.
+In another experiment, the combination of concepts and bag-of-words
+%in the form of query expansion, 
+outperforms a state-of-the-art baseline in one collection, and shows similar performances in other collections~\cite{DBLP:journals/ipm/MeijTRK10}. However, the experiments have been performed on 
+collections where documents have been manually annotated with concepts (domain-specific CLEF and TREC Genomics collections).
+
+\textbf{Examples:} The \emph{NCBO Resource Index}\footnote{\url{http://
+bioportal.bioontology.org/resources}}~\cite{DBLP:journals/ws/JonquetLFCNMS11} leverages the large amount of ontologies that exist in the biomedical domain.
+While some (of the 200 ontologies currently used) may capture more advanced semantics, they all are treated as lexical models consisting of connected concepts.
+Besides retrieval, concepts detected in documents are also used for concept-based iterative query construction and navigation, where similar to facets, users can add concepts to refine the queries and to browse documents along concepts, respectively.
+
+\subsection{Annotation-based Document Retrieval} This encompasses the newer type of approaches, which exploit advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as annotations (query and document annotations, respectively).
+This query interpretation has has been applied both to keywords~\cite{} and NL questions~\cite{}.
+That is, this category covers both keyword search and NL question answering over documents.
+
+To date, there exist only \emph{anecdotal evidences} for the merits of this type of systems. 
+The most conclusive result in this direction is based on experiments using the TREC Question Answering track: For a subset of queries, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
+The results there can also be interpreted as follows: The employed information extraction programs were optimized for a few specific types of relations and entities (e.g.
+\verb+Person+).
+High precision is possible for queries that can be covered by these types of annotations, i.e.
+they ask for information that matches these annotations.
+However, high recall is difficult because it requires the information extraction program to recognize arbitrary types of entities and relations.
+As discussed in the document interpretation part, there are promising ideas towards this kind of open information extraction.
+However, obtaining high quality results is still a problem that poses many challenges.
+Along this line, there is a study showing that the quality of information extractions significantly impacts semantic search performance~\cite{DBLP:conf/cikm/Chu-CarrollP07}.
+
+\textbf{Example:}
+IBM Avatar, WATSON, question answering ~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}
+
+\subsection{Entity Search} While the two mentioned types retrieve documents, this type of approaches search for entities representing real-world objects (anything objects but documents).
+It includes search over (1) documents (e.g.
+for processing entity-related factoid and list queries of the TREC Question Answering track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or expert search queries of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}), \dtr{todo: A particular type of entity search, expert retrieval has been the focus of a number of evaluations; also belong to the type of entity search that mainly operates on documents; + some other features?.} (2) over
+%documents associated with metadata, (for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), 
+%over (3) 
+Wikipedia data, which as discussed, can be seen as a kind of semantic data (e.g.
+for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), or over pure (3) semantic data crawled from the Web (e.g.
+for answering entity queries of the SemSearch Entity track~\cite{DBLP:conf/semweb/BlancoMV11}).
+
+Some type(1) systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}.
+However, they go standard beyond document retrieval to locate the parts (passages) in the documents that contain answers to the query.
+As mentioned in the previous Subsection, the work from IBM~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} showed that precision can be improved when high quality extraction outputs are available.
+
+The use of semantics in type(2) systems is limited to viewing Wikipedia pages as entities~\cite{DBLP:conf/cikm/KapteinSVK10}, exploiting categories associated with them~\cite{DBLP:journals/tois/BalogBR11} as well as links between them~\cite{DBLP:conf/ecir/PehcevskiVT08}.
+As a source of semantics, experiments have shown that category information helps to interpret the entity query and to enrich the Wikipedia documents and as a result, to outperform standard text-based retrieval~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:journals/tois/BalogBR11}.
+Interestingly,
+%it has been shown that 
+Wikipedia articles can also be effectively used as a pivot for entity search on the Web, i.e.
+not only for answering queries about Wikipedia entities: It contains entities for a large amount of queries as well as cues (e.g.
+external links), which can be used to find the homepages of entities on the Web, which are referred to by Wikipedia articles~\cite{DBLP:conf/cikm/KapteinSVK10}.
+
+While many type(3) systems~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/HoganHUKPD11,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09} have been built to search for entities over semantic data from the Web, solutions for ranking and the evaluation of their results have attracted interest only recently.
+The first systems (e.g.
+Falcons) simply used an underlying IR engine (Lucene) to index entities as documents and the built-in mechanism to rank entities.
+Recently, the SemSearch challenge attracted a large number of participants, which submitted results produced by different ranking schemes based on traditional IR concepts.
+To date, the best performed method~\cite{DBLP:conf/semweb/BlancoMV11} uses an adoption of BM25F.
+%, which ranks entities as documents that are segmented into different fields corresponding to entity attributes.
+
+\textbf{Example:}
+Ask Gianluca, Sig.ma~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, Yahoo!, EntityCube
+
+\subsection{Relational Keyword Search}
+This category comprises all approaches, which process keyword queries over semantic data~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}.
+While the results here include entities, the focus is to find possibly complex subgraphs encompassing several entities and relations between them (i.e.
+to support relational search).
+There exists a variety of indexing strategies and traversal algorithms that help to perform this task more efficiently.
+However, recent work~\cite{DBLP:conf/cikm/CoffmanW10} has shown that the proposed ranking strategies (e.g.
+~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiuYMC06}) based on the adoption of proximity, TFIDF and PageRank do not perform well when considering a broad range of queries.
+This work aims at a standardized framework and benchmark for evaluating the effectiveness of relational keyword search approaches.
+Based on this benchmark, it has been shown that high quality results can be achieved through the use of edge-specific language models that are constructed for results and queries~\cite{DBLP:conf/cikm/BicerTN11}.
+Also, the learning to rank strategy, which combines TFIDF-based ranking, proximity and other factors yields high performance~\cite{DBLP:conf/cikm/CoffmanW11}.
+
+\subsection{Relational NL Search} \dtr{are there benchmarks for NL QA over data?}
+
+\textbf{Example:}
+Ask Gianluca, Sig.ma~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, Yahoo!
+
+Possibly, the most conclusive result in this direction is based on experiments using the TREC Question Answering track: For a subset of manually chosen questions, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
+
+% Table generated by Excel2LaTeX from sheet 'Tabelle1'
+\begin{table*}[htbp]
+  \centering
+  \caption{Classification of systems into aspects.}
+    \begin{tabular}{rrcccccccccccccc}
+    \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Concept} & \multicolumn{2}{c}{Annotation} & \multicolumn{5}{c}{Entity}            & \multicolumn{3}{c}{Rel.
+Keyword} & \multicolumn{2}{c}{Rel.
+NL} & \\
+    \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & NCBO  & C-S.  & Avatar & Aqua* & Exp   & Falc. & Sig.  & Yah.! & E.Cube & S.Pro & Naga  & TAST. & Aqua. & Nalix \\
+    \multicolumn{1}{l}{\multirow{3}[0]{*}{Need}} & \multicolumn{1}{l}{Document} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Entity} &       &       &       &       &       & X     & X     & X     &       &       & X     &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relation} &       &       &       &       &       &       &       &       &       &       & X     &       &       &  \\
+    \multicolumn{1}{l}{\multirow{4}[0]{*}{Querying}} & \multicolumn{1}{l}{Keyword} & X     &       &       &       &       & X     & X     & X     &       &       & ?     &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{NL} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Facet} & X     &       &       &       &       &       & ?     & X     &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Iterative} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{\multirow{3}[0]{*}{Data}} & \multicolumn{1}{l}{Text} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Sem. Data} &       &       &       &       &       & X     &       & X     &       &       & X     &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Metadata} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{\multirow{2}[0]{*}{Sem. Model}} & \multicolumn{1}{l}{Lexical} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Knowledge} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{\multirow{3}[0]{*}{Content Int.}} & \multicolumn{1}{l}{Concept} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Entity} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relation} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{\multirow{3}[0]{*}{Query Int.}} & \multicolumn{1}{l}{Concept} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Entity} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relation} &       &       &       &       &       &       &       &       &       &       & ?     &       &       &  \\
+    \multicolumn{1}{l}{\multirow{4}[0]{*}{Matching}} & \multicolumn{1}{l}{Term} & X     &       &       &       &       & X     &       & X     &       &       & ?     &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Structure } &       &       &       &       &       &       &       &       &       &       & ?     &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Traversal} &       &       &       &       &       &       &       &       &       &       & ?     &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Inference} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{\multirow{3}[0]{*}{Ranking}} & \multicolumn{1}{l}{Centrality} &       &       &       &       &       &       &       & ?     &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Proximity} &       &       &       &       &       &       &       & ?     &       &       &       &       &       &  \\
+    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relevance} & X     &       &       &       &       & X     &       & X     &       &       & ?     &       &       &  \\
+    \end{tabular}%
+  \label{tab:examples}%
+\end{table*}%

### 2012-04-09 trunk/tr-semanticsearchsurvey-data/intro.tex

@@
 Often, this is aggravated by the bias toward a single popular answer.
-For example, when searching for 'George Bush', the top results are crowded by references to the same person, even though this is a common name.
-\footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}.
+For example, when searching for 'George Bush', the top results are crowded by references to the same person, even though this is a common name.\footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}
 
@@
 Different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and ~\ref{sec:semantics}.
-Then approaches are discussed along the subproblems of content interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}.
+Then approaches are discussed along the subproblems of data interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}.
 After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches}.

### 2012-04-09 tr-semanticsearchsurvey-data/overview.tex

@@
 Basically, semantic metadata is semantic data that captures information about the objects to be retrieved.
-Because it is clear from the context, these two terms are often used synonymously (in this work).
+Later, we also use the term \emph{documentation annotation} to refer to metadata created for text.
 Metadata include basic information about the objects such as \verb+author+ and the \verb+year+ it was published.
@@
 While they provide lower coverage, the quality of extracted outputs is higher compared to open information extraction tools, an aspect shown to be very influential in improving the precision of semantic search results~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}.
-Promising is the combined usage of targeted and open information extraction, a direction currently pursuit by Microsoft's EntityCube.
+Promising is the combined usage of targeted and open information extraction, a direction currently pursuit by Microsoft's EntityCube~\cite{DBLP:conf/www/ZhuNLZW09}.
 
@@
 Further, Table~\ref{tab:examples} provides an overview of selected systems and their classification along the main aspects of semantic search discussed in this survey.
+Since the technique used within the same system is similar for document and query interpretation, we omit this distinction in Table~\ref{tab:examples}.
+
+\dtr{Say what  systems do with respect to aspects}
 
@@
   \centering
-  \caption{Classification of approaches into types.}
+  \caption{Classification of selected approaches into types.}
     \begin{tabular}{|p{2cm}|p{1.5cm}|p{2cm}|p{1.5cm}|p{1.5cm}|p{2cm}|p{2cm}|p{1.5cm}|}
@@
 
-\textbf{Examples:} The \emph{NCBO Resource Index}\footnote{\url{http://
+\textbf{Examples:} While concepts may not directly help to improve relevance-based metrics such as precision and recall, there are many systems showing they can provide other benefits, such as for iterative concept-based query refinement or for browsing.
+These features are available with \emph{gopubmed} for instance.
+Targeting the same domain, the \emph{NCBO Resource Index}\footnote{\url{http://
 bioportal.bioontology.org/resources}}~\cite{DBLP:journals/ws/JonquetLFCNMS11} leverages the large amount of ontologies that exist in the biomedical domain.
@@
 Besides retrieval, concepts detected in documents are also used for concept-based iterative query construction and navigation, where similar to facets, users can add concepts to refine the queries and to browse documents along concepts, respectively.
-
-\subsection{Annotation-based Document Retrieval} This encompasses the newer type of approaches, which exploit advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as annotations (query and document annotations, respectively).
-This query interpretation has has been applied both to keywords~\cite{} and NL questions~\cite{}.
-That is, this category covers both keyword search and NL question answering over documents.
+Targeting the Web scenario, \emph{Hakia}\footnote{\url{http://hakia.com/}} (Hak) uses a cross-domain lexical model called the Commercial Ontology, which hierarchically organizes word senses at three different layers.
+Based on these concepts, Hakia interprets the content as ``knowledge bits'', and for efficiency reason, extracts and indexes all possible queries that can be constructed from them.
+The concepts and ontology are used for retrieval, for handling syntactic variants in keywords and NL queries (morphological variants, synonyms, generalization) in particular.
+
+\subsection{Annotation-based Document Retrieval} These approaches exploit the advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as annotations (query and document annotations, respectively).
+As shown in Table~\ref{tab:approaches}, this query interpretation has has been applied both to keywords and NL questions.
+%That is, this category covers both keyword search and NL question answering over documents.
 
@@
 
-\textbf{Example:}
-IBM Avatar, WATSON, question answering ~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}
+\textbf{Examples:}
+IBM's \emph{AVATAR}\footnote{now superseeded by SystemT, \url{http://www.almaden.ibm.com/cs/projects/avatar/}} (AVA), is an example of keyword search over documents, which uses UIMA for extracting annotations.
+It interprets keywords as a structure query, which is then processed against a database of annotations.
+As answers, the system does not return documents, but annotations representing information about entities and relations extracted from documents.
+In addition to annotations, other structured datasets (semantic data) can be used for search.
+\emph{Powerset} (PS) performs information extraction also to return information about entities and relations (to queries represented as keywords as well as NL).
+Its demo constructed for a subset of Wikipedia also returns pages as results.
+More focused towards the processing of complex NL inputs is Watson~\cite{DBLP:journals/aim/FerrucciBCFGKLMNPSW10} (J!).
+It targets the Jeopardy!
+quiz show, where the task is basically, to find factual answers related to entities, given the category and several clues.
+It is a complex system combining different techniques.
+The starting points are previous IBM works, the PIQUANT system for combining evidences~\cite{DBLP:conf/naacl/Chu-CarrollCPI03} and the GuruQA for using annotations~\cite{DBLP:conf/sigir/PragerBCR00,DBLP:conf/sigir/Chu-CarrollPCFD06} in question answering in particular.
+Besides question and content analysis to interpret the meaning in terms of entities and relations, the system also implements techniques not covered by this survey, such as corpus expansion (to identify and acquire sources of content on the Web, both unstructured Web documents as well semantic data such as YAGO) and question decomposition and classification (identify parts and types of questions that need special processing, e.g.
+a math question).
+Computing results requires merging partial evidences as well as their confidence values.
+Similar to learning to rank, a machine learning method is used for the combination.
+Watson also uses the semantics in some sources to perform reasoning, e.g.
+it exploits subsumption and
+disjointness in type taxonomies and applies geospatial and
+temporal reasoning. While geospatial reasoning is used
+to deal with spatial
+relations such as directionality, borders, and
+containment between geo-entities (e.g. when asked for an Asian city, then spatial containment
+provides evidence that Beijing is suitable, whereas Sydney is not), temporal reasoning helps to deal with 
+inconsistencies between dates in clues and answers.
 
@@
 It includes search over (1) documents (e.g.
-for processing entity-related factoid and list queries of the TREC Question Answering track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or expert search queries of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}), \dtr{todo: A particular type of entity search, expert retrieval has been the focus of a number of evaluations; also belong to the type of entity search that mainly operates on documents; + some other features?.} (2) over
+for processing entity-related factoid and list queries of the TREC Question Answering track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or expert search queries of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}),
+%\dtr{todo: A particular type of entity search, expert retrieval has been the focus of a number of evaluations; also belong to the type of entity search that mainly operates on documents; + some other features?.}
+(2) over 
 %documents associated with metadata, (for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), 
@@
 
-\textbf{Example:}
-Ask Gianluca, Sig.ma~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, Yahoo!, EntityCube
+\textbf{Examples:}
+Systems searching for entity related information extracted from documents include \emph{AVATAR}, \emph{Powerset} and \emph{Watson}.
+Targeting Wikipedia documents, \emph{SERWi}~\footnote{\url{http://godzilla.kbs.uni-hannover.de:8089/ER08Demo/}} (SER) runs on top of subsets used at INEX XER 2007 and 2008.
+It exploits category information treated as part of a knowledge model to interpret entity queries expressed as keywords, and returns a ranked list of entities represented by their Wikipedia pages.
+For the semantic data case, we have \emph{Sig.ma} as one representative system, which provides keyword querying capabilities over an index of semantic data sources.
+For query answering, it matches query terms against an inverted index of entity descriptions, presents the sources for which matches could be found, and also, allow users to approve or reject certain sources of information.
+As illustrated in Fig.~\ref{fig:screenshot_yahoo}, Yahoo!
+(Y!) also employs semantic data for entity search.
+It uses its own curated sources of semantic data (e.g.
+data about companies) to provide -- in addition to relevant Web pages -- specific information about the requested entity and links to related entities.
+Microsoft's \emph{EntityCube} (MS) extracts information from text~\cite{DBLP:conf/www/ZhuNLZW09} to support entity-related keyword queries over documents and extracted information.
+For every query, it displays matching documents and entity information, and allows users to refine results based on facets representing related entities.
+As opposed to Yahoo!, which uses BM25F for ranking~\cite{DBLP:conf/semweb/BlancoMV11}, it uses language models for query-relevance~\cite{DBLP:conf/www/NieMSWM07} and also, PopRank for centrality-based ranking~\cite{DBLP:conf/www/NieZWM05}.
 
@@
 
+\textbf{Examples:} \emph{AVATAR} in fact, not only can search over annotations but any kinds of semantic data.
+The structured queries AVATAR obtains from keywords may also involve relational information.
+Another system is \emph{SemSearchPro} (SPro), which exploits semantics throughout the search process: It uses lexical and knowledge models as well as the semantic data to translate keyword queries to SPARQL queries (interpretation), to find connections between entities mentioned in the keyword query and for processing fully structured SPARQL queries (matching), and to rank results based on structure-based proximity, centrality and query-relevance (ranking).
+As illustrated in Fig.~\ref{fig:screenshot_iwb}, it also supports faceted search, and iterative query construction where users can iteratively build complexer queries by selecting suggested terms and query completions as they type.
+TASTIER~\footnote{\url{http://tastier.ics.uci.edu/}} also supports this auto-completion search, suggesting results as users type.
+The relational search demo is available for DBLP~\footnote{\url{http://dblp.ics.uci.edu/}}, a dataset containing information about entities in the bibliographic domain.
+
 \subsection{Relational NL Search} \dtr{are there benchmarks for NL QA over data?}
+As opposed to NL search over documents (mainly studied by IR researchers), this topic attracts a separate community that deals with interfaces over databases and knowledge bases (expert systems).
+NL search
 
@@
   \centering
-  \caption{Classification of systems into aspects.}
+  \caption{Classification of selected systems into aspects.}
     \begin{tabular}{rrcccccccccccccc}

### 2012-04-11 trunk/tr-semanticsearchsurvey-data/intro.tex

@@
 Then approaches are discussed along the subproblems of data interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}.
-After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches}.
-Main challenges derived from that and implications for future work are presented in Section~\ref{sec:challenges}, before we finally conclude in Section~\ref{sec:conclusion}.
+After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches},
+%Main challenges derived from that and implications for future work are presented in Section~\ref{sec:challenges}, 
+before we finally conclude in Section~\ref{sec:conclusion}.

### 2012-04-11 tr-semanticsearchsurvey-data/overview.tex

@@
 Last but not least, the processing of NL queries over these semantic data entails specific challenges and opportunities, which has attracted interests from a specific community of researchers.
-We will now discuss these main types of approaches, several example systems, the ways they use semantics, as well as their reported performances.
+
+Accordingly, we distinguish approaches into five main types, namely concept-based document retrieval, annotation-based document retrieval, entity search, relational keyword search and relational NL search.
+These types are introduced to represent main communities, which may overlap in some aspects such that some approaches may be classified to multiple types.
+For instance, an entity search system may use documents and annotations, which would also characterize it as annotation-based search.
+Most relational search systems also support entity search.
+
+We will now discuss these main types of approaches, several example systems, and their reported performances.
 The classification of selected approaches into types is presented in Table~\ref{}.
 Further, Table~\ref{tab:examples} provides an overview of selected systems and their classification along the main aspects of semantic search discussed in this survey.
-Since the technique used within the same system is similar for document and query interpretation, we omit this distinction in Table~\ref{tab:examples}.
-
-\dtr{Say what  systems do with respect to aspects}
+
+%Since the technique used within the same system is similar for document and query interpretation, we omit this distinction in Table~\ref{tab:examples}.
 
@@
     \hline
-    \cite{DBLP:conf/sigir/Giger88, DBLP:conf/esws/GiunchigliaKZ09, DBLP:conf/sigir/QiuF93, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/ZhouYTS06,  DBLP:journals/ws/JonquetLFCNMS11, DBLP:conf/trec/JelierSEWMSMK03, DBLP:conf/sigir/Voorhees93, DBLP:conf/sigir/Voorhees94, DBLP:journals/ipm/MeijTRK10} & \cite{DBLP:conf/sigir/Chu-CarrollPCFD06, DBLP:journals/tkde/CastellsFV07, DBLP:journals/ws/FernandezCLVCM11, tran2007expressive, DBLP:conf/cikm/Chu-CarrollP07} &  	  \cite{DBLP:journals/tkde/CastellsFV07, DBLP:conf/sigmod/KandoganKRVZ06, tran2007expressive, DBLP:conf/aaai/JiangT06, DBLP:series/sci/NgoC10, DBLP:conf/www/RochaSA04, DBLP:conf/esws/SchumacherSS08, DBLP:conf/www/GuhaMM03} & \cite{DBLP:journals/ipm/BalogAR09, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/sigir/Chu-CarrollPCFD06} & \cite{DBLP:journals/tois/BalogBR11, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/cikm/BronBR10, DBLP:conf/ecir/PehcevskiVT08} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/sigir/BastCSW07, DBLP:conf/semweb/BlancoMV11, DBLP:journals/ijswis/ChengQ09, DBLP:journals/ws/TummarelloCCDDD10, DBLP:conf/eswc/Tran12,DBLP:conf/www/NieMSWM07, DBLP:conf/www/NieZWM05} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/cikm/BicerTN11, DBLP:conf/cikm/CoffmanW11, DBLP:journals/debu/ElbassuoniRSW10, DBLP:journals/ws/TranWH09, DBLP:journals/ws/TranHL11, DBLP:conf/icde/KasneciSIRW08, DBLP:conf/sigmod/LiJLF09, DBLP:conf/cikm/LadwigT11} & \cite{DBLP:conf/aswc/CaoCT08, DBLP:journals/dke/CimianoHHMS08, DBLP:conf/esws/WangXZY07, DBLP:conf/esws/DamljanovicAC10, DBLP:journals/ws/LopezUMP07} \bigstrut\\
+    \cite{DBLP:conf/sigir/Giger88, DBLP:conf/esws/GiunchigliaKZ09, DBLP:conf/sigir/QiuF93, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/ZhouYTS06,  DBLP:journals/ws/JonquetLFCNMS11, DBLP:conf/trec/JelierSEWMSMK03, DBLP:conf/sigir/Voorhees93, DBLP:conf/sigir/Voorhees94, DBLP:journals/ipm/MeijTRK10} & \cite{DBLP:conf/sigir/Chu-CarrollPCFD06, DBLP:journals/tkde/CastellsFV07, DBLP:journals/ws/FernandezCLVCM11, tran2007expressive, DBLP:conf/cikm/Chu-CarrollP07} &  	  \cite{DBLP:journals/tkde/CastellsFV07, DBLP:conf/sigmod/KandoganKRVZ06, tran2007expressive, DBLP:conf/aaai/JiangT06, DBLP:series/sci/NgoC10, DBLP:conf/www/RochaSA04, DBLP:conf/esws/SchumacherSS08, DBLP:conf/www/GuhaMM03} & \cite{DBLP:journals/ipm/BalogAR09, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/sigir/Chu-CarrollPCFD06} & \cite{DBLP:journals/tois/BalogBR11, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/cikm/BronBR10, DBLP:conf/ecir/PehcevskiVT08} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/sigir/BastCSW07, DBLP:conf/semweb/BlancoMV11, DBLP:journals/ijswis/ChengQ09, DBLP:journals/ws/TummarelloCCDDD10, DBLP:conf/eswc/Tran12,DBLP:conf/www/NieMSWM07, DBLP:conf/www/NieZWM05} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/cikm/BicerTN11, DBLP:conf/cikm/CoffmanW11, DBLP:journals/debu/ElbassuoniRSW10, DBLP:journals/ws/TranWH09, DBLP:journals/ws/TranHL11, DBLP:conf/icde/KasneciSIRW08, DBLP:conf/sigmod/LiJLF09, DBLP:conf/cikm/LadwigT11} & \cite{DBLP:conf/aswc/CaoCT08, DBLP:journals/dke/CimianoHHMS08, DBLP:conf/esws/WangXZY07, DBLP:conf/esws/DamljanovicAC10, DBLP:journals/ws/LopezUMP07, DBLP:journals/tods/LiYJ07, DBLP:conf/iui/HanNPPL10} \bigstrut\\
     \hline
@@
 
-\subsection{Concept-based Document Retrieval} This is the classic type of semantic search systems, which has been studied already in the early years of IR research.
+\subsection{Concept-based Document Retrieval} 
+As indicated by example systems shown in Table~\ref{tab:examples}, this type supports keyword search over documents, and based on concepts interpreted from keywords and documents, it may also provide additional querying mechanisms such as as concept-based iterative query construction.
+In fact, this is the classic type of semantic search systems, which has been studied already in the early years of IR research.
 Researchers have recognized for a richer representation of the information needs and data that goes beyond the bag-of-words model.
@@
 
-\subsection{Annotation-based Document Retrieval} These approaches exploit the advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as annotations (query and document annotations, respectively).
+\subsection{Annotation-based Document Retrieval} These approaches exploit the advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as \emph{annotations} (query and document annotations, respectively).
 As shown in Table~\ref{tab:approaches}, this query interpretation has has been applied both to keywords and NL questions.
@@
 
-\subsection{Entity Search} While the two mentioned types retrieve documents, this type of approaches search for entities representing real-world objects (anything objects but documents).
+\subsection{Entity Search} While the two mentioned types retrieve documents, this type of approaches search for \emph{entities} representing real-world objects (anything but documents).
 It includes search over (1) documents (e.g.
@@
 
-Some type(1) systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}.
+Some \emph{type(1)} systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}.
 However, they go standard beyond document retrieval to locate the parts (passages) in the documents that contain answers to the query.
-As mentioned in the previous Subsection, the work from IBM~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} showed that precision can be improved when high quality extraction outputs are available.
-
-The use of semantics in type(2) systems is limited to viewing Wikipedia pages as entities~\cite{DBLP:conf/cikm/KapteinSVK10}, exploiting categories associated with them~\cite{DBLP:journals/tois/BalogBR11} as well as links between them~\cite{DBLP:conf/ecir/PehcevskiVT08}.
+As mentioned in the previous Subsection, the work from IBM~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} showed that precision can be very high when quality extraction outputs are available.
+
+The use of semantics in \emph{type(2)} systems is limited to viewing Wikipedia pages as entities~\cite{DBLP:conf/cikm/KapteinSVK10}, exploiting categories associated with them~\cite{DBLP:journals/tois/BalogBR11} as well as links between them~\cite{DBLP:conf/ecir/PehcevskiVT08}.
 As a source of semantics, experiments have shown that category information helps to interpret the entity query and to enrich the Wikipedia documents and as a result, to outperform standard text-based retrieval~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:journals/tois/BalogBR11}.
@@
 
-While many type(3) systems~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/HoganHUKPD11,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09} have been built to search for entities over semantic data from the Web, solutions for ranking and the evaluation of their results have attracted interest only recently.
+While many \emph{type(3)} systems~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/HoganHUKPD11,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09} have been built to search for entities over semantic data from the Web, solutions for ranking and the evaluation of their results have attracted interest only recently.
 The first systems (e.g.
@@
 For query answering, it matches query terms against an inverted index of entity descriptions, presents the sources for which matches could be found, and also, allow users to approve or reject certain sources of information.
-As illustrated in Fig.~\ref{fig:screenshot_yahoo}, Yahoo!
-(Y!) also employs semantic data for entity search.
+As illustrated in Fig.~\ref{fig:screenshot_yahoo}, \emph{Yahoo!} (Y!) also employs semantic data for entity search.
 It uses its own curated sources of semantic data (e.g.
@@
 \subsection{Relational Keyword Search}
-This category comprises all approaches, which process keyword queries over semantic data~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}.
+This category comprises all approaches, which process \emph{keyword queries over semantic data} (or structured data capturing entities and relations)~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}.
 While the results here include entities, the focus is to find possibly complex subgraphs encompassing several entities and relations between them (i.e.
@@
 There exists a variety of indexing strategies and traversal algorithms that help to perform this task more efficiently.
-However, recent work~\cite{DBLP:conf/cikm/CoffmanW10} has shown that the proposed ranking strategies (e.g.
+However, regarding result quality, recent work~\cite{DBLP:conf/cikm/CoffmanW10} has shown that the proposed ranking strategies (e.g.
 ~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiuYMC06}) based on the adoption of proximity, TFIDF and PageRank do not perform well when considering a broad range of queries.
@@
 As illustrated in Fig.~\ref{fig:screenshot_iwb}, it also supports faceted search, and iterative query construction where users can iteratively build complexer queries by selecting suggested terms and query completions as they type.
-TASTIER~\footnote{\url{http://tastier.ics.uci.edu/}} also supports this auto-completion search, suggesting results as users type.
+\emph{TASTIER}~\footnote{\url{http://tastier.ics.uci.edu/}} (TAST) also supports this auto-completion search, suggesting results as users type.
 The relational search demo is available for DBLP~\footnote{\url{http://dblp.ics.uci.edu/}}, a dataset containing information about entities in the bibliographic domain.
 
-\subsection{Relational NL Search} \dtr{are there benchmarks for NL QA over data?}
-As opposed to NL search over documents (mainly studied by IR researchers), this topic attracts a separate community that deals with interfaces over databases and knowledge bases (expert systems).
-NL search
-
-\textbf{Example:}
-Ask Gianluca, Sig.ma~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, Yahoo!
-
-Possibly, the most conclusive result in this direction is based on experiments using the TREC Question Answering track: For a subset of manually chosen questions, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
+\subsection{Relational NL Search} As opposed to NL search over documents, which is mainly studied by IR researchers, this topic attracts a separate community that deals with interfaces over databases and knowledge bases.
+The underlying problem is about \emph{searching over semantic data}.
+We refer to it as relational NL search because relations in the data have to be processed to answer complex queries, possibly asking for relations between several entities.
+Just like relational keyword search, this type targets the more general relational search scenario, i.e.
+it can handle the entity query case, while it is not necessarily optimized for it, as opposed to entity search systems.
+
+Traditionally, this query interface is used for expert systems targeting one particular domain.
+The question of portability, and the problem of building domain-independent search systems have attracted attention in the past few years~\cite{DBLP:conf/esws/WangXZY07,DBLP:journals/dke/CimianoHHMS08,DBLP:conf/aaai/LiCYSJ07}.
+While this problem of open-domain NL search, e.g.
+NL search NL over large amounts of heterogeneous Web data, seems to be largely unsolved, relatively good results have been reported for single domain tasks.
+However, while there is TREC-based evaluation for NL search over documents, there exists no such thing close to a standardized evaluation in this community.
+The performances reported by previous approaches are hardly comparable because different queries and datasets have been chosen for the experiments, e.g.
+experimental settings in recent works~\cite{DBLP:conf/esws/DamljanovicAC10,DBLP:conf/iui/HanNPPL10,DBLP:journals/tods/LiYJ07} differ.
+
+\textbf{Example:} \emph{NaLIX}~\cite{DBLP:journals/tods/LiYJ07} (NaL) is a system built by IBM researchers that was initially focused on one domain and then extended to \emph{DaNaLIX}~\cite{DBLP:conf/aaai/LiCYSJ07} to deal with multiple domains.
+It interprets a NL query by producing a parse tree and then maps its elements to structured queries via rules.
+These mapping rules are manually specified and additionally, can be derived from user feedbacks.
+\emph{Wolfram Alpha} (WolfA) also interprets NL inputs via rules.
+Its specialty is the ability of computing additional information from the data and results.
+\emph{True Knowledge} (TrueK) also makes use of reasoning for processing questions and computing results, geospatial and temporal in particular.
 
@@
   \caption{Classification of selected systems into aspects.}
-    \begin{tabular}{rrcccccccccccccc}
-    \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Concept} & \multicolumn{2}{c}{Annotation} & \multicolumn{5}{c}{Entity}            & \multicolumn{3}{c}{Rel.
-Keyword} & \multicolumn{2}{c}{Rel.
-NL} & \\
-    \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & NCBO  & C-S.  & Avatar & Aqua* & Exp   & Falc. & Sig.  & Yah.! & E.Cube & S.Pro & Naga  & TAST. & Aqua. & Nalix \\
-    \multicolumn{1}{l}{\multirow{3}[0]{*}{Need}} & \multicolumn{1}{l}{Document} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Entity} &       &       &       &       &       & X     & X     & X     &       &       & X     &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relation} &       &       &       &       &       &       &       &       &       &       & X     &       &       &  \\
-    \multicolumn{1}{l}{\multirow{4}[0]{*}{Querying}} & \multicolumn{1}{l}{Keyword} & X     &       &       &       &       & X     & X     & X     &       &       & ?     &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{NL} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Facet} & X     &       &       &       &       &       & ?     & X     &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Iterative} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{\multirow{3}[0]{*}{Data}} & \multicolumn{1}{l}{Text} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Sem. Data} &       &       &       &       &       & X     &       & X     &       &       & X     &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Metadata} & X     &       &       &       &       &       &       & X     &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{\multirow{2}[0]{*}{Sem. Model}} & \multicolumn{1}{l}{Lexical} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Knowledge} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{\multirow{3}[0]{*}{Content Int.}} & \multicolumn{1}{l}{Concept} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Entity} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relation} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{\multirow{3}[0]{*}{Query Int.}} & \multicolumn{1}{l}{Concept} & X     &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Entity} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relation} &       &       &       &       &       &       &       &       &       &       & ?     &       &       &  \\
-    \multicolumn{1}{l}{\multirow{4}[0]{*}{Matching}} & \multicolumn{1}{l}{Term} & X     &       &       &       &       & X     &       & X     &       &       & ?     &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Structure } &       &       &       &       &       &       &       &       &       &       & ?     &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Traversal} &       &       &       &       &       &       &       &       &       &       & ?     &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Inference} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{\multirow{3}[0]{*}{Ranking}} & \multicolumn{1}{l}{Centrality} &       &       &       &       &       &       &       & ?     &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Proximity} &       &       &       &       &       &       &       & ?     &       &       &       &       &       &  \\
-    \multicolumn{1}{l}{} & \multicolumn{1}{l}{Relevance} & X     &       &       &       &       & X     &       & X     &       &       & ?     &       &       &  \\
+    \begin{tabular}{|r|r||c|c|r|c|c|c|c|c|c|c|c|c|c|r|}
+    \hline
+    \multicolumn{1}{|c}{} & \multicolumn{1}{c||}{} & \multicolumn{2}{c|}{Concept} & \multicolumn{2}{c|}{Annotation} &       & \multicolumn{4}{c|}{Entity}   & \multicolumn{2}{c|}{Rel.
+Keyword} & \multicolumn{3}{c|}{Rel.
+NL}   \bigstrut\\
+\cline{3-16}    \multicolumn{1}{|c}{} & \multicolumn{1}{c||}{} & NCBO  & Hak   & \multicolumn{1}{c|}{AVA} & PS    & J!
+& SER   & Sig.
+& Y!
+& MS    & SPro  & TAST  & NaL   & WolfA & \multicolumn{1}{c|}{TrueK} \bigstrut\\
+    \hline
+    \hline
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Need}} & \multicolumn{1}{l||}{Document} & X     & X     & X     & X     &       & X     &       & X     & X     &       &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Entity} &       &       & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relation} &       &       & X     & X     &       &       &       &       &       & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{4}[8]{*}{Querying}} & \multicolumn{1}{l||}{Keyword} & X     & X     & X     & X     &       & X     & X     & X     & X     & X     & X     &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{NL} &       & X     &       & X     & X     &       &       &       &       &       &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Facet} & X     &       &       &       &       &       &       & X     & X     & X     &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Iterative} & X     &       &       &       &       &       &       &       &       & X     & X     &       &       &  \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Data}} & \multicolumn{1}{l||}{Text} & X     & X     &       & X     & X     & X     &       & X     & X     &       &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Sem.
+Data} &       &       & X     &       & X     & X     & X     &       &       & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Metadata} & X     & X     & X     & X     & X     &       &       & X     & X     &       &       &       &       &  \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{2}[4]{*}{Sem.
+Model}} & \multicolumn{1}{l||}{Lexical} & X     & X     &       &       & X     &       &       &       &       & X     &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Knowledge} &       &       &       &       & X     & X     &       &       &       & X     &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Data Int.}} & \multicolumn{1}{l||}{Concept} & X     & X     &       &       & X     &       &       &       &       &       &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Entity} &       &       & X     & X     & X     &       &       &       & X     &       &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relation} &       &       & X     & X     & X     &       &       &       & X     &       &       &       &       &  \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Query Int.}} & \multicolumn{1}{l||}{Concept} & X     & X     &       &       & X     &       &       &       &       & X     &       &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Entity} &       &       & X     & X     & X     & X     &       &       & X     & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relation} &       &       & X     & X     & X     &       &       &       &       & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{4}[8]{*}{Matching}} & \multicolumn{1}{l||}{Term} & X     & X     &       & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Structure } &       &       & X     & X     &       &       &       &       &       & X     &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Traversal} &       &       & X     &       &       &       &       &       &       & X     & X     &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Inference} &       &       &       &       & X     &       &       &       &       &       &       &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Ranking}} & \multicolumn{1}{l||}{Centrality} &       &       &       &       &       &       &       &       & X     & X     &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Proximity} &       &       &       &       &       &       &       &       &       & X     &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relevance} & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+    \hline
     \end{tabular}%

### 2012-04-11 tr-semanticsearchsurvey-data/intro.tex
Finished updating intro...

@@
 
-Modern search engines are efficient in retrieving documents (web pages in the case of web search) from large collections based on matching the text of the user's query with the textual content of the document or words in linking to the current document (\emph{anchortext}).
-These textual features are often combined with additional features that measure the popularity of results based on usage data (\emph{click-behaviour} or using metrics computed on the web graph such as \emph{PageRank} and its derivates.
+Modern search engines are efficient in retrieving documents (web pages in the case of web search) from large collections based on matching the text of the user's query with the textual content of the document or words in linking to the current document (\emph{anchor text}).
+These textual features are often combined with additional features that measure the popularity of results based on usage data (\emph{click-log data}) or using metrics computed on the web graph such as \emph{PageRank} and its derivates.
 In combination, these relatively simple, but scalable matching techniques are are able to address a large fraction of common information needs.
@@
 
-\subsection{Many Unsolved Long-tail Queries}
+\subsection{Unsolved Queries}
 
@@
 Queries for events naturally involve multiple entities, typically the participant in the event and a reference to another item, e.g.
-\emph{barrack obama birth certificate}.
+\emph{barack obama birth certificate}.
 %\end{itemize}
@@
 Many queries in the long tail are both ambiguous and complex.
-They require \emph{deep understanding} of the need and the information behind the query and data, respectively.
+They are characterized by the requirement for a \emph{higher level understanding} of the meaning of the query and data than the level of keywords.
+As we discuss later, some semantic search approaches use this higher level, conceptual understanding of queries and data to compose answers (via reasoning or computation) that do not even explicitly appear in the data.
 
-\subsection{Large Amount of Semantic Data}
-Targeting these problematic cases, there is a category of search solutions -- often referred to as semantic search solutions -- that aim at exploiting the large and increasing amount of semantic resources that have been made available in different settings.
+\subsection{Semantic Resources}
+
+While the above problems are not new, the renewed interest in trying to address them can be explained by the increasing availability of semantic resources in terms of large data sets and schemas.
+Many semantic search systems have emerged specifically to exploit these resources.
+Here we review the main trends that have led to this development, and we return to describe the types of semantic data in more detail in Section~\ref{sec:data}.
+
+Semantic annotations of documents are available in increasing amounts due to advances in both Information Extraction and the adoption of standard formats for annotating documents.
+The two developments are complementary in providing annotations for the Web.
+IE technology is particularly adept at extraction from large sites on the Web, where the investments in creating training data for supervised methods of learning extractors (e.g.
+wrapper induction) pay off quickly.
+On the other hand, publishers are increasingly motivated by search engine providers to provide explicit semantic annotations so that consumers do not need to apply extraction.
+Semantic annotations in this case are embedded inside HTML pages using standards such as RDFa (a W3C standard\footnote{http://www.w3.org/TR/xhtml-rdfa-primer/} for embedding RDF data in Web pages), microformats or microdata.
+The practice of annotating webpages using these formats have thus brought us closer to acquiring semantic annotations in the long tail of the Web.
+As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups such as RDFa~\cite{}.
+
+Complementary to these efforts, the Linking Open Data\footnote{\url{http://www.w3.org/wiki/SweoIG/TaskForces/CommunityProjects/LinkingOpenData}} movement that has emerged in recent years facilitated the process of publishing entire datasets (knowledge bases) on the Web.
+Large structured datasets that have been formerly kept in closed databases are now exposed as publicly Web-accessible RDF data (e.g.
+Linked Data\footnote{\url{http://linkeddata.org/}}).
+This method of publishing is often used in the area of the sciences and the government where data is in the public domain.
+Efforts are under way to link these datasets by establishing links (references between entities) in different datasets.
+Besides these domain specific datasets, broad encyclopedic knowledge bases such as Dbpedia and Freebase are now also available for research.
+These resources are particularly valuable for supporting open domain search and query answering.
+Altogether, the Linked Data cloud is estimated to contain over 40B triples \cite{}.
+
+When making data available on the Web, publishers can choose the schema to publish their data.
+Many of the Linked Data datasets reflect the internal schema of the database that is being exposed.
+However, in this case the burden is on the consumer of the data to make sense of the schemas of the individual datasets and map them to a shared, global schema before being able to aggregate data.
+This type of schema matching is difficult and can not be fully automated in practice.
+A better approach is for publishers and consumers to agree on a shared schema and reuse that schema whenever possible.
+A recent example of this effort is the schema.org collaboration between the main search engine providers (currently, Bing, Google, Yahoo and Yandex).
+Schema.org provides a set of schemas for common types of objects on the Web, such as places, people, organizations, reviews, recipes etc.
+
+The Semantic Web movement catalyzed the above developments by establishing a basic knowledge representation paradigm (RDF)\footnote{RDF stands for Resource Description Framework, a W3C Semantic Web standard for data representation and exchange on the Web: \url{http://www.w3.org/RDF/}}.
+RDF is flexible enough to capture any data that can be represented as a graph and has a number of serialization formats.
+RDF is commonly used to publish and manipulate semantic resources and is supported by a growing range of tools and APIs in various programming languages.
+In particular, the so called 'triple stores' that provide storage for RDF data have matured over the years and scale to several hundreds of millions triples (facts) on single machines.
+(Triple stores, however, do not provide the kind of retrieval functionality described in this paper.) Another Semantic Web standard, the Web Ontology Language (OWL) has standardized the way in which schemas are shared on the Web.
+
+%Targeting these problematic cases, there is a category of search solutions -- often referred to as semantic search solutions -- that aim at exploiting the large and increasing amount of semantic resources that have been made available in different settings.
 Prominently, Google refers to this as the next generation of search in a recent issue of the Wall Street Journal.
 
-Semantic resources are used by these solutions for the interpretation of queries and data. They include taxonomies, thesauri and formal ontologies. 
+%Semantic resources are used by these solutions for the interpretation of queries and data.
+They include taxonomies, thesauri and formal ontologies.
 More generally, also structured data exposed as graph-structured RDF\footnote{RDF stands for Resource Description Framework, a W3C Semantic Web standard for data representation and exchange on the Web: \url{http://www.w3.org/RDF/}} data are regarded as semantic resources (often called \emph{semantic data}).
-They come as standalone RDF datasets or are embedded in Web pages in the form of RDFa (a W3C standard\footnote{http://www.w3.org/TR/xhtml-rdfa-primer/} for embedding RDF data in Web pages).
-These data have been increasing rapidly.
+They come as standalone RDF datasets or are embedded in Web pages in the form of RDFa These data have been increasing rapidly.
 As a result of community projects such as Linking Open Data\footnote{\url{http://www.w3.org/wiki/SweoIG/TaskForces/CommunityProjects/LinkingOpenData}}, a large amount of structured datasets formerly kept protected in databases are now exposed as publicly Web-accessible RDF data (e.g.
@@
 Besides large companies such as BestBuy and Facebook, also national governments such as the US and UK have followed this direction of publishing and linking semantic data on the Web.
-As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups such as RDFa~\cite{}.
 
@@
 
-\subsection{Plethora of Semantic Search Solutions}
-Capitalizing on the opportunities that arise from this large and increasing amount of semantic resources on the Web, commercial search engines have made different kinds of semantic search features available to end users.
-The first well-known example towards this direction is Powerset\footnote{\url{http://en.wikipedia.org/wiki/Powerset_(company)}}, which makes use of semantic data extracted from Wikipedia to answer complex questions.
-Semantic data embedded in Web pages are now actively used by Google to provide rich result snippets\footnote{\url{http://www.google.com/webmasters/tools/richsnippets}}.
+\subsection{Commercial Interest}
 
-Likewise, research interest in semantic search is stirring up.
-A wide range of semantic search approaches have been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web.
+Capitalizing on the opportunities that arise from this large and increasing amount of semantic resources on the Web, commercial search engines have shown increasing interest in Semantic Search.
+To call out some example, one of the first commercial search engines to employ semantic analysis was Powerset\footnote{\url{http://en.wikipedia.org/wiki/Powerset_(company)}}, which makes use of semantic data extracted from Wikipedia to answer complex questions.
+Yahoo!
+has pioneered the use of semantic annotations in their SearchMonkey product and the same method is also used by Google to provide rich result snippets\footnote{\url{http://www.google.com/webmasters/tools/richsnippets}}.
+Google also acquired Metaweb, the makers of Freebase, and widely published its intent to employ semantic search technology more extensively in the future\footnote{\url{http://on.wsj.com/w7OPag}}.
+
+\subsection{Research fragmentation}
+
+Despite the commercial interest, the research effort in semantic search has been hampered by the lack of dissemination across research fields.
+As we will show in our survey, a wide range of semantic search approaches have been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web.
 Correspondingly, semantic search has been viewed from different angles, resulting in a plethora of solutions.
+Existing approaches greatly vary in the \emph{data}, (2) the \emph{semantic resources}, the \emph{information needs} and (4) the \emph{querying paradigms} that are supported.
+Further, research work found in literatures often studies one of the specific (5) \emph{subproblems in search}: Namely, different concepts and techniques have been proposed for (5a) the interpretation of query inputs and data, (5b) matching the query intent against data and (5c) ranking results.
 
-Underlying all these efforts lie one central idea, namely to use semantic resources for more effective search.
-However, existing approaches greatly vary in the \emph{data}, (2) the \emph{semantic resources}, the \emph{information needs} and (4) the \emph{querying paradigms} that are supported.
-Most notably, there are principle differences between semantic search approaches, which use semantic resources to improve document retrieval, and the ones that compute direct results, i.e.
+%Most notably, there are principle differences between semantic search approaches, which use semantic resources to improve document retrieval, and the ones that compute direct results, i.e.
 semantic data retrieval.
@@
 Substantial differences also exist between systems, which either use NL, keywords or facet-based operations as the primary means for querying.
-Further, research work found in literatures often studies one of the specific (5) \emph{subproblems in search}: Namely, different concepts and techniques have been proposed for (5a) the interpretation of query inputs and data, (5b) matching the query intent against data and (5c) ranking results.
 
-\subsection{Contributions}
-Different solutions for semantic search have been around for a long time.
-In this work, we present a systematic survey to provide a taxonomy of various semantic search approaches, to reflect on the achievements that have been made over these years, and finally, to discuss the challenges ahead and directions for future research.
+Our work unifies the research field of semantic search by determining the key areas of research, identifying the key contributions independent of the field in which they were published and placing them in a unified framework.
+Such an overview of a state-of-the-art will enable researchers and practitioners to design and develop semantic search systems based on best-of-breed methods.
+We also reflect on the evaluation and demonstrated performance of various approaches and discuss the challenges ahead and directions for future research.
 
-% and their mainstream adoption into commercial solutions is increasingly visible. 
-There exist a few usability studies, which compare several semantic search solutions~\cite{DBLP:conf/semweb/KaufmannB07,DBLP:conf/esws/TranMH10}.
+There are few studies in related work that would compare different approaches to semantic search~\cite{DBLP:conf/semweb/KaufmannB07,DBLP:conf/esws/TranMH10}.
 However, this line of work focuses on the differences in querying paradigms.

### 2012-04-11 tr-semanticsearchsurvey-data/intro.tex
Lot's of small changes...

@@
 Solutions that are widely used especially on the Web are based on keyword search, and in smaller-scale scenarios, also support natural language (NL) inputs.
-While they are easy to use, the inputs provided by the users through these interfaces are \emph{ambiguous} such that the underlying information need (query intent) is not directly accessible to the system.
-Further, there are search scenarios where not only the query, but also the data representation does not precisely capture the semantics and structure of the underlying information.
+While they are easy to use, the inputs provided by the users through these interfaces are ambiguous and limited representations of the underlying information need (query intent) due to the limitations of the keyword search paradigm.
+Further, in most search scenarios not only the query, but also the data representation is lacking precise structure and semantics.
 Accordingly, the core problems to be addressed in search are (1) to \emph{understand the query intent and the data}, (2) to \emph{match query against data}, and (3) to \emph{rank results}.
 
-Modern search engines are efficient in retrieving documents (web pages in the case of web search) from large collections based on matching the text of the user's query with the textual content of the document or words in linking to the current document (\emph{anchor text}).
-These textual features are often combined with additional features that measure the popularity of results based on usage data (\emph{click-log data}) or using metrics computed on the web graph such as \emph{PageRank} and its derivates.
-In combination, these relatively simple, but scalable matching techniques are are able to address a large fraction of common information needs.
+Modern search engines are efficient in retrieving documents (web pages in the case of web search) from large collections based on matching the text of the user's query with the textual content of the document or the words used to label the links to the document (\emph{anchor text}).
+These textual clues are often combined with additional features that measure the popularity of results based on usage data (\emph{click-log data}) or using metrics computed on the web graph such as \emph{PageRank} and its derivates.
+In combination, these relatively simple, but scalable matching techniques are able to address a large fraction of common information needs.
 They work particularly well when the user is able to explicitly name the target of the query, this reference is unambiguous and refers to a popular item widely referred to with that name.
@@
 Baeza-Yates et al.
-report that even in a full year of query logs 88\% of the unique queries are singleton queries, i.e.
-appeared only once in the year.
+report that even when taken a full year of query logs 88\% of the unique queries are singleton queries, i.e.
+appear only once in the year \cite{baeza07sigir}.
 A lot of this variety comes from syntactic variations of the same popular need and can be addressed with spell-corrections and query suggestion techniques.
-However, the remaining queries tend to be less common because they refer to less popular needs that need disambiguation or require more complex explanation.
+However, the remaining queries tend to be less common because they refer to less popular needs that can not be easily addressed by popularity ranking (due to the sparsity of signals), and more likely to need disambiguation or to require complex processing.
 
@@
 The concept of digital camera covers a broad range of actual entities, and there might be some discussion as to which of these can be considered cheap.There are also systemic factors that lead to an increase in ambiguity.
-Despite the expectation that longer queries should leave to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ an AND semantics between words, and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult.
+Despite the expectation that longer queries should leave to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ conjunctive semantics (an implicit AND operator between words), and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult.
 Thus users have learned to avoid long queries, leading to shorter but more ambiguous queries.
@@
 Often, this is aggravated by the bias toward a single popular answer.
-For example, when searching for 'George Bush', the top results are crowded by references to the same person, even though this is a common name.\footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}
+For example, when searching for \emph{george bush}, the top results are crowded by references to the same person, even though this is a common name.\footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}
 
@@
 	\textbf{Complex Queries:} We include in this class all queries that go beyond a reference to a single named entity, and involve several entities and relationships between them.
-These queries arise again when the user does not know the answer to a question and therefore has to describe the item sought and it's relationships to other items that he or she can name.
+These queries arise again when the user does not know the answer to a question and therefore has to describe the item sought and its relationships to other items that he or she can name.
 For example, searching for this paper by the name of the second author is relatively straightforward.
-However, assuming the user does not know (or do not remember) the name, he or she might look for a "semantic search survey paper written by a researcher at yahoo".
+However, assuming the user does not know (or do not remember) the name, he or she might look for a \emph{semantic search survey paper written by a young researcher at yahoo}.
 Complex queries are particularly hard to address in the traditional information retrieval paradigm when they require information extraction and aggregation, i.e.
@@
 
-Semantic annotations of documents are available in increasing amounts due to advances in both Information Extraction and the adoption of standard formats for annotating documents.
+Semantic annotations of documents are available in increasing amounts due to advances in both Information Extraction and the adoption of standard formats for the semantic annotation of documents.
 The two developments are complementary in providing annotations for the Web.
@@
 The practice of annotating webpages using these formats have thus brought us closer to acquiring semantic annotations in the long tail of the Web.
-As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups such as RDFa~\cite{}.
+As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups such as RDFa~\cite{DBLP:conf/semweb/MikaMZ09}.
 
 Complementary to these efforts, the Linking Open Data\footnote{\url{http://www.w3.org/wiki/SweoIG/TaskForces/CommunityProjects/LinkingOpenData}} movement that has emerged in recent years facilitated the process of publishing entire datasets (knowledge bases) on the Web.
-Large structured datasets that have been formerly kept in closed databases are now exposed as publicly Web-accessible RDF data (e.g.
-Linked Data\footnote{\url{http://linkeddata.org/}}).
-This method of publishing is often used in the area of the sciences and the government where data is in the public domain.
+Large structured datasets that have been formerly kept in closed databases are now exposed as publicly Web-accessible RDF data.
+(For a list of datasets, see the Linked Data\footnote{\url{http://linkeddata.org/}} community site or the Data Hub \footnote{\url{http://thedatahub.org/}} maintained by CKAN.) This method of publishing is often used in the area of the sciences and the government where data is in the public domain.
 Efforts are under way to link these datasets by establishing links (references between entities) in different datasets.
@@
 These resources are particularly valuable for supporting open domain search and query answering.
-Altogether, the Linked Data cloud is estimated to contain over 40B triples \cite{}.
+Altogether, the Linked Data cloud is difficult to estimate in size but it contains billions of triples\footnote{\url{http://stats.lod2.eu/}}.
 
@@
 Many of the Linked Data datasets reflect the internal schema of the database that is being exposed.
-However, in this case the burden is on the consumer of the data to make sense of the schemas of the individual datasets and map them to a shared, global schema before being able to aggregate data.
+However, in this case the burden is on the consumer of the data to make sense of the schemas of the individual datasets and map them to a shared, global schema before being able to aggregate instance data.
 This type of schema matching is difficult and can not be fully automated in practice.
@@
 RDF is commonly used to publish and manipulate semantic resources and is supported by a growing range of tools and APIs in various programming languages.
-In particular, the so called 'triple stores' that provide storage for RDF data have matured over the years and scale to several hundreds of millions triples (facts) on single machines.
-(Triple stores, however, do not provide the kind of retrieval functionality described in this paper.) Another Semantic Web standard, the Web Ontology Language (OWL) has standardized the way in which schemas are shared on the Web.
+In particular, the so called 'triple stores' that provide storage for RDF data have matured over the years and scale to several hundreds of millions triples (facts) on single machines.\footnote{For a benchmark of triple stores, see \url{http://www4.wiwiss.fu-berlin.de/bizer/BerlinSPARQLBenchmark/}} Triple stores, however, do not provide the kind of retrieval functionality described in this paper.
+Another Semantic Web standard, the Web Ontology Language (OWL) has standardized the way in which schemas are shared on the Web.
 
@@
 
-Capitalizing on the opportunities that arise from this large and increasing amount of semantic resources on the Web, commercial search engines have shown increasing interest in Semantic Search.
+Capitalizing on the opportunities that arise from the already large and increasing amount of semantic resources on the Web, commercial search engines have shown increasing interest in Semantic Search.
 To call out some example, one of the first commercial search engines to employ semantic analysis was Powerset\footnote{\url{http://en.wikipedia.org/wiki/Powerset_(company)}}, which makes use of semantic data extracted from Wikipedia to answer complex questions.
 Yahoo!
-has pioneered the use of semantic annotations in their SearchMonkey product and the same method is also used by Google to provide rich result snippets\footnote{\url{http://www.google.com/webmasters/tools/richsnippets}}.
+has pioneered the use of semantic annotations in Yahoo!
+SearchMonkey, which has been experimentally proven to help users judge the relevance of search results \cite{DBLP:conf/sigir/HaasMTB11}.
+The same method is also used by Google to provide rich result snippets\footnote{\url{http://www.google.com/webmasters/tools/richsnippets}}.
 Google also acquired Metaweb, the makers of Freebase, and widely published its intent to employ semantic search technology more extensively in the future\footnote{\url{http://on.wsj.com/w7OPag}}.
+As a last example, Facebook intends to extend its internal graph of people and other types of resources (e.g.
+organizations with Facebook pages) with additional knowledge from webpages.
+Facebook publishes a set of schemas under the name Open Graph Protocol \footnote{\url{http://ogp.me}} for developers who want to annotate their webpages.
+OGP annotations are also used by Facebook to interpret the type of object that the user is interested in when pressing a 'Like' button on a webpage.
 
@@
 Despite the commercial interest, the research effort in semantic search has been hampered by the lack of dissemination across research fields.
-As we will show in our survey, a wide range of semantic search approaches have been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web.
+As we will show in our survey, a wide range of semantic search approaches have been proposed by researchers from different communities, including Databases, Information Retrieval (IR) and Semantic Web.
 Correspondingly, semantic search has been viewed from different angles, resulting in a plethora of solutions.
 Existing approaches greatly vary in the \emph{data}, (2) the \emph{semantic resources}, the \emph{information needs} and (4) the \emph{querying paradigms} that are supported.
-Further, research work found in literatures often studies one of the specific (5) \emph{subproblems in search}: Namely, different concepts and techniques have been proposed for (5a) the interpretation of query inputs and data, (5b) matching the query intent against data and (5c) ranking results.
+Further, research work found in literatures often studies one of the specific (5) \emph{subproblems in search}: namely, different concepts and techniques have been proposed for (5a) the interpretation of query inputs and data, (5b) matching the query intent against data and (5c) ranking results.
 
@@
 Such an overview of a state-of-the-art will enable researchers and practitioners to design and develop semantic search systems based on best-of-breed methods.
-We also reflect on the evaluation and demonstrated performance of various approaches and discuss the challenges ahead and directions for future research.
+We also reflect on the evaluation and demonstrated performance of various approaches and discuss the challenges ahead.
 
@@
 However, this line of work focuses on the differences in querying paradigms.
-Towards a classification of semantic search approaches, Mangold discusses existing solutions along the dimensions of architecture, coupling, transparency, user context, ontology structure and ontology technology~\cite{DBLP:journals/ijmso/Mangold07}.
+In a step towards a classification of semantic search approaches, Mangold discusses existing solutions along the dimensions of architecture, coupling, transparency, user context, ontology structure and ontology technology~\cite{DBLP:journals/ijmso/Mangold07}.
 The last two criteria basically capture the differences in semantic resources among existing systems, which are also discussed in our study.
@@
 \subsection{Outline}
-The paper is organized as follows: An overview of semantic search and the concepts it entails is presented in Section~\ref{sec:ss}.
+The paper is organized as follows.
+An overview of semantic search and the concepts it entails is presented in Section~\ref{sec:ss}.
 Then, the paper is organized mainly along the aspects based on which we distinguish different semantic search approaches.

### 2012-04-11 tr-semanticsearchsurvey-data/overview.tex
Lot's of small changes...

@@
 This is illustrated in the left portion of Fig.~\ref{fig:semsearch}.
-One main characteristic of search concepts is its emphasize on end users.
-That is, search typically involves intuitive interfaces targeting users, who may do not possess knowledge about the domain, the data and structured query languages.
+One main characteristic of search concepts is its emphasis on end users.
+That is, search typically involves intuitive interfaces targeting users, who may not possess knowledge about the domain, the data and structured query languages.
 The query inputs that can be obtained from these interfaces are often ambiguous.
-That is, they allow for many possible \emph{interpretation}s, which in turn, yield many possible results that vary in relevance w.r.t.~ the intended query intent.
+That is, they allow for many possible \emph{interpretation}s, which in turn, yield many possible results that vary in relevance w.r.t.~the intended query intent.
 % Because end users are often only interested in the few best results, 
@@
 There are exist different notions of semantics.
-One the one hand, there are proposals for using the semantics of words captured as latent concepts (e.g.
+One the one hand, there are proposals for exploiting the hidden of implicit semantics of words based on their usage.
+This may be captured as latent concepts (e.g.
 inferred through Latent Semantic Indexing~\cite{DBLP:conf/sigir/Hofmann99}) or latent topics (e.g.
@@
 
-\begin{definition} \emph{Semantic search} is a search paradigm that makes use of explicit semantics to solve core search tasks, i.e.
+\begin{definition} \emph{Semantic search} is a search paradigm that makes use of \textbf{explicit} semantics to solve core search tasks, i.e.
 to use semantics for interpreting query and data, matching query against data and ranking results.
@@
 
-For instance, we can look at the differences in the data to arrive at the distinction between document retrieval and data retrieval, two major research directions in search that mark the borders of large communities.
+We will treat each of these topics separately in the following sections.
+But as an illustration, we can look at the differences in the data to arrive at the distinction between document retrieval and data retrieval, two major research directions in search that mark the borders of large communities.
 
@@
 Thus, in the IR context, these queries are also referred to as navigational queries.
-Recently, semantic data embedded in Web pages have been exploited to address this type of queries.
-This was pioneered by Yahoo!
-in their SearchMonkey program, and later adopted by Google to present rich entity snippets\footnote{Google Rich Snippets} as answers to this kind of queries.
-As an example, Fig.~\ref{fig:semantic_layer} illustrates the entity search functionalities provided by Yahoo!.
-Not only there are Web pages but also entity descriptions appear as results.
+Recently, semantic data embedded in Web pages have been exploited to address this type of queries, e.g.
+in producing richer search result presentations.
+As an example, Fig.~\ref{fig:semantic_layer} illustrates the entity search functionalities provided by a modern search engine, Yahoo!
+Search.
+Besides individual web pages as results, there are also entity descriptions shows in separate information boxes.
 These descriptions are directly retrieved from semantic data (in this case, a dataset about music artists and their albums).
+When it comes to entity search, pure semantic search engines only differ in that they do not provide web pages as results.
 Instead of searching over a collection of documents, semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results.
@@
 
-\subsection{NL Search} This is the other paradigm for users to express their needs using their own words.
+\subsection{NL Search} Complete natural language questions and statements are a natural paradigm for users to express themselves fully in their own words.
 Traditionally, it has been used to pose complex questions against expert systems built for specific domains.
@@
 For ``queen single'', the interpretations shown indicate that the query intent may be something matching the word ``queen'' that is of the type \verb+single+, or something that is of the type \verb+single+, which is produced (or written) by something else matching the word ``queen''.
-Google, Freebase\footnote{\url{http://www.freebase.com/docs/suggest}} and True Knowledge also present possible interpretations of the query as the user type or after issuing a query.
+Web search engines, Freebase\footnote{\url{http://www.freebase.com/docs/suggest}} and TrueKnowledge also present possible interpretations of the query as the user type or after issuing a query.
 
@@
 have been converted to and published on the Web as RDF data.
-Several semantic search systems have been built that specifically target the retrieval of semantic data.
-Instead of searching directly over semantic data, classic retrieval systems search over a raw data representation of information objects such as audios, videos, images and texts.
+Several semantic search systems have been built that specifically target the retrieval of semantic data,  in contrast to classic retrieval systems that search over raw information objects such as audios, videos, images and texts.
 For instance, document retrieval systems search for textual documents that are represented as bags of words.
 As opposed to semantic data, raw data do not explicitly capture the semantics of information resources in terms of entities and their relations.
-Thus, for supporting document (or image, video or audio) retrieval as semantic search, one core subtask is the recognition of named entity in the raw text.
+Thus, for supporting document (or image, video or audio) retrieval as semantic search, one core subtask is the recognition of entities and their relationships in the raw text.
 Named entity recognition and other data interpretation tasks such as relation extraction are performed to obtain a semantic data representation of raw data (also called \emph{semantic metadata}).
@@
 \textbf{Structured Entity Descriptions:} This type of semantic data is ubiquitous on the Web, capturing information about real-world objects as RDF resource descriptions (or structured entity descriptions that can be directly converted to RDF).
-Through industry efforts such as Yahoo's SearchMonkey, Google's Rich Snippets and Facebook Like\footnote{\url{http://developers.facebook.com/docs/reference/plugins/like/}}, a large amount of RDF descriptions of resources such as restaurants and movies have been embedded into existing Web pages as RDFa.
+Through industry efforts such as Yahoo's SearchMonkey, Google's Rich Snippets and Facebook's Open Graph Protocol, a large amount of RDF descriptions of resources such as restaurants and movies have been embedded into existing Web pages as RDFa.
 Besides, hundreds of large-scale RDF datasets have been made available on the Web.
 Started with the Linking Open Data, more and more data are made freely available on the Web and linked with other public datasets.
-Not only Web content providers but many companies, public institutions and national governments (US, UK etc.) are now actively publishing and linking RDF data on the Web (called Linked Data).
+Not only Web content providers but many companies, public institutions and national governments (US, UK etc.) are now actively publishing and linking RDF data on the Web.
 Availably datasets can be subdivided into broad/domain-independent ones such as as DBpedia and Freebase\footnote{\url{http://www.freebase.com/}} or deep/domain-specific ones.
@@
 \subsection{Semantic Metadata}
-Basically, semantic metadata is semantic data that captures information about the objects to be retrieved.
+We call semantic metadata any kind of semantic data that provides additional information about the objects to be searched.
 Later, we also use the term \emph{documentation annotation} to refer to metadata created for text.
@@
 Not only entities may be recognized but for instance, the content of a document may be interpreted as referring to a \verb+meeting+ with the two \verb+researchers+ \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participants+.
-Semantic metadata representing the content may also be manually produced and embedded into the objects.
-Recently, several industry projects such as Google Rich Snippets and Yahoo!
-SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages.
-Complementary to this,  schema.org\footnote{\url{http://schema.org/}} is an initiative promoted by major Web search companies (Google, Microsoft, Yahoo!) aiming at the provision of a common vocabulary that can be used by site owners to capture their data.
+Semantic metadata representing the content may also be manually produced and embedded into the objects such as PDF documents or HTML pages.
 In this regard, we note that while Wikipedia can be conceived as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).
 
-While the amount of available metadata is increasing, it is still too sparse to cover all information needs.
+While the amount of available metadata is increasing, most web pages are still not explicitly annotated and not amenable to Information Extraction.
+Semantic metadata is thus still too sparse to cover generic information needs.
 Thus, metadata is mostly used as additional information that can help to improve standard search over raw data~\cite{DBLP:journals/tkde/CastellsFV07,DBLP:journals/ws/FernandezCLVCM11}.
@@
 While concepts in knowledge models stand for classes of real-world entities, concepts in lexical models correspond to \emph{senses of words}.
-Lexical concepts are more general such that they may refer to entities, classes, relations, attributes, or other senses of words.
+This also means that lexical models are limited to capture concepts for which words have been created in a given human language.
+Lexical concepts are also more heterogeneous such that they may refer to entities, classes, relations, attributes, or other senses of words.
 While these different ``types'' of senses are not explicitly distinguished like in a knowledge model, concepts can be organized along lexical relationships in a lexical model.
 
-\emph{Thesaurus} 
+A \emph{thesaurus} 
 %(often, \emph{lexicon} is also used as synonym) 
@@
 IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} makes use of UIMA\footnote{\url{http://uima.apache.org/}}, a framework of annotators that can be configured in a pipeline to analyze and extract data from text.
-There is a another work from IBM, which focuses on extracting named entities and relations from text and using them for more precise search (employing XML fragments as queries~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}).
+Another work from IBM focuses on extracting named entities and relations from text and using them for more precise search (employing XML fragments as queries~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}).
 
@@
 In this case, the typical analysis includes tokenization, POS tagging, chunking sentences into noun phrases, and some information extraction systems even derive entire parse trees from the text.
-Besides the syntactic information derived from text analysis, different semantic resources are used.
+Different semantic resources may be employed besides the syntactic information derived from text analysis.
 In particular, Gazetteers are frequently used, which can be seen as a lexical model.
@@
 \section{Query Interpretation}\label{sec:query} 
-	Essentially, interpreting queries is similar to the task of understanding text in documents.
-However, these problems are studied from different viewpoints by overlapping but not same communities of researchers.
+	Interpreting queries is similar to the task of understanding text in documents.
+However, these problems are studied from different viewpoints by partially overlapping communities of researchers.
 Thus, the emphases are put on different subproblems.
@@
 Concept-based query expansion \cite{DBLP:conf/sigir/QiuF93} for instance, detects the concept behind the query, and performs selection and weighting of additional search terms directly based on this concept (instead of the query terms).
-This and other works in this area, were based on the use of thesauri that capture concepts and relationships.
-WordNet for instance, was use to represent concepts by WordNet synonym sets, and for expanding query terms by following WordNet links \cite{DBLP:conf/sigir/Voorhees93}.
-WordNet links (is-a in particular) were also used to disambiguate query terms and to choose their senses \cite{DBLP:conf/sigir/Voorhees94}.
+Most commonly, the authors use the English language WordNet thesaurus to represent concepts by WordNet synonym sets, and for expanding query terms by following WordNet links \cite{DBLP:conf/sigir/Voorhees93}.
+WordNet links (is-a in particular) have also been found beneficial in disambiguating query terms and in choosing their senses \cite{DBLP:conf/sigir/Voorhees94}.
 
@@
 conceptual graphs~\cite{DBLP:conf/aswc/CaoCT08}, logical formulas~\cite{DBLP:journals/dke/CimianoHHMS08} or XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
-An overview of this task is illustrated in Fig.~\ref{fig:inter_keywords}
+An overview of this task is shown in Fig.~\ref{fig:inter_keywords}.
 
@@
 For instance, the Stanford Parser~\footnote{\url{http://nlp.stanford.edu/software/lex-parser.shtml}} and GATE~\footnote{\url{http://gate.ac.uk/}} are used by FREyA~\cite{DBLP:conf/esws/DamljanovicAC10} to identify concepts in NL questions and to derive the syntactic parse tree, respectively.
-The use of domain-specific lexicons provide is a common way to deal with ambiguities, especially for traditional NL translation systems that are focused on a particular domain.
+It is common to use domain-specific lexicons for dealing with ambiguities, especially for traditional NL translation systems that are focused on a particular domain.
 Basically, a lexicon captures the mappings from syntactic elements to semantic elements.
@@
 For instance, adding and removing facets result in the addition (query expansion) and removal (query refinement) of query predicates, respectively.
-Clearly, the difference to work on keyword and NL query interpretation is the lack of ambiguity, i.e.
-the semantics of every user input is clear.
+Clearly, the difference to work on keyword and NL query interpretation is the lack of ambiguity.
+Since only elements known to the system are presented to the sure, the semantics of every user input is well-defined.
 
@@
 
-Which kind of matchings is needed depends on the query given as input. This could be either directly the query input provided the user, or input preprocessed via query interpretation. 
-The differences in inputs between term matching, structure matching and graph traversal are illustrated in Fig.~\ref{fig:matching}.
+The kind of matching that one would apply depends on the query given as input. This could be either directly the query input provided the user, or input preprocessed via query interpretation. 
+The differences in inputs between term matching, structure matching and graph traversal are illustrated in Fig.~\ref{fig:matching} and discussed further below.
 We can see that term matching and graph traversal are particularly needed when the query is keyword-based.
-Whereas document retrieval or entity retrieval in general, can be solved through term matching, relational search requires graph traversal for finding connections between keywords.
+Whereas document retrieval or entity retrieval in general can be solved through term matching, relational search requires graph traversal for finding connections between keywords.
 Likewise, graph traversal is also useful for finding connection between elements, which have been recognized in the keywords through the preprocessing step of keyword interpretation.
@@
 Many semantic data retrieval systems such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} also employ bag-of-words representations -- at the query and sometime, also at the level of semantic data.
-For instance, Sindice\footnote{\url{http://sindice.com/}}, the inverted index implementation behind Sig.ma, supports keyword queries on entity descriptions that essentially, are indexed as bag-of-words just like unstructured documents.
+For instance, Sindice\footnote{\url{http://sindice.com/}}, the inverted index implementation behind Sig.ma, supports keyword queries on entity descriptions that are indexed as bag-of-words just like unstructured documents.
 In this case, the semantics available in the data are not taken into account during the matching (but may have been used in other steps such as query interpretation, e.g.
@@
 Falcons and SemSearchPro use Apache Lucene\footnote{\url{http://lucene.apache.org/core/}}) supports fuzzy term matching such that syntactically similar terms can also be recognized as matches.
-Besides, systems such as SemSearchPro uses a lexical model such as WordNet in additional, to find also lexical variants that match in terms of meaning.
+Besides, systems such as SemSearchPro uses a lexical model such as WordNet to find also lexical variants.
 This technique is similar to the use of lexical resources for concept detection during document and query interpretation.
-After matches are identified for every query term, they are joined (or combined via union) to obtain those, which match all (some) query keywords (AND- vs.
-OR-semantics).
+After matches are identified for every query term, they are joined (or combined via union) to obtain those that match all or some query keywords (AND vs.
+OR-semantics, respectively).
+
 %This matching goes beyond the term-level to consider the content, which may contain several mentions of the query terms, as well as mentions of terms that do not appear in the query.
@@
 \subsection{Matching Complete Structure Patterns (Structure Matching)} 
-	This matching is possible when the query and document are interpreted or are directly available as a structured query and semantic data, respectively.
+	 We can apply this matching when the query and document are interpreted or are directly available as a structured query and semantic data, respectively.
 That is, the semantics of both the query and data is represented in terms of some entities and their relations.
@@
 However, edges in the BGP are not required to be connected such that basically, a BGP can be seen as a set of connected components.
-Results obtained for every connected component are finally combined via union.
+\dtr{Improve the description, or at least the language (remove basically, you are saying it too much, basically :) }Results obtained for every connected component are finally combined via union.
 Through join variables, the query engine knows how to combine intermediate results obtained for edges in every connected component, i.e.
@@
 For processing these BGPs, the underlying engine leverages standard database query evaluation techniques, i.e.
-it precompiles the query to capture an optimal evaluation plan, then retrieves data (from optimized, compressed indexes) for each triple pattern and joins intermediate results according to the plan.
+it precompiles the query to capture an optimal evaluation plan, then retrieves data (from optimized, compressed indexes) and joins intermediate results according to the plan.
 This processing is supported by off-the-shelf triple stores such as Virtuoso\dtr{footnote} and Sesame\dtr{footnote}.
@@
 That is, the structured query pattern might be incomplete such that some connections between query elements are not explicitly given.
+\dtr{These last two sentences are confusing...
+it would be good to start with the less technical story: that for various reasons a user may not be able to specify the right relations between entities in the query, or interpretation to produce a structured query may fail}.
 This is the case with relational search, when the relations are unknown and have to be searched for.
@@
 
-We note that graph traversal has also been applied in the structured query setting to deal with cases, where relations (paths) are unknown.
+We note that graph traversal has also been applied in the structured query setting to deal with cases where relations (paths) are unknown.
 For instance, the graph traversal algorithm used by SemSearchPro~\cite{DBLP:journals/ws/TranHL11,DBLP:conf/icde/TranWRC09}, a keyword search system, is similar to the one proposed for answering P-Queries~\cite{DBLP:conf/www/AnyanwuS03}, a special type of structured queries that ask for unknown semantic associations between entities.
@@
 Complex models for advanced analytics however, are only available in expert systems and data warehouses.
-With Wolfram Alpha, the use of of computational models based on statistical and mathematical formulas to derive further insights from the results has crossed the boundaries of specific domains to reach the mass of Web users.
+With Wolfram Alpha, the use of computational models based on statistical and mathematical formulas to derive further insights from the results has crossed the boundaries of specific domains to reach the mass of Web users.
 In fact, simple analytical processing has been available in popular Web search engines such as Google for a while.
@@
 Similar to this idea, semantic data sources have been considered as Web pages~\cite{DBLP:conf/esws/DelbruTCTD10,DBLP:conf/semweb/HarthKD09}.
-However, a two-layer approach has been pursuit here, where the PageRank scores computed for the datasets propagate to the entities contained in them~\cite{DBLP:conf/semweb/HarthKD09}.
+Authors of the latter pursue a two-layer approach where the PageRank scores computed for the datasets propagate to the entities contained in them~\cite{DBLP:conf/semweb/HarthKD09}.
 
@@
 
-Also worth mentioning, we have EntityAuthority~\cite{DBLP:conf/webdb/StoyanovichBBW07}, which operates not only on the semantic data graph but on a combined graph that contains both entities and documents as nodes.
+EntityAuthority~\cite{DBLP:conf/webdb/StoyanovichBBW07} operates not only on the semantic data graph but on a combined graph that contains both entities and documents as nodes.
 
@@
 the query-relevance) and ranking results based on relevance represent a classic problem in IR.
-In the semantic search setting, existing IR concepts proposed for that have been used and extended to deal with semantic data and to leverage the availability of semantics.
+In the semantic search setting, existing IR concepts have been used and extended to deal with semantic data and to leverage the availability of semantics.
 
@@
 
-For ranking more complex (relational search) results, there are keyword search systems, which adopt the vector space model and \emph{TFIDF-based} term weighting.
+For ranking more complex (relational search) results, there are keyword search systems, which adopt the vector space model and TFIDF-based term weighting.
 The result in this setting is actually a graph, which is simply conceived a set of keyword matching nodes.
@@
 they all are relevant.
-Besides centrality-based measures such as PageRank (and other ones derived from connectivity information in the RDF graph), also features external to the data such as Google n-gram statistics were considered.
+Besides centrality-based measures such as PageRank (and other ones derived from connectivity information in the RDF graph), the authors also consider features external to the data such as Google n-gram statistics.
 For relational keyword search over semantic data, TFIDF-based ranking scores obtained for individual nodes in the result graph as well as structure proximity scores derived from the result graph have been studied for learning to rank~\cite{DBLP:conf/cikm/CoffmanW11}.
 
-\section{Main Types of Approaches and Their Performances}\label{sec:approaches}	
+\section{Common Approaches and Their Performance}\label{sec:approaches}	
 Semantic search has been investigated from different communities in different contexts.
@@
 
-Accordingly, we distinguish approaches into five main types, namely concept-based document retrieval, annotation-based document retrieval, entity search, relational keyword search and relational NL search.
-These types are introduced to represent main communities, which may overlap in some aspects such that some approaches may be classified to multiple types.
+Accordingly, we distinguish five common types of approaches, namely concept-based document retrieval, annotation-based document retrieval, entity search, relational keyword search and relational NL search.
+These types of approaches each represent substantial communities with significant bodies of work, although just as the communities the approaches themselves may overlap in some aspects.
 For instance, an entity search system may use documents and annotations, which would also characterize it as annotation-based search.
@@
 In fact, this is the classic type of semantic search systems, which has been studied already in the early years of IR research.
-Researchers have recognized for a richer representation of the information needs and data that goes beyond the bag-of-words model.
+Researchers in this community have recognized the need for a richer representation of the information needs and data that goes beyond the bag-of-words model.
 It became evident that constructing a full-fledge logic-based representation~\cite{DBLP:conf/sigir/Rijsbergen89} for queries and especially for documents is not practical.
@@
 To date, there exist only \emph{anecdotal evidences} for the merits of this type of systems. 
-The most conclusive result in this direction is based on experiments using the TREC Question Answering track: For a subset of queries, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
-The results there can also be interpreted as follows: The employed information extraction programs were optimized for a few specific types of relations and entities (e.g.
+The most conclusive result in this direction is based on experiments using the TREC Question Answering track: for a subset of queries, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
+The results there can also be interpreted as follows: the employed information extraction programs were optimized for a few specific types of relations and entities (e.g.
 \verb+Person+).
@@
 It targets the Jeopardy!
-quiz show, where the task is basically, to find factual answers related to entities, given the category and several clues.
+quiz show, where the task is basically to find factual answers related to entities, given the category and several clues.
 It is a complex system combining different techniques.
@@
 Some \emph{type(1)} systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}.
-However, they go standard beyond document retrieval to locate the parts (passages) in the documents that contain answers to the query.
+However, they go beyond standard document retrieval to locate the parts (passages) in the documents that contain answers to the query.
 As mentioned in the previous Subsection, the work from IBM~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} showed that precision can be very high when quality extraction outputs are available.
@@
 Recently, the SemSearch challenge attracted a large number of participants, which submitted results produced by different ranking schemes based on traditional IR concepts.
-To date, the best performed method~\cite{DBLP:conf/semweb/BlancoMV11} uses an adoption of BM25F.
+To date, the best performed method~\cite{DBLP:conf/semweb/BlancoMV11} uses an adaptation of BM25F.
 %, which ranks entities as documents that are segmented into different fields corresponding to entity attributes.
@@
 It uses its own curated sources of semantic data (e.g.
-data about companies) to provide -- in addition to relevant Web pages -- specific information about the requested entity and links to related entities.
+data about companies) to provide -- in addition to relevant Web pages -- specific information about the requested entity and links to related entities whose ranking is computed based on co-occurrence in query logs and social media \cite{vanZwol:2010:FEI:1772690.1772788}.
 Microsoft's \emph{EntityCube} (MS) extracts information from text~\cite{DBLP:conf/www/ZhuNLZW09} to support entity-related keyword queries over documents and extracted information.
@@
 The structured queries AVATAR obtains from keywords may also involve relational information.
-Another system is \emph{SemSearchPro} (SPro), which exploits semantics throughout the search process: It uses lexical and knowledge models as well as the semantic data to translate keyword queries to SPARQL queries (interpretation), to find connections between entities mentioned in the keyword query and for processing fully structured SPARQL queries (matching), and to rank results based on structure-based proximity, centrality and query-relevance (ranking).
+Another system is \emph{SemSearchPro} (SPro), which exploits semantics throughout the search process: it uses lexical and knowledge models as well as the semantic data to translate keyword queries to SPARQL queries (interpretation), to find connections between entities mentioned in the keyword query and for processing fully structured SPARQL queries (matching), and to rank results based on structure-based proximity, centrality and query-relevance (ranking).
 As illustrated in Fig.~\ref{fig:screenshot_iwb}, it also supports faceted search, and iterative query construction where users can iteratively build complexer queries by selecting suggested terms and query completions as they type.
@@
 While this problem of open-domain NL search, e.g.
-NL search NL over large amounts of heterogeneous Web data, seems to be largely unsolved, relatively good results have been reported for single domain tasks.
-However, while there is TREC-based evaluation for NL search over documents, there exists no such thing close to a standardized evaluation in this community.
+NL search over large amounts of heterogeneous Web data, seems to be largely unsolved, relatively good results have been reported for single domain tasks.
+However, while there is TREC-based evaluation for NL search over documents (TREC QA track), there exists no such thing close to a standardized evaluation in this community.
 The performances reported by previous approaches are hardly comparable because different queries and datasets have been chosen for the experiments, e.g.

### 2012-05-10 paper-iswc-reification/paper.tex

\documentclass{llncs}
%
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{epsfig}
\usepackage{url}
\usepackage{color}
\usepackage[utf8]{inputenc}
%\usepackage{subfig}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{makeidx} % allows for indexgeneration
%\usepackage{natbib}
\usepackage{amsmath,amsfonts,amssymb}
%\usepackage[top=3.95cm, bottom=4cm, left=4.6cm, right=4.6cm]{geometry}

% \usepackage{latexsym}
% \usepackage{amsmath}
% \usepackage{amssymb}
\newcommand{\dtr}[1]{(\textbf{Thanh: #1})}
%\newcommand{\todo}[1]{
%\textbf{(todo: #1)}
%}

%\input{commands}

%\renewcommand{\baselinestretch}{0.98}
\frontmatter          % for the preliminaries
\pagestyle{headings}  % switches on printing of running heads
\mainmatter           % start of the contributions

%\sloppy
\title{Efficient Management of Meta-level Information for RDF}

%\thanks{This work has been supported by the European Commission
%under contract IST-2006-027595 NeOn, and by the Deutsche
%Forschungsgemeinschaft (DFG) under the ReaSem project.}}

%\titlerunning{}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Olaf Hartig$^1$, Mike Personick$^2$, Yrjana Rankka$^3$, Bryan Thompson$^2$, Thanh Tran$^4$}

\authorrunning{Hartig}   % abbreviated author list (for running head)

%%% modified list of authors for the TOC (add the affiliations)
\tocauthor{}

\institute{
$^1$Humboldt University, Berlin, Germany\\
$^2$SYSTAP LLC, Washington, USA\\
$^3$OpenLink Software, Burlington, USA\\
$^4$Institute AIFB, Karlsruhe Institute of Technology, Germany
}

\makeindex

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\input{intro}
\input{related}
\input{rep}
\input{querying}
\input{dis}
\input{exp}
\input{conc}

%\begin{appendix}
%\input{appendix}
%\end{appendix}
%
\bibliographystyle{abbrv}
\bibliography{paper}
\end{document}

### 2012-05-10 paper-iswc-reification/rep.tex

\section{Representation}
Syntax 
Expressed tersely as:
  <<:SAP :bought :sybase>> dc:source reuters:us-sybase .
Statements are “wrapped” by << … >> 
Turtle Extension
<<:SAP :bought :sybase>> dc:source reuters:us-sybase ;
			  dc:created “1995-01-07” ;
                        		 dc:author  “James R. Jones“ .

-	The statement can appear in either the subject or object position.
-	Recursion in statements is allowed
-	But depth is shallow in practice
Semantics

### 2012-05-10 trunk/paper-iswc-reification/dis.tex

\section{Discussion}
What are benefits compared to RDF reification and other related work:
Compact Representation 
Efficient Querying 
 # Who bought Sybase and where did we get that fact?

SELECT ?src ?who {
   <<?who :bought :sybase>> dc:source ?src
}

Answered efficiently
-	2-bound POS index scan (?who :bought sybase) => ?sid
-	Join with (?sid dc:source ?src)

# Explicit bind of statement on variable for multiple joins.

SELECT ?src ?who ?created {
   <<?who :bought :sybase>> as ?sid
   ?sid dc:source ?src
   OPTIONAL {?sid dc:created ?created}
}

Compatibility with Existing Standards
-	Harmonized with RDF Reification
-	Can be combined with named graphs

### 2012-05-10 trunk/paper-iswc-reification/exp.tex

\section{Experiments}
Show the benefits in experiments
Systems
-	Bigdata
-	Virtuoso

Data
-	Datasets + artificially generated meta-level statements
-	Size of the data
-	Size of the indexes 
Loading Time Performance
Querying Time Performance

### 2012-05-10 trunk/paper-iswc-reification/intro.tex

\section{Introduction}
Motivation
\begin{itemize}
	\item 
Necessary in several domains
\item	Entity link extraction (confidence values)
\item	Graph databases (link attributes)
\item	Intelligence analysis (provenance on assertions)
\item	Statement level security
\end{itemize}

### 2012-05-10 trunk/paper-iswc-reification/related.tex

\section{Related Work}
Overview of related work and their problems / reasons why not adopted in commercial solutions, e.g. 
Reification
Reification builds a model of a statement:
_:s1 rdf:subject   :SAP .
_:s1 rdf:predicate :bought .
_:s1 rdf:object    :sybase .
_:s1 rdf:type      rdf:Statement .
_:s1 dc:source     reuters:us-sybase .

-	Has a very bad reputation
-	Extremely inefficient 
-	5x the data on disk when you reify statements.
-	Awkward syntax
-	Cognitively challenging to write queries against reified data
-	Rarely used.
Other approaches to be discussed:
-	Bernhard Schueler, Sergej Sizov, Steffen Staab, Duc Thanh Tran: Querying for meta knowledge. WWW 2008:625-634
-	Thanh Tran, Peter Haase, Boris Motik, Bernardo Cuenca Grau, Ian Horrocks: Metalevel Information in Ontology-Based Applications. AAAI 2008:1237-1242
-	Nuno Lopes, Axel Polleres, Umberto Straccia, Antoine Zimmermann: AnQL: SPARQLing Up Annotated RDFS. International Semantic Web Conference 2010:518-533
-	Antoine Zimmermann, Nuno Lopes, Axel Polleres, Umberto Straccia: A general framework for representing, reasoning and querying with annotated Semantic Web data. J. Web Sem. 11: 72-95 (2012)
-	Umberto Straccia, Nuno Lopes, Gergely Lukacsy, Axel Polleres: A General Framework for Representing and Reasoning with Annotated Semantic Web Data. AAAI 2010
-	Jeremy J. Carroll, Christian Bizer, Patrick J. Hayes, Patrick Stickler: Named graphs. J. Web Sem. (WS) 3(4):247-267 (2005)
-	Paula Severi, José Luiz Fiadeiro, David Ekserdjian: Guiding Reification in OWL through Aggregation. Description Logics 2010
-	Nicole Alexander, Siva Ravada: RDF Object Type and Reification in the Database. ICDE 2006:93
Solution & Contributions
-	Efficient management of meta-level statements 
o	Avoids the 5x growth in data associated with RDF Reification
o	Fast query answering
-	Convenient syntax for data and queries
o	Proposed extensions for SPARQL, Turtle
-	Harmonized with RDF Reification
o	Existing data and queries still work
o	Extension to SPARQL Semantics and Algebra
-	Can be combined with named graphs
o	Both methods can be mixed in the same database.

### 2012-05-11 paper-iswc-reification/paper.tex
made the whole thing compile

@@
 \documentclass{llncs}
-%
-\usepackage[ruled,vlined]{algorithm2e}
-\usepackage{graphicx}
-\usepackage{subfig}
-\usepackage{epsfig}
-\usepackage{url}
-\usepackage{color}
-\usepackage[utf8]{inputenc}
+
+\usepackage{amsmath,amssymb}
+% \usepackage[ruled,vlined]{algorithm2e}
+% \usepackage{graphicx}
+% \usepackage{subfig}
+% \usepackage{epsfig}
+% \usepackage{url}
+% \usepackage{color}
+% \usepackage[utf8]{inputenc}
 %\usepackage{subfig}
@@
 %\usepackage{algorithmic}
-\usepackage{makeidx} % allows for indexgeneration
+% \usepackage{makeidx} % allows for indexgeneration
 %\usepackage{natbib}
-\usepackage{amsmath,amsfonts,amssymb}
 %\usepackage[top=3.95cm, bottom=4cm, left=4.6cm, right=4.6cm]{geometry}
@@
 %\renewcommand{\baselinestretch}{0.98}
-\frontmatter          % for the preliminaries
-\pagestyle{headings}  % switches on printing of running heads
-\mainmatter           % start of the contributions
+% \frontmatter          % for the preliminaries
+% \pagestyle{headings}  % switches on printing of running heads
+% \mainmatter           % start of the contributions
 
@@
 %
-\author{Olaf Hartig$^1$, Mike Personick$^2$, Yrjana Rankka$^3$, Bryan Thompson$^2$, Thanh Tran$^4$}
+\author{Olaf Hartig\inst{1} \and Mike Personick\inst{2} \and Yrj{\"a}n{\"a} Rankka\inst{3} \and Bryan Thompson\inst{2} \and Thanh Tran\inst{4}}
 
@@
 
-\institute{
-$^1$Humboldt University, Berlin, Germany\\
-$^2$SYSTAP LLC, Washington, USA\\
-$^3$OpenLink Software, Burlington, USA\\
-$^4$Institute AIFB, Karlsruhe Institute of Technology, Germany
+\institute{%
+Humboldt-Universit{\"a}t zu Berlin, Berlin, Germany\\
+\and
+SYSTAP LLC, Washington, USA\\
+\and
+OpenLink Software, Burlington, USA\\
+\and
+Institute AIFB, Karlsruhe Institute of Technology, Germany
 }

### 2012-05-11 paper-iswc-reification/related.tex
made the whole thing compile

--- 2012-05-10 trunk/paper-iswc-reification/related.tex
@@
 Reification builds a model of a statement:
-_:s1 rdf:subject   :SAP .
-_:s1 rdf:predicate :bought .
-_:s1 rdf:object    :sybase .
-_:s1 rdf:type      rdf:Statement .
-_:s1 dc:source     reuters:us-sybase .
+\_:s1 rdf:subject   :SAP .
+\_:s1 rdf:predicate :bought .
+\_:s1 rdf:object    :sybase .
+\_:s1 rdf:type      rdf:Statement .
+\_:s1 dc:source     reuters:us-sybase .
 
@@
 -	Jeremy J. Carroll, Christian Bizer, Patrick J. Hayes, Patrick Stickler: Named graphs. J. Web Sem. (WS) 3(4):247-267 (2005)
--	Paula Severi, José Luiz Fiadeiro, David Ekserdjian: Guiding Reification in OWL through Aggregation. Description Logics 2010
+-	Paula Severi, Jos{\'e} Luiz Fiadeiro, David Ekserdjian: Guiding Reification in OWL through Aggregation. Description Logics 2010
 -	Nicole Alexander, Siva Ravada: RDF Object Type and Reification in the Database. ICDE 2006:93
-Solution & Contributions
+Solution \& Contributions
 -	Efficient management of meta-level statements 

### 2012-05-11 trunk/paper-iswc-reification/dis.tex
made the whole thing compile

@@
 Efficient Querying 
- # Who bought Sybase and where did we get that fact?
+ \# Who bought Sybase and where did we get that fact?
 
@@
 
-# Explicit bind of statement on variable for multiple joins.
+\# Explicit bind of statement on variable for multiple joins.
 

### 2012-05-13 trunk/paper-iswc-reification/commands.tex
added 'commands.tex'

%%% review commands:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcounter{todo}

\newcommand{\todo}[1]
	{\stepcounter{todo}\noindent{\color{red} \textsf{Todo~{\arabic{todo}}: #1}}}  % use this for drafts
	%{}                                                                           % use this for the final version

\newcommand{\Todo}[2]
	{{\color{red}\textsf{#1}\footnote{\todo{#2}}}}  % use this for drafts
	%{#1}                                           % use this for the final version

\newcommand{\removable}[1]%
	{{\color{gray}#1}}  % use this for drafts
	%{#1}               % use this for the final version

%%% key terminology:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\RDFplus}{RDF$^{\mathsf{\text{\tiny +\!meta}}}$}
\newcommand{\RDFplusTriple}{{\RDFplus} triple}

\newcommand{\TRef}%
	%{triple reference}
	{tref}
\newcommand{\TRefLongVersion}{triple reference}

%%% relevant math symbols
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\emptyset}{\varnothing}

\newcommand{\symAllURIs}{\mathcal{U}} % the symbol for the set of all URIs
\newcommand{\symAllLiterals}{\mathcal{L}} % the symbol for the set of all literals
\newcommand{\symAllBNodes}{\mathcal{B}} % the symbol for the set of all blank nodes
\newcommand{\symAllVariables}{\mathcal{V}} % the symbol for the set of all query variables
	\newcommand{\symAllTRefsInfinite}{\mathcal{R}} % don't use that; it was required to define \symAllTRefs
\newcommand{\symAllTRefs}{\overline{\symAllTRefsInfinite}} % the symbol for the set of all triple references

\newcommand{\symTermsFct}{\mathrm{terms}} % the name used for \fctTerms
\newcommand{\fctTerms}[1]{\symTermsFct(#1)} % the set of all terms in triple/graph #1

\newcommand{\symTRefFct}{\mathrm{trefs}} % the name used for \fctTref
\newcommand{\fctTRef}[1]{\symTRefFct(#1)} % the set of all triple references in triple/graph #1

\newcommand{\symDerefFct}{\mathit{deref}} % the name used for \fctDeref
\newcommand{\fctDeref}[1]{\symDerefFct(#1)} % the triple denoted by triple reference #1

\newcommand{\mathTinyRDF}[1]{\texttt{\footnotesize #1}}

### 2012-05-13 trunk/paper-iswc-reification/rep.tex
made the whole thing compile
first draft of the data model section

--- 2012-05-10 paper-iswc-reification/rep.tex
@@
-\section{Representation}
-Syntax 
-Expressed tersely as:
-  <<:SAP :bought :sybase>> dc:source reuters:us-sybase .
-Statements are “wrapped” by << … >> 
-Turtle Extension
-<<:SAP :bought :sybase>> dc:source reuters:us-sybase ;
-			  dc:created “1995-01-07” ;
-                        		 dc:author  “James R. Jones“ .
+\section{Data Model} \label{Section:DataModel}
 
--	The statement can appear in either the subject or object position.
--	Recursion in statements is allowed
--	But depth is shallow in practice
-Semantics
+In this section we introduce
+	%an extension of the RDF data model~\cite{Klyne04:RDFconcepts} that makes 
+	our data model which we call {\RDFplus}.
+This model is an extension of the RDF data model~\cite{Klyne04:RDFconcepts}.
+{\RDFplus} extends RDF by making metadata statements a first class citizen in the data model.
+% In the following we \todo{...}
+
+% Main purposes of our data model: 1.)~it allows for a more compact representation; 2.)~it allows for efficient processing
+% with {\RDFplus} our goal is to extend/expand the applicability/usefulness/usability of such triples for cases where ...
+
+\subsection{Concepts}
+
+We assume
+	%\removable{three,}
+pairwise disjoint sets $\symAllURIs$ (all URI references), $\symAllBNodes$ (blank nodes), and $\symAllLiterals$ (literals).
+	As usual, an \emph{RDF triple} is a tuple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ and an \emph{RDF graph} is a set of RDF triples.
+	%As usual, a tuple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ is an \emph{RDF triple}.
+% A set of RDF triples is an \emph{RDF graph}.
+
+{\RDFplus} extends such triples by permitting the embedding of another triple in the subject or object position of a given triple.
+We shall interpret the embedding triple as a statement about the embedded triple.
+An embedded triple may itself be a statement about a triple and, thus, may also contain embedded triples; and so forth.
+	%Therefore, the model should allow for nesting.
+%
+	%As a basis for formalizing
+	To formalize
+such kind of (nested) embedding we
+	%introduce
+	define
+a set $\symAllTRefsInfinite := (\symAllTRefsInfinite \cup \symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllTRefsInfinite \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$.
+%
+	As a basis for ruling
+	%To rule
+out infinitely deep nesting we introduce the notion of \emph{$k$-nestedness} (where $k$
+	is an arbitrary
+	%may be any
+natural number): A tuple $r=(s,p,o) \in \symAllTRefsInfinite$ is $k$-nested if either 1.)~$k=0$ and $r\in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ or 2.)~$k>0$ and for all $x \in \bigl( \lbrace s,o \rbrace \cap \symAllTRefsInfinite \bigr)$ holds $x$ is $(k\!-\!1$)-nested.
+%
+Using $k$-nestedness we now
+	%define
+	introduce {\TRefLongVersion}s as
+the new type of elements that may be used for triples in {\RDFplus}: A 
+%
+%Using $k$-nestedness we now define a
+	%\emph{{\TRef}}
+	\emph{{\TRefLongVersion}}, or \emph{\TRef} for short,
+is a tuple $r = (s,p,o) \in \symAllTRefsInfinite$ for which exists a natural number $k$ such that $r$ is $k$-nested; to denote the set of all {\TRef}s we write $\symAllTRefs$, i.e.~$\symAllTRefs \subset \symAllTRefsInfinite$.
+
+An \emph{{\RDFplusTriple}} is a tuple $(s,p,o) \in (\symAllTRefs \cup \symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllTRefs \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$.
+A set
+	%of {\RDFplusTriple}s
+	of~{\RDFplusTriple}s  %% Layout Adjustment
+is an \emph{{\RDFplusGraph}}.
+We call an {\RDFplusTriple}
+	%that contains a triple reference (in its subject or object position)
+	$(s,p,o)$ for which $s \in \symAllTRefs$ or $o \in \symAllTRefs$,
+a \emph{metadata triple}; note that any other {\RDFplusTriple} is an ordinary RDF triple.
+For any {\RDFplusTriple} $t=(s,p,o)$ we define
+	%$\fctTerms{t} := \lbrace s,p,o \rbrace$ and $\fctTRef{t} := \fctTerms{t} \cap \symAllTRefs$.
+	$\fctTerms{t} := \lbrace s,p,o \rbrace$.
+Overloading
+	%functions $\symTermsFct$ and $\symTRefFct$, we write $\fctTerms{G} := \bigcup_{t \in G} \fctTerms{t}$ and $\fctTRef{G} := \fctTerms{G} \cap \symAllTRefs$ for any set $G$ of {\RDFplusTriple}s.
+	function $\symTermsFct$, for any {\RDFplusGraph} $G$ we define $\fctTerms{G} := \bigcup_{t \in G} \fctTerms{t}$; furthermore, $\fctTRef{G} := \fctTerms{G} \cap \symAllTRefs$.
+
+While syntactically {\RDFplusTriple}s and {\TRef}s are the same, they represent different concepts: {\RDFplusTriple}s may be interpreted as statements (similar to RDF triples) whereas a {\TRef} denotes an {\RDFplusTriple}
+	%that is embedded in other {\RDFplusTriple}s.
+	for the purpose of making a statement about it.
+%
+	\removable{Hence, trefs may be understood as a particular type of name for {\RDFplusTriple}s.}
+However, since {\TRef}s carry all elements of the {\RDFplusTriple}s they denote, it is possible to obtain such a triple from its reference: We introduce a bijective function $\symDerefFct$ that maps the set of {\TRef}s to the set of all {\RDFplusTriple}s and that is defined as follows: Let $r=(s,p,o) \in \symAllTRefs$ be an arbitrary {\TRef}, then $\fctDeref{r}$ is the {\RDFplusTriple} $(s,p,o)$.
+
+\subsection{Interpretation}
+
+\todo{introduce this subsection (explain the purpose of the conversion function defined here)}
+
+For any RDF triple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ and blank node $b \in \symAllBNodes$ we define:
+\begin{align*}
+	\mathrm{reif}\bigl( s,p,o, b \bigr) := \big\lbrace
+		& (b,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
+		(b,\mathTinyRDF{rdf\!:\!subject},s), \\
+		& (b,\mathTinyRDF{rdf\!:\!predicate},p),
+		(b,\mathTinyRDF{rdf\!:\!object},o)
+	\big\rbrace
+\end{align*}
+
+\noindent
+Let $G$ be a set of {\RDFplusTriple}s.
+For converting $G$ into a set of RDF triples we assume a bijective function $id : \fctTRef{G} \rightarrow B$ where $B \subset \symAllBNodes$ is a set of blank nodes such that $| B | = | \fctTRef{G} |$ and $B \cap \fctTerms{G} = \emptyset$.
+Hence, $id$ associates each {\TRef} in $G$ with a fresh blank node (not used in $G$).
+Furthermore, we introduce
+	%an injective function $id^* : \fctTerms{G} \rightarrow \fctTerms{G} \cup B$
+	another bijective function $id^*\! : \fctTerms{G} \rightarrow B \cup \bigl( \fctTerms{G} \!\setminus\! \fctTRef{G} \bigr)$
+that is defined as follows: Let $x \in \fctTerms{G}$. If $x \in \symAllTRefs$ then $id^*\!(x) := id(x)$; if $x \notin \symAllTRefs$ then $id^*\!(x) := x$.
+%
+	Using $id^*$,
+	%Overloading function $\mathrm{reif}$,
+for any {\TRef} $r = (s,p,o) \in \fctTRef{G}$ we define:
+% \vspace{-3mm} % Layout Adjustment
+\begin{equation*}
+	\mathrm{reif}( r ) := \mathrm{reif}\bigl( \, id^*\!(s), id^*\!(p), id^*\!(o), id^*\!(r) \, \bigr)
+\end{equation*}
+
+\noindent
+For any {\RDFplusTriple} $t = (s,p,o) \in G$ we define:
+\begin{equation*}
+	\fctDescent{t} := \begin{cases}
+\vspace{1mm}
+		\big\lbrace (id(s),p,o) \big\rbrace \cup \mathrm{reif}(s) \cup \symDescentFct\bigl(\fctDeref{s}\bigr) & \text{if $s \in \symAllTRefs$ and $o \notin \symAllTRefs$,} \\
+\vspace{1mm}
+		\big\lbrace (s,p,id(o)) \big\rbrace \cup \mathrm{reif}(o) \cup \symDescentFct\bigl(\fctDeref{o}\bigr) & \text{if $s \notin \symAllTRefs$ and $o \in \symAllTRefs$,} \\
+\vspace{1mm}
+		\begin{minipage}[c]{65mm}\vspace{1mm}
+			$\big\lbrace (id(s),p,id(o)) \big\rbrace \cup \mathrm{reif}(s) \cup \mathrm{reif}(o)$ \\
+			\hspace*{15mm}$\cup \, \symDescentFct\bigl(\fctDeref{s}\bigr) \cup \symDescentFct\bigl(\fctDeref{o}\bigr)$
+		\end{minipage} & \text{if $s \in \symAllTRefs$ and $o \notin \symAllTRefs$,} \\
+		\big\lbrace (s,p,o) \big\rbrace & \text{else} .
+\end{cases}
+\end{equation*}
+
+\noindent
+Finally:
+\begin{equation*}
+	\fctDescent{G} := \bigcup_{t \in G} \fctDescent{t}
+\end{equation*}
+
+\begin{example}
+	Let $G_\mathsf{ex} = \lbrace t_\mathsf{ex} \rbrace$ be an {\RDFplusGraph} that consists of a single {\RDFplusTriple} $t_\mathsf{ex} = \bigl( (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}), \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf} \bigr)$.
+% 	The result of converting $G_\mathsf{ex}$ to an RDF graph is:
+% 	\begin{align*}
+% 		\fctDescent{G_\mathsf{ex}} = \big\lbrace
+% 			& (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}),
+% 			(b, \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf}), \\
+% 			& (b,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
+% 			(b,\mathTinyRDF{rdf\!:\!subject},\mathTinyRDF{ex:olaf}), \\
+% 			& (b,\mathTinyRDF{rdf\!:\!predicate},\mathTinyRDF{foaf:name}),
+% 			(b,\mathTinyRDF{rdf\!:\!object},\mathTinyRDF{"Olaf"})
+% 		\big\rbrace
+% 	\end{align*}
+	The result of converting $G_\mathsf{ex}$ to an RDF graph $\fctDescent{G_\mathsf{ex}}$ is (in Turtle notation, prefix declarations omitted):
+	\begin{footnotesize}%
+	\begin{verbatim}
+		 ex:olaf foaf:name "Olaf" .
+		 _:b dct:source ex:olaf ; rdf:type rdf:Statement ;
+		     rdf:subject ex:olaf ; rdf:predicate foaf:name ; rdf:object "Olaf" .
+	\end{verbatim}%
+	\end{footnotesize}
+\end{example}
+
+\noindent
+Based on the conversion function, it is possible to interpret any {\RDFplus} model via the usual RDF semantics as defined in~\cite{Hayes04:RDFsemantics}.
+
+\subsection{Representation}
+\todo{briefly introduce our extension for Turtle and explain how this extension is related to {\RDFplus} and how it should be parsed by systems that do not ``understand'' {\RDFplus}}
+
+	\begin{footnotesize}%
+	\begin{verbatim}
+		 <<ex:olaf foaf:name "Olaf">> dct:source ex:olaf .
+	\end{verbatim}%
+	\end{footnotesize}
+
+\todo{From a didactic point of view it may be better to move this subsection to the beginning of Section~\ref{Section:DataModel}}

### 2012-05-14 tr-semanticsearchsurvey-data/intro.tex

@@
 % unsolved information needs%
-Advancements in search technologies enable users to deal with and to exploit the ever increasing amount of information that we can find in different settings -- from the personal desktop to enterprises' databases up to the large-scale Web.
+Advancements in search technologies enable users to deal with and to exploit the ever increasing amount of information that we can find in different settings -- from the personal desktops to enterprises' databases up to the large-scale Web.
 As opposed to the structured querying capabilities commonly provided by commercial databases that are only accessible by experts, \emph{search} is rather understood as an end-user oriented paradigm that is based on intuitive interfaces and access mechanisms.
-Solutions that are widely used especially on the Web are based on keyword search, and in smaller-scale scenarios, also support natural language (NL) inputs.
-While they are easy to use, the inputs provided by the users through these interfaces are ambiguous and limited representations of the underlying information need (query intent) due to the limitations of the keyword search paradigm.
+Solutions that are widely used especially on the Web are based on keyword search
+%, and in smaller-scale scenarios, also 
+or 
+%support 
+natural language (NL) interfaces.
+While they are easy to use, the inputs provided by users through these interfaces are ambiguous and do not precisely capture the underlying information need (query intent).
+% due to the limitations of the keyword search paradigm. 
 Further, in most search scenarios not only the query, but also the data representation is lacking precise structure and semantics.
@@
 
-Modern search engines are efficient in retrieving documents (web pages in the case of web search) from large collections based on matching the text of the user's query with the textual content of the document or the words used to label the links to the document (\emph{anchor text}).
-These textual clues are often combined with additional features that measure the popularity of results based on usage data (\emph{click-log data}) or using metrics computed on the web graph such as \emph{PageRank} and its derivates.
-In combination, these relatively simple, but scalable matching techniques are able to address a large fraction of common information needs.
+Modern search engines are efficient in retrieving documents (Web pages in the case of Web search) from large collections based on \emph{matching the text} of the user's query with the textual content of the document or the words used to label the links to the document (anchor text).
+These textual clues are often combined with additional features that measure the \emph{popularity} of results based on usage data (click-log data) or using metrics computed on the web graph such as PageRank and its derivates.
+In combination, these relatively simple, but scalable techniques for matching and ranking are able to address a large fraction of common information needs.
 They work particularly well when the user is able to explicitly name the target of the query, this reference is unambiguous and refers to a popular item widely referred to with that name.
-An example is a product search, where the user enters the name of the product and that product is widely known by that name, e.g \emph{canon ixus 115}, a digital camera.
+An example is a product search, where the user enters the name of the product and that product is widely known by that name, e.g ``canon ixus 115'', a digital camera.
 
@@
 appear only once in the year \cite{baeza07sigir}.
-A lot of this variety comes from syntactic variations of the same popular need and can be addressed with spell-corrections and query suggestion techniques.
-However, the remaining queries tend to be less common because they refer to less popular needs that can not be easily addressed by popularity ranking (due to the sparsity of signals), and more likely to need disambiguation or to require complex processing.
+This variety also comes from syntactic variations of the same popular need and can be addressed with spell-corrections and query suggestion techniques.
+However, the remaining queries are less common.
+They refer to less popular needs that can not be easily addressed by popularity-based ranking (due to the sparsity of signals).
+In particular,
+these two cases still remain challenging for state-of-the-art
+search systems:
 
-%\begin{itemize}
-%	\item 
-	\textbf{Ambiguous Queries:} 
-	Ambiguous queries arise naturally when the user may not be able to name precisely the item that is sought.
+\textbf{ambiguous Queries:} Ambiguous queries arise naturally when the user may not be able to name precisely the item that is sought.
 Coming back to the example of product search, a user who is in the early stages of selection may not know exactly which product to look for.
-In this case, the user may name one or two characteristics of the product, such as \emph{cheap digital camera}.
-The concept of digital camera covers a broad range of actual entities, and there might be some discussion as to which of these can be considered cheap.There are also systemic factors that lead to an increase in ambiguity.
-Despite the expectation that longer queries should leave to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ conjunctive semantics (an implicit AND operator between words), and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult.
+In this case, the user may name one or two characteristics of the product, such as ``cheap digital camera''.
+The concept of digital camera covers a broad range of actual entities, and there might be some discussion as to which of these can be considered cheap.
+%	There are also systemic factors that lead to an increase in ambiguity.
+Despite the expectation that longer queries should lead to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ conjunctive semantics (an implicit AND operator between words), and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult.
 Thus users have learned to avoid long queries, leading to shorter but more ambiguous queries.
@@
 For example, when searching for people the user may type in a name, only to realize that there are multiple persons with the same name.
-Often, this is aggravated by the bias toward a single popular answer.
+%	Often, this is aggravated by the bias toward a single popular answer.
 For example, when searching for \emph{george bush}, the top results are crowded by references to the same person, even though this is a common name.\footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}
@@
 For example, searching for this paper by the name of the second author is relatively straightforward.
-However, assuming the user does not know (or do not remember) the name, he or she might look for a \emph{semantic search survey paper written by a young researcher at yahoo}.
-Complex queries are particularly hard to address in the traditional information retrieval paradigm when they require information extraction and aggregation, i.e.
-when not all the entities and relationships are mentioned in a single document.
+However, assuming the user does not know (or do not remember) the name, he or she might look for a ``semantic search survey paper written by a young researcher at yahoo''.
+%	Complex queries are particularly hard to address in the traditional information retrieval paradigm 
+%%	when they require information extraction and aggregation, i.e. 
+%when not all the entities and relationships are mentioned in a single document.
 Queries for events naturally involve multiple entities, typically the participant in the event and a reference to another item, e.g.
-\emph{barack obama birth certificate}.
+``barack obama birth certificate''.
 %\end{itemize}
@@
 They are characterized by the requirement for a \emph{higher level understanding} of the meaning of the query and data than the level of keywords.
-As we discuss later, some semantic search approaches use this higher level, conceptual understanding of queries and data to compose answers (via reasoning or computation) that do not even explicitly appear in the data.
+%As we discuss later, some 
+%Semantic search approaches use this higher level, conceptual understanding of queries and data to compose answers (via reasoning or computation) that do not even explicitly appear in the data.
 
@@
 
-While the above problems are not new, the renewed interest in trying to address them can be explained by the increasing availability of semantic resources in terms of large data sets and schemas.
+While the above problems are not new, the renewed interest in trying to address them can be explained by the increasing availability of semantic resources in terms of document annotations (also called metadata), large datasets and schemas.
 Many semantic search systems have emerged specifically to exploit these resources.
-Here we review the main trends that have led to this development, and we return to describe the types of semantic data in more detail in Section~\ref{sec:data}.
+%The main idea behind \emph{semantic search solutions} is to use these semantic resources to improve the search performance. 
+Thesauri and particularly schemas capture semantics that can be used to understand the query and data and to \emph{resolve ambiguities}.
+Instead of returning textual data (Web pages, documents), precise facts capturing entity related information and their relationships can be directly retrieved from semantic annotations and data to \emph{provide direct answers to complex queries}.
+Here we review the main trends that have led to the availability of semantic resources, and we return to describe their types in more detail in Section~\ref{sec:data}.
 
-Semantic annotations of documents are available in increasing amounts due to advances in both Information Extraction and the adoption of standard formats for the semantic annotation of documents.
-The two developments are complementary in providing annotations for the Web.
+\textbf{Semantic Annotations:} These resources are available in increasing amounts due to advances in both Information Extraction (IE) and the adoption of standard formats for annotating documents. 
+%The two developments are complementary in providing annotations for the Web. 
 IE technology is particularly adept at extraction from large sites on the Web, where the investments in creating training data for supervised methods of learning extractors (e.g.
 wrapper induction) pay off quickly.
-On the other hand, publishers are increasingly motivated by search engine providers to provide explicit semantic annotations so that consumers do not need to apply extraction.
-Semantic annotations in this case are embedded inside HTML pages using standards such as RDFa (a W3C standard\footnote{http://www.w3.org/TR/xhtml-rdfa-primer/} for embedding RDF data in Web pages), microformats or microdata.
-The practice of annotating webpages using these formats have thus brought us closer to acquiring semantic annotations in the long tail of the Web.
+On the other hand, publishers are increasingly motivated by search engine providers to create explicit semantic annotations.
+% so that consumers do not need to apply extraction. 
+Semantic annotations in this case are embedded inside HTML pages using standards such as RDFa (a W3C standard~\footnote{http://www.w3.org/TR/xhtml-rdfa-primer/} for embedding RDF data in Web pages), microformats or microdata.
+%The practice of annotating webpages using these formats have thus brought us closer to acquiring semantic annotations in the long tail of the Web. 
 As a result of active adoption and support from Web search engines providers such as Google and Yahoo!, 10 percent of all Web pages are estimated to contain some form of semantic data markups such as RDFa~\cite{DBLP:conf/semweb/MikaMZ09}.
 
-Complementary to these efforts, the Linking Open Data\footnote{\url{http://www.w3.org/wiki/SweoIG/TaskForces/CommunityProjects/LinkingOpenData}} movement that has emerged in recent years facilitated the process of publishing entire datasets (knowledge bases) on the Web.
-Large structured datasets that have been formerly kept in closed databases are now exposed as publicly Web-accessible RDF data.
-(For a list of datasets, see the Linked Data\footnote{\url{http://linkeddata.org/}} community site or the Data Hub \footnote{\url{http://thedatahub.org/}} maintained by CKAN.) This method of publishing is often used in the area of the sciences and the government where data is in the public domain.
-Efforts are under way to link these datasets by establishing links (references between entities) in different datasets.
-Besides these domain specific datasets, broad encyclopedic knowledge bases such as Dbpedia and Freebase are now also available for research.
+\textbf{Semantic Data:} Complementary to these efforts, the Linking Open Data~\footnote{\url{http://www.w3.org/wiki/SweoIG/TaskForces/CommunityProjects/LinkingOpenData}} movement that has emerged in recent years facilitated the process of publishing entire datasets on the Web.
+Large structured datasets that have been formerly kept in closed databases are now exposed as publicly Web-accessible RDF data also called semantic data.
+(For a list of datasets, see the Linked Data~\footnote{\url{http://linkeddata.org/}} community site or the Data Hub~\footnote{\url{http://thedatahub.org/}} maintained by CKAN.) This method of publishing is often used in the area of the sciences and the government where data is in the public domain.
+%Efforts are under way to connect these datasets by establishing links (references between entities) in different datasets.
+Besides domain specific datasets, broad encyclopedic knowledge bases such as Dbpedia and Freebase are now also available for research.
 These resources are particularly valuable for supporting open domain search and query answering.
-Altogether, the Linked Data cloud is difficult to estimate in size but it contains billions of triples\footnote{\url{http://stats.lod2.eu/}}.
+Altogether, the Linked Data cloud is difficult to estimate in size but it contains billions of triples~\footnote{\url{http://stats.lod2.eu/}}.
 
-When making data available on the Web, publishers can choose the schema to publish their data.
-Many of the Linked Data datasets reflect the internal schema of the database that is being exposed.
-However, in this case the burden is on the consumer of the data to make sense of the schemas of the individual datasets and map them to a shared, global schema before being able to aggregate instance data.
+\textbf{Schemas:} Basically, a schema represents the vocabulary and the meaning of terms that are used to capture data.
+For making data available on the Web, publishers can use their own schemas to publish their data.
+%Many of the Linked Data datasets reflect the internal schema of the database that is being exposed. However, in this case the burden is on the 
+%Consumer of the data to make sense of the schemas of the individual datasets and map them to a shared, global schema before being able to aggregate the data.
 This type of schema matching is difficult and can not be fully automated in practice.
-A better approach is for publishers and consumers to agree on a shared schema and reuse that schema whenever possible.
+An approach, which facilitates a shared understanding of the data and its usage, is for publishers and consumers to agree on certain schemas and reuse them whenever possible.
 A recent example of this effort is the schema.org collaboration between the main search engine providers (currently, Bing, Google, Yahoo and Yandex).
@@
 
-The Semantic Web movement catalyzed the above developments by establishing a basic knowledge representation paradigm (RDF)\footnote{RDF stands for Resource Description Framework, a W3C Semantic Web standard for data representation and exchange on the Web: \url{http://www.w3.org/RDF/}}.
+%The Semantic Web movement catalyzed the above developments by establishing a basic knowledge representation paradigm (RDF)\footnote{RDF stands for Resource Description Framework, a W3C Semantic Web standard for data representation and exchange on the Web: \url{http://www.w3.org/RDF/}}.
 RDF is flexible enough to capture any data that can be represented as a graph and has a number of serialization formats.
@@
 
-The main idea behind semantic search solutions is to use these semantic resources to improve the search performance.
-Taxonomies, thesauri, and ontologies capture semantics that can be used to understand the query and data and to \emph{resolve ambiguities}.
-Instead of returning textual data (Web pages, documents), precise facts capturing entity related information and their relationships can be directly retrieved from semantic data to provide \emph{direct answers to complex queries}.
-
 \subsection{Commercial Interest}
 
-Capitalizing on the opportunities that arise from the already large and increasing amount of semantic resources on the Web, commercial search engines have shown increasing interest in Semantic Search.
-To call out some example, one of the first commercial search engines to employ semantic analysis was Powerset\footnote{\url{http://en.wikipedia.org/wiki/Powerset_(company)}}, which makes use of semantic data extracted from Wikipedia to answer complex questions.
+Capitalizing on the opportunities that arise from the already large and increasing amount of semantic resources on the Web, commercial search engines have shown increasing interest in semantic search.
+To call out some examples, one of the first commercial search engines to employ semantic analysis was Powerset~\footnote{\url{http://en.wikipedia.org/wiki/Powerset_(company)}}, which makes use of semantic data extracted from Wikipedia to answer complex questions.
 Yahoo!
@@
 SearchMonkey, which has been experimentally proven to help users judge the relevance of search results \cite{DBLP:conf/sigir/HaasMTB11}.
-The same method is also used by Google to provide rich result snippets\footnote{\url{http://www.google.com/webmasters/tools/richsnippets}}.
-Google also acquired Metaweb, the makers of Freebase, and widely published its intent to employ semantic search technology more extensively in the future\footnote{\url{http://on.wsj.com/w7OPag}}.
-As a last example, Facebook intends to extend its internal graph of people and other types of resources (e.g.
+The same method is also used by Google to provide rich result snippets~\footnote{\url{http://www.google.com/webmasters/tools/richsnippets}}.
+Google also acquired Metaweb, the makers of Freebase, and widely published its intent to employ semantic search technology more extensively in the future~\footnote{\url{http://on.wsj.com/w7OPag}}.
+%As a last example, Facebook intends to extend its internal graph of people and other types of resources (e.g.
 organizations with Facebook pages) with additional knowledge from webpages.
-Facebook publishes a set of schemas under the name Open Graph Protocol \footnote{\url{http://ogp.me}} for developers who want to annotate their webpages.
-OGP annotations are also used by Facebook to interpret the type of object that the user is interested in when pressing a 'Like' button on a webpage.
+Facebook publishes a set of schemas under the name Open Graph Protocol\footnote{\url{http://ogp.me}} for developers who want to annotate their webpages.
+These annotations are used by Facebook to interpret the type of object that the user is interested in when pressing a 'Like' button on a webpage.
 
@@
 Correspondingly, semantic search has been viewed from different angles, resulting in a plethora of solutions.
-Existing approaches greatly vary in the \emph{data}, (2) the \emph{semantic resources}, the \emph{information needs} and (4) the \emph{querying paradigms} that are supported.
+Existing approaches greatly vary in (1) the \emph{data}, (2) the \emph{semantic resources}, (3) the \emph{information needs} and (4) the \emph{querying paradigms} that are supported.
 Further, research work found in literatures often studies one of the specific (5) \emph{subproblems in search}: namely, different concepts and techniques have been proposed for (5a) the interpretation of query inputs and data, (5b) matching the query intent against data and (5c) ranking results.
@@
 Our work unifies the research field of semantic search by determining the key areas of research, identifying the key contributions independent of the field in which they were published and placing them in a unified framework.
-Such an overview of a state-of-the-art will enable researchers and practitioners to design and develop semantic search systems based on best-of-breed methods.
-We also reflect on the evaluation and demonstrated performance of various approaches and discuss the challenges ahead.
+%Such an overview of a state-of-the-art will enable researchers and practitioners to design and develop semantic search systems based on best-of-breed methods.
+We also reflect on the evaluation and demonstrated performance of various approaches to point at the challenges ahead.
 
-There are few studies in related work that would compare different approaches to semantic search~\cite{DBLP:conf/semweb/KaufmannB07,DBLP:conf/esws/TranMH10}.
-However, this line of work focuses on the differences in querying paradigms.
+There are few studies in related work that compare different approaches to semantic search~\cite{DBLP:conf/semweb/KaufmannB07,DBLP:conf/esws/TranMH10}.
+However, this line of work focuses on the differences in \emph{querying paradigms}.
 In a step towards a classification of semantic search approaches, Mangold discusses existing solutions along the dimensions of architecture, coupling, transparency, user context, ontology structure and ontology technology~\cite{DBLP:journals/ijmso/Mangold07}.
-The last two criteria basically capture the differences in semantic resources among existing systems, which are also discussed in our study.
+The last two criteria basically capture the differences in \emph{semantic resources} among existing systems, which are also discussed in our study.
 In addition to query paradigms and semantic resources, our study includes the aspects of data, information needs, and provides a fine-grained taxonomy that distinguishes approaches by the subproblems in search they addressing.
-Further, whereas the previous survey~\cite{DBLP:journals/ijmso/Mangold07} focuses on document retrieval, our study aims at a unified view of document and data retrieval.
+Further, whereas the previous survey~\cite{DBLP:journals/ijmso/Mangold07} focuses on document retrieval, our study aims at a unified view of document and data retrieval approaches from the major communities of IR, Database and Semantic Web.
 In particular, we cover a large body of recent work that is not part of that previous survey.
@@
 Then, the paper is organized mainly along the aspects based on which we distinguish different semantic search approaches.
-Different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and ~\ref{sec:semantics}.
+Namely, different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and~\ref{sec:semantics}.
 Then approaches are discussed along the subproblems of data interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}.

### 2012-05-14 trunk/tr-semanticsearchsurvey-data/overview.tex

@@
 		\includegraphics[width=0.35\textwidth]{figs/semsearch.pdf}
-	\caption{Semantic Search.}
+	\caption{Semantic search.}
 	\label{fig:semsearch}
+	\vspace{-0.7cm}
 \end{figure}
 
-Basically, \emph{search} can be characterized by three components, namely the \emph{data}, the \emph{query} and the \emph{matching} framework for computing results from the data for a given query.
+\emph{Search} can be characterized by three components, namely the \emph{data}, the \emph{query} and the \emph{matching} framework for computing results from the data for a given query.
 This is illustrated in the left portion of Fig.~\ref{fig:semsearch}.
-One main characteristic of search concepts is its emphasize on end users.
-That is, search typically involves intuitive interfaces targeting users, who may do not possess knowledge about the domain, the data and structured query languages.
+One main characteristic of search concepts is their emphasis on end users.
+That is, search typically involves intuitive interfaces targeting users, who may not possess knowledge about the domain, the data and structured query languages.
 The query inputs that can be obtained from these interfaces are often ambiguous.
-That is, they allow for many possible \emph{interpretation}s, which in turn, yield many possible results that vary in relevance w.r.t.~ the intended query intent.
+They allow for many possible \emph{interpretation}s, which in turn, yield many possible results that vary in relevance w.r.t.~the query intent.
 % Because end users are often only interested in the few best results, 
@@
 to distinguish results in terms of relevance.
-Basically, matching can be conceived as the task of identifying matches whereas ranking is more specifically about the degree of matching.
+Matching can be conceived as the task of identifying matches whereas ranking is more specifically about the degree of matching.
 
@@
 Considering the core search tasks, semantics has been used to obtain a better understanding of the data and query as well as to improve matching and ranking based on that (see Fig.~\ref{fig:semsearch}).
-There are exist different notions of semantics.
-One the one hand, there are proposals for using the semantics of words captured as latent concepts (e.g.
+There exist different notions of semantics.
+One the one hand, there are proposals for exploiting the hidden or implicit semantics of words based on their usage.
+This may be captured as latent concepts (e.g.
 inferred through Latent Semantic Indexing~\cite{DBLP:conf/sigir/Hofmann99}) or latent topics (e.g.
@@
 For instance, Explicit Semantic Analysis uses Wikipedia articles, categories, and relations between articles to capture semantics in terms concepts, which are then used for concept-based IR~\cite{DBLP:journals/tois/EgoziMG11}.
-Other explicit models of semantics (henceforth called \emph{semantic models}) include thesauri, the terminological part (TBox) of ontologies and data schemas.
+Other explicit models of semantics (henceforth called \emph{semantic models}) include thesauri, the terminological part (Tbox) of ontologies and schemas.
 While these models capture semantics at the conceptual level, there are also \emph{semantic data} capturing the semantics of individual entities.
@@
 
-\begin{definition} \emph{Semantic search} is a search paradigm that makes use of explicit semantics to solve core search tasks, i.e.
+\begin{definition} \emph{Semantic search} is a search paradigm that makes use of \emph{explicit} semantics to solve core search tasks, i.e.
 to use semantics for interpreting query and data, matching query against data and ranking results.
@@
 \item the representation of information resources (\emph{data}), 
-\item the representation of the information need (\textit{query}) or respectively, the underlying method for querying the data (querying paradigms), 
+\item the representation of the information need (\textit{query}) or respectively, the underlying method for querying the data (\emph{querying paradigms}), 
 \item the \emph{semantic models} used to understand and to represent the meaning behind query and data, 
@@
 
-For instance, we can look at the differences in the data to arrive at the distinction between document retrieval and data retrieval, two major research directions in search that mark the borders of large communities.
-
-\textbf{Document Retrieval:} The IR community targets the document retrieval context where results are retrieved from a collection of documents (primarily textual data).
+%%We will treat each of these aspects separately in the following sections. But 
+%As an illustration, we can look at the differences in the data to arrive at the distinction between document retrieval and data retrieval, two major research directions in search that mark the borders of large communities.
+%
+%\textbf{Document Retrieval:} The IR community targets the document retrieval context where results are retrieved from a collection of documents (primarily textual data).
 Semantic search of this type is different from standard document retrieval approaches in the use of semantics.
@@
 Recently, semantic data such as RDF resource descriptions have also been employed to interpret query and documents in terms of real-world entities and their relations.
-
-\textbf{Data Retrieval:} Querying entities and their relations is a core problem in database research.
+%
+%\textbf{Data Retrieval:} Querying entities and their relations is a core problem in database research.
 As opposed to the hidden semantics of textual content in documents, information about entities and their relations are explicitly available in this setting -- either directly as semantic data in RDF or as some kinds of structured data that can be converted to RDF.
@@
 Hence, semantic search approaches of this type have to deal with the resulting problems of interpreting the query intent and ranking the many possible results.
-%Just like in the document context, the goal here is to enable easy access to the most relevant results.
+%%Just like in the document context, the goal here is to enable easy access to the most relevant results.
 Especially in the Semantic Web community, solutions targeting this problem are also referred to as semantic search because they use semantic data to interpret the query intent and to rank results.
-
-%In this section, we establish the main dimensions in which existing solutions vary and then discussed them in more detail in the subsequent sections. 
-% and then, provide a taxonomy of semantic search approaches.
+%
+%%In this section, we establish the main dimensions in which existing solutions vary and then discussed them in more detail in the subsequent sections. 
+%% and then, provide a taxonomy of semantic search approaches.
 We focus on approaches studied by researchers in the Semantic Web community that explicitly target semantic search.
 Selectively, we also point out works from the IR and database communities that deal with the same problem.
-%Search is about retrieving information that are relevant with respect to a given information need. 
-%Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs.
-
-More fine-grained than this general breakdown into document and data retrieval, Fig.~\ref{fig:semsearch_detailed} illustrates the specific differences in queries, data, semantics, results (corresponding to information needs) and solutions for the subproblems that distinguish existing semantic search approaches.
+%%Search is about retrieving information that are relevant with respect to a given information need. 
+%%Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs.
+%
+%More fine-grained than this general breakdown into document and data retrieval, 
+Fig.~\ref{fig:semsearch_detailed} illustrates the specific differences in queries, data, semantics, results (corresponding to information needs) and solutions for the subproblems that distinguish existing semantic search approaches.
 We can see that central to semantic search is the use of semantics (depicted as gray boxes in Fig.~\ref{fig:semsearch_detailed}).
@@
 		\includegraphics[width=0.75\textwidth]{figs/semsearch_detailed}
-	\caption{Overview of Semantic Search Approaches.}
+	\caption{Overview of semantic search approaches.}
 	\label{fig:semsearch_detailed}
+	\vspace{-0.5cm}
 \end{figure*}
@@
 Research Lab Barcelona''.
-We will now discuss several common types of queries and the information needs behind them, from the more simple entity queries to complex relational and analytical queries.
+%We will now discuss several common types of queries and the information needs behind them, from the more simple entity queries to complex relational and analytical queries.
 
@@
 Thus, in the IR context, these queries are also referred to as navigational queries.
-Recently, semantic data embedded in Web pages have been exploited to address this type of queries.
-This was pioneered by Yahoo!
-in their SearchMonkey program, and later adopted by Google to present rich entity snippets\footnote{Google Rich Snippets} as answers to this kind of queries.
-As an example, Fig.~\ref{fig:semantic_layer} illustrates the entity search functionalities provided by Yahoo!.
-Not only there are Web pages but also entity descriptions appear as results.
+Recently, semantic data embedded in Web pages have been exploited to address this type of queries, e.g.
+in producing richer search result presentations.
+As an example, Fig.~\ref{fig:semantic_layer} illustrates the entity search functionalities provided by a modern search engine, Yahoo!
+Search.
+Besides individual Web pages shown as results, there are also entity descriptions displayed in separate information boxes.
 These descriptions are directly retrieved from semantic data (in this case, a dataset about music artists and their albums).
-Instead of searching over a collection of documents, semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results.
-Examples for this type of queries include the one asking for ``young scholars in Germany'' already mentioned before, or the query ``Researcher Thanh Tran'' depicted in the top left portion of Fig.~\ref{fig:matching}.
-Results for queries of this type comprise one or several entities.
+%When it comes to entity search, pure semantic search engines only differ in that they do not provide Web pages as results. 
+%Instead of searching over a collection of documents, 
+Semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results.
+An example
+%Examples for this type 
+%%of queries 
+%include 
+%the query for ``young scholars in Germany'', 
+%% already mentioned before, 
+%or 
+query is ``Researcher Thanh Tran'' depicted in the top left portion of Fig.~\ref{fig:matching}. Results for queries of this type comprise one or several entities.
 
@@
 Many searches on the Web for instance, aim at finding the ratings of restaurants, or the phone number of a particular person.
-To continue with our example, users may directly ask for ``the birth place of young scholars in Germany''.
-Direct answers to this type of queries are supported by WolframAlpha\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge\footnote{\url{http://www.trueknowledge.com/}}, or the various research prototypes such as Hermes~\cite{DBLP:journals/ws/TranWH09} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}.
+%To continue with our example, users may directly ask for ``the birth place of young scholars in Germany''. 
+Direct answers to this type of queries in the form of facts are supported by WolframAlpha~\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge~\footnote{\url{http://www.trueknowledge.com/}}, or the various research prototypes such as Hermes~\cite{DBLP:journals/ws/TranWH09} (later incorporated into a larger system called SemSearchPro~\cite{DBLP:journals/ws/TranHL11}).
+% or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}. 
 Since factual search is mostly about facts that correspond to attribute values of entities, it is often regarded as a particular type of entity search.
@@
 \subsection{Relational Search} The information need here goes beyond single entities and their factual information.
-Answers to queries of this type comprise several entities and relationships between them.
+Answers to queries of this type comprise several entities and relations between them.
 Hence, processing these queries requires some understanding of relations between entities.
-For instance, the example presented in the introduction about 32 year old computer scientists requires knowledge about their \verb+lives in+ and \verb+birth place+ relations to some locations.
+For instance, the example presented in the introduction about semantic search surveys requires knowledge about the \verb+written by+ relation between papers and researchers.
 Relations may be explicitly specified as part of the keyword or NL query, and entities satisfying these relation constraints can be computed using SemSearchPro~\cite{DBLP:journals/ws/TranHL11} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}.
@@
 
-Even though Yahoo!
+%Even though Yahoo!
 entity search as shown in Fig.~\ref{fig:screenshot_yahoo} does not directly search for relations, it can be seen on the left portion that relations between entities captured in semantic data constitute valuable information for suggesting related entities.
-Searching for known relations or unknown relations is supported by the Information Workbench\footnote{\url{http://iwb.fluidops.com}}, a commercial adoption of SemSearchPro.
-On the bottom part of Fig.~\cite{fig:screenshot_iwb}, we can see results returned to a query that specifically asks for entities connected through the \verb+producer+ relation.
+Searching for known relations or unknown relations is supported by the Information Workbench~\footnote{\url{http://iwb.fluidops.com}}, a commercial adoption of SemSearchPro.
+On the bottom part of Fig.~\ref{fig:screenshot_iwb}, we can see results returned to a query that specifically asks for entities connected through the \verb+producer+ relation.
 When relations are not explicitly given in the query but only entities and (or) concepts, this system is also able to explore paths between them.
@@
 Generally speaking, any kind of additional computation may be applied to the data and results for the purpose of analytical search.
-Analytics often found in semantic search engines are supported through simple sorting and averaging, more sophisticated statistical and mathematical models, or some form of Machine Learning based inductive reasoning or logic-based deductive reasoning.
+Analytics often found in semantic search engines are supported through simple sorting and averaging, more sophisticated statistical and mathematical models, or some form of Machine Learning (ML) based inductive reasoning or logic-based deductive reasoning.
 For instance, WolframAlpha is advertised as a computation engine because it applies different kinds of mathematical models to compute answers to queries, whereas True Knowledge uses an inference engine to perform temporal and geospatial reasoning.
@@
 	\label{fig:screenshot_yahoo}
+	\vspace{-0.5cm}
 \end{figure}
@@
 \section{Querying Paradigms}\label{sec:querying}
-Typically, addressing complex needs requires the expertise of technical users who know the underlying data and schema and use them to formulate questions as structured queries.
-However, search is commonly seen as an end-user oriented paradigm, which instead of using structured query languages, involves intuitive and easy-to use access interfaces.
-The three main interfaces studied for semantic search are based on keywords, NL, and facets.
+Typically, addressing complex needs requires the expertise of technical users who know the underlying data and schemas and use them to formulate questions as structured queries.
+However, as an end-user oriented paradigm,
+%which instead of using structured query languages, 
+search requires more intuitive and easy-to use access interfaces. 
+%The three main interfaces studied for semantic search are based on keywords, NL, and facets.
 Often, a combination of these paradigms, e.g.
-keywords and facets, is used to support an iterative search process where instead of constructing the query at once, the user modifies the query and results respectively, through a series of operations.
+keywords and facets, is used to support an iterative search process where
+%%instead of constructing the query at once, 
+%the user modifies the query and results respectively, through a series of operations.
 
@@
 Keywords can also be used to formulate more complex relational searches.
-Addressing this scenario, engines such as Hermes~\cite{DBLP:journals/ws/TranWH09}, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}, TASTIER~\cite{DBLP:conf/sigmod/LiJLF0} and IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} retrieve entities matching keywords, and search for relations between them in the data.
+Addressing this scenario, engines such as SemSearchPro~\cite{DBLP:journals/ws/TranHL11}, TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} and IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} retrieve entities matching keywords, and search for relations between them in the data.
 
-\subsection{NL Search} This is the other paradigm for users to express their needs using their own words.
+\subsection{NL Search} Complete natural language questions and statements are a natural paradigm for users to express themselves fully in their own words.
 Traditionally, it has been used to pose complex questions against expert systems built for specific domains.
-Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha, True Knowledge and Apple's Siri\footnote{\url{http://en.wikipedia.org/wiki/Siri_(software)}}.
+Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha, True Knowledge and Apple's Siri~\footnote{\url{http://en.wikipedia.org/wiki/Siri_(software)}}.
 
-\subsection{Faceted Search} Instead of formulating the entire query at once, \emph{faceted search} supports an iterative process of querying, browsing and query refinement.
+\subsection{Faceted Search} Instead of formulating the entire query at once, faceted search supports an iterative process of querying, browsing and query refinement.
 This belongs to the broader category of approaches called \emph{exploratory search}, which assumes that users do not precisely know how or what to search and thus, combines querying and browsing strategies to enable learning and investigation.
 Upon the initial search performed by the user (e.g.
-using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/semweb/FerreH11,DBLP:conf/esws/HeimEZ10} present results as well as facets representing attributes and relations that are applicable for refining (or simply, are related to) the current results.
+using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/esws/HeimEZ10} present results as well as facets representing attributes and relations that are applicable for refining (or simply, are related to) the current results.
 These facets can then be used to browse, to refine or to expand the results (i.e.
 to modify the query, respectively).
-Microsoft's EntityCube\footnote{\url{http://entitycube.research.microsoft.com/}} for instance, returns entities upon users' keyword search requests along with relations and attributes of these entity results as facets.
-Parallax\footnote{\url{http://www.freebase.com/labs/parallax/}} is another commercial faceted search solution (from Freebase, now Google) that enables a combination of search, intelligent result visualization and facet-based browsing.
+Microsoft's EntityCube~\footnote{\url{http://entitycube.research.microsoft.com/}} for instance, returns entities upon users' keyword search requests along with relations of these entity results as facets.
+%Parallax~\footnote{\url{http://www.freebase.com/labs/parallax/}} is another commercial faceted search solution (from Freebase, now Google) that enables a combination of search, intelligent result visualization and facet-based browsing.
 
@@
 \subsection{Iterative / Exploratory Search} 
-While faceted search is the most popular paradigm in the industry, there are other exploratory search interfaces that support an \emph{iterative search} process.
+While faceted search is the most popular paradigm in the industry, there are other exploratory search interfaces that support an iterative search process.
 Instead of showing facets as users type, also \emph{completions} of the single user keywords (term completions) or of the entire query representing the full query intent (query completions) have been proposed.
 One example system supporting this is the Information Workbench shown in Fig.~\ref{fig:screenshot_iwb}, which presents terms matching the current tokens entered by the users, as well as full interpretations of the entire query.
-For ``queen single'', the interpretations shown indicate that the query intent may be something matching the word ``queen'' that is of the type \verb+single+, or something that is of the type \verb+single+, which is produced (or written) by something else matching the word ``queen''.
-Google, Freebase\footnote{\url{http://www.freebase.com/docs/suggest}} and True Knowledge also present possible interpretations of the query as the user type or after issuing a query.
+For ``queen single'', the interpretations shown indicate that the query intent may be something matching the word ``queen'' that is of the type \verb+single+.
+%, or something that is of the type \verb+single+, which is produced (or written) by something else matching the word ``queen''. 
+Web search engines, Freebase~\footnote{\url{http://www.freebase.com/docs/suggest}} and TrueKnowledge also present possible interpretations of the query as the user type or after issuing a query.
 
-Instead query-based completions, also results matching the (possible interpretations of the) keywords provided so far have been presented (called result completions~\cite{DBLP:conf/esws/TranMH10}).
+%Instead of query-based completions, also results matching the (possible interpretations of the) keywords provided so far have been presented (called result completions~\cite{DBLP:conf/esws/TranMH10}).
 For instance, ESTER~\cite{DBLP:conf/sigir/BastCSW07} shows entity search results matching the keywords as well as their facets (see CompleteSearch~\footnote{\url{http://www.dblp.org/search/index.php}}, which is an adoption of ESTER) whereas TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} provides type-ahead search by finding complex (joins of) database tuples as the user types query keywords.
+
 With these systems, users can iteratively construct the query by selecting the presented completions and facets.
@@
 	\label{fig:screenshot_iwb}
+	\vspace{-0.5cm}
 \end{figure}
@@
 
-Basically, semantic data describe real-world objects in terms of entities and their relations.
-Primarily, semantic data have been used to refer to RDF datasets, or instance data contained in ontologies represented in Semantic Web languages such as OWL (the Web Ontology Language, a logic-based W3C standard\footnote{http://www.w3.org/TR/owl-features/} for representing the semantics of vocabulary / schema elements) and RIF (the Rule Interchange Format, a W3C standard for representing and exchanging rules).
-However, different kinds of structured data actually correspond to this rather general notion of semantic data.
-In fact, large amounts of structured data formerly kept in hidden
-%XML or relational 
-Web databases 
-have been converted to and published on the Web as RDF data.
-Several semantic search systems have been built that specifically target the retrieval of semantic data.
-Instead of searching directly over semantic data, classic retrieval systems search over a raw data representation of information objects such as audios, videos, images and texts.
+Semantic data describe real-world objects in terms of entities and their relations.
+Primarily, semantic data have been used to refer to RDF datasets, or instance data contained in ontologies represented in Semantic Web languages such as OWL (the Web Ontology Language, a logic-based W3C standard~\footnote{http://www.w3.org/TR/owl-features/} for representing the semantics of vocabulary / schema elements).
+% and RIF (the Rule Interchange Format, a W3C standard for representing and exchanging rules). 
+% However, different kinds of structured data actually correspond to this rather general notion of semantic data. In fact, large amounts of structured data formerly kept in hidden 
+%%XML or relational 
+%Web databases 
+%have been converted to and published on the Web as RDF data.
+
+Several semantic search systems have been built that specifically target the retrieval of semantic data,  in contrast to classic retrieval systems that search over raw information objects such as audios, videos, images and texts.
 For instance, document retrieval systems search for textual documents that are represented as bags of words.
 As opposed to semantic data, raw data do not explicitly capture the semantics of information resources in terms of entities and their relations.
-Thus, for supporting document (or image, video or audio) retrieval as semantic search, one core subtask is the recognition of named entity in the raw text.
-Named entity recognition and other data interpretation tasks such as relation extraction are performed to obtain a semantic data representation of raw data (also called \emph{semantic metadata}).
+Thus, for supporting document (or image, video or audio) retrieval as semantic search, one core subtask is the recognition of entities and their relationships in the raw text.
+Named entity recognition and other data interpretation tasks such as relation extraction are performed to obtain a semantic data representation of raw data (also called \emph{semantic metadata}, or annotations).
 
@@
 This general graph-structured model can be used to capture structured data of different types.
-In fact, most of the data made publicly available on the Web and incorporated into semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09}, Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} and Hermes~\cite{DBLP:journals/ws/TranWH09} originate from relational or XML databases.
+In fact, most of the data made publicly available on the Web and incorporated into semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09}, Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} and SemSearchPro~\cite{DBLP:journals/ws/TranHL11} originate from relational or XML databases.
 XML elements can be represented as nodes, and their structure information can be captured as edges.
 Likewise, information contained in tuples of a relation database can be mapped to nodes, while foreign key relationships can be modeled as edges.
-In fact, the conversion of XML and relational data to a RDF semantic data graph can be accomplished by using mapping rules, and there exist many standards and tools for accomplishing that (e.g.
-see W3C RDB2RDF\footnote{\url{http://www.w3.org/2001/sw/rdb2rdf/}}).
+The conversion of XML and relational data to a RDF semantic data graph can be accomplished by using mapping rules, and there exist many standards and tools for accomplishing that (e.g.
+see W3C RDB2RDF~\footnote{\url{http://www.w3.org/2001/sw/rdb2rdf/}}).
 Represented as RDF, these and possibly other types of structured data also capture information about real-world objects in terms of entities and their relations.
@@
 contains mainly textual data), it fits the presented notion of semantic data because every Wikipedia page corresponds to an entity, and there are links between Wikipedia pages that can be seen as relations.
-In fact, exploiting this and other specific features of Wikipedia articles such as Infoboxes, a RDF dataset called DBpedia~\cite{DBLP:journals/ws/BizerLKABCH09} has been automatically derived from this collection.
+%In fact, exploiting this and other specific features of Wikipedia articles such as Infoboxes, a RDF dataset called DBpedia~\cite{DBLP:journals/ws/BizerLKABCH09} has been automatically derived from this collection.
 Wikipedia as a source of semantics is particularly popular for search systems that focus on expert search or entity search in general.
@@
 \textbf{Structured Entity Descriptions:} This type of semantic data is ubiquitous on the Web, capturing information about real-world objects as RDF resource descriptions (or structured entity descriptions that can be directly converted to RDF).
-Through industry efforts such as Yahoo's SearchMonkey, Google's Rich Snippets and Facebook Like\footnote{\url{http://developers.facebook.com/docs/reference/plugins/like/}}, a large amount of RDF descriptions of resources such as restaurants and movies have been embedded into existing Web pages as RDFa.
+As discussed in the introduction, the amount of RDF data embedded in webpages or are made available as Linked Data is large and rapidly increasing.
+
+%Through industry efforts such as Yahoo's SearchMonkey, Google's Rich Snippets and Facebook's Open Graph Protocol, a large amount of RDF descriptions of resources such as restaurants and movies have been embedded into existing Web pages as RDFa.
 Besides, hundreds of large-scale RDF datasets have been made available on the Web.
 Started with the Linking Open Data, more and more data are made freely available on the Web and linked with other public datasets.
-Not only Web content providers but many companies, public institutions and national governments (US, UK etc.) are now actively publishing and linking RDF data on the Web (called Linked Data).
-Availably datasets can be subdivided into broad/domain-independent ones such as as DBpedia and Freebase\footnote{\url{http://www.freebase.com/}} or deep/domain-specific ones.
+Not only Web content providers but many companies, public institutions and national governments (US, UK etc.) are now actively publishing and linking RDF data on the Web.
+Availably datasets can be subdivided into broad/domain-independent ones such as as DBpedia and Freebase~\footnote{\url{http://www.freebase.com/}} or deep/domain-specific ones.
 Large domains covered by Linked Data today include government, health care, entertainment and geography.
@@
 the knowledge that is entailed by the semantics).
-While the formal model of semantics specified for RDF is relatively simple (consists only of a few inference rules), semantic data in some existing search systems are represented using more expressive knowledge representation languages such as OWL and F-logic~\cite{DBLP:conf/sigmod/KiferL89} (basically, a combination of logic and object-oriented frame-based languages).
-For instance, Serene~\cite{DBLP:journals/ws/FazzingaGGL11} makes use of facts that are captured as Abox assertions (i.e.
-instance data, as opposed to Tbox, the schema part) of an OWL ontology.
-ORAKEL~\cite{DBLP:journals/dke/CimianoHHMS08} searches over an F-logic knowledge base.
-However, while the use of formal semantics and reasoning has been investigated for some scenarios, it plays only a limited role in existing systems.
-The
-majority of approaches does not rely on reasoning.
-It seems that the research focus still lies in correctly understanding the ambiguous queries and data (namely, to interpret queries and data as elements of the semantic data model as defined above), while reasoning over semantic data may be beneficial but not essential yet.
+While the formal model of semantics specified for RDF is relatively simple (consists only of a few inference rules), semantic data in some existing search systems are represented using more expressive knowledge representation languages such as OWL and F-logic.
+%~\cite{DBLP:conf/sigmod/KiferL89} (a combination of logic and object-oriented frame-based languages). 
+For instance, Serene~\cite{DBLP:journals/ws/FazzingaGGL11} makes use of facts that are captured as Abox assertions (i.e. instance data, as opposed to Tbox, the schema part) of an OWL ontology. 
+% ORAKEL~\cite{DBLP:journals/dke/CimianoHHMS08} searches over an F-logic knowledge base. 
+%However, 
+%While the use of formal semantics and reasoning has been investigated for some scenarios (e.g.
+and applied by commercial engines such as True Knowledge for some problems), we observed it is not the focus of current semantic search research, possibly because capturing formal models of semantics is a difficult tasks and exploiting them
 
-To sum up, a general notion of semantic data is employed in this work to consider all those systems, which capture the semantics of information resources and real-world objects as entities and relations.
+%% used it plays only a limited role in existing systems as the 
+%%majority of approaches does not rely on reasoning but focuses . 
+%%
+%%It seems that the research 
+%focus still lies in correctly understanding the ambiguous queries and data (namely, to interpret queries and data as elements of the semantic data model as defined above), while reasoning over semantic data may be beneficial but not essential yet.
+
+%To sum up, a general notion of semantic data is employed in this work to consider all those systems, which capture the semantics of information resources and real-world objects as entities and relations.
 Often, these entities and relations are specified on the account of a formal data model with well-defined semantics (e.g.
@@
 	\centering
-		\includegraphics[width=0.5\textwidth]{figs/matching.pdf}
+		\includegraphics[width=0.5\textwidth]{figs/matching}
 	\caption{Examples for semantic data, queries and matching techniques.}
 	\label{fig:matching}
+	\vspace{-0.5cm}
 \end{figure}
 
-There are engines operating directly on semantic data to provide direct answers (data retrieval systems).
-These are mainly systems, which provide search interfaces over RDF data and ontologies crawled from the Semantic web~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TranWH09,DBLP:journals/ws/HoganHUKPD11}, or structured databases that have been converted to semantic data graphs~\cite{DBLP:conf/sigmod/LiJLF09,DBLP:conf/sigmod/LiOFWZ08}.
+\subsection{Semantic Metadata}
+%There are engines operating directly on semantic data to provide direct answers (data retrieval systems).
+These are mainly systems, which provide search interfaces over RDF data and ontologies crawled from the Semantic Web~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TranWH09}, or structured databases that have been converted to semantic data graphs~\cite{DBLP:conf/sigmod/LiJLF09}.
 Besides them, there are also semantic search systems supporting the retrieval of documents or information objects in general.
@@
 
-\subsection{Semantic Metadata}
-Basically, semantic metadata is semantic data that captures information about the objects to be retrieved.
-Because it is clear from the context, these two terms are often used synonymously (in this work).
+Besides engines operating directly on semantic data (data retrieval systems), there are also systems targeting the retrieval of documents or information objects in general.
+They employ semantic metadata, often in combination with the raw data representation of these objects.
+We call semantic metadata any kind of semantic data that provides additional information about the objects to be searched.
+Later, we also use the term document \emph{annotation} to refer to metadata created for text.
 Metadata include basic information about the objects such as \verb+author+ and the \verb+year+ it was published.
@@
 For instance, if a particular Web page is about a restaurant, its metadata may contain a structured description of that restaurant (as RDFa) corresponding to the text contained in the page.
-In fact, one main challenge in semantic search is to interpret the semantics behind the content of information objects and to represent it as semantic metadata.
+%In fact, one main challenge in semantic search is to interpret the semantics behind the content of information objects and to represent it as semantic metadata.
 Not only entities may be recognized but for instance, the content of a document may be interpreted as referring to a \verb+meeting+ with the two \verb+researchers+ \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participants+.
-Semantic metadata representing the content may also be manually produced and embedded into the objects.
-Recently, several industry projects such as Google Rich Snippets and Yahoo!
-SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages.
-Complementary to this,  schema.org\footnote{\url{http://schema.org/}} is an initiative promoted by major Web search companies (Google, Microsoft, Yahoo!) aiming at the provision of a common vocabulary that can be used by site owners to capture their data.
+Semantic metadata representing the content may also be manually produced and embedded into the objects such as PDF documents or HTML pages.
 In this regard, we note that while Wikipedia can be conceived as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).
 
-While the amount of available metadata is increasing, it is still too sparse to cover all information needs.
+While the amount of available metadata is increasing, most Web pages are still not explicitly annotated and not amenable to IE.
+Semantic metadata is thus still too sparse to cover generic information needs.
 Thus, metadata is mostly used as additional information that can help to improve standard search over raw data~\cite{DBLP:journals/tkde/CastellsFV07,DBLP:journals/ws/FernandezCLVCM11}.
-Search over raw data can also be seen as a fall-back solution for cases where metadata cannot completely satisfy the information need.
-There exist also 	proposals for ontology-based IR, which completely rely on metadata~\cite{tran2007expressive}.
+%Search over raw data can also be seen as a fall-back solution for cases where metadata cannot completely satisfy the information need. 
+There exist also proposals for ontology-based IR, which completely relies on metadata~\cite{DBLP:conf/sigmod/KandoganKRVZ06}.
 In this case, the retrieval of documents is formulated as a data retrieval task, where data about the documents (metadata) are returned as direct answers.
@@
 	\label{fig:semantic_layer}
+	\vspace{-0.5cm}
 \end{figure}
@@
 by matching queries against semantic data), or as a semantic resource to interpret raw data and queries (as we shall see in more detail in subsequent sections).
-More specifically, Fig.~\ref{fig:semantic_layer} shows that in the textual raw data context, these semantics can be used to interpret words in terms of entities and relations.
-It also shows the other sources of semantics called semantic models.
-Broadly, \emph{lexical models}, which capture semantics at the level of words in terms of concepts, can be distinguished from \emph{knowledge models}, which capture real-world knowledge in terms of entity classes, relations, and attributes.
+More specifically, Fig.~\ref{fig:semantic_layer} also shows
+%that in the textual raw data context, this type of semantics can be used to interpret words in terms of entities and relations. It also shows the 
+other sources of semantics called semantic models, namely \emph{lexical} and \emph{knowledge models}. 
+%Broadly, \emph{lexical models}, which capture semantics at the level of words in terms of concepts, can be distinguished from \emph{knowledge models}, which capture real-world knowledge in terms of entity classes, relations, and attributes.
 
-We have discussed semantic data as one source of semantics in the previous section.
-In this section, we provide an overview of the semantic models used by current systems, and subsequently, present a notion of semantics that combines the instance-level semantics captured by the data and the schema-level (conceptual) semantics captured by the semantic models.
+%We have discussed semantic data as one source of semantics in the previous section.
+In this section, we provide an overview of the semantic models used by current systems, and subsequently, present a notion of semantics that combines the \emph{instance-level} semantics captured by the data and the \emph{schema-level} (conceptual) semantics captured by the semantic models.
 
-\subsection{Knowledge Models} While semantic data capture concrete entities (instances), these are abstract models of knowledge, basically representing classes of entities, attributes associated with these classes, and relations between classes.
+\subsection{Knowledge Models} While semantic data capture concrete entities (instances), these are abstract models of knowledge, representing classes of entities, attributes associated with these classes, and relations between classes.
 This is visualized in the top left portion of Fig.~\ref{fig:semantic_layer}.
@@
 
-Also, \emph{conceptual graphs} (CGs) have been employed for representing ontology models, and used for the tasks of NL questions interpretation and answering~\cite{DBLP:conf/aswc/CaoCT08} as well as for interpreting and representing documents~\cite{DBLP:conf/iccs/ComparotHH07}.
+Also, \emph{conceptual graphs} (CGs) have been employed for representing ontology models~\cite{DBLP:conf/ecai/CorbyDF04}, and used for the tasks of NL questions interpretation and answering~\cite{DBLP:conf/aswc/CaoCT08} as well as for interpreting and representing documents.
 CGs combine the intuitiveness of graph-based languages and the formal foundation of logics, enabling the modeling of knowledge in terms of concepts and their relations and its mapping to different formal languages.
-Corese~\cite{DBLP:conf/ecai/CorbyDF04} uses CGs as an internal model (to take advantage of previous work on CGs in the KR community), which however, are then translated to RDFS to conform with this more commonly used standard language for representing RDF schemas.
+%Corese~\cite{DBLP:conf/ecai/CorbyDF04} uses CGs as an internal data model. 
+% (to take advantage of previous work on CGs in the KR community), which however, are then translated to RDFS to conform with this more commonly used standard language for representing RDF schemas.
 
@@
 While concepts in knowledge models stand for classes of real-world entities, concepts in lexical models correspond to \emph{senses of words}.
-Lexical concepts are more general such that they may refer to entities, classes, relations, attributes, or other senses of words.
+%This also means that lexical models are limited to capture concepts for which words have been created in a given human language. 
+Lexical concepts are more heterogeneous such that they may refer to entities, classes, relations, attributes, or other senses of words.
 While these different ``types'' of senses are not explicitly distinguished like in a knowledge model, concepts can be organized along lexical relationships in a lexical model.
 
-\emph{Thesaurus} 
+A \emph{thesaurus} 
 %(often, \emph{lexicon} is also used as synonym) 
-is a popular lexical model that has been extensively used for document retrieval in IR, which basically, groups words together according to their semantic similarity.
+is a popular lexical model that has been extensively used for document retrieval in IR, which groups words together according to their semantic similarity.
 Each group represents a different word sense.
-In practice, lexical databases also considered as thesauri such as WordNet, or thesauri used in classic IR systems~\cite{DBLP:conf/sigir/Giger88}, not only capture senses (concepts) and their lexical variants, but also relationships between them such as synonym, broader, narrower and related.
+In practice, lexical databases also considered as thesauri such as WordNet,
+%or thesauri used in classic IR systems~\cite{DBLP:conf/sigir/Giger88}, 
+not only capture senses (concepts) and their lexical variants, but also relationships between them such as synonym, broader, narrower and related.
 This is illustrated in the bottom part of Fig.~\ref{fig:semantic_layer}.
+
+A \emph{lexicon} also aims to capture the meanings of words that is often used as a synonym for thesaurus.
+However, lexicons in semantic search systems mostly go beyond that, providing concrete mappings of words to elements in the lexical or knowledge model.
 
@@
 
-A prominent example that can be used to illustrate these many aspects of semantics is Wikipedia.
-As discussed, it has been used as semantic data to answer entity search queries, and converted to a semantic dataset called DBpedia~\cite{DBLP:journals/ws/BizerLKABCH09}.
+A prominent example that can be used to illustrate these many aspects of semantics is Wikipedia. As discussed, it has been used as a type of semantic data to answer entity search queries. 
+%, and converted to a semantic dataset called DBpedia
+%~\cite{DBLP:journals/ws/BizerLKABCH09}. 
 The Wikipedia categories of pages have been treated as classes and used to construct hierarchies of classes in an ontology called YAGO~\cite{DBLP:conf/www/SuchanekKW07}.
@@
 Because ESA does not distinguish entities from classes, the concepts here can be seen as capturing word senses.
-Thus, Wikipedia pages and links constitute a lexical model in this context.
+Thus, Wikipedia pages and links constitute a lexical model in this regard.
 
@@
 For instance, the employed formalisms have been used to represent temporal or fuzzy aspects of world knowledge.
-However, there are practical reasons why the focus of current research (and this paper) is set on simple descriptions of entities (via attribute and binary relations).
-On the one hand,
+However, most semantic search systems, whether document or data retrieval systems, rely primarily on the semantics of entities and relations.
+
+There are practical reasons why the focus of current research (and this paper) is set on simple descriptions of entities (via attribute and binary relations). On the one hand, 
 %most queries on the Web ask about entities and their relations. That is, 
@@
 It became evident that manually capturing the content of documents as complex logical formulas does not scale.
-Extracting entities and relations from documents at high quality still remain hard problems, representing the limits of what can be done automatically by data extraction technologies.
-Also, most of the data residing in databases nowadays are mainly about entities and their relations.
+Extracting entities and relations from documents at high quality still remain hard problems, representing the limits of what can be done automatically by IE technologies.
+Also, most of the data residing in databases or published on the Web (as RDF) today, are mainly about entities and their relations.
 
@@
   \label{fig:extraction}
+  \vspace{-0.5cm}
 \end{figure*}
 
-\section{Content Interpretation}\label{sec:content}
+\section{Document Interpretation}\label{sec:content}
 
@@
 as semantic data or elements of a semantic model.
-In fact, there is a dedicated area of research focusing on this problem of knowledge extraction from text.
+In fact, there is a dedicated area of research focusing on this problem of IE from text.
 Problems that have been studied include named entity recognition, semantic role labeling and relation extraction.
 For an overview of solutions proposed in this area, we refer the interested readers to surveys specifically focused on this problem~\cite{DBLP:journals/tkde/ChangKGS06}.
-Here, we discuss the kind of knowledge extraction that has been performed for the purpose of semantic search.
+Here, we discuss the kind of IE that has been performed for the purpose of semantic search.
 
@@
 
-Documents have been analyzed to extract concepts for the task of modeling documents as conceptual graphs~\cite{DBLP:conf/iccs/ComparotHH07}.
-For C-Search~\cite{DBLP:conf/esws/GiunchigliaKZ09}, which represent documents as DL concepts corresponding to WordNet senses, the authors identify words in documents matching Wordnet senses (i.e.
-direct matching), and uses part-of-speech (POS) tagging information and Wordnet, as lexical database of senses and word-level relationships, to perform word sense disambiguation.
+Documents have been analyzed to extract concepts for the task of modeling documents as conceptual graphs~\cite{DBLP:conf/ecai/CorbyDF04}.
+For C-Search~\cite{DBLP:conf/esws/GiunchigliaKZ09}, which represents documents as DL concepts corresponding to WordNet senses, the authors identify words in documents matching Wordnet senses (i.e.
+direct matching), and uses part-of-speech (POS) tagging information and Wordnet, as a lexical database of senses and word-level relationships, to perform word sense disambiguation.
 While words are mapped to atomic concepts, phrases are represented as complex concepts using DL formulas~\cite{DBLP:conf/esws/GiunchigliaKZ09}.
@@
 One of the platforms, which is frequently used by semantic search systems for extracting semantic data and
-automatically annotating document collections at a large scale is KIM~\cite{KIM DBLP:journals/ws/KiryakovPTMO04}.
-IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} makes use of UIMA, a framework of annotators that can be configured in a pipeline to analyze and extract data from text.
-There is a another work from IBM, which focuses on extracting named entities and relations from text and using them for more precise search (employing XML fragments as queries~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}).
+automatically annotating document collections at a large scale is KIM~\cite{DBLP:journals/ws/KiryakovPTMO04}.
+IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} makes use of UIMA~\footnote{\url{http://uima.apache.org/}}, a framework of annotators that can be configured in a pipeline to analyze and extract data from text.
+Another work from IBM focuses on extracting named entities and relations from text and using them for more precise search (employing XML fragments as queries~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}).
 
@@
 As for most text interpretation tasks, a syntactic analysis of the text is needed.
-In this case, the typical analysis includes tokenization, POS tagging, chunking sentences into noun phrases, and some data extraction systems even derive entire parse trees from the text.
-Besides the syntactic information derived from text analysis, different semantic resources are used.
-In particular, Gazetteers are frequently used, which can be seen as a lexical model.
+In this case, the typical analysis includes tokenization, POS tagging, chunking sentences into noun phrases, and some IE systems even derive entire parse trees from the text.
+Different semantic resources may be employed besides the syntactic information derived from text analysis.
+In particular, Gazetteers are frequently used.
+%, which can be seen as a lexical model. 
 The simplest way for detecting entities is simply to match words (tokens) against Gazetteer's entries representing entities of different classes.
-For disambiguating named entities mentions in text, it has been shown that semantic data about entities and their relations provides valuable information~\cite{DBLP:conf/esws/KlebA10}.
+For disambiguating named entity mentions in text, it has been shown that semantic data about entities and their relations provides valuable information~\cite{DBLP:conf/esws/KlebA10}.
 The technique behind this is based on graph traversal, which starts from nodes matching the entity mentions.
@@
 These contextual interpretations are then used for disambiguation.
-This resembles the general technique called collective matching, which applied to this case, assumes entity mentions (words) to form a context.
+%This resembles the general technique called collective matching, which applied to this case, assumes entity mentions (words) to form a context.
 We have a higher a confidence that a word matches an entity $e$, when other words in this context, match entities related to $e$, i.e.
@@
 works for ?+, matching texts can be identified and relevant entities and relations can be extracted.
-Matching patterns are specified manually or learned automatically through machine learning techniques for pattern induction.
-Current state-of-the-art data extraction programs in fact, not only use simple word patterns, but complex combination of features derived from the words (e.g.
-orthographic features such as whether the word contain digits or hyphens, word types such as lowercased and capitalized and syntactic features such as POS information), from the context (i.e.
-words in a text window along with their tags, labels etc.) as well as from background knowledge (e.g.
+Matching patterns are specified manually or learned automatically through ML techniques for pattern induction.
+Current state-of-the-art IE programs in fact, not only use simple word patterns, but complex combination of features derived from the words (e.g.
+orthographic
+%features 
+%such as whether the word contain digits or hyphens, word types such as lowercased and capitalized 
+and syntactic features such as POS information), from the context 
+%(i.e. words in a text window along with their tags, labels etc.) 
+as well as from background knowledge (e.g.
 from Gazetteers).
 These features along with labeled training examples are then used to train a classifier (one for every entity / relation type) or a probabilistic sequence model such as the Conditional Random Field~\cite{DBLP:conf/icml/ZhuNWZM05}.
-Besides these learning methods proposed for targeted information extraction, which assume a fixed set of predefined types of entities / relations to be extracted, there are also proposals for open information extraction~\cite{DBLP:conf/ijcai/EtzioniFCSM11}.
-So far, semantic search systems focus on the use of targeted information extraction tools (e.g.
+Besides these learning methods proposed for targeted IE, which assume a fixed set of predefined types of entities / relations to be extracted, there are also proposals for open IE~\cite{DBLP:conf/ijcai/EtzioniFCSM11}.
+So far, semantic search systems focus on the use of targeted IE tools (e.g.
 IBM's UIMA, SOFIE~\cite{DBLP:conf/www/SuchanekSW09}).
-While they provide lower coverage, the quality of extracted outputs is higher compared to open extraction tools, an aspect shown to be very influential in improving the precision of semantic search results~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}.
-Promising is the combined usage of targeted and open information extraction, a direction currently pursuit by Microsoft's EntityCube.
+While they provide lower coverage, the quality of extracted outputs is higher compared to open IE tools, an aspect shown to be very influential in improving the precision of semantic search results~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}.
+Promising is the combined usage of targeted and open IE, a direction currently pursuit by Microsoft's EntityCube~\cite{DBLP:conf/www/ZhuNLZW09}.
 
-Many patterns and particularly rules used for extraction explicitly capture when candidates can be considered as matches, i.e.
+Many patterns and particularly rules used for IE explicitly capture when candidates can be considered as matches, i.e.
 when they are considered as belonging to some types of entities or relations.
-These patterns can be seen as sources of semantics that feed as inputs to the extraction systems.
-Besides these matching-specific knowledge, also general as well as domain-specific knowledge stored in ontologies have been used as semantic constraints to filter matches, i.e.
+These patterns can be seen as sources of semantics that feed as inputs to the IE systems.
+Besides these matching-specific knowledge, also
+%general as well as 
+(domain-specific) knowledge stored in ontologies have been used as semantic constraints to filter matches, i.e.
 those that lead to semantic inconsistencies.
 For instance, SOFIE~\cite{DBLP:conf/www/SuchanekSW09} prunes extraction outputs that do not satisfy the semantic constraints captured by YAGO.
-As an example, having the pattern \verb+ ?x is mayor of ?y+ and the knowledge that \verb+ x, mayorOf, y+ requires \verb+ x, type, Person+ and \verb+ y, type, City+, we can filter out those extracted \verb+is mayor of+ relations that do not involve a person or a city.
+As an example, having the pattern \verb+ ?x is mayor of ?y+ and the knowledge that \verb+ x,mayorOf,y+ requires \verb+ x,type,Person+ and \verb+ y,type,City+, we can filter out those extracted \verb+is mayor of+ relations that do not involve a person or a city.
 
 \section{Query Interpretation}\label{sec:query} 
-	Essentially, interpreting queries is similar to the task of understanding text in documents.
-However, these problems are studied from different viewpoints by overlapping but not same communities of researchers.
+	Interpreting queries is similar to the task of understanding text in documents.
+However, these problems are studied from different viewpoints by partially overlapping communities of researchers.
 Thus, the emphases are put on different subproblems.
-Further, besides NL text, also keywords may be provided as inputs to query interpretation.
-Keywords are different from NL text in the amount of syntactic features that can be obtained.
+%	Further, besides NL text, also keywords may be provided as inputs to query interpretation. Keywords are different from NL text in the amount of syntactic features that can be obtained.
 
@@
 
-Compared to detecting concepts in text as illustrated in Fig.~\ref{fig:detecting_concepts}, solutions to the problem of detecting concepts in queries are different in the usage of features: Keywords are also matched and disambiguated against a thesaurus.
+Compared to detecting concepts in text as illustrated in Fig.~\ref{fig:detecting_concepts}, solutions to the problem of detecting concepts in queries are different in the usage of features: keywords are also matched and disambiguated against a thesaurus.
 However, there is no syntactic information such as POS tags that can be exploited.
@@
 Concept-based IR is especially needed in the biomedical domain due to the frequent presence of acronyms, homonyms and synonyms.
-For detecting the underlying concepts, many lexical resources that are abundantly available for this domain, such as the Online Dictionary of Abbreviations from MEDLINE, the MESH thesaurus and the Gene Ontology have been used~\cite{DBLP:conf/sigir/ZhongH06,DBLP:conf/trec/JelierSEWMSMK03}.
-The detected concepts are used to expand the query~\cite{DBLP:conf/sigir/QiuF93,DBLP:conf/trec/JelierSEWMSMK03}.
+For detecting the underlying concepts, many lexical resources that are abundantly available for this domain, such as the Online Dictionary of Abbreviations from MEDLINE, the MESH thesaurus and the Gene Ontology have been used~\cite{DBLP:conf/sigir/ZhongH06}.
+The detected concepts are used to expand the query~\cite{DBLP:conf/sigir/QiuF93}.
 Concept-based query expansion \cite{DBLP:conf/sigir/QiuF93} for instance, detects the concept behind the query, and performs selection and weighting of additional search terms directly based on this concept (instead of the query terms).
-This and other works in this area, were based on the use of thesauri that capture concepts and relationships.
-WordNet for instance, was use to represent concepts by WordNet synonym sets, and for expanding query terms by following WordNet links \cite{DBLP:conf/sigir/Voorhees93}.
-WordNet links (is-a in particular) were also used to disambiguate query terms and to choose their senses \cite{DBLP:conf/sigir/Voorhees94}.
+Most commonly, the authors use the English language WordNet thesaurus to represent concepts by WordNet synonym sets, and for expanding query terms by following WordNet links \cite{DBLP:conf/sigir/Voorhees93}.
+WordNet links (is-a in particular) have also been found beneficial in disambiguating query terms and in choosing their senses \cite{DBLP:conf/sigir/Voorhees94}.
 
-Recently, a technique based on the idea of relevance model has been proposed to recognize the concepts underlying the query, referred to as conceptual query modeling~\cite{DBLP:journals/ipm/MeijTRK10}.
-Instead of detecting the concepts based on a thesaurus, this approach retrieves the top pseudo-relevance feedback documents through an initial query run.
-Concept annotations associated with these documents are then used to construct the conceptual representation of the relevance model (the query).
-While OntoSearch~\cite{DBLP:conf/aaai/JiangT06} does not explicitly target the approximation of a relevance model, it follows a similar idea.
+%Recently, a technique based on the idea of relevance model has been proposed to recognize the concepts underlying the query, referred to as conceptual query modeling~\cite{DBLP:journals/ipm/MeijTRK10}.
+Instead of using a thesaurus, top pseudo-relevance feedback documents have been retrieved through an initial query run~\cite{DBLP:journals/ipm/MeijTRK10}.
+Then, concept annotations associated with these documents (or inferred through spreading activation~\cite{DBLP:conf/aaai/JiangT06} using these concepts as seeds) are used to construct the conceptual representation of the query.
+%While OntoSearch~\cite{DBLP:conf/aaai/JiangT06} does not explicitly target the approximation of a relevance model, it follows a similar idea.
 Concepts captured by ontologies (seen as a semantic network of concepts) are used here.
@@
 concept, relation and entity names are mapped to query predicates and constants).
-While the common language used to query semantic data in RDF is SPARQL\footnote{\url{http://www.w3.org/TR/rdf-sparql-query/}} (basically, a language for expressing graph patterns), other (logic-based) formalisms have been used, i.e.
+While the common language used to query semantic data in RDF is SPARQL~\footnote{\url{http://www.w3.org/TR/rdf-sparql-query/}} (a language for expressing graph patterns), other (logic-based) formalisms have been used, i.e.
 recognized entities, classes and relations can be mapped to SPARQL queries~\cite{DBLP:conf/esws/DamljanovicAC10},
 conceptual graphs~\cite{DBLP:conf/aswc/CaoCT08}, logical formulas~\cite{DBLP:journals/dke/CimianoHHMS08} or XML Fragments~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
-An overview of this task is illustrated in Fig.~\ref{fig:inter_keywords}
+An overview of this task is shown in Fig.~\ref{fig:inter_keywords}.
 
@@
 interpretations) but directly output answers.
-As the user types, TASTIER completes the query with answers that possibly match the intended information need.
+%As the user types, TASTIER completes the query with answers that possibly match the intended information need.
 
@@
  \label{fig:translation}
+ \vspace{-0.5cm}
 \end{figure*}
@@
 One the one hand, it can be tackled in a way similar to the translation of keyword queries.
-This solution (depicted in the bottom left portion of Fig.~\ref{fig:inter_NL}) involves the detection of concepts, entities, and relations~\cite{DBLP:conf/aswc/CaoCT08}, and their mapping to elements of structured queries.
+This solution (depicted in the bottom right portion of Fig.~\ref{fig:inter_NL}) involves the detection of concepts, entities, and relations~\cite{DBLP:conf/aswc/CaoCT08}, and their mapping to elements of structured queries.
 The problem of ambiguity is solved here by using robust techniques for the matching of words in the NL query against elements in the semantic data and semantic models, and for the ranking and disambiguation of resulting matches.
 In fact, this kind of approaches is particularly popular among domain-independent NL query translation systems.
-AquaLog~\cite{DBLP:journals/ws/LopezUMP07}) for instance, maps words in NL queries to elements in the semantic data, and disambiguates results using domain-independent lexical resources (e.g.
+AquaLog~\cite{DBLP:journals/ws/LopezUMP07} for instance, maps words in NL queries to elements in the semantic data, and disambiguates results using domain-independent lexical resources (e.g.
 WordNet).
 
-As depicted in Fig.~\ref{fig:inter_NL}, the other category of approaches involves the use of lexicons, often in combination with a syntactic analysis tools. 
+%As depicted in Fig.~\ref{fig:inter_NL}, 
+The other category of approaches involves the use of lexicons, often in combination with a syntactic analysis tools. 
 %Because NL questions also provide syntactic features, 
-In fact, the same text analysis tools used for content interpretation can be applied here.
+In fact, the same text analysis tools used for document interpretation can be applied here.
 For instance, the Stanford Parser~\footnote{\url{http://nlp.stanford.edu/software/lex-parser.shtml}} and GATE~\footnote{\url{http://gate.ac.uk/}} are used by FREyA~\cite{DBLP:conf/esws/DamljanovicAC10} to identify concepts in NL questions and to derive the syntactic parse tree, respectively.
-The use of domain-specific lexicons provide is a common way to deal with ambiguities, especially for traditional NL translation systems that are focused on a particular domain.
-Basically, a lexicon captures the mappings from syntactic elements to semantic elements.
+Lexicons are used for dealing with ambiguities, especially for traditional NL translation systems that are focused on a particular domain.
+A lexicon here captures the mappings from syntactic elements to semantic elements.
 For instance, ORAKEL uses a lexicon, which specifies the mappings between nouns (verbs) with their arguments identified through the syntactic analysis and concepts (relations) in the semantic models~\cite{DBLP:journals/dke/CimianoHHMS08}.
@@
 This is also the objective of other related approaches that fall into the general category of query construction.
-For instance, faceted search~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/esws/HeimEZ10,DBLP:conf/semweb/FerreH11} as well as the other kind of iterative query interfaces based on visual manipulation (drag and drop)~\cite{DBLP:journals/ws/Harth10} as presented before, also belong to this general category.
+For instance, faceted search~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/esws/HeimEZ10} as well as the other kind of iterative query interfaces based on visual manipulation (drag and drop)~\cite{DBLP:journals/ws/Harth10} as presented before, also belong to this general category.
 In these systems, user operations are directly mapped to changes in the query.
 For instance, adding and removing facets result in the addition (query expansion) and removal (query refinement) of query predicates, respectively.
-Clearly, the difference to work on keyword and NL query interpretation is the lack of ambiguity, i.e.
-the semantics of every user input is clear.
+Clearly, the difference to work on keyword and NL query interpretation is the lack of ambiguity.
+Since only elements known to the system are presented to the user, the semantics of every user input is well-defined.
 
@@
   \caption{Overview of matching approaches.}
-    \begin{tabular}{|c|c|c|}
+    \begin{tabular}{|p{2.2cm}|p{2.7cm}|p{2.5cm}|}
     \hline
@@
     \hline
-    Syntactic-based & Join  & Forward chaining \bigstrut\\
+    Syntactic similarity & Graph pattern matching  & Logic-based inferencing \bigstrut\\
     \hline
-    Lexicon-based & Graph traversal & Backward chaining \bigstrut\\
+    Semantic similarity & Graph traversal, spreading activation & Mathematical/statistical models\bigstrut\\
     \hline
     \end{tabular}%
-  \label{tab:addlabel}%
+  \label{tab:matching}%
+  \vspace{-0.5cm}
 \end{table}%
 
-\dtr{some systems may do interpretation, some not....}
-The differences between term matching, structure matching and graph traversal are illustrated in Fig.~\ref{fig:matching}.
+The kind of applicable matching techniques depends on the given query input. The input to this could be either the query directly provided the user, or preprocessed via query interpretation. 
+The differences in inputs between term matching, structure matching and graph traversal are illustrated in Fig.~\ref{fig:matching} and discussed further below.
+We can see that term matching and graph traversal are particularly needed when the query is keyword-based.
+Whereas document retrieval or entity retrieval in general can be solved through term matching, relational search requires graph traversal for finding connections between keywords.
+Likewise, graph traversal is also useful for finding connection between elements, which have been recognized in the keywords through the preprocessing step of keyword interpretation.
+Structure matching is only possible when the input has been fully translated to a structured query.
+An overview of matching techniques is presented in Table~\ref{tab:matching}.
 
@@
 %\subsubsection{Term- / Content-based Matching}
-This matching is needed when the representation of query and data is based on terms (i.e.
+This matching is needed when the representation of query or data is based on terms (i.e.
 is a bag of words).
-This is the case with all the existing concept-based document retrieval solutions~\cite{DBLP:conf/sigir/Giger88,DBLP:conf/sigir/ZhongH06,DBLP:conf/trec/JelierSEWMSMK03,DBLP:conf/sigir/QiuF93,DBLP:conf/sigir/QiuF93,DBLP:conf/sigir/Voorhees93,DBLP:conf/sigir/Voorhees94,DBLP:journals/ipm/MeijTRK10}, which identify the concepts behind the query and content but however, only use them for query or document expansion (i.e.
-expand the term-based query / content representation with additional terms corresponding to the identified concepts).
-Likewise, there are approaches, which interpret the query as entities and relations and to use this understanding to expand the queries with corresponding terms~\cite{DBLP:series/sci/NgoC10}.
-Many semantic data retrieval systems such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} also employ bag-of-words representations -- both of the query and the semantic data.
-In these cases, the structure and semantics are not taken into account during the matching (but possibly, might have been used in other steps such as query interpretation).
-The matching boils down to the standard IR retrieval problem.
-Namely, given a set of keywords, documents matching individual keywords are retrieved.
-Typically, they are then joined to obtain those, which match all query keywords (AND-semantics).
+This is the case with all the existing concept-based document retrieval solutions~\cite{DBLP:conf/sigir/Giger88,DBLP:conf/sigir/ZhongH06,DBLP:conf/sigir/QiuF93,DBLP:conf/sigir/Voorhees93,DBLP:conf/sigir/Voorhees94,DBLP:journals/ipm/MeijTRK10}, which identify the concepts behind the query and document but however, only use them for query or document expansion (i.e.
+expand the term-based query / document representation with additional terms corresponding to the identified concepts).
+Likewise, there are approaches, which interpret the query as entities and relations and use this understanding to expand the query with corresponding terms~\cite{DBLP:series/sci/NgoC10}.
+That is, instead of concept-based, entity- and relation-based query expansion are applied.
+In all these cases, the resulting query is still a bag of words.
+
+Many semantic data retrieval systems such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} also employ bag-of-words representations -- at the query and sometime, also at the level of semantic data.
+For instance, Sindice~\footnote{\url{http://sindice.com/}}, the inverted index implementation behind Sig.ma, supports keyword queries on RDF entity descriptions that are indexed as bag-of-words just like unstructured documents.
+In this case, the semantics available in the RDF data are not taken into account during the matching (but may have been used in other steps such as query interpretation, e.g.
+for concept-based query expansion as discussed).
+
+Matching here boils down to the standard IR retrieval problem.
+Namely, given a set of keywords, bag-of-words models of the data matching individual keywords are retrieved.
+Besides document retrieval style ranking of results, most IR engines employed by semantic search systems for this task (e.g.
+Falcons and SemSearchPro use Apache Lucene~\footnote{\url{http://lucene.apache.org/core/}}) support fuzzy term matching such that syntactically similar terms can also be recognized as matches.
+Besides, systems such as SemSearchPro uses a lexical model such as WordNet to deal with semantic similarity, i.e.
+to find syntactic variants that are similar in meaning.
+This technique is similar to the use of lexical resources for concept detection during document and query interpretation.
+
+After matches are identified for every query term, they are joined (or combined via union) to obtain those that match all or some query keywords (AND vs. OR-semantics, respectively).
+
 %This matching goes beyond the term-level to consider the content, which may contain several mentions of the query terms, as well as mentions of terms that do not appear in the query.
@@
 \subsection{Matching Complete Structure Patterns (Structure Matching)} 
-	This matching is possible when the query and content are interpreted or are directly available as a structured query and semantic data, respectively.
-That is, the semantics of both the query and data is represented in terms of some entities and their relations.
+	 We can apply this matching when the query and document are interpreted or are directly available as a structured query and semantic data, respectively.
+That is, the semantics of both the query and data are represented in terms of some entities and their relations.
 Most frequent is the combination SPARQL queries and RDF data.
-In particular, the three common types of information needs discussed previously can be captured through the basic graph pattern (BGP) feature of SPARQL.
-Just like semantic data, a BGP forms a graph where nodes and edges are either constants or variables.
-They form complete patterns in the sense that through explicitly captured join variables, the query engines know how to combine intermediate results obtained for subparts of the queries (for triple patterns in the BGP) to compute end results.
-Matching BGPs against semantic data boils down to the task of \emph{graph pattern matching} where constants in the BGP representing entities, relations, attributes and attribute values are matched against the RDF data graph to find matching subgraphs that contain bindings to variables in the BGP.
-Processing these BGPs involves standard \emph{database query evaluation} techniques, i.e.
-precompile the query to capture an optimal evaluation plan, then \emph{retrieve} data (from optimized indexes) for each triple pattern and \emph{join} intermediate results according to the plan.
-This matching is supported by off-the-shelf triple stores.
-For instance, it is used by SemSearchPro~\cite{DBLP:journals/ws/TranHL11} for computing results for SPARQL queries, after they have been derived from keywords through query interpretation.
+In particular, the three common types of information needs discussed previously can be captured through the \emph{basic graph pattern} (BGP) feature of SPARQL.
 
-	\subsection{Matching Incomplete Structure Patterns (Graph Traversal)}  While join-based evaluation is possible for structured pattern that are complete, traversing the data graph is needed when query patterns entail missing connections.
-That is, the query engines cannot directly combine partial results based on join variables but needs to explore for different paths between them.
-One combination that involves this type of matching is the evaluation of keyword queries over semantic data.
-As discussed before, the structure and semantics in the data can be used to interpret the keyword query and to convert it to a structured query.
-Instead of query interpretation, there are also systems~\cite{DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}, which use the same \emph{graph traversal} mechanism to directly evaluate the keyword query.
-They skip the computation of queries and directly explore for results in the data (subgraphs) that match the keywords.
-As opposed to standard IR-style keyword search on documents, the results here are semantic data graphs.
-That is, the keywords in the query do not refer to single documents but possibly, several entities that are connected through paths in the semantic data graph.
+	Just like semantic data, a BGP forms a graph where nodes and edges are either constants or variables (e.g.
+the structured query shown in Fig.~\ref{fig:matching}).
+Edges are connected when they share one common node (if that node represents a variable, it is called the \emph{join variable} node).
+However, edges in the BGP are not required to be connected such that a BGP can be seen as a set of connected components.
+Results obtained for every connected component are combined via union.
+Through join variables, the query engine knows how to combine intermediate results obtained for edges in every connected component, i.e.
+for combining results obtained for the triple patterns connected in the BGP.
+
+	In fact, matching BGPs against semantic data boils down to the task of \emph{graph pattern matching} where constants in the BGP are matched against elements in the RDF data graph to find matching subgraphs that contain bindings to variables in the BGP.
+For processing these BGPs, the underlying engine leverages standard database query evaluation techniques, i.e.
+it precompiles the query to capture an optimal evaluation plan, then retrieves data (from optimized, compressed indexes) for every triple pattern and joins intermediate results according to the plan.
+This processing is supported by off-the-shelf triple stores such as Virtuoso~\footnote{\url{http://virtuoso.openlinksw.com/}} and Sesame~\footnote{\url{http://www.openrdf.org/}}.
+For instance, a customized triple store is used by SemSearchPro~\cite{DBLP:journals/ws/TranHL11} for computing results for SPARQL queries, after they have been derived from keywords through query interpretation.
+
+\subsection{Matching Incomplete Structure Patterns (Graph Traversal)} 
+The graph pattern matching technique discussed previously assumes that the structured query pattern is complete.
+It performs a join or simply combine results via union when there are no join variables connecting triple patterns.
+As opposed to that, the lack of join variables or connections between query elements in general, may simply indicate incompleteness in the query, i.e.
+some connections between query elements are not explicitly given, or unknown.
+%This is the case with relational search, when some relations are unknown. Also, 
+Keyword queries are mostly incomplete in that sense. Even when the users know the connecting elements, they may fail to capture them as keywords or simply omit them in the query.
+
+	Instead of applying the union when there are no join variables, graph traversal aims to combine partial results by exploring for different paths between them that form \emph{connecting subgraphs}.
+It uses the structure and semantics captured in the data to find connections.
+This kind of matching has been used in different scenarios.
+As discussed, it has been applied to explore paths between keywords to translate a given keyword query to a structured query.
+Instead of query interpretation, there are also systems~\cite{DBLP:conf/cikm/LadwigT11}, which use the same graph traversal mechanism to directly evaluate the keyword query.
+They skip the computation of structured queries and directly explore for results in the data (subgraphs) that match the keywords.
+As opposed to standard IR-style keyword search on documents (i.e.
+document/entity search), the results here are semantic data graphs (i.e.
+relational search results).
+The keywords in the query do not refer to single documents but possibly, several entities that are connected through paths in the semantic data graph.
 Hence, simply joining results (documents), which match the query keywords is not sufficient.
-Entities matching keyword(s) in the query have to be retrieved, and subgraphs containing paths, which connect these keyword matching entities have to be explored in the data through traversing graph nodes and edges.
+Entities matching keywords in the query have to be retrieved, and subgraphs containing paths, which connect these keyword matching entities have to be explored in the data through traversing graph nodes and edges.
 
-	A different semantics has been used~\cite{DBLP:conf/www/RochaSA04}, where results do not have to cover those nodes matching the query keywords.
-Those parts of the data, which are interesting and thus, shall be explored and returned as results, are controlled through manually defined traversal constraints that are realized via spreading activation.
-
-Interestingly, graph traversal is also employed for the relational search scenario, where the relations (paths) between entities are unknown.
-For instance, the mechanism used by for graph exploration by Hermes~\cite{DBLP:journals/ws/TranWH09,DBLP:conf/icde/TranWRC09}, a keyword search system, is similar to the one proposed for answering P-Queries~\cite{DBLP:conf/www/AnyanwuS03}, a special type of queries that ask for unknown semantic associations between entities.
-
-Another application of graph traversal has been proposed for the combined scenario of document and data retrieval.
-The goal is to find entities in the knowledge base, which are related to the documents to be retrieved, or vice versa, to retrieve documents related to some given entities.
+	The common semantics employed by graph traversal approaches for interpreting or directly evaluating keyword queries mentioned above, is based on \emph{minimality}.
+They search for minimal subgraphs that for each keyword, contains at least one matching node.
+A different semantics has been used for a hybrid search approach that operates on documents and semantic data~\cite{DBLP:conf/www/RochaSA04}.
+%	results do not have to cover those nodes matching the query keywords. 
+Instead of minimality, those parts of the data, which are interesting and thus, shall be explored and returned as results, are controlled through manually defined traversal constraints that are realized via \emph{spreading activation}, a kind of graph traversal that is performed according to activation levels of nodes.
+In a similar hybrid search setting,
+%Another application of graph traversal has been proposed for the combined scenario of document and data retrieval. The goal is 
+spreading activation has been used to find entities in semantic data, which are related to the documents to be retrieved, or vice versa, to retrieve documents related to some given entities.
 The starting points here are thus documents or entities, and traversal from these points are controlled through spreading activation~\cite{DBLP:conf/esws/SchumacherSS08}.
 
-	\subsection{Reasoning} The formal well-defined semantics of some semantics models such as ontologies represented in OWL, have also be exploited for matching.
-More precisely, they are used for \emph{reasoning} to consider not only the available data but also new facts that can be automatically inferred from the formal semantics.
-For instance, the semantic models used in Serene~\cite{DBLP:journals/ws/FazzingaGGL11} is an ontology TBox represented as DL formulas, and semantic data are captured as ABox assertions of the same ontology.
-Serene uses an inference engine to derive new knowledge during an offline ontology compilation step.
-This computation is performed offline to improve the efficiency of online matching.
-Clearly, new knowledge relevant for the query can also be derived online.
+%We note that graph traversal has also been applied in the structured query setting to deal with cases where relations (paths) shall be retrieved.
+For instance, the graph traversal algorithm used by SemSearchPro~\cite{DBLP:journals/ws/TranHL11,DBLP:conf/icde/TranWRC09}, a keyword search system, is similar to the one proposed for answering P-Queries~\cite{DBLP:conf/www/AnyanwuS03}, a special type of structured queries that ask for semantic associations between entities.
+%
+
+	\subsection{Inferencing} Strictly speaking, this is not a matching task but a processing step performed either subsequent to or during the process of matching.
+Common to semantic search systems are the use of \emph{logic-based reasoning} and mathematical/statistical models of \emph{computation}.
+
+	Simple computation such as sorting and averaging are commonly applied to search results.
+Complex models for advanced analytics however, are only available in expert systems and data warehouses.
+With WolframAlpha, the use of computational models based on statistical and mathematical formulas to derive further insights from the results has crossed the boundaries of specific domains to reach the mass of Web users.
+In fact, simple analytical processing has been available in popular Web search engines such as Google for a while.
+For instance, users can pose queries to convert money from one currency to another.
+
+	The other type of inferencing based on the formal semantics of logic-based models such as OWL, has been more popular in semantic search research. 
+%	The formal well-defined semantics of some semantics models such as ontologies represented in OWL, have also be exploited for matching. More precisely, 
+It is used 
+%for \emph{reasoning} 
+to consider not only the available data but also facts that can be automatically inferred from the formal semantics.
+For instance, the semantic models used in Serene~\cite{DBLP:journals/ws/FazzingaGGL11} is an ontology Tbox represented as DL formulas, and semantic data are captured as Abox assertions of the same ontology.
+Exploiting this Tbox and Abox, Serene uses an inference engine to derive new knowledge during an offline ontology compilation step.
+This computation is performed offline to improve the efficiency of online processing.
+%, but in principle, could also be done online during the matching. 
+New knowledge relevant for the query can also be derived online. 
 In ORAKEL for instance, the inference of new facts is performed as part of the computation of query matches.
-Notably, the first system created in the early years of Semantic Web research, which makes use of logical reasoning for computing semantic matches is SHOE~\cite{DBLP:conf/dagstuhl/HeflinHL03}.
+Notably, the first system created in the early years of Semantic Web research, which makes use of logical reasoning for computing semantic matches, is SHOE~\cite{DBLP:conf/dagstuhl/HeflinHL03}.
 
-\subsection{Matching: Combination of Techniques}
+%\subsection{Matching: Combination of Techniques}
 
@@
 Ranking approaches leverage different factors, which in general, can be \emph{query-independent} or \emph{query-dependent}.
-The latter considers the \emph{relevance} of the result with respect to the query.
-The former includes different aspects, such as \emph{rarity} (measured in terms of occurrence~\cite{DBLP:journals/internet/Aleman-MezaHARS05}), \emph{popularity} (based on occurrences~\cite{DBLP:conf/icde/TranWRC09}, or centrality~\cite{DBLP:journals/internet/Aleman-MezaHARS05}), \emph{predictability} (based on information content~\cite{DBLP:conf/www/AnyanwuMS05}), \emph{trust} (e.g.
-trust assigned to sources~\cite{DBLP:journals/internet/Aleman-MezaHARS05}) or \emph{confidence} (e.g.
-confidence scores of data extraction outputs~\cite{DBLP:conf/www/NieZWM05,DBLP:conf/vldb/ChengYC07}).
+The latter type considers the \emph{relevance} of the result with respect to the query.
+The former type includes different aspects, such as \emph{rarity} (measured in terms of occurrence~\cite{DBLP:journals/internet/Aleman-MezaHARS05}), \emph{popularity} (based on occurrences~\cite{DBLP:conf/icde/TranWRC09}, or centrality~\cite{DBLP:journals/internet/Aleman-MezaHARS05}), \emph{predictability} (based on information content~\cite{DBLP:conf/www/AnyanwuMS05}), \emph{trust} (e.g.
+trust values manually assigned to sources~\cite{DBLP:journals/internet/Aleman-MezaHARS05}) or \emph{confidence} (e.g.
+confidence scores of IE outputs~\cite{DBLP:conf/www/NieZWM05,DBLP:conf/vldb/ChengYC07}).
 They could be seen as heuristics, which can complement the ranking based on query-relevance.
-Among those heuristics, there are two prominent ones that are widely used in existing approaches, namely \emph{centrality-} and \emph{proximity-based ranking}.
+There are two prominent heuristics that are extensively studied and widely used in existing approaches, namely for \emph{centrality}- and \emph{proximity}-based ranking.
 
@@
   \caption{Overview of centrality-based ranking.}
-    \begin{tabular}{|p{3.5cm}|p{3.5cm}|}
+    \begin{tabular}{|p{3.7cm}|p{3.4cm}|}
     \hline
-    Hyperlinks & Relations  \bigstrut\\
+    \textbf{Hyperlinks} & \textbf{Relations}  \bigstrut\\
     \hline
     \hline
-    Adoption of PageRank to (1) ontologies as documents, (2) two-layered graph with sources (documents) representing one layer & Authority transfer weights (1) specified by experts, (2) learned through simulated annealing or PARAFAC decomposition \bigstrut\\
+    Adoption of PageRank to (1) ontologies as Web pages, (2) two-layered graph with data sources (Web pages) representing one layer and source data the other & Authority transfer weights (1) specified by experts, (2) learned through simulated annealing or PARAFAC decomposition \bigstrut\\
     \hline
     \end{tabular}%
-  \label{tab:addlabel}%
+  \label{tab:centrality}%
+  \vspace{-0.5cm}
 \end{table}%
 
-\subsection{Centrality-based Ranking} The algorithms commonly used for computing centrality in the context of ranking is PageRank and HITS.
-Basically, the idea behind it is to perform link analysis on the graph formed by the hyperlink structure of documents to identify nodes that are important (or popular or authoritative).
-In the semantic search context, much effort has been invested in extending the original PageRank and HITS proposals towards dealing with semantic data graphs, where instead of documents and hyperlinks, there are entities that are connected through different types of semantic links.
+\subsection{Centrality-based Ranking} An overview of centrality-based techniques is presented in Table~\ref{tab:centrality}.
+The algorithms commonly used for computing centrality in the context of ranking is PageRank and HITS.
+The underlying idea is to perform link analysis on the graph formed by the hyperlink structure of documents to identify nodes that are important (or popular or authoritative).
+
+In the semantic search context, much effort has been invested in extending the original PageRank and HITS proposals towards dealing with semantic data graphs, where instead of documents and hyperlinks, there are entities that are connected through different types of semantic links (i.e.
+relations).
 One of the first proposal for using PageRank for dealing with semantic data is OntoRank~\cite{DBLP:conf/semweb/DingPFJPK05}.
-However, ranking here is only dealt with at the level of sources, namely ontolgies (instead of the entities contained in them).
-PageRank could be directly applied because ontologies are treated as Web pages, and there are no different types of links.
-ObjectRank~\cite{DBLP:conf/vldb/BalminHP04} build upon PageRank, but recognizes the variety of semantic links.
-Instead of using the same authority flow for all edges, it employs an authority transfer schema graph, which captures the strengths of authority for different types of edges.
-While all these weights has to be manually specified by domain experts in ObjectRank, PopRank~\cite{DBLP:conf/www/NieZWM05} incorporates a simulated annealing algorithm to learn these weights, based on a partial weighting provided by experts.
-A different direction for obtaining the weights of semantic relations is taken by TripleRank, which models data by means of a 3-dimensional tensor.
-Applying the PARAFAC decomposition (a multi-modal counterpart to HITS) then results in authority and hub scores for both the entities and links.
+However, ranking here is only dealt with at the level of sources, namely to rank ontologies instead of the entities contained in them.
+PageRank could be directly applied because ontologies are treated as Web pages, and there are no different types of links but only \verb+import+~\footnote{An ontology imports another one to make uses of its content.} relations.
+Similar to this idea, semantic data sources have been considered as Web pages~\cite{DBLP:conf/esws/DelbruTCTD10,DBLP:conf/semweb/HarthKD09}.
+Authors of the latter pursue a two-layer approach where the PageRank scores computed for the datasets propagate to the entities contained in them~\cite{DBLP:conf/semweb/HarthKD09}.
+
+ObjectRank~\cite{DBLP:conf/vldb/BalminHP04} also builds upon PageRank, but recognizes the variety of semantic links.
+Instead of using the same authority flow for all edges, it employs an authority transfer schema graph, which captures the strengths of authority for different types of links.
+While all these weights have to be manually specified by domain experts in ObjectRank, PopRank~\cite{DBLP:conf/www/NieZWM05} incorporates a simulated annealing algorithm to learn the weights, based on a partial weighting provided by experts.
+A different direction for obtaining the weights of different types of links is taken by TripleRank, which models semantic data by means of a 3-dimensional tensor.
+Applying the PARAFAC decomposition (a multi-modal counterpart to HITS) to the tensor results in authority and hub scores for both the entities and links.
+
 EntityAuthority~\cite{DBLP:conf/webdb/StoyanovichBBW07} operates not only on the semantic data graph but on a combined graph that contains both entities and documents as nodes.
-Also, a two-layer approach has been pursuit, where PageRank is computed both for the sources and the entities contained in them~\cite{DBLP:conf/esws/DelbruTCTD10,DBLP:conf/semweb/HarthKD09}.
 
-\subsection{Proximity-based Ranking} Another popular heuristic that has been successfully used in IR is the proximity between terms~\cite{DBLP:conf/sigir/ButtcherCL06a,DBLP:conf/sigir/TaoZ07}.
+\subsection{Proximity-based Ranking} Another popular heuristic that has been successfully used in IR is the proximity between terms~\cite{DBLP:conf/sigir/TaoZ07}.
 According to this, a result is ranked high when it contains query terms that appear closer to each other in its textual content.
-Note that while it is not independent of the query, this heuristic does not directly capture the query-relevance.
 This notion of proximity has also been used for XML data retrieval: XRank proposes to rank results based on the smallest text window, which contains all matches to query keywords~\cite{DBLP:conf/sigmod/GuoSBS03}.
@@
 Similar to text proximity, the intuition here is that more compact results more likely correspond to the intended need.
+Note that while it is not independent of the query, this heuristic does not directly capture the query-relevance.
 
@@
     \hline
-    Content & Structure  \bigstrut\\
+    \textbf{Content} & \textbf{Structure} / \textbf{Semantics}  \bigstrut\\
     \hline
     \hline
-    Treat entities as documents and adopt (1) Vector Space Model (2) unstructured LM & (1) BM25F, (2) structured LM, (3) edge-specific relevance model, (4) triple-based LM \bigstrut\\
+    Treat entities as documents and adopt (1) vector space model (2) unstructured LM & (1) BM25F, (2) structured LM for results, (3) for both query and results, (4) triple-based LM \bigstrut\\
     \hline
     \end{tabular}%
-  \label{tab:addlabel}%
+  \label{tab:queryrelevance}%
+  \vspace{-0.5cm}
 \end{table}%
 
-\subsection{Query-Relevance Based Ranking} Given the ambiguous query, different results can be found that vary in the degree relevance.
-This classic problem is extensively studied in IR.
+\subsection{Query-Relevance Based Ranking} An overview of these techniques is presented in Table~\ref{tab:queryrelevance}.
+Given the ambiguous query, and given we know the query intent, results can be distinguished in the degree of relevance w.r.t.~intent.
+Finding the query intent (i.e.
+the query-relevance) and ranking results based on relevance represent a classic problem in IR.
 In the semantic search setting, existing IR concepts have been used and extended to deal with semantic data and to leverage the availability of semantics.
 
-Many semantic search systems, which provide keyword search over semantic data, apply standard IR ranking.
-For instance, Falcons~\cite{DBLP:journals/ijswis/ChengQ09} uses a standard IR tool (Lucene~\footnote{\url{http://lucene.apache.org/java/docs/index.html}}) to index entities as documents, and uses the built-in ranking mechanism for entity ranking.
-
-For ranking more complex (relational search) results, there are keyword search systems, which use the Vector Space Model and adopted the \emph{TFIDF-based} term weighting.
-The result in this setting is a graph, which contain a set of keyword matching nodes.
-A popular ranking is based on sum of the individual TF-IDF score computed for every keyword match via pivoted normalization weighting.
-Specific normalization methods have proposed to recognize that the textual length of the matching elements is often very short (document length normalization), different attributes can be associated with different vocabularies (IDF normalization) and a result is actually an “aggregation of documents” and thus requires additional normalization beyond the document level.
-Also TF-IDF has been adopted for the case of document retrieval using semantic data.
-Here the TF-IDF weighting has to be modified to consider not only the frequency of terms but also the frequency of named entities~\cite{DBLP:series/sci/NgoC10} and annotations~\cite{DBLP:journals/tkde/CastellsFV07}.
+\textbf{TFIDF:} Many semantic search systems, which provide keyword search over semantic data, apply standard IR ranking.
+For instance, Falcons~\cite{DBLP:journals/ijswis/ChengQ09} uses a standard IR tool (Lucene) to index entities as documents, and uses the built-in ranking mechanism (TFIDF-based) for entity ranking.
+For ranking more complex relational search results, there are keyword search systems, which adopt the vector space model and TFIDF-based term weighting.
+The result in this setting is a graph, which is simply conceived as a set of keyword matching nodes.
+A popular ranking scheme is based on the sum of the individual TFIDF score computed via pivoted normalization weighting for every keyword matching node~\cite{DBLP:conf/icde/TranWRC09}.
+Specific \emph{normalization methods} have been proposed to recognize that the textual length of the matching nodes (i.e.
+entity descriptions instead of textual documents) is often very short (thus, document length normalization), different attributes actually represent different vocabularies (thus, IDF normalization) and a result is actually an ``aggregation of documents'' and thus, requires additional normalization beyond the document level~\cite{DBLP:conf/sigmod/LiuYMC06}.
+Also, TFIDF has been adopted for the case of document retrieval using semantic data.
+Here, the TFIDF weighting has to be modified to consider not only the frequency of terms but also the frequency of named entities~\cite{DBLP:series/sci/NgoC10} and annotations~\cite{DBLP:journals/tkde/CastellsFV07}.
 
 Taking the specific semantics of entity results into account, an extension of the \emph{BM25F} has been proposed~\cite{DBLP:conf/semweb/BlancoMV11}.
-The idea is to use different fields for indexing different properties of RDF entities.
-Different weights are assigned to these fields to recognize that some properties are more important than others in ranking entities.
+The idea here is to use different fields for indexing different attributes of entities, instead of considering entities as unstructured documents.
+Different weights are assigned to these fields to recognize that some attributes are more important than others in ranking entities.
 
-Also, the more recent \emph{language modeling} (LM) paradigm has been adapted to this case of complex results.
-Language models for documents and queries are employed to represent them as multinomial distributions over words of the vocabulary.
-The KL-divergence, basically measuring the distance between the query and document distribution, can then be used for ranking.
-For ranking structured objects, three different models were studies~\cite{DBLP:conf/www/NieMSWM07}: The simple unstructured model treats all object attributes and values as vocabulary terms.
+\textbf{Language Models:} Also, the language modeling (LM) approach has been adapted to the case of ranking complex results.
+Language models for documents and queries are employed to represent them as multinomial distributions over words of a vocabulary.
+The KL-divergence, basically measuring the distance between the query and document distributions, can then be used for ranking.
+For ranking structured objects, three different models were studies~\cite{DBLP:conf/www/NieMSWM07}: the simple unstructured model treats all object attributes and values as vocabulary terms.
 The structured variant employs language models for specific components of the structured results.
-The record-level representation models an object through several language models, each capturing a record of that object.
+The record-level representation models an object through several language models, each capturing a record of that object (an object here is the output of merging several records).
 The attribute-level representation further segments a record into multiple fields and assigns different weights to individual fields (similar to the idea behind BM25F).
-Moreover, specific term distributions for fields have been proposed.
-Using edge-specific relevance models~\cite{DBLP:conf/cikm/BicerTN11}, the probability of observing a word in a structured result may vary, depending on the attribute (the edge) to be considered.
-This edge-specific model is employed not only to exploit the structure and semantics in the data but also to capture the semantics behind the keyword query.
+%Similarly, a hierarchical view has been taken for the language modeling and ranking of entity search results: An entity can be decomposed into property groups consisting of individual properties.
+Each property is a distribution over terms.
+Moreover, specific term distributions for fields have been used for modeling results as well as queries.
+The query is modeled based on pseudo-relevance feedback results obtained from an initial query run, called the edge-specific relevance model~\cite{DBLP:conf/cikm/BicerTN11}.
+Similarly, the probability of observing a word in a structured result may vary, depending on the attribute (the edge) to be considered.
+This is captured by the edge-specific result model.
+%
+%s are employed not only to exploit the structure and semantics in the data but also to capture the semantics behind the keyword query.
 For this, an initial run over the semantic data is performed to obtain pseudo-relevance feedback (PRF) results for the keyword query.
-Instead of using the short and ambiguous keyword query, an edge-specific model constructed from these PRF results is used to capture the information need (the relevance).
+%This approach is proposed to deal short and ambiguous keyword query, an edge-specific model constructed from these PRF results is used to capture the information need (the relevance).
 
 As opposed to the approaches mentioned before, which model queries and documents based on words, there are also language models defined as probability distributions over RDF triples~\cite{DBLP:journals/debu/ElbassuoniRSW10}.
-The probability of a given triple should capture its ``informativeness'', which is measured based on witness counts.
-The authors implement this by issuing keyword queries for each triple using Web search engines, and used the reported result sizes as witness count estimates.
+The probability of a given triple should capture its ``informativeness'', which is measured based on a notion called witness counts.
+The authors implement this by issuing keyword queries derived for each triple against Web search engines, and using the reported result sizes as witness count estimates.
 Following the same direction, NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} not only uses informativeness but also a measure of confidence to estimate parameters of the language models.
@@
 \subsection{Ranking: Combination of Factors}
-Clearly, the ranking implemented by a system is often a combination of factors.
-For instance, for searching entities detected from documents, EntityRank~\cite{DBLP:conf/vldb/ChengYC07} rank entities based on the popularity of documents they have been extracted from (computed via PageRank), the confidence of the extraction outputs, contextual constraints as well as the proximity among entities and query words.
-For retrieving more complex objects (comprises multiple records) extracted from web documents, experiments with Libra (a scientific Web search engine) have shown that ranking can be improved when taking extraction confidences both at the record- and attribute-level into account~\cite{DBLP:conf/www/NieMSWM07}.
-Structured results (a subgraph) obtained from keyword search over structured data is mostly ranked based on the PageRank of its constituent nodes, aggregation of query-relevance scores obtained for individual nodes (records) matching query keywords, and the proximity defined through the length of paths between nodes~\cite{DBLP:conf/icde/TranWRC09}.
+The ranking implemented by a system is often a combination of factors.
+For instance, for searching entities detected from documents, EntityRank~\cite{DBLP:conf/vldb/ChengYC07} rank entities based on the popularity of documents they have been extracted from (computed via PageRank), the confidence of the extraction outputs, contextual constraints as well as the proximity among entities and words.
+For retrieving more complex objects (comprising multiple records) extracted from Web documents, experiments with Libra~\footnote{\url{http://libra.msra.cn}} (a search engine for scientific literatures) have shown that ranking can be improved when taking extraction confidences both at the record- and attribute-level into account~\cite{DBLP:conf/www/NieMSWM07}.
+Structured results (subgraphs) obtained from keyword search over semantic data are mostly ranked based on the PageRank of its constituent nodes, an aggregation of query-relevance scores obtained for individual nodes (records, entities) matching query keywords, and the proximity captured through the length of paths between nodes~\cite{DBLP:conf/icde/TranWRC09}.
 
-\dtr{todo:learning to rank  \cite{DBLP:conf/cikm/CoffmanW11}}
+A robust and generic mechanism for combining these factors is \emph{learning to rank}.
+Given labeled examples, i.e.
+relevance judgments capturing which results are relevant, a learning to rank algorithm such as RankSVM can be used to learn the weights that control the influence of individual factors.
+For instance, RankSVM has been used to learn the optimal combination of query-independent factors in the entity search setting~\cite{DBLP:conf/eswc/Tran12}.
+In this study, the goal is to find out the factors, which determine the ranking of entities, given they do not distinguish in terms of query-relevance, i.e.
+they all are relevant.
+Besides centrality-based measures such as PageRank (and other ones derived from connectivity information in the RDF graph), the authors also consider features external to the data such as Google n-gram statistics.
+For relational keyword search over semantic data, TFIDF-based ranking scores obtained for individual nodes in the result graph as well as structure proximity scores derived from the result graph have been studied for learning to rank~\cite{DBLP:conf/cikm/CoffmanW11}.
 
-\section{Main Approaches and Their Performances}\label{sec:approaches}	
-Semantic search has been investigated from different communities in different context.
-In the IR community, semantic search has mainly been viewed from the perspective of \emph{document retrieval}.
-Here, classic \emph{conceptual} approaches based on the use of lexical models can be distinguished from more recent approaches that employ of \emph{annotations in the form of semantic data}.
-Another line of research is \emph{entity search}, which has been studied in the context of entities extracted from Web pages, Wikipedia pages corresponding to entities, and entities captured by databases and Semantic Web datasets.
-Another popular topic is \emph{keyword search over databases and Semantic Web data}, which is mainly about relational information.
-Last but not least, the \emph{processing of NL questions} entail specific challenges and opportunities, which has attracted attention from a specific community of researchers.
-We will now discuss the role of semantics in solving these different search tasks and its impact on performance.
+\section{Common Approaches and Their Performance}\label{sec:approaches}	
+Semantic search has been investigated from different communities in different contexts.
+In the IR community, semantic search has mainly been viewed from the perspective of document retrieval.
+Here, classic \emph{concept}-based approaches based on the use of lexical models can be distinguished from more recent approaches that leverage document \emph{annotations} in the form of semantic data.
+Another line of research is \emph{entity} search, which has been studied in the context of entities extracted from Web pages, Wikipedia pages corresponding to entities, as well as entities captured by databases and semantic data sources.
+Another popular topic is keyword search over databases and semantic data, which is mainly about \emph{relational} information.
+Last but not least, the processing of NL queries over these semantic data entails specific challenges and opportunities, which has attracted interests from a specific community of researchers.
 
-\subsection{Conceptual Document Retrieval} This is the classic type of semantic search systems, which has been studied already in the early years of IR research.
-Researchers have recognized for a richer representation of the information needs and data that goes beyond the bag-of-words model.
+Accordingly, we distinguish five common types of approaches, namely concept-based document retrieval, annotation-based document retrieval, entity search, relational keyword search and relational NL search.
+These types of approaches represent major communities with significant bodies of work, although just as the communities the approaches themselves may overlap in some aspects.
+For instance, an entity search system may use documents and annotations, which would also characterize it as annotation-based search.
+Most relational search systems also support entity search.
+
+We will now discuss these main types of approaches, several example systems, and their reported performances.
+The classification of selected approaches into types is presented in Table~\ref{tab:approaches}.
+Further, Table~\ref{tab:examples} provides an overview of selected systems and their classification along the main aspects of semantic search discussed in this survey.
+
+%Since the technique used within the same system is similar for document and query interpretation, we omit this distinction in Table~\ref{tab:examples}.
+
+% Table generated by Excel2LaTeX from sheet 'Tabelle5'
+\begin{table*}[htbp]
+  \centering
+  \caption{Classification of selected approaches into types.}
+    \begin{tabular}{|p{2cm}|p{1.5cm}|p{2cm}|p{1.5cm}|p{1.5cm}|p{2cm}|p{2cm}|p{1.5cm}|}
+%    \hline
+%    \multicolumn{1}{|c|}{\multirow{2}[4]{*}{Concept-based}} & \multicolumn{2}{c|}{Annotation-based} & \multicolumn{3}{c|}{Entity Search} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel.
+Keyword}} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel.
+NL}} \bigstrut\\
+%    
+%        \begin{tabular}{|c|c|c|c|c|c|r|r|}
+    \hline
+    \multirow{2}[4]{*}{Concept-based} & \multicolumn{2}{c|}{Annotation-based} & \multicolumn{3}{c|}{Entity} & \multicolumn{2}{c|}{Relational}  \bigstrut\\
+\cline{2-8}          & NL    & Keyword  & Document & Wikipedia & Semantic Data & Keyword & NL \bigstrut\\
+
+%\cline{2-6}    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{NL} & \multicolumn{1}{c|}{Keyword } & \multicolumn{1}{c|}{Document} & \multicolumn{1}{c|}{Wikipedia} & \multicolumn{1}{c|}{Semantic Data} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} \bigstrut\\
+    \hline
+    \hline
+    \cite{DBLP:conf/sigir/Giger88, DBLP:conf/esws/GiunchigliaKZ09, DBLP:conf/sigir/QiuF93, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/ZhouYTS06,  DBLP:journals/ws/JonquetLFCNMS11, DBLP:conf/sigir/Voorhees93, DBLP:conf/sigir/Voorhees94, DBLP:journals/ipm/MeijTRK10} & \cite{DBLP:conf/sigir/Chu-CarrollPCFD06, DBLP:journals/tkde/CastellsFV07, DBLP:journals/ws/FernandezCLVCM11, DBLP:conf/cikm/Chu-CarrollP07} &  	  \cite{DBLP:journals/tkde/CastellsFV07, DBLP:conf/sigmod/KandoganKRVZ06, DBLP:conf/aaai/JiangT06, DBLP:series/sci/NgoC10, DBLP:conf/www/RochaSA04, DBLP:conf/esws/SchumacherSS08} & \cite{DBLP:journals/ipm/BalogAR09, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/sigir/Chu-CarrollPCFD06} & \cite{DBLP:journals/tois/BalogBR11, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/cikm/BronBR10, DBLP:conf/ecir/PehcevskiVT08} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/sigir/BastCSW07, DBLP:conf/semweb/BlancoMV11, DBLP:journals/ijswis/ChengQ09, DBLP:journals/ws/TummarelloCCDDD10, DBLP:conf/eswc/Tran12,DBLP:conf/www/NieMSWM07, DBLP:conf/www/NieZWM05} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/cikm/BicerTN11, DBLP:conf/cikm/CoffmanW11, DBLP:journals/debu/ElbassuoniRSW10, DBLP:journals/ws/TranWH09, DBLP:journals/ws/TranHL11, DBLP:conf/icde/KasneciSIRW08, DBLP:conf/sigmod/LiJLF09, DBLP:conf/cikm/LadwigT11} & \cite{DBLP:conf/aswc/CaoCT08, DBLP:journals/dke/CimianoHHMS08, DBLP:conf/esws/WangXZY07, DBLP:conf/esws/DamljanovicAC10, DBLP:journals/ws/LopezUMP07, DBLP:journals/tods/LiYJ07, DBLP:conf/iui/HanNPPL10} \bigstrut\\
+    \hline
+    \end{tabular}%
+  \label{tab:approaches}%
+  \vspace{-0.5cm}
+\end{table*}%
+
+\subsection{Concept-based Document Retrieval} 
+As indicated by example systems shown in Table~\ref{tab:examples}, this type supports keyword search over documents, and based on concepts interpreted from keywords and documents, it may also provide additional querying mechanisms such as as concept-based iterative query construction.
+In fact, this is the classic type of semantic search systems, which has been studied already in the early years of IR research.
+Researchers in this community have recognized the need for a richer representation of the information needs and data that goes beyond the bag-of-words model.
 It became evident that constructing a full-fledge logic-based representation~\cite{DBLP:conf/sigir/Rijsbergen89} for queries and especially for documents is not practical.
-Thus, lightweight \emph{lexical models} have been employed to interpret the semantics of query and documents as concepts, and used within standard bag-of-words IR paradigm (e.g.
+Thus, lightweight \emph{lexical models} have been employed to interpret the semantics of query and documents as concepts, and used within the standard bag-of-words IR paradigm (e.g.
 vector space model and language model).
-Then, retrieval may be done based on concepts alone, or in the form of query and document expansion.
+In fact, retrieval may be done based on concepts alone, i.e.
+using bag-of-concepts, or in the form of query and document expansion.
 In the latter case, bag-of-words model constitutes the basis while the conceptual understanding helps to refine or add more relevant words.
-However, there are \emph{no clear evidences suggesting conceptual IR can outperform standard IR techniques}.
-It has been shown that automatic query expansion in the large diverse TREC collection using WordNet degrades performance.
-Even when selected by hand, it helps only when the query is an incomplete description of the need~\cite{DBLP:conf/sigir/Voorhees94}.
+
+There are \emph{no clear evidences} suggesting conceptual IR can outperform standard IR techniques.
+It has been shown that automatic query expansion in the large and diverse TREC collection using WordNet degrades performance.
+Even when concepts are selected by hand, it helps only when the query is an incomplete description of the need~\cite{DBLP:conf/sigir/Voorhees94}.
 More recently, it has been shown for the medical domain (TREC Genomics) that retrieval based on concepts alone could not outperform the standard baseline based on words~\cite{DBLP:conf/trec/TrieschniggKS06,DBLP:conf/trec/ZhouYTS06}.
-Current work in this direction, which combines concepts and bag-of-words in the form of query expansion, outperforms a state of the art baseline in one collection, and shows similar performances in other collections~\cite{DBLP:journals/ipm/MeijTRK10}.
-However, the experiments have been performed on
+In another experiment, the combination of concepts and bag-of-words
+%in the form of query expansion, 
+outperforms a state-of-the-art baseline in one collection, and shows similar performances in other collections~\cite{DBLP:journals/ipm/MeijTRK10}. However, the experiments have been performed on 
 collections where documents have been manually annotated with concepts (domain-specific CLEF and TREC Genomics collections).
 
-\subsection{Annotation-based Document Retrieval} This encompasses the newer type of approaches, which exploit advancements in data extraction technologies to obtain a richer representation of queries and documents, namely as entities and relations represented as annotations (query and document annotations, respectively).
-To date, there exist only anecdotal evidences for the merits of this type of systems.
-Possibly, the most conclusive result in this direction is based on experiments using the TREC Question Answering track: For a subset of manually chosen questions, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
-The results there can also be interpreted as follows: The employed data extraction programs were optimized for a few specific types of relations and entities (e.g.
+\textbf{Examples:} While concepts may not directly help to improve relevance-based metrics such as precision and recall, there are many systems showing they can provide other benefits, such as for iterative concept-based query refinement or for browsing.
+These features are available with \emph{gopubmed} for instance.
+Targeting the same domain, the \emph{NCBO Resource Index}~\footnote{\url{http://
+bioportal.bioontology.org/resources}}~\cite{DBLP:journals/ws/JonquetLFCNMS11} leverages the large amount of ontologies that exist in the biomedical domain.
+While some (of the 200 ontologies currently used) may capture more advanced semantics, they all are treated as lexical models consisting of connected concepts.
+Besides retrieval, concepts detected in documents are also used for concept-based iterative query construction and navigation, where similar to facets, users can add concepts to refine the queries and to browse documents along concepts, respectively.
+Targeting the Web scenario, \emph{Hakia}~\footnote{\url{http://hakia.com/}} (Hak) uses a cross-domain lexical model called the Commercial Ontology, which hierarchically organizes word senses at three different layers.
+Based on these concepts, Hakia interprets the content as ``knowledge bits'', and for efficiency reason, extracts and indexes all possible queries that can be constructed from them.
+The concepts and ontology are used for retrieval, for handling syntactic variants in keywords and NL queries (morphological variants, synonyms, generalization) in particular.
+
+\subsection{Annotation-based Document Retrieval} These approaches exploit the advancement in IE technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as \emph{annotations} (query and document annotations, respectively).
+As shown in Table~\ref{tab:approaches}, this query interpretation has has been applied both to keywords and NL questions.
+%That is, this category covers both keyword search and NL question answering over documents.
+
+To date, there exist only \emph{anecdotal evidences} for the merits of this type of systems. 
+The most conclusive result in this direction is based on experiments using the TREC Question Answering track: for a subset of queries, it has been shown that higher precision could be obtained~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
+The results there can also be interpreted as follows: the employed IE programs were optimized for a few specific types of relations and entities (e.g.
 \verb+Person+).
-High precision is possible for questions that can be covered by these types of annotations.
-However, high recall is difficult because it requires the data extraction program to recognize arbitrary types of entities and relations.
-While there are promising ideas towards this kind of open data extraction, this problem remains an open challenge.
-Along this line, there is a study showing that the quality of data extractions significantly impacts search performance~\cite{DBLP:conf/cikm/Chu-CarrollP07}.
+High precision is possible for queries that can be covered by these types of annotations, i.e.
+they ask for information that matches these annotations.
+However, high recall is difficult because it requires the IE program to recognize arbitrary types of entities and relations.
+As discussed in the document interpretation part, there are promising ideas towards this kind of open IE.
+However, obtaining high quality results is still a problem that poses many challenges.
+Along this line, there is a study showing that the quality of IEs significantly impacts semantic search performance~\cite{DBLP:conf/cikm/Chu-CarrollP07}.
 
-\subsection{Entity Search} While the two mentioned types focus on documents, this category includes search over (1) documents (for processing factoid and list questions of the TREC QA track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or for expert search questions of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}), over Wikipedia data, which as discussed, can be seen as a kind of semantic data, or (2) documents associated with metadata, (for answering entity related questions of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), or over pure (3) semantic data (for answering entity queries of the SemSearch Entity track~\cite{DBLP:conf/semweb/BlancoMV11}).
-Some type(1) systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}.
-As discussed, it has been shown that precision can be improved when high quality extraction outputs are available~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}.
-The use of semantics in type(2) systems is limited to viewing Wikipedia pages as entities~\cite{DBLP:conf/cikm/KapteinSVK10}, exploiting categories associated with them~\cite{DBLP:journals/tois/BalogBR11} and links between them~\cite{DBLP:conf/ecir/PehcevskiVT08}.
-It has been shown that Wikipedia articles can be effectively used as a pivot for entity search on the Web: it contain entities for a large amount of queries as well as cues (e.g.
-external links) that can be used to effectively find entities' official homepages on the Web~\cite{DBLP:conf/cikm/KapteinSVK10}.
-As a source of semantics, experiments have shown that category information helps to interpret the query and entity documents and to outperform standard text-based retrieval~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:journals/tois/BalogBR11}.
-While many type(3) systems~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/HoganHUKPD11,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09} have been built to search for entities over data crawled from the Semantic Web, solutions for ranking and the evaluation of their results have attracted interest only recently.
-The best performed method~\cite{DBLP:conf/semweb/BlancoMV11} is based on BM25F, which ranks entities as documents that are segmented into different fields corresponding to entity attributes.
+\textbf{Examples:}
+IBM's \emph{AVATAR}~\footnote{now superseeded by SystemT, \url{http://www.almaden.ibm.com/cs/projects/avatar/}} (AVA), is an example of keyword search over documents, which uses UIMA for extracting annotations.
+It interprets keywords as a structure query, which is then processed against a database of annotations.
+As answers, the system does not return documents, but annotations representing information about entities and relations extracted from documents.
+In addition to annotations, other structured datasets (semantic data) can be used for search.
+\emph{Powerset} (PS) performs IE also to return information about entities and relations (to queries represented as keywords as well as NL).
+Its demo constructed for a subset of Wikipedia also returns pages as results.
+More focused towards the processing of complex NL inputs is Watson~\cite{DBLP:journals/aim/FerrucciBCFGKLMNPSW10} (J!).
+It targets the Jeopardy!
+quiz show, where the task is to find factual answers related to entities, given the category and several clues.
+It is a complex system combining different techniques.
+The starting points are previous IBM works, the PIQUANT system for combining evidences~\cite{DBLP:conf/naacl/Chu-CarrollCPI03} and the GuruQA for using annotations~\cite{DBLP:conf/sigir/PragerBCR00,DBLP:conf/sigir/Chu-CarrollPCFD06} in question answering in particular.
+Besides question and content analysis to interpret the meaning in terms of entities and relations, the system also implements techniques not covered by this survey, such as corpus expansion (to identify and acquire sources of content on the Web, both unstructured Web documents as well semantic data such as YAGO) and question decomposition and classification (identify parts and types of questions that need special processing, e.g.
+a math question).
+Computing results requires merging partial evidences as well as their confidence values.
+Similar to learning to rank, a ML method is used for the combination.
+Watson also uses the semantics in some sources to perform reasoning, e.g.
+it exploits subsumption and
+disjointness in type taxonomies and applies geospatial and
+temporal reasoning. While geospatial reasoning is used
+to deal with spatial
+relations such as directionality, borders, and
+containment between geo-entities (e.g. when asked for an Asian city, then spatial containment
+provides evidence that Beijing is suitable, whereas Sydney is not), temporal reasoning helps to deal with 
+inconsistencies between dates in clues and answers.
+
+\subsection{Entity Search} While the two mentioned types retrieve documents, this type of approaches search for \emph{entities} representing real-world objects (anything but documents).
+It includes search over (1) documents (e.g.
+for processing entity-related factoid and list queries of the TREC Question Answering track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or expert search queries of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}),
+%\dtr{todo: A particular type of entity search, expert retrieval has been the focus of a number of evaluations; also belong to the type of entity search that mainly operates on documents; + some other features?.}
+(2) over 
+%documents associated with metadata, (for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), 
+%over (3) 
+Wikipedia data, which as discussed, can be seen as a kind of semantic data (e.g.
+for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), or over pure (3) semantic data crawled from the Web (e.g.
+for answering entity queries of the SemSearch Entity track~\cite{DBLP:conf/semweb/BlancoMV11}).
+
+Some \emph{type(1)} systems can also be categorized as annotation-based document retrieval systems because they detect entities and relations in data and queries~\cite{DBLP:conf/vldb/ChengYC07,DBLP:conf/www/NieMSWM07,DBLP:conf/sigir/Chu-CarrollPCFD06}.
+However, they go beyond standard document retrieval to locate the parts (passages) in the documents that contain answers to the query.
+As mentioned in the previous Subsection, the work from IBM~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06} showed that precision can be very high when quality extraction outputs are available.
+
+The use of semantics in \emph{type(2)} systems is limited to viewing Wikipedia pages as entities~\cite{DBLP:conf/cikm/KapteinSVK10}, exploiting categories associated with them~\cite{DBLP:journals/tois/BalogBR11} as well as links between them~\cite{DBLP:conf/ecir/PehcevskiVT08}.
+As a source of semantics, experiments have shown that category information helps to interpret the entity query and to enrich the Wikipedia documents and as a result, to outperform standard text-based retrieval~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:journals/tois/BalogBR11}.
+Interestingly,
+%it has been shown that 
+Wikipedia articles can also be effectively used as a pivot for entity search on the Web, i.e.
+not only for answering queries about Wikipedia entities: it contains entities for a large amount of queries as well as cues (e.g.
+external links), which can be used to find the homepages of entities on the Web, which are referred to by Wikipedia articles~\cite{DBLP:conf/cikm/KapteinSVK10}.
+
+While many \emph{type(3)} systems~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09} have been built to search for entities over semantic data from the Web, solutions for ranking and the evaluation of their results have attracted interest only recently.
+The first systems (e.g.
+Falcons) simply used an underlying IR engine (Lucene) to index entities as documents and the built-in mechanism to rank entities.
+Recently, the SemSearch challenge attracted a large number of participants, which submitted results produced by different ranking schemes based on traditional IR concepts.
+To date, the best performed method~\cite{DBLP:conf/semweb/BlancoMV11} uses an adaptation of BM25F.
+%, which ranks entities as documents that are segmented into different fields corresponding to entity attributes.
+
+\textbf{Examples:}
+Systems searching for entity related information extracted from documents include \emph{AVATAR}, \emph{Powerset} and \emph{Watson}.
+Targeting Wikipedia documents, \emph{SERWi}~\footnote{\url{http://godzilla.kbs.uni-hannover.de:8089/ER08Demo/}} (SER) runs on top of subsets of Wikipedia used at INEX XER 2007 and 2008.
+It exploits category information treated as part of a knowledge model to interpret entity queries expressed as keywords, and returns a ranked list of entities represented by their Wikipedia pages.
+For the semantic data case, we have \emph{Sig.ma} as one representative system, which provides keyword querying capabilities over an index of semantic data sources.
+For query answering, it matches query terms against an inverted index of entity descriptions, presents the sources for which matches could be found, and also, allow users to approve or reject certain sources of information.
+As illustrated in Fig.~\ref{fig:screenshot_yahoo}, \emph{Yahoo!} (Y!) also employs semantic data for entity search.
+It uses its own curated sources of semantic data (e.g.
+data about companies) to provide -- in addition to relevant Web pages -- specific information about the requested entity and links to related entities whose ranking is computed based on co-occurrence in query logs and social media \cite{vanZwol:2010:FEI:1772690.1772788}.
+Microsoft's \emph{EntityCube} (MS) extracts information from text~\cite{DBLP:conf/www/ZhuNLZW09} to support entity-related keyword queries over documents and extracted information.
+For every query, it displays matching documents and entity information, and allows users to refine results based on facets representing related entities.
+As opposed to Yahoo!, which uses BM25F for ranking~\cite{DBLP:conf/semweb/BlancoMV11}, it uses language models for query-relevance~\cite{DBLP:conf/www/NieMSWM07} and also, PopRank for centrality-based ranking~\cite{DBLP:conf/www/NieZWM05}.
 
 \subsection{Relational Keyword Search}
-This category comprises all approaches, which process keyword queries over semantic data~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/cikm/LadwigT11,DBLP:conf/sigmod/LiOFWZ08}.
+This category comprises all approaches, which process \emph{keyword queries over semantic data} (or structured data capturing entities and relations)~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/cikm/LadwigT11}.
 While the results here include entities, the focus is to find possibly complex subgraphs encompassing several entities and relations between them (i.e.
 to support relational search).
-There exist a variety of indexing strategies and traversal algorithms that help to perform this task more efficiently.
-However, recent work~\cite{DBLP:conf/cikm/CoffmanW10} has shown that the proposed ranking strategies~\ref{DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiuYMC06} based on the adoption of proximity, TFIDF and PageRank do not perform well when considering a broad range of queries.
-This work aims at a standardized framework and benchmark for evaluating the effectiveness of relational keyword search approaches~\cite{DBLP:conf/cikm/CoffmanW10}.
-Based on this benchmark, it has been shown that best performance can be achieved through the use of edge-specific language models that are constructed for results and queries (based on PRF results)~\cite{DBLP:conf/cikm/BicerTN11}.
-\dtr{compare to recent learning to rank approach \cite{DBLP:conf/cikm/CoffmanW11}}.
+There exists a variety of indexing strategies and traversal algorithms that help to perform this task more efficiently.
+However, regarding result quality, recent work~\cite{DBLP:conf/cikm/CoffmanW10} has shown that the proposed ranking strategies (e.g.
+~\cite{DBLP:conf/icde/TranWRC09,DBLP:conf/sigmod/LiuYMC06}) based on the adoption of proximity, TFIDF and PageRank do not perform well when considering a broad range of queries.
+This work aims at a standardized framework and benchmark for evaluating the effectiveness of relational keyword search approaches.
+Based on this benchmark, it has been shown that high quality results can be achieved through the use of edge-specific language models that are constructed for results and queries~\cite{DBLP:conf/cikm/BicerTN11}.
+Also, the learning to rank strategy, which combines TFIDF-based ranking, proximity and other factors yields high performance~\cite{DBLP:conf/cikm/CoffmanW11}.
 
-\subsection{NL Question Answering} \dtr{are there benchmarks for NL QA over data?}
+\textbf{Examples:} \emph{AVATAR} in fact, not only can search over annotations but any kinds of semantic data.
+The structured queries AVATAR obtains from keywords may also involve relational information.
+Another system is \emph{SemSearchPro} (SPro), which exploits semantics throughout the search process: it uses lexical and knowledge models as well as the semantic data to translate keyword queries to SPARQL queries (interpretation), to find connections between entities mentioned in the keyword query and for processing fully structured SPARQL queries (matching), and to rank results based on structure-based proximity, centrality and query-relevance (ranking).
+As illustrated in Fig.~\ref{fig:screenshot_iwb}, it also supports faceted search, and iterative query construction where users can iteratively build complexer queries by selecting suggested terms and query completions as they type.
+\emph{TASTIER}~\footnote{\url{http://tastier.ics.uci.edu/}} (TAST) also supports this auto-completion search, suggesting results as users type.
+The relational search demo is available for DBLP~\footnote{\url{http://dblp.ics.uci.edu/}}, a dataset containing information about entities in the bibliographic domain.
+
+\subsection{Relational NL Search} As opposed to NL search over documents, which is mainly studied by IR researchers, this topic attracts a separate community that deals with interfaces over databases and knowledge bases.
+The underlying problem is about \emph{searching over semantic data}.
+We refer to it as relational NL search because relations in the data have to be processed to answer complex queries, possibly asking for relations between several entities.
+Just like relational keyword search, this type targets the more general relational search scenario, i.e.
+it can handle the entity query case, while it is not necessarily optimized for it, as opposed to entity search systems.
+
+Traditionally, this query interface is used for expert systems targeting one particular domain.
+The question of portability, and the problem of building domain-independent search systems have attracted attention in the past few years~\cite{DBLP:conf/esws/WangXZY07,DBLP:journals/dke/CimianoHHMS08,DBLP:conf/aaai/LiCYSJ07}.
+While this problem of open-domain NL search, e.g.
+NL search over large amounts of heterogeneous Web data, seems to be largely unsolved, relatively good results have been reported for single domain tasks.
+However, while there is TREC-based evaluation for NL search over documents (TREC QA track), there exists no such thing close to a standardized evaluation in this community.
+The performances reported by previous approaches are hardly comparable because different queries and datasets have been chosen for the experiments, e.g.
+experimental settings in recent works~\cite{DBLP:conf/esws/DamljanovicAC10,DBLP:conf/iui/HanNPPL10,DBLP:journals/tods/LiYJ07} differ.
+
+\textbf{Example:} \emph{NaLIX}~\cite{DBLP:journals/tods/LiYJ07} (NaL) is a system built by IBM researchers that was initially focused on one domain and then extended to \emph{DaNaLIX}~\cite{DBLP:conf/aaai/LiCYSJ07} to deal with multiple domains.
+It interprets a NL query by producing a parse tree and then maps its elements to structured queries via rules.
+These mapping rules are manually specified and additionally, can be derived from user feedbacks.
+\emph{WolframAlpha} (WolfA) also interprets NL inputs via rules.
+Its specialty is the ability of computing additional information from the data and results.
+\emph{True Knowledge} (TrueK) also makes use of reasoning for processing questions and computing results, geospatial and temporal in particular.
 
@@
   \centering
-  \caption{Add caption}
-    \begin{tabular}{r|r|r|r|r|r|r|r|r|r}
+  \caption{Classification of selected systems into aspects.}
+    \begin{tabular}{|r|r||c|c|r|c|c|c|c|c|c|c|c|c|c|r|}
     \hline
-          &       & C-Search & IBM   & Falcons & Yahoo! & AquaLog & Hermes & Naga  & TASTIER \bigstrut\\
+    \multicolumn{1}{|c}{} & \multicolumn{1}{c||}{} & \multicolumn{2}{c|}{Concept} & \multicolumn{3}{c|}{Annotation}        & \multicolumn{4}{c|}{Entity}   & \multicolumn{2}{c|}{Rel.
+Keyword} & \multicolumn{3}{c|}{Rel.
+NL}   \bigstrut\\
+\cline{3-16}    \multicolumn{1}{|c}{} & \multicolumn{1}{c||}{} & NCBO  & Hak   & \multicolumn{1}{c|}{AVA} & PS    & J!
+& SER   & Sig.
+& Y!
+& MS    & SPro  & TAST  & NaL   & WolfA & \multicolumn{1}{c|}{TrueK} \bigstrut\\
     \hline
-    \multicolumn{1}{l|}{\multirow{3}[6]{*}{Need}} & \multicolumn{1}{l|}{Entity} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Fact} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Relation} &       &       &       &       &       &       &       &  \bigstrut\\
     \hline
-    \multicolumn{1}{l|}{\multirow{4}[8]{*}{Query}} & \multicolumn{1}{l|}{Keyword} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{NL} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Facet} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Iterative} &       &       &       &       &       &       &       &  \bigstrut\\
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Need}} & \multicolumn{1}{l||}{Document} & X     & X     & X     & X     &       & X     &       & X     & X     &       &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Entity} &       &       & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relation} &       &       & X     & X     &       &       &       &       &       & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
     \hline
-    \multicolumn{1}{l|}{\multirow{3}[6]{*}{Data}} & \multicolumn{1}{l|}{Raw Data} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Semantic Data} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Semantic Metadata} &       &       &       &       &       &       &       &  \bigstrut\\
+    \multicolumn{1}{|l|}{\multirow{4}[8]{*}{Querying}} & \multicolumn{1}{l||}{Keyword} & X     & X     & X     & X     &       & X     & X     & X     & X     & X     & X     &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{NL} &       & X     &       & X     & X     &       &       &       &       &       &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Facet} & X     &       &       &       &       &       &       & X     & X     & X     &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Iterative} & X     &       &       &       &       &       &       &       &       & X     & X     &       &       &  \bigstrut\\
     \hline
-    \multicolumn{1}{l|}{\multirow{2}[4]{*}{Semantic Model}} & \multicolumn{1}{l|}{Lexical} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Knowledge} &       &       &       &       &       &       &       &  \bigstrut\\
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Data}} & \multicolumn{1}{l||}{Text} & X     & X     &       & X     & X     & X     &       & X     & X     &       &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Sem.
+Data} &       &       & X     &       & X     & X     & X     &       &       & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Metadata} & X     & X     & X     & X     & X     &       &       & X     & X     &       &       &       &       &  \bigstrut\\
     \hline
-    \multicolumn{1}{l|}{\multirow{3}[6]{*}{Interpretation}} & \multicolumn{1}{l|}{Concept} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Entity} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Relation} &       &       &       &       &       &       &       &  \bigstrut\\
+    \multicolumn{1}{|l|}{\multirow{2}[4]{*}{Sem.
+Model}} & \multicolumn{1}{l||}{Lexical} & X     & X     &       &       & X     &       &       &       &       & X     &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Knowledge} &       &       &       &       & X     & X     &       &       &       & X     &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
     \hline
-    \multicolumn{1}{l|}{\multirow{4}[8]{*}{Matching}} & \multicolumn{1}{l|}{Term } &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Structured Pattern } &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Reasoning} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Traversal} &       &       &       &       &       &       &       &  \bigstrut\\
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Data Int.}} & \multicolumn{1}{l||}{Concept} & X     & X     &       &       & X     &       &       &       &       &       &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Entity} &       &       & X     & X     & X     &       &       &       & X     &       &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relation} &       &       & X     & X     & X     &       &       &       & X     &       &       &       &       &  \bigstrut\\
     \hline
-    \multicolumn{1}{l|}{\multirow{3}[6]{*}{Ranking}} & \multicolumn{1}{l|}{Centrality} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Proximity} &       &       &       &       &       &       &       &  \bigstrut\\
-\cline{2-10}    \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{Query Relevance} &       &       &       &       &       &       &       &  \bigstrut\\
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Query Int.}} & \multicolumn{1}{l||}{Concept} & X     & X     &       &       & X     &       &       &       &       & X     &       &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Entity} &       &       & X     & X     & X     & X     &       &       & X     & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relation} &       &       & X     & X     & X     &       &       &       &       & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{4}[8]{*}{Matching}} & \multicolumn{1}{l||}{Term} & X     & X     &       & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Structure } &       &       & X     & X     &       &       &       &       &       & X     &       & X     & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Traversal} &       &       & X     &       &       &       &       &       &       & X     & X     &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Inference} &       &       &       &       & X     &       &       &       &       &       &       &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
+    \hline
+    \multicolumn{1}{|l|}{\multirow{3}[6]{*}{Ranking}} & \multicolumn{1}{l||}{Centrality} &       &       &       &       &       &       &       &       & X     & X     &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Proximity} &       &       &       &       &       &       &       &       &       & X     &       &       &       &  \bigstrut\\
+\cline{2-16}    \multicolumn{1}{|l|}{} & \multicolumn{1}{l||}{Relevance} & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     & X     &       & X     & \multicolumn{1}{c|}{X} \bigstrut\\
     \hline
     \end{tabular}%
-  \label{tab:addlabel}%
+  	\label{tab:examples}%
+  	\vspace{-0.5cm}
 \end{table*}%

### 2012-05-14 trunk/paper-iswc-reification/rep.tex
some clarifications

@@
 
-\todo{introduce this subsection (explain the purpose of the conversion function defined here)}
-
-For any RDF triple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ and blank node $b \in \symAllBNodes$ we define:
-\begin{align*}
-	\mathrm{reif}\bigl( s,p,o, b \bigr) := \big\lbrace
-		& (b,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
-		(b,\mathTinyRDF{rdf\!:\!subject},s), \\
-		& (b,\mathTinyRDF{rdf\!:\!predicate},p),
-		(b,\mathTinyRDF{rdf\!:\!object},o)
-	\big\rbrace
-\end{align*}
-
-\noindent
 Let $G$ be a set of {\RDFplusTriple}s.
-For converting $G$ into a set of RDF triples we assume a bijective function $id : \fctTRef{G} \rightarrow B$ where $B \subset \symAllBNodes$ is a set of blank nodes such that $| B | = | \fctTRef{G} |$ and $B \cap \fctTerms{G} = \emptyset$.
+For \Todo{converting}{introduce this subsection (explain the purpose of the conversion function defined here)} $G$ into a set of RDF triples we assume a bijective function $id : \fctTRef{G} \rightarrow B$ where $B \subset \symAllBNodes$ is a set of blank nodes such that $| B | = | \fctTRef{G} |$ and $B \cap \fctTerms{G} = \emptyset$.
 Hence, $id$ associates each {\TRef} in $G$ with a fresh blank node (not used in $G$).
@@
 %
-	Using $id^*$,
-	%Overloading function $\mathrm{reif}$,
-for any {\TRef} $r = (s,p,o) \in \fctTRef{G}$ we define:
-% \vspace{-3mm} % Layout Adjustment
-\begin{equation*}
-	\mathrm{reif}( r ) := \mathrm{reif}\bigl( \, id^*\!(s), id^*\!(p), id^*\!(o), id^*\!(r) \, \bigr)
-\end{equation*}
+Using $id^*$, for any {\TRef} $r = (s,p,o) \in \fctTRef{G}$ we define:
+\begin{align*}
+	\mathrm{reif}\bigl( r \bigr) := \big\lbrace
+		& (id^*\!(r),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
+		(id^*\!(r),\mathTinyRDF{rdf\!:\!subject},id^*\!(s)), \\
+		& (id^*\!(r),\mathTinyRDF{rdf\!:\!predicate},id^*\!(p)),
+		(id^*\!(r),\mathTinyRDF{rdf\!:\!object},id^*\!(o))
+	\big\rbrace
+\end{align*}
 
@@
 \noindent
-Finally:
+\Todo{Finally}{add some more text here}:
 \begin{equation*}

### 2012-05-18 paper-iswc-reification/commands.tex
removed the concept of 'triple references' from the data model and added a first draft of the querying section

%%% review commands:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcounter{todo}

\newcommand{\todo}[1]
	{\stepcounter{todo}\noindent{\color{red} \textsf{Todo~{\arabic{todo}}: #1}}}  % use this for drafts
	%{}                                                                           % use this for the final version

\newcommand{\Todo}[2]
	{{\color{red}\textsf{#1}\footnote{\todo{#2}}}}  % use this for drafts
	%{#1}                                           % use this for the final version

\newcommand{\removable}[1]%
	{{\color{gray}#1}}  % use this for drafts
	%{#1}               % use this for the final version

%%% key terminology:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\xxxPLUS}% % don't use that; it is required to define \RDFplus and \SPARQLplus
	%{$^{\mathsf{\text{\tiny +\!meta}}}$}
	{$^\star$}

\newcommand{\RDFplus}{RDF\xxxPLUS}
\newcommand{\SPARQLplus}{SPARQL\xxxPLUS}

\newcommand{\RDFplusTriple}{{\RDFplus}\! triple}
\newcommand{\RDFplusGraph}{{\RDFplus}\! graph}
\newcommand{\TPplus}{triple\xxxPLUS pattern}

\newcommand{\TRef}%
	%{triple reference}
	{tref}
\newcommand{\TRefLongVersion}{triple reference}

\newcommand{\TRefPtt}{{\TRef} pattern}
\newcommand{\TRefPttLongVersion}{{\TRefLongVersion} pattern}

%%% relevant math symbols
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\emptyset}{\varnothing}

\newcommand{\symDomFct}{\mathrm{dom}} % the name used for \fctDom
\newcommand{\fctDom}[1]{\symDomFct(#1)} % the domain of function/mapping #1

\newcommand{\symAllURIs}{\mathcal{U}} % the symbol for the set of all URIs
\newcommand{\symAllLiterals}{\mathcal{L}} % the symbol for the set of all literals
\newcommand{\symAllBNodes}{\mathcal{B}} % the symbol for the set of all blank nodes
\newcommand{\symAllVariables}{\mathcal{V}} % the symbol for the set of all query variables

	\newcommand{\symAllTriplesInfinite}{\mathcal{T}} % don't use that; it is required to define \symAllTriples
\newcommand{\symAllTriples}{\overline{\symAllTriplesInfinite}} % the symbol for the set of all triple references
	\newcommand{\symAllTPsInfinite}{\mathcal{TP}} % don't use that; it is required to define \symAllTPs
\newcommand{\symAllTPs}{\overline{\symAllTPsInfinite}} % the symbol for the set of all triple references

	\newcommand{\symAllTRefsInfinite}{\mathcal{R}} % don't use that; it is required to define \symAllTRefs
\newcommand{\symAllTRefs}{\overline{\symAllTRefsInfinite}} % the symbol for the set of all triple references
	\newcommand{\symAllTRefPttsInfinite}{\mathcal{RP}} % don't use that; it is required to define \symAllTRefPtts
\newcommand{\symAllTRefPtts}{\overline{\symAllTRefPttsInfinite}} % the symbol for the set of all triple reference patterns

\newcommand{\symTermsFct}{\mathrm{terms}} % the name used for \fctTerms
\newcommand{\fctTerms}[1]{\symTermsFct(#1)} % the set of all terms in triple #1

\newcommand{\symTermsPlusFct}{\symTermsFct^+} % the name used for \fctTermsPlus
\newcommand{\fctTermsPlus}[1]{\symTermsPlusFct\!(#1)} % the set of all terms in triple #1 and its embedded triples

\newcommand{\symTRefsFct}{\mathrm{trefs}} % the name used for \fctTrefs
\newcommand{\fctTRefs}[1]{\symTRefsFct(#1)} % the set of all triple references in triple/graph #1

% \newcommand{\symDerefFct}{\mathrm{deref}} % the name used for \fctDeref
% \newcommand{\fctDeref}[1]{\symDerefFct(#1)} % the triple denoted by triple reference #1

% \newcommand{\symCloseFct}{\mathrm{cl}} % the name used for \fctClose
% \newcommand{\fctClose}[1]{\symCloseFct(#1)} % the tref-closure of #1

\newcommand{\symVarsFct}{\mathrm{vars}} % the name used for \fctVars
\newcommand{\fctVars}[1]{\symVarsFct(#1)} % the set of all variables in pattern #1

\newcommand{\symDescentFct}{\mathrm{rdf}} % the name used for \fctDescent
\newcommand{\fctDescent}[1]{\symDescentFct(#1)} % set of RDF triples for an RDF+ triple/graph

\newcommand{\mathTinyRDF}[1]{\texttt{\footnotesize #1}}

\newcommand{\OpAND}{\text{ \normalfont\scriptsize\textsf{AND} }}
\newcommand{\OpUNION}{\text{ \normalfont\scriptsize\textsf{UNION} }}
\newcommand{\OpOPT}{\text{ \normalfont\scriptsize\textsf{OPT} }}
\newcommand{\OpFILTER}{\text{ \normalfont\scriptsize\textsf{FILTER} }}
\newcommand{\OpAS}{\text{ \normalfont\scriptsize\textsf{AS} }}
\newcommand{\compatible}{\sim} % the symbol for compatibility between valuations
\newcommand{\fctEval}[2]{[\![#1]\!]_{#2}} % the symbol for the evaluation of SPARQL pattern #1 over an RDF graph #2

%% The following definitions of a symbol for left outer join work best in Springer format:
\def\ojoin{\setbox0=\hbox{$\Join$}\rule[.01ex]{.25em}{.45pt}\llap{\rule[1.05ex]{.25em}{.4pt}}}
\def\LJoin{\mathbin{\ojoin\mkern-7.5mu\Join}}

### 2012-05-18 paper-iswc-reification/querying.tex
removed the concept of 'triple references' from the data model and added a first draft of the querying section

\section{Querying}
\todo{introduction for this section}

\subsection{Syntax of {\SPARQLplus}}

	Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$ where $\symAllVariables$ is a set of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively.
	%We assume a set $\symAllVariables$ of query variables that is disjoint from $\symAllURIs$, $\symAllBNodes$, and $\symAllLiterals$, respectively. Let $\symAllTPsInfinite := (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs) \times (\symAllVariables \cup \symAllURIs) \times (\symAllVariables \cup \symAllTPsInfinite \cup \symAllURIs \cup \symAllLiterals)$.
A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).
	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVars{tp}$; hence, $\fctVars{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVars{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
	For any {\TPplus} $tp \!=\! (s,p,o)$ we define $\fctVars{tp} \!:=\! \bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVars{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.

	We now define \emph{{\SPARQLplus} expression}s recursively \removable{as follows}:
	%\emph{{\SPARQLplus} expression}s are defined recursively \removable{as follows}:
\begin{enumerate}
	\item A \emph{\TPplus} is a {\SPARQLplus} expression.
	\item Let $tp \in \symAllTPs$ and $?v \in \symAllVariables$, then $(tp \OpAS ?v)$ is a {\SPARQLplus} expression.
	\item Let $P_1$ and $P_2$ be {\SPARQLplus} expressions and $R$ a filter condition%
		\footnote{For a formal definition of
			\removable{the syntax and semantics of}
		filter conditions we refer to~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.}%
	, then $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, and $(P_1 \OpFILTER R)$ are {\SPARQLplus} expressions.
\end{enumerate}

\subsection{{\RDFplus} Semantics of {\SPARQLplus}}
	To define the semantics of {\SPARQLplus} we introduce
	%We define the semantics of {\SPARQLplus} based on
\emph{valuation}s, that are, partial mappings $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
Two valuations $\eta$ and $\eta'$ are \emph{compatible}, denoted by $\eta \compatible \eta'$, if for all $?v \in \fctDom{\eta} \cap \fctDom{\eta'}$ holds $\eta(?v) = \eta'(?v)$; note,
	%$\fctDom{\eta}$ denotes
	$\fctDom{\eta}$~denotes %% Layout Adjustment
the domain of a valuation $\eta$.

Let $\Omega_1$, $\Omega_2$ and $\Omega$ be sets of valuations; let $R$ be a filter condition. The binary operations \emph{join}, \emph{union}, \emph{difference}, and \emph{left outer-join} between $\Omega_1$ and $\Omega_2$ are defined as follows:
\begin{align*}
	\Omega_1 \Join \Omega_2 & := \lbrace \eta_1 \cup \eta_1 \,|\, \eta_1 \in \Omega_1 \text{ and } \eta_2 \in \Omega_2 \text{ and } \eta_1 \sim \eta_2 \rbrace \\
	\Omega_2 \cup \Omega_2 & := \lbrace \eta \,|\, \eta \in \Omega_1 \text{ or } \eta \in \Omega_2 \rbrace \\
	\Omega_1 \setminus \Omega_2 & := \lbrace \eta_1 \in \Omega_1 \,|\, \forall \eta_2 \in \Omega_2 : \eta_1 \not\sim \eta_2 \rbrace \\
	\Omega_1 \LJoin \Omega_2 &:= \left( \Omega_1 \Join \Omega_2 \right) \cup \left( \Omega_1 \setminus \Omega_2 \right) \\
	\sigma_R ( \Omega ) &:= \lbrace \eta \in \Omega \,|\, \eta \text{ satisfies } R \rbrace
\end{align*}

%For a valuation $\eta$ and a {\TPplus} $tp$, we write $\eta[tp]$ to denote the {\TPplus} that we obtain by replacing the variables in $tp$ (including potentially embedded {\TPplus}s) according to $\eta$. Note, if $\fctVars{tp} \subseteq \fctDom{\eta}$, then $\eta[tp]$ is an {\RDFplusTriple}.

	%Let $P$ be a {\SPARQLplus} expression and let $G$ be an {\RDFplusGraph}. The \emph{evaluation of $P$ over $G$},
	The \emph{evaluation} of {\SPARQLplus} expression $P$ over {\RDFplusGraph} $G$,
denoted by $\fctEval{P}{G}$, is defined recursively as follows:
\begin{enumerate}
	\item If $P$ is a {\TPplus} $tp$, then
		\begin{equation*}
			\fctEval{P}{G} := \big\lbrace \eta \,\big|\,
				\eta \text{ is a valuation with } \fctDom{\eta} = \fctVars{tp}
				\text{ and } \eta[tp] \in G \cup \fctTRefs{G}
			\big\rbrace
		\end{equation*}
		where $\eta[tp]$ denotes the {\TPplus} that we obtain by replacing the variables in $tp$ (including potentially embedded {\TPplus}s) according to $\eta$ (note, if $\fctVars{tp} \subseteq \fctDom{\eta}$, then $\eta[tp]$ is an {\RDFplusTriple}).
		\vspace{1ex} %% Layout Adjustment
	\item If $P$ is $(tp \OpAS ?v)$, then
		\begin{align*}
			\fctEval{P}{G} := \big\lbrace \eta \,\big|\,
				& \eta' \in \fctEval{tp}{G} 
				\text{ and } %\eta \text{ is a valuation with }
					\fctDom{\eta} = \fctDom{\eta'}\cup \lbrace ?v \rbrace
				\text{ and } \eta \compatible \eta' \text{ and }\\
				& \eta(?v) = \eta[tp] \,
			\big\rbrace
		\end{align*}
		\item If $P$ is $(P_1 \OpAND P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \Join \fctEval{P_2}{G}$.
		\item If $P$ is $(P_1 \OpUNION P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \cup \fctEval{P_2}{G}$.
		\item If $P$ is $(P_1 \OpOPT P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \LJoin \fctEval{P_2}{G}$.
		\item If $P$ is $(P' \OpFILTER R)$, then $\fctEval{P}{G} := \sigma_R\bigl( \fctEval{P'}{G} \bigr)$.
	\end{enumerate}
	Each valuation $\eta \in \fctEval{P}{G}$ is called a \emph{solution} for $P$ in $G$.

\begin{proposition}
	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEval{P}{G} = \fctEval{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
\end{proposition}

\subsection{RDF Semantics of {\SPARQLplus}}
	%For RDF storage systems that do not support our {\RDFplus} data model (but the ordinary RDF data model), we define an alternative semantics for {\SPARQLplus}.
	In addition to the {\SPARQLplus} semantics defined in the previous section, we now define an alternative semantics for {\SPARQLplus}. This alternative semantics enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.

\todo{...}

### 2012-05-18 paper-iswc-reification/rep.tex
removed the concept of 'triple references' from the data model and added a first draft of the querying section

@@
-\section{Representation}
-Syntax 
-Expressed tersely as:
-  <<:SAP :bought :sybase>> dc:source reuters:us-sybase .
-Statements are “wrapped” by << … >> 
-Turtle Extension
-<<:SAP :bought :sybase>> dc:source reuters:us-sybase ;
-			  dc:created “1995-01-07” ;
-                        		 dc:author  “James R. Jones“ .
+\section{Data Model} \label{Section:DataModel}
 
--	The statement can appear in either the subject or object position.
--	Recursion in statements is allowed
--	But depth is shallow in practice
-Semantics
+In this section we introduce
+	%an extension of the RDF data model~\cite{Klyne04:RDFconcepts} that makes 
+	our data model which we call {\RDFplus}.
+This model is an extension of the RDF data model~\cite{Klyne04:RDFconcepts}.
+{\RDFplus} extends RDF by making metadata statements a first class citizen in the data model.
+% In the following we \todo{...}
+
+% Main purposes of our data model: 1.)~it allows for a more compact representation; 2.)~it allows for efficient processing
+% with {\RDFplus} our goal is to extend/expand the applicability/usefulness/usability of such triples for cases where ...
+
+\subsection{Concepts}
+
+We assume
+	%\removable{three,}
+pairwise disjoint sets $\symAllURIs$ (all URI references), $\symAllBNodes$ (blank nodes), and $\symAllLiterals$ (literals).
+	As usual, an \emph{RDF triple} is a tuple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ and an \emph{RDF graph} is a set of RDF triples.
+	%As usual, a tuple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ is an \emph{RDF triple}.
+% A set of RDF triples is an \emph{RDF graph}.
+
+{\RDFplus} extends such triples by permitting the embedding of another triple in the subject or object position of a given triple.
+We shall interpret the embedding triple as a statement about the embedded triple.
+An embedded triple may itself be a statement about a triple and, thus, may also contain embedded triples; and so forth.
+	%Therefore, the model should allow for nesting.
+%
+	%As a basis for formalizing
+	To formalize
+such kind of (nested) embedding we
+	%introduce
+	define
+a set $\symAllTriplesInfinite := (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$.
+%
+	As a basis for ruling
+	%To rule
+out infinitely deep nesting we introduce the notion of \emph{$k$-nestedness} (where $k$
+	is an arbitrary
+	%may be any
+natural number): A tuple $(s,p,o) \in \symAllTriplesInfinite$ is $k$-nested if either 1.)~$k=0$ and
+	%$(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$
+	$(s,p,o)$ is an RDF triple
+or 2.)~$k>0$ and for all $x \in \bigl( \lbrace s,o \rbrace \cap \symAllTriplesInfinite \bigr)$ holds $x$ is $(k\!-\!1$)-nested. Using $k$-nestedness we now define our extended notion of triples%
+	.
+	%:
+
+An \emph{{\RDFplusTriple}} is a tuple $t \in \symAllTriplesInfinite$ for which exists a natural number $k$ such that $t$ is $k$-nested; to denote the set of all {\RDFplusTriple}s we write $\symAllTriples$ (i.e.~$\symAllTriples \subset \symAllTriplesInfinite$).
+For any {\RDFplusTriple} $t=(s,p,o)$ we define
+	$\fctTermsPlus{t} := \lbrace s,p,o \rbrace \cup \big\lbrace x' \in \fctTermsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTriples \big\rbrace$.
+	%$\fctTermsPlus{t} := \lbrace s,p,o \rbrace \cup \bigcup_{x \in \lbrace s,o \rbrace \cap \symAllTriples} \fctTermsPlus{x}$.
+%Furthermore, we write $\fctTRef{t}$ to denote the set of all {\RDFplusTriple}s that are (recursively) embedded in $t$; formally: $\fctTRef{t} := \bigl( \lbrace s,o \rbrace \cap \symAllTriples \bigr) \cup \big\lbrace t' \in \fctTRef{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTriples \big\rbrace$.
+We call an {\RDFplusTriple}
+	$t=(s,p,o)$ for which $s \in \symAllTriples$ or $o \in \symAllTriples$,
+	%$t$ for which $\fctTRef{t} = \emptyset$,
+a \emph{metadata triple}%
+	%; note that any other {\RDFplusTriple} is an ordinary RDF triple.
+	.
+
+A set of {\RDFplusTriple}s is an \emph{\RDFplusGraph}.
+Overloading function $\symTermsPlusFct$, for any {\RDFplusGraph} $G$ we define $\fctTermsPlus{G} := \bigcup_{t \in G} \fctTermsPlus{t}$.
+Furthermore, for {\RDFplusGraph} $G$, we write $\fctTRefs{G}$ to denote the set of all {\RDFplusTriple}s that are (recursively) embedded in {\RDFplusTriple}s of $G$; hence $\fctTRefs{G} := \fctTermsPlus{G} \cap \symAllTriples$.
+
+% Any {\RDFplusTriple} that is embedded in another {\RDFplusTriple} is also assumed to be (implicitly) contained in data that contains the embedding triple.
+To make this assumption explicit we introduce an operation that (recursively) unnests {\RDFplusTriple}s: Let $t=(s,p,o)$ be an {\RDFplusTriple}, then $\fctClose{t}$ is a set of {\RDFplusTriple}s that is defined as follows:
+% \begin{equation*}
+% 	\fctClose{t} := \big\lbrace t' \,\big|\, t' = t \text{ or } \exists \, t^* \in \lbrace s,o \rbrace \cap \symAllTriples : t' \in \fctClose{t^*} \big\rbrace
+% \end{equation*}
+% Overloading
+% 	function $\symCloseFct$,
+% 	%notation,
+% for any {\RDFplusGraph} $G$ we define $\fctClose{G} := \bigcup_{t \in G} \fctClose{t}$.
+
+% While syntactically {\RDFplusTriple}s and {\TRef}s are the same, they represent different concepts: {\RDFplusTriple}s may be interpreted as statements (similar to RDF triples) whereas a {\TRef} denotes an {\RDFplusTriple}
+% 	%that is embedded in other {\RDFplusTriple}s.
+% 	for the purpose of making a statement about it.
+% %
+% 	\removable{Hence, trefs may be understood as a particular type of name for {\RDFplusTriple}s.}
+% However, since {\TRef}s carry all elements of the {\RDFplusTriple}s they denote, it is possible to obtain such a triple from its reference: We introduce a bijective function $\symDerefFct$ that maps the set of {\TRef}s to the set of all {\RDFplusTriple}s and that is defined as follows: Let $r=(s,p,o) \in \symAllTRefs$ be an arbitrary {\TRef}, then $\fctDeref{r}$ is the {\RDFplusTriple} $(s,p,o)$.
+
+% \todo{$G$ and $\fctClose{G}$ are semantically equivalent!!}
+\todo{$G$ and $G \cup \fctTRefs{G}$ are semantically equivalent!!}
+
+\subsection{Interpretation}
+
+Let $G$ be an {\RDFplusGraph}.
+For \Todo{converting}{introduce this subsection (explain the purpose of the conversion function defined here)} $G$ into a set of RDF triples we assume a bijective function $id : \fctTRefs{G} \rightarrow B$ where $B \subset \symAllBNodes$ is a set of blank nodes such that $| B | = | \fctTRefs{G} |$ and $B \cap \fctTerms{G} = \emptyset$.
+Hence, $id$ associates each {\TRef} in $G$ with a fresh blank node (not used in $G$).
+Furthermore, we introduce
+	%an injective function $id^* : \fctTermsPlus{G} \rightarrow \fctTermsPlus{G} \cup B$
+	another bijective function $id^*\! : \fctTermsPlus{G} \rightarrow B \cup \bigl( \fctTermsPlus{G} \!\setminus\! \fctTRefs{G} \bigr)$
+that is defined as follows: Let $x \in \fctTermsPlus{G}$. If $x \in \symAllTriples$ then $id^*\!(x) := id(x)$; if $x \notin \symAllTriples$ then $id^*\!(x) := x$.
+%
+Using $id^*$, for any $t = (s,p,o) \in \fctTRefs{G}$ we define:
+\begin{align*}
+	\mathrm{reif}\bigl( t \bigr) := \big\lbrace
+		& (id^*\!(t),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
+		(id^*\!(t),\mathTinyRDF{rdf\!:\!subject},id^*\!(s)), \\
+		& (id^*\!(t),\mathTinyRDF{rdf\!:\!predicate},id^*\!(p)),
+		(id^*\!(t),\mathTinyRDF{rdf\!:\!object},id^*\!(o))
+	\big\rbrace
+\end{align*}
+
+\noindent
+For any {\RDFplusTriple} $t = (s,p,o) \in G$ we define:
+\begin{equation*}
+	\fctDescent{t} := \begin{cases}
+\vspace{1mm}
+		\big\lbrace (id(s),p,o) \big\rbrace \cup \mathrm{reif}(s) \cup \fctDescent{s} & \text{if $s \in \symAllTriples$ and $o \notin \symAllTriples$,} \\
+\vspace{1mm}
+		\big\lbrace (s,p,id(o)) \big\rbrace \cup \mathrm{reif}(o) \cup \fctDescent{o} & \text{if $s \notin \symAllTriples$ and $o \in \symAllTriples$,} \\
+\vspace{1mm}
+		\begin{minipage}[c]{55mm}\vspace{1mm}
+			$\big\lbrace (id(s),p,id(o)) \big\rbrace \cup \mathrm{reif}(s) \cup \fctDescent{s}$ \\
+			\hspace*{27.5mm}$\cup \, \mathrm{reif}(o) \cup \fctDescent{o}$
+		\end{minipage} & \text{if $s \in \symAllTriples$ and $o \in \symAllTriples$,} \\
+		\big\lbrace (s,p,o) \big\rbrace & \text{else} .
+\end{cases}
+\end{equation*}
+
+\noindent
+\Todo{Finally}{add some more text here}:
+\begin{equation*}
+	\fctDescent{G} := \bigcup_{t \in G} \fctDescent{t}
+\end{equation*}
+
+\begin{example}
+	Let $G_\mathsf{ex} = \lbrace t_\mathsf{ex} \rbrace$ be an {\RDFplusGraph} that consists of a single {\RDFplusTriple} $t_\mathsf{ex} = \bigl( (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}), \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf} \bigr)$.
+% 	The result of converting $G_\mathsf{ex}$ to an RDF graph is:
+% 	\begin{align*}
+% 		\fctDescent{G_\mathsf{ex}} = \big\lbrace
+% 			& (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}),
+% 			(b, \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf}), \\
+% 			& (b,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
+% 			(b,\mathTinyRDF{rdf\!:\!subject},\mathTinyRDF{ex:olaf}), \\
+% 			& (b,\mathTinyRDF{rdf\!:\!predicate},\mathTinyRDF{foaf:name}),
+% 			(b,\mathTinyRDF{rdf\!:\!object},\mathTinyRDF{"Olaf"})
+% 		\big\rbrace
+% 	\end{align*}
+	The result of converting $G_\mathsf{ex}$ to an RDF graph $\fctDescent{G_\mathsf{ex}}$ is (in Turtle notation, prefix declarations omitted):
+	\begin{footnotesize}%
+	\begin{verbatim}
+		 ex:olaf foaf:name "Olaf" .
+		 _:b dct:source ex:olaf ; rdf:type rdf:Statement ;
+		     rdf:subject ex:olaf ; rdf:predicate foaf:name ; rdf:object "Olaf" .
+	\end{verbatim}%
+	\end{footnotesize}
+\end{example}
+
+\noindent
+Based on the conversion function, it is possible to interpret any {\RDFplus} model via the usual RDF semantics as defined in~\cite{Hayes04:RDFsemantics}.
+
+\begin{proposition}
+	For any {\RDFplusGraph} $G$ it holds $\fctDescent{G} = \fctDescent{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
+\end{proposition}
+
+\subsection{Representation}
+\todo{briefly introduce our extension for Turtle and explain how this extension is related to {\RDFplus} and how it should be parsed by systems that do not ``understand'' {\RDFplus}}
+
+	\begin{footnotesize}%
+	\begin{verbatim}
+		 <<ex:olaf foaf:name "Olaf">> dct:source ex:olaf .
+	\end{verbatim}%
+	\end{footnotesize}
+
+\todo{From a didactic point of view it may be better to move this subsection to the beginning of Section~\ref{Section:DataModel}}

### 2012-05-28 paper-iswc-reification/exp.tex

\section{Experiments}
We now study the advantages of our approach as discussed previously through an experimental analysis, in which we compare our work with an implementation of the standard proposal for RDF reification. The results suggest...

\subsection{Data}
-	dataset description: which dataset, which version, how did we generate meta-level statements, what kinds\\
- dataset statistics: how many triples, how many meta-level triples\\

\subsection{Queries}
-	query set description: which queries, how did we generate meta-level queries, what kinds\\
- query statistics: average, min, max number of triple patterns / meta-level triple patterns per query\\ 
- group queries according to complexity classes: (1) according to overall number of triple patterns, e.g. 1,2,3 and so on (2) according to number of meta-level triple patterns, (3) according to data size / selectivity (measured in terms of the total number of triples that have to be loaded), e.g. 1-1000 triples, 1000-1000, and so on\\

\subsection{Systems}
- Description of Bigdata: what is that, how does it implement our proposal: h

Virtuoso

\subsection{Data Management Performance}

\subsection{Query Processing Performance}

Show the benefits in experiments
Systems

Data
-	Size of the data
-	Size of the indexes 
Loading Time Performance
Querying Time Performance

### 2012-05-28 trunk/paper-iswc-reification/dis.tex

@@
 \section{Discussion}
-What are benefits compared to RDF reification and other related work:
-Compact Representation 
-Efficient Querying 
+What are benefits compared to RDF reification and other related work. We discuss the benefits in terms of data management and query processing.
+
+\subsection{Data Management}
+- model efficient representation: less triples needed\\
+- thus more compact serialization: smaller turtle export\\
+
+\subsection{Query Processing}
+- more efficient processing because less data has to be loaded and \\
+- less joins are needed to combine binding for different triple patterns\\
+
  \# Who bought Sybase and where did we get that fact?

### 2012-05-28 trunk/paper-iswc-reification/exp.tex

@@
 \section{Experiments}
-Show the benefits in experiments
-Systems
--	Bigdata
--	Virtuoso
+We now study the advantages of our approach as discussed previously through an experimental analysis, in which we compare our work (henceforth referred to as \emph{Refi+}) with an implementation of the standard proposal for RDF reification (\emph{Refi}).
+The results suggest...
 
-Data
--	Datasets + artificially generated meta-level statements
--	Size of the data
--	Size of the indexes 
-Loading Time Performance
-Querying Time Performance
+\subsection{Data}
+-	dataset description: which dataset, which version, how did we generate meta-level statements, what kinds\\
+- dataset statistics: how many triples, how many meta-level triples (the meta-level triples needed for \emph{Refi}) \\
+
+\subsection{Queries}
+-	query set description: which queries, how did we generate meta-level queries, what kinds\\
+- query statistics: average, min, max number of triple patterns / meta-level triple patterns per query\\
+- group queries according to complexity classes:\\
+(1) according to overall number of triple patterns, e.g. 1,2,3 and so on \\
+(2) according to number of meta-level triple patterns, \\
+(3) according to data size / selectivity (measured in terms of the total number of triples that have to be loaded / also here meta-level triples are counted based on the \emph{Refi} implementation), e.g.
+1-1000 triples, 1000-1000, and so on\\
+
+\subsection{Systems}
+We have two commercial systems that implement our work, \emph{Refi+}, as well as the original RDF reification proposal, \emph{Refi}.\\
+
+- Description of Bigdata: what is Bigdata, how does it implement our proposal and the RDF reification baseline\\
+- (1) in terms of data management (see the data management performance subsection below): representation (short: what is the data structure used to represent triples and so on), serialization (short: which serialization supports, say a bit about how we support/implement the turtle serialization of our proposal), indexing (what indexes are used for accessing triples /  meta-level triples)\\
+- (2) and in terms of query processing: join implementation\\
+
+- Description of Virtuoso: what is Virtuoso, how does it implement our proposal and the RDF Reification baseline\\
+- (1) in terms of data management (see the data management performance subsection below): representation (short: what is the data structure used to represent triples and so on), serialization (short: which serialization supports, say a bit about how we support/implement the turtle serialization of our proposal), indexing (the data structure used for implementing the indexes; for which access patterns indexes are created for accessing triples /  meta-level triples)\\
+- (2) and in terms of query processing: join implementation\\
+
+\subsection{Data Management Performance}
+Compared to Refi, we show that Refi+ (1) requires less triples to manage meta-level triples, (2) its turtle export is more compact in size and (3) its indexes are smaller, required less time to be computed.
+For this, we compare Refi and Refi+ in terms of \\
+- Data representation: the \emph{number of triples} needed\\
+- Data serialization: we serialize the model in Turtle syntax then compare the \emph{size of the resulting exports}\\
+- Data indexing: size of the indexes, time needed to produce all the indexes (while Bigdata and Virtuoso may used different data structures for index implementation, and create different indexes for supporting different kinds / number of access patterns, the index configuration used for Refi and Refi+ within these systems should be same!)
+
+\subsection{Query Processing Performance}
+Compare to Refi, we show Refi+ requires less time to answer queries.
+In particular, we show that for Refi+, less data has to be accessed, and also, a smaller number of joins is needed.
+Thus, we should further decompose times into fractions attributable (1) to loading triples (scan / index lookups for answering every triple patterns) and (2) combing them  (union / join results for answering several patterns) and (3) additional processing (sort, group, filter).
+
+We compare Refi and Refi+ in terms of \\ 
+- Total performance: total time in ms (a) average over all queries, (b) average for every complexity class of queries (see queries subsection)\\
+- Load performance: load time in ms (a) average over all queries, (b) average for every complexity class of queries (see queries subsection)\\ 
+- Join performance: time needed for join/union in ms (a) average over all queries, (b) average for every complexity class of queries (see queries subsection); additionally, we also count and compare the number of join operations needed

### 2012-05-29 trunk/paper-iswc-reification/querying.tex
added projection operation to the SPARQL fragment we focus on; started to draft the RDF-compatible semantics for our SPARQL extension

--- 2012-05-18 paper-iswc-reification/querying.tex
@@
 	, then $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, and $(P_1 \OpFILTER R)$ are {\SPARQLplus} expressions.
+	\item Let $P$ be a {\SPARQLplus} expression and $S \subset \symAllVariables$ be a finite set of variables, then $\OpSELECT_S(P)$ is a {\SPARQLplus} expression.
 \end{enumerate}
@@
 
-Let $\Omega_1$, $\Omega_2$ and $\Omega$ be sets of valuations; let $R$ be a filter condition.
-The binary operations \emph{join}, \emph{union}, \emph{difference}, and \emph{left outer-join} between $\Omega_1$ and $\Omega_2$ are defined as follows:
+Let $\Omega_1$, $\Omega_2$ and $\Omega$ be sets of valuations; let $R$ be a filter condition; and let $S \subset \symAllVariables$ be a finite set of variables.
+The algebra operators \emph{join}, \emph{union}, \emph{difference}, \emph{left outer-join}, \emph{selection}, and \emph{projection} are defined as follows:
 \begin{align*}
@@
 	\Omega_1 \LJoin \Omega_2 &:= \left( \Omega_1 \Join \Omega_2 \right) \cup \left( \Omega_1 \setminus \Omega_2 \right) \\
-	\sigma_R ( \Omega ) &:= \lbrace \eta \in \Omega \,|\, \eta \text{ satisfies } R \rbrace
+	\sigma_R ( \Omega ) &:= \lbrace \eta \in \Omega \,|\, \eta \text{ satisfies } R \rbrace \\
+	\pi_S ( \Omega ) &:= \lbrace \eta \,|\, \exists \, \eta' : \eta \cup \eta' \in \Omega \text{ and } \fctDom{\eta} \subseteq S \text{ and } \fctDom{\eta'} \cap S = \emptyset \rbrace
 \end{align*}
@@
 	The \emph{evaluation} of {\SPARQLplus} expression $P$ over {\RDFplusGraph} $G$,
-denoted by $\fctEval{P}{G}$, is defined recursively as follows:
+denoted by $\fctEvalPlus{P}{G}$, is defined recursively as follows:
 \begin{enumerate}
@@
 		\begin{equation*}
-			\fctEval{P}{G} := \big\lbrace \eta \,\big|\,
+			\fctEvalPlus{P}{G} := \big\lbrace \eta \,\big|\,
 				\eta \text{ is a valuation with } \fctDom{\eta} = \fctVars{tp}
@@
 		\begin{align*}
-			\fctEval{P}{G} := \big\lbrace \eta \,\big|\,
-				& \eta' \in \fctEval{tp}{G} 
+			\fctEvalPlus{P}{G} := \big\lbrace \eta \,\big|\,
+				& \eta' \in \fctEvalPlus{tp}{G} 
 				\text{ and } %\eta \text{ is a valuation with }
@@
 		\end{align*}
-		\item If $P$ is $(P_1 \OpAND P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \Join \fctEval{P_2}{G}$.
-		\item If $P$ is $(P_1 \OpUNION P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \cup \fctEval{P_2}{G}$.
-		\item If $P$ is $(P_1 \OpOPT P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \LJoin \fctEval{P_2}{G}$.
-		\item If $P$ is $(P' \OpFILTER R)$, then $\fctEval{P}{G} := \sigma_R\bigl( \fctEval{P'}{G} \bigr)$.
+	\item If $P$ is $(P_1 \OpAND P_2)$, then $\fctEvalPlus{P}{G} := \fctEvalPlus{P_1}{G} \Join \fctEvalPlus{P_2}{G}$.
+	\item If $P$ is $(P_1 \OpUNION P_2)$, then $\fctEvalPlus{P}{G} := \fctEvalPlus{P_1}{G} \cup \fctEvalPlus{P_2}{G}$.
+	\item If $P$ is $(P_1 \OpOPT P_2)$, then $\fctEvalPlus{P}{G} := \fctEvalPlus{P_1}{G} \LJoin \fctEvalPlus{P_2}{G}$.
+	\item If $P$ is $(P' \OpFILTER R)$, then $\fctEvalPlus{P}{G} := \sigma_R\bigl( \fctEvalPlus{P'}{G} \bigr)$.
+	\item If $P$ is $\OpSELECT_S(P')$, then $\fctEvalPlus{P}{G} := \pi_S\bigl( \fctEvalPlus{P'}{G} \bigr)$.
 \end{enumerate}
-	Each valuation $\eta \in \fctEval{P}{G}$ is called a \emph{solution} for $P$ in $G$.
+Each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.
 
 \begin{proposition}
-	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEval{P}{G} = \fctEval{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
+	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
 \end{proposition}
+
+\todo{There is a minimal $G_\mathsf{min} \subseteq G$ with $G_\mathsf{min} = G^+$ ...}
 
@@
 \todo{...}
+
+GOAL: for all $P$ that do not contain a subexpression of the form $(tp \OpAS ?v)$ for which $?v \in pVars(\fctEvalPlus{P}{G})$ it shall hold: $\fctEvalPlus{P}{G} = \fctEvalPlus{\fctDescent{P}}{\fctDescent{G}} = \fctEval{\fctDescent{P}}{\fctDescent{G}}$.
+Note, the set of possible variable $pVars\bigl(\fctEvalPlus{P}{G}\bigr)$ of a {\SPARQLplus} algebra expression $\fctEvalPlus{P}{G}$ is defined in the same way Schmidt et al.~define $pVars$ for SPARQL set algebra expressions~\cite{Schmidt10:FoundationsOfSPARQLOptimization}, we only extend the definition for our $\OpAS$ expression as follows: $pVars\bigl(\fctEvalPlus{(tp \OpAS ?v)}{G}\bigr) := \lbrace ?v \rbrace \cup \fctVars{tp}$.
+
+Let $P$ be a {\SPARQLplus} expression and let $V_\mathsf{new} \subseteq \symAllVariables \cap \fctVars{P}$.
+\todo{we need a mapping from all triple reference patterns in $P$ to $V_\mathsf{new}$ so that we can use the same var all the time}
+The \emph{RDF compatible expression} of {\SPARQLplus} expression $P$,
+denoted by $\fctDescent{P}^V$, is defined recursively as follows:
+\begin{enumerate}
+	\item If $P$ is a {\TPplus} $tp$, then $\fctDescent{P}^V$ is \todo{...}
+	\item If $P$ is $(tp \OpAS ?v)$, then $\fctDescent{P}^V$ is \todo{...}
+	\item If $P$ is $(P_1 \OpAND P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpAND P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
+	\item If $P$ is $(P_1 \OpUNION P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpUNION P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
+	\item If $P$ is $(P_1 \OpOPT P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpOPT P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
+	\item If $P$ is $(P_1 \OpFILTER R)$, then $\fctDescent{P}^V$ is $(P_1' \OpFILTER R)$ where $P_1'$ is $\fctDescent{P_1}^V$.
+	\item If $P$ is $\OpSELECT_S(P_1)$, then $\fctDescent{P}^V$ is $\OpSELECT_S(P_1')$ where $P_1'$ is $\fctDescent{P_1}^V$.
+\end{enumerate}

### 2012-06-02 trunk/paper-iswc-reification/abstract.tex
added Abstract (as written by Thanh, but with slight improvements of the English)

Meta-level information is commonly associated with RDF statements to capture provenance as well as quality related aspects. RDF reification is the standard mechanism to express this kind of information at the statement-level. In this work, we revisit the drawbacks of this mechanism. Specifically in the RDF data management and query processing context, we show that not only it results in a large number of triples but also, requires a large number of joins in queries that ask for meta-level information. To address these problems we propose a solution for reification that extends the current RDF and SPARQL standards. Based on two commercial RDF stores' adoption of this solution, we show in experiments that our proposal significantly improves the efficiency of RDF data management and SPARQL query processing, compared to the original RDF reification proposal.

### 2012-06-02 paper-iswc-reification/querying.tex
added vars+(tp)

@@
 A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).
-	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVars{tp}$; hence, $\fctVars{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVars{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
+	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVarsPlus{tp}$; hence, $\fctVarsPlus{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
 	For any {\TPplus} $tp \!=\!
-(s,p,o)$ we define $\fctVars{tp} \!:=\!
-\bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVars{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
+(s,p,o)$ we define $\fctVarsPlus{tp} \!:=\!
+\bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
 
@@
 	, then $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, and $(P_1 \OpFILTER R)$ are {\SPARQLplus} expressions.
+	\item Let $P$ be a {\SPARQLplus} expression and $S \subset \symAllVariables$ be a finite set of variables, then $\OpSELECT_S(P)$ is a {\SPARQLplus} expression.
 \end{enumerate}
+
+\todo{introduce $\fctVarsPlus{P}$}
 
@@
 	\Omega_1 \LJoin \Omega_2 &:= \left( \Omega_1 \Join \Omega_2 \right) \cup \left( \Omega_1 \setminus \Omega_2 \right) \\
-	\sigma_R ( \Omega ) &:= \lbrace \eta \in \Omega \,|\, \eta \text{ satisfies } R \rbrace
+	\sigma_R ( \Omega ) &:= \lbrace \eta \in \Omega \,|\, \eta \text{ satisfies } R \rbrace \\
+	\pi_S ( \Omega ) &:= \lbrace \eta \,|\, \exists \, \eta' : \eta \cup \eta' \in \Omega \text{ and } \fctDom{\eta} \subseteq S \text{ and } \fctDom{\eta'} \cap S = \emptyset \rbrace
 \end{align*}
 
+\noindent
 %For a valuation $\eta$ and a {\TPplus} $tp$, we write $\eta[tp]$ to denote the {\TPplus} that we obtain by replacing the variables in $tp$ (including potentially embedded {\TPplus}s) according to $\eta$.
-Note, if $\fctVars{tp} \subseteq \fctDom{\eta}$, then $\eta[tp]$ is an {\RDFplusTriple}.
-
+Note, if $\fctVarsPlus{tp} \subseteq \fctDom{\eta}$, then $\eta[tp]$ is an {\RDFplusTriple}.
+%
 	%Let $P$ be a {\SPARQLplus} expression and let $G$ be an {\RDFplusGraph}. The \emph{evaluation of $P$ over $G$},
 	The \emph{evaluation} of {\SPARQLplus} expression $P$ over {\RDFplusGraph} $G$,
-denoted by $\fctEval{P}{G}$, is defined recursively as follows:
+denoted by $\fctEvalPlus{P}{G}$, is defined recursively as follows:
 \begin{enumerate}
@@
 		\begin{equation*}
-			\fctEval{P}{G} := \big\lbrace \eta \,\big|\,
-				\eta \text{ is a valuation with } \fctDom{\eta} = \fctVars{tp}
+			\fctEvalPlus{P}{G} := \big\lbrace \eta \,\big|\,
+				\eta \text{ is a valuation with } \fctDom{\eta} = \fctVarsPlus{tp}
 				\text{ and } \eta[tp] \in G \cup \fctTRefs{G}
@@
 		\end{equation*}
-		where $\eta[tp]$ denotes the {\TPplus} that we obtain by replacing the variables in $tp$ (including potentially embedded {\TPplus}s) according to $\eta$ (note, if $\fctVars{tp} \subseteq \fctDom{\eta}$, then $\eta[tp]$ is an {\RDFplusTriple}).
+		where $\eta[tp]$ denotes the {\TPplus} that we obtain by replacing the variables in $tp$ (including potentially embedded {\TPplus}s) according to $\eta$ (note, if $\fctVarsPlus{tp} \subseteq \fctDom{\eta}$, then $\eta[tp]$ is an {\RDFplusTriple}).
 		\vspace{1ex} %% Layout Adjustment
@@
 \todo{...}
+
+GOAL: for all $P$ that do not contain a subexpression of the form $(tp \OpAS ?v)$ for which $?v \in pVars(\fctEvalPlus{P}{G})$ it shall hold: $\fctEvalPlus{P}{G} = \fctEvalPlus{\fctDescent{P}}{\fctDescent{G}} = \fctEval{\fctDescent{P}}{\fctDescent{G}}$.
+Note, the set of possible variable $pVars\bigl(\fctEvalPlus{P}{G}\bigr)$ of a {\SPARQLplus} algebra expression $\fctEvalPlus{P}{G}$ is defined in the same way Schmidt et al.~define $pVars$ for SPARQL set algebra expressions~\cite{Schmidt10:FoundationsOfSPARQLOptimization}, we only extend the definition for our $\OpAS$ expression as follows: $pVars\bigl(\fctEvalPlus{(tp \OpAS ?v)}{G}\bigr) := \lbrace ?v \rbrace \cup \fctVarsPlus{tp}$.
+
+Let $P$ be a {\SPARQLplus} expression and let $V_\mathsf{new} \subseteq \symAllVariables \cap \fctVarsPlus{P}$.
+\todo{we need a mapping from all triple reference patterns in $P$ to $V_\mathsf{new}$ so that we can use the same var all the time}
+The \emph{RDF compatible expression} of {\SPARQLplus} expression $P$,
+denoted by $\fctDescent{P}^V$, is defined recursively as follows:
+\begin{enumerate}
+	\item If $P$ is a {\TPplus} $tp$, then $\fctDescent{P}^V$ is \todo{...}
+	\item If $P$ is $(tp \OpAS ?v)$, then $\fctDescent{P}^V$ is \todo{...}
+	\item If $P$ is $(P_1 \OpAND P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpAND P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
+	\item If $P$ is $(P_1 \OpUNION P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpUNION P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
+	\item If $P$ is $(P_1 \OpOPT P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpOPT P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
+	\item If $P$ is $(P_1 \OpFILTER R)$, then $\fctDescent{P}^V$ is $(P_1' \OpFILTER R)$ where $P_1'$ is $\fctDescent{P_1}^V$.
+	\item If $P$ is $\OpSELECT_S(P_1)$, then $\fctDescent{P}^V$ is $\OpSELECT_S(P_1')$ where $P_1'$ is $\fctDescent{P_1}^V$.
+\end{enumerate}

### 2012-06-02 paper-iswc-reification/intro.tex

\section{Introduction}
RDF Statements capturing knowledge about the world can be distinguished into two types. One the one hand hand, there are statements about real-world objects of a particular domain, representing domain knowledge (henceforth called \emph{domain data}). Then, there are also statements about statements, which in literatures, have been referred to using different synonymous concepts such as meta-level information, statement annotations or, just \emph{metadata}. The need for capturing metadata about statements arises in different scenarios. Commonly found is metadata associated with statements produced by data extraction programs, which captures the source from which the statements have been extracted, the extraction time, and the confidence degree of the program regarding these extraction outputs. Another use case is data security, where access rights are associated with statements to implement fine-grained access control policies at the \emph{statement-level}. Among many possible types of metadata, the three common types discussed in literatures are \emph{fuzzy} (e.g. degree of confidence, truth or trust), \emph{temporal} (e.g. creation date) and \emph{provenance} (e.g. source) metadata.

One popular mechanism extending the RDF standard for capturing metadata is \emph{named graphs}~\cite{DBLP:journals/ws/CarrollBHS05}. A named graph is an RDF graph, which is assigned
a name in the form of a URI reference. Given its URI reference, a named graph can be treated just like other RDF resources. In particular, the metadata of a graph can be captured as RDF triples in which the graph's URI appears as the subject. In principle, statement-level metadata can be captured using this mechanism as every statement can be named and act as a graph. However, this defies the original purpose of named graphs, which was introduced as a convenient way to associate the same metadata to several triples contained in one particular RDF graph. Using one graph for every statement is particularly problematic when querying RDF data. Using SPARQL, the standard query language for RDF, a query can be formulated and posed against the RDF dataset. The dataset is conceived as comprising of one graph, called the default graph, and a set of named graphs. Querying information in the named graphs require them to be mentioned explicitly in the \verb+FROM NAMED+ clause of the SPARQL query. This means querying metadata associated with named graphs representing single statements requires every such statement to be stated in \verb+FROM NAMED+ clause of the query.

Thus, while named graphs are widely used for graph-level metadata, the main mechanism for capturing statement-level metadata is still \emph{RDF reification}~\cite{Klyne04:RDFconcepts,Hayes04:RDFsemantics} (\emph{Reifi}). Its usage is illustrated in the following example:

\begin{example}
An RDF data graph about \verb+Alice+ and \verb+Bob+ is given in Turtle notation (prefix declarations omitted) as follows:

	\begin{footnotesize}%
	\begin{verbatim}
		 _:alice rdf:type foaf:Person ; foaf:name "Alice" ; 
		         foaf:mbox <mailto:alice@work> ; foaf:knows _:bob.
		 _:bob rdf:type foaf:Person ; foaf:name "Bob" ; foaf:knows _:alice ;
       foaf:mbox <mailto:bob@work> ; foaf:mbox <mailto:bob@home> .
	\end{verbatim}%
	\end{footnotesize}
In order to capture metadata about a particular statement $s$ using RDF reification, $s$ is reified; this means an URI is introduced to refer to $s$ as a statement, and an additional set of three triples are needed to captures the subject, the predicate and the object associated with $s$. For instance, provenance and temporal metadata for one of the above statement can be stated as 
  \begin{footnotesize}%
	\begin{verbatim}
	 _:s rdf:type rdf:Statement ; rdf:subject _:bob ; 
	     rdf:predicate foaf:mbox ; rdf:object <mailto:bob@home> ; 
	 	   dc:creator	<http://hr.example.com/infra/crawlers#we1> ;
			     dc:created "2011-04-05T12:00:00Z"^^xsd:dateTime ; 
			     dc:source <http://whatever.nu/profile/bob1975> .
	\end{verbatim}%
	\end{footnotesize}
\end{example}

Clearly, this example illustrates that using RDF reification requires a
quad for every triple to be reified, resulting in a five fold increase. Moreover, a large number of joins is needed when querying metadata captured this way:

\begin{example}
For instance, the query ``What is the source for Bob knows Alice?'' can be formulated as

\begin{footnotesize}%
	\begin{verbatim}
Select ?s where {
  ?z rdf:type rdf:Statement ; rdf:subject _:alice ;
     rdf:predicate foaf:knows ; rdf:object _:bob ; dc:source ?s. }

\end{verbatim}%
\end{footnotesize}
%?x foaf:name "Alice" . ?y foaf:name "Bob" .
%Combining the results for the first and the second triple patterns with results for the subsequent ones requires joining on $x$ and $y$. 
%Additionally, 
To process this query, results have to be retrieved for the triple patterns representing the subject, the object, the predicate and the source of $z$, and joined with triples representing $z$. This illustrates that retrieving metadata always involves a minimum number of three joins (on subject, predicate and object triples, respectively). 
\end{example}

Thus, Reifi not only leads to large additional overheads in terms of RDF data management due to the increased size of the data but also, has a negative effect on the efficiency of RDF query processing. In this work, we propose an efficient mechanism for RDF reification, called \emph{Reifi+}, which can avoid this five fold blowup of data and reduce the number of joins. Instead of using four additional triples for reification, Reifi+ only needs one particular URI, called \emph{triple reference}. For instance, information captured by the four triples specified above for the reified statements is represented in Reifi+ using the single URI \verb+_:bob foaf:mbox <mailto:bob@home>+ (note this URI directly encodes the information captured in the original triple). We propose extensions for the RDF and SPARQL standards to support this concept of triple reference. Also, we incorporate Reifi+ into two commercial RDF stores (Virtuoso, Bigdata), showing in experiments that compared to Reifi, this proposal results in substantial performance gain both in terms of RDF data management and SPARQL query processing: on average, Reifi+ reduces data size requirements by \todo{X percent} and improves response time by \todo{X percent}.

%-	Efficient management of meta-level statements 
%o	Avoids the 5x growth in data associated with RDF Reification
%o	Fast query answering
%-	Convenient syntax for data and queries
%o	Proposed extensions for SPARQL, Turtle
%-	Harmonized with RDF Reification
%o	Existing data and queries still work
%o	Extension to SPARQL Semantics and Algebra
%-	Can be combined with named graphs
%o	Both methods can be mixed in the same database.
%

\textbf{Outline.} We will start in Section 2 with the related work section where we provide a broader overview of works on RDF metadata beyond named graphs and RDF reification. The main idea behind Reifi+ and its main advantages over Reifi are discussed in Section 3. Then, we discuss how to extend RDF and SPARQL to incorporate this reification mechanism in Section 4 and 5, respectively. We present experimental results in Section 6 and conclude in Section 7.

### 2012-06-02 paper-iswc-reification/paper.tex

@@
 % \usepackage[ruled,vlined]{algorithm2e}
+\usepackage{color}  \definecolor{gray}{rgb}{.5,.5,.5}
+\usepackage{times}
 % \usepackage{graphicx}
@@
 % \usepackage{url}
-% \usepackage{color}
 % \usepackage[utf8]{inputenc}
+% \usepackage{paralist}
 %\usepackage{subfig}
@@
 % \usepackage{latexsym}
-% \usepackage{amsmath}
-% \usepackage{amssymb}
-\newcommand{\dtr}[1]{(\textbf{Thanh: #1})}
-%\newcommand{\todo}[1]{
-%\textbf{(todo: #1)}
-%}
 
-%\input{commands}
+\input{commands}
 
@@
 %\sloppy
-\title{Efficient Management of Meta-level Information for RDF}
+\title{Efficient Management of Reified Statements in RDF}
 
@@
 \begin{abstract}
+Metadata is commonly associated with RDF statements to capture provenance as well as quality related aspects.
+RDF reification is the standard mechanism to express this kind of information at the statement-level.
+In this work, we revisit the drawbacks of this mechanism.
+Specifically in the RDF data management and query processing context, we show that not only it results in a large number of triples but also, requires a large number of joins in queries asking for RDF statements' metadata.
+Addressing these problems, we propose a solution for reification that extends the current RDF and SPARQL standards.
+Based on two commercial RDF stores adoption of this solution, we show in experiments that compared to the original RDF reification proposal, it significantly improves the efficiency of RDF data management and SPARQL query processing.
 \end{abstract}
@@
 \input{related}
+\input{dis}
 \input{rep}
 \input{querying}
-\input{dis}
 \input{exp}

### 2012-06-02 trunk/paper-iswc-reification/related.tex

@@
-\section{Related Work}
-Overview of related work and their problems / reasons why not adopted in commercial solutions, e.g. 
-Reification
-Reification builds a model of a statement:
-_:s1 rdf:subject   :SAP .
-_:s1 rdf:predicate :bought .
-_:s1 rdf:object    :sybase .
-_:s1 rdf:type      rdf:Statement .
-_:s1 dc:source     reuters:us-sybase .
+\section{Related Work} Many proposals for extending Semantic Web standards to support different metadata scenarios exist.
 
--	Has a very bad reputation
--	Extremely inefficient 
--	5x the data on disk when you reify statements.
--	Awkward syntax
--	Cognitively challenging to write queries against reified data
--	Rarely used.
-Other approaches to be discussed:
--	Bernhard Schueler, Sergej Sizov, Steffen Staab, Duc Thanh Tran: Querying for meta knowledge. WWW 2008:625-634
--	Thanh Tran, Peter Haase, Boris Motik, Bernardo Cuenca Grau, Ian Horrocks: Metalevel Information in Ontology-Based Applications. AAAI 2008:1237-1242
--	Nuno Lopes, Axel Polleres, Umberto Straccia, Antoine Zimmermann: AnQL: SPARQLing Up Annotated RDFS. International Semantic Web Conference 2010:518-533
--	Antoine Zimmermann, Nuno Lopes, Axel Polleres, Umberto Straccia: A general framework for representing, reasoning and querying with annotated Semantic Web data. J. Web Sem. 11: 72-95 (2012)
--	Umberto Straccia, Nuno Lopes, Gergely Lukacsy, Axel Polleres: A General Framework for Representing and Reasoning with Annotated Semantic Web Data. AAAI 2010
--	Jeremy J. Carroll, Christian Bizer, Patrick J. Hayes, Patrick Stickler: Named graphs. J. Web Sem. (WS) 3(4):247-267 (2005)
--	Paula Severi, José Luiz Fiadeiro, David Ekserdjian: Guiding Reification in OWL through Aggregation. Description Logics 2010
--	Nicole Alexander, Siva Ravada: RDF Object Type and Reification in the Database. ICDE 2006:93
-Solution & Contributions
--	Efficient management of meta-level statements 
-o	Avoids the 5x growth in data associated with RDF Reification
-o	Fast query answering
--	Convenient syntax for data and queries
-o	Proposed extensions for SPARQL, Turtle
--	Harmonized with RDF Reification
-o	Existing data and queries still work
-o	Extension to SPARQL Semantics and Algebra
--	Can be combined with named graphs
-o	Both methods can be mixed in the same database.
+For data captured in OWL ontologies, a strict separation of domain data and metadata at the level of semantics has been proposed~\cite{DBLP:conf/aaai/TranHMGH08}.
+Interpreting these two types of data together can lead to undesirable effects on the semantics and in particular, introduce large overhead in reasoning and answering queries that involve both types of data.
+Based on the observation that these two types have distinct universes of discourses, it has been proposed to represent metadata as axiom annotations, ontology elements akin to comments that do not affect the semantics of domain data.
+Semantics is then given to metadata by translating it to a metaview, an ontology capturing the semantics of metadata that is interpreted independently from the ontology about domain data.
+
+Several extensions have also been proposed for RDF to support some specific types of metadata.
+Using Fuzzy RDF~\cite{DBLP:conf/rr/Straccia09} for instance, a degree of truth can be assigned to RDF triples such as \verb+(_:bob foaf:mbox <mailto:bob@home>):0.9+.
+Further works in this direction~\cite{swap2004,DBLP:conf/semweb/MazzieriD05} focus on the semantics of metadata, basically answering the question of what it means to have triples associated with some truth values and how to use them for reasoning by the deductive system.
+For dealing with temporal metadata, Temporal RDF as been proposed, which is equipped with semantics and a deductive system that can be reduced to the standard semantics of and inferences over RDF graphs~\cite{DBLP:journals/tkde/GutierrezHV07}.
+
+There are also several extensions to SPARQL for querying metadata.
+Hartig proposes tSPARQL for querying trust values of results that can be found for graph patterns specified in SPARQL queries~\cite{DBLP:conf/esws/Hartig09}.
+Besides extensions (such as tSPARQL) that introduce specific SPARQL constructors to access a particular type of metadata, there exists also a framework for querying metadata that generalizes over the many possible types of metadata~\cite{DBLP:conf/www/SchuelerSST08}.
+It defines a \verb+WITH META+ clause that can be used in SPARQL queries to specify the graphs for which metadata shall be retrieved.
+Since different types of metadata might be associated with such graphs, this framework enables querying over metadata in a generic fashion.
+
+Generalizing over RDF and SPARQL extensions that address a particular type of metadata, a general framework for representing, querying and reasoning with metadata has been proposed recently~\cite{DBLP:journals/ws/ZimmermannLPS12}.
+As in previous works such as Fuzzy RDF, it uses an abstract syntax for representing metadata: a triple annotated with metadata is represented as $\tau: \lambda$ where $\tau$ is a triple and $\lambda$ is an annotation value.
+The RDFS semantics is then extended to provide a deductive system for
+this kind of annotated triples, called the Annotated RDFS semantics.
+In order to accommodate for the different possible semantics of annotation values, e.g.
+temporal, fuzzy or provenance annotation values, a general structure based on semiring is used as the interpretation domain.
+Finally, AnQL~\cite{DBLP:conf/semweb/LopesPSZ10} is introduced as an SPARQL extension for querying metadata.
+Similar to the abstract syntax for annotated triples, an AnQL query is constructed based on annotated triple patterns of the form  $\eta : \pi$ where $\eta$ is a triple pattern and $\pi$ is either an annotation value or an annotation variable.
+
+These previous works are focused on the semantics of metadata, providing corresponding extensions to the RDF(S) semantics to enable reasoning and querying over different types of metadata.
+However, they do not directly address the problem of representing metadata in RDF.
+In fact, RDF reification and named graphs are still the main mechanisms that underly these approaches.
+For instance, Fuzzy RDF statements represented in the abstract syntax, e.g.
+\verb+(_:bob foaf:mbox <mailto:bob@home>):0.9+, are translated into RDF triples by using RDF reification~\cite{swap2004}.
+Metadata used in the querying framework discussed before are assumed to be represented as named graphs~\cite{DBLP:conf/www/SchuelerSST08}.
+Orthogonal to existing works on the semantics of metadata, we provide an efficient RDF reification mechanism.
+The SPARQL extension that goes along with it is specifically needed to query metadata captured by this mechanism.
+It can be used as the basis for supporting the more specific query semantics as proposed for different types of metadata.

### 2012-06-03 paper-iswc-reification/querying.tex
first draft of the section that defines the conversion from SPARQL* to ordinary SPARQL

@@
 	, then $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, and $(P_1 \OpFILTER R)$ are {\SPARQLplus} expressions.
-	\item Let $P$ be a {\SPARQLplus} expression and $S \subset \symAllVariables$ be a finite set of variables, then $\OpSELECT_S(P)$ is a {\SPARQLplus} expression.
+% 	\item Let $P$ be a {\SPARQLplus} expression and $S \subset \symAllVariables$ be a finite set of variables, then $\OpSELECT_S(P)$ is a {\SPARQLplus} expression.
 \end{enumerate}
 
-\todo{introduce $\fctVarsPlus{P}$}
+\begin{note}
+		We note that any
+		%Any
+	(ordinary) SPARQL expression is a {\SPARQLplus} expression.
+\end{note}
+
+\todo{introduce $\fctVarsPlus{P}$ and $\fctTRefs{P}$ ...}
+
+	\begin{tabular}{|c||c|c|} \hline
+		{\SPARQLplus} expression $P$ &
+		$\fctVarsPlus{P}$ &
+		$\fctTRefs{P}$
+		\\ \hline
+		\hline
+% 		{\TPplus} $(s,p,o)$ &
+% 		$\bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$ &
+% 		$\bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$
+% 		\\ \hline
+		$(tp \OpAS ?v)$ &
+		$\fctVarsPlus{tp} \cup \lbrace ?v \rbrace$ &
+		$\fctTRefs{tp} \cup \lbrace tp \rbrace$
+		\\ \hline
+		$(P_1 \OpAND P_2)$ &
+		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
+		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
+		\\ \hline
+		$(P_1 \OpOPT P_2)$ &
+		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
+		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
+		\\ \hline
+		$(P_1 \OpUNION P_2)$ &
+		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
+		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
+		\\ \hline
+		$(P' \OpFILTER R)$ &
+		$\fctVarsPlus{P'} \cup \fctVars{R}$ &
+		$\fctTRefs{P'}$
+		\\ \hline
+% 		$\OpSELECT_S(P')$ &
+% 		$\fctVarsPlus{P'} \cup S$ &
+% 		$\fctTRefs{P'}$
+% 		\\ \hline
+	\end{tabular}
 
@@
 
-Let $\Omega_1$, $\Omega_2$ and $\Omega$ be sets of valuations; let $R$ be a filter condition; and let $S \subset \symAllVariables$ be a finite set of variables.
-The algebra operators \emph{join}, \emph{union}, \emph{difference}, \emph{left outer-join}, \emph{selection}, and \emph{projection} are defined as follows:
+Let $\Omega_1$, $\Omega_2$ and $\Omega$ be sets of
+	%valuations; let
+	valuations and let
+$R$ be a filter condition%
+	%; and let $S \subset \symAllVariables$ be a finite set of variables.
+	.
+The algebra operators \emph{join}, \emph{union}, \emph{difference}, \emph{left outer-join},
+	%\emph{selection}, and \emph{projection}
+	and \emph{selection}
+are defined as follows:
 \begin{align*}
-	\Omega_1 \Join \Omega_2 & := \lbrace \eta_1 \cup \eta_1 \,|\, \eta_1 \in \Omega_1 \text{ and } \eta_2 \in \Omega_2 \text{ and } \eta_1 \sim \eta_2 \rbrace \\
-	\Omega_2 \cup \Omega_2 & := \lbrace \eta \,|\, \eta \in \Omega_1 \text{ or } \eta \in \Omega_2 \rbrace \\
-	\Omega_1 \setminus \Omega_2 & := \lbrace \eta_1 \in \Omega_1 \,|\, \forall \eta_2 \in \Omega_2 : \eta_1 \not\sim \eta_2 \rbrace \\
-	\Omega_1 \LJoin \Omega_2 &:= \left( \Omega_1 \Join \Omega_2 \right) \cup \left( \Omega_1 \setminus \Omega_2 \right) \\
-	\sigma_R ( \Omega ) &:= \lbrace \eta \in \Omega \,|\, \eta \text{ satisfies } R \rbrace \\
-	\pi_S ( \Omega ) &:= \lbrace \eta \,|\, \exists \, \eta' : \eta \cup \eta' \in \Omega \text{ and } \fctDom{\eta} \subseteq S \text{ and } \fctDom{\eta'} \cap S = \emptyset \rbrace
+	\Omega_1 \Join \Omega_2 & := \lbrace \eta_1 \cup \eta_1 \,|\, \eta_1 \in \Omega_1 \text{ and } \eta_2 \in \Omega_2 \text{ and } \eta_1 \sim \eta_2 \rbrace
+	\\
+	\Omega_2 \cup \Omega_2 & := \lbrace \eta \,|\, \eta \in \Omega_1 \text{ or } \eta \in \Omega_2 \rbrace
+	\\
+	\Omega_1 \setminus \Omega_2 & := \lbrace \eta_1 \in \Omega_1 \,|\, \forall \eta_2 \in \Omega_2 : \eta_1 \not\sim \eta_2 \rbrace
+	\\
+	\Omega_1 \LJoin \Omega_2 &:= \left( \Omega_1 \Join \Omega_2 \right) \cup \left( \Omega_1 \setminus \Omega_2 \right)
+	\\
+	\sigma_R ( \Omega ) &:= \lbrace \eta \in \Omega \,|\, \eta \text{ satisfies } R \rbrace
+% 	\\
+% 	\pi_S ( \Omega ) &:= \lbrace \eta \,|\, \exists \, \eta' : \eta \cup \eta' \in \Omega \text{ and } \fctDom{\eta} \subseteq S \text{ and } \fctDom{\eta'} \cap S = \emptyset \rbrace
 \end{align*}
@@
 	\item If $P$ is $(P' \OpFILTER R)$, then $\fctEvalPlus{P}{G} := \sigma_R\bigl( \fctEvalPlus{P'}{G} \bigr)$.
-	\item If $P$ is $\OpSELECT_S(P')$, then $\fctEvalPlus{P}{G} := \pi_S\bigl( \fctEvalPlus{P'}{G} \bigr)$.
+% 	\item If $P$ is $\OpSELECT_S(P')$, then $\fctEvalPlus{P}{G} := \pi_S\bigl( \fctEvalPlus{P'}{G} \bigr)$.
 \end{enumerate}
-Each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.
+
+\noindent
+\removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
+
+The following result shows that the query semantics introduced in this section is fully compatible to the usual SPARQL semantics (as defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus}
+	and {\SPARQLplus}
+may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.
+
+\begin{proposition} \label{Proposition:EquivalenceOfSemantics}
+	For any (ordinary) RDF graph $G$ and any (ordinary) SPARQL expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEval{P}{G}$.
+\end{proposition}
+
+\todo{...}
 
@@
 
-\todo{...}
+Let $P$ be a {\SPARQLplus} expression.
+We assume an \removable{(arbitrary)} injective function $v : \fctTRefs{P} \rightarrow \symAllVariables \cap \fctVarsPlus{P}$.
+Furthermore, we introduce another injective function $w : (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals) \rightarrow (\symAllVariables \cup \symAllURIs \cup \symAllLiterals)$ that is defined as follows: Let $x \in (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals)$.
+If $x \in \fctTRefs{P}$, then $w(x) := v(x)$; if $v \notin \fctTRefs{P}$, then $w(x) := x$.
+%
+Using $w$, for any $rp = (s,p,o) \in \fctTRefs{P}$ we write $\mathrm{reif}^w( rp )$ to denote
+	the SPARQL expression $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
+	%following SPARQL expression: \begin{align*}
+	%	\Bigl( \Bigl( \,\, \Bigl( & \bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr) \OpAND \bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr) \Bigr) \OpAND \\
+	%	& \bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr) \Bigr) \OpAND \bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr) \Bigr)
+	%\end{align*}
 
-GOAL: for all $P$ that do not contain a subexpression of the form $(tp \OpAS ?v)$ for which $?v \in pVars(\fctEvalPlus{P}{G})$ it shall hold: $\fctEvalPlus{P}{G} = \fctEvalPlus{\fctDescent{P}}{\fctDescent{G}} = \fctEval{\fctDescent{P}}{\fctDescent{G}}$.
-Note, the set of possible variable $pVars\bigl(\fctEvalPlus{P}{G}\bigr)$ of a {\SPARQLplus} algebra expression $\fctEvalPlus{P}{G}$ is defined in the same way Schmidt et al.~define $pVars$ for SPARQL set algebra expressions~\cite{Schmidt10:FoundationsOfSPARQLOptimization}, we only extend the definition for our $\OpAS$ expression as follows: $pVars\bigl(\fctEvalPlus{(tp \OpAS ?v)}{G}\bigr) := \lbrace ?v \rbrace \cup \fctVarsPlus{tp}$.
+The \emph{$w$-based, RDF compatible expression} of $P$, denoted by $\fctDescent{P}^{w}$, is defined recursively as follows:
+\begin{enumerate}
+	\item If $P$ is a {\TPplus} $(s,p,o)$, and:
+		\begin{enumerate}
+			\item if $s \notin \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescent{P}^w$ is $(s,p,o)$; or
+			\item if $s \in \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescent{P}^w$ is $\bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND (s'\!,p,o) \bigr)$; or
+			\item if $s \notin \symAllTPs$ and $o \in \symAllTPs$, then $\fctDescent{P}^w$ is $\bigl( \bigl( P_{o1} \OpAND P_{o2} \bigr) \OpAND (s,p,o') \bigr)$; or
+			\item else $\fctDescent{P}^w$ is $\bigl( \bigl( \bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND P_{o1} \bigr) \OpAND P_{o2} \bigr) \OpAND (s'\!,p,o') \bigr)$;
+		\end{enumerate}
+		where $s'$ is $w(s)$, $o'$ is $w(o)$, $P_{s1}$ is $\mathrm{reif}^w(s)$, $P_{s2}$ is $\fctDescent{s}^w$, $P_{o1}$ is $\mathrm{reif}^w(o)$, and $P_{o2}$ is $\fctDescent{o}^w$.
+		\vspace{1ex}
 
-Let $P$ be a {\SPARQLplus} expression and let $V_\mathsf{new} \subseteq \symAllVariables \cap \fctVarsPlus{P}$.
-\todo{we need a mapping from all triple reference patterns in $P$ to $V_\mathsf{new}$ so that we can use the same var all the time}
-The \emph{RDF compatible expression} of {\SPARQLplus} expression $P$,
-denoted by $\fctDescent{P}^V$, is defined recursively as follows:
-\begin{enumerate}
-	\item If $P$ is a {\TPplus} $tp$, then $\fctDescent{P}^V$ is \todo{...}
-	\item If $P$ is $(tp \OpAS ?v)$, then $\fctDescent{P}^V$ is \todo{...}
-	\item If $P$ is $(P_1 \OpAND P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpAND P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
-	\item If $P$ is $(P_1 \OpUNION P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpUNION P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
-	\item If $P$ is $(P_1 \OpOPT P_2)$, then $\fctDescent{P}^V$ is $(P_1' \OpOPT P_2')$ where $P_1'$ is $\fctDescent{P_1}^V$ and $P_2'$ is $\fctDescent{P_2}^V$.
-	\item If $P$ is $(P_1 \OpFILTER R)$, then $\fctDescent{P}^V$ is $(P_1' \OpFILTER R)$ where $P_1'$ is $\fctDescent{P_1}^V$.
-	\item If $P$ is $\OpSELECT_S(P_1)$, then $\fctDescent{P}^V$ is $\OpSELECT_S(P_1')$ where $P_1'$ is $\fctDescent{P_1}^V$.
+	\item If $P$ is
+			%$(tp \OpAS ?v)$ with $tp = (s,p,o)$,
+			$\bigl( (s,p,o) \OpAS ?v \bigr)$,
+		then $\fctDescent{P}^w$ is $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
+
+% 	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, $(P_1 \OpFILTER R)$, or $\OpSELECT_S(P_1)$, then $\fctDescent{P}^w$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, $(P_1' \OpFILTER R)$, and $\OpSELECT_S(P_1')$, respectively; where $P_1'$ is $\fctDescent{P_1}^w$ and $P_2'$ is $\fctDescent{P_2}^w$.
+
+		\vspace{1ex}
+	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, or $(P_1 \OpFILTER R)$, then $\fctDescent{P}^w$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, and $(P_1' \OpFILTER R)$, respectively; where $P_1'$ is $\fctDescent{P_1}^w$ and $P_2'$ is $\fctDescent{P_2}^w$.
+
+% 	\begin{tabular}{|c||c||c||c||c||c|} \hline
+% 		$\boldsymbol{P}$ &
+% 		$(P_1 \OpAND P_2)$ &
+% 		$(P_1 \OpOPT P_2)$ &
+% 		$(P_1 \OpUNION P_2)$ &
+% 		$(P_1 \OpFILTER R)$ &
+% 		$\OpSELECT_S(P_1)$
+% 		\\ \hline
+% 		$\boldsymbol{ \fctDescent{P}^w}$ &
+% 		$(P_1' \OpAND P_2')$ &
+% 		$(P_1' \OpOPT P_2')$ &
+% 		$(P_1' \OpUNION P_2')$ &
+% 		$(P_1' \OpFILTER R)$ &
+% 		$\OpSELECT_S(P_1')$
+% 		\\ \hline
+% 	\end{tabular}
+%
+% 	\begin{center}
+% 	\begin{tabular}{|c|c|} \hline
+% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescent{P}^w}$ \\ \hline \hline
+% 		$(P_1 \OpAND P_2)$ & $(P_1' \OpAND P_2')$ \\ \hline
+% 		$(P_1 \OpOPT P_2)$ & $(P_1' \OpOPT P_2')$ \\ \hline
+% 	\end{tabular}
+% 	\hspace{10mm}
+% 	\begin{tabular}{|c|c|} \hline
+% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescent{P}^w}$ \\ \hline \hline
+% 		$(P_1 \OpUNION P_2)$ & $(P_1' \OpUNION P_2')$ \\ \hline
+% 		$(P_1 \OpFILTER R)$ & $(P_1' \OpFILTER R)$ \\ \hline
+% 	\end{tabular}
+% 	\end{center}
 \end{enumerate}
+
+\begin{proposition} \label{Proposition:EquivalenceOfSyntaxAfterConverting}
+	For any {\SPARQLplus} expression $P$ any RDF compatible expression of $P$ is an (ordinary) SPARQL expression.
+\end{proposition}
+
+\noindent
+To show a (semantic) equivalence between {\SPARQLplus} expressions and the corresponding SPARQL expressions we need an additional algebra operator to project out (bindings for) query variables that the conversion introduces.
+We define \emph{projection} as follows: Let $\Omega$ be a set of valuations and let $S \subset \symAllVariables$ be a finite set of variables, then $\pi_S ( \Omega ) := \lbrace \eta \,|\, \exists \, \eta' : \eta \cup \eta' \in \Omega \text{ and } \fctDom{\eta} \subseteq S \text{ and } \fctDom{\eta'} \cap S = \emptyset \rbrace$.
+Using projection we may now show the following equivalence:
+
+\begin{proposition} \label{Proposition:QueryEquivalenceAfterConverting}
+	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ that does not contain a sub-expression
+		\removable{of the form}
+	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEvalPlus{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescent{P}^w$ of $P$.
+\end{proposition}
+
+\noindent
+The following result is a direct consequence of Propositions~\ref{Proposition:EquivalenceOfSemantics}, \ref{Proposition:EquivalenceOfSyntaxAfterConverting}, and~\ref{Proposition:QueryEquivalenceAfterConverting}:
+\begin{corollary}
+	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ that does not contain a sub-expression
+		\removable{of the form}
+	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEval{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescent{P}^w$ of $P$.
+\end{corollary}
+
+\noindent
+\todo{briefly discuss the Corollary}

### 2012-06-04 paper-iswc-reification/abstract.tex
improved Abstract a bit

--- 2012-06-02 trunk/paper-iswc-reification/abstract.tex
@@
 To address these problems we propose a solution for reification that extends the current RDF and SPARQL standards.
-Based on two commercial RDF stores' adoption of this solution, we show in experiments that our proposal significantly improves the efficiency of RDF data management and SPARQL query processing, compared to the original RDF reification proposal.
+Based on two commercial RDF stores' adoption of this solution, we show in experiments that --compared to original RDF reification-- our proposal significantly improves the efficiency of RDF data management and SPARQL query processing.

### 2012-06-04 trunk/paper-iswc-reification/intro.tex
added macros for Reifi and Reifi*

@@
 \section{Introduction}
-Motivation
-\begin{itemize}
-	\item 
-Necessary in several domains
-\item	Entity link extraction (confidence values)
-\item	Graph databases (link attributes)
-\item	Intelligence analysis (provenance on assertions)
-\item	Statement level security
-\end{itemize}
+RDF Statements capturing knowledge about the world can be distinguished into two types.
+One the one hand hand, there are statements about real-world objects of a particular domain, representing domain knowledge (henceforth called \emph{domain data}).
+Then, there are also statements about statements, which in literatures, have been referred to using different synonymous concepts such as meta-level information, statement annotations or, just \emph{metadata}.
+The need for capturing metadata about statements arises in different scenarios.
+Commonly found is metadata associated with statements produced by data extraction programs, which captures the source from which the statements have been extracted, the extraction time, and the confidence degree of the program regarding these extraction outputs.
+Another use case is data security, where access rights are associated with statements to implement fine-grained access control policies at the \emph{statement-level}.
+Among many possible types of metadata, the three common types discussed in literatures are \emph{fuzzy} (e.g.
+degree of confidence, truth or trust), \emph{temporal} (e.g.
+creation date) and \emph{provenance} (e.g.
+source) metadata.
+
+One popular mechanism extending the RDF standard for capturing metadata is \emph{named graphs}~\cite{DBLP:journals/ws/CarrollBHS05}. A named graph is an RDF graph, which is assigned
+a name in the form of a URI reference.
+Given its URI reference, a named graph can be treated just like other RDF resources.
+In particular, the metadata of a graph can be captured as RDF triples in which the graph's URI appears as the subject.
+In principle, statement-level metadata can be captured using this mechanism as every statement can be named and act as a graph.
+However, this defies the original purpose of named graphs, which was introduced as a convenient way to associate the same metadata to several triples contained in one particular RDF graph.
+Using one graph for every statement is particularly problematic when querying RDF data.
+Using SPARQL, the standard query language for RDF, a query can be formulated and posed against the RDF dataset.
+The dataset is conceived as comprising of one graph, called the default graph, and a set of named graphs.
+Querying information in the named graphs require them to be mentioned explicitly in the \verb+FROM NAMED+ clause of the SPARQL query.
+This means querying metadata associated with named graphs representing single statements requires every such statement to be stated in \verb+FROM NAMED+ clause of the query.
+
+Thus, while named graphs are widely used for graph-level metadata, the main mechanism for capturing statement-level metadata is still \emph{RDF reification}~\cite{Klyne04:RDFconcepts,Hayes04:RDFsemantics} (\emph{\Reifi}).
+Its usage is illustrated in the following example:
+
+\begin{example}
+An RDF data graph about \verb+Alice+ and \verb+Bob+ is given in Turtle notation (prefix declarations omitted) as follows:
+
+	\begin{footnotesize}%
+	\begin{verbatim}
+		 _:alice rdf:type foaf:Person ; foaf:name "Alice" ; 
+		         foaf:mbox <mailto:alice@work> ; foaf:knows _:bob.
+		 _:bob rdf:type foaf:Person ; foaf:name "Bob" ; foaf:knows _:alice ;
+       foaf:mbox <mailto:bob@work> ; foaf:mbox <mailto:bob@home> .
+	\end{verbatim}%
+	\end{footnotesize}
+In order to capture metadata about a particular statement $s$ using RDF reification, $s$ is reified; this means an URI is introduced to refer to $s$ as a statement, and an additional set of three triples are needed to captures the subject, the predicate and the object associated with $s$.
+For instance, provenance and temporal metadata for one of the above statement can be stated as
+  \begin{footnotesize}%
+	\begin{verbatim}
+	 _:s rdf:type rdf:Statement ; rdf:subject _:bob ; 
+	     rdf:predicate foaf:mbox ; rdf:object <mailto:bob@home> ; 
+	 	   dc:creator	<http://hr.example.com/infra/crawlers#we1> ;
+			     dc:created "2011-04-05T12:00:00Z"^^xsd:dateTime ; 
+			     dc:source <http://whatever.nu/profile/bob1975> .
+	\end{verbatim}%
+	\end{footnotesize}
+\end{example}
+
+Clearly, this example illustrates that using RDF reification requires a
+quad for every triple to be reified, resulting in a five fold increase. Moreover, a large number of joins is needed when querying metadata captured this way:
+
+\begin{example}
+For instance, the query ``What is the source for Bob knows Alice?'' can be formulated as
+
+\begin{footnotesize}%
+	\begin{verbatim}
+Select ?s where {
+  ?z rdf:type rdf:Statement ; rdf:subject _:alice ;
+     rdf:predicate foaf:knows ; rdf:object _:bob ; dc:source ?s. }
+
+\end{verbatim}%
+\end{footnotesize}
+%?x foaf:name "Alice" . ?y foaf:name "Bob" .
+%Combining the results for the first and the second triple patterns with results for the subsequent ones requires joining on $x$ and $y$. 
+%Additionally, 
+To process this query, results have to be retrieved for the triple patterns representing the subject, the object, the predicate and the source of $z$, and joined with triples representing $z$.
+This illustrates that retrieving metadata always involves a minimum number of three joins (on subject, predicate and object triples, respectively).
+\end{example}
+
+Thus, {\Reifi} not only leads to large additional overheads in terms of RDF data management due to the increased size of the data but also, has a negative effect on the efficiency of RDF query processing.
+In this work, we propose an efficient mechanism for RDF reification, called \emph{\ReifiPlus}, which can avoid this five fold blowup of data and reduce the number of joins.
+Instead of using four additional triples for reification, {\ReifiPlus} only needs one particular URI, called \emph{triple reference}.
+For instance, information captured by the four triples specified above for the reified statements is represented in {\ReifiPlus} using the single URI \verb+_:bob foaf:mbox <mailto:bob@home>+ (note this URI directly encodes the information captured in the original triple).
+We propose extensions for the RDF and SPARQL standards to support this concept of triple reference.
+Also, we incorporate {\ReifiPlus} into two commercial RDF stores (Virtuoso, Bigdata), showing in experiments that compared to {\Reifi}, this proposal results in substantial performance gain both in terms of RDF data management and SPARQL query processing: on average, {\ReifiPlus} reduces data size requirements by \todo{X percent} and improves response time by \todo{X percent}.
+
+%-	Efficient management of meta-level statements 
+%o	Avoids the 5x growth in data associated with RDF Reification
+%o	Fast query answering
+%-	Convenient syntax for data and queries
+%o	Proposed extensions for SPARQL, Turtle
+%-	Harmonized with RDF Reification
+%o	Existing data and queries still work
+%o	Extension to SPARQL Semantics and Algebra
+%-	Can be combined with named graphs
+%o	Both methods can be mixed in the same database.
+%
+
+\textbf{Outline.} We will start in Section 2 with the related work section where we provide a broader overview of works on RDF metadata beyond named graphs and RDF reification.
+The main idea behind {\ReifiPlus} and its main advantages over {\Reifi} are discussed in Section 3.
+Then, we discuss how to extend RDF and SPARQL to incorporate this reification mechanism in Section 4 and 5, respectively.
+We present experimental results in Section 6 and conclude in Section 7.

### 2012-06-04 paper-iswc-reification/intro.tex
some small changes in the intro

@@
 \section{Introduction}
-RDF Statements capturing knowledge about the world can be distinguished into two types.
-One the one hand hand, there are statements about real-world objects of a particular domain, representing domain knowledge (henceforth called \emph{domain data}).
-Then, there are also statements about statements, which in literatures, have been referred to using different synonymous concepts such as meta-level information, statement annotations or, just \emph{metadata}.
+RDF statements capturing knowledge about the world can be distinguished into two types: On the one hand, there are statements about objects of a particular domain, representing domain knowledge (henceforth called \emph{domain data}).
+Then, there are also statements about statements, which in the  literature, have been referred to using different synonymous concepts such as meta-level information, statement annotations, or \emph{metadata}.
 The need for capturing metadata about statements arises in different scenarios.
@@
 Another use case is data security, where access rights are associated with statements to implement fine-grained access control policies at the \emph{statement-level}.
-Among many possible types of metadata, the three common types discussed in literatures are \emph{fuzzy} (e.g.
-degree of confidence, truth or trust), \emph{temporal} (e.g.
-creation date) and \emph{provenance} (e.g.
-source) metadata.
+Among many possible types of metadata, the three common types discussed in the literature are \emph{fuzzy} (e.g.~degree of confidence, truth or trust), \emph{temporal} (e.g.~creation date) and \emph{provenance} (e.g.~source) metadata.
+\marginpar{Remark: I'm not sure about the last sentence.
+First, where does this classification into three types comes from?
+Then, why is confidence, truth or trust classified as ``fuzzy''?
+And, why does 'creation date' not belong to the class ``provenance''?}
 
-One popular mechanism extending the RDF standard for capturing metadata is \emph{named graphs}~\cite{DBLP:journals/ws/CarrollBHS05}. A named graph is an RDF graph, which is assigned
+A popular mechanism that extends the RDF standard for capturing metadata is \emph{named graphs}~\cite{DBLP:journals/ws/CarrollBHS05}. A named graph is an RDF graph, which is assigned
 a name in the form of a URI reference.
 Given its URI reference, a named graph can be treated just like other RDF resources.
-In particular, the metadata of a graph can be captured as RDF triples in which the graph's URI appears as the subject.
-In principle, statement-level metadata can be captured using this mechanism as every statement can be named and act as a graph.
+In particular, metadata about such a graph may be captured as RDF triples in which the graph URI appears as the subject.
+In principle, statement-level metadata may be represented using this mechanism as every statement may be wrapped in a dedicated named graph.
 However, this defies the original purpose of named graphs, which was introduced as a convenient way to associate the same metadata to several triples contained in one particular RDF graph.
-Using one graph for every statement is particularly problematic when querying RDF data.
-Using SPARQL, the standard query language for RDF, a query can be formulated and posed against the RDF dataset.
+Using a graph for every statement is particularly problematic when querying RDF data.
+Using SPARQL, the standard query language for RDF, a query can be formulated and posed against an RDF dataset.
 The dataset is conceived as comprising of one graph, called the default graph, and a set of named graphs.
-Querying information in the named graphs require them to be mentioned explicitly in the \verb+FROM NAMED+ clause of the SPARQL query.
-This means querying metadata associated with named graphs representing single statements requires every such statement to be stated in \verb+FROM NAMED+ clause of the query.
+Querying information in these named graphs require them to be mentioned explicitly in a \verb+FROM NAMED+ clause of SPARQL queries.
+This means querying metadata associated with named graphs representing single statements, requires referring to each such statement via a \verb+FROM NAMED+ clause in the query.
 
-Thus, while named graphs are widely used for graph-level metadata, the main mechanism for capturing statement-level metadata is still \emph{RDF reification}~\cite{Klyne04:RDFconcepts,Hayes04:RDFsemantics} (\emph{Reifi}).
-Its usage is illustrated in the following example:
+Thus, while named graphs are widely used for graph-level metadata, the main mechanism for capturing statement-level metadata is still \emph{RDF reification}~\cite{Klyne04:RDFconcepts,Hayes04:RDFsemantics} (hereafter abbreviated by \emph{\Reifi}).
+The following example illustrated the usage of {\Reifi}:
 
 \begin{example}
-An RDF data graph about \verb+Alice+ and \verb+Bob+ is given in Turtle notation (prefix declarations omitted) as follows:
-
+Assume the following RDF data about Alice and Bob%
+\footnote{We use Turtle notation for presenting RDF data in examples. Furthermore, we omit prefix declarations; instead, we use the usual prefixes as can be found via the http://prefix.cc service.}%
+:
 	\begin{footnotesize}%
@@
 		 _:alice rdf:type foaf:Person ; foaf:name "Alice" ; 
-		         foaf:mbox <mailto:alice@work> ; foaf:knows _:bob.
-		 _:bob rdf:type foaf:Person ; foaf:name "Bob" ; foaf:knows _:alice ;
-       foaf:mbox <mailto:bob@work> ; foaf:mbox <mailto:bob@home> .
+		         foaf:mbox <mailto:alice@work> ; foaf:knows _:bob .
+		 _:bob rdf:type foaf:Person ; foaf:name "Bob" ;
+		       foaf:knows _:alice ; foaf:mbox <mailto:bob@home> .
 	\end{verbatim}%
 	\end{footnotesize}
-In order to capture metadata about a particular statement $s$ using RDF reification, $s$ is reified; this means an URI is introduced to refer to $s$ as a statement, and an additional set of three triples are needed to captures the subject, the predicate and the object associated with $s$.
-For instance, provenance and temporal metadata for one of the above statement can be stated as
+
+\todo{Rewrite this example (i.e. remove the first part) if we don't need the example data (so far it doesn't seem we do).}
+
+\noindent
+In order to capture metadata about a particular statement $s$ using RDF reification, $s$ is reified; this means a URI (or a blank node) is introduced to refer to $s$ as a statement, and an additional set of three triples are needed to captures the subject, the predicate and the object associated with $s$.
+For instance, provenance and temporal metadata for the last triple of our example data can be stated as
   \begin{footnotesize}%
@@
 
+\marginpar{What means ``a quad'' here?}
+
 Clearly, this example illustrates that using RDF reification requires a
@@
 \begin{example}
-For instance, the query ``What is the source for Bob knows Alice?'' can be formulated as
+For instance, the question ``What is the source for the triple that claims Bob knows Alice?'' can be formulated as the following SPARQL query:
 
@@
 	\begin{verbatim}
-Select ?s where {
+SELECT ?s WHERE {   ?z dc:source ?s .
   ?z rdf:type rdf:Statement ; rdf:subject _:alice ;
-     rdf:predicate foaf:knows ; rdf:object _:bob ; dc:source ?s. }
+  rdf:predicate foaf:knows ; rdf:object _:bob . }
 
@@
 
-Thus, Reifi not only leads to large additional overheads in terms of RDF data management due to the increased size of the data but also, has a negative effect on the efficiency of RDF query processing.
-In this work, we propose an efficient mechanism for RDF reification, called \emph{Reifi+}, which can avoid this five fold blowup of data and reduce the number of joins.
-Instead of using four additional triples for reification, Reifi+ only needs one particular URI, called \emph{triple reference}.
-For instance, information captured by the four triples specified above for the reified statements is represented in Reifi+ using the single URI \verb+_:bob foaf:mbox <mailto:bob@home>+ (note this URI directly encodes the information captured in the original triple).
+Thus, {\Reifi} not only leads to large additional overhead in terms of RDF data management due to the increased size of the data but also, has a negative effect on the efficiency of query processing.
+In this work, we propose an efficient mechanism for RDF reification, called \emph{\ReifiPlus}, which can avoid this five fold blowup of data and reduce the number of joins.
+Instead of using four additional triples for reification, {\ReifiPlus} only needs one particular URI, called \emph{triple reference}.
+For instance, information captured by the four triples specified above for the reified statements is represented in {\ReifiPlus} using the single URI \verb+_:bob foaf:mbox <mailto:bob@home>+ (note this URI directly encodes the information captured in the original triple).
 We propose extensions for the RDF and SPARQL standards to support this concept of triple reference.
-Also, we incorporate Reifi+ into two commercial RDF stores (Virtuoso, Bigdata), showing in experiments that compared to Reifi, this proposal results in substantial performance gain both in terms of RDF data management and SPARQL query processing: on average, Reifi+ reduces data size requirements by \todo{X percent} and improves response time by \todo{X percent}.
+Also, we incorporate {\ReifiPlus} into two commercial RDF stores (Virtuoso, Bigdata), showing in experiments that compared to {\Reifi}, this proposal results in substantial performance gain both in terms of RDF data management and SPARQL query processing: on average, {\ReifiPlus} reduces data size requirements by \todo{X percent} and improves response time by \todo{X percent}.
 
@@
 \textbf{Outline.} We will start in Section 2 with the related work section where we provide a broader overview of works on RDF metadata beyond named graphs and RDF reification.
-The main idea behind Reifi+ and its main advantages over Reifi are discussed in Section 3.
+The main idea behind {\ReifiPlus} and its main advantages over {\Reifi} are discussed in Section 3.
 Then, we discuss how to extend RDF and SPARQL to incorporate this reification mechanism in Section 4 and 5, respectively.

### 2012-06-04 paper-iswc-reification/intro.tex
added labels for the main sections and used these to cross-reference in the outline paragraph of the intro

@@
 
-\textbf{Outline.} We will start in Section 2 with the related work section where we provide a broader overview of works on RDF metadata beyond named graphs and RDF reification.
-The main idea behind {\ReifiPlus} and its main advantages over {\Reifi} are discussed in Section 3.
-Then, we discuss how to extend RDF and SPARQL to incorporate this reification mechanism in Section 4 and 5, respectively.
-We present experimental results in Section 6 and conclude in Section 7.
+\textbf{Outline.} We will start in Section~\ref{Section:RelWork} with the related work section where we provide a broader overview of works on RDF metadata beyond named graphs and RDF reification.
+The main idea behind {\ReifiPlus} and its main advantages over {\Reifi} are discussed in Section~\ref{Section:Discussion}.
+Then, we discuss how to extend RDF and SPARQL to incorporate this reification mechanism in Section~\ref{Section:DataModel} and~\ref{Section:Querying}, respectively.
+We present experimental results in Section~\ref{Section:Experiments} and conclude in Section~\ref{Section:Conclusion}.

### 2012-06-04 trunk/paper-iswc-reification/exp.tex
added labels for the main sections and used these to cross-reference in the outline paragraph of the intro

@@
-\section{Experiments}
+\section{Experiments} \label{Section:Experiments}
 We now study the advantages of our approach as discussed previously through an experimental analysis, in which we compare our work (henceforth referred to as \emph{Refi+}) with an implementation of the standard proposal for RDF reification (\emph{Refi}).

### 2012-06-04 trunk/paper-iswc-reification/querying.tex
added labels for the main sections and used these to cross-reference in the outline paragraph of the intro

--- 2012-05-18 paper-iswc-reification/querying.tex
@@
-\section{Querying}
+\section{Querying} \label{Section:Querying}
+
 \todo{introduction for this section}
@@
 	, then $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, and $(P_1 \OpFILTER R)$ are {\SPARQLplus} expressions.
+% 	\item Let $P$ be a {\SPARQLplus} expression and $S \subset \symAllVariables$ be a finite set of variables, then $\OpSELECT_S(P)$ is a {\SPARQLplus} expression.
 \end{enumerate}
+
+\begin{note}
+		We note that any
+		%Any
+	(ordinary) SPARQL expression is a {\SPARQLplus} expression.
+\end{note}
+
+\todo{introduce $\fctVarsPlus{P}$ and $\fctTRefs{P}$ ...}
+
+	\begin{tabular}{|c||c|c|} \hline
+		{\SPARQLplus} expression $P$ &
+		$\fctVarsPlus{P}$ &
+		$\fctTRefs{P}$
+		\\ \hline
+		\hline
+% 		{\TPplus} $(s,p,o)$ &
+% 		$\bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$ &
+% 		$\bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$
+% 		\\ \hline
+		$(tp \OpAS ?v)$ &
+		$\fctVarsPlus{tp} \cup \lbrace ?v \rbrace$ &
+		$\fctTRefs{tp} \cup \lbrace tp \rbrace$
+		\\ \hline
+		$(P_1 \OpAND P_2)$ &
+		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
+		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
+		\\ \hline
+		$(P_1 \OpOPT P_2)$ &
+		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
+		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
+		\\ \hline
+		$(P_1 \OpUNION P_2)$ &
+		$\fctVarsPlus{P_1} \cup \fctVarsPlus{P_2}$ &
+		$\fctTRefs{P_1} \cup \fctTRefs{P_2}$
+		\\ \hline
+		$(P' \OpFILTER R)$ &
+		$\fctVarsPlus{P'} \cup \fctVars{R}$ &
+		$\fctTRefs{P'}$
+		\\ \hline
+% 		$\OpSELECT_S(P')$ &
+% 		$\fctVarsPlus{P'} \cup S$ &
+% 		$\fctTRefs{P'}$
+% 		\\ \hline
+	\end{tabular}
 
@@
 
-Let $\Omega_1$, $\Omega_2$ and $\Omega$ be sets of valuations; let $R$ be a filter condition.
-The binary operations \emph{join}, \emph{union}, \emph{difference}, and \emph{left outer-join} between $\Omega_1$ and $\Omega_2$ are defined as follows:
+Let $\Omega_1$, $\Omega_2$ and $\Omega$ be sets of
+	%valuations; let
+	valuations and let
+$R$ be a filter condition%
+	%; and let $S \subset \symAllVariables$ be a finite set of variables.
+	.
+The algebra operators \emph{join}, \emph{union}, \emph{difference}, \emph{left outer-join},
+	%\emph{selection}, and \emph{projection}
+	and \emph{selection}
+are defined as follows:
 \begin{align*}
-	\Omega_1 \Join \Omega_2 & := \lbrace \eta_1 \cup \eta_1 \,|\, \eta_1 \in \Omega_1 \text{ and } \eta_2 \in \Omega_2 \text{ and } \eta_1 \sim \eta_2 \rbrace \\
-	\Omega_2 \cup \Omega_2 & := \lbrace \eta \,|\, \eta \in \Omega_1 \text{ or } \eta \in \Omega_2 \rbrace \\
-	\Omega_1 \setminus \Omega_2 & := \lbrace \eta_1 \in \Omega_1 \,|\, \forall \eta_2 \in \Omega_2 : \eta_1 \not\sim \eta_2 \rbrace \\
-	\Omega_1 \LJoin \Omega_2 &:= \left( \Omega_1 \Join \Omega_2 \right) \cup \left( \Omega_1 \setminus \Omega_2 \right) \\
+	\Omega_1 \Join \Omega_2 & := \lbrace \eta_1 \cup \eta_1 \,|\, \eta_1 \in \Omega_1 \text{ and } \eta_2 \in \Omega_2 \text{ and } \eta_1 \sim \eta_2 \rbrace
+	\\
+	\Omega_2 \cup \Omega_2 & := \lbrace \eta \,|\, \eta \in \Omega_1 \text{ or } \eta \in \Omega_2 \rbrace
+	\\
+	\Omega_1 \setminus \Omega_2 & := \lbrace \eta_1 \in \Omega_1 \,|\, \forall \eta_2 \in \Omega_2 : \eta_1 \not\sim \eta_2 \rbrace
+	\\
+	\Omega_1 \LJoin \Omega_2 &:= \left( \Omega_1 \Join \Omega_2 \right) \cup \left( \Omega_1 \setminus \Omega_2 \right)
+	\\
 	\sigma_R ( \Omega ) &:= \lbrace \eta \in \Omega \,|\, \eta \text{ satisfies } R \rbrace
+% 	\\
+% 	\pi_S ( \Omega ) &:= \lbrace \eta \,|\, \exists \, \eta' : \eta \cup \eta' \in \Omega \text{ and } \fctDom{\eta} \subseteq S \text{ and } \fctDom{\eta'} \cap S = \emptyset \rbrace
 \end{align*}
 
+\noindent
 %For a valuation $\eta$ and a {\TPplus} $tp$, we write $\eta[tp]$ to denote the {\TPplus} that we obtain by replacing the variables in $tp$ (including potentially embedded {\TPplus}s) according to $\eta$.
-Note, if $\fctVars{tp} \subseteq \fctDom{\eta}$, then $\eta[tp]$ is an {\RDFplusTriple}.
-
+Note, if $\fctVarsPlus{tp} \subseteq \fctDom{\eta}$, then $\eta[tp]$ is an {\RDFplusTriple}.
+%
 	%Let $P$ be a {\SPARQLplus} expression and let $G$ be an {\RDFplusGraph}. The \emph{evaluation of $P$ over $G$},
 	The \emph{evaluation} of {\SPARQLplus} expression $P$ over {\RDFplusGraph} $G$,
-denoted by $\fctEval{P}{G}$, is defined recursively as follows:
+denoted by $\fctEvalPlus{P}{G}$, is defined recursively as follows:
 \begin{enumerate}
@@
 		\end{align*}
-		\item If $P$ is $(P_1 \OpAND P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \Join \fctEval{P_2}{G}$.
-		\item If $P$ is $(P_1 \OpUNION P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \cup \fctEval{P_2}{G}$.
-		\item If $P$ is $(P_1 \OpOPT P_2)$, then $\fctEval{P}{G} := \fctEval{P_1}{G} \LJoin \fctEval{P_2}{G}$.
-		\item If $P$ is $(P' \OpFILTER R)$, then $\fctEval{P}{G} := \sigma_R\bigl( \fctEval{P'}{G} \bigr)$.
+	\item If $P$ is $(P_1 \OpAND P_2)$, then $\fctEvalPlus{P}{G} := \fctEvalPlus{P_1}{G} \Join \fctEvalPlus{P_2}{G}$.
+	\item If $P$ is $(P_1 \OpUNION P_2)$, then $\fctEvalPlus{P}{G} := \fctEvalPlus{P_1}{G} \cup \fctEvalPlus{P_2}{G}$.
+	\item If $P$ is $(P_1 \OpOPT P_2)$, then $\fctEvalPlus{P}{G} := \fctEvalPlus{P_1}{G} \LJoin \fctEvalPlus{P_2}{G}$.
+	\item If $P$ is $(P' \OpFILTER R)$, then $\fctEvalPlus{P}{G} := \sigma_R\bigl( \fctEvalPlus{P'}{G} \bigr)$.
+% 	\item If $P$ is $\OpSELECT_S(P')$, then $\fctEvalPlus{P}{G} := \pi_S\bigl( \fctEvalPlus{P'}{G} \bigr)$.
 \end{enumerate}
-	Each valuation $\eta \in \fctEval{P}{G}$ is called a \emph{solution} for $P$ in $G$.
+
+\noindent
+\removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
+
+The following result shows that the query semantics introduced in this section is fully compatible to the usual SPARQL semantics (as defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus}
+	and {\SPARQLplus}
+may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.
+
+\begin{proposition} \label{Proposition:EquivalenceOfSemantics}
+	For any (ordinary) RDF graph $G$ and any (ordinary) SPARQL expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEval{P}{G}$.
+\end{proposition}
+
+\todo{...}
 
 \begin{proposition}
-	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEval{P}{G} = \fctEval{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
+	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
 \end{proposition}
+
+\todo{There is a minimal $G_\mathsf{min} \subseteq G$ with $G_\mathsf{min} = G^+$ ...}
 
@@
 
-\todo{...}
+Let $P$ be a {\SPARQLplus} expression.
+We assume an \removable{(arbitrary)} injective function $v : \fctTRefs{P} \rightarrow \symAllVariables \cap \fctVarsPlus{P}$.
+Furthermore, we introduce another injective function $w : (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals) \rightarrow (\symAllVariables \cup \symAllURIs \cup \symAllLiterals)$ that is defined as follows: Let $x \in (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals)$.
+If $x \in \fctTRefs{P}$, then $w(x) := v(x)$; if $v \notin \fctTRefs{P}$, then $w(x) := x$.
+%
+Using $w$, for any $rp = (s,p,o) \in \fctTRefs{P}$ we write $\mathrm{reif}^w( rp )$ to denote
+	the SPARQL expression $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
+	%following SPARQL expression: \begin{align*}
+	%	\Bigl( \Bigl( \,\, \Bigl( & \bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr) \OpAND \bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr) \Bigr) \OpAND \\
+	%	& \bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr) \Bigr) \OpAND \bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr) \Bigr)
+	%\end{align*}
+
+The \emph{$w$-based, RDF compatible expression} of $P$, denoted by $\fctDescent{P}^{w}$, is defined recursively as follows:
+\begin{enumerate}
+	\item If $P$ is a {\TPplus} $(s,p,o)$, and:
+		\begin{enumerate}
+			\item if $s \notin \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescent{P}^w$ is $(s,p,o)$; or
+			\item if $s \in \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescent{P}^w$ is $\bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND (s'\!,p,o) \bigr)$; or
+			\item if $s \notin \symAllTPs$ and $o \in \symAllTPs$, then $\fctDescent{P}^w$ is $\bigl( \bigl( P_{o1} \OpAND P_{o2} \bigr) \OpAND (s,p,o') \bigr)$; or
+			\item else $\fctDescent{P}^w$ is $\bigl( \bigl( \bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND P_{o1} \bigr) \OpAND P_{o2} \bigr) \OpAND (s'\!,p,o') \bigr)$;
+		\end{enumerate}
+		where $s'$ is $w(s)$, $o'$ is $w(o)$, $P_{s1}$ is $\mathrm{reif}^w(s)$, $P_{s2}$ is $\fctDescent{s}^w$, $P_{o1}$ is $\mathrm{reif}^w(o)$, and $P_{o2}$ is $\fctDescent{o}^w$.
+		\vspace{1ex}
+
+	\item If $P$ is
+			%$(tp \OpAS ?v)$ with $tp = (s,p,o)$,
+			$\bigl( (s,p,o) \OpAS ?v \bigr)$,
+		then $\fctDescent{P}^w$ is $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
+
+% 	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, $(P_1 \OpFILTER R)$, or $\OpSELECT_S(P_1)$, then $\fctDescent{P}^w$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, $(P_1' \OpFILTER R)$, and $\OpSELECT_S(P_1')$, respectively; where $P_1'$ is $\fctDescent{P_1}^w$ and $P_2'$ is $\fctDescent{P_2}^w$.
+
+		\vspace{1ex}
+	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, or $(P_1 \OpFILTER R)$, then $\fctDescent{P}^w$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, and $(P_1' \OpFILTER R)$, respectively; where $P_1'$ is $\fctDescent{P_1}^w$ and $P_2'$ is $\fctDescent{P_2}^w$.
+
+% 	\begin{tabular}{|c||c||c||c||c||c|} \hline
+% 		$\boldsymbol{P}$ &
+% 		$(P_1 \OpAND P_2)$ &
+% 		$(P_1 \OpOPT P_2)$ &
+% 		$(P_1 \OpUNION P_2)$ &
+% 		$(P_1 \OpFILTER R)$ &
+% 		$\OpSELECT_S(P_1)$
+% 		\\ \hline
+% 		$\boldsymbol{ \fctDescent{P}^w}$ &
+% 		$(P_1' \OpAND P_2')$ &
+% 		$(P_1' \OpOPT P_2')$ &
+% 		$(P_1' \OpUNION P_2')$ &
+% 		$(P_1' \OpFILTER R)$ &
+% 		$\OpSELECT_S(P_1')$
+% 		\\ \hline
+% 	\end{tabular}
+%
+% 	\begin{center}
+% 	\begin{tabular}{|c|c|} \hline
+% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescent{P}^w}$ \\ \hline \hline
+% 		$(P_1 \OpAND P_2)$ & $(P_1' \OpAND P_2')$ \\ \hline
+% 		$(P_1 \OpOPT P_2)$ & $(P_1' \OpOPT P_2')$ \\ \hline
+% 	\end{tabular}
+% 	\hspace{10mm}
+% 	\begin{tabular}{|c|c|} \hline
+% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescent{P}^w}$ \\ \hline \hline
+% 		$(P_1 \OpUNION P_2)$ & $(P_1' \OpUNION P_2')$ \\ \hline
+% 		$(P_1 \OpFILTER R)$ & $(P_1' \OpFILTER R)$ \\ \hline
+% 	\end{tabular}
+% 	\end{center}
+\end{enumerate}
+
+\begin{proposition} \label{Proposition:EquivalenceOfSyntaxAfterConverting}
+	For any {\SPARQLplus} expression $P$ any RDF compatible expression of $P$ is an (ordinary) SPARQL expression.
+\end{proposition}
+
+\noindent
+To show a (semantic) equivalence between {\SPARQLplus} expressions and the corresponding SPARQL expressions we need an additional algebra operator to project out (bindings for) query variables that the conversion introduces.
+We define \emph{projection} as follows: Let $\Omega$ be a set of valuations and let $S \subset \symAllVariables$ be a finite set of variables, then $\pi_S ( \Omega ) := \lbrace \eta \,|\, \exists \, \eta' : \eta \cup \eta' \in \Omega \text{ and } \fctDom{\eta} \subseteq S \text{ and } \fctDom{\eta'} \cap S = \emptyset \rbrace$.
+Using projection we may now show the following equivalence:
+
+\begin{proposition} \label{Proposition:QueryEquivalenceAfterConverting}
+	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ that does not contain a sub-expression
+		\removable{of the form}
+	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEvalPlus{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescent{P}^w$ of $P$.
+\end{proposition}
+
+\noindent
+The following result is a direct consequence of Propositions~\ref{Proposition:EquivalenceOfSemantics}, \ref{Proposition:EquivalenceOfSyntaxAfterConverting}, and~\ref{Proposition:QueryEquivalenceAfterConverting}:
+\begin{corollary}
+	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ that does not contain a sub-expression
+		\removable{of the form}
+	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEval{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescent{P}^w$ of $P$.
+\end{corollary}
+
+\noindent
+\todo{briefly discuss the Corollary}

### 2012-06-04 trunk/paper-iswc-reification/querying.tex
intro for the query section

@@
 
-\todo{introduction for this section}
+To fully benefit from our extended data model we extend the RDF query language SPARQL.
+Our extension, which we call \emph{\SPARQLplus}, adds new features that enable users to directly access metadata triples in queries.
+In particular, {\SPARQLplus} introduces a possibility for binding {\RDFplusTriple}s to query variables; such a variable may then be used in a triple pattern in order to ask for matching metadata triples.
+Furthermore, as a shortcut, (recursively nested) triple patterns may be directly embedded in triple patterns.
+
+In this section we define {\SPARQLplus} formally.
+Due to space limitations, we focus on a core fragment of the language; this fragment corresponds to the core fragment of SPARQL that P\'{e}rez et al.~discuss in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
+We also adapt P\'{e}rez et al.'s formalization approach, that is, we define {\SPARQLplus} using an algebraic syntax.
+In what follows we first introduce the syntax and then specify a compositional set semantics for {\SPARQLplus} queries.
+While an implementation of this semantics requires a system that supports our {\RDFplus} data model, we also aim to enable existing SPARQL execution systems to answer
+	\removable{metadata-related}
+{\SPARQLplus} queries over ordinary RDF data (in which statement-level metadata is represented via RDF reification). Consequently, we complement the definition of {\SPARQLplus}
+	%in this section
+with a function for converting {\SPARQLplus} queries to SPARQL queries. % and we show that the resulting SPARQL queries produce the same answer
 
@@
 
-\subsection{{\RDFplus} Semantics of {\SPARQLplus}}
+\subsection{({\RDFplus} Based) Semantics of {\SPARQLplus}}
 	To define the semantics of {\SPARQLplus} we introduce
@@
 
-\subsection{RDF Semantics of {\SPARQLplus}}
+\subsection{Using {\SPARQLplus} for Querying RDF Reification Based Metadata}
 	%For RDF storage systems that do not support our {\RDFplus} data model (but the ordinary RDF data model), we define an alternative semantics for {\SPARQLplus}.

### 2012-06-06 trunk/paper-iswc-reification/querying.tex
polished Sections 5.1 and 5.2

@@
 A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).
-	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVarsPlus{tp}$; hence, $\fctVarsPlus{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
-	For any {\TPplus} $tp \!=\!
-(s,p,o)$ we define $\fctVarsPlus{tp} \!:=\!
-\bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
+%	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVarsPlus{tp}$; hence, $\fctVarsPlus{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
+%	For any {\TPplus} $tp \!=\!
+(s,p,o)$ we define $\fctVarsPlus{tp} := \bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$ and $\fctTRefs{tp} := \bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
 
@@
 		%Any
-	(ordinary) SPARQL expression is a {\SPARQLplus} expression.
+	(ordinary) SPARQL expression (as defined by P\'{e}rez et al.~\cite{Perez09:SemanticsAndComplexityOfSPARQL}) is a {\SPARQLplus} expression.
 \end{note}
 
-\todo{introduce $\fctVarsPlus{P}$ and $\fctTRefs{P}$ ...}
-
+\noindent
+For any {\SPARQLplus} expression $P$ we write $\fctTRefs{P}$ to denote the set of all {\TPplus}s embedded in a {\TPplus} in $P$; and $\fctVarsPlus{P}$ denotes the set of all variables mentioned in $P$ (including in embedded {\TPplus}s).
+Formally, if $P$ is a {\TPplus} $tp \!=\!
+(s,p,o)$,
+then $\fctVarsPlus{tp} := \bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$
+and $\fctTRefs{tp} := \bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
+If $P$ is not a {\TPplus}, then $\fctVarsPlus{P}$ and $\fctTRefs{P}$ are defined as follows:
+	\par \vspace{1pt}
+	\parbox{0.95\linewidth}{\centering
 		\begin{tabular}{|c||c|c|} \hline
@@
 		\end{tabular}
+	}
+	\par
 
@@
 \noindent
-\removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
-
-The following result shows that the query semantics introduced in this section is fully compatible to the usual SPARQL semantics (as defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus}
-	and {\SPARQLplus}
-may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.
+% \removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
+% 
+We emphasize that our definitions in this section resemble the definitions with which
+	%P\'{e}rez et al.~define
+the evaluation function $\fctEval{\cdot}{ }$ for ordinary SPARQL
+	%expressions~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
+	expressions is defined~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
+As the primary difference we note that the definitions for SPARQL are based on so called \emph{solution mapping}s, that are, partial mappings $\mu : \symAllVariables \rightarrow \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$, whereas we use valuations $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
+However, any valuation
+	%$\eta$ for which $\forall \, ?v \in \fctDom{\eta} : \eta(?v) \notin \symAllTriples$,
+	that binds variables only to URIs, blank nodes, or literals (but not to {\RDFplusTriple}s),
+may also be understood as a solution mapping.
+Based on this understanding, the following result shows that our query semantics for {\SPARQLplus} is fully compatible to the usual SPARQL semantics (defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus} and {\SPARQLplus} may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.
 
 \begin{proposition} \label{Proposition:EquivalenceOfSemantics}
-	For any (ordinary) RDF graph $G$ and any (ordinary) SPARQL expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEval{P}{G}$.
+	For any
+		%(ordinary)
+	RDF graph $G$ and any
+		%(ordinary)
+	SPARQL
+		%expression $P$
+		expr.~$P$
+	holds $\fctEvalPlus{P}{G} \!=\! \fctEval{P}{G}$.
 \end{proposition}
 
-\todo{...}
+\todo{Motivate the following proposition (it is cool because it shows that we may reduce queried {\RDFplus} data to a minimum base and it nicely corresponds to Proposition~\ref{Proposition:JustificationForDataMinimality1}}
 
-\begin{proposition}
+\begin{proposition} \label{Proposition:JustificationForDataMinimality2}
 	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
@@
 \subsection{Using {\SPARQLplus} for Querying RDF Reification Based Metadata}
-	%For RDF storage systems that do not support our {\RDFplus} data model (but the ordinary RDF data model), we define an alternative semantics for {\SPARQLplus}.
-	In addition to the {\SPARQLplus} semantics defined in the previous section, we now define an alternative semantics for {\SPARQLplus}.
-This alternative semantics enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.
+
+In addition to the {\SPARQLplus} semantics defined in the previous section, we now define
+	%an alternative semantics for {\SPARQLplus}. This alternative semantics
+	a function for converting {\SPARQLplus} queries to SPARQL queries. This conversion function
+enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.
 

### 2012-06-06 trunk/paper-iswc-reification/rep.tex
polished Sections 5.1 and 5.2

--- 2012-05-10 paper-iswc-reification/rep.tex
@@
-\section{Representation}
-Syntax 
-Expressed tersely as:
-  <<:SAP :bought :sybase>> dc:source reuters:us-sybase .
-Statements are “wrapped” by << … >> 
-Turtle Extension
-<<:SAP :bought :sybase>> dc:source reuters:us-sybase ;
-			  dc:created “1995-01-07” ;
-                        		 dc:author  “James R. Jones“ .
+\section{Data Model} \label{Section:DataModel}
 
--	The statement can appear in either the subject or object position.
--	Recursion in statements is allowed
--	But depth is shallow in practice
-Semantics
+In this section we introduce
+	%an extension of the RDF data model~\cite{Klyne04:RDFconcepts} that makes 
+	our data model which we call {\RDFplus}.
+This model is an extension of the RDF data model~\cite{Klyne04:RDFconcepts}.
+{\RDFplus} extends RDF by making metadata statements a first class citizen in the data model.
+% In the following we \todo{...}
+
+% Main purposes of our data model: 1.)~it allows for a more compact representation; 2.)~it allows for efficient processing
+% with {\RDFplus} our goal is to extend/expand the applicability/usefulness/usability of such triples for cases where ...
+
+\subsection{Concepts}
+
+We assume
+	%\removable{three,}
+pairwise disjoint sets $\symAllURIs$ (all URI references), $\symAllBNodes$ (blank nodes), and $\symAllLiterals$ (literals).
+	As usual, an \emph{RDF triple} is a tuple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ and an \emph{RDF graph} is a set of RDF triples.
+	%As usual, a tuple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ is an \emph{RDF triple}.
+% A set of RDF triples is an \emph{RDF graph}.
+
+{\RDFplus} extends such triples by permitting the embedding of another triple in the subject or object position of a given triple.
+We shall interpret the embedding triple as a statement about the embedded triple.
+An embedded triple may itself be a statement about a triple and, thus, may also contain embedded triples; and so forth.
+	%Therefore, the model should allow for nesting.
+%
+	%As a basis for formalizing
+	To formalize
+such kind of (nested) embedding we
+	%introduce
+	define
+a set $\symAllTriplesInfinite := (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$.
+%
+	As a basis for ruling
+	%To rule
+out infinitely deep nesting we introduce the notion of \emph{$k$-nestedness} (where $k$
+	is an arbitrary
+	%may be any
+natural number): A tuple $(s,p,o) \in \symAllTriplesInfinite$ is $k$-nested if either 1.)~$k=0$ and
+	%$(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$
+	$(s,p,o)$ is an RDF triple
+or 2.)~$k>0$ and for all $x \in \bigl( \lbrace s,o \rbrace \cap \symAllTriplesInfinite \bigr)$ holds $x$ is $(k\!-\!1$)-nested. Using $k$-nestedness we now define our extended notion of triples%
+	.
+	%:
+
+An \emph{{\RDFplusTriple}} is a tuple $t \in \symAllTriplesInfinite$ for which exists a natural number $k$ such that $t$ is $k$-nested; to denote the set of all {\RDFplusTriple}s we write $\symAllTriples$ (i.e.~$\symAllTriples \subset \symAllTriplesInfinite$).
+For any {\RDFplusTriple} $t=(s,p,o)$ we define
+	$\fctTermsPlus{t} := \lbrace s,p,o \rbrace \cup \big\lbrace x' \in \fctTermsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTriples \big\rbrace$.
+	%$\fctTermsPlus{t} := \lbrace s,p,o \rbrace \cup \bigcup_{x \in \lbrace s,o \rbrace \cap \symAllTriples} \fctTermsPlus{x}$.
+%Furthermore, we write $\fctTRef{t}$ to denote the set of all {\RDFplusTriple}s that are (recursively) embedded in $t$; formally: $\fctTRef{t} := \bigl( \lbrace s,o \rbrace \cap \symAllTriples \bigr) \cup \big\lbrace t' \in \fctTRef{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTriples \big\rbrace$.
+We call an {\RDFplusTriple}
+	$t=(s,p,o)$ for which $s \in \symAllTriples$ or $o \in \symAllTriples$,
+	%$t$ for which $\fctTRef{t} = \emptyset$,
+a \emph{metadata triple}%
+	%; note that any other {\RDFplusTriple} is an ordinary RDF triple.
+	.
+
+A set of {\RDFplusTriple}s is an \emph{\RDFplusGraph}.
+Overloading function $\symTermsPlusFct$, for any {\RDFplusGraph} $G$ we define $\fctTermsPlus{G} := \bigcup_{t \in G} \fctTermsPlus{t}$.
+Furthermore, for {\RDFplusGraph} $G$, we write $\fctTRefs{G}$ to denote the set of all {\RDFplusTriple}s that are (recursively) embedded in {\RDFplusTriple}s of $G$; hence $\fctTRefs{G} := \fctTermsPlus{G} \cap \symAllTriples$.
+
+% Any {\RDFplusTriple} that is embedded in another {\RDFplusTriple} is also assumed to be (implicitly) contained in data that contains the embedding triple.
+To make this assumption explicit we introduce an operation that (recursively) unnests {\RDFplusTriple}s: Let $t=(s,p,o)$ be an {\RDFplusTriple}, then $\fctClose{t}$ is a set of {\RDFplusTriple}s that is defined as follows:
+% \begin{equation*}
+% 	\fctClose{t} := \big\lbrace t' \,\big|\, t' = t \text{ or } \exists \, t^* \in \lbrace s,o \rbrace \cap \symAllTriples : t' \in \fctClose{t^*} \big\rbrace
+% \end{equation*}
+% Overloading
+% 	function $\symCloseFct$,
+% 	%notation,
+% for any {\RDFplusGraph} $G$ we define $\fctClose{G} := \bigcup_{t \in G} \fctClose{t}$.
+
+% While syntactically {\RDFplusTriple}s and {\TRef}s are the same, they represent different concepts: {\RDFplusTriple}s may be interpreted as statements (similar to RDF triples) whereas a {\TRef} denotes an {\RDFplusTriple}
+% 	%that is embedded in other {\RDFplusTriple}s.
+% 	for the purpose of making a statement about it.
+% %
+% 	\removable{Hence, trefs may be understood as a particular type of name for {\RDFplusTriple}s.}
+% However, since {\TRef}s carry all elements of the {\RDFplusTriple}s they denote, it is possible to obtain such a triple from its reference: We introduce a bijective function $\symDerefFct$ that maps the set of {\TRef}s to the set of all {\RDFplusTriple}s and that is defined as follows: Let $r=(s,p,o) \in \symAllTRefs$ be an arbitrary {\TRef}, then $\fctDeref{r}$ is the {\RDFplusTriple} $(s,p,o)$.
+
+% \todo{$G$ and $\fctClose{G}$ are semantically equivalent!!}
+\todo{$G$ and $G \cup \fctTRefs{G}$ are semantically equivalent!!}
+
+\subsection{Interpretation}
+
+Let $G$ be an {\RDFplusGraph}.
+For \Todo{converting}{introduce this subsection (explain the purpose of the conversion function defined here)} $G$ into a set of RDF triples we assume a bijective function $id : \fctTRefs{G} \rightarrow B$ where $B \subset \symAllBNodes$ is a set of blank nodes such that $| B | = | \fctTRefs{G} |$ and $B \cap \fctTerms{G} = \emptyset$.
+Hence, $id$ associates each {\TRef} in $G$ with a fresh blank node (not used in $G$).
+Furthermore, we introduce
+	%an injective function $id^* : \fctTermsPlus{G} \rightarrow \fctTermsPlus{G} \cup B$
+	another bijective function $id^*\! : \fctTermsPlus{G} \rightarrow B \cup \bigl( \fctTermsPlus{G} \!\setminus\! \fctTRefs{G} \bigr)$
+that is defined as follows: Let $x \in \fctTermsPlus{G}$. If $x \in \symAllTriples$ then $id^*\!(x) := id(x)$; if $x \notin \symAllTriples$ then $id^*\!(x) := x$.
+%
+Using $id^*$, for any $t = (s,p,o) \in \fctTRefs{G}$ we define:
+\begin{align*}
+	\mathrm{reif}\bigl( t \bigr) := \big\lbrace
+		& (id^*\!(t),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
+		(id^*\!(t),\mathTinyRDF{rdf\!:\!subject},id^*\!(s)), \\
+		& (id^*\!(t),\mathTinyRDF{rdf\!:\!predicate},id^*\!(p)),
+		(id^*\!(t),\mathTinyRDF{rdf\!:\!object},id^*\!(o))
+	\big\rbrace
+\end{align*}
+
+\noindent
+For any {\RDFplusTriple} $t = (s,p,o) \in G$ we define:
+\begin{equation*}
+	\fctDescent{t} := \begin{cases}
+\vspace{1mm}
+		\big\lbrace (id(s),p,o) \big\rbrace \cup \mathrm{reif}(s) \cup \fctDescent{s} & \text{if $s \in \symAllTriples$ and $o \notin \symAllTriples$,} \\
+\vspace{1mm}
+		\big\lbrace (s,p,id(o)) \big\rbrace \cup \mathrm{reif}(o) \cup \fctDescent{o} & \text{if $s \notin \symAllTriples$ and $o \in \symAllTriples$,} \\
+\vspace{1mm}
+		\begin{minipage}[c]{55mm}\vspace{1mm}
+			$\big\lbrace (id(s),p,id(o)) \big\rbrace \cup \mathrm{reif}(s) \cup \fctDescent{s}$ \\
+			\hspace*{27.5mm}$\cup \, \mathrm{reif}(o) \cup \fctDescent{o}$
+		\end{minipage} & \text{if $s \in \symAllTriples$ and $o \in \symAllTriples$,} \\
+		\big\lbrace (s,p,o) \big\rbrace & \text{else} .
+\end{cases}
+\end{equation*}
+
+\noindent
+\Todo{Finally}{add some more text here}:
+\begin{equation*}
+	\fctDescent{G} := \bigcup_{t \in G} \fctDescent{t}
+\end{equation*}
+
+\begin{example}
+	Let $G_\mathsf{ex} = \lbrace t_\mathsf{ex} \rbrace$ be an {\RDFplusGraph} that consists of a single {\RDFplusTriple} $t_\mathsf{ex} = \bigl( (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}), \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf} \bigr)$.
+% 	The result of converting $G_\mathsf{ex}$ to an RDF graph is:
+% 	\begin{align*}
+% 		\fctDescent{G_\mathsf{ex}} = \big\lbrace
+% 			& (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}),
+% 			(b, \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf}), \\
+% 			& (b,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
+% 			(b,\mathTinyRDF{rdf\!:\!subject},\mathTinyRDF{ex:olaf}), \\
+% 			& (b,\mathTinyRDF{rdf\!:\!predicate},\mathTinyRDF{foaf:name}),
+% 			(b,\mathTinyRDF{rdf\!:\!object},\mathTinyRDF{"Olaf"})
+% 		\big\rbrace
+% 	\end{align*}
+	The result of converting $G_\mathsf{ex}$ to an RDF graph $\fctDescent{G_\mathsf{ex}}$ is (in Turtle notation, prefix declarations omitted):
+	\begin{footnotesize}%
+	\begin{verbatim}
+		 ex:olaf foaf:name "Olaf" .
+		 _:b dct:source ex:olaf ; rdf:type rdf:Statement ;
+		     rdf:subject ex:olaf ; rdf:predicate foaf:name ; rdf:object "Olaf" .
+	\end{verbatim}%
+	\end{footnotesize}
+\end{example}
+
+\noindent
+Based on the conversion function, it is possible to interpret any {\RDFplus} model via the usual RDF semantics as defined in~\cite{Hayes04:RDFsemantics}.
+
+\begin{proposition} \label{Proposition:JustificationForDataMinimality1}
+	For any {\RDFplusGraph} $G$ it holds $\fctDescent{G} = \fctDescent{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
+\end{proposition}
+
+\subsection{Representation}
+\todo{briefly introduce our extension for Turtle and explain how this extension is related to {\RDFplus} and how it should be parsed by systems that do not ``understand'' {\RDFplus}}
+
+	\begin{footnotesize}%
+	\begin{verbatim}
+		 <<ex:olaf foaf:name "Olaf">> dct:source ex:olaf .
+	\end{verbatim}%
+	\end{footnotesize}
+
+\todo{From a didactic point of view it may be better to move this subsection to the beginning of Section~\ref{Section:DataModel}}

### 2012-06-06 paper-iswc-reification/commands.tex
added projection operation to the SPARQL fragment we focus on; started to draft the RDF-compatible semantics for our SPARQL extension
added vars+(tp)
added macros for Reifi and Reifi*
some polishing in Sec.5.3

@@
 
+\newcommand{\Reifi}{Reifi}
+\newcommand{\ReifiPlus}{Reifi\xxxPLUS}
 \newcommand{\RDFplus}{RDF\xxxPLUS}
@@
 
+\newcommand{\symVarsPlusFct}{\mathrm{vars}^+} % the name used for \fctVarsPlus
+\newcommand{\fctVarsPlus}[1]{\symVarsPlusFct\!(#1)} % the set of all variables in pattern #1 and its embedded patterns
+
 \newcommand{\symDescentFct}{\mathrm{rdf}} % the name used for \fctDescent
 \newcommand{\fctDescent}[1]{\symDescentFct(#1)} % set of RDF triples for an RDF+ triple/graph
+\newcommand{\fctDescentWP}[2]{\symDescentFct^{#1}\!(#2)} % the #1-based, RDF compatible expression of #2
 
@@
 \newcommand{\OpAS}{\text{ \normalfont\scriptsize\textsf{AS} }}
+\newcommand{\OpSELECT}{\text{\normalfont\scriptsize\textsf{SELECT}}}
 \newcommand{\compatible}{\sim} % the symbol for compatibility between valuations
+\newcommand{\fctEvalPlus}[2]{[\![#1]\!]^\star_{#2}} % the symbol for the evaluation of SPARQL* pattern #1 over an RDF* graph #2
 \newcommand{\fctEval}[2]{[\![#1]\!]_{#2}} % the symbol for the evaluation of SPARQL pattern #1 over an RDF graph #2

### 2012-06-06 paper-iswc-reification/querying.tex
some polishing in Sec.5.3

@@
-\section{Querying}
-\todo{introduction for this section}
+\section{Querying} \label{Section:Querying}
+
+To fully benefit from our extended data model we extend the RDF query language SPARQL.
+Our extension, which we call \emph{\SPARQLplus}, adds new features that enable users to directly access metadata triples in queries.
+In particular, {\SPARQLplus} introduces a possibility for binding {\RDFplusTriple}s to query variables; such a variable may then be used in a triple pattern in order to ask for matching metadata triples.
+Furthermore, as a shortcut, (recursively nested) triple patterns may be directly embedded in triple patterns.
+
+In this section we define {\SPARQLplus} formally.
+Due to space limitations, we focus on a core fragment of the language; this fragment corresponds to the core fragment of SPARQL that P\'{e}rez et al.~discuss in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
+We also adapt P\'{e}rez et al.'s formalization approach, that is, we define {\SPARQLplus} using an algebraic syntax.
+In what follows we first introduce the syntax and then specify a compositional set semantics for {\SPARQLplus} queries.
+While an implementation of this semantics requires a system that supports our {\RDFplus} data model, we also aim to enable existing SPARQL execution systems to answer
+	\removable{metadata-related}
+{\SPARQLplus} queries over ordinary RDF data (in which statement-level metadata is represented via RDF reification). Consequently, we complement the definition of {\SPARQLplus}
+	%in this section
+with a function for converting {\SPARQLplus} queries to SPARQL queries. % and we show that the resulting SPARQL queries produce the same answer
 
@@
 A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).
-	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVarsPlus{tp}$; hence, $\fctVarsPlus{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
-	For any {\TPplus} $tp \!=\!
-(s,p,o)$ we define $\fctVarsPlus{tp} \!:=\!
-\bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
 
@@
 		\end{tabular}
+	}
+	\par
 
-\subsection{{\RDFplus} Semantics of {\SPARQLplus}}
-	To define the semantics of {\SPARQLplus} we introduce
-	%We define the semantics of {\SPARQLplus} based on
-\emph{valuation}s, that are, partial mappings $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
-Two valuations $\eta$ and $\eta'$ are \emph{compatible}, denoted by $\eta \compatible \eta'$, if for all $?v \in \fctDom{\eta} \cap \fctDom{\eta'}$ holds $\eta(?v) = \eta'(?v)$; note,
-	%$\fctDom{\eta}$ denotes
-	$\fctDom{\eta}$~denotes %% Layout Adjustment
-the domain of a valuation $\eta$.
+\subsection{({\RDFplus} Based) Semantics of {\SPARQLplus}}
+To define the semantics of {\SPARQLplus} we introduce \emph{valuation}s, that are, partial mappings $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
+Two valuations $\eta$ and $\eta'$ are \emph{compatible}, denoted by $\eta \compatible \eta'$, if for all $?v \in \fctDom{\eta} \cap \fctDom{\eta'}$ holds $\eta(?v) = \eta'(?v)$; note, $\fctDom{\eta}$ denotes the domain of a valuation $\eta$.
 
@@
 \noindent
-\removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
-
-The following result shows that the query semantics introduced in this section is fully compatible to the usual SPARQL semantics (as defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus}
-	and {\SPARQLplus}
-may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.
+% \removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
+% 
+We emphasize that our definitions in this section resemble the definitions with which
+	%P\'{e}rez et al.~define
+the evaluation function $\fctEval{\cdot}{ }$ for ordinary SPARQL
+	%expressions~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
+	expressions is defined~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
+As the primary difference we note that the definitions for SPARQL are based on so called \emph{solution mapping}s, that are, partial mappings $\mu : \symAllVariables \rightarrow \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$, whereas we use valuations $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
+However, any valuation
+	%$\eta$ for which $\forall \, ?v \in \fctDom{\eta} : \eta(?v) \notin \symAllTriples$,
+	that binds variables only to URIs, blank nodes, or literals (but not to {\RDFplusTriple}s),
+may also be understood as a solution mapping.
+Based on this understanding, the following result shows that our query semantics for {\SPARQLplus} is fully compatible to the usual SPARQL semantics (defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus} and {\SPARQLplus} may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.
 
 \begin{proposition} \label{Proposition:EquivalenceOfSemantics}
-	For any (ordinary) RDF graph $G$ and any (ordinary) SPARQL expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEval{P}{G}$.
+	For any
+		%(ordinary)
+	RDF graph $G$ and any
+		%(ordinary)
+	SPARQL
+		%expression $P$
+		expr.~$P$
+	holds $\fctEvalPlus{P}{G} \!=\! \fctEval{P}{G}$.
 \end{proposition}
 
-\todo{...}
+% \todo{Motivate the following proposition (it is cool because it shows that we may reduce queried {\RDFplus} data to a minimum base and it nicely corresponds to Proposition~\ref{Proposition:JustificationForDataMinimality1}}
+% 
+% \begin{proposition} \label{Proposition:JustificationForDataMinimality2}
+% 	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
+% \end{proposition}
+% 
+% \todo{There is a minimal $G_\mathsf{min} \subseteq G$ with $G_\mathsf{min} = G^+$ ...}
 
-\begin{proposition}
-	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
-\end{proposition}
+\subsection{Using {\SPARQLplus} for Querying RDF Reification Based Metadata}
 
-\todo{There is a minimal $G_\mathsf{min} \subseteq G$ with $G_\mathsf{min} = G^+$ ...}
-
-\subsection{RDF Semantics of {\SPARQLplus}}
-	%For RDF storage systems that do not support our {\RDFplus} data model (but the ordinary RDF data model), we define an alternative semantics for {\SPARQLplus}.
-	In addition to the {\SPARQLplus} semantics defined in the previous section, we now define an alternative semantics for {\SPARQLplus}.
-This alternative semantics enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.
+In addition to the {\SPARQLplus} semantics defined in the previous section, we now define
+	%an alternative semantics for {\SPARQLplus}. This alternative semantics
+	a function for converting {\SPARQLplus} queries to SPARQL queries. This conversion function
+enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.
 
 Let $P$ be a {\SPARQLplus} expression.
-We assume an \removable{(arbitrary)} injective function $v : \fctTRefs{P} \rightarrow \symAllVariables \cap \fctVarsPlus{P}$.
+	%We
+	For converting $P$ to a SPARQL expression we
+assume an \removable{(arbitrary)} injective function $v : \fctTRefs{P} \rightarrow \symAllVariables \cap \fctVarsPlus{P}$.
 Furthermore, we introduce another injective function $w : (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals) \rightarrow (\symAllVariables \cup \symAllURIs \cup \symAllLiterals)$ that is defined as follows: Let $x \in (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals)$.
@@
 %
-Using $w$, for any $rp = (s,p,o) \in \fctTRefs{P}$ we write $\mathrm{reif}^w( rp )$ to denote
+Using $w$, for any $rp = (s,p,o) \in \fctTRefs{P}$ we write $\mathrm{reif}^w\!( rp )$ to denote
 	the SPARQL expression $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(w(rp),\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
@@
 	%\end{align*}
-
-The \emph{$w$-based, RDF compatible expression} of $P$, denoted by $\fctDescent{P}^{w}$, is defined recursively as follows:
+%
+Now, the \emph{$w$-based, RDF compatible expression} of $P$, denoted by $\fctDescentWP{w}{P}$, is defined recursively: % as follows:
 \begin{enumerate}
@@
 		\begin{enumerate}
-			\item if $s \notin \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescent{P}^w$ is $(s,p,o)$; or
-			\item if $s \in \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescent{P}^w$ is $\bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND (s'\!,p,o) \bigr)$; or
-			\item if $s \notin \symAllTPs$ and $o \in \symAllTPs$, then $\fctDescent{P}^w$ is $\bigl( \bigl( P_{o1} \OpAND P_{o2} \bigr) \OpAND (s,p,o') \bigr)$; or
-			\item else $\fctDescent{P}^w$ is $\bigl( \bigl( \bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND P_{o1} \bigr) \OpAND P_{o2} \bigr) \OpAND (s'\!,p,o') \bigr)$;
+			\item if $s \notin \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescentWP{w}{P}$ is $(s,p,o)$; or
+			\item if $s \in \symAllTPs$ and $o \notin \symAllTPs$, then $\fctDescentWP{w}{P}$ is $\bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND (s'\!,p,o) \bigr)$; or
+			\item if $s \notin \symAllTPs$ and $o \in \symAllTPs$, then $\fctDescentWP{w}{P}$ is $\bigl( \bigl( P_{o1} \OpAND P_{o2} \bigr) \OpAND (s,p,o') \bigr)$; or
+			\item else $\fctDescentWP{w}{P}$ is $\bigl( \bigl( \bigl( \bigl( P_{s1} \OpAND P_{s2} \bigr) \OpAND P_{o1} \bigr) \OpAND P_{o2} \bigr) \OpAND (s'\!,p,o') \bigr)$;
 		\end{enumerate}
-		where $s'$ is $w(s)$, $o'$ is $w(o)$, $P_{s1}$ is $\mathrm{reif}^w(s)$, $P_{s2}$ is $\fctDescent{s}^w$, $P_{o1}$ is $\mathrm{reif}^w(o)$, and $P_{o2}$ is $\fctDescent{o}^w$.
+		where $s'$ is $w(s)$, $o'$ is $w(o)$, $P_{s1}$ is $\mathrm{reif}^w\!(s)$, $P_{s2}$ is $\fctDescentWP{w}{s}$, $P_{o1}$ is $\mathrm{reif}^w\!(o)$, and $P_{o2}$ is $\fctDescentWP{w}{o}$.
 		\vspace{1ex}
@@
 			$\bigl( (s,p,o) \OpAS ?v \bigr)$,
-		then $\fctDescent{P}^w$ is $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
+		then $\fctDescentWP{w}{P}$ is $( ( ( tp_1 \OpAND tp_2 ) \OpAND tp_3 ) \OpAND tp_4 )$ where $tp_1$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}\bigr)$, $tp_2$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!subject},w(s)\bigr)$, $tp_3$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!predicate},w(p)\bigr)$, and $tp_4$ is $\bigl(?v,\mathTinyRDF{rdf\!:\!object},w(o)\bigr)$.
 
-% 	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, $(P_1 \OpFILTER R)$, or $\OpSELECT_S(P_1)$, then $\fctDescent{P}^w$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, $(P_1' \OpFILTER R)$, and $\OpSELECT_S(P_1')$, respectively; where $P_1'$ is $\fctDescent{P_1}^w$ and $P_2'$ is $\fctDescent{P_2}^w$.
+% 	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, $(P_1 \OpFILTER R)$, or $\OpSELECT_S(P_1)$, then $\fctDescentWP{w}{P}$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, $(P_1' \OpFILTER R)$, and $\OpSELECT_S(P_1')$, respectively; where $P_1'$ is $\fctDescentWP{w}{P_1}$ and $P_2'$ is $\fctDescentWP{w}{P_2}$.
 
 		\vspace{1ex}
-	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, or $(P_1 \OpFILTER R)$, then $\fctDescent{P}^w$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, and $(P_1' \OpFILTER R)$, respectively; where $P_1'$ is $\fctDescent{P_1}^w$ and $P_2'$ is $\fctDescent{P_2}^w$.
+	\item If $P$ is $(P_1 \OpAND P_2)$, $(P_1 \OpUNION P_2)$, $(P_1 \OpOPT P_2)$, or $(P_1 \OpFILTER R)$, then $\fctDescentWP{w}{P}$ is $(P_1' \OpAND P_2')$, $(P_1' \OpUNION P_2')$, $(P_1' \OpOPT P_2')$, and $(P_1' \OpFILTER R)$, respectively; where $P_1'$ is $\fctDescentWP{w}{P_1}$ and $P_2'$ is $\fctDescentWP{w}{P_2}$.
 
@@
 % 		\\ \hline
-% 		$\boldsymbol{ \fctDescent{P}^w}$ &
+% 		$\boldsymbol{ \fctDescentWP{w}{P}}$ &
 % 		$(P_1' \OpAND P_2')$ &
@@
 % 	\begin{tabular}{|c|c|} \hline
-% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescent{P}^w}$ \\ \hline \hline
+% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescentWP{w}{P}}$ \\ \hline \hline
 % 		$(P_1 \OpAND P_2)$ & $(P_1' \OpAND P_2')$ \\ \hline
@@
 % 	\begin{tabular}{|c|c|} \hline
-% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescent{P}^w}$ \\ \hline \hline
+% 		$\boldsymbol{P}$ & $\boldsymbol{ \fctDescentWP{w}{P}}$ \\ \hline \hline
 % 		$(P_1 \OpUNION P_2)$ & $(P_1' \OpUNION P_2')$ \\ \hline
@@
 
+\noindent
+It is easy to see that our conversion function $\fctDescentWP{w}{P}$ replaces any \SPARQLplus-spe\-cif\-ic syntax element in $P$ by elements from the usual SPARQL syntax (defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}).
+Thus:
+
 \begin{proposition} \label{Proposition:EquivalenceOfSyntaxAfterConverting}
-	For any {\SPARQLplus} expression $P$ any RDF compatible expression of $P$ is an (ordinary) SPARQL expression.
+	For any {\SPARQLplus} expression $P$ any ($w$-based) RDF compatible expression of $P$ is an ordinary SPARQL expression (for all possible $w$).
 \end{proposition}
@@
 		\removable{of the form}
-	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEvalPlus{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescent{P}^w$ of $P$.
+	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEvalPlus{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescentWP{w}{P}$ of $P$.
 \end{proposition}
@@
 		\removable{of the form}
-	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEval{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescent{P}^w$ of $P$.
+	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEval{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescentWP{w}{P}$ of $P$.
 \end{corollary}

### 2012-06-06 trunk/paper-iswc-reification/rep.tex
elaborated a bit more on minizing RDF* graphs

@@
 
-\begin{example}
+\begin{example} \label{Example:ConvertingRDFplusToRDF}
 	Let $G_\mathsf{ex} = \lbrace t_\mathsf{ex} \rbrace$ be an {\RDFplusGraph} that consists of a single {\RDFplusTriple} $t_\mathsf{ex} = \bigl( (\mathTinyRDF{ex:olaf},\mathTinyRDF{foaf:name},\mathTinyRDF{"Olaf"}), \mathTinyRDF{dct:source}, \mathTinyRDF{ex:olaf} \bigr)$.
@@
 
+Using such an interpretation it is easy to see that for each {\RDFplusGraph} $G$ exists a \emph{minimum base} $G^-$ of $G$ that is the minimum of all possible sets $G' \subseteq G$ for which $\fctDescent{G'} = \fctDescent{G^+}$.
+$G^-$ may be computed by removing any $t \in G$ from $G$ for which exists another $t' \in G$ such that $t \in \fctTermsPlus{t'}$.
+
 \subsection{Representation}

### 2012-06-06 trunk/paper-iswc-reification/commands.tex
first draft of the data model section
added example to the query section

@@
 
-\newcommand{\RDFplus}{RDF$^{\mathsf{\text{\tiny +\!meta}}}$}
-\newcommand{\RDFplusTriple}{{\RDFplus} triple}
+\newcommand{\xxxPLUS}% % don't use that; it is required to define \RDFplus and \SPARQLplus
+	%{$^{\mathsf{\text{\tiny +\!meta}}}$}
+	{$^\star$}
+
+\newcommand{\Reifi}{Reifi}
+\newcommand{\ReifiPlus}{Reifi\xxxPLUS}
+\newcommand{\RDFplus}{RDF\xxxPLUS}
+\newcommand{\SPARQLplus}{SPARQL\xxxPLUS}
+
+\newcommand{\RDFplusTriple}{{\RDFplus}\! triple}
+\newcommand{\RDFplusGraph}{{\RDFplus}\! graph}
+\newcommand{\TPplus}{tri\-ple\xxxPLUS pattern}
 
@@
 
+\newcommand{\TRefPtt}{{\TRef} pattern}
+\newcommand{\TRefPttLongVersion}{{\TRefLongVersion} pattern}
+
 %%% relevant math symbols
@@
 
+\newcommand{\symDomFct}{\mathrm{dom}} % the name used for \fctDom
+\newcommand{\fctDom}[1]{\symDomFct(#1)} % the domain of function/mapping #1
+
 \newcommand{\symAllURIs}{\mathcal{U}} % the symbol for the set of all URIs
@@
 \newcommand{\symAllVariables}{\mathcal{V}} % the symbol for the set of all query variables
-	\newcommand{\symAllTRefsInfinite}{\mathcal{R}} % don't use that; it was required to define \symAllTRefs
+
+	\newcommand{\symAllTriplesInfinite}{\mathcal{T}} % don't use that; it is required to define \symAllTriples
+\newcommand{\symAllTriples}{\overline{\symAllTriplesInfinite}} % the symbol for the set of all triple references
+	\newcommand{\symAllTPsInfinite}{\mathcal{TP}} % don't use that; it is required to define \symAllTPs
+\newcommand{\symAllTPs}{\overline{\symAllTPsInfinite}} % the symbol for the set of all triple references
+
+	\newcommand{\symAllTRefsInfinite}{\mathcal{R}} % don't use that; it is required to define \symAllTRefs
 \newcommand{\symAllTRefs}{\overline{\symAllTRefsInfinite}} % the symbol for the set of all triple references
+	\newcommand{\symAllTRefPttsInfinite}{\mathcal{RP}} % don't use that; it is required to define \symAllTRefPtts
+\newcommand{\symAllTRefPtts}{\overline{\symAllTRefPttsInfinite}} % the symbol for the set of all triple reference patterns
 
 \newcommand{\symTermsFct}{\mathrm{terms}} % the name used for \fctTerms
-\newcommand{\fctTerms}[1]{\symTermsFct(#1)} % the set of all terms in triple/graph #1
+\newcommand{\fctTerms}[1]{\symTermsFct(#1)} % the set of all terms in triple #1
 
-\newcommand{\symTRefFct}{\mathrm{trefs}} % the name used for \fctTref
-\newcommand{\fctTRef}[1]{\symTRefFct(#1)} % the set of all triple references in triple/graph #1
+\newcommand{\symTermsPlusFct}{\symTermsFct^+} % the name used for \fctTermsPlus
+\newcommand{\fctTermsPlus}[1]{\symTermsPlusFct\!(#1)} % the set of all terms in triple #1 and its embedded triples
 
-\newcommand{\symDerefFct}{\mathit{deref}} % the name used for \fctDeref
-\newcommand{\fctDeref}[1]{\symDerefFct(#1)} % the triple denoted by triple reference #1
+\newcommand{\symTRefsFct}{\mathrm{trefs}} % the name used for \fctTrefs
+\newcommand{\fctTRefs}[1]{\symTRefsFct(#1)} % the set of all triple references in triple/graph #1
+
+% \newcommand{\symDerefFct}{\mathrm{deref}} % the name used for \fctDeref
+% \newcommand{\fctDeref}[1]{\symDerefFct(#1)} % the triple denoted by triple reference #1
+
+% \newcommand{\symCloseFct}{\mathrm{cl}} % the name used for \fctClose
+% \newcommand{\fctClose}[1]{\symCloseFct(#1)} % the tref-closure of #1
+
+\newcommand{\symVarsFct}{\mathrm{vars}} % the name used for \fctVars
+\newcommand{\fctVars}[1]{\symVarsFct(#1)} % the set of all variables in pattern #1
+
+\newcommand{\symVarsPlusFct}{\mathrm{vars}^+} % the name used for \fctVarsPlus
+\newcommand{\fctVarsPlus}[1]{\symVarsPlusFct\!(#1)} % the set of all variables in pattern #1 and its embedded patterns
+
+\newcommand{\symDescentFct}{\mathrm{rdf}} % the name used for \fctDescent
+\newcommand{\fctDescent}[1]{\symDescentFct(#1)} % set of RDF triples for an RDF+ triple/graph
+\newcommand{\fctDescentWP}[2]{\symDescentFct^{#1}\!(#2)} % the #1-based, RDF compatible expression of #2
 
 \newcommand{\mathTinyRDF}[1]{\texttt{\footnotesize #1}}
+
+\newcommand{\OpAND}{\text{ \normalfont\scriptsize\textsf{AND} }}
+\newcommand{\OpUNION}{\text{ \normalfont\scriptsize\textsf{UNION} }}
+\newcommand{\OpOPT}{\text{ \normalfont\scriptsize\textsf{OPT} }}
+\newcommand{\OpFILTER}{\text{ \normalfont\scriptsize\textsf{FILTER} }}
+\newcommand{\OpAS}{\text{ \normalfont\scriptsize\textsf{AS} }}
+\newcommand{\OpSELECT}{\text{\normalfont\scriptsize\textsf{SELECT}}}
+\newcommand{\compatible}{\sim} % the symbol for compatibility between valuations
+\newcommand{\fctEvalPlus}[2]{[\![#1]\!]^\star_{#2}} % the symbol for the evaluation of SPARQL* pattern #1 over an RDF* graph #2
+\newcommand{\fctEval}[2]{[\![#1]\!]_{#2}} % the symbol for the evaluation of SPARQL pattern #1 over an RDF graph #2
+
+%% The following definitions of a symbol for left outer join work best in Springer format:
+\def\ojoin{\setbox0=\hbox{$\Join$}\rule[.01ex]{.25em}{.45pt}\llap{\rule[1.05ex]{.25em}{.4pt}}}
+\def\LJoin{\mathbin{\ojoin\mkern-7.5mu\Join}}

### 2012-06-06 trunk/paper-iswc-reification/querying.tex
added example to the query section

@@
 A \emph{\TPplus} is a tuple $tp \in \symAllTPsInfinite$ for which exists a natural number $k$ such that $tp$ is $k$-nested\footnote{$k$-nestedness for $\symAllTPsInfinite$ is defined analog to $k$-nestedness for $\symAllTriplesInfinite$.}; to denote the set of all {\TPplus}s we write $\symAllTPs$ (i.e.~$\symAllTPs \subset \symAllTPsInfinite$).
-%	%To denote the set of all variables in a {\TPplus} $tp=(s,p,o)$ we write $\fctVarsPlus{tp}$; hence, $\fctVarsPlus{tp} := (\lbrace s,p,o \rbrace \cap \symAllVariables) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
-%	For any {\TPplus} $tp \!=\!
-(s,p,o)$ we define $\fctVarsPlus{tp} := \bigl( \lbrace s,p,o \rbrace \cap \symAllVariables \bigr) \cup \big\lbrace ?v \in \fctVarsPlus{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$ and $\fctTRefs{tp} := \bigl( \lbrace s,o \rbrace \cap \symAllTPs \bigr) \cup \big\lbrace tp \in \fctTRefs{x} \,\big|\, x \in \lbrace s,o \rbrace \cap \symAllTPs \big\rbrace$.
 
@@
 
+\begin{example} \label{Example:SPARQLplusExpression}
+		The following {\SPARQLplus} expression $P_\mathsf{ex}$ represents the query from Example~\Todo{X}{refer to the informal example that appears in the intro or in the discussion section before}:
+		%We represent the query from Example~\Todo{X}{refer to the informal example that appears in the intro or in the discussion section before} using {\SPARQLplus} expression $P_\mathsf{ex}$:
+	%
+		%$\bigl( (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}), \mathTinyRDF{dct:source} , ?\mathit{src} \bigr)$.
+		$\bigl( \, \bigl( (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}) \OpAS ?v \bigr) \OpAND (?v , \mathTinyRDF{dct:source} , ?\mathit{src}) \, \bigr)$.
+% 	Let $P_\mathsf{ex}$ be the {\SPARQLplus} expression that represents the query in Example~\Todo{X}{refer to the informal example that appears in the intro or in the discussion section before}, that is, $P_\mathsf{ex}$ is
+% 		%$\bigl( (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}), \mathTinyRDF{dct:source} , ?\mathit{src} \bigr)$.
+% 		\begin{equation*}\Bigl( \bigl( (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}) \OpAS ?v \bigr) \OpAND (?v , \mathTinyRDF{dct:source} , ?\mathit{src}) \Bigr)\end{equation*}
+	It holds $\fctVarsPlus{P_\mathsf{ex}} = \lbrace ?\mathit{who}, ?v, ?\mathit{src} \rbrace$ and $\fctTRefs{P_\mathsf{ex}} = \big\lbrace (?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase}) \big\rbrace$.
+\end{example}
+
 \subsection{({\RDFplus} Based) Semantics of {\SPARQLplus}}
-	To define the semantics of {\SPARQLplus} we introduce
-	%We define the semantics of {\SPARQLplus} based on
-\emph{valuation}s, that are, partial mappings $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
-Two valuations $\eta$ and $\eta'$ are \emph{compatible}, denoted by $\eta \compatible \eta'$, if for all $?v \in \fctDom{\eta} \cap \fctDom{\eta'}$ holds $\eta(?v) = \eta'(?v)$; note,
-	%$\fctDom{\eta}$ denotes
-	$\fctDom{\eta}$~denotes %% Layout Adjustment
-the domain of a valuation $\eta$.
+To define the semantics of {\SPARQLplus} we introduce \emph{valuation}s, that are, partial mappings $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$.
+Two valuations $\eta$ and $\eta'$ are \emph{compatible}, denoted by $\eta \compatible \eta'$, if for all $?v \in \fctDom{\eta} \cap \fctDom{\eta'}$ holds $\eta(?v) = \eta'(?v)$; note, $\fctDom{\eta}$ denotes the domain of a valuation $\eta$.
 
@@
 
+\todo{adjust the following example once the previous examples are fixed}
+\begin{example} \label{Example:SPARQLplusEvaluation}
+	The evaluation of {\SPARQLplus} expression $P_\mathsf{ex}$ (cf.~Example~\ref{Example:SPARQLplusExpression}) over the {\RDFplusGraph} $G_\mathsf{ex}$ from Example~\ref{Example:ConvertingRDFplusToRDF} consists of a single valuation
+		%$\eta_1$ (i.e.~$\fctEvalPlus{P_\mathsf{ex}}{G_\mathsf{ex}} = \lbrace \eta_1 \rbrace$)
+		$\eta_1 \in \fctEvalPlus{P_\mathsf{ex}}{G_\mathsf{ex}}$
+	such that $\fctDom{\eta} = \lbrace ?\mathit{who}, ?v, ?\mathit{src} \rbrace$ and $\eta(?\mathit{who})=\mathTinyRDF{:who}$, $\eta(?v)=(\mathTinyRDF{:who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase})$, and $\eta(?\mathit{src})=\mathTinyRDF{:src}$.
+\end{example}
+
 \noindent
@@
 
-\todo{Motivate the following proposition (it is cool because it shows that we may reduce queried {\RDFplus} data to a minimum base and it nicely corresponds to Proposition~\ref{Proposition:JustificationForDataMinimality1}}
-
-\begin{proposition} \label{Proposition:JustificationForDataMinimality2}
-	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
-\end{proposition}
-
-\todo{There is a minimal $G_\mathsf{min} \subseteq G$ with $G_\mathsf{min} = G^+$ ...}
+% \todo{Motivate the following proposition (it is cool because it shows that we may reduce queried {\RDFplus} data to a minimum base and it nicely corresponds to Proposition~\ref{Proposition:JustificationForDataMinimality1}}
+% 
+% \begin{proposition} \label{Proposition:JustificationForDataMinimality2}
+% 	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ it holds $\fctEvalPlus{P}{G} = \fctEvalPlus{P}{G^+}$ where $G^+ = G \cup \fctTRefs{G}$.
+% \end{proposition}
+% 
+% \todo{There is a minimal $G_\mathsf{min} \subseteq G$ with $G_\mathsf{min} = G^+$ ...}
 
@@
 Let $P$ be a {\SPARQLplus} expression.
-We assume an \removable{(arbitrary)} injective function $v : \fctTRefs{P} \rightarrow \symAllVariables \cap \fctVarsPlus{P}$.
+	%We
+	For converting $P$ to a SPARQL expression we
+assume an \removable{(arbitrary)} injective function $v : \fctTRefs{P} \rightarrow \symAllVariables \cap \fctVarsPlus{P}$.
 Furthermore, we introduce another injective function $w : (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals) \rightarrow (\symAllVariables \cup \symAllURIs \cup \symAllLiterals)$ that is defined as follows: Let $x \in (\symAllVariables \cup \fctTRefs{P} \cup \symAllURIs \cup \symAllLiterals)$.
@@
 
+\noindent
+It is easy to see that our conversion function $\fctDescentWP{w}{P}$ replaces any \SPARQLplus-spe\-cif\-ic syntax element in $P$ by elements from the usual SPARQL syntax (defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}).
+Thus:
+
 \begin{proposition} \label{Proposition:EquivalenceOfSyntaxAfterConverting}
-	For any {\SPARQLplus} expression $P$ any RDF compatible expression of $P$ is an (ordinary) SPARQL expression.
+	For any {\SPARQLplus} expression $P$ any ($w$-based) RDF compatible expression of $P$ is an ordinary SPARQL expression (for all possible $w$).
 \end{proposition}
+
+\todo{adjust the following example once the previous examples are fixed}
+\begin{example} \label{Example:ConvertingSPARQLplusToSPARQL}
+% 	Let $tp_\mathsf{ex}$ be the embedded {\TPplus} $(?\mathit{who},\mathTinyRDF{:bought},\mathTinyRDF{:sybase})$ from Example~\ref{Example:SPARQLplusExpression} (i.e.~$tp_\mathsf{ex} \in \fctTRefs{P_\mathsf{ex}}$) and let $w(tp_\mathsf{ex})=?v$.
+	For the {\SPARQLplus} expression $P_\mathsf{ex}$ from Example~\ref{Example:SPARQLplusExpression} holds that $\fctDescentWP{w}{P_\mathsf{ex}}$ is:
+	\begin{align*}
+		\bigl( \bigl( \bigl( \bigl( & (?v,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}) \OpAND (?v,\mathTinyRDF{rdf\!:\!subject},?\mathit{who}) \bigr) \OpAND \\
+		& (?v,\mathTinyRDF{rdf\!:\!predicate},\mathTinyRDF{:bought}) \bigr) \OpAND (?v,\mathTinyRDF{rdf\!:\!object},\mathTinyRDF{:sybase}) \bigr) \bigr) \OpAND \\
+		& (?v , \mathTinyRDF{dct:source} , ?\mathit{src}) \bigr)	
+	\end{align*}
+\end{example}
 

### 2012-06-07 trunk/paper-iswc-reification/mainext.tex
added a second version of the paper that is meant to become the extended version with an appendix that contains all proofs

--- 2012-05-11 paper-iswc-reification/paper.tex
@@
 %\sloppy
-\title{Efficient Management of Meta-level Information for RDF}
+\title{Efficient Management of Reified Statements in RDF}
+\subtitle{(Extended Version)\footnote{This report presents an extended version of a paper submitted to ISWC 2012. This extended version contains proofs for all
+	%propositions, lemmas, and theorems
+	technical results
+in the paper (cf.~\appendixname~\ref{Appendix:Proofs}).}
+% \vspace{-5mm} % Layout Adjustment
+}
 
@@
 \begin{abstract}
+\input{abstract}
 \end{abstract}
@@
 \input{intro}
+For full technical proofs of all propositions in this paper we refer to \appendixname~\ref{Appendix:Proofs}.
+
 \input{related}
+\input{dis}
 \input{rep}
 \input{querying}
-\input{dis}
 \input{exp}
@@
 \bibliography{paper}
+
+\newpage
+\appendix
+\input{proofs}
+
 \end{document}

### 2012-06-07 trunk/paper-iswc-reification/querying.tex
further clarification in the querying section

@@
 	%P\'{e}rez et al.~define
-the evaluation function $\fctEval{\cdot}{ }$ for ordinary SPARQL
+the evaluation function
+	%$\fctEval{\cdot}{ }$
+	$\fctEval{P}{G}$
+for ordinary SPARQL
 	%expressions~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
@@
 may also be understood as a solution mapping.
-Based on this understanding, the following result shows that our query semantics for {\SPARQLplus} is fully compatible to the usual SPARQL semantics (defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus} and {\SPARQLplus} may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.
+Based on this understanding, the following result shows that our query semantics for {\SPARQLplus} is backwards compatible w.r.t.~the usual SPARQL semantics (%
+	%as defined
+in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus} and {\SPARQLplus} may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.
 
@@
 
-In addition to the {\SPARQLplus} semantics defined in the previous section, we now define
-	%an alternative semantics for {\SPARQLplus}. This alternative semantics
-	a function for converting {\SPARQLplus} queries to SPARQL queries. This conversion function
-enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.
+In addition to the {\SPARQLplus} semantics defined in the previous section, we now define an approach for answering {\SPARQLplus} queries using the usual SPARQL semantics.
+This approach is based on a function for converting {\SPARQLplus} queries to SPARQL queries.
 
@@
 The following result is a direct consequence of Propositions~\ref{Proposition:EquivalenceOfSemantics}, \ref{Proposition:EquivalenceOfSyntaxAfterConverting}, and~\ref{Proposition:QueryEquivalenceAfterConverting}:
-\begin{corollary}
+
+\begin{corollary} \label{Corollary:EquivalenceSPARQLplusAndSPARQL}
 	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ that does not contain a sub-expression
@@
 \noindent
-\todo{briefly discuss the Corollary}
+The importance of Corollary~\ref{Corollary:EquivalenceSPARQLplusAndSPARQL} lies in providing an alternative approach for answering {\SPARQLplus} queries (without $\OpAS$\!) that is based on the usual SPARQL semantics only.
+This approach presents an easy implementable interim solution for supporting {\SPARQLplus} in existing SPARQL execution systems before they are upgraded to our {\RDFplus} data model.

### 2012-06-07 trunk/paper-iswc-reification/rep.tex
some clarification and a layout improvement

@@
 
-In this section we introduce
-	%an extension of the RDF data model~\cite{Klyne04:RDFconcepts} that makes 
-	our data model which we call {\RDFplus}.
-This model is an extension of the RDF data model~\cite{Klyne04:RDFconcepts}.
-{\RDFplus} extends RDF by making metadata statements a first class citizen in the data model.
+This section introduces our data model which we call \emph{\RDFplus}.
+{\RDFplus} extends the RDF data model~\cite{Klyne04:RDFconcepts} by making metadata statements a first class citizen in the data model.
 % In the following we \todo{...}
@@
 
-{\RDFplus} extends such triples by permitting the embedding of another triple in the subject or object position of a given triple.
-We shall interpret the embedding triple as a statement about the embedded triple.
-An embedded triple may itself be a statement about a triple and, thus, may also contain embedded triples; and so forth.
+{\RDFplus} extends such triples by permitting the embedding of a given triple in
+	%the subject 
+	the~subject %%% Layout Adjustment
+or object position of another triple. We shall interpret the embedding triple
+	%as a statement
+	as~a~statement %%% Layout Adjustment
+about the embedded triple. An embedded triple may itself be a statement about a triple and, thus, may also contain embedded triples; and so forth.
 	%Therefore, the model should allow for nesting.

### 2012-06-23 trunk/tr-rankingsurvey/intro.tex

\section{Introduction}\label{sec:intro}

\paragraph{Outline}

### 2012-06-23 trunk/tr-rankingsurvey/paper.tex

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
%%!PS-Adobe-3.0 EPSF-3.0
%%%BoundingBox: 19 19 221 221
%%%CreationDate: Mon Sep 29 1997
%%%Creator: programmed by hand (JK)
%%%EndComments
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
%%
%\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

\usepackage{graphicx,amssymb,subfig}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{latexsym}
\usepackage{verbatim}
\usepackage{xspace}
\usepackage{algorithm}
\usepackage{float}
\usepackage{multirow} 
\usepackage{bigstrut}
%\usepackage{algorithmic}
%hola
\usepackage{amstext} % for text in math forumla
\usepackage{indentfirst} % make the first paragraph also indent

%\newtheorem{definition}{Definition}
%\newtheorem{example}{Example}
%\newtheorem{proposition}{Proposition}
\newcommand{\dtr}[1]{(\textbf{Thanh: #1})}

\begin{document}

\title{A Survey of Approaches for Ranking on Structured Data%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{First Author         \and
        Second Author %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Style}
\label{sec:1}
Text with citations \cite{RefB} and \cite{RefJ}.
\subsection{Subsection title}
\label{sec:2}
as required. Don't forget to give each section
and subsection a unique label (see Sect.~\ref{sec:1}).
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

\input{intro}
\input{overview}
\input{approaches}
\input{relevance}
\input{popularity}
\input{other}
\input{ltr}
\input{sample}
\input{future}

\section{Conclusion}\label{sec:conclusion}
For consistency, we use bibtex entries from dblp, e.g. \url{http://www.dblp.org/rec/bibtex/conf/sigmod/BalminKT12}. Many bibtex entries are already in the paper.tex file so just searched for these entries there first and add only new entries when needed to avoid redundancy.

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics

\bibliography{paper}   % name your BibTeX data base

% Non-BibTeX users please use
%\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
%\bibitem{RefJ}
% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
%\end{thebibliography}

\end{document}
% end of file template.tex

### 2012-06-23 tr-rankingsurvey/approaches.tex

\section{Ranking Approaches}

\subsection{Historical Development}

\subsection{Generic Architecture}

\subsection{Main Dimensions} 
Features: content, structure, context, two meanings of context: context of user; and context of the data such as trust values of source, truth value / confidence degree of individual records; make clear this survey does not discuss user-context based methods in details\\
Results: entity, relationships, subgraphs, graphs (entire dataset)\\
Techniques:\\
- may vary in terms of methods: used \emph{NLP} for understanding keywords, used \emph{ML} for classifying keywords (I know some ML-based query classification approaches for document retrieval, are there also examples for structured data ranking?) and for learning to rank, (other) statistics-based methods: Vector Space Model (VSM), Language Modeling (LM), Information Theory\\
- may vary in terms of heuristics: two main ones are query-relevance and popularity; other heuristics are proximity, informativeness (based on Information Theory, e.g. entropy) and context-based: trust, truth value, locality etc.

\subsection{Foundation}
Here we discuss all basics needed to understand the approaches presented in the following sections.\\
Vector-Space Model: also discuss pivoted normalization and point out problems of short document length etc. in the context of structured data\\
Language Modeling: also discuss smoothing strategies\\
Link Analysis\\
Learning to Rank\\
...

\subsection{Taxonomy of Ranking Approaches}
Classify approaches mainly based on the type of \emph{heuristics} they used. Those that use same heuristics are distinguished in terms of \emph{methods}. E.g. Query-relevance based solutions can be further distinguished in terms of VSM-based and LM-based approaches.\\

### 2012-06-23 tr-rankingsurvey/overview.tex

\section{The Ranking Problem}\label{sec:ranking}

\subsection{Ranking on Structured Data}
Structured data: can be conceived as graphs\\
Ranking: traditionally, core IR problem, many techniques have been adopted to deal with structured data\\
Ranking over structured data: ranked list of results\\
Types of ranked results: entities, relations, subgraphs, entire datasets (graphs)\\
Evaluating ranked results: different metrics\\

\subsection{Ranking on Structured Data vs. Ranking on Unstructured Data}
Discuss differences\\
Say we focus on structured data\\

\subsection{Ranking vs. Matching}
Discuss differences\\
Say we focus on ranking\\

\subsection{Applications} 
Optional / can be short but should provide good coverage of different application domains

### 2012-06-23 tr-rankingsurvey/sample.tex

\section{Sample Approaches from the Literature}
Before, we discuss the concepts/techniques behind existing approaches. Here we provide a sample

### 2012-06-26 trunk/tr-nlisurvey/src/document.tex

\documentclass[10pt,journal,letterpaper,compsoc]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[12pt,journal,compsoc]{../sty/IEEEtran}

% added packages
\usepackage{multirow}
\usepackage{url}

\ifCLASSOPTIONcompsoc

\else

\fi

\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
% declare the path(s) where your graphic files are
\graphicspath{{images/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
\DeclareGraphicsExtensions{.png}
\else

\fi

%
\usepackage{array}

\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand{\TODO}[1]{{\textcolor{green}{TODO:#1}}}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Natural Language Interfaces to Structured Data}

\author{Author 1, Author 2, Author 3}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~6, No.~1, January~2007}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
Abstract will be written later\ldots
\end{abstract}

\begin{keywords}
Computer Society, IEEEtran, journal, \LaTeX, paper, template.
\end{keywords}}

% make the title area
\maketitle

\IEEEdisplaynotcompsoctitleabstractindextext

\IEEEpeerreviewmaketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  INTRODUCTION                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}

%{\bf Possible quotation:} M.P. Schutzenberger, 1970: (in the AI domain: humans
%learn how to use systems, see the usage of Google, keywords etc.)

Natural Language (NL) is the most natural and easy way to express information
need~\cite{Hearst:2011:NSU:2018396.2018414}. Moreover, it is not restricted to
experts who have a good knowledge on how to formulate a formal query.

NL as an interface has been investigated by researchers in both Information
Retrieval (IR) and Database communities. In the IR community however, the
keyword paradigm has become the most popular, for sure because of the success of
commercial search engines. NL interfaces for unstructured documents are
refered to as Question Answering (Q\&A) systems, that have received much
researchers' attention as the Web had made avaialble huge amount of textual
data, and recently as the famous {\it Jeopardy!} quiz was won by IBM's {\sc
Watson}~\cite{FerrucciBCFGKLMNPSW10} system.
{\sc WolframAlpha}\footnote{\url{http://www.wolframalpha.com/}} is a popular
search service based on structured data, that accepts keyword queries as well
as some questions in natural language.

NL interfaces (to structured data) has focused much researchers' attention for
decades, but the field seems to have known a renewed interest for a few
years, probably thanks to the development of the semantic Web. {\bf See also
the quotation in~\cite{DBLP:journals/semweb/LopezUSM11}: users prefer NL interfaces
than logic used in the Semantic Web.}
However, the challenge of answering NL
questions is far from being solved~\cite{Kotov:2010:TNQ:1772690.1772746}.

NL interface: not only in the context of search (information retrieval), for
instance natural language query can be translated in goals / commands in the
context of (household) appliances (see {\sc
Exact}~\cite{Yates:2003:RNL:604045.604075}, not surveyed here).

In this survey, we try to point out the major dimensions of existing systems
and to present the new trends and challenges of state-of-the-art systems.
The history of NL interfaces can be developped as follows:
\begin{enumerate}
  \item early years of domain-specific systems
  \item complex question answering in a specific domain
  \item rise of domain awareness in NL interfaces (through learning techniques)
  \item data-driven systems with respect to
  \begin{itemize}
    \item resources: almost domain-independent systems
    \item large-scale data: domain-independent systems
  \end{itemize}
\end{enumerate}

We will present the ``big picture'' of the approaches in
section~\ref{sec:big-picture}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BIG PICTURE                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Main Dimensions}
In this section, we introduce the main dimensions based on which NLI approaches can be distinguished. The input to every NLI is the (1) \emph{data}, 
and (2) \emph{user questions} representing information needs, which are translated to an (3) \emph{internal representation} of the needs employed by the system and/or directly mapped to 
(4) \emph{database queries} that finally, are executed by the underlying query engine to produce the final answers. The main problem tackled by a NLI approach is to transform the question to the internal representation and then to the database query (2 $\mapsto$ 3 $\mapsto$ 4), or to directly mapped the question to the query (2 $\mapsto$ 4). This problem is hard when considering the large and rapidly evolving mass of structured data that have become available. The major challenges modern NLI systems are facing in this regard is to operate across domains (5, \emph{domain-independence}) as well as to adopt to new domains (6, \emph{portability}). For evaluating the quality of the NLI output, different (6) \emph{metrics} based on the user questions the system can understand as well as the database queries it can produce, have been proposed.

----------
\TODO{old content that might be considered:}
Dimensions:
\begin{itemize}
  \item What kind of query? (NL, controlled language)
  \item What are the data? 
  \item Target structured query: select query? update query?
  \item What are the answers?
  \item How portable is the system? Does it improve its performance over time?
  \item What is the linguistic coverage of the system? 
  \item Error feedback: how well is the user informed of misunderstanding of her
  question
  \item Predictability: how the system disambiguates / lets the user decide what
  should be the correct interpretation
  \item Performance: response time / evaluation metrics
\end{itemize}

----------

\subsection{Data}
\label{sec:data}
\TODO{Discuss the different types of structured data models that have been used, make clear that while they vary in expressiveness, they commonly enables capturing resources/entities/objects and relationships between then. Besides domain information captured in terms of entities and relationships, also point out other popular types of information that have considered, e.g. temporal and spatial information}

Structured data:
\begin{itemize}
  \item relational databases; data warehouses
  \item XML databases
  \item early data structures (Prolog databases; list-structured databases)
  \item ontologies; {\it linked data}
\end{itemize}
%Data structured in a database belong to a {\it domain}\ldots
In the survey, we refer to {\it database elements} which stand for named
properties of the database. For instance in a relational database, they stand
for relation names, attributes names and values, \ldots

Data structures are associated with a data model or schema, which is explicitely
defined in modern databases.
Despite the effort of modeling and conceptualizing structured data, there is
still a gap between the physical view of structured data (database
administrators' view point) and the conceptual view of end users; interfaces
concerned in this survey attempt to bridge this gap.

\subsection{Question}
\TODO{Discuss different types user questions}

\label{sec:big-picture-question}
Traditional database management systems provide an interface that allows users
to query the data in a formal language (e.g., SQL).
\subsubsection{Keyword query}
A {\it keyword query} consists in a set of words
traditionally used in the context of document search (i.e. searching relevant
documents given a textual query).
The classic idea is to represent documents in a vector model, where the vector
is composed of terms of documents. Search engines have made this paradigm
popular.
\cite{Hearst:2011:NSU:2018396.2018414} reports that the number of words
in queries over Web search engines trends to increase (the experiment compared
queries performed over a month in 2009 and in 2010): queries from 5 to 8 words
increase up to 10\% while queries from 1 to 4 words decrease up to 2\%.
It seems indeed that users are more and more aware of new capabilities of
state-of-the-art search engines, and are less reluctant to express their
information need in a more ``natural'' way.

\subsubsection{Natural language query}
Early systems understood some English words and English syntactic constructions;
such language was called ``English-like'' by
authors~\cite{Woods:1973:PNL:1499586.1499695}. More recent systems try to go
further and to capture as much as possible the regularities as well as the
irregularities of NL.

Current systems handle only a subset of NL questions (the questions that the
system can understand). This ``subset'' of NL is called controled NL. Some
systems even go further, and are able to analyze why a question can not be
answered. It could be out of coverage of linguistic understanding of the system
(the question is not understood) or cannot be answered because the knowledge
base does not contain the answer (even if the semantics of the question is
fully captured).

Users prefer NL questions than keywords~\cite{Hearst:2011:NSU:2018396.2018414}.
In this survey, we focus on natural language interfaces, and not on keyword
search over structured data, even if the latter has become more popular
lately\footnote{Paper to be published at VLDB 2012: ``SODA: Generating SQL for
Business Users'' from Blunschi et al.: Keyword-based interface to data
warehouses}.

\subsection{Internal Representation}
\label{sec:big-picture-syntactic}
\TODO{Discuss different types user questions}

Syntactic question representation (also called {\it parse tree} because the
tree graph structure is used most of the time) is an intermediate
representation, before the creation of the internal semantic representation. In
lots of systems, however, the syntactic representation also contain semantic
pieces of information: nodes of the syntactic tree contain information about how
to generate fragments of the target database query. 
The nodes of the tree representation contain information about words and
relations between words of the question. 
Typical semantic information contained in a syntactic parse tree are the
database elements that those words refer to. 
Those semantic information (also referred to as ``meaning'' in early systems)
are kept in a lexicon. 
The syntactic parse tree usually does not try to resolve
ambiguities, and keep all possible interpretations. Resolution of ambiguities
is done afterward, when building the semantic representation out of the
syntactic representation.

\subsection{Database Query}
\label{sec:big-picture-semantic}
\TODO{Discuss query languages; discuss the different types of queries expressed by these languages, e.g. entity queries, relational queries, additional constructs such as group by etc.}

The parse tree (which may or not contain semantic information in parse tree
nodes) must then be {\it interpreted} in some internal semantic representation.
Table~\ref{tab:semantic-meaning-representation} displays semantic meaning
representations used in different systems.
\begin{table*}[!h]
\centering
\begin{tabular}{|c|c|c|}\hline
{\bf System} & {\bf Internal representation} & {\bf DB query}\\\hline\hline
{\sc Baseball}~\cite{Green:1961:BAQ:1460690.1460714} & specification list &
$\surd$\\\hline
{\sc Lunar}~\cite{Woods:1973:PNL:1499586.1499695} & meaning representation
language & X\\\hline 
{\sc Chat-80}~\cite{Warren:1982:EEA:972942.972944} &
logic expression & X\\\hline
{\sc Team}~\cite{Grosz:1987:TED:25672.25674} & logic expression & X\\\hline
{\sc Qwerty}~\cite{Nelken:2000:QTD:992730.992808} & logic expression & X\\\hline
{\sc Irus}~\cite{Bates:1983:IRU:511793.511804} & meaning representation language
& X\\\hline
{\sc Precise}~\cite{Popescu:2003:TTN:604045.604070} & graph representation &
X\\\hline
{\sc Masque/SQL}~\cite{Androutsopoulos93masque} & meaning representation
language (LQL) & X \\\hline 
{\sc NaLIX} \& {\sc
DaNaLIX}~\cite{Li:2005:NIN:1066157.1066281,Li:2007:DDN:1247480.1247643} & XQuery
& $\surd$\\\hline 
{\sc C-Phrase}~\cite{Minock:2010:CSB:1715942.1716190} & $\lambda$-calculus & X
\\\hline
{\sc Panto}~\cite{Wang:2007:PPN:1419662.1419706} & graph representation (query
triples) & X\\\hline 
{\sc Orakel}~\cite{Cimiano:2007:PNL:1216295.1216330} & $\lambda$-calculus &
X\\\hline
Miller et al.~\cite{Miller:1996:FSA:981863.981871} &
semantic frames & X\\\hline 
Zettlemoyer et
Collins~\cite{DBLP:conf/uai/ZettlemoyerC05} & $\lambda$-calculus &
$\surd$\\\hline 
{\sc Wolfie}~\cite{Thompson:2003:AWM:1622420.1622421} & Prolog & $\surd$
\\\hline {\sc PowerAqua}~\cite{DBLP:conf/esws/LopezMU06} & graph representation
(query triples) & X\\\hline
{\sc DeepQA}~\cite{FerrucciBCFGKLMNPSW10} & semantic triples & $\surd$\\\hline
\end{tabular}
\caption{Semantic meaning representations}
\label{tab:semantic-meaning-representation}
\end{table*}
As shown in this table, the internal semantic representation can be or not the
targetted query representation. 
The expressivity of the database query is discussed in section
section~\ref{sec:big-picture-expressivity}. 
The semantic representation is intented to capture as much as possible users'
intent, and is sufficient to generate the final database query. 
While the syntactic representation may contain lots of ambiguities, the semantic
representation does not. 
The semantic representation depends on the data structure. However, to
demonstrate their portability features, some systems contain components that
can translate the semantic representation for different database query
languages.

TOBECONSIDERED
-------
\subsubsection{Expressivity of database query}
\label{sec:big-picture-expressivity}
-----------

\subsection{Results}
\label{sec:big-picture-results}
NL interfaces produce database queries.
Those queries must be then be executed by underlying DBMS.
The execution of queries can lead to different failing states:
\begin{itemize}
  \item the query execution fails (the generated database query is not valid)
  \item the query execution lead to an empty result set
\end{itemize}
In these cases, the system may inform the user and/or suggest/rephrase the
query. This is especially performed in systems belonging to the feedback
approach (see section~\ref{sec:feedback-driven}).

\subsection{Query-independence}
\subsection{Portability}

\subsection{Metrics}
\label{sec:big-picture-metrics}
Several evaluation metrics have been introduced in various systems. We review
them briefly below.
We present the interesting figure~\ref{fig:interface} copied from Han et al.
work~\cite{Han:2010:NLI:1719970.1720022}. It shows the tradeoff between
linguistic coverage (``Expressions interpretable by a System'') and the
expressions that can be answered from a knowledge base. The goal of any
interface would be that the linguistic coverage comprises all expressions that
can be answered by the knowledge base.

 \begin{figure}[!h]
\centering
\includegraphics[width=8cm]{images/interface}
\caption{Linguistic coverage vs. logical coverage within interfaces, copied
from~\cite{Han:2010:NLI:1719970.1720022}}
\label{fig:interface}
\end{figure}

\subsubsection{Fluency$_{Woods}$}
Woods~\cite{Woods:1973:PNL:1499586.1499695} defines {\it fluency} as ``the degree
to which virtually any way of expressing a given request is acceptable''.
Fluency measures roughly how easy to use is a system. 
Intuitively, a good fluency means a ``natural'' interface in the sense of
natural interfaces~\cite{Hearst:2011:NSU:2018396.2018414}. This requires
advanced natural language techniques, and would probably lead to systems that
can interpret more expressions than those that can be actually answered by the
knowledge base ($S\setminus K$ in figure~\ref{fig:interface} would not be
negligeable).

\subsubsection{Completeness$_{Woods}$}
{\it Completeness} was first defined in Woods' work related to the {\sc
Lunar}~\cite{Woods:1973:PNL:1499586.1499695} system. 
It measures if there is a way of expressing any query which is logically
possible from the database. In the end, it measures if the interface can answer
all possible questions. In figure~\ref{fig:interface}, completeness would be
represented by $S$ comprising $K$ ($K\subset S$).

\subsubsection{Soundness$_{Popescu}$}
An interface is said {\it sound} if ``any SQL output is a valid interpretation
of the input English sentence''~\cite{Yates:2003:RNL:604045.604075}. In
figure~\ref{fig:interface}, this evaluates the expressions of $V=S\cap K$.

\subsubsection{Completeness$_{Popescu}$}
An interface is said {\it complete} if it ``returns all valid interpretations of
input sentences''~\cite{Yates:2003:RNL:604045.604075}.
Yates et al. have reused this metrics in their {\sc Exact} system (not surveyed
here). They do not claim that users should restrict their questions to query
only tractable qestions; but they suggest that identifying classes of questions
that are semantically tractable and measuring the prevalence of these questions
is the direction of current research.

\subsubsection{User's intent}
Yates~\cite{Yates:2003:RNL:604045.604075} makes an assumption, that if the
interface is sound, complete and if a single SQL statement can be produced from
a NL question, then the interface has unambiguously determined user's intent.

\subsubsection{Predictability}
Within user interfaces, predictability has been pointed out as the essential
feature of user interfaces in the 90' by
Norman~\cite{Norman:1994:MPI:176789.176796} and Schneiderman et
Maes~\cite{Shneiderman:1997:DMV:267505.267514}. 
Predictability and the feel of control seems however to be in contradiction with
personalization, which is the one pillar of recent IR systems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ANATOMY OF SYSTEMS                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Anatomy of NLI systems}
\label{sec:anatomy}
The main problem to solve is to map user's intent expressed in a natural way
(say unstructured way) to a database query, which is a very structured
expression where there is no room for ambiguity unlike natural language.
As a result, all interfaces must deal with words or terms ``meaning''. This
``meaning'' or semantics is in the end defined in terms of ``database
elements''.

\subsection{Lexicon}
The lexicon is a data structure that is used to reduce the ambiguity in words
when analyzing users' questions. 
NLI are usually composed of two lexicons: a domain-dependant lexicon and a
domain-independant lexicon. 
The domain-dependant lexicon defines words in terms of semantic rules (see
section~\ref{sec:anatomy-semantic-rules}).
The domain-independant lexicon defines how to interpret words independant from a
given domain. For instance, {\it wh}-question words define constraints on the
structure of the expected database query (for SQL, for the ``WHERE'' statement
for instance).

\subsection{Semantic rules}
\label{sec:anatomy-semantic-rules}
Semantic rules define the semantics of question words. The input in a node, or a
part of the parse tree being constructed, and the output contains information on
how to construct part of the final database query. The final database query will
be generated from the parse tree, which contains semantic information in the
nodes, in addition to lexical and syntactic information. 
The idea behind this process is a linguistic theory [missing ref], where the
global meaning of a sentence is defined by the individual meanings of words /
expressions in the sentence, and by the syntactic relationships between the
words / phrases.

\subsection{Main problems to solve}
The main problems to solve:
\begin{itemize}
  \item have the boroadest linguistic coverage (let users use their own
  terminology)
  \item mechanisms that permit to query other domains with a low porting cost
  \item ensure that the resulting database query is valid
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OVERVIEW SECTION                    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Taxonomy of main approaches}
\label{sec:overview}

\subsubsection{Classic translation approach}
TOBECONSIDERED
----------
The classic translation approach consists in going from (1) to (4).
To reach step (3), semantic rules are needed to find out what database elements
should be associated to question phrases.

\subsubsection{Iterative approach}
The iterative approach does not go directly from (1) to (3), but goes back to
(1) several times before reaching step (3). 
Those iterations correspond to question reformulations, that involve
user-feedback to interpret semantically the question in terms of a database
query.

\subsubsection{Configurable interfaces}
Configurable interfaces let users improve the system's capabilities, in
particular the linguistic coverage. 
Minock et al.~\cite{Minock:2010:CSB:1715942.1716190} have identified three kinds
of configuration applicable to NL interfaces:
\begin{itemize}
  \item let users name database elements, so that phrases used in the question
  can be easily mathed with database elements
  \item offer a GUI that generates automatically semantic rules or a grammar for
  translating NL questions to database queries
  \item use machine learning techniques to induce semantic rules or a grammar
  from annotated corpora
\end{itemize}
The configuration is particularly important when porting the interface to other
domains. However the three kinds of configuration mentionned above are not
equally costly: for instance, the third one (machine learning techniques) can be
hightly costly if it requires a huge volume of annotated data. The cheapest
configuration is based on user interaction, where no initial configuration is
needed, but domain-specific knowledge is learned based on user interaction. An
example of such a system is {\sc NaLIX}~\cite{Li:2005:NIN:1066157.1066281}.

Most recent interfaces integrate configuration capabilities, since it allows
domain portability which is a great improvement of interfaces. In the following
we will emphasize the role of user interaction ({\it feedback-driven
approaches}) and machine learning techniques ({\it learning-based approaches}).

---------------

The way translation from NL questions to formal query has evolved over years.
Table~\ref{tab:overview} presents an overview of major systems that we consider
in the survey.

\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|}\hline
%\begin{tabular}{|c|c|c|c|c|c|c|c|}\hline
\multirow{2}{*}{\bf Approach} & \multirow{2}{*}{\bf System} &
\multicolumn{6}{c|}{\bf Dimensions}\\\cline{3-8}
& & {\bf Query} & {\bf Data} & {\bf Answers} & {\bf Portability} & {\bf
Linguistic coverage} & {\bf Error feedback}\\\hline\hline 
\multirow{2}{*}{Domain-dependent semantic parsing} & {\sc
Baseball}~\cite{Green:1961:BAQ:1460690.1460714} & & & & & & \\\cline{2-8}
& {\sc Lunar}~\cite{Woods:1973:PNL:1499586.1499695} & & & & & & \\\hline
\multirow{5}{*}{Complex question translation} & {\sc
Chat-80}~\cite{Warren:1982:EEA:972942.972944} & & & & & & \\\cline{2-8}
& {\sc Irus}~\cite{Bates:1983:IRU:511793.511804} & & & & & & \\\cline{2-8}
& {\sc Qwerty}~\cite{Nelken:2000:QTD:992730.992808} & & & & & & \\\cline{2-8}
& {\sc
Precise}~\cite{Popescu:2004:MNL:1220355.1220376,Popescu:2003:TTN:604045.604070}
& & & & & & \\\cline{2-8}
& {\sc Panto}~\cite{Wang:2007:PPN:1419662.1419706} & & & & & & \\\hline
\multirow{5}{*}{Feedback-driven approaches} &
{\sc Masque/SQL}~\cite{Androutsopoulos93masque} & & & & & & \\\cline{2-8}
& {\sc Team}~\cite{Grosz:1987:TED:25672.25674} & & & & & & \\\cline{2-8}
& {\sc NaLIX} \& {\sc DaNaLIX}~\cite{Li:2005:NIN:1066157.1066281} & & & & & &
\\\cline{2-8}
& {\sc C-Phrase}~\cite{Minock:2010:CSB:1715942.1716190} & & & & & &
\\\cline{2-8}
& {\sc
Orakel}~\cite{Cimiano:2007:PNL:1216295.1216330} & & & & & & \\\hline
\multirow{3}{*}{Learning-based approaches} & Zettlemoyer
et al.~\cite{DBLP:conf/uai/ZettlemoyerC05} & & & & & & \\\cline{2-8}
& Miller et al.~\cite{Miller:1996:FSA:981863.981871} & & & & & & \\\cline{2-8}
& {\sc Wolfie}~\cite{Thompson:2003:AWM:1622420.1622421} & & & & & &
\\\hline
\multirow{2}{*}{Schema-unaware approaches} & {\sc
PowerAqua}~\cite{DBLP:conf/esws/LopezMU06} & & & & & & \\\cline{2-8}
 & {\sc DeepQA}~\cite{DBLP:journals/aim/FerrucciBCFGKLMNPSW10} & & & & & &
 \\\hline
\end{tabular}
\caption{Overview of major NL interfaces to structured data}
\label{tab:overview}
\end{table*}

\subsection{Domain-dependent semantic parsing}
Early systems belong to this class of approaches.
The knowledge necessary to translate NL questions to database queries
is encoded in lexicon.
The systems allows users to use a subset of English (controlled language) to
query databases. 
The lexicon, however, is a huge linguistic resource which defines how each word
must be translated into database elements, and what semantic rules to trigger to
get, in the end, the desired database query.

\subsubsection{Lexicon}
The lexicon is a resource that ``defines'' a set of words that belong to a
domain. Those words are associated to a ``meaning'', which is a semantic rule
that says how this word must be interpreted in the data domain and given
the data structure.
In addition, the lexicon also contains a list of specific rules that modify 
the global meaning of the sentence, given some words that are already defined in
the lexion.
The lexicon usually combines both syntactic with semantics information.
For instance, the same word would have a different interpretation if it's a noun
or a verb in a sentence.

\subsubsection{Limitation}
The domain dependence is however the great limitation of those systems; this is
due to the cost of the lexicon. Indeed, porting such systems to other domain
would mean provide a new lexicon and corresponding semantic rules, which is
highly costly.

\subsection{Complex question translation}
The next generation of NL interfaces aims at increasing the linguistic coverage.
This is performed with the distinction of both domain-dependent knoweldge and
domain-independent knowledge.
The domain-dependent knowledge base consists in semantic rules triggered by
words, phrases or syntactic information encoded in a parse tree. Those rules
produce fragments of the target query language (or of the intermediate query
language) to be then combined and modified to generate the final qurey language.
The domain-independent knowledge base is composed of lexical information in a
dictionary (which might be completed with domain-dependent knowledge, like the
most likely senses of words used in the application domain).

\subsection{Feedback-driven approaches}
This range of systems translate NL questions to database queries basing on
users' feedback. 
We distinguish between the following kinds of feedback:

\subsubsection{Authoring tool configuration}
Authoring tools are GUI that permits users to edit domain-specific knowledge
(e.g., the lexicon that is used to translate NL questions to internal queries). 
Domain-specific knowledge edited within such tools can be straightforward (like
synonyms to be used in user's question to describe the same database elements)
or more complex like semantic rules to translate user's terms to logical
elements.
Describing this knowledge is not an easy task for standard users, for instance
semantic rules that define how to map words/phrases to logical elements, and
rules that define how information from the parse tree must be combine to
produce the final logical query.
For that reason, recent advanced systems try to infer such rules basing on
dialog-like interaction.

\subsubsection{Interactivity}
Authoring tools presented in the previous section are intended to be used as a
preliminary task when porting the interface to other domains. 
Other systems do not explicitely ask users to answer question to get the
domain-specific knowledge, but infer this knowledge basing on interaction when
using it. 
This range of systems suggests users NL questions that could be reformulations
of the current user's question. 
To the best of our knowledge, there are two different kinds of such interaction,
when the system cannot interpret a question:
\begin{itemize}
  \item the system tries to change words/phrases in user's question, so that the
  system is able to interpret the question
  \item the system also comprises a repository of successfully answered
  questions, and suggests one of those questions replacing some slots with terms
  used in the user's question, and ensuring that the generated question can be
  interpreted by the system
\end{itemize}
Recent work~\cite{DBLP:conf/icde/KoutrikaSI10} investigate how to present
similar questions in NL as interpretations of the current question. 
This is a way of making the user think she controls what is happening, which is
one of the features of modern interfaces. 
This paraphrasing feature is also present in {\sc NaLIX}/{\sc
DaNaLIX}~\cite{Li:2005:NIN:1066157.1066281,Li:2007:DDN:1247480.1247643} and {\sc
C-Phrase}~\cite{Minock:2010:CSB:1715942.1716190} works.

\subsection{Learning-based approaches}
Learning-based approach consists in learning a grammar or a set of rules that
map NL sentences to logical forms. 
Learning approaches are popular among the NLP community. Indeed, learning
techniques reduces the cost of linguistic resources, which is being learned over
time.
In the case of NL interfaces, this permits to port the system to other domains
with limited cost. 
Most systems need a corpus of labelled examples, e.g., a set of sentences mapped
to their corresponding logical form.

However, such corpora are rarely available, and are costly to produce.
Some systems adopt strategies to address this (see {\sc Wolfie}
section~\ref{sec:wolfie} for instance.)

\subsubsection{Statistical models}
\label{sec:statistical-model}
Table~\ref{tab:statistical-models} summarizes the different statistical models
used by learning-based systems.
\begin{table}
\centering
\begin{tabular}{|c|c|}\hline
{\bf System} & {\bf Model}\\\hline\hline
Miller et al.~\cite{Miller:1996:FSA:981863.981871} & recursive transition
network\\\hline
Zettlemoyer et Collins~\cite{DBLP:conf/uai/ZettlemoyerC05} & log-linear
model\\\hline
\end{tabular}
\caption{Different statistical models used by learning-based systems}
\label{tab:statistical-models}
\end{table}
Miller et al.~\cite{Miller:1996:FSA:981863.981871} use a probabilistic recursive
transition network and consider the probability $P(T|W)$ of a parse tree $T$
given a word string $W$:
$$P(T|W)=\frac{P(T)\times P(W|T)}{P(W)}$$
This model combines both {\it state transition probabilities} and {\it word
transition probabilities}. The state transition probability concerns the
labelling of a combination of semantic and syntactic information recursively
(the label of a node is computed given the labels of the previous node in the
syntactic order, and the parent node).
The word transition probability is the probability of a word, given the previous
syntactic word and a semantic information (attached to the parent node in the
parse tree).

Zettlemoyer et Collins~\cite{DBLP:conf/uai/ZettlemoyerC05} use a log-linear
model to learn a combinatory categorial grammar.
This grammar, which also defines the domain-specific lexicon of the parser,
contains semantic information ({\it i.e.} to which $\lambda$-calculus formula a
given word/phrase should be associated).

\subsubsection{Shortcomings of these approaches}
These components rely on statistical models, that often require a huge amount of
annotated data.
For instance, a statistical parser require a significant number of questions
annotated with corresponding parse tree. Table~\ref{tab:training-data} shows the
volume of training data corresponding to various systems.
\begin{table}
\centering
\begin{tabular}{|c|c|}\hline
{\bf System} & {\bf Training data volume}\\\hline\hline
Miller et al. & 4000 sentences\\\hline
Zettlemoyer et Collins~\cite{DBLP:conf/uai/ZettlemoyerC05} & 600/500 training
examples\footnote{The system is being experimented on two data sets}\\\hline
\end{tabular}
\caption{Volume of training data of different systems}
\label{tab:training-data}
\end{table}
Besides, training data should also be composed of negative examples, whose
availability is a strong requirement as pointed out by Giordani et
Moschitti~\cite{Giordani:2009:SSK:1617768.1617815}.

\subsection{Schema-unaware approaches}
A range of recent systems aggregate potential answers from different sources.
This range of systems have emerged in parallel with the success of the semantic
web technologies. 
The particularity of these approaches, is that they cannot rely on the schema of
underlying knowledge bases, because the different sources are potentially
modelled in very different ways. 
Thus, the set of systems represented by these approaches try to bridge the gap
between user terminologies and the different terminologies used in the different
knowledge bases that the interface talks to.
These approaches can be seen as an extension of several approaches presented
before, namely ``complex question translation'' (because the question is
further analyzed to map it with the terminology used in the different knowledge
bases) and ``learning-based approaches'' (because some of the systems
represented in these approaches comprise learning components).

\subsubsection{Terminology mapping}
In previous approaches, end-users were not aware of how data are modeled in the
knowledge base. This requires advanced natural language processing to map user's
terminology with database terminology. In schema-unaware apppraoches, the
systems do not talk to a single database, but to potentially an unlimited number
of sources where the structured data are to be found. Each of those sources have
its own logical schema, naming conventions, etc.
Then, the system must know how to communicate with these knowledge bases, and
what strategies to adopt to reduce the computation cost of generating
distributed queries (see section below~\ref{sec:schema-unaware-shortcoming}).
In some cases, it's also critical to aggregate results from different sources.

\subsubsection{Shortcoming of these approaches}
\label{sec:schema-unaware-shortcoming}
The major shortcoming is related to scalability and efficiency. In particular,
in cases where the knowledge bases are searched over Internet (for instance
Linked Data\footnote{See~\url{http://linkeddata.org/}.}), the computational
complexity of mapping and expanding user query terms to the terminology of
respective knowledge bases is a limiting factor. Internet latency in this case
is also to be considered since the databases are not hosted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   DOMAIN-DEPENDENT SEMANTIC PARSING %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Domain-dependent semantic parsing}
\label{sec:domain-dependent}
The major systems are {\sc Baseball}~\cite{Green:1961:BAQ:1460690.1460714} and
{\sc Lunar}~\cite{Woods:1973:PNL:1499586.1499695}.
Both systems are surveyed below.

\subsection{{\sc Baseball}~\cite{Green:1961:BAQ:1460690.1460714}}
{\sc Baseball} aims at answering questions about baseball results. The main
concepts in the data are games, teams, scores, day, month, place (of a
game). The domain is quite close, which means that there is few ambiguity in
terms of word meaning.

\subsubsection{Data structure}
\label{sec:baseball-data-structure}
The data structure is a list structure called {\it specification list}. This is
a hierarchical structure, where each level correspond to an attribute associated
to a value, or a nested specification list.
An attribute can also be modified.
For instance, the city {\it Boston} is represented by ``City=Boston'';
an unknown number of games is represented by ``Game$_{\textnormal{number
of}}$=?''.

\subsubsection{Semantic knowledge}
The semantic knowledge necessary to map questions to the data structure is
defined in the lexicon on the one hand, and in a set of semantic rules (called
subroutines) on the other hand.

\paragraph{Lexicon}
The lexicon maps words or idioms to their meaning in the same data structure
presented section~\ref{sec:baseball-data-structure} as well as their POS
(part-of-speech).
Wh-words are also referenced in the lexicon.

\paragraph{Subroutines}
Subroutines are a set of semantic rules that modify the query representation or
make choices in cases of ambiguity. 
For instance, a word that can have two POS (noun and verb) is disambiguated with
the help of some heuristic, like the fact that any sentence can only have one
main verb. 
A meaning modification consists for instance in adding a modifier in an
attribute. 
For example, the word ``team'' has the meaning ``Team=(blank)''. The word
``winning'' before the word ``team'' will lead to the modification
``Team$_{\textnormal{winning}}$=(blank)''.

\subsubsection{Question translation step by step}
\label{sec:baseball-question-translation}

\paragraph{Dictionary lookup}
The question is first tokenized in words, and empty words are left aside.
The remaining words as well as adjoining words are looked up in the lexicon for
the POS and the meaning. The output is a list of attribute/value pairs with
extra information like the POS of each word and if the word is a wh-word.

\paragraph{Syntactic bracketting}
POS of each word is used to syntactically analyze the question in term of
phrases. Phrases are surrounded by brackets and the main verb is left aside.
The parsing proceeds from right to left and bases on heuristics. For instance,
prepositions are associted to the rearest right noun phrase to generate a
prepositional phrase. 
Each phrase is then tagged with its functional role in the sentence (subject
and object).

\paragraph{Subroutines activation}
Some words trigger additional rules that modify the data structure of the query
and/or disambiguate some words. 
For instance, the word {\it What} followed by the word {\it team} (whose
meaning is ``Team=(blank)'') modify the latter meaning to ``Team=?''.

\subsubsection{Shortcomings}
The main shortcoming of the system is the cost that is recquired to produce the
semantic knowledge base (the lexicon and the set of semantic rules).
Authors suggest an improvement for handling unknown words, where the meaning
could be expressed basing on existing words in the lexicon.
However, to port the system to another domain, one needs to rewrite entirely the
knowledge base which represents a significant effort.

\subsection{{\sc Lunar}~\cite{Woods:1973:PNL:1499586.1499695}}
{\sc Lunar} was published more than ten years after {\sc Baseball}. 
{\sc Lunar} (unlike {\sc Baseball}) has been experimented with scientific data
and targets expert users.

\subsubsection{Data structure}
Authors do not give much details about the data (provided by the NASA). It looks
almost like relational tables with a dedicated formal query language.
The data are about the chemical analysis of lunar rocks of the Apollo 11
expedition. The application domain is again very closed but more complex than
that of {\sc Baseball}; some expertise is required to validate the answered
provided by {\sc Lunar}.

\subsubsection{Internal query representation}
\label{sec:lunar-query-representation}
Woods~\cite{Woods:1973:PNL:1499586.1499695} has defined a meaning representation
language which is used to represent internally users' intent. This language is a
combination of propositions (whose evaluation leads to a truth value) and
commands (or actions to be performed by the DBMS). Propositions are composed of
database objects (classes or table names; instances or variables). Propositions
are combined together with logical predicates like OR, AND, etc. Commands are
``TEST'' (to test the truth of a proposition), ``PRINTOUT'' to print out the
evaluation of a proposition and commands for loops (``FOR'') to be used with a
quantifier.

\subsubsection{Question translation step by step}
\paragraph{Syntactic parsing}the input question is first syntactically parsed
using a general-purpose grammar (domain-independent grammar). The grammar in use
bases on Augmented Transition Networks linguistic formalism (Chomsky), which is
almost equivalent to the context-free grammar formalism.
The syntactic parsing also needs a lexicon which contains terms in use in the
domain. It contains for instance the technical names of samples recolted during
the expedition. ``S10046'' is thus recognized as a proper noun by the
parser~\cite{Woods:1986:SQN:21922.24336}.

\paragraph{Semantic mapping}a set of rules transform the syntactic parse
tree into a meaning representation (see
section~\ref{sec:lunar-query-representation}).
The rules are triggered both by the syntactic structure of the parse tree (the
label of nodes like ``NP'' for noun phrase or ``VP'' for verb phrase) but also
on the question words (like ``S10046'' which is a sample name in the lexicon,
or ``contain'' which has a semantics also defined in the lexicon).
The rule results in a database query pattern with slots to be filled with items
from the lexicon.
As the system also supports quantification, authors presents some heuristics on
how to resolve the attachment in the generated propositions.

\paragraph{Query execution}The internal query representation is composed of
commands that the database retrieval component understands and executes to
retrieve data and display/print them.

% \subsubsection{Something to tell somewhere?}
% The meaning representation is in the form of a database query (in particular
% through database commands). This is the intermediate step between {\sc Baseball}
% where the internal representation (spec lists) is in the form of the data
% themselves and the recent systems (like the one about household compliance)
% where the database commands are generated afterwards from a logical
% representation of user's intent (independent from the data AND from the
% database).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   COMPLEX QUESTION TRANSLATION      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Complex question translation}
\label{sec:complex-question}
This class of approaches aims at increase the coverage of NL questions.
In addition to the increased linguistic coverage, the systems of this class need
domain knowledge, but the involved processing are independant from the unerlying
DBMS.

As for domain-dependant systems, the domain-dependent knowledge base corresponds
to a lexicon which defines the ``meaning'' of words/expressions. This meaning is
expressed with a set of semantic rules that map words/expressions and/or
syntactic information to database query fragments.

Besides, the domain-independant knowledge base is composed of the following
components:
\begin{enumerate}
  \item a syntactic parser which operates iteratively with the semantic rules
  \item a set of NLP tasks that aim at resolve linguistic ambiguities (e.g.,
  anaphora resolution and ellipsis
  resolution~\cite{Bates:1983:IRU:511793.511804})
\end{enumerate}
The parsing might be performed iteratively with the semantic component process
as in {\sc Irus}~\cite{Bates:1983:IRU:511793.511804}.

\subsection{{\sc Chat-80}~\cite{Warren:1982:EEA:972942.972944}}
It is the basis of many future
interfaces~\cite{DBLP:journals/corr/cmp-lg-9503016} like {\sc
Masque}~\cite{Androutsopoulos93masque}.
The database is composed of facts about world geography
(facts about ocans, seas, rivers, cities and relations, the largest one is
``borders''). The database itself is implemented as ordinary Prolog.
Questions are expressed in a subset of English. The subset of
English qustions is a formal but user-friendly
language~\cite{Warren:1982:EEA:972942.972944}.
The main difference with its predecessor ({\sc Lunar}) is that much effort has
been spent on increasing the linguistic coverage. 
In particular, the system translates English determiners ({\it a}, {\it the},
{\it some}, {\it all}, {\it every}) and negation and focus on linguistic
phenomena, like noun attachment and ``transformational aspects'' (that cannot
be covered by context-free grammars).

\subsubsection{Portability}
The authors claim the system to be adaptable to other
application~\cite{Warren:1982:EEA:972942.972944}. In particular, it is
composed of a small vocabulary of about 100 domains (excluding proper nouns),
and a domain-independant knowledge base of about 50 words.

\subsubsection{Lexicons}
The system is composed of a small vocabulary of
English words that are related to the database domain, plus a dictionary of
about 50 domain-independent words.
These lexicons consist in rules in the XG formalism from Pereira; those rules
are processed by Prolog and output Prolog clauses.
In addition to these two lexicons used to parse the question, a dictionary is
made up of semantic rules in the form of templates that define how a word
associated to a predicate must be also associated with its arguments.

\subsubsection{Question translation step by step}
\paragraph{Parsing}
The parser analyzes the syntactic categories of words; words like determiners
(domain-independant lexicon) and database-related elements (domain-dependant
lexicon): these elements are nouns or verbs that correspond to database
predicates.
Proper nouns are represented by logical constants; most verbs, nouns and
adjectives are represented as predicates with one or more constants.

\paragraph{Interpretation}
The interpretation step consists in ``filling'' the predicates identified in the
previous step. This is performed using a set of templates.

\paragraph{Scoping}
This step is used to define the scope of determiners and some operators (for
instance, operator to count).

\paragraph{Planning}
The output of the previous step is a logical expression. 
However, to avoid combinatory explosion when executing the Prolog query, some
strategies to optimize the query have been implemented: reordering the
``predications'' in the Prolog query; putting braces arround independent
``subproblems'' to avoid too many backtracking procedures

\subsubsection{Limitations}
Constraints in NL are not convered (for instance ``Which ocean\ldots''
presuppose there is only one right answer).

\paragraph{Query execution}
Even relatively complex queries are answered in less than
one second~\cite{Warren:1982:EEA:972942.972944}.
The Prolog expression is executed to retrieve the
answer.
Authors note however, that the answering process (query execution) is the
limiting factor (while modern systems are limited by the question analysis task).

\subsection{{\sc Qwerty}~\cite{Nelken:2000:QTD:992730.992808}}
The specificity of this system is that it is intended to interface temporal
databases. This system has thus an increased linguistic coverage, a better
temporal expressivity. 
Input questions are expressed in controlled NL.
The grammar used in the system takes into account some aspects of
temporality of NL: tenses and temporal PPs that modify sentences.
The system produces queries in SQL/Temporal, a database query language
dedicated to temporal databases.

\subsubsection{Portability}
The grammar used for parsing questions and translating it
into the formal language is specifically designed for use with a particular
database schema. Thus, this system cannot be considered as a portable system.

\subsubsection{Question translation step by step}
\paragraph{Semantic parsing}
The NL question is parsed using the Type Grammar framework. While parsing, the
question is being trasformed into a logical representation called $L_{Allen}$.
This formal language is based on interval operators. 
The translation bases on a linguistic theory, that semantics of sentences is
modified by temporal preposition phrases (PPs). 
In this work, PPs are considered as variants of standard generalized
quantifiers, where the quantification is over time. 
The temporality in NL questions can be explicit (like ``When'', ``Which year'')
or implicit (``Did Mary work in marketing?''). 
The quantification also allows iterations of PPs (``every year until 1992''). 
In addition to temporal quantifiers, the system recognized quantification over
individuals (``some employees''), coordination and negation.
The semantic mapping to logical expression is performed basing on a bottom-up
approach, simultineously with the parsing.

\paragraph{Query translation}
The logic expression is translated in SQL/Temporal, the database query language
dedicated to temporal databases. 
Some logical query produce infinite SQL/Temporal queries. Some heuristics have
been implemented to prevent such behaviour.

\paragraph{Query execution}
The SQL/Temporal query is finally evaluated by the database engine to produce
the answers.

\subsection{{\sc Irus}~\cite{Bates:1983:IRU:511793.511804}}
The {\sc Irus} system processes the question independantly from the underlying
domain and DBMS, which is a big change wrt previous systems.
The meaning formalism to represent internally the query is the same as in the
{\sc Luanr} system (MRL) but its expression is domain and DBMS-independent.
Besides, {\sc Irus} analyses linguistically the question and integrates
state-of-the-art NLP components, such as anaphora and ellipsis resolution.

\subsubsection{Internal query representation}
The internal meaning representation language is a descendant of that of {\sc
Lunar}
The language has the following general form~\cite{Bates:1983:IRU:511793.511804}:
$$(FOR <quant> X / <class> : (p\ X) ; (q\ X)) $$
where $quant$ is a quantifier such as EVERY, SOME, THREE, HALF, etc., $X$ is the
variable of quantification, $<class>$ is the class of quantification of $X$,
$(P\ X)$ is a predicate that restricts the domain of quantification and $(q\ X)$
is an expression being quantified, or an action such as $PRINT\ Y$.

\subsubsection{Question translation step by step}
\paragraph{Syntactic parsing}
The syntactic parsing of NL questions is performed using the ATN
grammar formalism.
The authors claim that the syntactic parser can benefit from semantic mapping as
well in the syntactic parsing, both evolving in a {\it cascaded system}.
The output of the syntactic parsing is a partse tree, where nodes correspond to
syntactic information about question words/phrases

\paragraph{Semantic mapping}
The semantic mapping is done in interaction with the syntactic parser.
It requires a domain lexicon, which defines the semantics of the words and
expressions used in users' queries.
The main subtasks involve disambiguation (pronouns and other anaphoric
expression resolution, ellipsis resolution, references resolution through
discource information).

\paragraph{Query execution}
The MRL can be used to interface any database system, at the condition that
there is a component responsible for the translation from the MRL to the target
dtabase query language.

\subsection{{\sc Precise}~\cite{Popescu:2003:TTN:604045.604070,Popescu:2004:MNL:1220355.1220376}}
{\sc Precise} maps questions expressed in natural language to SQL queries.
The interesting approach in this system, is the introduction of {\it
semantically tractable questions}.
This class of questions is guaranteed to be mapped to the correct SQL query.
This reduces then the classic gap between the query space and the data space.

\subsubsection{Internal query representation}
The internal query representation is original compared to previous systems. 
The system builds an ``attribute-value graph'' that maps words of the question
to database elements, and a ``relation graph'' that maps ``relation tokens''
(some question words) to database relation names. Both graphs are then used to
generate the final SQL query.

\subsubsection{Lexicon}
The lexicon defines the mapping between tokens and database elements. It is
composed of 1) the tokens; 2) the database elements; 3) the binary relations
that bind both tokens and database elements.

\subsubsection{Question translation step by step}
\paragraph{Syntactic parsing} A lexicon is composed of automatically
extracted database elements, and is used to perform the matching with
question tokens. NLP task are: tokenizing the question into words,
categorizing those tokens into ``syntactic markers'' (empty words?) and
``tokens'' (which are words that can be potentially associated with
database elements). 
In addition to the lexicon, the system expects a parser (implemented as a
plug-in, it can thus be changed for experimentation purposes).
Authors experimented it with a syntactic dependency parser which outputs a graph
(``attribute/value graph'') composed of paths linking database elements
together. Those path will then be composed together (aggregation / foreign keys
for relational databases).
The lexicon is also composed of a set of restrictions corresponding to
prepositions and verbs: those restrictions define the join paths connecting
relation/attributes. The set of those restrictions defines the semantic part
of the lexicon.
A component is also responsible for classifying
questions into tractable and not-tractable questions. This is done linking
words of the question with a set of ``compatible'' elements of the
database.
{\sc Precise} also implements strategies for correcting syntactic parsing
errors (semantic over-rides) given the semantics (defined in the lexicon).

\paragraph{Semantic mapping}
the interpretation consists in choosing paths
between database elements. This choice is a constraint satisfying problem.
Paths generate SQL fragments that are then
aggregated. The aggregation is done using the join paths available in the
restrictions.

\subsubsection{Feedback component}
In cases when no interpretation is possible (even trying to correct
possible syntactic errors) the system asks the user to rephrase the
question.

\subsection{{\sc Panto}~\cite{Wang:2007:PPN:1419662.1419706}}
{\sc Panto} generates SPARQL queries, that can be executed
to get answers to the information need expressed through a question in NL.
The data are organized in a knowledge base, more specifically
an ontology (RDF or OWL formalism).
The most interesting aspect in {\sc Panto} is that its most important component
(the linguistic component, the parser) is implemented as a ``plug-in''
component, that can be easily replaced by an other one. This permits thus to
benefit from the improvements in terms of linguistic coverage, when integrating
state-of-the-art parsers.

\subsubsection{Portablity}
``{\sc Panto} is designed to be ontology-portable''. To
ensure portability, a domain-independent component is comprised in {\sc
Panto}. This component is a lexicon composed of WordNet entries. For
portability purposes, users can collaborate and improve the domain-dependent
component (the domain ontology) defining their own synonyms to be added in the
lexicon used in the question parsing step.

\subsubsection{Internal query representation}
The internal query representation is a graph representation called ``query
triples''. 
It is a representation of the parse tree, that is then mapped to database
queries (i.e. RDF triples) thanks to the lexicon.

\subsubsection{Question translation step by step}
\paragraph{Syntactic parsing}
words from the NL query are first mapped to
entities (concepts, instances, relations) of the ontology. This corresponds
to the ``entity recognition'' task, and several tools are used, such as
WordNet and string metrics algorithms.
Then, a syntactic parser is used to recognize nominal phrases in the
sentence (the question). Those phrases are represented by pairs in the
parse treee.
In addition, some NLP tasks are integrated in this step, such as the
negation recognition.

\paragraph{Semantic mapping}
Pairs of nominal phrases from the parse tree
are associated to triples in the sense of the ontology, and composed of
entities of the domain ontology.
This association is performed using the domain knowledge (the database).
Besides, two additonal components are involved in this step: the question
target identifier which identifies the target in the parse tree, and a
component responsible for the recognition of solution modifier in the sense
of SPARQL (e.g., commands ``FILTER'' or ``UNION''). Those components
basically base on rules triggered by the recognition of some words (e.g.,
wh-words for the former component).
The triples mentionned before along with the target and
modifier information constitute the internal representation of the query.

\paragraph{Query execution}
The internal representation of the query
mentionned above is interpreted into SPARQL statements, that can then be
executed to retrieve requested facts.
The target item is used in this step to decide what to
put after the ``SELECT'' command in the generated SPARQL statement.
Query post-processing procedures are triggered, for example basing on the
negation recognized in the parsing step. The negation is usually translated
in the ``FILTER'' SPARQL clause to specificy the set of triples that must
not appear in the result of the execution of the SPARQL statement.

% \subsection{{\sc Exact}~\cite{Yates:2003:RNL:604045.604075}}
% {\sc Exact} is a successor of {\sc Precise}. It maps questions to SQL query.
% This query is then transformed to create a PDDL goal, which is then used to
% generate a set of appliance commands to satisfy user's request.
% In the end, the system looks like other NLIDB, but has additional steps in
% addition to perform the generation of goals for appliance devices. 
% Besides, generated SQL statements are not only ``SELECT'' ones but also
% ``UPDATE'' once; which means that the interface may change the state of the
% database (unlike other classic interfaces).
% 
% \subsubsection{Predictability}
% Guarantees of soundness of SQL interpretations (semantically tractable
% questions).
% In particular, different classes of questions are not handled the same way.
% In the case of {\it complex} questions, e.g., questions that must be decomposed
% in several ones, user is not informed of this decomposition. 
% In the case of questions that cannot be answered (impossible requests), the
% system informs explicitely the user that the request has been understook, but
% that it cannot be answered. In the case of appliances, it might be because the
% physical device does not permit to perform the desired goal; in the case of
% structured data it might be that the desired data is not present (null value) or
% is not modelled in the data model.
% 
% 
% \subsubsection{Portability}
% 
% 
% 
% 
% \subsubsection{Internal query representation}
% 
% 
% \subsubsection{Query modification}
% Bofore becoming a goal, SQL queries must be modified. 
% 
% 
% \subsubsection{Query execution}
% Unlike other NL interfaces, all the generated database queries are not executed
% as is. Some of them are first translated into a goal, then into a plan. The
% plan is eventually send to devices which then inform the database about the fact
% that the devices' states have changed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  FEEDBACK-DRIVEN APPROACHES         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Feedback-driven approaches}
\label{sec:feedback-driven}

The systems presented in the previous section still require intensive
configuration efforts, and thus cannot be considered as {\it portable}.
As a result, several systems have arisen where semantic grammars are created
automatically on the basis of user interaction. We distinguishes between
configuration (authoring tools) and knowledge acquisition through user
interaction in use mode.

%{\bf What about explanatory questions?} (see Koutrika et
%al.~\cite{DBLP:conf/icde/KoutrikaSI10}).

\subsection{{\sc Team}~\cite{Grosz:1987:TED:25672.25674}}
The data are structured in a database about geographic facts like the largest
cities in the world, the population of every countries etc.
The {\sc Team} system is intended to be used with two kinds of users: standard
users and database experts, who engages dialogue to provide needed information
to port the system to other application domains. 
This system belongs thus in {\it configurable} systems, where the required
knowledge to port the system is provided by the expert user, through the
interaction with an authoring tool.

\subsubsection{Internal query representation}
The meaning of users' queries are internally represented in formal logic.

\subsubsection{Lexicon}
A lexicon is used to map words and expressions of NL to their meaning in terms
of database elements. 
Close classes of words are supposed to be domain-independent and a fix meaning.
Open classes words, however, have a much more important frequency in users'
queries, and their meaning is supposed to be domain-independent. 
The ``meaning'' is composed of both syntactic and semantic information.
Entries for nouns are the instance to which their refer, or a class (or
concept) in a type hierarchy; entries for adjectives and verbs correspond to
the possible predicate and how to find arguments of the predicate in the NL
question.

\subsubsection{Database schema}
In addition to the lexicon, a resource about how logical forms can be translated
in terms of database elements must be available. 
This resource expresses for instance the link between predicates (that appear in the
logical forms) and database relations and attributes or the definition of the
class hierarchy in terms of database relations or fields.

\subsubsection{Portability}
Portability is performed in using the system in a different mode (knowledge
acquisition). In this mode, the database/domain expert informs the system on how
data are organized in the database, what are the database elements and what
words and expressions from NL are used for those elements.
The acquisition consists in a tool, where the expert must answer questions; the
answers of those questions will impact the resources like the lexicon and the
database schema, that are both used to interface the database.

\subsubsection{Question translation step by step}
The system is divided into two sub-systems: DIALOGIC that maps NL questions to
formal expressions and a schema translator that translates formal logical
queries in database queries. 
\paragraph{Syntactic parsing}
The parsing of the NL question is performed using an augmented-phrase structure
grammar. The parser produces possibly several parse trees for one question; then
one parse tree is selected basing on syntactic heuristics.

\paragraph{Semantic mapping}
Several processings are responsible for resolving some domain-specific
ambiguities like noun-noun combinations and ``vague'' predicates like {\it
have} or {\it of}~\cite{Grosz:1987:TED:25672.25674}. Finally, a quantifier
determination process is triggered. 
In the end, a logical form of the question is identified.

\paragraph{Query generation}
The logical form is then translated in the database query. This translation
needs the conceptual schema as well as the database schema (which defines the
structure of the database) to perform the translation.

\subsection{{\sc Masque/SQL}~\cite{Androutsopoulos93masque}}
{\sc Masque} is a NL interface to Prolog databases, and {\sc Masque/SQL} is an
extension of it that supports SQL query language. The system is entirely written
in Prolog.
The system is meant to be domain-portable. Users can indeed add new entity in
the lexicon through a domain-editor.

\subsubsection{Lexicon}
The lexicon defines the semantic of words that are expected to appear
in users' questions. The meaning of words are described in logic predicate.
Possible argument types of predicates are organized using the hierarchical {\it
is-a} relation.

\subsubsection{Internal query representation}
The internal query representation is a Prolog-like language called Logical Query
Language.
Question words are translated to predicates or predicate arguments. The types of
those arguments are described in the {\it is-a} relation hierarchy

\subsubsection{Portability}
The system can be used with different domain databases, but
this requires to edit the specific knowledge in an editor. This knowledge
consists in entities linked with the hierarchical {\it is-a} relation. User
also has to explicit links between words and corresponding logic predicates;
the entities in the taxonomy are used to restrict the possible arguments of
the predicates. Each predicate is also linked to the corresponding SQL
statement.

\subsubsection{Question translation step by step}
\paragraph{Syntactic parsing}
a dictionary consists of all English words that the
system understands and is used by an extraposition grammar to parse the
question.
\paragraph{Semantic mapping}
the dictionary composed of lexical units
also associates words to their meaning in the form of logic predicate.
The internal formal representation is a Prolog-like meaning
representation language (LQL).
\paragraph{Query execution}
The internal representation is translated to
SQL using an algorithm, and then SQL is executed in the underlying DBMS.
The translation consists of rules triggered by the structure of the LQL
expression; each unit LQL expression is associated with a SQL fragment; all
fragments are then combined to produce the final SQL expression.
The system has also been experimented with Prolog as query language in
association with a Prolog database.

\subsection{{\sc NaLIX}~\cite{Li:2005:NIN:1066157.1066281} and {\sc
DaNaLIX}~\cite{Li:2007:DDN:1247480.1247643}}
{\sc NaLIX} is an interactive interface to XML databases for questions expressed
in natural language.

\subsubsection{Question history}
The system is composed of a query history that keeps all
successfully answered queries. Queries from this history are intended to be
used as templates for formulating new queries. This feature also permits users
better understand the linguistic coverage of the system.

\subsubsection{Internal query representation}
The internal query representation is the target database query, {\it i.e.}
XQuery.

\subsubsection{Portability}
%% tell something about domain portability
There is no internal representation of the query (the NL
question is directly translated to XQuery). Thus, the translation is dependent
on the database and the chosen query language (XQuery).
In addition to the portability feature of {\sc NaLIX}, {\sc DaNaLIX} takes
advantage of domain-dependent knowledge which can also be automatically acquired
from user interaction. When ported to a new domain, the system starts with a
generic framework; then domain-dependent knowledge is learned from user
interaction.

\subsubsection{Question translation step by step}
\paragraph{Syntactic parsing}
The parsing consists in identifying words and
phrases using {\sc Minipar} which is a dependency parser (dependency among
words and not hierarchical constituents).
An other component is responsible for checking whether words/phrases
identified in the previous step can be mapped to directives (e.g.,
``return'' or ``group by'' clauses) in the target query language (XQuery).
Each word/phrase that can match a directive is further typed, depending on
the kind of directive.
The output of the parser is a tree with those roles as labels of phrases
of the initial query.
The vocabulary mismatch is overcome using
WordNet\footnote{\url{http://www.cogsci.princeton.edu/~wn/}}.
In {\sc DaNaLIX}, an additional step consists in transforming the parse tree
using domain knowledge, basing on relevant rules.

\paragraph{Semantic mapping}
Each item from the parse tree is translated into a constituent of the target
query language (XQuery). This is done using a series of processings; basically
a set of rules define how to combine items of the parse tree to XQuery
clauses. There are also further treatments like ``nesting'' and ``grouping''
developped in~\cite{DBLP:conf/edbt/LiYJ06}.
In cases when the system does not understand how to map a given phrase to a
XQuery constituent, the system interacts with users and suggests potential
reformulations. {\sc NaLIX} seems to be the first NL interfaces that
introduces user interaction to select the correct parse interpretation.
\paragraph{Query execution}
The question is directly
translated into a XQuery expression, which is the data query language. The
XQuery expression is then executed to retrieve answers.
Answers are basically XML answers. Different visualization
of the answers are possible (text view for simple answers, hierarchical list
view or raw XML).
Besides answers to queries, the system implements an advanced error manager
that also supports users in rephrasing queries that were not parsed and
translated correctly.

\subsection{{\sc C-Phrase}~\cite{Minock:2010:CSB:1715942.1716190}}
{\sc C-Phrase} is a system that translate questions expressed in NL in a query
for relational database.
The system outputs expression in tuple calculus (FOL) that can be easily
translated in a database query language like SQL.

\subsubsection{Lexicon}
Semantic information are encoded in a lexicon. It maps tokens with syntactic
information (such as head/modifier in dependency analysis) and semantic
information (translation in $\lambda$-calculus).
It is represented as a set of rules that form the grammar of the parser.
For instance, the rule
\begin{center}
HEAD$\rightarrow\langle$``cities'',$\lambda x.City(x)\rangle$
\end{center}
In addition, the system comprises a set of sentence patterns, in the form of
context-free rules. For instance:
\begin{center}
QUERY$\rightarrow\langle$``list the''$.NP, answers({x|NP(x)})$
\end{center}
Authors say they ``rarely'' see users who do not use already defined sentence
paterns.
This set of rules are automatically created by an authoring tool.
The tool explicitely asks for meaningful names of different database elements
(relations, attributes and join paths). 
It also permits to define new concepts in NL language.

\subsubsection{Internal query representation}
The internal query reprsentation is $\lambda$-calculus.

\subsubsection{Question translation step by step}
\paragraph{Semantic parsing}
The parsing bases on a context-free grammar, augmented with $\lambda$-calculus
expressions.
The framework ($\lambda$-SCFG) works with two parsing trees: one for parsing
syntactically the NL sentence; the other one for expressing the semantics of the
first one in $\lambda$-calculus.
The input question is first tokenized and normalized. 
Then, the sequence of tokens is analyzed to idenfity database elements, numeric
values, and proceed to some spelling corrections. 
The structure is then transformed in the form of tuple calculus queries. 
This is done based on a set of rules that map lexical/syntactic parses to
tuples. Each rule has a plausibility; in the end, the product of plausitilities
of all rules used in a parse is used to rank potential semantic interpretations. 
In case of ambiguity, the user is asked to rephrase the question, or to select
some rephrasing propositions. 
\paragraph{Query generation}
The tuple query is converted in SQL.

\subsection{{\sc Orakel}~\cite{Cimiano:2007:PNL:1216295.1216330}}
{\sc Orakel}~\cite{Cimiano:2007:PNL:1216295.1216330}'s main feature is the
portability. This portability is based on the use of subcategorization frames,
which are linguistic structures (predicate + arguments).
The feedback aspect consists of an authoring tool. This tool (FrameMapper) is
used to generate the domain-specific knowledge, and is intended to be used by
expert of the domain.

\subsubsection{Role of lexicon}
The system is composed of three kinds of lexicon: 1) domain-independant lexicon
defining determiners, {\it wh}-pronouns and spatio-temporal prepositions; 2)
domain-specific lexicon which defines the meaning of verbs, nouns and adjectives
(see section~\ref{sec:orakel-portability}); and 3) ontological lexicon which is
automatically created from the data, and maps ontology instances and concepts to
proper nouns and standard nouns.
Categories of the domain-independant lexicon are ``generic'' categories such as
those of a generic ontology like DOLCE.

\subsubsection{Internal query representation}
The internal query representation is $\lambda$-calculus.
The question is represented in a language which is an extension of FOL (in
addition to FOL: quantifiers and operators).

\subsubsection{Customization process / portability}
\label{sec:orakel-portability}
Users can customize the system, {\it i.e.} create a domain-specific lexicon
which maps subcategorization frames (arity $n$) to an ontology relation (arity
$n$) (a definition in the database).
The interesting thing is that binary relation where the range is an integer
(for instance $height(mountain,int)$) can also be mapped to adjectives with the
different possible degrees (base, comparative, superlative forms) and possibly
the positive or negative scale (as in {\sc Team}).
This mapping is performed by users themselves through a front-end.

\subsubsection{Question translation step by step}
\paragraph{Semantic mapping}
Both processes question parsing and semantic mapping are done in the same
process.
The parsing is based on the LTAG linguistic representation.
The parsing operates in a bottom-up fashion: each question word is associated
with an elementary tree. Then, all elementary trees are combined together to get
the syntactic parse tree of the entire sentence.
\paragraph{Query execution}
The FOL internal query representation is then translated in the database query
language like SPARQL (for ontologies expressed in OWL) or the language used for
ontologies expressed in F-Logic.
This translation is peformed using a Prolog program.

\subsubsection{Shortcomings}
Supports only factoid questions ({\it wh}-questions plus questions starting
with expressions like ``How many'' for counting) but not ``complex'' questions
like those starting with {\it why} or {\it how}.
Besides, there is a (strong) assumption that categories of the
domain-independant lexicon should be aligned with those of the database (the
domain ontology). The second one, is that the generation of the ontological
lexicon assumes that the labels used in the database correspond to
instance/concept names.
The front-end used to improve the domain-specific knowledge permits to increase
the linguistic coverage and is a nice tool for porting the interface; however it
might not be user-friendly since the underlying concepts (like the semantic
frames) are complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  LEARNING-BASED  APPROACHES         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Learning-based approaches}
\label{sec:leraning-based}

Learning-based approaches are approaches where machine learning algorithms are
the core of the translation mechanism. 
These algorithms aims at learning domain-specific knowledge (e.g., a lexicon).
This knowledge is used to parse the question and get clues on on how to
translate it to a database query.

\subsection{Miller et al.~\cite{Miller:1996:FSA:981863.981871}}
The main caracteristics of this system is that it is fully statiscal.
It is composed of three components for parsing, semantic interpretation and
discourse resolution and are associated with corresponding statistic models.
Each component produces a set of ranked items, and the chosen interpretation of
the question is the best one of the final component.

\subsubsection{Question translation step by step}
The different steps correspond to the different components of the system.
\paragraph{Syntactic parsing}The string of words $W$ is searched for
the $n$-best candidates of parse trees $T$ basing on the measure $P(T)P(W|T)$.
The parse tree contains syntactic information as well as semantic ones.
The statistical model is based on the recursive transition network model. This
model is more detailed section~\ref{sec:statistical-model}.
The model is trained with a set of questions annotated with the corresponding
parse trees.

\paragraph{Semantic mapping}The semantic mapping step is composed of two
sub-steps: first, a model associates a ``pre-discourse meaning'' to both a parse
tree and the corresponding string of words. Second, a ``post-discourse meaning''
is retrieved from the pre-discourse meaning, the string of caracters, the parse
tree and the history.
Both pre-discourse meaning and post-discourse meaning are represented using
frame semantics.
The construction of the frames is integrated in the parse tree. Then, the
statistical model is used to disambiguate the frames, for instance when there is
no information about the frame type or when there is no information about a slot
fill.
The second phase (post-discourse meaning) correspond to ellipsis resolution. It
takes the previous meaning (final meaning of previous questions) and the
pre-discourse meaning (of the current question), and finds the best meaning.
Previous meaning and pre-discourse meaning are represented as vectors, whose
elements correspond to slots in the frame meaning representation. The
statistical model applies different kinds of operations on those vectors
(INITIAL, TACIT, REITERATE, CHANGE and IRRELEVANT). Those operations combine
elemnts of both vectors to compute the vector which corresponds to the meaning
of the current question.
\paragraph{Query generation}
The paper does not expalin how is performed the query generation.

\subsection{Zettlemoyer et Collins~\cite{DBLP:conf/uai/ZettlemoyerC05}}
The system aims at translating NL sentences to $\lambda$-calculus expressions.
The system is based on a lerning algorithm that needs a corpus of sentences
labelled with $\lambda$-calculus expressions. The system induces then a grammar.
The statistic model is a log-linear model.
The paper focus only on the generation of $\lambda$-calculus expression from
questions expressed in natural language.

\subsubsection{Portability}
The proposal has been tested for two application domains: a database of US
geography and a database of job listings.

\subsubsection{Internal query representation}
The query is internally represented in $\lambda$-calculus.

\subsubsection{Question translation}
The syntactic parsing is performed using a combinatory categorial grammar.
Resulting parse tree's nodes are composed of both syntactic and semantic
information.
The grammar of the parse operates with a domain-specific lexicon, which maps
question words/expressions to a syntactic type as well as a semantic type.
Several funtional rules define how syntactic types can be associated

\subsubsection{Learning component}
The learning algorithm takes as input a training set composed of pairs
$(S_i,L_i)$ where $S_i$ is a string of words and $L_i$ a logical form. The
algorithm also takes as input a lexicon $\Lambda_0$.
The learning algorithm will determine how a given string of words will be parsed
to produce a parse tree, and what words from the lexicon are required to produce
such trees. The algorithm involves then learning the lexicon and learning
the distribution over parse trees for a given string of words.

\subsubsection{Shortcomings}
The experiments are based on database rewritten in $\lambda$-calculus. It would
be interesting to implement an additional module that transforms
$\lambda$-calculus expressions to any database query language and measure the
overall performance.

\subsection{{\sc Wolfie}~\cite{Thompson:2003:AWM:1622420.1622421}}
\label{sec:wolfie}
{\sc Wolfie} is a system that learns a lexicon, that is used to translate NL
questions in database queries.

\subsubsection{Lexicon} 
The lexicon consists in a mapping from sentences to semantic representation
(logical database queries).
The mapping consists in two steps: first, phrases that compose the sentence 
are associated to database elements (or {\it symbols} in the representation).
Second, it says how those intermediate representation must be combined to get
the final database query.

\subsubsection{Learning}
Due to the nature of the lexicon, the number of possible interpretations given a
NL sentence is very complex (the problem is computationally intractable).
To cope with that, authors propose an active learning algorithm which selects 
only most relevant examples to be then annotated.
The learning algorithm bases on a greedy approach. The generation of candidate
meanings for each phrase consists in finding maximally common meaning for each
phrase.
But, the algorithm also aims at finding a general meaning for the whole sentence
(not only meanings for the phrases that are part of the sentence).

- evaluation: corpus of 250 questions on US geography paired with Prolog queries

\subsubsection{Shortcomings}
The system has not been evaluated with long phrases; the paper describes how it
works for phrases of maximum two words. Besides, ``the algorithm is not
guaranteed to learn a correct lexicon in even a noise-free corpus''.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DATA-DRIVEN APPROACHES              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Data-driven approaches}
%\label{sec:data-driven}

% \subsection{Han et al.~\cite{Han:2010:NLI:1719970.1720022}}
% A big advantage of this system, is that it does not distinguish the linguistic
% understanding of users' questions and the database coverage of the question
% (the fact that the question can actually be asnwered from the database).
% The system answers questions expressed in natural language, and the data are
% organized in an ontology. The database queries are expressed in SPARQL.
% 
% \subsubsection{Portability}
% Underlying data are structured in an ontology, which
% permits easily to change the domain. Dictionary is generated automatically
% from the ontology.
% Porting the interface to other domains is easy using an authoring tool that
% permits users to specify the semantics of domain-specific words/expressions in
% terms of schema-level information in the ontology (what word or expression used
% in NL questions is associated to which relations, concept or instance in the
% ontology?).
% 
% 
% 
% \subsubsection{Question translation step by step}
% Traditional interfaces map question words or expressions to database elements.
% The candidate paths that link those elements are then used to generate valid
% database queries.
% Here, the approach consists in exploring all possible database (or formal)
% queries from database elements.
% The cost of exploring all possible database queries is huge. To reduce the
% formal query space, authors consider templates of database queries.
% 
% \paragraph{Query template generation}
% Queries are generated at the schema level (not the instance level). Each
% relation in the ontology is used to generate a ``schema-level query group'',
% where the object and the predicate of the relation can be either a value or a
% variable (of the expected type of the resource in the ontology).
% The next step (preparation of the question) will permit to match the question to
% the query group.
% 
% \paragraph{Question parsing}
% \label{sec:han-question-parsing}
% The NL question is first syntactically/semantically parsed in a similar fashion
% as in classic systems.
% The question is tokenized and is possibly annotated with semantic
% labels. Semantic information can be a concept or an instance (e.g., ``I:City''
% for the question word {\it Berlin} or ``C:River'' for the question word {\it
% river}). Such semantic annotation is performed using a lexicon (which can be
% built automatically from the ontology).
% 
% \paragraph{``Preparation'' of NL questions}
% Each formal query template is associated with a set of NL questions. This
% association is performed with the help of an authoring tool.
% Within this tool, users can type a natural language query corresponding to a
% schema-level query group. As a result, the tool generate the normalized query
% (the query parsed as presented in section~\ref{sec:han-question-parsing}). In
% case of ambiguity, users can select the correct normalized query, which is then
% saved in the knowledge base of normalized query associated to schema-level query
% groups.
% 
% \paragraph{Semantic mapping}
% user's question is compared with prepared queries. To perform this, the user's
% question is normalized, and the normalized question is being compared with
% all normalized queries. In the case where the question is composed of two
% predicates, two normalized queries must be retrieved.
% The matching is based on similarity measures, and the best association is
% retrieved.
% 
% 
% \subsubsection{Shortcomings}
% Preparing queries from natural language sentences has to be performed by a
% domain expert, and a technician aware of the underlying data structure
% (how the data are semantically encoded in the database: predicates, instances
% and concepts). We believe this limits somehow the portability of the system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  SCHEMA-UNAWARE APPROACHES          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Schema-unaware approaches}
\label{sec:schema-unaware-details}

\subsection{{\sc PowerAqua}~\cite{DBLP:conf/esws/LopezMU06}}
{\sc PowerAqua} takes as input several semantic sources (heterogeneous
ontologies) and a question (expressed in natural language).
This system is an improvement of the system {\sc
Aqualog}~\cite{Garcia:2006:AOQ:1225785.1225790}. The latter system was able to
answer questions related to one domain ontology only (which is a problem in the
context of the semantic web composed of many heterogeneous ontologies).
The geatest contribution of {\sc PowerAqua} is the method for mapping user
terminology with ontology terminology (and the system is unaware of the
structure of the semantic sources).

\subsubsection{Domain portability}
The portability cost is ``negligible''.
Indeed, the system has a learning component responsible for the acquisition of
domain-specific lexicon which maps users' relations (expressed in natural
language) to knowledge represented in the domain ontology.

\subsubsection{Internal query representation}
The internal query representation is called {\it query triples}. It is triples
like RDF triples used in the data (ontology), but these triples are based on
terms of the query.

\subsubsection{Lexicon}
{\sc PowerAqua} (as well as {\sc Aqualog}) use domain-independant lexicon
WordNet.

\subsubsection{Question translation step by step}
\paragraph{Syntactic parsing}
Users' questions are first parsed syntactically, and questions are categorized
(for instance on the basis of the {\it wh}-question word). Both the parse tree
and the category of the question are used to generate the internal query
representation, query triples.
The sense of words used in the question are disambiguated using word sense
disambiguation algorithms. 
Those query triples are composed of words of the
question, and may be then modified so that they are {\it compatible} with the
database.
The linguistic component of {\sc PowerAqua} also consists in algorithms that
make decisions, for instance for correctly interpreting the conjunction /
disjunction terms (and/or). The question may also contain constraints, that are
sub-questions to be anewered prior the actual question. 
Furthermore, the system provides a way to treat two instances (from two
semantic sources) as equivalent, and thus ease the answering process (in
particular in cases where more than one semantic source are required to answer
the question). 
The mapping from users' terms to database elements is done using edition
distance-like metrics.

\paragraph{Semantic mapping}
the semantic mapping consists in processing query triples to retrieve the
ontology triples that are associated to the query triples. 
First, the algorithm tries to filter the sources (the ontologies) in order to
only consider those that contain all or most of the {\it query triples}. 
Query triples must then be filtered to take into account the potential high
number of triples generated in the previous step, and the fact that a question
can involve several different semantic sources.
The mappings established in the previous step (query terms and ontology terms)
are ranked basing on a sense disambiguation algorithm that uses WordNet and the
is-a taxonomy. In this step, the equivalence between two terms is computed based
on the label of the term (edition distance) but also on the position in the
taxonomy (ancestors and descendants).

\paragraph{Query generation}
Potential ontology terms (database elements) must be processed to generate the
final ontology query. 
Terms identified in different relevant ontologies must be used to generate
triples (first sub-step); these triples must then be linked, these triples
belonging or not to the same ontology (second sub-step). 
In this step, relations will be created from terms identified in the previous
step. A relation (in the query triple) does not always correspond to a relation
(expressed in ontology triple): sometimes, a new triples must be generated.

\subsubsection{Limitation}
Authors make an assumption, that the Semantic Web provides an indexing
mechanism.

\subsection{{\sc DeepQA}~\cite{DBLP:journals/aim/FerrucciBCFGKLMNPSW10}}
The {\sc DeepQA} project is part of the well-known {\sc Watson} system. 
{\sc Watson} has been the major event in the Q\&A community in 2010. Indeed, it
is the first artificial system which has won the american {\it Jeopardy!} quizz.
%We classify the underlying {\sc DeepQA} system in machine learning-based
%approaches. The system involves massive parallelism approach to get multiple
%interpretations and hypothesis. In the end, statistical models are used to
%merge and rank hypothesis and evidences. 
{\sc Watson} queries a wide range of different sources and aggregates the
different results to produce answers.

\subsubsection{Question}
{\sc Watson} has been designed for {\it Jeopardy!} where questions are not
standard questions, but {\it clues} that should help understanding what the
question is about. For instance, in a classic Q\&A process a question would be ``What
drug has been shown to relieve the symptoms of ADD with relatively few side
effects?''. In {\it Jeopardy!} the corresponding clue would be ``This drug has
been shown to erlieve the symptoms of ADD with relatively few side effects''.
The expected response would then be ``What is the Ritalin?'' (see
section~\ref{sec:jeoparty-answers})~\cite{FerrucciBCFGKLMNPSW10}.

\subsubsection{Answers}
\label{sec:jeoparty-answers}
Another particularity of {\it Jeopardy!} is that an answer are not simply a
phrase corresponding to what the clues are about, but the answer must be the
expected question corresponding to the clues. For instance, a valid response
can be ``Who is Ulysses S. Grant?'' but not ``Ulysses S.
Grant''~\cite{FerrucciBCFGKLMNPSW10}.

\subsubsection{Data}
The data (sources) used by {\sc Watson} are mostly unstructured documents as in
most Q\&A systems. {\sc DeepQA} however also leverages databases and ontologies
such as {\sc dbPedia}\footnote{See \url{http://dbpedia.org/About}.} and the {\sc
Yago}\footnote{See \url{http://www.mpi-inf.mpg.de/yago-naga/yago/}.} ontology;
this is why we consider this system in this survey.

\subsubsection{Question translation}
Question translation for databases involves different steps.
\paragraph{Question analysis}
\label{sec:jeoparty-question-analysis}
it involves many tasks: shallow parses;
deep parses; logical forms; semantic role labelling; coreference resolution;
relations (attachment relation and semantic relations); named entities; \ldots
Semantic relation detection is one of those tasks. 
For instance for the question ``They're the two states you could be reentering
if you're crossing Florida's northern border'', the relation would be
\verb+borders(Florida, ?x, north)+.

\paragraph{Hypothesis generation}
The module responsible for this step takes as input the analysis parses
(see section~\ref{sec:jeoparty-question-analysis}) and generates candidate
answers for every system sources. Those candidate answers are considered as
hypothesis to be then proved basing on some degree of confidence. 
To produce candidate answers, a large variety of search techniques are used.
Most of them concern textual search, but some consist in searching knowledge
bases, more specifically triple stores. 
The different search techniques lead to the generation of multiple search
queries for a single question; then the result list is modified to take into
account constraints identified in the question. 
The search is based on named entities identified in the clue. If a semantic
relation has been identified in the question analysis
step~\ref{sec:jeoparty-question-analysis}, a more specific SPARQL query can be
performed on the triple store. 
In this step, recall is preferred as precision, leading to the generation of
hundreds of candidate answers to be then ranked according to the confidence of
each candidate.

\paragraph{Soft filtering}
Candidate answers are not directly scored and ranked, since those algorithms 
require lots of resources. 
Instead, the hundreads of candidate answers corresponding to a single question
are first pruned, to produce a subset of initial candidate answers. The involved
algorithms are lightweight in the sense that they do not require intensive
resources (soft filtering).
The candidate that do not pass the soft filtering threshold are routed directly
to the final merging stage. 
The model used to filter the candidate in this step as well as the threshold are
determined on the basis of machine learning over training data.

\paragraph{Hypothesis and evidence scoring}
Candidate answers that successfully pass the previous step are scored again in
this step. This involves a wide range of scoring analystics to support evidences
for candidate answers.
First, evidences for the candidate answers are being retrieved. In the context
of triple stores, those evidences are triples related to entities and semantic
relations identified in the question. Those evidences are then scored, to
measure the degree of certainty of these evidences. 
For instance the score is determined on the basis of subsumption, geospacial and
temporal reasoning.  
The {\sc DeepQA} framework suports a wide range of scorers
(components) that provide scores for evidences wrt a given candidate answer. 
The evidences from different types of sources can also be combined (for
instance from unstructured content and from triple stores) using a wide range of
metrics. 
In the end, scores of evidences are combined into an {\it evidence profile}.
This profile ``groups features into aggragate evidence dimensions that provide an
intuitive view of the feature view''.

\paragraph{Final merging and ranking}
This step aims at ranking and merging ``the hundreds of hypotheses based on
potentially hundreds of thousands of scores to identify the single
best-supported hypthesis given the evidence and to estimate its confidence'' (or
likelyhood).

\paragraph{Answer merging}
To cope with candidate answers that might be equivalent ({\it e.g.}, leading to
the same answer) but with different surface forms, authors propose to first find
similar candidate answers to merge them in a single candidate answer.

\paragraph{Final ranking}
After merging candidate answers, they must be ranked based on merged scores.
This is done using a machine-learning approach. This approach requires a
training dataset of questions with known answers with appropriate scores. 
In this step ranking scores and confidence estimation (estimation of the
likelihood of a given candidate answer) must be computed in two separated
processes in intelligent systems. 
For both processes, the set of scores can be grouped according to the domain and
intermediate models specifically used for the task. The output of these
intermediate models is a set of intermediate scores.
Then, a ``metalearner'' is trained over this ensemble of scores.
This approach allows for iteratively improving the system with more complex
models, and adding new scorers. 
The metalearner uses multiple trained models to handle different question
classes (for instance, scores for factoid questions might not be appropriate
for puzzle questions).

\subsubsection{Drawbacks}
{\sc Watson} has been primarly designed for unstructured content: ``Watson's
current ability to effectively use curated databases to simply `look up' the
answers is limited to fewer than 2 percent of the clues''.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  CHALLENGES                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Challenges}
\label{sec:challenges}
From Hearst~\cite{Hearst:2011:NSU:2018396.2018414}
\begin{itemize}
  \item speech input (dialog-like interaction: Siri). This means that the future
  systems must be able to understand ill-formed sentences and mispelled words.
  \item social search (collaboration, asking people, crowdsourcing). This could
  also comprise systems that broadcast the question to other systems expert in
  some fields, and then aggregate the answer
\end{itemize}
The next generation of interfaces will not focus on the user (personalized
systems) but on non-textual information through non-textual
input~\cite{Hearst:2011:NSU:2018396.2018414}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  CONCLUSION                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}
The conclusion goes here.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.

% use section* for acknowledgement
%\ifCLASSOPTIONcompsoc
% The Computer Society usually uses the plural form
%  \section*{Acknowledgments}
%\else
% regular IEEE prefers the singular form
%  \section*{Acknowledgment}
%\fi
%
%
%The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
\newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibliography}

% biography section
%
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

%\begin{IEEEbiography}{Author 1}
%Biography text here.
%\end{IEEEbiography}

% if you will not have a photo at all:
%\begin{IEEEbiographynophoto}{Author 2}
%Biography text here.
%\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

%\begin{IEEEbiographynophoto}{Author 3}
%Biography text here.
%\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2012-06-26 trunk/tr-rankingsurvey/approaches.tex

\section{Ranking Approaches}

\subsection{Historical Development}

\subsection{Generic Architecture}

\subsection{Main Dimensions} 
\emph{Data}: structured data conceived as graphs? All existing approaches are applicable to data graphs or are there any that exploit special characteristics of specific types of structured data? Only in the latter case, approaches shall be distinguished along this data dimension\\

\emph{Queries}: same as data dimension: are there many different approaches dealing with different types of queries so that we can use query as a dimension to distinguish approaches?\\

\emph{Features}: content, structure, context, two meanings of context: context of user; and context of the data such as trust values of source, truth value / confidence degree of individual records; make clear this survey does not discuss user-context based methods in details\\

\emph{Results}: entity, relationships, subgraphs, graphs (entire dataset)\\

\emph{Techniques}:\\
- may vary in terms of methods: used \emph{NLP} for understanding keywords, used \emph{ML} for classifying keywords (I know some ML-based query classification approaches for document retrieval, are there also examples for structured data ranking?) and for learning to rank, (other) statistics-based methods: Vector Space Model (VSM), Language Modeling (LM), Information Theory\\
- may vary in terms of heuristics: two main ones are query-relevance and popularity; other heuristics are proximity, informativeness (based on Information Theory, e.g. entropy) and context-based: trust, truth value, locality etc.

\subsection{Foundation}
Here we discuss all basics needed to understand the approaches presented in the following sections.\\
Vector-Space Model: also discuss pivoted normalization and point out problems of short document length etc. in the context of structured data\\
Language Modeling: also discuss smoothing strategies\\
Link Analysis\\
Learning to Rank\\
...

\subsection{Taxonomy of Ranking Approaches}
Classify approaches mainly based on the type of \emph{heuristics} they used, i.e. (1) Query-relevance, (2) Popularity, (3) Other Heuristics and (4) All Heuristics / LTR.\\

Those that use same heuristics are distinguished in terms of \emph{methods}. E.g. query-relevance based solutions can be further distinguished in terms of VSM-based and LM-based approaches.\\

an

### 2012-07-11 trunk/tr-nlisurvey/src/document.tex

@@
 expression where there is no room for ambiguity unlike natural language.
-As a result, all interfaces must deal with words or terms ``meaning''. This
-``meaning'' or semantics is in the end defined in terms of ``database
-elements''.
+The problem can be formalized as:
+\begin{equation}
+f:\left\{
+\begin{array}{l}
+Q\rightarrow (Q^\prime\times S)^I\\
+q\mapsto(q^\prime_i, s_i)_i
+\end{array}\right.
+\end{equation}
+where $q$ is the user's question, $q^\prime_i$ a structured query and $s_i$ a
+score associated to the structured query $q^\prime_i$, and used to rank the
+query (the index $i\in I=[0,n]$ is the rank).
 
@@
 \label{sec:overview}
+
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{images/query-language}
+\caption{Blabla}
+\label{fig:query-languages}
+\end{figure*}
 

### 2012-07-20 trunk/tr-rankingsurvey/popularity.tex

\section{Popularity}
Wikipedia defines popularity\footnote{http://en.wikipedia.org/wiki/Popularity} as the quality of being well-liked or common, or having a 
high social status. Translating this to information systems, popularity ranking algorithms rely on link analysis to compute the relevance of a 
node of the graph in terms of its input and output linkage.
With the arrival of the Web, link analysis was proposed as a new method to rank the hypertext documents considering the way the information 
is represented and related \cite{}(Getoor and Diehl, 2005). Unlike content-based (statistics-based?) ranking, link analysis strategies try to incorporate 
structural features of the information during the ranking computation. Link analysis is a technique relying on examining the graph structure 
established among items, where the nodes of the graph are the items to rank and the edges are the relationships or links among items. By inspecting 
the graph structure implicit properties can be derived and included in the ranking process. Link analysis can be thought as a case of success, 
which was originally implemented in algorithms like PageRank \cite{}(Brin \& Page, 1998), HITS \cite{}(Kleinberg, 1998) and SALSA \cite{}(Lempel \& Moran, 2000), 
commercially exploited by the most popular search engines. Inspired by this philosophy several extensions have been developed that increase 
the corpus of link analysis methodologies to deal with structured and semi-structured information\footnote{This classification has been taken from 
\cite{}(Delbru, Toupikov, Catasta, Tummarello \& Decker, 2010)}, namely:
\begin{itemize}
\item Weighted link analysis. The aim of this technique is to assign more relevance to certain kind of links depending on its type during the ranking 
computation. A major challenge is how to assign the weight to the links without having negative performance implications. Most of the approaches 
under this classification were proposed in the topic of database research, and for this reason they are not directly applicable on web-scale. 
As an example for this category we can consider the works described in \cite{}(Xing \& Ghorbani, 2004) and \cite{}(Baeza-Yates \& Davis, 2004).
\item Hierarchical link analysis. This technique performs a layered exploration of the underlying data and it is intended for distributed environments. 
For example, first considering relationships among super nodes or datasets and secondly considering relationships among resources. An example for this 
category can be found in \cite{}(Xue, et al. 2005).
\item Semantic Web link analysis. This family of methods tries to exploit the semantic of relationships during the ranking process. This technique can 
be thought as an evolution of the weighted link analysis applied to the Semantic Web context. As an example we can consider the algorithms described 
in \cite{}(Ding et al., 2004) and \cite{}(Anyanwu, Maduko, \& Sheth, 2005), being the last one the culmination of the ideas previously introduced in 
\cite{}(Anyanwu \& Sheth, 2002) and \cite{}(Anyanwu \& Sheth, 2003). Examples of early commercial applications exploiting semantic Web link analysis include the 
works described in \cite{}(Sheth, Avant \& Bertram, 2001), \cite{}(Avant et. al, 2002) and \cite{}(Sheth, 2005).
\end{itemize}

### 2012-07-20 tr-rankingsurvey/sample.tex
Abstract, Intro, Ranking problem, Applications and initial list of sample approaches added

@@
 Before, we discuss the concepts/techniques behind existing approaches. Here we provide a sample
+
+\begin{table*}[htdp]
+\begin{center}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Algorithm}&\textbf{Reference}\\ \hline
+OntologyRank & Ding et al., 2004 \cite{Ding2004}\\ \hline
+ObjectRank & Balmin, Hristidis, \& Papakonstantinou, 2004 \cite{Balmin2004}\\ \hline
+PopRank & Nie, Zhang, Wen \& Ma, 2005 \cite{Nie2005}\\ \hline
+SemRank & Anyanwu, Maduko \& Sheth, 2005 \cite{Anyanwu2005}\\ \hline
+ReConRank	& Hogan, Harth \& Decker, 2006 \cite{Hogan2006}\\ \hline
+AKTiveRank	 & Alani, Brewster \& Shadbolt, 2006 \cite{Alani2006}\\ \hline
+Naming Authority Rank & Harth, Kinsella \& Decker, 2009 \cite{Harth2009}\\ \hline
+TripleRank & Franz, Schultz, Sizov \& Staab, 2009 \cite{Franz2009}\\ \hline
+RareRank & Wei, 2009 \cite{Wei2009}\\ \hline
+DBpediaRanker	& Mirizzi, Ragone, Di Noia \& Di Sciascio, 2010 \cite{Mirizzi2010}\\ \hline
+DING & Delbru, Toupikov, Catasta, Tummarello \& Decker, 2010 \cite{Delbru2010}\\ \hline
+\end{tabular}
+\end{center}
+\caption{Summary of semantic ranking algorithms and references}
+\label{tab:table1}
+\end{table*}%
+
+TODO: adapt table to new taxonomy
+
+\begin{table*}[htdp]
+\begin{center}
+\begin{tabular}{l l l |c|c|c|c|c|c|c|c|c|c|c|} \cline{4-14}
+& & & \rotatebox{90}{OntologyRank} & \rotatebox{90}{ObjectRank} & \rotatebox{90}{PopRank} & \rotatebox{90}{SemRank} & \rotatebox{90}{ReConRank} & \rotatebox{90}{AKTiveRank} & \rotatebox{90}{Hart et.
+al} & \rotatebox{90}{TripleRank} & \rotatebox{90}{RareRank} & \rotatebox{90}{DBpediaRanker} & \rotatebox{90}{DING} \\ \cline{2-14}
+& \multicolumn{1}{|c|}{\multirow{2}{*}{Query dependency}} & Static ranking  & x & x & x & x &  &  & x & x & x & x & x\\ \cline{3-14}
+								     & \multicolumn{1}{|c|}{} & Dynamic ranking &  & x &  & x & x & x &  &  &  &  & \\ \cline{1-14}
+ \multicolumn{1}{|c|}{\multirow{7}{*}{\rotatebox{90}{Granularity}}} & \multicolumn{1}{|c|}{\multirow{5}{*}{Item granularity}} & Document & x &  &  &  &  & x &  &  &  &  & \\ \cline{3-14}
+\multicolumn{1}{|c|}{}
+														  & \multicolumn{1}{|c|}{} & Dataset &  &  &  &  &  &  & x &  &  &  & x\\ \cline{3-14}
+\multicolumn{1}{|c|}{}														  
+														  & \multicolumn{1}{|c|}{} & Entity(Resource) &  & x & x &  & x &  &  & x & x & x & x\\ \cline{3-14}
+\multicolumn{1}{|c|}{}														  
+														  &\multicolumn{1}{|c|}{} & Identifier &  &  &  &  &  &  & x &  &  &  & \\ \cline{3-14}
+\multicolumn{1}{|c|}{}														  
+														  & \multicolumn{1}{|c|}{} & Relationship &  &  &  & x &  &  &  & x &  &  & \\ \cline{2-14}
+						\multicolumn{1}{|c|}{}  &	\multicolumn{1}{|c|}{\multirow{2}{*}{Ranking granularity}} & Document relationships & x &  &  &  &  &  &  &  &  &  & \\ \cline{3-14}						  
+						  									\multicolumn{1}{|c|}{}   & \multicolumn{1}{|c|}{} & Entity (Resource) relationships &  & x & x & x & x &  &  & x & x &  & x\\ \cline{1-14}	
+& \multicolumn{1}{|c|}{\multirow{5}{*}{Ranking factor}} & Provenance &  & x &  &  & x &  & x & x & x &  & x\\ \cline{3-14}
+							     & \multicolumn{1}{|c|}{} & Context (Topic) &  & x & x & x &  & x &  & x & x & x & \\ \cline{3-14}
+							     & \multicolumn{1}{|c|}{} & Similarity measure &  &  &  & x &  & x &  &  &  & x & \\ \cline{3-14}
+							     & \multicolumn{1}{|c|}{} & Locality & &  &  &  &  &  &  &  &  & & x\\ \cline{3-14}
+							     & \multicolumn{1}{|c|}{} & Predictability &  &  &  & x &  &  &  &  &  &  & \\ \cline{2-14}	 																   						  						
+\end{tabular}
+\end{center}
+\caption{Summary of ranking algorithms and data features}
+\label{tab:table3}
+\end{table*}

### 2012-07-20 trunk/tr-rankingsurvey/intro.tex
Abstract, Intro, Ranking problem, Applications and initial list of sample approaches added

@@
 \section{Introduction}\label{sec:intro}
+Scenarios characterized by searching and browsing on large volumes of data or documents require of special treatment in order to guide the users to the most relevant pieces of information.
+Typically, users have to select and filter all the information they go through until they find a relevant piece of data that matches what they are looking for.
+Also, user behavior studies have found out that users in Web search engines are viewing fewer result pages (Jansen \& Spink, 2006), which evidences the importance of ranking outcomes.
+
+In the traditional Web the information space is modeled as a corpus of documents that establish links among them as an implicit way to state relationships within the information they contain.
+Users can make use of these links to navigate the information moving from one document to another using Web browsers.
+Following this model, referred to as the Web of documents, search engines were proposed as a way to facilitate the navigation towards finding the required information, and retrieval mechanisms have been devised that make use of known properties of the link structure (Broder et al., 2000), being a notable example the PageRank algorithm (Brin \& Page, 1998).
+Despite current Web document retrieval solutions have demonstrated to be useful, new challenges appear when dealing with finer-grained information spaces where entities formally described and the relationships among them play the main role, and not the documents where they appear or are mentioned in (Sheth, Budak Arpinar \& Kashyap, 2004).
+New methods for exploiting semantic relationships between data must be considered in order to make the most out of the information usage.
+These ideas are used and applied in the context of what is called the “Web of Data”, described in (Bizer, Heath, \& Berners-Lee, 2009) as “a Web of things in the world”, in contrast to the traditional abovementioned Web of documents.
+Basically, what favors the trend from the Web of documents to the Web of Data relies on the limitations of human capabilities for consuming huge amounts of information and the need for data.
+This, together with the improvements on machine’s power, helps to process the information and convert it into data ready for direct consumption.
+Furthermore, converting Web documents (unstructured data) to data (structured) helps to achieve data and service integration purposes.
+In what follows we describe the main elements of the Linked Data initiative\footnote{http://linkeddata.org/} as it can be considered the cornerstone of the Web of Data nowadays.
+
+In the last decade, methodologies from database, artificial intelligence, information retrieval and linguistics research have been combined under the idea of pursuing a Semantic Web that helps to overcome the challenge of dealing with vast amounts of heterogeneous information (Lassila, 2007).
+All the efforts carried out to find a solution to this problem have produced different formalisms to model the knowledge implicitly contained in the information.
+Notably, the specification of the Resource Description Framework (Klyne \& Carroll, 2004), RDF Schema (McGuinness \& van Harmelen, 2004) and the Web Ontology Language (Brickley \& Guha, 2004) have been devised as languages for the representation of semantics.
+While having the required tools and capabilities to express the available knowledge, the fact of unifying all different perceptions of the real world under the same formal representation is still nowadays a challenge, due to the distributed nature of the Web that requires reconciling the semantics of disparate, heterogeneous schemas and representations.
+In order to overcome this problem approaches like the Linked Open Data initiative have arisen.
+As stated in (Bizer, Heath, \& Berners-Lee, 2009) ``Linked Data is simply about using the Web to create typed links between data from different sources''.
+In this way, the Web of Linked Data aims at building a dynamic set of data modeled using very simple principles while still keeping a common representation of the shared knowledge.
+As outlined in (Berners-Lee, 2006), the main principles of Linked Data are:
+\begin{enumerate}
+	\item Use URIs as names for things;
+	\item Use HTTP URIs so that people can look up those names;
+	\item When someone looks up an URI, provide useful information, using the standards (RDF, SPARQL);
+	\item Include links to other URIs, so that they can discover more things.
+\end{enumerate}
+
+In addition, the main tasks that have to be performed in order to publish data as Linked Data are (i) to assign consistent URIs to data published, (ii) to generate links, and (iii) to publish metadata that allows further exploration and discovery of relevant datasets.
+
+The Linked Data initiative has an enormous potential because it facilitates access to the very large amounts of information available on the Web in a structured and integrated fashion (Bizer, Heath, \& Berners-Lee, 2009).
+However, exploiting vast amounts of information requires new techniques that facilitate the user requirements for consuming and managing data.
+When searching for information, the fact of retrieving a significant collection of results satisfying the user requirements is very important, but the manner how these results are presented, filtered or ranked to the user can impact in a more important grade the way a user identifies the piece of information that better approximates to the target of his/her search.
+To help in this task ranking algorithms are used.
+
+In a few words, a ranking algorithm implements a function that accepts a set of items and returns an ordered version of the set without modifying the items themselves.
+The function is implemented taking into account certain preferences that determine the order of the items.
+In this way, the same collection of items could be ranked following different approaches, i.e.
+different order functions.
+Whilst the area of information retrieval has addressed and provided different approaches for this problem, e.g.
+PageRank (Brin \& Page, 1998), HITS (Kleinberg, 1998) and SALSA (Lempel \& Moran, 2000), there is still a lack of consensus referring to the problem of ranking structured data as that exposed in the Web of Linked Data.
+As stated previously, when dealing with structured information, entities and the relationships among them play the main role, and not the documents where they appear.
+
+The motivation of this work is to formalize the problem of ranking linked data and give a comprehensive overview of existent ranking methods for the Web of Data.
+There are other survey studies concerning to the topic of semantic Web search (Hildebrand, van Ossenbruggen \& Hardman 2007; Mäkelä, 2007; Want, 2008), where ranking algorithms for structured data are to some extent described.
+However, to the best of our knowledge none of the existing works gives a complete overview of ranking methodologies for the Web of Data that helps to understand the benefits and drawbacks of each one.
+This is of great importance for the future of the Web of Linked Data, as the same problems of volume that appear in the Web will arise as the Web of Data grows.
+The main target of this work focuses on helping researchers in the Semantic Web community to identify and understand the problem of ranking information.
+After a review of the literature, we have selected the most relevant algorithms according to their impact in this field.
+In this way, we have tried to homogenize the vocabulary employed with the aim of settling a common reference for semantic ranking methodologies.
 

### 2012-07-20 trunk/tr-rankingsurvey/overview.tex
Abstract, Intro, Ranking problem, Applications and initial list of sample approaches added

\section{The Ranking Problem}\label{sec:ranking}
A ranking algorithm implements a function, which accepts a set of items and returns an ordered version of the set without modifying the items. The function is implemented taking into account certain preferences that determine the order of the items. In this way, the same collection of items could be ranked following different approaches, i.e. different order functions. 
Formally, a ranking algorithm implements a function of total order $f: X \rightarrow \Re$ such that for any $a, b \in X: f(a) \leq f(b) \leftrightarrow a \prec b$, where $\prec$ defines a binary relationship on the set $X$. Note that $\prec$ makes reference to the factor that guides the ranking strategy.

%TODO change image size and orientation
\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=0.35\textwidth]{figs/algo-arch.pdf}
\caption{{\bf Structure of a ranking algorithm}}
\label{fig:fig1}
\end{center}
\end{figure}

Figure \ref{fig:fig1} depicts the components that integrate the functionality of a ranking algorithm. The input to any ranking method is a bunch of raw data that needs to be inspected to get the relevant information out of it. This task is carried out by the feature extractor, which generates a data model that will be used for the ranking function described above to produce the ranked set of items. The feature extractor together with the data structures that allocate the data model and the ranking function compose the functional architecture of the ranking algorithm.

\subsection{Ranking on Structured Data}
Structured data: can be conceived as graphs\\
Ranking: traditionally, core IR problem, many techniques have been adopted to deal with structured data\\
Ranking over structured data: ranked list of results\\
Types of ranked results: entities, relations, subgraphs, entire datasets (graphs)\\
Evaluating ranked results: different metrics\\

\subsection{Ranking on Structured Data vs. Ranking on Unstructured Data}
Discuss differences\\
Say we focus on structured data\\

\subsection{Ranking vs. Matching}
Discuss differences\\
Say we focus on ranking\\

\subsection{Applications} 
%Optional / can be short but should provide good coverage of different application domains
Using information is directly related to the way in which it is presented and consumed. This means that without methodologies to exploit properly the data it can be very difficult to deal with the huge amount of information available. This function is carried out by ranking algorithms and a proof of its applicability is the different use cases where they can be deployed. In the following, we describe how ranking algorithms are used within semantic search engines, semantic browsers and interlinking approaches.

\subsubsection{Semantic Search Engines}
Like in the traditional hypertext Web, semantic search engines are used as the entry point to navigate the information burden. The architecture of these systems is built on top of a crawler which is responsible for automatically exploring the Web of Data to retrieve any piece of semantic information (RDF, RDFa, etc.). This stream of information fed by the crawler constitutes the knowledge base that will be used to resolve the users ́s queries. It is in this phase where ranking algorithms play their role, by means of manipulating the information in the knowledge base to calculate the relevance of results.
Table \ref{tab:tab} shows the existent semantic search engines and the correspondence with the underlying implemented ranking algorithm.

TODO table with sse

In the following, we describe the approach followed by each search engine.

\paragraph{Sindice}
Sindice (Tummarello, Delbru, Oren, 2007) is a lookup service built with the aim of enabling information retrieval over the resources of the semantic Web. Through crawling techniques, Sindice analyzes each source of data, i.e. RDF document or SPARQL endpoint, and extracts all the resources encountered. The information related to these resources is stored in an index that can be queried based on full-text search, URIs or inverse-functional properties (IFPs).

\paragraph{SemSearch}
SemSearch (Lei, Uren, Motta, 2006) is a keyword-based semantic search engine that tries to bring the power of the semantic Web to all kind of users regardless of their knowledge about semantic technologies while producing accurate results at the same time. It provides a Google- like interface which ranks the search results according to the degree of their proximity to the user query. The search engine takes two factors into consideration when ranking. One is the matching distance between each keyword and its semantic matches. The other is the number of keywords the search results satisfies. The matching strategy relies on simple string comparisons between the user keywords and the labels available in the RDF data sources. Authors justify this choice stating that “from the user point of view labels often catch the meaning of semantic entities in an understandable way”.

\paragraph{Swoogle}
Swoogle (Ding et al., 2004) was intended as a search engine for retrieving semantic Web documents. With this aim it is composed of a crawler than constantly checks the Web looking for new RDF or OWL documents containing any kind of semantic information. Once the documents are found, the system uses an index to store the information and facilitate the retrieval. In the same way than traditional search engines over HTML documents, Swoogle allows users to look for any term within the indexed documents. The way how results are returned to the user is determined by the OntologyRank algorithm.

\paragraph{Falcons}
Falcons (Cheng, \& Qu, 2009) is a keyword-based search engine supporting full-text queries related to data in the semantic Web. It works at entity level granularity, and so, for each entity it shows information about its types, possible labels and number of documents where it appears. The search engine is fully implemented relying on an index that stores textual information about each entity, as well as its relationships with other entities. Falcons applies the TF-IDF technique over the index to retrieve information about the entities and therefore about the ontologies where they appear.

\paragraph{Sig.ma}
(Tumarello et. al, 2009) describes the implementation of Sig.ma, an application that shows a possible interpretation of how the Web of Data functionality should look like. It combines large scale semantic web indexing, logic reasoning, data aggregation heuristics, ad hoc ontology consolidation, user interaction and refinement.
Sig.ma is built on top of Sindice, which means it follows the same ranking approach. More than a search engine, it has been designed with the aim of mashing up information, i.e., it gathers information from different sources and place it in a single interface to provide a richer experience to the user. Sig.ma can be considered as an extension to Sindice, which enables a refinement towards entity-oriented search.

\paragraph{SWSE}
The Semantic Web Search Engine (Hogan et. al, 2010) unlike other search engines works over Linked Open Data. It consists of crawling, data enhancing, indexing and a user interface for search, browsing and retrieval of information. It has been designed to deal with two main challenges: scalability to large amounts of data and tolerance to heterogeneous, noisy and conflicting data retrieved from different sources.
The search performed by the SWSE is focused on entities over instance data, in contrast to other approaches like Swoogle, which follows a document oriented search over ontologies. The underlying ranking strategy of SWSE relies on ReConRank, which means that it focuses on provenance of data to establish an order for results.

\paragraph{Watson}
Watson (d’Aquin et. al, 2007) is intended to be a gateway to access the content of the semantic Web. It provides keyword search facilities over semantic Web documents, but additionally provides search over entities. Authors establish that while following a traditional Web approach to retrieve information about ontologies is useful, it is not enough and must be complemented with specific techniques to exploit the semantics they model. In this way, approaches like OntologyRank that rely on the popularity of ontologies to establish the order of results are criticized, as they do not reflect the real quality of the information contained. In real scenarios, where the main aim of these systems is the reutilization, the quality of the ontology can be as important as its popularity. Therefore, Watson implements a ranking strategy similar to the one implemented by AKTiveRank, where the scores are calculated relying on exhaustive analysis to derive the quality of data.

\subsubsection{Semantic Browsers}
Browsers are the tool utilized by users to access the information on the Web. This means that the way how the information is presented to the users is a decisive factor for its consumption, because it determines the next steps for the user while the exploration. In the same way than traditional browsers explore the links between hypertext documents, semantic browsers intend to explore links between RDF data. Tabulator (Berners-Lee et al. 2006; Berners-Lee et al. 2008) and Marble (Becker \& Bizer, 2008) are two examples of semantic browsers that apply ranking methodologies to analyze the provenance of data at the same time that merging information from different data sources.

\subsubsection{Interlinking}
Interlinking can be defined as the process of creating new links between related entities in different RDF datasets for which there are not any link previously established. The final aim of interlinking is creating a network of related entities in order to facilitate its discovery and navigation of the Web of Data.
As introduced in (Bizer et. al, 2009), automatic and semi-automatic interlinking approaches rely on the computation of similarities between entities, mostly guided by related work on record linkage, duplicate detection in databases and ontology matching. However, what is not directly mentioned is that ranking algorithms can complement interlinking methods by providing previous analysis of data. Statistics about entities can give information about the truthfulness of concepts as stated in (Bizer \& Cyganiak, 2009). For example, if a concept representing the city of Barcelona is pointed from different sources where properties make reference to this city, it means there is a chance that this concept really represents the city of Barcelona. In this way, the number of links targeting the same concept could be used as an indicator of the veracity of such concept when referring to an entity of the real world.

### 2012-07-20 trunk/tr-rankingsurvey/paper.tex
Abstract, Intro, Ranking problem, Applications and initial list of sample approaches added

@@
 \begin{abstract}
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-\keywords{First keyword \and Second keyword \and More}
+Ranking information resources is a task that usually happens within more complex workflows and that typically occurs in any form of information retrieval, being commonly implemented by Web search engines.
+By filtering and rating data, ranking strategies guide the navigation of users when exploring large volumes of information items.
+There exist a considerable number of ranking algorithms that follow different approaches focusing on different aspects of the complex nature of the problem, and reflecting the variety of strategies that are possible to follow.
+With the growth of the Web of Linked Data, a new problem space for ranking algorithms has emerged, as the nature of the information items to be ranked is very different from the case of Web pages.
+As a consequence, existing ranking algorithms have been adapted to the case of Linked Data and some specific strategies have started to be proposed and implemented.
+Researchers and organizations deploying Linked Data solutions thus require an understanding of the applicability, characteristics and state of evaluation of ranking strategies and algorithms as applied to Linked Data.
+Elaborating a technical comparison of ranking strategies is a difficult task due to the heterogeneity of approaches and the diversity of data used for the task.
+Further, in many cases, the source code of the implementations is not available, but just a methodology describing the behavior of a proposed algorithm.
+However, a thorough analysis is still required to understand the advantages and drawbacks of the different approaches.
+In order to fulfill this need, this survey proposes a reference framework that formalizes and contextualizes under a common terminology the problem of ranking Linked Data.
+In addition, an analysis and contrast of the similarities, differences and applicability of the different approaches is provided.
+
+\keywords{Linked data \and information retrieval \and semantic search \and ranking algorithms \and link analysis \and Semantic Web data management}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 
-\section{Style}
-\label{sec:1}
-Text with citations \cite{RefB} and \cite{RefJ}.
-\subsection{Subsection title}
-\label{sec:2}
-as required. Don't forget to give each section
-and subsection a unique label (see Sect.~\ref{sec:1}).
-\paragraph{Paragraph headings} Use paragraph headings as needed.
-\begin{equation}
-a^2+b^2=c^2
-\end{equation}
+%\section{Style}
+%\label{sec:1}
+%Text with citations \cite{RefB} and \cite{RefJ}.
+%\subsection{Subsection title}
+%\label{sec:2}
+%as required. Don't forget to give each section
+%and subsection a unique label (see Sect.~\ref{sec:1}).
+%\paragraph{Paragraph headings} Use paragraph headings as needed.
+%\begin{equation}
+%a^2+b^2=c^2
+%\end{equation}
 
 % For one-column wide figures use
-\begin{figure}
+%\begin{figure}
 % Use the relevant command to insert your figure file.
@@
 % figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:1}       % Give a unique label
-\end{figure}
+%\caption{Please write your figure caption here}
+%\label{fig:1}       % Give a unique label
+%\end{figure}
 %
 % For two-column wide figures use
-\begin{figure*}
+%\begin{figure*}
 % Use the relevant command to insert your figure file.
@@
 % figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:2}       % Give a unique label
-\end{figure*}
+%\caption{Please write your figure caption here}
+%\label{fig:2}       % Give a unique label
+%\end{figure*}
 %
 % For tables use
-\begin{table}
+%\begin{table}
 % table caption is above the table
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
+%\caption{Please write your table caption here}
+%\label{tab:1}       % Give a unique label
 % For LaTeX tables use
-\begin{tabular}{lll}
-\hline\noalign{\smallskip}
-first & second & third  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-number & number & number \\
-number & number & number \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
+%\begin{tabular}{lll}
+%\hline\noalign{\smallskip}
+%first & second & third  \\
+%\noalign{\smallskip}\hline\noalign{\smallskip}
+%number & number & number \\
+%number & number & number \\
+%\noalign{\smallskip}\hline
+%\end{tabular}
+%\end{table}
 
@@
 \input{other}
-\input{ltr}
+\input{combining}
 \input{sample}

### 2012-07-20 trunk/tr-rankingsurvey/future.tex
initial thoughts about open challenges

\section{Open Research Challenges}\label{sec:challenges}

While this survey evidences a considerable degree of progress in ranking for the Web of Linked Data, it also evidences some areas that are still to be developed and several problems that need further research and development. They include the following:
\begin{itemize}
	\item How to add support for data streams. The development of high scalable models is a must to deal with this kind of environments.
	\item Lack of mechanisms to capture the social dimension of linked open data and its exploitation in ranking.
	\item How to include support for personalized ranking functions. If users are the consumers of the information they should be able to customize the consumption.	
\end{itemize}

### 2012-07-28 trunk/tr-nlisurvey/src/nli-survey.tex
section 2

--- 2012-07-11 trunk/tr-nlisurvey/src/document.tex
@@
 
-% added packages
 \usepackage{multirow}
 \usepackage{url}
+\usepackage{color}
 
@@
 \usepackage[pdftex]{graphicx}
-% declare the path(s) where your graphic files are
 \graphicspath{{images/}}
-% and their extensions so you won't have to specify these with
-% every instance of \includegraphics
 \DeclareGraphicsExtensions{.png}
@@
 
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\newcommand{\TODO}[1]{{\textcolor{green}{TODO:#1}}}
-
+%\hyphenation{op-tical net-works semi-conduc-tor}
+
+\newcommand\TODO[1]{{\textcolor{red}{TODO:#1}}}
 \begin{document}
@@
 
-\IEEEcompsoctitleabstractindextext{%
+\IEEEcompsoctitleabstractindextext{
 \begin{abstract}
-%\boldmath
-Abstract will be written later\ldots
+Natural language interfaces to databases allow users to formulate queries in
+natural language to databases. The benefits are twofold: first, users do not
+have to know how the data have been modeled in the database, what term refers to
+what database entity. Second, these systems can interface several data sources
+that are possibly of different implementation and which data belong to different
+domains.
+In this paper we provide a survey of major natural language interfaces, from the
+very beginning of artificial intelligence to most recent systems.
 \end{abstract}
@@
 \begin{keywords}
-Computer Society, IEEEtran, journal, \LaTeX, paper, template.
+Natural Language, Database
 \end{keywords}}
@@
 \label{sec:introduction}
-
-%{\bf Possible quotation:} M.P. Schutzenberger, 1970: (in the AI domain: humans
-%learn how to use systems, see the usage of Google, keywords etc.)
-
 Natural Language (NL) is the most natural and easy way to express information
@@
 Retrieval (IR) and Database communities. In the IR community however, the
-keyword paradigm has become the most popular, for sure because of the success of
-commercial search engines. NL interfaces for unstructured documents are
-refered to as Question Answering (Q\&A) systems, that have received much
-researchers' attention as the Web had made avaialble huge amount of textual
-data, and recently as the famous {\it Jeopardy!} quiz was won by IBM's {\sc
+keyword paradigm has become the most popular, for sure because of the success
+of commercial search engines. 
+%NL interfaces for unstructured documents are refered to as Question Answering
+%(Q\&A) systems, that have received much researchers' attention as the Web had
+Interfaces to unstructured documents has become popular as
+the Web has made available huge amount of textual data, and recently as the
+famous {\it Jeopardy!} quiz was won by IBM's {\sc
 Watson}~\cite{FerrucciBCFGKLMNPSW10} system.
+This trend seems to evolve slightly. For instance,
 {\sc WolframAlpha}\footnote{\url{http://www.wolframalpha.com/}} is a popular
@@
 decades, but the field seems to have known a renewed interest for a few
-years, probably thanks to the development of the semantic Web. {\bf See also
-the quotation in~\cite{DBLP:journals/semweb/LopezUSM11}: users prefer NL interfaces
-than logic used in the Semantic Web.}
-However, the challenge of answering NL
-questions is far from being solved~\cite{Kotov:2010:TNQ:1772690.1772746}.
+years, probably thanks to the development of the semantic Web. 
+Today's semantic technologies can be directly manipulated by experts, and
+therefore there is still a need for interfaces. Indeed, users prefer NL
+interfaces than the logic which is used in the semantic
+Web~\cite{Kotov:2010:TNQ:1772690.1772746}.
+However, the challenge of answering NL questions is far from being
+solved~\cite{Kotov:2010:TNQ:1772690.1772746}.
 
@@
 
-In this survey, we try to point out the major dimensions of existing systems
-and to present the new trends and challenges of state-of-the-art systems.
+In this survey, we outline the major dimensions of existing systems
+and present the new trends and challenges of state-of-the-art systems.
 The history of NL interfaces can be developped as follows:
@@
 \end{enumerate}
-
-We will present the ``big picture'' of the approaches in
-section~\ref{sec:big-picture}.
+We present section~\ref{sec:main-dimensions} the main dimensions used throughout
+the paper.
 
@@
 \section{Main Dimensions}
-In this section, we introduce the main dimensions based on which NLI approaches can be distinguished. The input to every NLI is the (1) \emph{data}, 
-and (2) \emph{user questions} representing information needs, which are translated to an (3) \emph{internal representation} of the needs employed by the system and/or directly mapped to 
-(4) \emph{database queries} that finally, are executed by the underlying query engine to produce the final answers.
-The main problem tackled by a NLI approach is to transform the question to the internal representation and then to the database query (2 $\mapsto$ 3 $\mapsto$ 4), or to directly mapped the question to the query (2 $\mapsto$ 4).
-This problem is hard when considering the large and rapidly evolving mass of structured data that have become available.
-The major challenges modern NLI systems are facing in this regard is to operate across domains (5, \emph{domain-independence}) as well as to adopt to new domains (6, \emph{portability}).
-For evaluating the quality of the NLI output, different (6) \emph{metrics} based on the user questions the system can understand as well as the database queries it can produce, have been proposed.
-
-----------
+\label{sec:main-dimensions}
+In this section, we introduce the main dimensions based on which NLI approaches
+can be distinguished. The input to every NLI is the (1)~\emph{data}, and
+(2)~\emph{user questions} representing information needs, which are translated
+to an (3)~\emph{internal representation} of the needs employed by the system
+and/or directly mapped to (4)~\emph{database queries} that finally, are
+executed by the underlying query engine to produce the final answers. The main
+problem tackled by a NLI approach is to transform the question to the internal
+representation and then to the database query (2 $\mapsto$ 3 $\mapsto$ 4), or
+to directly mapped the question to the query (2 $\mapsto$ 4). This problem is
+hard when considering the large and rapidly evolving mass of structured data
+that have become available. The major challenges modern NLI systems are facing
+in this regard is to operate across domains (5)~\emph{domain-independence} as
+well as to adopt to new domains (6)~\emph{portability}. For evaluating the
+quality of the NLI output, different (7)~\emph{metrics} based on the user
+questions the system can understand as well as the database queries it can
+produce, have been proposed.
+
 \TODO{old content that might be considered:} 
@@
 
-----------
-
 \subsection{Data}
 \label{sec:data}
-\TODO{Discuss the different types of structured data models that have been used, make clear that while they vary in expressiveness, they commonly enables capturing resources/entities/objects and relationships between then.
-Besides domain information captured in terms of entities and relationships, also point out other popular types of information that have considered, e.g.
-temporal and spatial information}
-
-Structured data:
+%\TODO{Discuss the different types of structured data models that have been
+% used, make clear that while they vary in expressiveness, they commonly enables
+%capturing resources/entities/objects and relationships between them. Besides
+%domain information captured in terms of entities and relationships, also point
+%out other popular types of information that have considered, e.g. temporal and
+%spatial information}
+
+There is a great variety of structured data sources:
 \begin{itemize}
-  \item relational databases; data warehouses
+  \item early data structures (Prolog databases; hierarchical lists)
+  \item relational databases
   \item XML databases
-  \item early data structures (Prolog databases; list-structured databases)
-  \item ontologies; {\it linked data}
+  \item ontologies; \emph{linked data}
 \end{itemize}
-%Data structured in a database belong to a {\it domain}\ldots
-In the survey, we refer to {\it database elements} which stand for named
-properties of the database. For instance in a relational database, they stand
-for relation names, attributes names and values, \ldots
-
-Data structures are associated with a data model or schema, which is explicitely
-defined in modern databases.
-Despite the effort of modeling and conceptualizing structured data, there is
-still a gap between the physical view of structured data (database
-administrators' view point) and the conceptual view of end users; interfaces
-concerned in this survey attempt to bridge this gap.
-
-\subsection{Question}
-\TODO{Discuss different types user questions}
+Structures of these data sources are different, as well as the way to access and
+modify data (i.e. how to query data, which language to use, etc.).
+For example, relational databases are represented with the entity/relationship
+model and queries are usually expressed in a SQL-like language. Hierarchical
+lists are hierarchical structures (like XML documents) that are composed of
+embeded key-value pairs with optional attributes. XML documents are more
+generic, since ``keys'' in those documents are nodes (i.e. can be trees
+themselves). 
+Ontologies are not more generic than XML databases from the structure point of
+view, but allow to express easily semantic relationships.
+
+Dome data structures are dedicated to some types of information. For instance,
+temporal databases are similar to relational databases, but capture \emph{time}
+in addition. Indeed, in some domains, the truth value of a fact or of
+a resultset is determined by a \emph{timestamp}, while in classic database facts
+are true in general.
+
+At the end, all these data structures manipulate \emph{entities} (i.e. named
+properties of the database) and \emph{relations} between these entities.
+Any database selection query can be reduced to a set of constraints on these
+entities and relations.
+
+\subsection{Users' questions}
+%\TODO{Discuss different types user questions}
 
@@
 to query the data in a formal language (e.g., SQL).
+
+Question typing is a research task within the Q\&A field.
+This community has classified questions in \emph{facto\"id questions} (i.e.
+questions that can be answered by an \emph{objective} fact, typically questions
+staring with wh-words except ``why'') and \emph{complex questions} which
+answers are usually \emph{subjective} to the answerer, and for which there
+might be several \emph{true} answers, possibly contradicting each other.
+Complex questions can be ``why''-questions, ``how''-questions or
+\emph{definition}-questions.
+Facto\"id question is defined by Soricut \&
+Brill~\cite{Soricut:2006:AQA:1127331.1127342} as questions ``for which a
+complete answer can be given in 50 bytes or less, which is roughly a few
+words''.
+Several finer classification have been proposed in specific domains or
+applications. 
+For instance, in the case of temporal questions, Saquete et
+al.~\cite{Saquete:2004:SCT:1218955.1219027} have proposed the classification
+reproduced table~\ref{tab:saquete-classification}.
+\begin{table}
+\centering
+\begin{tabular}{ll}\hline
+\multicolumn{1}{c}{\textbf{Question type}} &
+\multicolumn{1}{c}{\textbf{Example}}\\\hline\hline
+Single event temporal questions &
+``When did Jordan close \\
+ without temporal expressions & the port of Aqaba to Kuwait?''\\\hline 
+ Single event temporal questions & 
+``Who won the 1988 New \\
+ with temporal expressions & Hampshire republican primary?''\\\hline
+ \multirow{2}{*}{Multiple events temporal questions} & ``What did G. Bush do
+ after\\
+  & the U.N. Security Council\\
+ \multirow{2}{*}{with temporal expressions} & ordered a global embargo on\\
+  & trade with Irak in August 90?''\\\hline
+  \multirow{2}{*}{Multiple events temporal questions} & ``What happened to world
+  oil\\
+   & prices after the Iraqi\\
+  without temporal expressions & annexation of Kuwait?''\\\hline
+
+\end{tabular}
+\caption{Question classification for temporal databases from~\cite{Saquete:2004:SCT:1218955.1219027}}
+\label{tab:saquete-classification}
+\end{table}
+
 \subsubsection{Keyword query}
@@
 popular.
-\cite{Hearst:2011:NSU:2018396.2018414} reports that the number of words
+Hearst~\cite{Hearst:2011:NSU:2018396.2018414} reports that the number of words
 in queries over Web search engines trends to increase (the experiment compared
@@
 
-\subsection{Internal Representation}
+\subsection{Internal representation}
 \label{sec:big-picture-syntactic}
-\TODO{Discuss different types user questions}
 
@@
 
-\subsection{Database Query}
+\subsection{Database queries}
 \label{sec:big-picture-semantic}
-\TODO{Discuss query languages; discuss the different types of queries expressed by these languages, e.g. entity queries, relational queries, additional constructs such as group by etc.}
+\TODO{Discuss query languages; discuss the different types of queries expressed
+by these languages, e.g. entity queries, relational queries, additional
+constructs such as group by etc.}
 
@@
 
-TOBECONSIDERED
--------
 \subsubsection{Expressivity of database query}
 \label{sec:big-picture-expressivity}
------------
-
-\subsection{Results}
-\label{sec:big-picture-results}
+
+%\subsection{Results}
+%\label{sec:big-picture-results}
+
 NL interfaces produce database queries.
@@
 
-\subsection{Query-independence}
+\subsection{Domain-independence}
+
 \subsection{Portability}

### 2012-08-06 tr-nlisurvey/src/nli-survey.tex
commit

--- 2012-07-28 trunk/tr-nlisurvey/src/nli-survey.tex
@@
 complete answer can be given in 50 bytes or less, which is roughly a few
-words''.
+words'' (see also Kwok et al. ``Scaling question answering to the Web, WWW).
 Several finer classification have been proposed in specific domains or
@@
 \label{sec:big-picture-semantic}
-\TODO{Discuss query languages; discuss the different types of queries expressed
-by these languages, e.g. entity queries, relational queries, additional
-constructs such as group by etc.}
-
-The parse tree (which may or not contain semantic information in parse tree
-nodes) must then be {\it interpreted} in some internal semantic representation.
-Table~\ref{tab:semantic-meaning-representation} displays semantic meaning
-representations used in different systems.
-\begin{table*}[!h]
+%\TODO{Discuss query languages; discuss the different types of queries expressed
+%by these languages, e.g. entity queries, relational queries, additional
+%constructs such as group by etc.}
+
+\begin{table*}[h!]
 \centering
@@
 \end{table*}
+
+The parse tree (which may or not contain semantic information in parse tree
+nodes) must then be {\it interpreted} in some internal semantic representation.
+Table~\ref{tab:semantic-meaning-representation} displays semantic meaning
+representations used in different systems.
 As shown in this table, the internal semantic representation can be or not the
@@
 
+\subsubsection{Query languages}
+Relational databases are generally associated with the SQL query language (and
+temporal databases are associated to an extension of SQL called temporal SQL).
+Multidimensional databases (e.g., data warehouses) are associated with MDX,
+which is a SQL-like query languages dedicated for handling measures, dimensions
+and hierarchies (key concepts of multidimensional models).
+Other data stuctures are associated with their own query language. For instance,
+hierarchical lists (or specification lists) is not associated with a language,
+but to a similar structure, which is a template where empty slots correspond to
+the expected items of the resultset. XML databases are associated to XPath, and
+semantic databases (e.g., RDF) are usually queried with languages derived from
+SPARQL which looks similar to SQL.
+Recently, new query languages have appeared (``no-SQL''). 
+\TODO{Develop\ldots}
+
+\paragraph{Selection}
+\label{sec:query-languages-selection}
+a selection consists in choosing the expected database attribute to appear in
+the resultset.
+In SQL, the selection is expressed as \verb?SELECT t.x?, where $t$ is a table
+and $x$ a field or attribute belonging to $t$. In SPARQL it corresponds to
+\emph{variables} that are defined in the query, and that must satisfy the
+constraints defined in the \verb?WHERE? section of the SPARQL query (see
+section~\ref{sec:query-languages-constraints}).
+In MDX, the selection corresponds to the ordered set of dimensions or measures
+that should appear in the resultset, with the information about the level of the
+expected attributes in the hierarchy, and the filters. For instance,
+\verb?SELECT Country.[All members]? corresponds to the selection of the
+dimension ``Country'' with no filter (i.e. selection of all members of the
+dimension ``Country'').
+Selection for a hierarchical list corresponds to a slot in the structure
+template.
+A selection in a XPath query corresponds to\ldots\footnote{\TODO{Find what}}
+In SPARQL, a selection can be expressed also differently. Indeed, the output of
+a SPARQL query can be a data structure of the same kind than the data themselves
+(i.e. a graph). This is performed with the \verb?CONSTRUCT? keyword.
+
+\paragraph{Constraints}
+\label{sec:query-languages-constraints}
+Canstraints in database queries aim at reducing the size of the resultset.
+In the case of SQL, SPARQL and MDX, such constraints are introduced with the
+\verb?WHERE? keyword. For SQL, these constraints can define how different tables
+can be \emph{joined} together such that attributes belonging to different tables
+can appear in a single view (i.e. in the resultset). Other kinds of constraints
+are about the values of attributes.
+For SPARQL, the constraints are expressed with \emph{triples} (which can be
+made of some \emph{blank node} or undefined node). Thus, a SPARQL constraint is
+about relations between entities (see \emph{joins} for relational databases), or
+about entities themselves (which type must be the entity? If this is a
+\emph{litteral}, in what range of value must it belong?,etc.).
+
+\paragraph{Query modifiers}
+\label{sec:query-languages-modifiers}
+Conceptually, modifiers are primitives that modify the resultset afterwards.
+Such primitives can - order the resultset along a given attribute (e.g.,
+\verb?ORDER BY? in SQL); - select at most $n$ \emph{tuples} of the resultset
+(e.g., \verb?LIMIT x? in SQL); - select only different tuples (e.g., the
+keyword \verb?DISTINCT? in SQL).
+In SPARQL, it is possible to test if a set of constraints can be satisfied from
+the data, and to combine these tests with optional constraints (\verb?OPTIONAL?
+keyword) or mandatory constraints (\verb?FILTER? keyword).
+
 \subsubsection{Expressivity of database query}
@@
 \subsection{Domain-independence}
+Domain-independance is the ability of a system, to operate accross different
+domains simultaneously. 
+In practice, this means that a domain-independant system would be on top of
+different data sources that belong to different domains, and that this system is
+able to meet users' requests for any of these domains. 
+The main difficulty of building domain-independant systems is the ability to
+translate NL constructions differently in the different application domains.
+For instance, the qualitative expression ``middle-aged'' can be interpreted
+completely differently accross the different domains.
 
@@
 \subsubsection{Classic translation approach}
-TOBECONSIDERED
-----------
+
 The classic translation approach consists in going from (1) to (4).

### 2012-08-10 tr-nlisurvey/src/nli-survey.tex
Standard commit Following sections have been updated: sections 2 and 3

@@
 \markboth{Journal of \LaTeX\ Class Files,~Vol.~6, No.~1, January~2007}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer
+Society Journals}
 
@@
 \subsection{Domain-independence}
+\label{sec:main-dimensions-domain-independance}
 Domain-independance is the ability of a system, to operate accross different
@@
 \subsection{Portability}
+\label{sec:main-dimensions-portability}
+A system is said \emph{portable} if it can be easily configured for different
+domains (than the domain for which it was first designed).
+Domain-independance (section~\ref{sec:main-dimensions-domain-independance}) is a
+step further, because different domains are considered simultaneously; while in
+portable systems the challenge is to ease the configuration.
+Portable systems are also referred to as \emph{configurable} interfaces in the
+following.
+Configurable interfaces let users improve the system's capabilities, both the
+linguistic coverage $S$ and the system coverage $K$ (see
+Fig.~\ref{fig:interface}).
+
+Minock et al.~\cite{Minock:2010:CSB:1715942.1716190} have identified three kinds
+of configuration applicable to NL interfaces:
+\begin{itemize}
+  \item let users name database elements, so that phrases used in the question
+  can be easily mathed with database elements
+  \item offer a GUI that generates automatically semantic rules or a grammar for
+  translating NL questions to database queries
+  \item use machine learning techniques to induce semantic rules or a grammar
+  from annotated corpora
+\end{itemize}
+These ways of configuring interfaces are not equally costly: for instance, the
+third one (machine learning techniques) can be highly costly if it requires a
+huge volume of annotated data. The cheapest configuration is based on user
+interaction, where no initial configuration is needed, but domain-specific
+knowledge is learned based on user interaction. An example of such a
+system is {\sc NaLIX}~\cite{Li:2005:NIN:1066157.1066281}.
 
@@
 The main problem to solve is to map user's intent expressed in a natural way
-(say unstructured way) to a database query, which is a very structured
-expression where there is no room for ambiguity unlike natural language.
-The problem can be formalized as:
+(say unstructured way) to a database query, which is a structured expression
+where there is no room for ambiguity unlike natural language. The problem that
+NLI systems try to solve, is equivalent to finding a mapping $f$ between natural
+language questions $q$ and families of structured queries $(q^\prime_i)_i$
+(where the index corresponds to the \emph{rank} of the structured query):
 \begin{equation}
@@
 \begin{array}{l}
-Q\rightarrow (Q^\prime\times S)^I\\
-q\mapsto(q^\prime_i, s_i)_i
+Q\rightarrow (Q^\prime)^I\\
+q\mapsto(q^\prime_i)_i
 \end{array}\right.
 \end{equation}
-where $q$ is the user's question, $q^\prime_i$ a structured query and $s_i$ a
-score associated to the structured query $q^\prime_i$, and used to rank the
-query (the index $i\in I=[0,n]$ is the rank).
+where $i\in I=[0,n]$ is the index of $q^\prime_i$.
 
@@
 \label{sec:overview}
-
-\begin{figure*}
-\centering
-\includegraphics[width=12cm]{images/query-language}
-\caption{Blabla}
-\label{fig:query-languages}
-\end{figure*}
-
-\subsubsection{Classic translation approach}
-
+% \begin{figure*}
+% \centering
+% \includegraphics[width=12cm]{images/query-language}
+% \caption{Blabla}
+% \label{fig:query-languages}
+% \end{figure*}
+
+\textbf{Classic translation approach}
 The classic translation approach consists in going from (1) to (4).
@@
 
-\subsubsection{Iterative approach}
+\textbf{Iterative approach}
 The iterative approach does not go directly from (1) to (3), but goes back to
@@
 query.
-
-\subsubsection{Configurable interfaces}
-Configurable interfaces let users improve the system's capabilities, in
-particular the linguistic coverage. 
-Minock et al.~\cite{Minock:2010:CSB:1715942.1716190} have identified three kinds
-of configuration applicable to NL interfaces:
-\begin{itemize}
-  \item let users name database elements, so that phrases used in the question
-  can be easily mathed with database elements
-  \item offer a GUI that generates automatically semantic rules or a grammar for
-  translating NL questions to database queries
-  \item use machine learning techniques to induce semantic rules or a grammar
-  from annotated corpora
-\end{itemize}
-The configuration is particularly important when porting the interface to other
-domains. However the three kinds of configuration mentionned above are not
-equally costly: for instance, the third one (machine learning techniques) can be
-hightly costly if it requires a huge volume of annotated data. The cheapest
-configuration is based on user interaction, where no initial configuration is
-needed, but domain-specific knowledge is learned based on user interaction. An
-example of such a system is {\sc NaLIX}~\cite{Li:2005:NIN:1066157.1066281}.
-
-Most recent interfaces integrate configuration capabilities, since it allows
-domain portability which is a great improvement of interfaces. In the following
-we will emphasize the role of user interaction ({\it feedback-driven
-approaches}) and machine learning techniques ({\it learning-based approaches}).
-
----------------
 

### 2012-08-10 trunk/tr-nlisurvey/src/nli-survey.tex
Standard commit Following sections have been updated: section 4: picture

@@
 
+% multirow
 \usepackage{multirow}
+
+% url
 \usepackage{url}
+
+% allow colors for inline comments
 \usepackage{color}
 
+% draw pictures with tikz package
+\usepackage{tikz}
+
 \ifCLASSOPTIONcompsoc
@@
 \ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
 \graphicspath{{images/}}
@@
 
-\newcommand\TODO[1]{{\textcolor{red}{TODO:#1}}}
+\newcommand\TODO[1]{{\textcolor{red}{TODO:#1\\}}}
 \begin{document}
@@
 \subsection{Domain-independence}
+\label{sec:main-dimensions-domain-independance}
+Domain-independance is the ability of a system, to operate accross different
+domains simultaneously. 
+In practice, this means that a domain-independant system would be on top of
+different data sources that belong to different domains, and that this system is
+able to meet users' requests for any of these domains. 
+The main difficulty of building domain-independant systems is the ability to
+translate NL constructions differently in the different application domains.
+For instance, the qualitative expression ``middle-aged'' can be interpreted
+completely differently accross the different domains.
 
 \subsection{Portability}
+\label{sec:main-dimensions-portability}
+A system is said \emph{portable} if it can be easily configured for different
+domains (than the domain for which it was first designed).
+Domain-independance (section~\ref{sec:main-dimensions-domain-independance}) is a
+step further, because different domains are considered simultaneously; while in
+portable systems the challenge is to ease the configuration.
+Portable systems are also referred to as \emph{configurable} interfaces in the
+following.
+Configurable interfaces let users improve the system's capabilities, both the
+linguistic coverage $S$ and the system coverage $K$ (see
+Fig.~\ref{fig:interface}).
+
+Minock et al.~\cite{Minock:2010:CSB:1715942.1716190} have identified three kinds
+of configuration applicable to NL interfaces:
+\begin{itemize}
+  \item let users name database elements, so that phrases used in the question
+  can be easily mathed with database elements
+  \item offer a GUI that generates automatically semantic rules or a grammar for
+  translating NL questions to database queries
+  \item use machine learning techniques to induce semantic rules or a grammar
+  from annotated corpora
+\end{itemize}
+These ways of configuring interfaces are not equally costly: for instance, the
+third one (machine learning techniques) can be highly costly if it requires a
+huge volume of annotated data. The cheapest configuration is based on user
+interaction, where no initial configuration is needed, but domain-specific
+knowledge is learned based on user interaction. An example of such a
+system is {\sc NaLIX}~\cite{Li:2005:NIN:1066157.1066281}.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=12cm]{images/query-language}
-\caption{Blabla}
-\label{fig:query-languages}
-\end{figure*}
-
-\subsubsection{Classic translation approach}
-TOBECONSIDERED
-----------
+\begin{tikzpicture}
+
+\def \n {5}
+\def \radius {3cm}
+\def \margin {8} % margin in angles, depends on the radius
+
+\foreach \s in {1,...,\n}
+{
+  \node[draw, circle] at ({360/\n * (\s - 1)}:\radius) {$\s$};
+  \draw[->, >=latex] ({360/\n * (\s - 1)+\margin}:\radius) 
+    arc ({360/\n * (\s - 1)+\margin}:{360/\n * (\s)-\margin}:\radius);
+}
+\end{tikzpicture}
+\caption{Big picture of NLI systems}
+\label{fig:big-picture}
+\end{figure}
+
+\textbf{Classic translation approach}
 The classic translation approach consists in going from (1) to (4).

### 2012-08-10 trunk/tr-nlisurvey/src/nli-survey.tex
Standard commit Following sections have been updated: section 4: picture

@@
 \usepackage{tikz}
+\usetikzlibrary{arrows, petri, topaths}
+\usepackage{tkz-berge}
 
@@
 
+\begin{figure*}
+\centering
+\begin{tikzpicture}[transform shape]
+%\tikzset{VertexStyle/.append style = {minimum size = 3pt}}
+\node at (0,0) [draw,circle,inner sep=2pt](1){1};
+\node at (3,0) [draw,circle,inner sep=2pt](2){2};
+\node at (7,0) [draw,circle,inner sep=2pt](3){3};
+\node at (10,0) [draw,circle,inner sep=2pt](4){4};
+\node at (14,0) [draw,circle,inner sep=2pt](5){5};
+\node at (0,0) [draw=none,fill=none,label={[label distance=3pt]0:{NL query}}]
+{}; 
+\node at (3,0) [draw=none,fill=none,label={[label
+distance=3pt]0:{intermediate query}}] {}; 
+\node at (7,0) [draw=none,fill=none,label={[label
+distance=3pt]0:{query graph}}] {};
+\node at (10,0) [draw=none,fill=none,label={[label
+distance=3pt]0:{logic query graph}}] {};
+\node at (14,0) [draw=none,fill=none,label={[label
+distance=3pt]0:{database query}}] {};
+\draw[->](1) edge[bend left] (2);
+\draw[->](2) edge[bend left] (3);
+\draw[->](3) edge[bend left] (4);
+\draw[->](4) edge[bend left] (5);
+\end{tikzpicture}
+\caption{Big picture of NLI systems}
+\label{fig:big-picture}
+\end{figure*}
+
 \subsubsection{Predictability}
@@
 \label{sec:overview}
-
-\begin{figure}
-\centering
-\begin{tikzpicture}
-
-\def \n {5}
-\def \radius {3cm}
-\def \margin {8} % margin in angles, depends on the radius
-
-\foreach \s in {1,...,\n}
-{
-  \node[draw, circle] at ({360/\n * (\s - 1)}:\radius) {$\s$};
-  \draw[->, >=latex] ({360/\n * (\s - 1)+\margin}:\radius) 
-    arc ({360/\n * (\s - 1)+\margin}:{360/\n * (\s)-\margin}:\radius);
-}
-\end{tikzpicture}
-\caption{Big picture of NLI systems}
-\label{fig:big-picture}
-\end{figure}
 

### 2012-08-27 tr-nlisurvey/src/nli-survey.tex
commit

@@
 
+% multirow
 \usepackage{multirow}
+
+% url
 \usepackage{url}
+
+% allow colors for inline comments
 \usepackage{color}
 
+% draw pictures with tikz package
+\usepackage{tikz}
+\usetikzlibrary{arrows, petri, topaths}
+\usepackage{tkz-berge}
+
+\usepackage{rotating}
+
 \ifCLASSOPTIONcompsoc
@@
 Recently, new query languages have appeared (``no-SQL'').
-\TODO{Develop\ldots}
 
@@
 
+\begin{figure*}
+\centering
+\begin{tikzpicture}[transform shape]
+%\tikzset{VertexStyle/.append style = {minimum size = 3pt}}
+\node at (0,0) [draw,circle,inner sep=2pt](1){1};
+\node at (3,0) [draw,circle,inner sep=2pt](2){2};
+\node at (7,0) [draw,circle,inner sep=2pt](3){3};
+\node at (10,0) [draw,circle,inner sep=2pt](4){4};
+\node at (14,0) [draw,circle,inner sep=2pt](5){5};
+\node at (0,0) [draw=none,fill=none,label={[label distance=3pt]0:{NL query}}]
+{}; 
+\node at (3,0) [draw=none,fill=none,label={[label
+distance=3pt]0:{intermediate query}}] {}; 
+\node at (7,0) [draw=none,fill=none,label={[label
+distance=3pt]0:{query graph}}] {};
+\node at (10,0) [draw=none,fill=none,label={[label
+distance=3pt]0:{logic query graph}}] {};
+\node at (14,0) [draw=none,fill=none,label={[label
+distance=3pt]0:{database query}}] {};
+\draw[->](1) edge[bend left] (2);
+\draw[->](2) edge[bend left] (3);
+\draw[->](3) edge[bend left] (4);
+\draw[->](4) edge[bend left] (5);
+\draw[<->](1) edge[bend right] (3);
+\draw[->](4) edge[bend left] (3);
+\end{tikzpicture}
+\caption{Big picture of NLI systems}
+\label{fig:big-picture}
+\end{figure*}
+
 \subsubsection{Predictability}
@@
 \label{sec:overview}
-% \begin{figure*}
-% \centering
-% \includegraphics[width=12cm]{images/query-language}
-% \caption{Blabla}
-% \label{fig:query-languages}
-% \end{figure*}
+
+Figure~\ref{fig:big-picture} depicts the big picture of translating NL queries
+to database queries.
 
 \textbf{Classic translation approach}
-The classic translation approach consists in going from (1) to (4).
+The classic translation approach consists in going from
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {1}}}
+to \raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {5}}} through
+ \raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {2}}},
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}}
+and 
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {4}}} (step
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {2}}} being optional).
+
 To reach step (3), semantic rules are needed to find out what database elements
@@
 \textbf{Iterative approach}
-The iterative approach does not go directly from (1) to (3), but goes back to
-(1) several times before reaching step (3). 
+The iterative approach does not go directly from
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {1}}} to
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {4}}}, but goes back to
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}} (and/or to
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {4}}}) several times before
+reaching step \raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {5}}}.
 Those iterations correspond to question reformulations, that involve
@@
 
-\begin{table*}
+\begin{table}
 \centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|}\hline
+\rotatebox{90}{
+\begin{minipage}{\textheight}
+\begin{tabular}{|c|l|c|c|c|c|c|c|}\hline
 %\begin{tabular}{|c|c|c|c|c|c|c|c|}\hline
-\multirow{2}{*}{\bf Approach} & \multirow{2}{*}{\bf System} &
+\multirow{2}{*}{\bf Approach} & \multirow{2}{*}{\bf System}
+&
 \multicolumn{6}{c|}{\bf Dimensions}\\\cline{3-8}
@@
 \end{tabular}
+\end{minipage}
+}
 \caption{Overview of major NL interfaces to structured data}
 \label{tab:overview}
-\end{table*}
+\end{table}
 
@@
 is encoded in lexicon.
-The systems allows users to use a subset of English (controlled language) to
+The systems allow users to use a subset of English (controlled language) to
 query databases. 

### 2012-08-27 trunk/tr-nlisurvey/src/nli-survey.tex
Standard commit Following sections have been updated: section 4: picture
minor

@@
 \usepackage{tkz-berge}
+
+\usepackage{rotating}
 
@@
 \draw[->](4) edge[bend left] (5);
+\draw[<->](1) edge[bend right] (3);
+\draw[->](4) edge[bend left] (3);
 \end{tikzpicture}
@@
 (where the index corresponds to the \emph{rank} of the structured query):
-\begin{equation}
-f:\left\{
+% \begin{equation}
+$$f:\left\{
 \begin{array}{l}
@@
 q\mapsto(q^\prime_i)_i
-\end{array}\right.
-\end{equation}
+\end{array}\right.$$
+% \end{equation}
 where $i\in I=[0,n]$ is the index of $q^\prime_i$.
@@
 
+Figure~\ref{fig:big-picture} depicts the big picture of translating NL queries
+to database queries.
+
 \textbf{Classic translation approach}
-The classic translation approach consists in going from (1) to (4).
+The classic translation approach consists in going from
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {1}}}
+to \raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {5}}} through
+ \raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {2}}},
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}}
+and 
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {4}}} (step
+\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {2}}} being optional).
+
 To reach step (3), semantic rules are needed to find out what database elements

### 2012-09-17 tr-nlisurvey/src/nli-survey.tex
commit

@@
 The way translation from NL questions to formal query has evolved over years.
-Table~\ref{tab:overview} presents an overview of major systems that we consider
-in the survey.
+Table~\ref{tab:overview} presents an overview of major systems that we take into
+consideration in this survey.
 
@@
 \multirow{5}{*}{Complex question translation} & {\sc
-Chat-80}~\cite{Warren:1982:EEA:972942.972944} & & & & & & \\\cline{2-8}
-& {\sc Irus}~\cite{Bates:1983:IRU:511793.511804} & & & & & & \\\cline{2-8}
-& {\sc Qwerty}~\cite{Nelken:2000:QTD:992730.992808} & & & & & & \\\cline{2-8}
-& {\sc
+Chat-80}~\cite{Warren:1982:EEA:972942.972944} & & & & + & + & \\\cline{2-8}
+& {\sc Irus}~\cite{Bates:1983:IRU:511793.511804} & & & & + & & \\\cline{2-8}
+& {\sc Qwerty}~\cite{Nelken:2000:QTD:992730.992808} & & temporal & & - & &
+\\\cline{2-8} & {\sc
 Precise}~\cite{Popescu:2004:MNL:1220355.1220376,Popescu:2003:TTN:604045.604070}
-& & & & & & \\\cline{2-8}
-& {\sc Panto}~\cite{Wang:2007:PPN:1419662.1419706} & & & & & & \\\hline
+& & & & & & + \\\cline{2-8}
+& {\sc Panto}~\cite{Wang:2007:PPN:1419662.1419706} & & & & & + & + \\\hline
 \multirow{5}{*}{Feedback-driven approaches} &
-{\sc Masque/SQL}~\cite{Androutsopoulos93masque} & & & & & & \\\cline{2-8}
-& {\sc Team}~\cite{Grosz:1987:TED:25672.25674} & & & & & & \\\cline{2-8}
-& {\sc NaLIX} \& {\sc DaNaLIX}~\cite{Li:2005:NIN:1066157.1066281} & & & & & &
+{\sc Masque/SQL}~\cite{Androutsopoulos93masque} & & Prolog/SQL & & + & &
+\\\cline{2-8} & {\sc Team}~\cite{Grosz:1987:TED:25672.25674} & & & & + & & + \\\cline{2-8}
+& {\sc NaLIX} \& {\sc DaNaLIX}~\cite{Li:2005:NIN:1066157.1066281} & & & & + & &
 \\\cline{2-8}
@@
 & {\sc
-Orakel}~\cite{Cimiano:2007:PNL:1216295.1216330} & & & & & & \\\hline
+Orakel}~\cite{Cimiano:2007:PNL:1216295.1216330} & & & & + & & \\\hline
 \multirow{3}{*}{Learning-based approaches} & Zettlemoyer
@@
 bases) and ``learning-based approaches'' (because some of the systems
-represented in these approaches comprise learning components).
+represented in these approaches contain learning components).
 
@@
 systems do not talk to a single database, but to potentially an unlimited number
-of sources where the structured data are to be found. Each of those sources have
+of sources where the structured data are to be found. Each of those sources has
 its own logical schema, naming conventions, etc.
